### 2019-02-11 stats/kids_basic_me.Rmd
add first pass of me experiments

---
title: "Kids Basic Mutual Exclusivity"
author: "Manuel Bohn"
output: html_document
---

```{r import data, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

## importing data
files <- dir("~/Work/Spin/raw_data/kids/basic_me/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/Spin/raw_data/kids/basic_me/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,44,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

# length(unique(raw_data$subid))
# 
# d_raw <-raw_data %>%
#   mutate(test_date = as.Date(test_date),
#          experiment = "mcc_kids_inf_2_2",
#          subid= ifelse(subid=="193101_1_inf2","190131_1_inf2",subid))
# 
# log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
#   filter(Condition == "inf2")%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
# length(unique(log$subid))
# 
# 
# sum(log$keep_drop=="drop")
# 
# d <- left_join(d_raw,log, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(dob = as.numeric(dob),
#          dob = as.Date(dob,origin = "1899-12-30"),
#          age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
# 
# length(unique(d$subid))

#write_csv(d, "data/kids_inf_2_data.csv")

```

# Sample size per age bin

```{r kids per age group,echo = F }

d %>%
  group_by(subage)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)

```

# Plot filler by age

```{r filler by age, echo= FALSE, warning= FALSE}
pf1 <- d %>%
      filter(trial == "filler1" | trial == "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

pf2 <- pf1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = pf1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = pf2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Plot test trials by age bin

```{r plot by age, echo= FALSE}

p1 <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Plot with age as continuous variable

```{r plot by numerical age, echo = F}
p5 <- d %>%
  filter(trial != "filler1",
         trial != "filler2") %>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_smooth(method = "lm", se = T)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Performance by trial and age bin

```{r plot trials, echo = F}
ms <- d %>%
  filter(trial != "filler1",
         trial != "filler2") %>%
  group_by(subage, trial, subid) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = trial, y = mean, col = subage)) +
  geom_line(aes(group= subage)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

## T-tests against chance per age bin
```{r, echo = F}
## t tests against chance
d %>%
  filter(trial != "filler1",
         trial != "filler2") %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(subage,df,t_value,p_value) %>%
  knitr::kable(digits = 3)

```

## GLMM

```{r, include=F}
## model
library(lme4)

lm_data <- d%>%
  filter(trial != "filler1",
         trial != "filler2") %>%
  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))

# maximal converging model
lm <- glmer(correct ~ age_num + (1 | subid), 
              data = lm_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```

```{r, echo = F}
summary(lm)
```

# Effect of target position

Target was either the closer (inner) or further away (outer) object.

```{r, echo = F}
p5 <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by( subage, targetPosition, subid) %>%
  summarise(correct = mean(correct))

p6 <- p5 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p5, aes(x = targetPosition, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p6, aes(x = targetPosition, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Target switch

In half of the trials, the target switched sides from exposure to test.

```{r, echo = F}
p7 <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by( subage, targetSwitch, subid) %>%
  summarise(correct = mean(correct))

p8 <- p7 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p7, aes(x = targetSwitch, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p8, aes(x = targetSwitch, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Joining round 1 and round 2

```{r}
files <- dir("~/Work/MCC/git-mcc/kids_info_data/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,45,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

d_raw <-raw_data %>%
  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
         subid= ifelse(subid == "181031_3", "181031_3_inf",subid),
         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
         test_date= ifelse(test_date == "18-09-12", "2018-09-12",test_date),
         experiment = "mcc_kids_inf_2")

log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "inf")%>%
  select(subid,experimenter,keep_drop,sex,dob)

d2 <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

d_sum <- bind_rows(d%>%select(-test_date),d2%>%select(-test_date)%>%filter(subage!="2"))%>%
    filter(trial != "filler1",
         trial != "filler2")

```

```{r}
d_sum %>%
  group_by(subage)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

```{r plot by age, echo= FALSE}

p_sum1 <- d_sum %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

p_sum2 <- p_sum1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p_sum1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p_sum2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Plot with age as continuous variable

```{r plot by numerical age, echo = F}
p_sum3 <- d_sum %>%
  filter(trial != "filler1",
         trial != "filler2") %>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p_sum3, aes(x = age_num, y = correct)) +
  geom_smooth(method = "lm", se = T)+
  geom_point( alpha = .5, width = 0.02)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

```{r, include=F}
## model
library(lme4)

lm_data_sum <- d_sum%>%
  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))

# maximal converging model
lm_sum <- glmer(correct ~ age_num + (1 | subid), 
              data = lm_data_sum, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

```

```{r, echo = F}
summary(lm_sum)
```

### 2019-02-11 stats/kids_me_novel.Rmd
add first pass of me experiments

--- 2019-02-11 stats/kids_basic_me.Rmd
@@
 ## importing data
-files <- dir("~/Work/Spin/raw_data/kids/basic_me/")
+files <- dir("~/Work/Spin/raw_data/kids/me_novel/")
 
@@
 for (f in files) {
-  jf <- paste("~/Work/Spin/raw_data/kids/basic_me/",f,sep="")
+  jf <- paste("~/Work/Spin/raw_data/kids/me_novel/",f,sep="")
   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))

### 2019-02-11 experiments/adults/adults_me.js

@@ -1,0 +1,516 @@
+// preload
+var preObjects = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png"];
+//for critical trials and fillers
+var images = new Array();
+for (i = 0; i < preObjects.length; i++) {
+	images[i] = new Image();
+	images[i].src = "images/" + preObjects[i];
+    images[i].id = preObjects[i];
+}
+
+
+var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3"];
+//for critical trials and fillers
+var sound = new Array();
+for (i = 0; i < preSounds.length; i++) {
+	sound[i] = new Audio();
+	sound[i].src = "sound/" + preSounds[i];
+}
+
+// ## Helper functions
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+  // Hide all slides
+	$(".text").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+  // Hide all slides
+	$(".agent").hide();
+}
+
[…]

### 2019-02-11 experiments/kids/kids_me.js

@@ -1,0 +1,513 @@
+// preload
+var preObjects = ["duck.png","car.png","bear.png","ball.png","t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t06.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png"];
+//for critical trials and fillers
+var images = new Array();
+for (i = 0; i < preObjects.length; i++) {
+	images[i] = new Image();
+	images[i].src = "images/" + preObjects[i];
+    images[i].id = preObjects[i];
+}
+
+
+var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3"];
+//for critical trials and fillers
+var sound = new Array();
+for (i = 0; i < preSounds.length; i++) {
+	sound[i] = new Audio();
+	sound[i].src = "sound/" + preSounds[i];
+}
+
+// ## Helper functions
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+  // Hide all slides
+	$(".text").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+  // Hide all slides
+	$(".agent").hide();
+}
+
[…]

### 2019-02-11 experiments/kids/kids_me_novel.js

@@ -1,0 +1,777 @@
+// preload
+var preObjects = ["duck.png","car.png","bear.png","ball.png","t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t06.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png"];
+//for critical trials and fillers
+var images = new Array();
+for (i = 0; i < preObjects.length; i++) {
+	images[i] = new Image();
+	images[i].src = "images/" + preObjects[i];
+    images[i].id = preObjects[i];
+}
+
+
+var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3"];
+//for critical trials and fillers
+var sound = new Array();
+for (i = 0; i < preSounds.length; i++) {
+	sound[i] = new Audio();
+	sound[i].src = "sound/" + preSounds[i];
+}
+
+// ## Helper functions
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+  // Hide all slides
+	$(".text").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+  // Hide all slides
+	$(".agent").hide();
+}
+
[…]

### 2019-02-11 experiments/kids/mmturkey_spin_kids_me.js

@@ -1,0 +1,263 @@
+// Bundle in Crockford's JSON2.js
+var JSON;JSON||(JSON={});
+(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
+e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
+"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2019-02-11 experiments/kids/mmturkey_spin_kids_me_novel.js

@@ -1,0 +1,263 @@
+// Bundle in Crockford's JSON2.js
+var JSON;JSON||(JSON={});
+(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
+e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
+"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2019-02-21 stats/kids_familiar_words.Rmd
add images and AoA ratings

---
title: "Familiar words AoA ratings"
author: "Manuel Bohn"
output: html_document
---

```{r import data, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(readxl)
library(ggimage)

## importing data

all_d <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)

spin_words <- c(
"shoe",
"carrot",
"hat",
"duck",
"bottle",
"cup",
"bread",
"bear",
"truck",
"phone",
"apple",
"horse",
"bowl",
"kite",
"cone",
"tent",
"pencilsharpener",
"horseshoe",
"plug",
"grill",
"garlic",
"antenna",
"violin",
"gear",
"barrel",
"eggplant",
"stethoscope",
"pawn",
"papaya",
"laptop")

d <- all_d %>%
  filter(Word %in% spin_words )%>%
  mutate(Rating.Mean = as.numeric(Rating.Mean))

```

```{r}

spin_select <- c("carrot","duck","bread","apple","kite","horseshoe","plug","garlic","barrel","eggplant","pawn","papaya")

d_select <- d %>%
  mutate(select = if_else(d$Word %in% select, 1.5,-1),
         image = paste("../experiments/kids/images/",Word,".png", sep=""))
```

# Plot by AoA rating
```{r, fig.height=12}

ggplot(d_select, aes(x = reorder(Word, Rating.Mean), y = Rating.Mean)) +
  theme_light(base_size = 22) +
  geom_point(size =5, aes(col = as.character(select)))+
  ylab("Mean Age of Acquisition rating")+
  xlab("Word")+
  guides(col =F)+
  ylim(0,15)+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  geom_linerange(aes(ymin = Rating.Mean+select, ymax = Rating.Mean))+
  geom_image(aes(image=image, y = Rating.Mean+select), asp = 2)+
  scale_color_solarized()

```

### 2019-02-21 experiments/kids/kids_me.js

@@ -159,7 +159,7 @@ var  testNovels= shuffle(["t01","t02","t03","t04","t06","t07","t08","t09","t11",
 var novels = trainNovels.concat(testNovels);
 
 var trainFamiliars = ["t13","t10"];
-var  testFamiliars= shuffle(["papaya","gear","truck","bread","horse","truck","antenna","tent","bottle","apple","hat","bean","cup","bowl","bear","duck","garlic","sharpener","grill","kite","eggplant","mouse","laptop","stethoscope","plug","balloon","cone","phone"]);
+var  testFamiliars= shuffle(["papaya","gear","bread","horse","truck","antenna","tent","bottle","apple","hat","bean","cup","bowl","bear","duck","garlic","sharpener","grill","kite","eggplant","mouse","laptop","stethoscope","plug","balloon","cone","phone"]);
 var familiars = trainFamiliars.concat(testFamiliars);
 
 // orientation of agent 

### 2019-02-24 stats/data_sim.Rmd
add data sim for one item

---
title: "Spin data simulation"
author: "Manuel Bohn"
output: html_document
---

```{r, message=F, warning=F}
library(tidyverse)
library(purrr)
library(copula)
library(langcog)
library(ggthemes)
```

# Data simulation for one item

## Item specs

*Average ME effect across age = 0.6

*Correlation between age and ME effect = 0.3

## Simulation specs

*100 simualtions for each age bin

```{r}
fun <- function (n){
  tmp <- normalCopula(
    0.3, # correlation btw. age and ME effect
    dim=2 )
  x <- rCopula(n, tmp)
  correct = qbinom(
    x[,1], 
    1, 
    .6) # average ME effect
  age= x[,2]

  data.frame(age = age,
             correct = correct)

}

n_sim <- 100

sim_60 <- map(seq_len(n_sim), ~fun(60))%>%
  map_df(bind_rows)%>%
  mutate(case = rep(1:60,length(seq_len(n_sim))),
         iter = rep(1:length(seq_len(n_sim)), each = 60),
         age_bin=cut(age, breaks=c(0, 1/3, 2/3, 1), labels=c("2","3","4")),
         sample = "n = 20 / age bin")

sim_90 <- map(seq_len(n_sim), ~fun(90))%>%
  map_df(bind_rows)%>%
  mutate(case = rep(1:90,length(seq_len(n_sim))),
         iter = rep(1:length(seq_len(n_sim)), each = 90),
         age_bin=cut(age, breaks=c(0, 1/3, 2/3, 1), labels=c("2","3","4")),
         sample = "n = 30 / age bin")

sim_120 <- map(seq_len(n_sim), ~fun(120))%>%
  map_df(bind_rows)%>%
  mutate(case = rep(1:120,length(seq_len(n_sim))),
         iter = rep(1:length(seq_len(n_sim)), each = 120),
         age_bin=cut(age, breaks=c(0, 1/3, 2/3, 1), labels=c("2","3","4")),
         sample = "n = 40 / age bin")

sim <- bind_rows(sim_60,sim_90,sim_120)
```

## Plotting the 100 simulations with age continuous

```{r plot, fig.width=10, fig.height=5}

ggplot(data = sim, aes(x = age, y = correct, group = iter, col = sample)) +
  geom_smooth(method = "glm", se = T, size = 0.25, alpha = .04)+
  geom_hline(yintercept = 0.5, lty=2)+
  facet_grid(~sample)+
  ylab("ME effect")+
  ylim(0,1)+
  theme_few()

```

## Plotting the 100 simulations by age bin

Each point is the mean from one simulation (with 95%CI). No vertical jitter.

```{r}
sim_bin <- sim %>%
  group_by(sample, iter, age_bin)%>%
  multi_boot_standard(col = "correct")

ggplot(sim_bin, aes(x = age_bin, y = mean, col = age_bin)) +
  geom_pointrange( aes(ymin = ci_lower, ymax = ci_upper),size = .3, alpha = .2, position = position_jitter(width = 0.35,height = 0))+
  geom_hline(yintercept = 0.5, lty=2)+
  facet_grid(~sample)+
  ylab("ME effect")+
  ylim(0,1)+
  theme_few() 
```

### 2019-02-24 experiments/adults/adults_me.js

@@ -1,516 +1,0 @@
-// preload
-var preObjects = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png"];
-//for critical trials and fillers
-var images = new Array();
-for (i = 0; i < preObjects.length; i++) {
-	images[i] = new Image();
-	images[i].src = "images/" + preObjects[i];
-    images[i].id = preObjects[i];
-}
-
-
-var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3"];
-//for critical trials and fillers
-var sound = new Array();
-for (i = 0; i < preSounds.length; i++) {
-	sound[i] = new Audio();
-	sound[i].src = "sound/" + preSounds[i];
-}
-
-// ## Helper functions
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-function showText(id) {
-  // Hide all slides
-	$(".text").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-
-function showAgent(id, orient) {
-	$(".agent").hide();
-    $(".point_agent_l").hide();
-    $(".point_agent_r").hide();
-	$("#"+id+"_"+orient).show();
-}
-
-function hideAgent() {
-  // Hide all slides
-	$(".agent").hide();
-}
-
[…]

### 2019-02-24 experiments/kids/kids_me.js

@@ -159,7 +159,7 @@ var  testNovels= shuffle(["t01","t02","t03","t04","t06","t07","t08","t09","t11",
 var novels = trainNovels.concat(testNovels);
 
 var trainFamiliars = ["t13","t10"];
-var  testFamiliars= shuffle(["papaya","gear","bread","horse","truck","antenna","tent","bottle","apple","hat","bean","cup","bowl","bear","duck","garlic","sharpener","grill","kite","eggplant","mouse","laptop","stethoscope","plug","balloon","cone","phone"]);
+var  testFamiliars= shuffle(["pawn","horseshoe","carrot","barrel","papaya","bread","apple","duck","garlic","kite","eggplant","plug"]);
 var familiars = trainFamiliars.concat(testFamiliars);
 
 // orientation of agent 

### 2019-03-01 stats/kids_basic_me.Rmd
update fam picture plot

@@
 # 
-# d_raw <-raw_data %>%
-#   mutate(test_date = as.Date(test_date),
-#          experiment = "mcc_kids_inf_2_2",
-#          subid= ifelse(subid=="193101_1_inf2","190131_1_inf2",subid))
+d_raw <-raw_data %>%
+  mutate(test_date = as.Date(test_date))
 # 
-# log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
-#   filter(Condition == "inf2")%>%
-#   select(subid,experimenter,keep_drop,sex,dob)
+log <- read_excel("../../../SPIN-subject_log.xlsx", 1)%>%
+  filter(Condition == "me")%>%
+  select(subid,experimenter,keep_drop,sex,dob)
 # 
@@
 # 
-# d <- left_join(d_raw,log, by = "subid")%>%
-#   filter(keep_drop == "keep")%>%
-#   mutate(dob = as.numeric(dob),
-#          dob = as.Date(dob,origin = "1899-12-30"),
-#          age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-#          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+d <- left_join(d_raw,log, by = "subid")%>%
+  filter(keep_drop == "keep")%>%
+  mutate(dob = as.numeric(dob),
+         dob = as.Date(dob,origin = "1899-12-30"),
+         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
 # 

### 2019-03-29 stats/kids_basic_me.Rmd
kids novelty exp

@@
 library(readxl)
+library(brms)
+library(here)
+library(brmstools)
+library(ggpubr)
+library(rwebppl)
 
 ## importing data
+
 files <- dir("~/Work/Spin/raw_data/kids/basic_me/")
@@
 
-# length(unique(raw_data$subid))
-# 
+length(unique(raw_data$subid))
+
 d_raw <-raw_data %>%
-  mutate(test_date = as.Date(test_date))
-# 
-log <- read_excel("../../../SPIN-subject_log.xlsx", 1)%>%
+  mutate(subid = ifelse(subid == "190314_3", "190314_3_me",subid),
+         subid = ifelse(subid == "190221_6_me", "190321_6_me",subid),
+         subid = ifelse(subid == "192203_4_me", "190322_4_me",subid),
+         subage = ifelse(subid == "190313_5_me", "3",subage),
+         test_date = as.Date(test_date))
+
+log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
   filter(Condition == "me")%>%
+  mutate(dob = as.character(dob),
+         dob = ifelse(subid == "190313_7_me", "2015-11-15",dob),
+         dob = ifelse(subid == "190313_11_me", "2016-04-18",dob),
+         dob = ifelse(subid == "190320_8_me", "2014-04-28",dob),
+         dob = as.Date(dob))%>%
   select(subid,experimenter,keep_drop,sex,dob)
-# 
-# length(unique(log$subid))
-# 
-# 
-# sum(log$keep_drop=="drop")
-# 
+
+d_raw%>%
+  group_by(subid)%>%
+  summarise(n())%>%
+  filter(!(subid %in% unique(log$subid)))
+
 d <- left_join(d_raw,log, by = "subid")%>%
   filter(keep_drop == "keep")%>%
-  mutate(dob = as.numeric(dob),
-         dob = as.Date(dob,origin = "1899-12-30"),
-         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
-# 
-# length(unique(d$subid))
 
-#write_csv(d, "data/kids_inf_2_data.csv")
+#write_csv(d, "../data/child_basic_me.csv")
 
@@
 pf1 <- d %>%
-      filter(trial == "filler1" | trial == "filler2")%>%
-  group_by(control,subage, subid) %>%
+      filter(trial == "train1" | trial == "train2")%>%
+  group_by(subage, subid) %>%
   summarise(correct = mean(correct))
@@
 ggplot() +
-  geom_jitter(data = pf1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = pf2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = pf1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = pf2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   theme_few() +
-  facet_wrap(~subage)+
   ylim(-0.05,1.05)+
@@
   theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+  scale_colour_solarized()
 ```
 
-# Plot test trials by age bin
+# Itmes by age bin
 
 ```{r plot by age, echo= FALSE}
+aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
+
+aoa_ratings <- aoa_ratings_all %>%
+  filter(Word %in% d_raw$familiar )%>%
+  mutate(mean_aoa = as.numeric(Rating.Mean),
+         familiar = Word)%>%
+  select(familiar,mean_aoa)
 
 p1 <- d %>%
-  filter(trial != "filler1",
-         trial != "filler2")%>%
-  group_by(control,subage, subid) %>%
-  summarise(correct = mean(correct))
+  filter(trial != "train1",
+         trial != "train2")%>%
+  group_by(subage, familiar) %>%
+  multi_boot_standard(col = "correct")%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
 
-p2 <- p1 %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+ggplot(data = p1, aes(x = familiar, y = mean, group=1, col = subage)) +
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),size = .8)+
+  stat_summary(aes(group = subage, col = subage),fun.y=mean, geom="line")+
+  labs(x="",y="Proportion Correct")+
   theme_few() +
-  facet_wrap(~subage)+
   ylim(-0.05,1.05)+
   guides(alpha = F)+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  scale_colour_solarized()
 ```
@@
 ```{r plot by numerical age, echo = F}
-p5 <- d %>%
-  filter(trial != "filler1",
-         trial != "filler2") %>%
-  group_by(age_num, subid) %>%
-  summarise(correct = mean(correct))
+p2 <- d %>%
+  filter(trial != "train1",
+         trial != "train2")%>%
+    left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
 
-ggplot(data = p5, aes(x = age_num, y = correct)) +
-  geom_smooth(method = "lm", se = T)+
-  geom_jitter( alpha = .5, height = 0.04)+
+data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
+  geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
+  labs(x="Age",y="Proportion correct")+
+  #facet_grid(~familiar)+
+  ggtitle("Data")+
+  guides(col = F, fill = F)+
   theme_few() +
   ylim(-0.05,1.05)+
+  xlim(2,5)+
   guides(alpha = F)+ 
-  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Speaker Change",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+  scale_colour_viridis_d(name = "familiar object")+
+  scale_fill_viridis_d(name = "familiar object")
 ```
 
-# Performance by trial and age bin
+```{r}
+d_model <- d %>%
+    filter(trial != "train1",
+         trial != "train2")%>%
+  mutate(age_num = scale(age_num))
 
-```{r plot trials, echo = F}
-ms <- d %>%
-  filter(trial != "filler1",
-         trial != "filler2") %>%
-  group_by(subage, trial, subid) %>%
-  summarise(correct = mean(correct)) %>%
-  multi_boot_standard(col = "correct")
+model <- brm(correct ~ age_num + (1|subid) + (age_num | familiar),
+                    data = d_model, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
 
-ggplot(ms, 
-       aes(x = trial, y = mean, col = subage)) +
-  geom_line(aes(group= subage)) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
+summary(model)
+
+fixef <- as_tibble(fixef(model), rownames = "term")
+
+ranef <-  ranef(model)
+
+ranef_plot <- as_tibble(ranef$familiar, rownames = "familiar")%>%
+  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
+         grand_slope = fixef%>%filter(term=="age_num")%>%pull(Estimate))%>%
+  group_by(familiar) %>%
+  expand(Estimate.Intercept,Estimate.age_num,grand_intercept,grand_slope,age = scale(d$age_num))%>%
+  mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age_num+grand_slope)*age), 
+         age = age+mean(d$age_num))%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
+
+model_plot <- ggplot(ranef_plot, aes(x=age,y = y, col = familiar))+
   geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(size = 1)+
+  ggtitle("Model")+
+  labs(x="Age",y="Proportion correct")+
   theme_few() +
-  scale_colour_solarized()
-```
-
-## T-tests against chance per age bin
-```{r, echo = F}
-## t tests against chance
-d %>%
-  filter(trial != "filler1",
-         trial != "filler2") %>%
-  group_by(subage, subid) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(subage) %>%
-  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(subage,df,t_value,p_value) %>%
-  knitr::kable(digits = 3)
-
-```
-
-## GLMM
-
-```{r, include=F}
-## model
-library(lme4)
-
-lm_data <- d%>%
-  filter(trial != "filler1",
-         trial != "filler2") %>%
-  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
-
-# maximal converging model
-lm <- glmer(correct ~ age_num + (1 | subid), 
-              data = lm_data, family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-```
-
-```{r, echo = F}
-summary(lm)
-```
-
-# Effect of target position
-
-Target was either the closer (inner) or further away (outer) object.
-
-```{r, echo = F}
-p5 <- d %>%
-  filter(trial != "filler1",
-         trial != "filler2")%>%
-  group_by( subage, targetPosition, subid) %>%
-  summarise(correct = mean(correct))
-
-p6 <- p5 %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p5, aes(x = targetPosition, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p6, aes(x = targetPosition, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few() +
-  facet_wrap(~subage)+
   ylim(-0.05,1.05)+
+  xlim(2,5)+
   guides(alpha = F)+ 
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-```
-
-# Target switch
-
-In half of the trials, the target switched sides from exposure to test.
-
-```{r, echo = F}
-p7 <- d %>%
-  filter(trial != "filler1",
-         trial != "filler2")%>%
-  group_by( subage, targetSwitch, subid) %>%
-  summarise(correct = mean(correct))
-
-p8 <- p7 %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p7, aes(x = targetSwitch, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p8, aes(x = targetSwitch, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few() +
-  facet_wrap(~subage)+
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-```
-
-# Joining round 1 and round 2
-
-```{r}
-files <- dir("~/Work/MCC/git-mcc/kids_info_data/")
-
-raw_data <- data_frame()
-for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
-  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,45,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
-  raw_data <- bind_rows(raw_data, id)
-}
-
-d_raw <-raw_data %>%
-  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
-         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
-         subid= ifelse(subid == "181031_3", "181031_3_inf",subid),
-         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
-         test_date= ifelse(test_date == "18-09-12", "2018-09-12",test_date),
-         experiment = "mcc_kids_inf_2")
-
-log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
-  filter(Condition == "inf")%>%
-  select(subid,experimenter,keep_drop,sex,dob)
-
-d2 <- left_join(d_raw,log, by = "subid")%>%
-  filter(keep_drop == "keep")%>%
-  mutate(dob = as.numeric(dob),
-         dob = as.Date(dob,origin = "1899-12-30"),
-         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
-
-d_sum <- bind_rows(d%>%select(-test_date),d2%>%select(-test_date)%>%filter(subage!="2"))%>%
-    filter(trial != "filler1",
-         trial != "filler2")
+  scale_colour_viridis_d(name = "familiar object")
 
@@
 ```{r}
-d_sum %>%
-  group_by(subage)%>%
-  summarise(n = length(unique(subid)))%>%
-  knitr::kable(digits = 2)
+ggarrange(data_plot,model_plot, common.legend = T, legend = "right")
 ```
 
-```{r plot by age, echo= FALSE}
+```{r}
 
-p_sum1 <- d_sum %>%
-  filter(trial != "filler1",
-         trial != "filler2")%>%
-  group_by(control,subage, subid) %>%
-  summarise(correct = mean(correct))
+cor_plot <- as_tibble(ranef$familiar, rownames = "familiar") %>%
+  left_join(aoa_ratings)
 
-p_sum2 <- p_sum1 %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p_sum1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p_sum2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few() +
-  facet_wrap(~subage)+
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-```
-
-# Plot with age as continuous variable
-
-```{r plot by numerical age, echo = F}
-p_sum3 <- d_sum %>%
-  filter(trial != "filler1",
-         trial != "filler2") %>%
-  group_by(age_num, subid) %>%
-  summarise(correct = mean(correct))
-
-ggplot(data = p_sum3, aes(x = age_num, y = correct)) +
-  geom_smooth(method = "lm", se = T)+
-  geom_point( alpha = .5, width = 0.02)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Speaker Change",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-```
-
-```{r, include=F}
-## model
-library(lme4)
-
-lm_data_sum <- d_sum%>%
-  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
-
-# maximal converging model
-lm_sum <- glmer(correct ~ age_num + (1 | subid), 
-              data = lm_data_sum, family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+ggplot(cor_plot, aes(x = mean_aoa, y = Estimate.Intercept))+
+  geom_point()+
+  geom_smooth(method = "lm")+
+  xlab("Age of acquisition rating")+
+  ylab("ME effect (model intercept)")+
+  stat_cor(method = "pearson", label.x = 8, label.y = .99)+
+  coord_fixed(ratio = 2)+
+  theme_few()
 
 ```
-
-```{r, echo = F}
-summary(lm_sum)
-```

### 2019-03-29 stats/kids_novelty.Rmd
kids novelty exp

---
title: "SPIN Novelty"
author: "Manuel Bohn"
output: html_document
---

```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = FALSE)
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(brms)
library(here)
library(brmstools)
library(ggpubr)
library(rwebppl)

# import spin data

files <- dir("~/Work/Spin/raw_data/kids/novelty/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/Spin/raw_data/kids/novelty/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,46,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

length(unique(raw_data$subid))

d_raw <-raw_data %>%
  mutate(test_date = as.Date(test_date))

log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
  filter(Condition == "nov")%>%
  mutate(dob = as.character(dob),
         dob = as.Date(dob))%>%
  select(subid,experimenter,keep_drop,sex,dob)

d_raw%>%
  group_by(subid)%>%
  summarise(n())%>%
  filter(!(subid %in% unique(log$subid)))

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep",
         trial != "train1", trial != "train2")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
  select(-pick_src)

## import mcc data

files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")

raw_data_mcc <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,51,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data_mcc <- bind_rows(raw_data_mcc, id)
}

d_raw_mcc <-raw_data_mcc %>%
  mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
         test_date = as.Date(test_date))

log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "nov")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"))%>%
  select(subid,experimenter,keep_drop,sex,dob)

d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         leftObject = leftFruit,
         rightObject = rightFruit, 
         pick = str_sub(pick,72,str_length(pick)-4),
         condition = "dis_novelty_mcc")%>%
  filter(speakerChange == "false", trial != "train")%>%
  select(-speakerChange,-altAgent,-leftFruit,-rightFruit)

# join datasets

d <- bind_rows(d, d_mcc)

```

```{r sanity checks, echo = FALSE,warning = FALSE, message = FALSE}

## sanity checks
d %>%
  group_by(condition,subage) %>%
  summarise(n = length(unique(subid)))

```

```{r}
p1 <- d %>%
  group_by(condition,subage, subid) %>%
  summarise(correct = mean(correct))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = subage, y = correct, col = condition, alpha = .2),width = .3,height = .025, position = position_dodge(width = .5))+
  geom_pointrange(data = p2, aes(x = subage, y = mean, col = condition, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_color_solarized()
```

## Plot with age as continuous variable

```{r plot by numerical age}
p5 <- d %>%
  group_by(condition,age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct, col = condition)) +
  geom_smooth(data = d, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized()
```

## GLMM

```{r}
## model
library(brms)

model_data <- d%>%
  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))

# maximal converging model
bm <- brm(correct ~ age_num * condition + (1 | subid) + (age_num * condition | agent), 
          data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

summary(bm)

```

### 2019-03-29 experiments/kids/kids_novel.js

@@ -1,0 +1,668 @@
+// preload
+var preObjects = ["duck.png","car.png","bear.png","ball.png","t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t06.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png", "t19.png","t20.png","t21.png","t22.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png"];
+//for critical trials and fillers
+var images = new Array();
+for (i = 0; i < preObjects.length; i++) {
+	images[i] = new Image();
+	images[i].src = "images/" + preObjects[i];
+    images[i].id = preObjects[i];
+}
+
+var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3", ];
+//for critical trials and fillers
+var sound = new Array();
+for (i = 0; i < preSounds.length; i++) {
+	sound[i] = new Audio();
+	sound[i].src = "sound/" + preSounds[i];
+}
+
+// ## Helper functions
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+  // Hide all slides
+	$(".text").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+  // Hide all slides
[…]

### 2019-03-29 experiments/kids/mmturkey_spin_kids_novel.js

@@ -1,0 +1,263 @@
+// Bundle in Crockford's JSON2.js
+var JSON;JSON||(JSON={});
+(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
+e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
+"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2019-03-29 experiments/kids/kids_novel.js
kids novelty exp

@@ -394,13 +394,13 @@ pause: function () {
     };
     
     
-    // choice can be made by clicking the objects after - possible after 8s
+    // choice can be made by clicking the objects after - possible after 5s
     setTimeout(function() {
         $(".object_l").click(experiment.eat);
 
         $(".object_r").click(experiment.eat);
 
-    }, 000);
+    }, 5000);
   },
         
 // moving on within a trial

### 2019-04-10 stats/kids_basic_me.Rmd
add kids basic me data

@@
 
-```{r import data, include = F}
-###
+```{r setup}
 library(tidyverse)
@@
 library(rwebppl)
+```
 
-## importing data
+Importing and processing raw data locally (see next chunk for loading processed data)
+
+```{r import data, include = F}
+## importing data locally
 
@@
 #write_csv(d, "../data/child_basic_me.csv")
+```
 
+```{r}
+# import data
+d <- read_csv("../data/child_basic_me.csv")%>%
+  mutate(subage = factor(subage))
+
+aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
+
+aoa_ratings <- aoa_ratings_all %>%
+  filter(Word %in% d_raw$familiar )%>%
+  mutate(mean_aoa = as.numeric(Rating.Mean),
+         familiar = Word)%>%
+  select(familiar,mean_aoa)
 ```
@@
 ```{r plot by age, echo= FALSE}
-aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
-
-aoa_ratings <- aoa_ratings_all %>%
-  filter(Word %in% d_raw$familiar )%>%
-  mutate(mean_aoa = as.numeric(Rating.Mean),
-         familiar = Word)%>%
-  select(familiar,mean_aoa)
-
 p1 <- d %>%
@@
   geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
-  labs(x="Age",y="Proportion correct")+
+  labs(x="Age",y="Mutual Exclusivity effect")+
   #facet_grid(~familiar)+
   ggtitle("Data")+
-  guides(col = F, fill = F)+
   theme_few() +
@@
 ```
+
+```{r}
+reduced_model <- brm(correct ~ 1 + (1|subid) + (age_num | familiar),
+                    data = d_model, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
+
+summary(reduced_model)
+
+child_waic <- brms::WAIC(model, reduced_model, compare = F)
+
+child_weights <- model_weights(model, reduced_model)
+
+# Bayes Factors (slightly variable)
+bf_full_null <- bayes_factor(model, reduced_model, log = F, maxiter = 5000)
+
+data_frame(
+  model = c("model_w_age","reduced_model"),
+  WAIC = c(child_waic$model$estimates[3,1],child_waic$reduced_model$estimates[3,1]),
+  SE = c(child_waic$model$estimates[3,2],child_waic$reduced_model$estimates[3,2]),
+  weight = c(child_weights[1],child_weights[2]),
+  BF10 = c(round(bf_full_null$bf,2),"-"))%>%
+  mutate_if(is.numeric, round, 2)
+```

### 2019-04-10 stats/kids_novelty.Rmd
add kids basic me data

@@
 
-d <- bind_rows(d, d_mcc)
+d <- bind_rows(d_raw, d_mcc)
 
@@
 ggplot() +
-  geom_jitter(data = p1, aes(x = subage, y = correct, col = condition, alpha = .2),width = .3,height = .025, position = position_dodge(width = .5))+
+  geom_point(data = p1, aes(x = subage, y = correct, col = condition, alpha = .2), position = position_jitterdodge(dodge.width = .6, jitter.width = .2, jitter.height = .05))+
   geom_pointrange(data = p2, aes(x = subage, y = mean, col = condition, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .5))+
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Correct")+
+  labs(x="Age",y="Proportion Correct")+
   theme_few() +
@@
   guides(alpha = F)+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
   scale_color_solarized()
+
 ```
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
+  labs(x="Age",y="Proportion Expected Choice")+
   theme_few() +

### 2019-04-10 stats/kids_basic_me.Rmd
update combination experiment

@@
 
+## Facets by item
+
+```{r plot by numerical age, echo = F}
+p2 <- d %>%
+  filter(trial != "train1",
+         trial != "train2")%>%
+    left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
+
+ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(~familiar)+
+  ggtitle("Data")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d(name = "familiar object")+
+  scale_fill_viridis_d(name = "familiar object")
+```
+
 ```{r plot by numerical age, echo = F}
@@
   ggtitle("Data")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d(name = "familiar object")+
+  scale_fill_viridis_d(name = "familiar object")
+```
+
+```{r plot by numerical age, echo = F}
+p4 <- d %>%
+  filter(trial != "train1",
+         trial != "train2")%>%
+    group_by(subage,age_num,subid,subage)%>%
+  multi_boot_standard(col = "correct")
+
+ggplot(data = p4, aes(x = age_num, y = mean)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_smooth(method = "lm", se = T, alpha = .5)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
   theme_few() +

### 2019-04-10 stats/kids_combination.Rmd
update combination experiment

---
title: "Kids Combination"
author: "Manuel Bohn"
output: html_document
---

```{r import data, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

## importing data
files <- dir("~/Work/Spin/raw_data/kids/combination/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/Spin/raw_data/kids/combination/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,56,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

raw_data %>%
  mutate(discourseNovel = str_sub(discourseNovel,11),
         mutExNovel = str_sub(mutExNovel, 10))

```

### 2019-04-10 stats/kids_novelty.Rmd
update combination experiment

@@
   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
+         experiment = condition)%>%
   select(-pick_src)
@@
          pick = str_sub(pick,72,str_length(pick)-4),
-         condition = "dis_novelty_mcc")%>%
+         experiment = "dis_novelty_mcc")%>%
   filter(speakerChange == "false", trial != "train")%>%
@@
 d %>%
-  group_by(condition,subage) %>%
+  group_by(experiment,subage) %>%
   summarise(n = length(unique(subid)))
@@
 p1 <- d %>%
-  group_by(condition,subage, subid) %>%
+  group_by(experiment,subage, subid) %>%
   summarise(correct = mean(correct))
@@
 ggplot() +
-  geom_point(data = p1, aes(x = subage, y = correct, col = condition, alpha = .2), position = position_jitterdodge(dodge.width = .6, jitter.width = .2, jitter.height = .05))+
-  geom_pointrange(data = p2, aes(x = subage, y = mean, col = condition, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .5))+
+  geom_point(data = p1, aes(x = subage, y = correct, col = experiment, alpha = .2), position = position_jitterdodge(dodge.width = .6, jitter.width = .2, jitter.height = .05))+
+  geom_pointrange(data = p2, aes(x = subage, y = mean, col = experiment, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .5))+
   geom_hline(yintercept = 0.5, lty=2)+
@@
 p5 <- d %>%
-  group_by(condition,age_num, subid) %>%
+  group_by(experiment,age_num, subid) %>%
   summarise(correct = mean(correct))
 
-ggplot(data = p5, aes(x = age_num, y = correct, col = condition)) +
+ggplot(data = p5, aes(x = age_num, y = correct, col = experiment)) +
   geom_smooth(data = d, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
@@
 # maximal converging model
-bm <- brm(correct ~ age_num * condition + (1 | subid) + (age_num * condition | agent), 
+bm <- brm(correct ~ age_num * experiment + (1 | subid) + (age_num * experiment | agent), 
           data = model_data, family = bernoulli(),

### 2019-04-10 experiments/kids/kids_combination.js

@@ -1,5 +1,5 @@
 // preload
-var preObjects = ["duck.png","car.png","bear.png","ball.png","t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t19.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png","t20.png","t21.png","t22.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png"];
+var preObjects = ["duck.png","car.png","bear.png","ball.png","t01.png", "t02.png", "t03.png", "t04.png", "t05.png", "t06.png", "t07.png", "t08.png", "t09.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png", "t19.png","t20.png","t21.png","t22.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png"];
 //for critical trials and fillers
 var images = new Array();
 for (i = 0; i < preObjects.length; i++) {
@@ -8,8 +8,7 @@ for (i = 0; i < preObjects.length; i++) {
     images[i].id = preObjects[i];
 }
 
-
-var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3"];
[…]

### 2019-04-10 experiments/kids/mmturkey_spin_kids_combination.js

@@ -214,12 +214,12 @@ turk = turk || {};
 // htmlify(rawData)
 
 
-      $.post("https://langcog.stanford.edu/cgi-bin/SPIN/me_novel/spin.php",{expHTML: JSON.stringify(rawData)}, "json");
+      $.post("https://langcog.stanford.edu/cgi-bin/SPIN/combination/spin.php",{expHTML: JSON.stringify(rawData)}, "json");
 
       return;
     }
 
-    $.post("https://langcog.stanford.edu/cgi-bin/SPIN/me_novel/spin.php",{expHTML: JSON.stringify(rawData)}, "json");
+    $.post("https://langcog.stanford.edu/cgi-bin/SPIN/combination/spin.php",{expHTML: JSON.stringify(rawData)}, "json");
     // // Otherwise, submit the form
     // form.action = "https://langcog.stanford.edu/cgi-bin/SC_noisy/parenting_proj.php";
     // form.method = "POST";

### 2019-04-16 stats/kids_basic_me.Rmd
first pass model and me by age

@@
          trial != "train2")%>%
-  mutate(age_num = scale(age_num))
+  mutate(age_num = age_num - mean(age_num))
 
@@
   group_by(familiar) %>%
-  expand(Estimate.Intercept,Estimate.age_num,grand_intercept,grand_slope,age = scale(d$age_num))%>%
+  expand(Estimate.Intercept,Estimate.age_num,grand_intercept,grand_slope,age = d$age_num - mean(d$age_num))%>%
   mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age_num+grand_slope)*age), 

### 2019-04-16 stats/model.Rmd
first pass model and me by age

---
title: "Model"
author: "M. Bohn"
date: "12 4 2019"
output: html_document
---

## Model utilities

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
```

```{r rsaUtils}
rsaUtils <- '
var all_objects = [
{ shape: "novel_object"},  
{ shape: "familiar_object"}
]

var labels = ["novel_word","familiar_word"]

var lexicon1 = function(utterance, obj, sem_knowledge){
utterance.label == "novel_word" ? obj.shape == "novel_object" :
utterance.label == "familiar_word" ? flip(sem_knowledge) ? obj.shape == "familiar_object" :  obj.shape == "novel_object" : 
true
}

var lexicon2 = function(utterance, obj, sem_knowledge){
utterance.label == "novel_word" ? obj.shape == "familiar_object" :
utterance.label == "familiar_word" ? flip(sem_knowledge) ? obj.shape == "familiar_object" :  obj.shape == "novel_object" : 
true
}

var lexiconObjects = {
"novel_word = novel_object": {
novel_object: "novel_word", familiar_object: "familiar_word"
},
"novel_word = familiar_object": {
novel_object: "familiar_word", familiar_object: "familiar_word"
},
}

var lexiconObject = {
"novel_word = novel_object": lexicon1,
"novel_word = familiar_object" : lexicon2
}

var utterancePrior = function(){ return uniformDraw([ {label: "novel_word"}, {label: "familiar_word"}]) }

var LexiconPrior = Categorical({vs: ["novel_word = novel_object","novel_word = familiar_object" ], ps: [1, 1]})
'
```

```{r rsa model}
rsaModel <- '
var literalListener = cache(function(utterance, priorProbs, sem_knowledge){
  Infer({method: "enumerate", model: function(){
    var lexiconName = sample(LexiconPrior); 
    var lexicon = lexiconObject[lexiconName];
    var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
    if ("label" in utterance) {
      var truthValue = lexicon(utterance, obj, sem_knowledge);
      condition(truthValue)
    }
    return obj.shape 
  }})
})

var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality, sem_knowledge){
  Infer({method: "enumerate", model: function(){
    var utterance = utterancePrior();
    var L0 = literalListener(utterance, priorProbs, sem_knowledge);
    factor(speakerOptimality * L0.score(obj.shape))
    return utterance
  }})
})

var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality, sem_knowledge){
  Infer({method: "enumerate", model: function(){
    var lexiconName = sample(LexiconPrior);
    var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
    var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality, sem_knowledge);
    observe(S1, utterance)
    return obj.shape == "novel_object" ? 1 : 0
  }})
})

var priorProbs = [.5,.5]

var speakerOptimality = 1;

var sem_knowledge = 1

var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality,sem_knowledge)

modelPredictions

'
```

```{r}
webppl(program_code = paste(rsaUtils, rsaModel, sep='\n'))
```
# Model for ME Effect
```{r}
me_data <- read_csv("../data/child_basic_me.csv")%>%
    filter(trial != "train1",
           trial != "train2")%>%
  mutate(z_age = age_num - mean(age_num))

# me_model <- brm(correct ~ z_age + (1|subid) + (z_age | familiar),
#                 data = me_data,
#                 family = bernoulli(),
#                 control = list(adapt_delta = 0.95),
#                 sample_prior = F,
#                 save_all_pars = TRUE,
#                 iter = 2000)

saveRDS(me_model, "../saves/me_effect_model.rds")

me_model <- readRDS("../saves/me_effect_model.rds")

summary(me_model)

fixef <- as_tibble(fixef(me_model), rownames = "term")

ranef <-  ranef(me_model)

age_me_effect <- as_tibble(ranef$familiar, rownames = "familiar")%>%
  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_slope = fixef%>%filter(term=="z_age")%>%pull(Estimate))%>%
  group_by(familiar) %>%
  expand(Estimate.Intercept,Estimate.z_age,grand_intercept,grand_slope,z_age = me_data$age_num - mean(me_data$age_num), mean_age = mean(me_data$age_num))%>%
  mutate(me_effect = plogis(grand_intercept + Estimate.Intercept+(Estimate.z_age+grand_slope)*z_age), 
         age = z_age+mean_age)%>%
  select(familiar, me_effect, age)

```

### 2019-04-16 stats/model.Rmd
first pass model inferring semantic strength

@@
 author: "M. Bohn"
-date: "12 4 2019"
 output: html_document
@@
 library(brms)
+library(coda)
+library(ggthemes)
+library(readxl)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+
 ```
@@
 var LexiconPrior = Categorical({vs: ["novel_word = novel_object","novel_word = familiar_object" ], ps: [1, 1]})
+
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
 '
@@
 
+'
+```
+
+```{r}
+baseMeModel <- '
+
+var sem_knowledge = 1
+
 var priorProbs = [.5,.5]
 
-var speakerOptimality = 1;
-
-var sem_knowledge = 1
+var speakerOptimality = 1
 
@@
 ```{r}
-webppl(program_code = paste(rsaUtils, rsaModel, sep='\n'))
+webppl(program_code = paste(rsaUtils, rsaModel, baseMeModel,sep='\n'))
 ```
-# Model for ME Effect
+
+# Inferring semantic knowledge
+```{r}
+semStr <- '
+var data = dataFromR.data
+
+var familiars = levels(data, "familiar")
+
+var model  = function(){
+
+  var params = map(function(cndtn){
+
+    var conditionData = _.filter(data, {condition: cndtn})
+
+    var sem_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+    var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})
+
+    foreach(function(row){
+
+      var age = row.age
+
+      var sem_knowledge = logistic(sem_int + sem_slope * age)
+
+      var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality,sem_knowledge)
+
+      observe(modelPredictions, row.correct)
+
+    }, conditionData)
+
+    return extend([
+      {int: sem_int, slope: sem_slope, familiar: cndtn}
+    ])
+
+  }, familiars)
+
+params
+
+}
+'
+```
+
+```{r}
+me_model_data <- read_csv("../data/child_basic_me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
+
+sem_know_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+  data = list(data = me_model_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples = 5000, burn = 2000, verbose = T)
+)
+
+sem_know <- sem_know_model %>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  rename(int = `0.int`,
+         slope = `0.slope`,
+         familiar = `0.familiar`)%>% 
+  gather(parameter, value, -familiar)
+
+sem_know_params <- sem_know %>%
+  group_by(familiar,parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+```
+
+```{r}
+ggplot(sem_know, aes(value))+
+  geom_density()+
+  xlab("Parameter")+
+  facet_grid(parameter ~familiar)+
+  theme_few()
+```
+## Plotting semantic knowledge
+```{r}
+
+aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
+
+aoa_ratings <- aoa_ratings_all %>%
+  filter(Word %in% sem_know_params$familiar )%>%
+  mutate(mean_aoa = as.numeric(Rating.Mean),
+         familiar = Word)%>%
+  select(familiar,mean_aoa)
+
+plot_sem_know <- sem_know_params%>%
+  select(-uci,-lci)%>%
+  spread(parameter, -familiar)%>%
+  expand(familiar, slope, int,age = me_model_data$age)%>%
+  mutate(sem_know = plogis(int + slope * age))%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
+
+ggplot(plot_sem_know, aes(x = age+2, y= sem_know, col = familiar))+
+  geom_line(size = 1)+
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_few()+
+  scale_colour_viridis_d(name = "familiar object")
+```
+
+# Ignore: Model for ME Effect
 ```{r}

### 2019-04-16 stats/model.Rmd
first pass model inferring semantic strength

@@
 library(readxl)
+library(ggpubr)
 
@@
 
-# Ignore: Model for ME Effect
+## For comparison: GLMM for ME effect and data
 ```{r}
@@
 
-saveRDS(me_model, "../saves/me_effect_model.rds")
+#saveRDS(me_model, "../saves/me_effect_model.rds")
 
@@
          age = z_age+mean_age)%>%
-  select(familiar, me_effect, age)
+  select(familiar, me_effect, age)%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
+
+model_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = familiar))+
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(size = 1)+
+  ggtitle("Model")+
+  labs(x="Age",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d(name = "familiar object")
+
+p2 <- read_csv("../data/child_basic_me.csv")%>%
+  filter(trial != "train1",
+         trial != "train2")%>%
+    left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
+
+data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  #facet_grid(~familiar)+
+  ggtitle("Data")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d(name = "familiar object")+
+  scale_fill_viridis_d(name = "familiar object")
 
 ```
+
+```{r}
+ggarrange(data_plot,model_plot, common.legend = T, legend = "right")
+```

### 2019-04-17 stats/model.Rmd
first pass model inferring semantic strength
model debugging; speakerOptimality not defined

@@
 
-var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality,sem_knowledge)
+var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality, sem_knowledge)
 
@@
 
+var priorProbs = [.5,.5]
+
 var model  = function(){
@@
 
-    var conditionData = _.filter(data, {condition: cndtn})
+    // display(data.slice(0, 4))
+    // display(cndtn)
+    var conditionData = _.filter(data, {familiar: cndtn})
 
@@
     var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})    
+    // display(conditionData)
 
@@
       var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality,sem_knowledge)
-
+      // display(row.correct)
       observe(modelPredictions, row.correct)
@@
 
-    return extend([
-      {int: sem_int, slope: sem_slope, familiar: cndtn}
-    ])
+    return {int: sem_int, slope: sem_slope, familiar: cndtn}
 
@@
 params
-
 }
@@
   model_var = "model",
-  chains = 4,
-  cores = 4,
-  inference_opts = list(method = "MCMC", samples = 5000, burn = 2000, verbose = T)
+  chains = 1,
+  cores = 1,
+  inference_opts = list(method = "MCMC", samples = 5, burn = 1, verbose = T)
 )

### 2019-04-17 stats/model.Rmd
infer sem knowledge model update

--- 2019-04-16 stats/model.Rmd
@@
 
+var priorProbs = [.5,.5]
+
+var speakerOptimality = 1
+
 var familiars = levels(data, "familiar")
@@
 
-    var conditionData = _.filter(data, {condition: cndtn})
+    var conditionData = _.filter(data, {familiar: cndtn})
 
-    var sem_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+    var sem_slope = uniformDrift({a: -2, b: 2, width: 0.2})
     var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})
+
+    // var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
+    // var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
 
@@
       var sem_knowledge = logistic(sem_int + sem_slope * age)
+
+      // var speakerOptimality = so_int  + so_slope * age
 
@@
     return extend([
-      {int: sem_int, slope: sem_slope, familiar: cndtn}
+      {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn}
     ])
@@
   cores = 4,
-  inference_opts = list(method = "MCMC", samples = 5000, burn = 2000, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 1000, burn = 1000, verbose = T)
 )
@@
   map_df(bind_rows)%>%
-  rename(int = `0.int`,
-         slope = `0.slope`,
+  rename(sem_int = `0.sem_int`,
+         sem_slope = `0.sem_slope`,
          familiar = `0.familiar`)%>%
+         #so_int = `0.so_int`,
+         #so_slope = `0.so_slope`)%>% 
   gather(parameter, value, -familiar)
@@
   spread(parameter, -familiar)%>%
-  expand(familiar, slope, int,age = me_model_data$age)%>%
-  mutate(sem_know = plogis(int + slope * age))%>%
+  expand(familiar, sem_slope, sem_int,age = me_model_data$age)%>%
+  mutate(sem_know = plogis(sem_int + sem_slope * age))%>%
   left_join(aoa_ratings)%>%

### 2019-04-17 stats/model.Rmd
infer sem knowledge with developmental so param

@@
 
-var speakerOptimality = 1
-
 var familiars = levels(data, "familiar")
@@
 var model  = function(){
+
+  var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
+  var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
 
@@
 
-    // var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
-    // var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
-
     foreach(function(row){
@@
 
-      // var speakerOptimality = so_int  + so_slope * age
+      var speakerOptimality = so_int  + so_slope * age
 
@@
     return extend([
-      {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn}
+      {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn, so_int: so_int, so_slope: so_slope}
     ])
@@
   cores = 4,
-  inference_opts = list(method = "MCMC", samples = 1000, burn = 1000, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 900, burn = 300, verbose = T)
 )
+# 
+# saveRDS(sem_know_model, "../saves/sem_know_model.rds")
+
+sem_know_model <- readRDS("../saves/sem_know_model.rds")
 
@@
          sem_slope = `0.sem_slope`,
-         familiar = `0.familiar`)%>%
-         #so_int = `0.so_int`,
-         #so_slope = `0.so_slope`)%>% 
+         familiar = `0.familiar`,
+         so_int = `0.so_int`,
+         so_slope = `0.so_slope`)%>% 
   gather(parameter, value, -familiar)
@@
   geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
+  geom_smooth(method = "loess", se = F, alpha = .5)+
   labs(x="Age",y="Mutual Exclusivity effect")+

### 2019-04-17 stats/model.Rmd
infer sem knowledge with developmental so param

@@
 
-sem_know_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-  data = list(data = me_model_data),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 4,
-  cores = 4,
-  inference_opts = list(method = "MCMC", samples = 900, burn = 300, verbose = T)
-)
+# sem_know_model<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+#   data = list(data = me_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 900, burn = 300, verbose = T)
+# )
 #  

### 2019-04-20 stats/model.Rmd

@@
 
-    return extend([
-      {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn, so_int: so_int, so_slope: so_slope}
-    ])
+    return {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn, so_int: so_int, so_slope: so_slope}
 
@@
 sem_know_model <- readRDS("../saves/sem_know_model.rds")
+
+sem_know_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+  data = list(data = me_model_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 1,
+  cores = 1,
+  inference_opts = list(method = "MCMC", samples = 5, burn = 1, verbose = T)
+)
 

### 2019-04-20 stats/kids_novelty.Rmd
update kids novelty

@@
 
-d <- left_join(d_raw,log, by = "subid")%>%
+d_spin <- left_join(d_raw,log, by = "subid")%>%
   filter(keep_drop == "keep",
@@
 
-d <- bind_rows(d_raw, d_mcc)
+d <- bind_rows(d_spin, d_mcc)
 

### 2019-04-20 stats/model.Rmd

--- 2019-04-17 stats/model.Rmd
@@
 library(ggpubr)
-
+library(stringr)
 estimate_mode <- function(s) {
@@
   }})
-})
+}, 10000)
 
@@
 
-  var params = map(function(cndtn){
+  foreach(function(cndtn){
 
@@
       var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality,sem_knowledge)
-
+      // display(modelPredictions.score(row.correct))
       observe(modelPredictions, row.correct)
@@
 
-    return extend([
-      {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn, so_int: so_int, so_slope: so_slope}
-    ])
+    query.add(cndtn, [sem_int, sem_slope])
 
@@
 
-params
-
+  query.add("speaker_optimality", [so_int, so_slope])
+  return query 
 }
@@
 
-sem_know_model <- readRDS("../saves/sem_know_model.rds")
+#sem_know_model <- readRDS("../saves/sem_know_model.rds")
+
+sem_know_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+  data = list(data = me_model_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 3,
+  cores = 3,
+  inference_opts = list(method = "incrementalMH", 
+                        samples = 5000, 
+                        burn = 2500,
+                        verbose = T,
+                        verboseLag = 500)
+)
+```
+
+```{r}
 
 sem_know <- sem_know_model %>%
-  select(value) %>%
-  map_df(bind_rows)%>%
-  rename(sem_int = `0.sem_int`,
-         sem_slope = `0.sem_slope`,
-         familiar = `0.familiar`,
-         so_int = `0.so_int`,
-         so_slope = `0.so_slope`)%>% 
-  gather(parameter, value, -familiar)
+  filter(Parameter != "speaker_optimality") %>%
+  mutate(Parameter = factor(Parameter)) %>%
+  separate(value, into = c("intercept", "slope"), 
+           sep = ", ") %>%
+  mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]"))) %>%
+  rename(item = Parameter) %>%
+  gather(parameter, value, intercept, slope)
+
+# sem_know <- sem_know_model %>%
+#   select(value) %>%
+#   map_df(bind_rows)%>%
+#   rename(sem_int = `0.sem_int`,
+#          sem_slope = `0.sem_slope`,
+#          familiar = `0.familiar`,
+#          so_int = `0.so_int`,
+#          so_slope = `0.so_slope`)%>% 
+#   gather(parameter, value, -familiar)
 
 sem_know_params <- sem_know %>%
-  group_by(familiar,parameter)%>%
+  group_by(item, parameter)%>%
   summarise(mode = estimate_mode(value),
@@
   xlab("Parameter")+
-  facet_grid(parameter ~familiar)+
+  facet_grid(parameter~item, scales = 'free')+
   theme_few()
@@
 aoa_ratings <- aoa_ratings_all %>%
-  filter(Word %in% sem_know_params$familiar )%>%
+  filter(Word %in% sem_know_params$item )%>%
   mutate(mean_aoa = as.numeric(Rating.Mean),
-         familiar = Word)%>%
-  select(familiar,mean_aoa)
+         item = Word)%>%
+  select(item,mean_aoa)
 
@@
   select(-uci,-lci)%>%
-  spread(parameter, -familiar)%>%
-  expand(familiar, sem_slope, sem_int,age = me_model_data$age)%>%
-  mutate(sem_know = plogis(sem_int + sem_slope * age))%>%
-  left_join(aoa_ratings)%>%
+  spread(parameter, -item) %>%
+  left_join(expand.grid(
+      age = unique(me_model_data$age),
+      item = me_model_data$familiar), .) %>%
+  mutate(sem_know = plogis(intercept + slope * age)) %>%
+  left_join(aoa_ratings) %>%
   ungroup()%>%
-  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
+  mutate(item = fct_reorder(factor(item), mean_aoa))
 
-ggplot(plot_sem_know, aes(x = age+2, y= sem_know, col = familiar))+
+ggplot(plot_sem_know, aes(x = age+2, y= sem_know, col = item, group = item))+
   geom_line(size = 1)+

### 2019-04-21 stats/model.Rmd
inverse model predictions

@@
 library(stringr)
+
 estimate_mode <- function(s) {
@@
 }
+
+me_data <- read_csv("../data/child_basic_me.csv")
 
@@
   var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
+  //var speakerOptimality = uniformDrift({a: -5, b: 5, width: 0.2})
 
@@
 
+  //query.add("speaker_optimality", [speakerOptimality])
   query.add("speaker_optimality", [so_int, so_slope])
@@
 #   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 900, burn = 300, verbose = T)
+#   inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
 # )
@@
 )
+
+#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
+sem_know_model <- readRDS("../saves/sem_know_model.rds")
 ```
@@
             lci = hdi_lower(value))
+
+speak_opt <- sem_know_model %>%
+  filter(Parameter == "speaker_optimality") %>%
+  separate(value, into = c("intercept", "slope"), 
+           sep = ", ")%>%
+  mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]"))) %>%
+  rename(item = Parameter) %>%
+  gather(parameter, value, intercept, slope)
+
 ```
@@
 ```
+
+```{r}
+ggplot(speak_opt, aes(value))+
+  geom_density()+
+  xlab("Parameter")+
+  facet_grid(~parameter, scales = 'free')+
+  theme_few()
+```
+
 ## Plotting semantic knowledge
 ```{r}
-
 aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
@@
   scale_colour_viridis_d(name = "familiar object")
+```
+
+# inverse predictions
+
+```{r}
+speak_opt_params <- speak_opt %>%
+  group_by(parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+inv_model_data <- sem_know_model %>%
+  filter(Parameter != "speaker_optimality") %>%
+  mutate(Parameter = factor(Parameter)) %>%
+  separate(value, into = c("intercept", "slope"), 
+           sep = ", ") %>%
+  mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]"))) %>%
+  rename(item = Parameter)%>%
+  group_by(item)%>%
+  summarise(sem_int = estimate_mode(intercept),
+            sem_slope = estimate_mode(slope))%>%
+  group_by(item)%>%
+  expand(sem_int,sem_slope,age = me_model_data$age)%>%
+  mutate(so_int = speak_opt_params%>%filter(parameter == "intercept")%>%pull(mode),
+         so_slope = speak_opt_params%>%filter(parameter == "slope")%>%pull(mode))%>%
+  mutate(speaker_optimality = so_int + so_slope * age,
+         semantic_knowledge = plogis(sem_int + sem_slope * age))
+
+```
+
+```{r}
+invPred <- '
+var allData = dataFromR.data
+
+var priorProbs = [.5,.5]
+
+var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, row.speaker_optimality,row.semantic_knowledge)
+
+    return extend([row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])
+
+}, allData)
+
+output
+
+'
+```
+
+```{r predictions pragmatic model ex 3 adults}
+inv_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
+  data =list(data = inv_model_data),
+  data_var = "dataFromR"
+)
+
+#saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
+#inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
+
+inv_predictions <- inv_model_pred %>%
+  separate(`0`, into = c("item", "age"), sep="/")%>%
+  mutate(age = as.numeric(age))%>%
+  rename( me_effect = `1`)%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa), 
+         age = age + min(me_data$age_num))
+
+inv_model_plot <- ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(size = 1)+
+  ggtitle("Inverse Model Predictions")+
+  labs(x="Age",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d()
 ```
@@
   mutate(me_effect = plogis(grand_intercept + Estimate.Intercept+(Estimate.z_age+grand_slope)*z_age), 
-         age = z_age+mean_age)%>%
-  select(familiar, me_effect, age)%>%
+         age = z_age+mean_age,
+         item = familiar)%>%
+  select(item, me_effect, age)%>%
   left_join(aoa_ratings)%>%
   ungroup()%>%
-  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
+  mutate(item = fct_reorder(factor(item), mean_aoa))
 
-model_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = familiar))+
+model_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = item))+
   geom_hline(yintercept = 0.5, lty=2)+
   geom_line(size = 1)+
-  ggtitle("Model")+
+  ggtitle("GLMM")+
   labs(x="Age",y="Proportion correct")+
@@
          trial != "train2")%>%
+  mutate(item = familiar)%>%
     left_join(aoa_ratings)%>%
   ungroup()%>%
-  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
+  mutate(familiar = fct_reorder(factor(item), mean_aoa))
 
@@
   geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  geom_smooth(method = "loess", se = F, alpha = .5)+
+  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
 ```{r}
-ggarrange(data_plot,model_plot, common.legend = T, legend = "right")
+ggarrange(data_plot,inv_model_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 3)
 ```

### 2019-04-22 stats/model.Rmd
more iterations

@@
 
-# sem_know_model<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-#   data = list(data = me_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
-# )
-# 
-# saveRDS(sem_know_model, "../saves/sem_know_model.rds")
-
-#sem_know_model <- readRDS("../saves/sem_know_model.rds")
-
 sem_know_model<- webppl(
@@
   inference_opts = list(method = "incrementalMH", 
-                        samples = 5000, 
+                        samples = 10000, 
                         burn = 2500,
@@
   gather(parameter, value, intercept, slope)
-
-# sem_know <- sem_know_model %>%
-#   select(value) %>%
-#   map_df(bind_rows)%>%
-#   rename(sem_int = `0.sem_int`,
-#          sem_slope = `0.sem_slope`,
-#          familiar = `0.familiar`,
-#          so_int = `0.so_int`,
-#          so_slope = `0.so_slope`)%>% 
-#   gather(parameter, value, -familiar)
 

### 2019-04-23 stats/kids_novelty.Rmd
update kids novelty model

@@
 d_raw <-raw_data %>%
-  mutate(test_date = as.Date(test_date))
+  mutate(test_date = as.Date(test_date),
+         subid = ifelse(subid =="190422_6_nov,","190422_6_nov",subid),
+         subage = ifelse(subid =="190422_2_nov","4",subage))
 
@@
   group_by(experiment,subage) %>%
-  summarise(n = length(unique(subid)))
+  summarise(n = length(unique(subid)),
+            data_points = n())
 
@@
 # maximal converging model
-bm <- brm(correct ~ age_num * experiment + (1 | subid) + (age_num * experiment | agent), 
+bm_full <- brm(correct ~ age_num * experiment + (1 | subid) + (age_num * experiment | agent), 
           data = model_data, family = bernoulli(),
@@
 
-summary(bm)
+summary(bm_full)
+
+bm_null <- brm(correct ~ age_num + (1 | subid) + (age_num * experiment | agent), 
+          data = model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
+
+summary(bm_null)
+
+bayes_factor(bm_full, bm_null, log = F, maxiter = 5000)
 

### 2019-04-26 stats/model.Rmd
update kids novelty model
hierarchical version of item parameters; begin to sketch out nesting within items and participants

@@
 
+  var sem_slope_global = uniformDrift({a: -2, b: 2, width: 0.2})
+  var sem_int_global = uniformDrift({a: 0, b: 5, width: 0.2})
+
+  var item_slope_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
+  // conceptually it might not make sense to have two sigmas, but maybe it does
+  // intercept sigma probably will be smaller than slope sigma
+  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
+
   foreach(function(cndtn){
@@
 
-    var sem_slope = uniformDrift({a: -2, b: 2, width: 0.2})
-    var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})
+    var sem_slope_item = gaussianDrift({mu: sem_slope_global, sigma: item_slope_sigma, width: 0.5})
+    var sem_int_item = gaussianDrift({mu: sem_int_global, sigma: item_int_sigma, width: 0.5})
+
+    // var sem_slope = uniformDrift({a: -2, b: 2, width: 0.2})
+    // var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})
 
@@
 
-      var sem_knowledge = logistic(sem_int + sem_slope * age)
+      var sem_knowledge = logistic(sem_int_item + sem_slope_item * age)
 
@@
 
-      var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality,sem_knowledge)
+      var modelPredictions = pragmaticListener({label: "novel_word"}, 
+            priorProbs, speakerOptimality, sem_knowledge)
       // display(modelPredictions.score(row.correct))
+
       observe(modelPredictions, row.correct)
+
+      query.add(["modelPrediction", cndtn], [age, Math.exp(modelPredictions.score(1))])
 
@@
 
-    query.add(cndtn, [sem_int, sem_slope])
+    query.add(["parameter", cndtn], [sem_int_item, sem_slope_item])
 
@@
 
-  //query.add("speaker_optimality", [speakerOptimality])
-  query.add("speaker_optimality", [so_int, so_slope])
+  query.add(["parameter", "speaker_optimality"], [so_int, so_slope])
+  query.add(["parameter", "global_sem"], [sem_int_global, sem_slope_global])
+  query.add(["parameter", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])
+
   return query 
@@
 ```{r}
-me_model_data <- read_csv("../data/child_basic_me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(age = age_num - min(age_num))
+# me_model_data <- read_csv("../data/child_basic_me.csv")%>%
+#     filter(trial != "train1",
+#            trial != "train2")%>%
+#   mutate(age = age_num - min(age_num))
 
@@
   model_var = "model",
-  chains = 3,
-  cores = 3,
+  chains = 1,
+  cores = 1,
   inference_opts = list(method = "incrementalMH", 
-                        samples = 10000, 
-                        burn = 2500,
-                        verbose = T,
-                        verboseLag = 500)
+                        samples = 10, 
+                        burn = 5,
+                        verbose = T)#,
+                        #verboseLag = 500)
 )
@@
 #saveRDS(sem_know_model, "../saves/sem_know_model.rds")
-sem_know_model <- readRDS("../saves/sem_know_model.rds")
+sem_know_model <- readRDS("../saves/sem_know_model.rds") %>%
+  filter(Chain != 1)
 ```
@@
 ```{r}
-ggplot(sem_know, aes(value))+
-  geom_density()+
+ggplot(sem_know, aes(x = value))+#, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
   xlab("Parameter")+
@@
   scale_colour_viridis_d()
+
+inv_model_plot
 ```
@@
   scale_fill_viridis_d(name = "familiar object")
-
+data_plot
 ```
@@
 ```
+
+#### WORK IN PROGRESS: nesting within participant
+
+to do:
+- bookkeeping: index correct participant/item variables at relevant part of code
+- inference: try HMC, variational
+
+```{r work in progress}
+semStr <- '
+var data = dataFromR.data
+
+var priorProbs = [.5,.5]
+
+var familiars = levels(data, "familiar")
+
+var model  = function(){
+
+  // global parameters
+  var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
+  var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
+
+  var sem_slope_global = uniformDrift({a: -2, b: 2, width: 0.2})
+  var sem_int_global = uniformDrift({a: 0, b: 5, width: 0.2})
+
+  var item_slope_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
+  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
+
+  var participant_age_adjust = gaussianDrift({mu: 0, sigma: 1, width: 0.2})
+
+  var sem_slope_item = repeat(familiars.length, function(){
+    gaussianDrift({mu: sem_slope_global, sigma: item_slope_sigma, width: 0.5} )
+  })
+
+  var sem_int_item = gaussianDrift({mu: sem_int_global, 
+        sigma: item_int_sigma, width: 0.5})
+
+  foreach(function(cndtn){
+
+    var conditionData = _.filter(data, {familiar: cndtn})
+
+    foreach(function(row){
+
+      var age = row.age
+
+      var sem_knowledge = logistic(sem_int_item + sem_slope_item * age)
+
+      var speakerOptimality = so_int  + so_slope * age
+
+      var modelPredictions = pragmaticListener({label: "novel_word"}, 
+            priorProbs, speakerOptimality, sem_knowledge)
+      // display(modelPredictions.score(row.correct))
+
+      observe(modelPredictions, row.correct)
+
+      query.add(["modelPrediction", cndtn], [age, Math.exp(modelPredictions.score(1))])
+
+    }, conditionData)
+
+    query.add(["parameter", cndtn], [sem_int_item, sem_slope_item])
+
+  }, familiars)
+
+  query.add(["parameter", "speaker_optimality"], [so_int, so_slope])
+  query.add(["parameter", "global_sem"], [sem_int_global, sem_slope_global])
+  query.add(["parameter", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])
+
+  return query 
+}
+'
+```

### 2019-04-26 stats/model.Rmd
test run hierarchical model

@@
 
+      display(age)
+
       var sem_knowledge = logistic(sem_int_item + sem_slope_item * age)
@@
 ```{r}
-# me_model_data <- read_csv("../data/child_basic_me.csv")%>%
-#     filter(trial != "train1",
-#            trial != "train2")%>%
-#   mutate(age = age_num - min(age_num))
+me_model_data <- read_csv("../data/child_basic_me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
 
@@
   inference_opts = list(method = "incrementalMH", 
-                        samples = 10, 
-                        burn = 5,
+                        samples = 1, 
+                        burn = 1,
                         verbose = T)#,
@@
 #saveRDS(sem_know_model, "../saves/sem_know_model.rds")
-sem_know_model <- readRDS("../saves/sem_know_model.rds") %>%
-  filter(Chain != 1)
+#sem_know_model <- readRDS("../saves/sem_know_model.rds")
 ```
@@
 
-sem_know <- sem_know_model %>%
-  filter(Parameter != "speaker_optimality") %>%
-  mutate(Parameter = factor(Parameter)) %>%
-  separate(value, into = c("intercept", "slope"), 
-           sep = ", ") %>%
-  mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]"))) %>%
-  rename(item = Parameter) %>%
-  gather(parameter, value, intercept, slope)
+model_pred <- sem_know_model %>%
+  separate(Parameter, into = c("type", "token"))%>%
+  filter(type == "modelPrediction")%>%
+  separate(value, into = c("age", "pred"),sep = ", ")%>%
+  mutate(age = as.numeric(str_remove_all(age, "[(c]")),
+         pred = as.numeric(str_remove(pred, "[)]"))) %>%
+  rename(item = token)
 
-sem_know_params <- sem_know %>%
+params<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type"), sep = ",")%>%
+  filter(parameter == "parameter")%>%
+  separate(value, into = c("slope", "int"),sep = ", ")%>%
+  mutate(slope = as.numeric(str_remove_all(slope, "[(c]")),
+         int = as.numeric(str_remove(int, "[)]")))%>%
+  gather(parameter, value, int, slope)
+
+sem_know_params <- params %>%
+  filter(type != "speaker_optimality",
+         type != "global_sem",
+         type != "global_sem_sigmas")%>%
+  rename(item = type)%>%
   group_by(item, parameter)%>%
@@
 
-speak_opt <- sem_know_model %>%
-  filter(Parameter == "speaker_optimality") %>%
-  separate(value, into = c("intercept", "slope"), 
-           sep = ", ")%>%
-  mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]"))) %>%
-  rename(item = Parameter) %>%
-  gather(parameter, value, intercept, slope)
+global_params <- params %>%
+  filter(type == "speaker_optimality" |
+         type == "global_sem")%>%
+  group_by(type, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
 
@@
 ```{r}
-ggplot(sem_know, aes(x = value))+#, fill = factor(Chain)))+
+item_params <- params %>%
+  filter(type != "speaker_optimality",
+         type != "global_sem",
+         type != "global_sem_sigmas")
+
+ggplot(item_params, aes(x = value))+#, fill = factor(Chain)))+
   geom_density(alpha = 0.3)+
   xlab("Parameter")+
-  facet_grid(parameter~item, scales = 'free')+
+  facet_grid(parameter~type, scales = 'free')+
   theme_few()
@@
 ```{r}
-ggplot(speak_opt, aes(value))+
-  geom_density()+
+param_params <- params %>%
+  filter(type == "speaker_optimality" |
+         type == "global_sem")
+
+ggplot(param_params, aes(x = value))+#, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
   xlab("Parameter")+
+  facet_grid(parameter~type, scales = 'free')+
+  theme_few()
+```
+
+```{r}
+sigma_params <- params %>%
+  filter(type == "global_sem_sigmas")
+
+ggplot(sigma_params, aes(x = value))+#, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Sigma")+
   facet_grid(~parameter, scales = 'free')+
@@
 
-inv_model_plot <- ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
+inv_model_plot <- ggplot(model_pred, aes(x=age+2,y = pred, col = item))+
   geom_hline(yintercept = 0.5, lty=2)+

### 2019-04-29 stats/kids_novelty.Rmd
model pred with age

@@
 p5 <- d %>%
-  group_by(experiment,age_num, subid) %>%
+  group_by(age_num, subid) %>%
   summarise(correct = mean(correct))
 
-ggplot(data = p5, aes(x = age_num, y = correct, col = experiment)) +
+ggplot(data = p5, aes(x = age_num, y = correct)) +
   geom_smooth(data = d, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="Age",y="Proportion Expected Choice")+
+  labs(x="Age",y="Proportion novel item chosen")+
   theme_few() +

### 2019-04-29 stats/model.Rmd
model pred with age

--- 2019-04-26 stats/model.Rmd
@@
 
+      //display(age)
+
       var sem_knowledge = logistic(sem_int_item + sem_slope_item * age)
@@
 
-      query.add(["modelPrediction", cndtn], [age, Math.exp(modelPredictions.score(1))])
+      query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
 
@@
 
-    query.add(["parameter", cndtn], [sem_int_item, sem_slope_item])
+    query.add(["parameter","items", cndtn], [sem_int_item, sem_slope_item])
 
@@
 
-  query.add(["parameter", "speaker_optimality"], [so_int, so_slope])
-  query.add(["parameter", "global_sem"], [sem_int_global, sem_slope_global])
-  query.add(["parameter", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])
+  query.add(["parameter","parameters","speaker_optimality"], [so_int, so_slope])
+  query.add(["parameter","parameters", "global_sem"], [sem_int_global, sem_slope_global])
+  query.add(["parameter","sigma", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])
 
@@
   model_var = "model",
-  chains = 1,
-  cores = 1,
+  chains = 3,
+  cores = 3,
   inference_opts = list(method = "incrementalMH", 
-                        samples = 10, 
-                        burn = 5,
-                        verbose = T)#,
-                        #verboseLag = 500)
+                        samples = 2000, 
+                        burn = 1000,
+                        verbose = T,
+                        verboseLag = 500)
 )
@@
 
-sem_know <- sem_know_model %>%
-  filter(Parameter != "speaker_optimality") %>%
-  mutate(Parameter = factor(Parameter)) %>%
-  separate(value, into = c("intercept", "slope"), 
-           sep = ", ") %>%
-  mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]"))) %>%
-  rename(item = Parameter) %>%
-  gather(parameter, value, intercept, slope)
+model_pred <- sem_know_model %>%
+  separate(Parameter, into = c("type", "item","x"))%>%
+  filter(type == "modelPrediction")%>%
+  separate(value, into = c("age", "pred"),sep = ", ")%>%
+  mutate(age = as.numeric(str_remove_all(age, "[(c]")),
+         pred = as.numeric(str_remove(pred, "[)]")))%>%
+  select(-x)
 
-sem_know_params <- sem_know %>%
+item_params<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
+  filter(parameter == "parameter", type == "items")%>%
+  separate(value, into = c("int", "slope"),sep = ", ")%>%
+  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]")))%>%
+  gather(parameter, value, int, slope)
+
+global_params <- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
+  filter(parameter == "parameter", type == "parameters")%>%
+    separate(value, into = c("int", "slope"),sep = ", ")%>%
+    mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]")))%>%
+    gather(parameter, value, int, slope)
+
+global_sigma<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
+  filter(parameter == "parameter", type == "sigma")%>%
+    separate(value, into = c("sigma_int", "sigma_slope"),sep = ", ")%>%
+    mutate(sigma_int = as.numeric(str_remove_all(sigma_int, "[(c]")),
+         sigma_slope = as.numeric(str_remove(sigma_slope, "[)]")))%>%
+    gather(parameter, value, sigma_int, sigma_slope)
+
+#### summaries
+
+model_pred_summary <- model_pred %>%
+  group_by(item,age)%>%
+  summarise(mode = estimate_mode(pred),
+            uci = hdi_upper(pred),
+            lci = hdi_lower(pred))
+
+item_params_summary <- item_params %>%
   group_by(item, parameter)%>%
@@
 
-speak_opt <- sem_know_model %>%
-  filter(Parameter == "speaker_optimality") %>%
-  separate(value, into = c("intercept", "slope"), 
-           sep = ", ")%>%
-  mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]"))) %>%
-  rename(item = Parameter) %>%
-  gather(parameter, value, intercept, slope)
+global_params_summary <- global_params %>%
+  group_by(token, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
 
@@
 ```{r}
-ggplot(sem_know, aes(x = value))+#, fill = factor(Chain)))+
+ggplot(item_params, aes(x = value))+#, fill = factor(Chain)))+
   geom_density(alpha = 0.3)+
@@
 ```{r}
-ggplot(speak_opt, aes(value))+
-  geom_density()+
+
+ggplot(global_params, aes(x = value))+#, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
   xlab("Parameter")+
+  facet_grid(parameter~token, scales = 'free')+
+  theme_few()
+```
+
+```{r}
+ggplot(global_sigma, aes(x = value))+#, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Sigma")+
   facet_grid(~parameter, scales = 'free')+
@@
 aoa_ratings <- aoa_ratings_all %>%
-  filter(Word %in% sem_know_params$item )%>%
+  filter(Word %in% item_params_summary$item )%>%
   mutate(mean_aoa = as.numeric(Rating.Mean),
@@
 
-plot_sem_know <- sem_know_params%>%
+plot_sem_know <- item_params_summary%>%
   select(-uci,-lci)%>%
@@
       item = me_model_data$familiar), .) %>%
-  mutate(sem_know = plogis(intercept + slope * age)) %>%
+  mutate(sem_know = plogis(int + slope * age)) %>%
   left_join(aoa_ratings) %>%
@@
 ```{r}
-speak_opt_params <- speak_opt %>%
-  group_by(parameter)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
-inv_model_data <- sem_know_model %>%
-  filter(Parameter != "speaker_optimality") %>%
-  mutate(Parameter = factor(Parameter)) %>%
-  separate(value, into = c("intercept", "slope"), 
-           sep = ", ") %>%
-  mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]"))) %>%
-  rename(item = Parameter)%>%
-  group_by(item)%>%
-  summarise(sem_int = estimate_mode(intercept),
-            sem_slope = estimate_mode(slope))%>%
-  group_by(item)%>%
-  expand(sem_int,sem_slope,age = me_model_data$age)%>%
-  mutate(so_int = speak_opt_params%>%filter(parameter == "intercept")%>%pull(mode),
-         so_slope = speak_opt_params%>%filter(parameter == "slope")%>%pull(mode))%>%
-  mutate(speaker_optimality = so_int + so_slope * age,
-         semantic_knowledge = plogis(sem_int + sem_slope * age))
+# speak_opt_params <- speak_opt %>%
+#   group_by(parameter)%>%
+#   summarise(mode = estimate_mode(value),
+#             uci = hdi_upper(value),
+#             lci = hdi_lower(value))
+# 
+# inv_model_data <- sem_know_model %>%
+#   filter(Parameter != "speaker_optimality") %>%
+#   mutate(Parameter = factor(Parameter)) %>%
+#   separate(value, into = c("intercept", "slope"), 
+#            sep = ", ") %>%
+#   mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
+#          slope = as.numeric(str_remove(slope, "[)]"))) %>%
+#   rename(item = Parameter)%>%
+#   group_by(item)%>%
+#   summarise(sem_int = estimate_mode(intercept),
+#             sem_slope = estimate_mode(slope))%>%
+#   group_by(item)%>%
+#   expand(sem_int,sem_slope,age = me_model_data$age)%>%
+#   mutate(so_int = speak_opt_params%>%filter(parameter == "intercept")%>%pull(mode),
+#          so_slope = speak_opt_params%>%filter(parameter == "slope")%>%pull(mode))%>%
+#   mutate(speaker_optimality = so_int + so_slope * age,
+#          semantic_knowledge = plogis(sem_int + sem_slope * age))
 
@@
 ```{r predictions pragmatic model ex 3 adults}
-inv_model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
-  data =list(data = inv_model_data),
-  data_var = "dataFromR"
-)
+# inv_model_pred<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
+#   data =list(data = inv_model_data),
+#   data_var = "dataFromR"
+# )
+# 
+# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
+# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
+# 
+# inv_predictions <- inv_model_pred %>%
+#   separate(`0`, into = c("item", "age"), sep="/")%>%
+#   mutate(age = as.numeric(age))%>%
+#   rename( me_effect = `1`)%>%
+#   left_join(aoa_ratings)%>%
+#   ungroup()%>%
+#   mutate(item = fct_reorder(factor(item), mean_aoa), 
+#          age = age + min(me_data$age_num))
+```
 
-#saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
-#inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
+```{r}
+plot_model_pred <- model_pred_summary%>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
 
-inv_predictions <- inv_model_pred %>%
-  separate(`0`, into = c("item", "age"), sep="/")%>%
-  mutate(age = as.numeric(age))%>%
-  rename( me_effect = `1`)%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa), 
-         age = age + min(me_data$age_num))
-
-inv_model_plot <- ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
+ggplot(plot_model_pred, aes(x=age+2,y = mode, col = item))+
   geom_hline(yintercept = 0.5, lty=2)+
@@
 
-inv_model_plot
 ```

### 2019-04-29 stats/model.Rmd
model pred with age
update model

@@
 #saveRDS(sem_know_model, "../saves/sem_know_model.rds")
-#sem_know_model <- readRDS("../saves/sem_know_model.rds")
+sem_know_model <- readRDS("../saves/sem_know_model.rds")
 ```
@@
 
-ggplot(global_params, aes(x = value))+#, fill = factor(Chain)))+
+ggplot(global_params, aes(x = value))#, fill = factor(Chain)))+
   geom_density(alpha = 0.3)+

### 2019-05-05 stats/kids_basic_me.Rmd
kids novelty data

@@
 
-#write_csv(d, "../data/child_basic_me.csv")
+write_csv(d, "../data/child_basic_me.csv")
 ```
@@
   weight = c(child_weights[1],child_weights[2]),
-  BF10 = c(round(bf_full_null$bf,2),"-"))%>%
+  BF10 = c(round(bf_full_null$bf,0),"-"))%>%
   mutate_if(is.numeric, round, 2)

### 2019-05-05 stats/kids_novelty.Rmd
kids novelty data

--- 2019-04-20 stats/kids_novelty.Rmd
@@
 ---
-title: "SPIN Novelty"
-author: "Manuel Bohn"
+title: "SPIN Novelty Data"
 output: html_document
@@
 ```{r setup, include= FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = F, warning = F)
 ###
@@
   mutate(dob = as.character(dob),
+         dob = ifelse(subid =="190502_9_nov","2016-10-08",dob),
          dob = as.Date(dob))%>%
@@
          pick = str_sub(pick,72,str_length(pick)-4),
+         agent = ifelse(speakerChange == "false", agent,altAgent),
          experiment = "dis_novelty_mcc")%>%
@@
 
+write_csv(d, "../data/child_novelty.csv")
+
 ```
 
-```{r sanity checks, echo = FALSE,warning = FALSE, message = FALSE}
+Main question: Do SPIN and MCC datasets differ?
+
+# Participants
+
+* dis_novelty_mcc = same speaker condition from MCC data collection
+* n = number of subjects
+* data_points = number of data points across subjects
+
+```{r sanity checks, echo = FALSE, warning = FALSE, message = FALSE}
+
+d <- read_csv("../data/child_novelty.csv")%>%
+  mutate(subage = factor(subage))
 
@@
   group_by(experiment,subage) %>%
-  summarise(n = length(unique(subid)))
+  summarise(n = length(unique(subid)),
+            data_points = n())%>%
+  kable()
 
 ```
+
+# Plots
+
+## Plot by age bin
 
@@
 
-## Plot with age as continuous variable
+## Plot by age continuous
 
@@
 p5 <- d %>%
-  group_by(experiment,age_num, subid) %>%
+  group_by(age_num,experiment, subid) %>%
   summarise(correct = mean(correct))
@@
   geom_smooth(data = d, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
-  geom_jitter( alpha = .5, height = 0.04)+
+  geom_jitter( alpha = .5, height = 0.01)+
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="Age",y="Proportion Expected Choice")+
+  labs(x="Age",y="Proportion novel item chosen")+
   theme_few() +
@@
 
-## GLMM
+# GLMM
 
-```{r}
-## model
-library(brms)
+## Models
+
+1. bm_full_1: correct ~ age_num * experiment + (1 | subid) + (age_num * experiment | agent)
+
+2. bm_full_2: correct ~ age_num * experiment + (1 | subid) + (age_num | agent)
+
+3. bm_null_1: correct ~ age_num + (1 | subid) + (age_num * experiment | agent)
+
+4. bm_null_2: correct ~ age_num + (1 | subid) + (age_num | agent)
+
+* experiment = SPIN or MCC
+* subid = subject id 
+* agent = animal making the request (item effect)
+* age_num = age (numeric)
+
+```{r, include = F, cache = T}
 
@@
 
-# maximal converging model
-bm <- brm(correct ~ age_num * experiment + (1 | subid) + (age_num * experiment | agent), 
+bm_full_1 <- brm(correct ~ age_num * experiment + (1 | subid) + (age_num * experiment | agent), 
           data = model_data, family = bernoulli(),
@@
 
-summary(bm)
+bm_full_2 <- brm(correct ~ age_num * experiment + (1 | subid) + (age_num | agent), 
+          data = model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
 
+bm_null_1 <- brm(correct ~ age_num + (1 | subid) + (age_num * experiment | agent), 
+          data = model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
+
+bm_null_2 <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
+          data = model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
+
+waic <- brms::waic(bm_full_1, bm_full_2,bm_null_1,bm_null_2, compare = F)
+
+weights <- model_weights(bm_full_1, bm_full_2,bm_null_1,bm_null_2, weights = "waic")
+
+bf_full_2_null_1 <- brms::bayes_factor(bm_full_2, bm_null_1, log = F, maxiter = 5000)
+bf_full_2_full_1 <- brms::bayes_factor(bm_full_2, bm_full_1, log = F, maxiter = 5000)
+bf_full_2_null_2 <- brms::bayes_factor(bm_full_2, bm_null_2, log = F, maxiter = 5000)
 ```
+
+## Model comparison
+
+* BF_full_2 = Bayes Factor compared to bm_full_2, the "winning" model in the model comparison.
+
+```{r}
+data_frame(
+  model = c("bm_full_1","bm_full_2","bm_null_1","bm_null_2"),
+  WAIC = c(waic$loo$bm_full_1$estimates[3,1],
+           waic$loo$bm_full_2$estimates[3,1],
+           waic$loo$bm_null_1$estimates[3,1],
+           waic$loo$bm_null_2$estimates[3,1]),
+  SE = c(waic$loo$bm_full_1$estimates[3,2],
+           waic$loo$bm_full_2$estimates[3,2],
+           waic$loo$bm_null_1$estimates[3,2],
+           waic$loo$bm_null_2$estimates[3,2]),
+  waic_weight = c(weights[1],weights[2],weights[3],weights[4]),
+  BF_full_2 = c(round(bf_full_2_full_1$bf,0),"-",round(bf_full_2_null_1$bf,0),round(bf_full_2_null_2$bf,0)))%>%
+  mutate_if(is.numeric, round, 2)%>%
+  kable()
+```
+
+Models with experiment as predictor provide better fit. This suggests that we should not combine the two datasets.
+
+## Summary for "winning" model
+
+```{r}
+fixef(bm_full_2)%>%
+  kable(digits = 2)
+```
+
+Estimate for interaction is relaibly different from 0, suggesting again that data sets are not the same.
+
+## Estiamte plots for "winning" model
+
+```{r}
+plot(bm_full_2)
+```

### 2019-05-05 stats/model-understanding.Rmd

--- 2019-04-29 stats/model.Rmd
@@
 ---
-title: "Model"
-author: "M. Bohn"
+title: "model-understanding"
+author: "MH Tessler"
+date: "5/4/2019"
 output: html_document
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
+## Breaking down the model, for understanding
 
@@
 ```
+
+## RSA model
 
@@
 '
+```
+
+## Priors for speaker optimality
+
+```{r FIXME}
+semKnowPriors <- '
+var data = dataFromR.data
+
+var priorProbs = [.5,.5]
+
+var familiars = levels(data, "familiar")
+
+var model  = function(){
+
+  var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
+  var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
+  //var speakerOptimality = uniformDrift({a: -5, b: 5, width: 0.2})
+
+  var sem_slope_global = uniformDrift({a: -2, b: 2, width: 0.2})
+  var sem_int_global = uniformDrift({a: 0, b: 5, width: 0.2})
+
+  var item_slope_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
+  // conceptually it might not make sense to have two sigmas, but maybe it does
+  // intercept sigma probably will be smaller than slope sigma
+  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
+
+  foreach(function(cndtn){
+
+    var conditionData = _.filter(data, {familiar: cndtn})
+
+    var sem_slope_item = gaussianDrift({mu: sem_slope_global, sigma: item_slope_sigma, width: 0.5})
+    var sem_int_item = gaussianDrift({mu: sem_int_global, sigma: item_int_sigma, width: 0.5})
+
+    // var sem_slope = uniformDrift({a: -2, b: 2, width: 0.2})
+    // var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})
+
+    foreach(function(row){
+
+      var age = row.age
+
+      //display(age)
+
+      var sem_knowledge = logistic(sem_int_item + sem_slope_item * age)
+
+      var speakerOptimality = so_int  + so_slope * age
+
+      var modelPredictions = pragmaticListener({label: "novel_word"}, 
+            priorProbs, speakerOptimality, sem_knowledge)
+      // display(modelPredictions.score(row.correct))
+
+      observe(modelPredictions, row.correct)
+
+      query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
+
+    }, conditionData)
+
+    query.add(["parameter","items", cndtn], [sem_int_item, sem_slope_item])
+
+  }, familiars)
+
+  query.add(["parameter","parameters","speaker_optimality"], [so_int, so_slope])
+  query.add(["parameter","parameters", "global_sem"], [sem_int_global, sem_slope_global])
+  query.add(["parameter","sigma", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])
+
+  return query 
+}
+'
+```
+
+## Priors for inferring semantic knowledge
+
+```{r old}
+semKnowPriors <- '
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+
+var data = dataFromR.data
+
+var priorProbs = [.5,.5]
+
+var familiars = levels(data, "familiar")
+
+var discreteUniformBins = function(lower, upper, bin_width){
+  _.range(lower, upper, bin_width)
+}
+
+var all_ages = sort(levels(data, "age"))
+
+var model  = function(){
+
+  var globalLineParameters = {
+    intercept:  discreteUniformBins(0, 5, 2),
+    slope: discreteUniformBins(-2, 2, 2)
+  }
+
+  var itemVariability = {
+    intercept: discreteUniformBins(0.01, 5, 2),
+    slope: discreteUniformBins(0.01, 5, 2)
+  }
+  // conceptually it might not make sense to have two sigmas, but maybe it does
+  // intercept sigma probably will be smaller than slope sigma
+
+  // display([
+  //  globalLineParameters.intercept, itemVariability.intercept,
+  //  globalLineParameters.slope, itemVariability.slope,
+  //  itemLineParameters.intercept, itemLineParameters.slope
+  // ])
+  var output = map(function(globalLineIntercept){
+    map(function(globalLineSlope){
+      map(function(itemVariabilityIntercept){
+          map(function(itemVariabilitySlope){
+
+            var itemLineParameters = {
+              intercept: discreteUniformBins(
+                globalLineIntercept - 1*itemVariabilityIntercept,
+                globalLineIntercept + 1*itemVariabilityIntercept,
+                itemVariabilityIntercept
+              ),
+              slope: discreteUniformBins(
+                globalLineSlope - 1*itemVariabilitySlope,
+                globalLineSlope + 1*itemVariabilitySlope,
+                itemVariabilitySlope
+              )
+            }
+
+            map(function(itemLineIntercept){
+                map(function(itemLineSlope){
+                  map(function(age){
+                    var sem_knowledge = logistic(itemLineIntercept + 
+                      itemLineSlope * age)
+                    // display(itemLineParameters.intercept + "+ " + itemLineParameters.slope + " X " + age + " =logistic= " + sem_knowledge)
+                    var priorProbs =  [.5,.5]
+                    var speakerOptimality = 1
+
+                    var modelPredictions = pragmaticListener({label: "novel_word"}, 
+                            priorProbs, speakerOptimality, sem_knowledge)
+                    var smk =  "semKnowledge_" + age
+                    var mpa =  "modelPrediction_" + age
+                    return {
+                      global_intercept: globalLineIntercept,
+                      global_slope: globalLineSlope,
+                      sigma_intercept:itemVariabilityIntercept, 
+                      sigma_slope:itemVariabilitySlope, 
+                      item_intercept: itemLineIntercept,
+                      item_slope: itemLineSlope,
+                      age: age,
+                      sem_knowledge : sem_knowledge,
+                      L1 : Math.exp(modelPredictions.score(1))
+                    }
+
+                  }, all_ages)
+
+              }, itemLineParameters.slope)
+            }, itemLineParameters.intercept)
+
+        }, itemVariability.slope)
+      }, itemVariability.intercept)
+    }, globalLineParameters.slope)
+  }, globalLineParameters.intercept)
+
+  _.flattenDeep(output)
+  // return query
+}
+'
+```
+
+```{r}
+me_model_data <- read_csv("../data/child_basic_me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
+
+sem_know_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, semKnowPriors , "model()", sep='\n'),
+  data = list(data = me_model_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  #inference_opts = list(method = "enumerate")
+)
+
+```
+
+# copied code
+
+=>
+```{r}
+save(sem_know_model, "parameter_enumeration_so1_flatPriors.RData")
+load(file = "parameter_enumeration_so1_flatPriors.RData")# sem_know_model
 ```
@@
 ```
-
-```{r}
-
-model_pred <- sem_know_model %>%
-  separate(Parameter, into = c("type", "item","x"))%>%
-  filter(type == "modelPrediction")%>%
-  separate(value, into = c("age", "pred"),sep = ", ")%>%
-  mutate(age = as.numeric(str_remove_all(age, "[(c]")),
-         pred = as.numeric(str_remove(pred, "[)]")))%>%
-  select(-x)
-
-item_params<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
-  filter(parameter == "parameter", type == "items")%>%
-  separate(value, into = c("int", "slope"),sep = ", ")%>%
-  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]")))%>%
-  gather(parameter, value, int, slope)
-
-global_params <- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
-  filter(parameter == "parameter", type == "parameters")%>%
-    separate(value, into = c("int", "slope"),sep = ", ")%>%
-    mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]")))%>%
-    gather(parameter, value, int, slope)
-
-global_sigma<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
-  filter(parameter == "parameter", type == "sigma")%>%
-    separate(value, into = c("sigma_int", "sigma_slope"),sep = ", ")%>%
-    mutate(sigma_int = as.numeric(str_remove_all(sigma_int, "[(c]")),
-         sigma_slope = as.numeric(str_remove(sigma_slope, "[)]")))%>%
-    gather(parameter, value, sigma_int, sigma_slope)
-
-#### summaries
-
-model_pred_summary <- model_pred %>%
-  group_by(item,age)%>%
-  summarise(mode = estimate_mode(pred),
-            uci = hdi_upper(pred),
-            lci = hdi_lower(pred))
-
-item_params_summary <- item_params %>%
-  group_by(item, parameter)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
-global_params_summary <- global_params %>%
-  group_by(token, parameter)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
-```
-
-```{r}
-ggplot(item_params, aes(x = value))+#, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Parameter")+
-  facet_grid(parameter~item, scales = 'free')+
-  theme_few()
-```
-
-```{r}
-
-ggplot(global_params, aes(x = value))#, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Parameter")+
-  facet_grid(parameter~token, scales = 'free')+
-  theme_few()
-```
-
-```{r}
-ggplot(global_sigma, aes(x = value))+#, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Sigma")+
-  facet_grid(~parameter, scales = 'free')+
-  theme_few()
-```
-
-## Plotting semantic knowledge
-```{r}
-aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
-
-aoa_ratings <- aoa_ratings_all %>%
-  filter(Word %in% item_params_summary$item )%>%
-  mutate(mean_aoa = as.numeric(Rating.Mean),
-         item = Word)%>%
-  select(item,mean_aoa)
-
-plot_sem_know <- item_params_summary%>%
-  select(-uci,-lci)%>%
-  spread(parameter, -item) %>%
-  left_join(expand.grid(
-      age = unique(me_model_data$age),
-      item = me_model_data$familiar), .) %>%
-  mutate(sem_know = plogis(int + slope * age)) %>%
-  left_join(aoa_ratings) %>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-ggplot(plot_sem_know, aes(x = age+2, y= sem_know, col = item, group = item))+
-  geom_line(size = 1)+
-  ylab("Semantic knowledge")+
-  xlab("Age")+
-  ylim(0,1)+
-  theme_few()+
-  scale_colour_viridis_d(name = "familiar object")
-```
-
-# inverse predictions
-
-```{r}
-# speak_opt_params <- speak_opt %>%
-#   group_by(parameter)%>%
-#   summarise(mode = estimate_mode(value),
-#             uci = hdi_upper(value),
-#             lci = hdi_lower(value))
-# 
-# inv_model_data <- sem_know_model %>%
-#   filter(Parameter != "speaker_optimality") %>%
-#   mutate(Parameter = factor(Parameter)) %>%
-#   separate(value, into = c("intercept", "slope"), 
-#            sep = ", ") %>%
-#   mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
-#          slope = as.numeric(str_remove(slope, "[)]"))) %>%
-#   rename(item = Parameter)%>%
-#   group_by(item)%>%
-#   summarise(sem_int = estimate_mode(intercept),
-#             sem_slope = estimate_mode(slope))%>%
-#   group_by(item)%>%
-#   expand(sem_int,sem_slope,age = me_model_data$age)%>%
-#   mutate(so_int = speak_opt_params%>%filter(parameter == "intercept")%>%pull(mode),
-#          so_slope = speak_opt_params%>%filter(parameter == "slope")%>%pull(mode))%>%
-#   mutate(speaker_optimality = so_int + so_slope * age,
-#          semantic_knowledge = plogis(sem_int + sem_slope * age))
-
-```
-
-```{r}
-invPred <- '
-var allData = dataFromR.data
-
-var priorProbs = [.5,.5]
-
-var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, row.speaker_optimality,row.semantic_knowledge)
-
-    return extend([row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions pragmatic model ex 3 adults}
-# inv_model_pred<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
-#   data =list(data = inv_model_data),
-#   data_var = "dataFromR"
-# )
-# 
-# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
-# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
-# 
-# inv_predictions <- inv_model_pred %>%
-#   separate(`0`, into = c("item", "age"), sep="/")%>%
-#   mutate(age = as.numeric(age))%>%
-#   rename( me_effect = `1`)%>%
-#   left_join(aoa_ratings)%>%
-#   ungroup()%>%
-#   mutate(item = fct_reorder(factor(item), mean_aoa), 
-#          age = age + min(me_data$age_num))
-```
-
-```{r}
-plot_model_pred <- model_pred_summary%>%
-  left_join(aoa_ratings) %>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-ggplot(plot_model_pred, aes(x=age+2,y = mode, col = item))+
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(size = 1)+
-  ggtitle("Inverse Model Predictions")+
-  labs(x="Age",y="Proportion correct")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d()
-
-```
-
-## For comparison: GLMM for ME effect and data
-```{r}
-me_data <- read_csv("../data/child_basic_me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(z_age = age_num - mean(age_num))
-
-# me_model <- brm(correct ~ z_age + (1|subid) + (z_age | familiar),
-#                 data = me_data,
-#                 family = bernoulli(),
-#                 control = list(adapt_delta = 0.95),
-#                 sample_prior = F,
-#                 save_all_pars = TRUE,
-#                 iter = 2000)
-
-#saveRDS(me_model, "../saves/me_effect_model.rds")
-
-me_model <- readRDS("../saves/me_effect_model.rds")
-
-summary(me_model)
-
-fixef <- as_tibble(fixef(me_model), rownames = "term")
-
-ranef <-  ranef(me_model)
-
-age_me_effect <- as_tibble(ranef$familiar, rownames = "familiar")%>%
-  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
-         grand_slope = fixef%>%filter(term=="z_age")%>%pull(Estimate))%>%
-  group_by(familiar) %>%
-  expand(Estimate.Intercept,Estimate.z_age,grand_intercept,grand_slope,z_age = me_data$age_num - mean(me_data$age_num), mean_age = mean(me_data$age_num))%>%
-  mutate(me_effect = plogis(grand_intercept + Estimate.Intercept+(Estimate.z_age+grand_slope)*z_age), 
-         age = z_age+mean_age,
-         item = familiar)%>%
-  select(item, me_effect, age)%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-model_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = item))+
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(size = 1)+
-  ggtitle("GLMM")+
-  labs(x="Age",y="Proportion correct")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d(name = "familiar object")
-
-p2 <- read_csv("../data/child_basic_me.csv")%>%
-  filter(trial != "train1",
-         trial != "train2")%>%
-  mutate(item = familiar)%>%
-    left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(familiar = fct_reorder(factor(item), mean_aoa))
-
-data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  #facet_grid(~familiar)+
-  ggtitle("Data")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d(name = "familiar object")+
-  scale_fill_viridis_d(name = "familiar object")
-data_plot
-```
-
-```{r}
-ggarrange(data_plot,inv_model_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 3)
-```
-
-#### WORK IN PROGRESS: nesting within participant
-
-to do:
-- bookkeeping: index correct participant/item variables at relevant part of code
-- inference: try HMC, variational
-
-```{r work in progress}
-semStr <- '
-var data = dataFromR.data
-
-var priorProbs = [.5,.5]
-
-var familiars = levels(data, "familiar")
-
-var model  = function(){
-
-  // global parameters
-  var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
-  var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
-
-  var sem_slope_global = uniformDrift({a: -2, b: 2, width: 0.2})
-  var sem_int_global = uniformDrift({a: 0, b: 5, width: 0.2})
-
-  var item_slope_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
-  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
-
-  var participant_age_adjust = gaussianDrift({mu: 0, sigma: 1, width: 0.2})
-
-  var sem_slope_item = repeat(familiars.length, function(){
-    gaussianDrift({mu: sem_slope_global, sigma: item_slope_sigma, width: 0.5} )
-  })
-
-  var sem_int_item = gaussianDrift({mu: sem_int_global, 
-        sigma: item_int_sigma, width: 0.5})
-
-  foreach(function(cndtn){
-
-    var conditionData = _.filter(data, {familiar: cndtn})
-
-    foreach(function(row){
-
-      var age = row.age
-
-      var sem_knowledge = logistic(sem_int_item + sem_slope_item * age)
-
-      var speakerOptimality = so_int  + so_slope * age
-
-      var modelPredictions = pragmaticListener({label: "novel_word"}, 
-            priorProbs, speakerOptimality, sem_knowledge)
-      // display(modelPredictions.score(row.correct))
-
-      observe(modelPredictions, row.correct)
-
-      query.add(["modelPrediction", cndtn], [age, Math.exp(modelPredictions.score(1))])
-
-    }, conditionData)
-
-    query.add(["parameter", cndtn], [sem_int_item, sem_slope_item])
-
-  }, familiars)
-
-  query.add(["parameter", "speaker_optimality"], [so_int, so_slope])
-  query.add(["parameter", "global_sem"], [sem_int_global, sem_slope_global])
-  query.add(["parameter", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])
-
-  return query 
-}
-'
-```

### 2019-05-05 stats/model.Rmd
restrict prior range to more sensible range; rename parameters for clarity

@@
 
-  var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
-  var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
-  //var speakerOptimality = uniformDrift({a: -5, b: 5, width: 0.2})
+  var speakerOptimalityParameters = {
+    intercept: uniformDrift({a: -2, b: 2, width: 0.5}),
+    slope: uniformDrift({a: -2, b: 2, width: 0.5})
+  }
 
-  var sem_slope_global = uniformDrift({a: -2, b: 2, width: 0.2})
-  var sem_int_global = uniformDrift({a: 0, b: 5, width: 0.2})
+  var globalLineParameters = {
+    intercept: uniformDrift({a: -3, b: 3, width: 1}),
+    slope: uniformDrift({a: -3, b: 3, width: 1})
+  }
 
-  var item_slope_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
+  var itemVariability = {
+    intercept: uniformDrift({a: 0, b: 1, width: 0.2}),
+    slope: uniformDrift({a: 0, b: 1, width: 0.2})
+  }
+
   // conceptually it might not make sense to have two sigmas, but maybe it does
@@
 
-    var sem_slope_item = gaussianDrift({mu: sem_slope_global, sigma: item_slope_sigma, width: 0.5})
-    var sem_int_item = gaussianDrift({mu: sem_int_global, sigma: item_int_sigma, width: 0.5})
-
-    // var sem_slope = uniformDrift({a: -2, b: 2, width: 0.2})
-    // var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})
+      var itemLineParameters = {
+        intercept: gaussianDrift({
+          mu: globalLineParameters.intercept, 
+          sigma: itemVariability.intercept, 
+          width: 0.5
+        }),
+        slope: gaussianDrift({
+          mu: globalLineParameters.slope, 
+          sigma: itemVariability.slope, 
+          width: 0.5
+        })
+      }
 
@@
 
-      var sem_knowledge = logistic(sem_int_item + sem_slope_item * age)
+      var sem_knowledge = logistic(itemLineParameters.intercept + 
+          itemLineParameters.slope * age)
 
-      var speakerOptimality = so_int  + so_slope * age
+      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * age
 
@@
 
-    query.add(["parameter","items", cndtn], [sem_int_item, sem_slope_item])
+    query.add(["parameter","items", cndtn], [itemLineParameters.intercept, itemLineParameters.slope])
 
@@
 
-  query.add(["parameter","parameters","speaker_optimality"], [so_int, so_slope])
-  query.add(["parameter","parameters", "global_sem"], [sem_int_global, sem_slope_global])
-  query.add(["parameter","sigma", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])
+  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
+  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
+  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
 

### 2019-05-05 stats/model-understanding.Rmd
simple model for effective range of item parameters; some viz

@@
 library(tidyverse)
+library(viridis)
 library(rwebppl)
@@
 
-```{r old}
+```{r loop through bda model structure}
 semKnowPriors <- '
@@
   var globalLineParameters = {
-    intercept:  discreteUniformBins(0, 5, 2),
-    slope: discreteUniformBins(-2, 2, 2)
+    intercept:  discreteUniformBins(0, 5, 1),
+    slope: discreteUniformBins(-2, 2.01, 1)
   }
@@
   var itemVariability = {
-    intercept: discreteUniformBins(0.01, 5, 2),
-    slope: discreteUniformBins(0.01, 5, 2)
+    intercept: discreteUniformBins(0.01, 5, 1),
+    slope: discreteUniformBins(0.01, 5, 1)
   }
@@
   var output = map(function(globalLineIntercept){
+  display(globalLineIntercept)
     map(function(globalLineSlope){
@@
               intercept: discreteUniformBins(
-                globalLineIntercept - 1*itemVariabilityIntercept,
-                globalLineIntercept + 1*itemVariabilityIntercept,
+                globalLineIntercept - 2*itemVariabilityIntercept,
+                 globalLineIntercept + 2*itemVariabilityIntercept,
                  itemVariabilityIntercept
@@
               slope: discreteUniformBins(
-                globalLineSlope - 1*itemVariabilitySlope,
-                globalLineSlope + 1*itemVariabilitySlope,
+                 globalLineSlope - 2*itemVariabilitySlope,
+                globalLineSlope + 2*itemVariabilitySlope,
                 itemVariabilitySlope
@@
                   map(function(age){
-                    var sem_knowledge = logistic(itemLineIntercept + 
-                      itemLineSlope * age)
-                    // display(itemLineParameters.intercept + "+ " + itemLineParameters.slope + " X " + age + " =logistic= " + sem_knowledge)
+                    var sem_knowledge = logistic(
+                      itemLineIntercept + itemLineSlope * age
+                    )
+
                     var priorProbs =  [.5,.5]
@@
                             priorProbs, speakerOptimality, sem_knowledge)
-                    var smk =  "semKnowledge_" + age
-                    var mpa =  "modelPrediction_" + age
+
                     return {
@@
   _.flattenDeep(output)
-  // return query
 }
@@
 
+subset.ages <- unique(sem_know_model$age)[seq(1, 90, 10)]
 ```
 
-# copied code
+Parameter ranges
 
-=>
 ```{r}
-save(sem_know_model, "parameter_enumeration_so1_flatPriors.RData")
-load(file = "parameter_enumeration_so1_flatPriors.RData")# sem_know_model
+summary(sem_know_model)
 ```
 
+- Is it expected that L1 predicitons should only range between 0.25 and 0.75? (this may be because speaker optimality = 1)
+
+### L1 prediction vs. sem_knowledge
+
 ```{r}
-baseMeModel <- '
-
-var sem_knowledge = 1
-
-var priorProbs = [.5,.5]
-
-var speakerOptimality = 1
-
-var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality, sem_knowledge)
-
-modelPredictions
-
-'
+sem_know_model %>% 
+  distinct(sem_knowledge, L1) %>%
+  ggplot(., aes( x = sem_knowledge, y = L1 ))+
+  geom_point()+
+  ylim(0, 1)
 ```
 
+### L1 prediction vs. item intercept
+
 ```{r}
-webppl(program_code = paste(rsaUtils, rsaModel, baseMeModel,sep='\n'))
+sem_know_model %>% 
+  distinct(item_intercept, L1) %>%
+  ggplot(., aes( x = item_intercept, y = L1 ))+
+  geom_point()+
+  ylim(0, 1)
 ```
 
-# Inferring semantic knowledge
+### L1 prediction vs. item slope
+
 ```{r}
-semStr <- '
+sem_know_model %>% 
+  distinct(item_slope, L1) %>%
+  ggplot(., aes( x = item_slope, y = L1 ))+
+  geom_point()+
+  ylim(0, 1)
+```
+
+#### Original priors entailed the effective range for item parameters of [-10, 10] for the slope and [-8, 8] for the intercept
+
+```{r loop through relevant range}
+semKnowPriorsReduced <- '
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+
 var data = dataFromR.data
@@
 
+var discreteUniformBins = function(lower, upper, bin_width){
+  _.range(lower, upper, bin_width)
+}
+
+var all_ages = sort(levels(data, "age"))
+
 var model  = function(){
+  var itemLineParameters = {
+    intercept: discreteUniformBins( -8, 9, 1),
+    slope: discreteUniformBins( -10, 11, 1 )
+  }
+  var output = map(function(itemLineIntercept){
+                map(function(itemLineSlope){
+                  map(function(age){
+                    var sem_knowledge = logistic(
+                      itemLineIntercept + itemLineSlope * age
+                    )
 
-  var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
-  var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
-  //var speakerOptimality = uniformDrift({a: -5, b: 5, width: 0.2})
-
-  var sem_slope_global = uniformDrift({a: -2, b: 2, width: 0.2})
-  var sem_int_global = uniformDrift({a: 0, b: 5, width: 0.2})
-
-  var item_slope_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
-  // conceptually it might not make sense to have two sigmas, but maybe it does
-  // intercept sigma probably will be smaller than slope sigma
-  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
-
-  foreach(function(cndtn){
-
-    var conditionData = _.filter(data, {familiar: cndtn})
-
-    var sem_slope_item = gaussianDrift({mu: sem_slope_global, sigma: item_slope_sigma, width: 0.5})
-    var sem_int_item = gaussianDrift({mu: sem_int_global, sigma: item_int_sigma, width: 0.5})
-
-    // var sem_slope = uniformDrift({a: -2, b: 2, width: 0.2})
-    // var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})
-
-    foreach(function(row){
-
-      var age = row.age
-
-      //display(age)
-
-      var sem_knowledge = logistic(sem_int_item + sem_slope_item * age)
-
-      var speakerOptimality = so_int  + so_slope * age
+                    var priorProbs =  [.5,.5]
+                    var speakerOptimality = 1
 
@@
                             priorProbs, speakerOptimality, sem_knowledge)
-      // display(modelPredictions.score(row.correct))
 
-      observe(modelPredictions, row.correct)
+                    return {
+                      item_intercept: itemLineIntercept,
+                      item_slope: itemLineSlope,
+                      age: age,
+                      sem_knowledge : sem_knowledge,
+                      L1 : Math.exp(modelPredictions.score(1))
+                    }
 
-      query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
+                  }, all_ages)
 
-    }, conditionData)
+              }, itemLineParameters.slope)
+            }, itemLineParameters.intercept)
 
-    query.add(["parameter","items", cndtn], [sem_int_item, sem_slope_item])
-
-  }, familiars)
-
-  query.add(["parameter","parameters","speaker_optimality"], [so_int, so_slope])
-  query.add(["parameter","parameters", "global_sem"], [sem_int_global, sem_slope_global])
-  query.add(["parameter","sigma", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])
-
-  return query 
+  _.flattenDeep(output)
 }
@@
 ```{r}
-me_model_data <- read_csv("../data/child_basic_me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(age = age_num - min(age_num))
 
-sem_know_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+sem_know_model_reduced <- webppl(
+  program_code = paste(rsaUtils, rsaModel, semKnowPriorsReduced , "model()", sep='\n'),
   data = list(data = me_model_data),
@@
   model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "incrementalMH", 
-                        samples = 2000, 
-                        burn = 1000,
-                        verbose = T,
-                        verboseLag = 500)
+  #inference_opts = list(method = "enumerate")
 )
 
-#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
-sem_know_model <- readRDS("../saves/sem_know_model.rds")
+subset.ages <- unique(sem_know_model$age)[seq(1, 90, 10)]
 ```
+
+### L1 prediction vs. item slope X item intercept
+
+```{r}
+sem_know_model_reduced %>% 
+  filter(age %in% subset.ages) %>%
+  filter(item_intercept < 5, item_intercept > -5,
+         item_slope < 5, item_slope > -5) %>%
+  distinct(age, item_intercept, item_slope, sem_knowledge) %>%
+  ggplot(., aes( x = item_intercept, y = item_slope, fill = sem_knowledge ))+
+  geom_tile()+
+  facet_wrap(~age)+
+  scale_fill_viridis()
+
+ggsave("semKnowledge_bySlope_int.pdf")
+```

### 2019-05-08 stats/model.Rmd
investigate model parameters

@@
 title: "Model"
-author: "M. Bohn"
 output: html_document
@@
     intercept: uniformDrift({a: -3, b: 3, width: 1}),
-    slope: uniformDrift({a: -3, b: 3, width: 1})
+    slope: uniformDrift({a: 0, b: 3, width: 1})
   }
@@
   // intercept sigma probably will be smaller than slope sigma
-  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
+  // var item_int_sigma = uniformDrift({a: 0, b: 3, width: 0.2})
 
@@
 
-      query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
+      // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
 
@@
   model_var = "model",
-  chains = 3,
-  cores = 3,
+  chains = 4,
+  cores = 4,
   inference_opts = list(method = "incrementalMH", 
@@
                         verbose = T,
-                        verboseLag = 500)
+                        #lag = 1,
+                        verboseLag = 1000)
 )
 
-#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
+saveRDS(sem_know_model, "../saves/sem_know_model.rds")
 sem_know_model <- readRDS("../saves/sem_know_model.rds")
+
+sem_know_model <- sem_know_model %>%
+  filter(Chain != 3)
+
 ```
@@
 ```{r}
-ggplot(item_params, aes(x = value))+#, fill = factor(Chain)))+
+ggplot(item_params, aes(x = value, fill = factor(Chain)))+
   geom_density(alpha = 0.3)+
@@
 
-ggplot(global_params, aes(x = value))#, fill = factor(Chain)))+
+ggplot(global_params, aes(x = value, fill = factor(Chain)))+
   geom_density(alpha = 0.3)+
@@
 ```{r}
-ggplot(global_sigma, aes(x = value))+#, fill = factor(Chain)))+
+ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
   geom_density(alpha = 0.3)+
@@
 #
-# inv_model_data <- sem_know_model %>%
-#   filter(Parameter != "speaker_optimality") %>%
-#   mutate(Parameter = factor(Parameter)) %>%
-#   separate(value, into = c("intercept", "slope"), 
-#            sep = ", ") %>%
-#   mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
-#          slope = as.numeric(str_remove(slope, "[)]"))) %>%
-#   rename(item = Parameter)%>%
-#   group_by(item)%>%
-#   summarise(sem_int = estimate_mode(intercept),
-#             sem_slope = estimate_mode(slope))%>%
-#   group_by(item)%>%
-#   expand(sem_int,sem_slope,age = me_model_data$age)%>%
-#   mutate(so_int = speak_opt_params%>%filter(parameter == "intercept")%>%pull(mode),
-#          so_slope = speak_opt_params%>%filter(parameter == "slope")%>%pull(mode))%>%
-#   mutate(speaker_optimality = so_int + so_slope * age,
-#          semantic_knowledge = plogis(sem_int + sem_slope * age))
+
+inv_model_data <- item_params_summary%>%
+  select(-uci,-lci)%>%
+  spread(parameter, mode)%>%
+  expand(item, int,slope,age = unique(me_model_data$age- min(me_model_data$age)))%>%
+  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
+         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode))%>%
+  mutate(speaker_optimality = so_int + so_slope * age,
+         semantic_knowledge = plogis(int + slope * age))
 
@@
 ```{r predictions pragmatic model ex 3 adults}
-# inv_model_pred<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
-#   data =list(data = inv_model_data),
-#   data_var = "dataFromR"
-# )
+inv_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
+  data =list(data = inv_model_data),
+  data_var = "dataFromR"
+)
 # 
@@
 # 
-# inv_predictions <- inv_model_pred %>%
-#   separate(`0`, into = c("item", "age"), sep="/")%>%
-#   mutate(age = as.numeric(age))%>%
-#   rename( me_effect = `1`)%>%
-#   left_join(aoa_ratings)%>%
-#   ungroup()%>%
-#   mutate(item = fct_reorder(factor(item), mean_aoa), 
-#          age = age + min(me_data$age_num))
+inv_predictions <- inv_model_pred %>%
+  separate(`0`, into = c("item", "age"), sep="/")%>%
+  mutate(age = as.numeric(age))%>%
+  rename( me_effect = `1`)%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         age = age + min(me_data$age_num))
 ```
@@
 
-ggplot(plot_model_pred, aes(x=age+2,y = mode, col = item))+
+ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   scale_fill_viridis_d(name = "familiar object")
+
 data_plot

### 2019-05-13 stats/model.Rmd
model predictions that make sense

@@
     intercept: uniformDrift({a: -2, b: 2, width: 0.5}),
-    slope: uniformDrift({a: -2, b: 2, width: 0.5})
+    slope: uniformDrift({a: 0, b: 2, width: 0.5})
   }
@@
   model_var = "model",
-  chains = 4,
-  cores = 4,
+  chains = 3,
+  cores = 3,
   inference_opts = list(method = "incrementalMH", 
-                        samples = 2000, 
-                        burn = 1000,
+                        samples = 6000, 
+                        burn = 2000,
                         verbose = T,
-                        #lag = 1,
+                        lag = 1,
                         verboseLag = 1000)
@@
 
-saveRDS(sem_know_model, "../saves/sem_know_model.rds")
+#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
 sem_know_model <- readRDS("../saves/sem_know_model.rds")
@@
 
-model_pred <- sem_know_model %>%
-  separate(Parameter, into = c("type", "item","x"))%>%
-  filter(type == "modelPrediction")%>%
-  separate(value, into = c("age", "pred"),sep = ", ")%>%
-  mutate(age = as.numeric(str_remove_all(age, "[(c]")),
-         pred = as.numeric(str_remove(pred, "[)]")))%>%
-  select(-x)
+# model_pred <- sem_know_model %>%
+#   separate(Parameter, into = c("type", "item","x"))%>%
+#   filter(type == "modelPrediction")%>%
+#   separate(value, into = c("age", "pred"),sep = ", ")%>%
+#   mutate(age = as.numeric(str_remove_all(age, "[(c]")),
+#          pred = as.numeric(str_remove(pred, "[)]")))%>%
+#   select(-x)
 
@@
 
-model_pred_summary <- model_pred %>%
-  group_by(item,age)%>%
-  summarise(mode = estimate_mode(pred),
-            uci = hdi_upper(pred),
-            lci = hdi_lower(pred))
+# model_pred_summary <- model_pred %>%
+#   group_by(item,age)%>%
+#   summarise(mode = estimate_mode(pred),
+#             uci = hdi_upper(pred),
+#             lci = hdi_lower(pred))
 
@@
 ```{r}
-plot_model_pred <- model_pred_summary%>%
-  left_join(aoa_ratings) %>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
+# plot_model_pred <- model_pred_summary%>%
+#   left_join(aoa_ratings) %>%
+#   ungroup()%>%
+#   mutate(item = fct_reorder(factor(item), mean_aoa))
 
-ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
+model_plot <- ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
   geom_hline(yintercept = 0.5, lty=2)+
@@
 
+```
+
+```{r}
+p2 <- read_csv("../data/child_basic_me.csv")%>%
+  filter(trial != "train1",
+         trial != "train2")%>%
+  mutate(item = familiar)%>%
+    left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiar = fct_reorder(factor(item), mean_aoa))
+
+data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  #facet_grid(~familiar)+
+  ggtitle("Data")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d(name = "familiar object")+
+  scale_fill_viridis_d(name = "familiar object")
+
+```
+```{r}
+ggarrange(data_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
 ```
@@
 
-p2 <- read_csv("../data/child_basic_me.csv")%>%
-  filter(trial != "train1",
-         trial != "train2")%>%
-  mutate(item = familiar)%>%
-    left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(familiar = fct_reorder(factor(item), mean_aoa))
-
-data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  #facet_grid(~familiar)+
-  ggtitle("Data")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d(name = "familiar object")+
-  scale_fill_viridis_d(name = "familiar object")
-
-data_plot
-```
-
-```{r}
-ggarrange(data_plot,inv_model_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 3)
 ```

### 2019-05-29 stats/kids_novelty.Rmd
investigate model parameters
add model predictions for combination

@@
 
+write_csv(d_spin, "../data/child_spin_novelty.csv")
 write_csv(d, "../data/child_novelty.csv")
-
 ```
@@
 
-# GLMM
+# SPIN GLMM
 
-## Models
+```{r}
+spin_model_data <- d_spin%>%
+  mutate(age_num = age_num-min(age_num))
+
+spin_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
+          data = spin_model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 2000)
+
+summary(spin_bm)
+```
+
+# Comparison with MCC Data
+
+## Model
 

### 2019-05-29 stats/model.Rmd
add model predictions for combination

@@
 
-sem_know_model <- sem_know_model %>%
-  filter(Chain != 3)
-
 ```
@@
 
-# inverse predictions
+# Inverse predictions
 
@@
 
-model_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = item))+
+glmm_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = item))+
   geom_hline(yintercept = 0.5, lty=2)+
@@
 
+```
+
+```{r}
+ggarrange(data_plot,model_plot,glmm_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
+```
+
+## Model predictions for combination
+
+```{r}
+# novelty data
+
+novel_data <- read_csv("../data/child_spin_novelty.csv")%>%
+  mutate(age_num = age_num-min(age_num))
+
+novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
+          data = novel_data, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = F,
+          iter = 10000)
+
+summary(novel_bm)
+
+novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
+  select(term,Estimate)%>%
+  spread(term, Estimate)
+
+comb_model_data_con <- inv_model_data %>%
+  mutate(nov_int = novel_params$Intercept,
+         nov_slope = novel_params$age_num,
+         prior = plogis(nov_int + age * nov_slope),
+         alignment = "congruent")
+
+comb_model_data_incon <- inv_model_data %>%
+  mutate(nov_int = novel_params$Intercept,
+         nov_slope = novel_params$age_num,
+         prior = 1- plogis(nov_int + age * nov_slope),
+         alignment = "incongruent")
+
+comb_model_data <- bind_rows(
+  comb_model_data_con,
+  comb_model_data_incon)
+```
+
+```{r}
+combPred <- '
+var allData = dataFromR.data
+
+var output = map(function(row){
+
+    var prior = [row.prior, 1-row.prior]
+
+    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.semantic_knowledge)
+
+    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])
+
+}, allData)
+
+output
+
+'
+```
+
+```{r predictions pragmatic model ex 3 adults}
+comb_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
+  data =list(data = comb_model_data),
+  data_var = "dataFromR"
+)
+# 
+# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
+# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
+# 
+comb_model_predictions <- comb_model_pred %>%
+  separate(`0`, into = c("alignment","item", "age"), sep="/")%>%
+  mutate(age = as.numeric(age))%>%
+  rename( me_effect = `1`)%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         age = age + min(me_data$age_num))
+```
+
+```{r}
+ggplot(comb_model_predictions, aes(x=age,y = me_effect, col = item))+
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(size = 1)+
+  ggtitle("Combination Model Predictions")+
+  labs(x="Age",y="Proportion correct")+
+  facet_grid(~alignment)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d()
 ```

### 2019-05-29 stats/model.Rmd
add second model run

@@
   model_var = "model",
-  chains = 3,
-  cores = 3,
+  chains = 8,
+  cores = 8,
   inference_opts = list(method = "incrementalMH", 
-                        samples = 6000, 
+                        samples = 4000, 
                         burn = 2000,
@@
 sem_know_model <- readRDS("../saves/sem_know_model.rds")
-
 ```
@@
 ```{r}
-ggarrange(data_plot,model_plot,glmm_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
+ggarrange(data_plot,model_plot,glmm_plot, common.legend = T, legend = "right", nrow = 1, ncol = 3)
 ```
@@
 
-novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
-          data = novel_data, family = bernoulli(),
-          control = list(adapt_delta = 0.95),
-          sample_prior = F,
-          save_all_pars = F,
-          iter = 10000)
+# novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
+#           data = novel_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.95),
+#           sample_prior = F,
+#           save_all_pars = F,
+#           iter = 10000)
+# 
+# saveRDS(novel_bm, "../saves/novelty_model.rds")
+
+novel_bm <- readRDS("../saves/novelty_model.rds")
 

### 2019-05-29 stats/model.Rmd
add second model run

@@
 #saveRDS(sem_know_model, "../saves/sem_know_model.rds")
+
+# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
 sem_know_model <- readRDS("../saves/sem_know_model.rds")
+# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
+sem_know_model <- readRDS("../saves/sem_know_model_2.rds")
 ```

### 2019-05-31 stats/model.Rmd
plot sem know params across model runs

@@
 
-sem_know_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-  data = list(data = me_model_data),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 8,
-  cores = 8,
-  inference_opts = list(method = "incrementalMH", 
-                        samples = 4000, 
-                        burn = 2000,
-                        verbose = T,
-                        lag = 1,
-                        verboseLag = 1000)
-)
+# sem_know_model<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+#   data = list(data = me_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 8,
+#   cores = 8,
+#   inference_opts = list(method = "incrementalMH", 
+#                         samples = 4000, 
+#                         burn = 2000,
+#                         verbose = T,
+#                         lag = 1,
+#                         verboseLag = 1000)
+# )
 
@@
       age = unique(me_model_data$age),
-      item = me_model_data$familiar), .) %>%
+      item = unique(me_model_data$familiar)), .) %>%
   mutate(sem_know = plogis(int + slope * age)) %>%
@@
   scale_colour_viridis_d(name = "familiar object")
+```
+
+### Comparing sem knowledge parameters between model runs
+
+```{r}
+
+# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
+sem_know_run_1 <- readRDS("../saves/sem_know_model.rds")%>%
+  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
+  filter(parameter == "parameter", type == "items")%>%
+  separate(value, into = c("int", "slope"),sep = ", ")%>%
+  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]")))%>%
+  mutate(run = "1")
+
+# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
+sem_know_run_2 <- readRDS("../saves/sem_know_model_2.rds")%>%
+  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
+  filter(parameter == "parameter", type == "items")%>%
+  separate(value, into = c("int", "slope"),sep = ", ")%>%
+  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]")))%>%
+  mutate(run = "2")
+
+sem_know_run_iteration <- bind_rows(
+   sem_know_run_1,
+   sem_know_run_2)
+
+sem_know_run_summary <- sem_know_run_iteration%>%
+  group_by(run,item)%>%
+  summarise(overall_int = estimate_mode(int),
+            overall_slope = estimate_mode(slope))
+
+sem_know_run <- sem_know_run_iteration %>%
+  left_join(sem_know_run_summary)
+
+run_comp <- sem_know_run %>%
+  left_join(expand.grid(
+      age = unique(me_model_data$age),
+      item = unique(me_model_data$familiar)), .) %>%
+  mutate(sem_know_ci = plogis(int + slope * age),
+         sem_know = plogis(overall_int + overall_slope * age)) %>%
+  group_by(run,item, age) %>%
+  summarise(sem_know = estimate_mode(sem_know), 
+            sem_know_uci = hdi_upper(sem_know_ci),
+            sem_know_lci = hdi_lower(sem_know_ci))
+
+ggplot(run_comp, aes(x = age+2, y= sem_know, fill = run))+
+  geom_line(size = 1, aes(col = run))+
+  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .2)+
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  facet_wrap(~item)+
+  theme_few()+
+  scale_colour_solarized()+
+  scale_fill_solarized()
 ```

### 2019-05-31 stats/model.Rmd
update model run comp
update model run comparison plot

@@
 ```{r}
+me_model_data <- read_csv("../data/child_basic_me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
 
@@
 sem_know_run_summary <- sem_know_run_iteration%>%
-  group_by(run,item)%>%
+  group_by(run,Chain,item)%>%
   summarise(overall_int = estimate_mode(int),
@@
          sem_know = plogis(overall_int + overall_slope * age)) %>%
-  group_by(run,item, age) %>%
+  group_by(run,Chain,item, age) %>%
   summarise(sem_know = estimate_mode(sem_know), 
@@
 
-ggplot(run_comp, aes(x = age+2, y= sem_know, fill = run))+
-  geom_line(size = 1, aes(col = run))+
-  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .2)+
+ggplot(run_comp, aes(x = age+2, y= sem_know, fill = run, group = paste(run,Chain)))+
+  geom_line(size = .3, aes(col = run))+
+  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .1)+
   ylab("Semantic knowledge")+
@@
   scale_fill_solarized()
+
+ggsave("../graphs/model_by_chain_run.pdf", width = 10, height = 8)
 ```

### 2019-06-09 stats/model.Rmd
update model plotting

@@
     intercept: uniformDrift({a: -2, b: 2, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 2, width: 0.5})
+    slope: uniformDrift({a: 0, b: 1, width: 0.5})
   }
@@
   var globalLineParameters = {
-    intercept: uniformDrift({a: -3, b: 3, width: 1}),
-    slope: uniformDrift({a: 0, b: 3, width: 1})
+    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
+    slope: uniformDrift({a: 0, b: 2, width: 0.5})
   }
@@
 
-# sem_know_model<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-#   data = list(data = me_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 8,
-#   cores = 8,
-#   inference_opts = list(method = "incrementalMH", 
-#                         samples = 4000, 
-#                         burn = 2000,
-#                         verbose = T,
-#                         lag = 1,
-#                         verboseLag = 1000)
-# )
+sem_know_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+  data = list(data = me_model_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "incrementalMH",
+                        samples = 6000,
+                        burn = 2000,
+                        verbose = T,
+                        lag = 1,
+                        verboseLag = 1000)
+)
 
@@
 sem_know_model <- readRDS("../saves/sem_know_model_2.rds")
+
+sem_know_model <- sem_know_model %>%
+  filter(Chain != "1")
 ```
@@
 
-### Comparing sem knowledge parameters between model runs
+### Comparing parameters between model runs
+
+#### sem knowledge
 
@@
   ylim(0,1)+
-  facet_wrap(~item)+
+  facet_grid(item~run)+
   theme_few()+
@@
 
-ggsave("../graphs/model_by_chain_run.pdf", width = 10, height = 8)
+ggsave("../graphs/model_by_chain_run.pdf", width = 3, height = 12, scale = 1.5)
 ```
 
+#### speaker optimality
+
+```{r}
+me_model_data <- read_csv("../data/child_basic_me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
+
+# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
+so_run_1 <- readRDS("../saves/sem_know_model.rds")%>%
+  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
+  filter(parameter == "parameter", type == "parameters", token == "speaker_optimality")%>%
+  separate(value, into = c("int", "slope"),sep = ", ")%>%
+  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]")))%>%
+  mutate(run = "1")
+
+# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
+so_run_2 <- readRDS("../saves/sem_know_model_2.rds")%>%
+  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
+  filter(parameter == "parameter", type == "parameters", token == "speaker_optimality")%>%
+  separate(value, into = c("int", "slope"),sep = ", ")%>%
+  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]")))%>%
+  mutate(run = "2")
+
+so_run_iteration <- bind_rows(
+   so_run_1,
+   so_run_2)
+
+so_run_summary <- so_run_iteration%>%
+  group_by(run,Chain)%>%
+  summarise(overall_int = estimate_mode(int),
+            overall_slope = estimate_mode(slope))
+
+so_run <- so_run_iteration %>%
+  left_join(so_run_summary)
+
+so_run_comp <-so_run%>%
+  group_by(run,Chain,Iteration)%>%
+  expand(int,slope,overall_int,overall_slope,age = unique(me_model_data$age))%>%
+  mutate(so_ci = int + slope * age,
+         so = overall_int + overall_slope * age) %>%
+  group_by(run,Chain, age) %>%
+  summarise(so = estimate_mode(so), 
+            so_uci = hdi_upper(so_ci),
+            so_lci = hdi_lower(so_ci))
+
+ggplot(so_run_comp, aes(x = age+2, y= so, fill = run, group = paste(run,Chain)))+
+  geom_line(size = .3, aes(col = run))+
+  geom_ribbon(aes(ymin=so_lci, ymax = so_uci), alpha = .1)+
+  ylab("speaker optimality")+
+  xlab("Age")+
+  facet_grid(~run)+
+  theme_few()+
+  scale_colour_solarized()+
+  scale_fill_solarized()
+
+ggsave("../graphs/model_by_chain_run.pdf", width = 3, height = 12, scale = 1.5)
+```
 # Inverse predictions

### 2019-06-21 stats/kids_novelty.Rmd
correlate model parameters between runs

@@
 ```{r plot by numerical age}
-p5 <- d %>%
+p5 <- d_spin %>%
   group_by(age_num,experiment, subid) %>%
@@
 ggplot(data = p5, aes(x = age_num, y = correct, col = experiment)) +
-  geom_smooth(data = d, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
+  geom_smooth(data = d_spin, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
   geom_jitter( alpha = .5, height = 0.01)+

### 2019-06-21 stats/model.Rmd
correlate model parameters between runs

--- 2019-05-31 stats/model.Rmd
@@
 
-# sem_know_model<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-#   data = list(data = me_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 8,
-#   cores = 8,
-#   inference_opts = list(method = "incrementalMH", 
-#                         samples = 4000, 
-#                         burn = 2000,
-#                         verbose = T,
-#                         lag = 1,
-#                         verboseLag = 1000)
-# )
+sem_know_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+  data = list(data = me_model_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 10,
+  cores = 10,
+  inference_opts = list(method = "incrementalMH",
+                        samples = 4000,
+                        burn = 2000,
+                        verbose = T,
+                        lag = 1,
+                        verboseLag = 1000)
+)
 
@@
 # 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
-sem_know_model <- readRDS("../saves/sem_know_model.rds")
-# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
-sem_know_model <- readRDS("../saves/sem_know_model_2.rds")
+sem_know_model <- readRDS("../saves/run_correlations.rds")#%>%
+  # filter(Chain != "15",
+  #        Chain != "1",
+  #        Chain != "30",
+  #        Chain != "6",
+  #        Chain != "5",
+  #        Chain != "7",
+  #        Chain != "3")
+
 ```
@@
 
-### Comparing sem knowledge parameters between model runs
+### Comparing parameters between model runs
+
+#### sem knowledge
 
 ```{r}
+me_model_data <- read_csv("../data/child_basic_me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
 
-# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
-sem_know_run_1 <- readRDS("../saves/sem_know_model.rds")%>%
+sem_know_run_summary <- item_params%>%
+  spread(parameter,value)%>%
+  group_by(Chain,item)%>%
+  summarise(overall_int = estimate_mode(int),
+            overall_slope = estimate_mode(slope))
+
+sem_know_run_iteration <- item_params%>%
+  spread(parameter,value)
+
+sem_know_chain <- sem_know_run_iteration %>%
+  left_join(sem_know_run_summary)
+
+chain_comp <- sem_know_chain %>%
+  left_join(expand.grid(
+      age = unique(me_model_data$age),
+      item = unique(me_model_data$familiar)), .) %>%
+  mutate(sem_know_ci = plogis(int + slope * age),
+         sem_know = plogis(overall_int + overall_slope * age)) %>%
+  group_by(Chain,item, age) %>%
+  summarise(sem_know = estimate_mode(sem_know), 
+            sem_know_uci = hdi_upper(sem_know_ci),
+            sem_know_lci = hdi_lower(sem_know_ci))
+
+ggplot(chain_comp, aes(x = age+2, y= sem_know, fill = factor(Chain)))+
+  geom_line(size = .3, aes(col = factor(Chain)))+
+  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .05)+
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  facet_wrap(~item, nrow = 3)+
+  theme_few()+
+  scale_colour_discrete()+
+  scale_fill_discrete()
+
+ggsave("../graphs/model_by_chain.pdf", width = 5, height = 4, scale = 1.5)
+```
+
+#### speaker optimality
+
+```{r}
+me_model_data <- read_csv("../data/child_basic_me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
+
+so_run_iteration <- global_params%>%
+  spread(parameter, value)
+
+so_run_summary <- so_run_iteration%>%
+  group_by(Chain)%>%
+  summarise(overall_int = estimate_mode(int),
+            overall_slope = estimate_mode(slope))
+
+so_run <- so_run_iteration %>%
+  left_join(so_run_summary)
+
+so_run_comp <-so_run%>%
+  group_by(Chain,Iteration)%>%
+  expand(int,slope,overall_int,overall_slope,age = unique(me_model_data$age))%>%
+  mutate(so_ci = int + slope * age,
+         so = overall_int + overall_slope * age) %>%
+  group_by(Chain, age) %>%
+  summarise(so = estimate_mode(so), 
+            so_uci = hdi_upper(so_ci),
+            so_lci = hdi_lower(so_ci))
+
+ggplot(so_run_comp, aes(x = age+2, y= so, fill = factor(Chain)))+
+  geom_line(size = .4, aes(col = factor(Chain)))+
+  geom_ribbon(aes(ymin=so_lci, ymax = so_uci), alpha = .05)+
+  ylab("speaker optimality")+
+  xlab("Age")+
+  #facet_grid(~run)+
+  theme_few()+
+  scale_colour_discrete()+
+  scale_fill_discrete()
+
+ggsave("../graphs/so_by_chain.pdf", width = 4, height = 3, scale = 1.5)
+```
+
+#### Correlations between parameters for semantic knowledge
+
+```{r}
+# sem_know_model_1<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+#   data = list(data = me_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 10,
+#   cores = 10,
+#   inference_opts = list(method = "incrementalMH",
+#                         samples = 4000,
+#                         burn = 2000,
+#                         verbose = T,
+#                         lag = 1,
+#                         verboseLag = 1000)
+# )
+# 
+# sem_know_model_2<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+#   data = list(data = me_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 10,
+#   cores = 10,
+#   inference_opts = list(method = "incrementalMH",
+#                         samples = 4000,
+#                         burn = 2000,
+#                         verbose = T,
+#                         lag = 1,
+#                         verboseLag = 1000)
+# )%>%
+#   mutate(Chain = Chain +10)
+# 
+# sem_know_model_3<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+#   data = list(data = me_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 10,
+#   cores = 10,
+#   inference_opts = list(method = "incrementalMH",
+#                         samples = 4000,
+#                         burn = 2000,
+#                         verbose = T,
+#                         lag = 1,
+#                         verboseLag = 1000)
+# )%>%
+#   mutate(Chain = Chain +20)
+# 
+# 
+# sem_know_cor_params <- bind_rows(
+#   sem_know_model_1,
+#   sem_know_model_2,
+#   sem_know_model_3
+# )%>%
+#   saveRDS(.,"../saves/run_correlations.rds")
+
+sem_know_cor_params  <- readRDS("../saves/run_correlations.rds")%>%
   separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
@@
          slope = as.numeric(str_remove(slope, "[)]")))%>%
-  mutate(run = "1")
+  gather(parameter, value, int, slope)
+ # %>%
+#   filter(Chain != "15",
+#          Chain != "1",
+#          Chain != "30",
+#          Chain != "6",
+#          Chain != "5",
+#          Chain != "7",
+#          Chain != "3")
 
-# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
-sem_know_run_2 <- readRDS("../saves/sem_know_model_2.rds")%>%
-  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
-  filter(parameter == "parameter", type == "items")%>%
-  separate(value, into = c("int", "slope"),sep = ", ")%>%
-  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]")))%>%
-  mutate(run = "2")
+```
 
-sem_know_run_iteration <- bind_rows(
-   sem_know_run_1,
-   sem_know_run_2)
+```{r}
+ggplot(sem_know_cor_params%>%filter(parameter == "int"), aes(x = value))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(Chain~item, scales = 'free')+
+  theme_few()
 
-sem_know_run_summary <- sem_know_run_iteration%>%
-  group_by(run,item)%>%
-  summarise(overall_int = estimate_mode(int),
-            overall_slope = estimate_mode(slope))
+ggsave("../graphs/item_by_chain.pdf", width = 15, height = 15, scale = 1.5)
+```
 
-sem_know_run <- sem_know_run_iteration %>%
-  left_join(sem_know_run_summary)
+```{r}
+item_params_cor <- sem_know_cor_params %>%
+  group_by(Chain,item, parameter)%>%
+  summarise(mode = estimate_mode(value))
+```
 
-run_comp <- sem_know_run %>%
-  left_join(expand.grid(
-      age = unique(me_model_data$age),
-      item = unique(me_model_data$familiar)), .) %>%
-  mutate(sem_know_ci = plogis(int + slope * age),
-         sem_know = plogis(overall_int + overall_slope * age)) %>%
-  group_by(run,item, age) %>%
-  summarise(sem_know = estimate_mode(sem_know), 
-            sem_know_uci = hdi_upper(sem_know_ci),
-            sem_know_lci = hdi_lower(sem_know_ci))
+```{r}
+library(corrr)
+library(corrplot)
 
-ggplot(run_comp, aes(x = age+2, y= sem_know, fill = run))+
-  geom_line(size = 1, aes(col = run))+
-  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .2)+
-  ylab("Semantic knowledge")+
-  xlab("Age")+
-  ylim(0,1)+
-  facet_wrap(~item)+
-  theme_few()+
-  scale_colour_solarized()+
-  scale_fill_solarized()
+## correaltion at 2
+cor_int_2 <- item_params_cor%>%
+  spread(Chain, mode) %>%
+  filter(parameter == "int")%>%
+  select(-parameter)%>%
+  ungroup()%>%
+  select(-item)%>%
+  correlate(method = "spearman")%>%
+  gather(key, value)%>%
+  filter(key !="rowname")%>%
+  na.omit()%>%
+  mutate(value = as.numeric(value),
+         age = "2")
+
+cor_int_3 <- item_params_cor%>%
+  spread(parameter, mode)%>%
+  mutate(mode = int + slope)%>%
+  select(Chain, item, mode)%>%
+  spread(Chain, mode)%>%
+  ungroup()%>%
+  select(-item)%>%
+  correlate(method = "spearman")%>%
+  gather(key, value)%>%
+  filter(key !="rowname")%>%
+  na.omit()%>%
+  mutate(value = as.numeric(value),
+         age = "3")
+
+cor_int_4 <- item_params_cor%>%
+  spread(parameter, mode)%>%
+  mutate(mode = int + 2*slope)%>%
+  select(Chain, item, mode)%>%
+  spread(Chain, mode)%>%
+  ungroup()%>%
+  select(-item)%>%
+  correlate(method = "spearman")%>%
+  gather(key, value)%>%
+  filter(key !="rowname")%>%
+  na.omit()%>%
+  mutate(value = as.numeric(value),
+         age = "4")
+
+cor_int_5 <- item_params_cor%>%
+  spread(parameter, mode)%>%
+  mutate(mode = int + 3*slope)%>%
+  select(Chain, item, mode)%>%
+  spread(Chain, mode)%>%
+  ungroup()%>%
+  select(-item)%>%
+  correlate(method = "spearman")%>%
+  gather(key, value)%>%
+  filter(key !="rowname")%>%
+  na.omit()%>%
+  mutate(value = as.numeric(value),
+         age = "5")
+
+cor_hist <- 
+bind_rows(
+  cor_int_2,
+  cor_int_3,
+  cor_int_4,
+  cor_int_5
+)
+
+ggplot(cor_hist, aes(x = value, fill =age))+
+  geom_density(alpha = .5)+
+  xlim(-1,1)+
+  xlab("Correlation")+
+  theme_few()
+
+ggsave("../graphs/corr_int_by_age.pdf", width = 5, height = 4, scale = 1.5)
+
 ```
@@
          age = age + min(me_data$age_num))
+
+ tail(comb_model_data)
 ```

### 2019-08-21 stats/kids_basic_me.Rmd
add combination data

@@
 
-files <- dir("~/Work/Spin/raw_data/kids/basic_me/")
+# files <- dir("~/Work/Spin/raw_data/kids/basic_me/")
+# 
+# raw_data <- data_frame()
+# for (f in files) {
+#   jf <- paste("~/Work/Spin/raw_data/kids/basic_me/",f,sep="")
+#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+#   date <- str_sub(jf,44,str_length(jf)-11)
+#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+#   raw_data <- bind_rows(raw_data, id)
+# }
+# 
+# 
+# length(unique(raw_data$subid))
+#  
+# d_raw <-raw_data %>%
+#   mutate(subid = ifelse(subid == "190314_3", "190314_3_me",subid),
+#          subid = ifelse(subid == "190221_6_me", "190321_6_me",subid),
+#          subid = ifelse(subid == "192203_4_me", "190322_4_me",subid),
+#          subage = ifelse(subid == "190313_5_me", "3",subage),
+#          test_date = as.Date(test_date))
+# 
+# 
+# log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
+#   filter(Condition == "me")%>%
+#   mutate(dob = as.character(dob),
+#          dob = ifelse(subid == "190313_7_me", "2015-11-15",dob),
+#          dob = ifelse(subid == "190313_11_me", "2016-04-18",dob),
+#          dob = ifelse(subid == "190320_8_me", "2014-04-28",dob),
+#          dob = as.Date(dob))%>%
+#   select(subid,experimenter,keep_drop,sex,dob)
+# 
+#  
+# d_raw%>%
+#   group_by(subid)%>%
+#   summarise(n())%>%
+#   filter(!(subid %in% unique(log$subid)))
+# 
+#  
+# d <- left_join(d_raw,log, by = "subid")%>%
+#   filter(keep_drop == "keep")%>%
+#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+#          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+# 
+# write_csv(d, "../data/me.csv")
 
-raw_data <- data_frame()
-for (f in files) {
-  jf <- paste("~/Work/Spin/raw_data/kids/basic_me/",f,sep="")
-  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,44,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
-  raw_data <- bind_rows(raw_data, id)
-}
-
-length(unique(raw_data$subid))
-
-d_raw <-raw_data %>%
-  mutate(subid = ifelse(subid == "190314_3", "190314_3_me",subid),
-         subid = ifelse(subid == "190221_6_me", "190321_6_me",subid),
-         subid = ifelse(subid == "192203_4_me", "190322_4_me",subid),
-         subage = ifelse(subid == "190313_5_me", "3",subage),
-         test_date = as.Date(test_date))
-
-log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
-  filter(Condition == "me")%>%
-  mutate(dob = as.character(dob),
-         dob = ifelse(subid == "190313_7_me", "2015-11-15",dob),
-         dob = ifelse(subid == "190313_11_me", "2016-04-18",dob),
-         dob = ifelse(subid == "190320_8_me", "2014-04-28",dob),
-         dob = as.Date(dob))%>%
-  select(subid,experimenter,keep_drop,sex,dob)
-
-d_raw%>%
-  group_by(subid)%>%
-  summarise(n())%>%
-  filter(!(subid %in% unique(log$subid)))
-
-d <- left_join(d_raw,log, by = "subid")%>%
-  filter(keep_drop == "keep")%>%
-  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
-
-write_csv(d, "../data/child_basic_me.csv")
+d <- read_csv("../data/me.csv")%>%
+  mutate(subage = factor(subage))
 ```
@@
   geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5)+
+  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
   labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(~familiar)+
-  ggtitle("Data")+
+  #facet_grid(~familiar)+
+  #ggtitle("Data")+
   theme_few() +
@@
   scale_fill_viridis_d(name = "familiar object")
+
+ggsave("../graphs/me_by_item.png", width = 6, height = 3, scale = 1.2)
 ```

### 2019-08-21 stats/kids_combination.Rmd
add combination data

@@
 library(readxl)
+library(brms)
 
 ## importing data
-files <- dir("~/Work/Spin/raw_data/kids/combination/")
+# files <- dir("~/Work/Spin/raw_data/kids/combination/")
+# 
+# raw_data <- data_frame()
+# for (f in files) {
+#   jf <- paste("~/Work/Spin/raw_data/kids/combination/",f,sep="")
+#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+#   date <- str_sub(jf,56,str_length(jf)-11)
+#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+#   raw_data <- bind_rows(raw_data, id)
+# }
+# 
+# d_raw <- raw_data %>%
+#   mutate(discourseNovel = str_sub(discourseNovel,11),
+#          mutExNovel = str_sub(mutExNovel, 10),
+#          subid = ifelse(subid == "190726_6_come", "190726_6_com", subid))
+# 
+# d_raw %>%
+#   filter(subid == "190727_1_com")
+# 
+# 
+# log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
+#   filter(Condition == "com")%>%
+#   mutate(dob = as.character(dob),
+# #         dob = ifelse(subid == "190313_7_me", "2015-11-15",dob),
+#          dob = as.Date(dob))%>%
+#   select(subid,experimenter,keep_drop,sex,dob)
+# 
+#  
+# d_raw%>%
+#   group_by(subid)%>%
+#   summarise(n())%>%
+#   filter(!(subid %in% unique(log$subid)))
+# 
+#  
+# d <- left_join(d_raw,log, by = "subid")%>%
+#   filter(keep_drop == "keep")%>%
+#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+#          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+# 
+# 
+# write_csv(d, "../data/combination.csv")
 
-raw_data <- data_frame()
-for (f in files) {
-  jf <- paste("~/Work/Spin/raw_data/kids/combination/",f,sep="")
-  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,56,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
-  raw_data <- bind_rows(raw_data, id)
-}
-
-raw_data %>%
-  mutate(discourseNovel = str_sub(discourseNovel,11),
-         mutExNovel = str_sub(mutExNovel, 10))
+d <- read_csv("../data/combination.csv")%>%
+  mutate(subage = factor(subage))
 
 ```
+
+```{r}
+aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
+
+aoa_ratings <- aoa_ratings_all %>%
+  filter(Word %in% d$familiarObject )%>%
+  mutate(mean_aoa = as.numeric(Rating.Mean),
+         familiarObject = Word)%>%
+  select(familiarObject,mean_aoa)
+```
+
+```{r}
+d %>%
+  filter(condition != "train")%>%
+  group_by(condition,subage) %>%
+  summarise(n = length(unique(subid)),
+            data_points = n())
+```
+
+```{r plot by numerical age, echo = F}
+p2 <- d %>%
+  filter(condition != "train")%>%
+    left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiarObject = fct_reorder(factor(familiarObject), mean_aoa))
+
+ggplot(data = p2, aes(x = age_num, y = correct, col = familiarObject, fill = familiarObject)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  #facet_grid(condition~familiarObject)+
+  facet_grid(~condition)+
+  #ggtitle("Data")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d(name = "familiar object")+
+  scale_fill_viridis_d(name = "familiar object")
+```
+
+```{r plot by age, echo= FALSE}
+p1 <- d %>%
+  filter(condition != "train")%>%
+  group_by(subage, familiarObject,condition) %>%
+  multi_boot_standard(col = "correct")%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiarObject = fct_reorder(factor(familiarObject), mean_aoa))
+
+ggplot(data = p1, aes(x = familiarObject, y = mean, group=1, col = subage)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),size = .8)+
+  stat_summary(aes(group = subage, col = subage),fun.y=mean, geom="line")+
+  labs(x="",y="Proportion Correct")+
+  facet_grid(condition~.)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  scale_colour_solarized()
+```
+
+```{r}
+d_model <- d %>%
+  filter(condition != "train")%>%
+  left_join(aoa_ratings)%>%
+  mutate(age_num = age_num - mean(age_num),
+         aoa = mean_aoa- mean(mean_aoa))
+
+model <- brm(correct ~ familiarObject * age_num * condition,
+                    data = d_model, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 5000)
+
+summary(model)
+
+plot(model)
+
+```

### 2019-08-21 stats/kids_novelty.Rmd
add combination data

@@
 
-files <- dir("~/Work/Spin/raw_data/kids/novelty/")
+# files <- dir("~/Work/Spin/raw_data/kids/novelty/")
+# 
+# raw_data <- data_frame()
+# for (f in files) {
+#   jf <- paste("~/Work/Spin/raw_data/kids/novelty/",f,sep="")
+#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+#   date <- str_sub(jf,46,str_length(jf)-11)
+#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+#   raw_data <- bind_rows(raw_data, id)
+# }
+# 
+# 
+# length(unique(raw_data$subid))
+# 
+# d_raw <-raw_data %>%
+#   mutate(test_date = as.Date(test_date),
+#          subid = ifelse(subid =="190422_6_nov,","190422_6_nov",subid),
+#          subage = ifelse(subid =="190422_2_nov","4",subage))
+# 
+# 
+# log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
+#   filter(Condition == "nov")%>%
+#   mutate(dob = as.character(dob),
+#          dob = ifelse(subid =="190502_9_nov","2016-10-08",dob),
+#          dob = as.Date(dob))%>%
+#   select(subid,experimenter,keep_drop,sex,dob)
+# 
+# d_raw%>%
+#   group_by(subid)%>%
+#   summarise(n())%>%
+#   filter(!(subid %in% unique(log$subid)))
+# 
+#  
+# d_spin <- left_join(d_raw,log, by = "subid")%>%
+#   filter(keep_drop == "keep",
+#          trial != "train1", trial != "train2")%>%
+#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
+#          experiment = condition)%>%
+#   select(-pick_src)
+# 
+# 
+# ## import mcc data
+# 
+# files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")
+# 
+# raw_data_mcc <- data_frame()
+# for (f in files) {
+#   jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
+#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+#   date <- str_sub(jf,51,str_length(jf)-11)
+#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+#   raw_data_mcc <- bind_rows(raw_data_mcc, id)
+# }
+# 
+# d_raw_mcc <-raw_data_mcc %>%
+#   mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
+#          test_date = as.Date(test_date))
+# 
+# 
+# log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
+#   filter(Condition == "nov")%>%
+#   mutate(dob = as.numeric(dob),
+#          dob = as.Date(dob,origin = "1899-12-30"))%>%
+#   select(subid,experimenter,keep_drop,sex,dob)
+# 
+# 
+# d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
+#   filter(keep_drop == "keep")%>%
+#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
+#          leftObject = leftFruit,
+#          rightObject = rightFruit, 
+#          pick = str_sub(pick,72,str_length(pick)-4),
+#          agent = ifelse(speakerChange == "false", agent,altAgent),
+#          experiment = "dis_novelty_mcc")%>%
+#   filter(speakerChange == "false", trial != "train")%>%
+#   select(-speakerChange,-altAgent,-leftFruit,-rightFruit)
+# 
+# 
+# # join datasets
+# 
+# d <- bind_rows(d_spin, d_mcc)
+# 
+# write_csv(d_spin, "../data/novelty.csv")
+# #write_csv(d, "../data/child_novelty.csv")
 
-raw_data <- data_frame()
-for (f in files) {
-  jf <- paste("~/Work/Spin/raw_data/kids/novelty/",f,sep="")
-  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,46,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
-  raw_data <- bind_rows(raw_data, id)
-}
+d <- read_csv("../data/novelty.csv")%>%
+  mutate(subage = factor(subage))
 
-length(unique(raw_data$subid))
-
-d_raw <-raw_data %>%
-  mutate(test_date = as.Date(test_date),
-         subid = ifelse(subid =="190422_6_nov,","190422_6_nov",subid),
-         subage = ifelse(subid =="190422_2_nov","4",subage))
-
-log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
-  filter(Condition == "nov")%>%
-  mutate(dob = as.character(dob),
-         dob = ifelse(subid =="190502_9_nov","2016-10-08",dob),
-         dob = as.Date(dob))%>%
-  select(subid,experimenter,keep_drop,sex,dob)
-
-d_raw%>%
-  group_by(subid)%>%
-  summarise(n())%>%
-  filter(!(subid %in% unique(log$subid)))
-
-d_spin <- left_join(d_raw,log, by = "subid")%>%
-  filter(keep_drop == "keep",
-         trial != "train1", trial != "train2")%>%
-  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
-         experiment = condition)%>%
-  select(-pick_src)
-
-## import mcc data
-
-files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")
-
-raw_data_mcc <- data_frame()
-for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
-  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,51,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
-  raw_data_mcc <- bind_rows(raw_data_mcc, id)
-}
-
-d_raw_mcc <-raw_data_mcc %>%
-  mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
-         test_date = as.Date(test_date))
-
-log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
-  filter(Condition == "nov")%>%
-  mutate(dob = as.numeric(dob),
-         dob = as.Date(dob,origin = "1899-12-30"))%>%
-  select(subid,experimenter,keep_drop,sex,dob)
-
-d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
-  filter(keep_drop == "keep")%>%
-  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
-         leftObject = leftFruit,
-         rightObject = rightFruit, 
-         pick = str_sub(pick,72,str_length(pick)-4),
-         agent = ifelse(speakerChange == "false", agent,altAgent),
-         experiment = "dis_novelty_mcc")%>%
-  filter(speakerChange == "false", trial != "train")%>%
-  select(-speakerChange,-altAgent,-leftFruit,-rightFruit)
-
-# join datasets
-
-d <- bind_rows(d_spin, d_mcc)
-
-write_csv(d_spin, "../data/child_spin_novelty.csv")
-write_csv(d, "../data/child_novelty.csv")
 ```
@@
 ```{r sanity checks, echo = FALSE, warning = FALSE, message = FALSE}
-
-d <- read_csv("../data/child_novelty.csv")%>%
-  mutate(subage = factor(subage))
 
@@
   ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
+  guides(alpha = F, col = F)+ 
   #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
   scale_colour_solarized()
+
+ggsave("../graphs/novelty.png", width = 5, height = 3, scale = 1.2)
 ```

### 2019-08-21 stats/model.Rmd
update code

@@
 
-me_data <- read_csv("../data/child_basic_me.csv")
+me_data <- read_csv("../data/me.csv")
 
@@
 # 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
-sem_know_model <- readRDS("../saves/run_correlations.rds")#%>%
-  # filter(Chain != "15",
-  #        Chain != "1",
-  #        Chain != "30",
-  #        Chain != "6",
-  #        Chain != "5",
-  #        Chain != "7",
-  #        Chain != "3")
+sem_know_model <- readRDS("../saves/run_correlations.rds")%>%
+  filter(Chain != "15",
+         Chain != "1",
+         Chain != "30",
+         Chain != "6",
+         Chain != "5",
+         Chain != "7",
+         Chain != "3")
 
@@
 ```{r}
-me_model_data <- read_csv("../data/child_basic_me.csv")%>%
+me_model_data <- read_csv("../data/me.csv")%>%
     filter(trial != "train1",
@@
 
-ggsave("../graphs/so_by_chain.pdf", width = 4, height = 3, scale = 1.5)
+#ggsave("../graphs/so_by_chain.pdf", width = 4, height = 3, scale = 1.5)
 ```
@@
   gather(parameter, value, int, slope)
- # %>%
-#   filter(Chain != "15",
-#          Chain != "1",
-#          Chain != "30",
-#          Chain != "6",
-#          Chain != "5",
-#          Chain != "7",
-#          Chain != "3")
+
+sem_know_cor_params <- sem_know_cor_params%>%
+  filter(Chain != "15",
+         Chain != "1",
+         Chain != "30",
+         Chain != "6",
+         Chain != "5",
+         Chain != "7",
+         Chain != "3")
 
@@
 
-ggsave("../graphs/item_by_chain.pdf", width = 15, height = 15, scale = 1.5)
+#ggsave("../graphs/item_by_chain.pdf", width = 15, height = 15, scale = 1.5)
 ```
@@
 
-ggsave("../graphs/corr_int_by_age.pdf", width = 5, height = 4, scale = 1.5)
+#ggsave("../graphs/corr_int_by_age.pdf", width = 5, height = 4, scale = 1.5)
 
@@
   spread(parameter, mode)%>%
-  expand(item, int,slope,age = unique(me_model_data$age- min(me_model_data$age)))%>%
+  tidyr::expand(item, int,slope,age = unique(me_model_data$age- min(me_model_data$age)))%>%
   mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
@@
 ```{r}
-p2 <- read_csv("../data/child_basic_me.csv")%>%
+p2 <- read_csv("../data/me.csv")%>%
   filter(trial != "train1",
@@
 
-novel_data <- read_csv("../data/child_spin_novelty.csv")%>%
+novel_data <- read_csv("../data/novelty.csv")%>%
   mutate(age_num = age_num-min(age_num))

### 2019-08-22 stats/kids_combination.Rmd
modified model predictions

@@
   geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
   geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+

### 2019-08-22 stats/model.Rmd
modified model predictions

@@
   utterance.label == "novel_word" ? obj.shape == "novel_object" :
-utterance.label == "familiar_word" ? flip(sem_knowledge) ? obj.shape == "familiar_object" :  obj.shape == "novel_object" : 
+  utterance.label == "familiar_word" ? flip(sem_knowledge) ? 
+    obj.shape == "familiar_object" :  
+  flip() ? obj.shape == "familiar_object" : obj.shape == "novel_object" : 
   true
@@
   utterance.label == "novel_word" ? obj.shape == "familiar_object" :
-utterance.label == "familiar_word" ? flip(sem_knowledge) ? obj.shape == "familiar_object" :  obj.shape == "novel_object" : 
+  utterance.label == "familiar_word" ? flip(sem_knowledge) ? 
+    obj.shape == "familiar_object" : 
+  flip() ? obj.shape == "familiar_object" : obj.shape == "novel_object" : 
   true
@@
     var lexicon = lexiconObject[lexiconName];
-    var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
+    var obj = sample( Categorical({vs: all_objects, ps: [.5,.5]}));
     if ("label" in utterance) {
@@
   var speakerOptimalityParameters = {
-    intercept: uniformDrift({a: -2, b: 2, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 1, width: 0.5})
+    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
+    slope: uniformDrift({a: 0, b: 3, width: 0.5})
   }
@@
 
-sem_know_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-  data = list(data = me_model_data),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 10,
-  cores = 10,
-  inference_opts = list(method = "incrementalMH",
-                        samples = 4000,
-                        burn = 2000,
-                        verbose = T,
-                        lag = 1,
-                        verboseLag = 1000)
-)
-
-#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
-
-# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
-sem_know_model <- readRDS("../saves/run_correlations.rds")%>%
-  filter(Chain != "15",
-         Chain != "1",
-         Chain != "30",
-         Chain != "6",
-         Chain != "5",
-         Chain != "7",
-         Chain != "3")
+# sem_know_model<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+#   data = list(data = me_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 10,
+#   cores = 10,
+#   inference_opts = list(method = "incrementalMH",
+#                         samples = 4000,
+#                         burn = 2000,
+#                         verbose = T,
+#                         lag = 1,
+#                         verboseLag = 500)
+# )
+
+# load this for model parameters
+sem_know_model <- readRDS("../saves/sem_know_new_model.rds")#%>%
+
+# load this for model parameters with wider prior on so_slope
+#saveRDS(sem_know_model, "../saves/sem_know_new_model_2.rds")
 
@@
   theme_few()
+```
+
+```{r}
+#ggsave("../graphs/item_params_by_chain.pdf", width = 8, height = 3, scale = 1.5)
 ```
@@
 ```{r}
-me_model_data <- read_csv("../data/child_basic_me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(age = age_num - min(age_num))
-
-sem_know_run_summary <- item_params%>%
-  spread(parameter,value)%>%
-  group_by(Chain,item)%>%
-  summarise(overall_int = estimate_mode(int),
-            overall_slope = estimate_mode(slope))
-
-sem_know_run_iteration <- item_params%>%
-  spread(parameter,value)
-
-sem_know_chain <- sem_know_run_iteration %>%
-  left_join(sem_know_run_summary)
-
-chain_comp <- sem_know_chain %>%
-  left_join(expand.grid(
-      age = unique(me_model_data$age),
-      item = unique(me_model_data$familiar)), .) %>%
-  mutate(sem_know_ci = plogis(int + slope * age),
-         sem_know = plogis(overall_int + overall_slope * age)) %>%
-  group_by(Chain,item, age) %>%
-  summarise(sem_know = estimate_mode(sem_know), 
-            sem_know_uci = hdi_upper(sem_know_ci),
-            sem_know_lci = hdi_lower(sem_know_ci))
-
-ggplot(chain_comp, aes(x = age+2, y= sem_know, fill = factor(Chain)))+
-  geom_line(size = .3, aes(col = factor(Chain)))+
-  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .05)+
-  ylab("Semantic knowledge")+
-  xlab("Age")+
-  ylim(0,1)+
-  facet_wrap(~item, nrow = 3)+
-  theme_few()+
-  scale_colour_discrete()+
-  scale_fill_discrete()
-
-ggsave("../graphs/model_by_chain.pdf", width = 5, height = 4, scale = 1.5)
+# me_model_data <- read_csv("../data/me.csv")%>%
+#     filter(trial != "train1",
+#            trial != "train2")%>%
+#   mutate(age = age_num - min(age_num))
+# 
+# sem_know_run_summary <- item_params%>%
+#   spread(parameter,value)%>%
+#   group_by(Chain,item)%>%
+#   summarise(overall_int = estimate_mode(int),
+#             overall_slope = estimate_mode(slope))
+# 
+# 
+# sem_know_run_iteration <- item_params%>%
+#   spread(parameter,value)
+# 
+# sem_know_chain <- sem_know_run_iteration %>%
+#   left_join(sem_know_run_summary)
+# 
+# chain_comp <- sem_know_chain %>%
+#   left_join(expand.grid(
+#       age = unique(me_model_data$age),
+#       item = unique(me_model_data$familiar)), .) %>%
+#   mutate(sem_know_ci = plogis(int + slope * age),
+#          sem_know = plogis(overall_int + overall_slope * age)) %>%
+#   group_by(Chain,item, age) %>%
+#   summarise(sem_know = estimate_mode(sem_know), 
+#             sem_know_uci = hdi_upper(sem_know_ci),
+#             sem_know_lci = hdi_lower(sem_know_ci))
+# 
+# ggplot(chain_comp, aes(x = age+2, y= sem_know, fill = factor(Chain)))+
+#   geom_line(size = .3, aes(col = factor(Chain)))+
+#   geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .05)+
+#   ylab("Semantic knowledge")+
+#   xlab("Age")+
+#   ylim(0,1)+
+#   facet_wrap(~item, nrow = 3)+
+#   theme_few()+
+#   scale_colour_discrete()+
+#   scale_fill_discrete()
+
+#ggsave("../graphs/model_by_chain.pdf", width = 5, height = 4, scale = 1.5)
 ```
@@
 ```{r}
-me_model_data <- read_csv("../data/me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(age = age_num - min(age_num))
-
-so_run_iteration <- global_params%>%
-  spread(parameter, value)
-
-so_run_summary <- so_run_iteration%>%
-  group_by(Chain)%>%
-  summarise(overall_int = estimate_mode(int),
-            overall_slope = estimate_mode(slope))
-
-so_run <- so_run_iteration %>%
-  left_join(so_run_summary)
-
-so_run_comp <-so_run%>%
-  group_by(Chain,Iteration)%>%
-  expand(int,slope,overall_int,overall_slope,age = unique(me_model_data$age))%>%
-  mutate(so_ci = int + slope * age,
-         so = overall_int + overall_slope * age) %>%
-  group_by(Chain, age) %>%
-  summarise(so = estimate_mode(so), 
-            so_uci = hdi_upper(so_ci),
-            so_lci = hdi_lower(so_ci))
-
-ggplot(so_run_comp, aes(x = age+2, y= so, fill = factor(Chain)))+
-  geom_line(size = .4, aes(col = factor(Chain)))+
-  geom_ribbon(aes(ymin=so_lci, ymax = so_uci), alpha = .05)+
-  ylab("speaker optimality")+
-  xlab("Age")+
-  #facet_grid(~run)+
-  theme_few()+
-  scale_colour_discrete()+
-  scale_fill_discrete()
-
-#ggsave("../graphs/so_by_chain.pdf", width = 4, height = 3, scale = 1.5)
+# me_model_data <- read_csv("../data/me.csv")%>%
+#     filter(trial != "train1",
+#            trial != "train2")%>%
+#   mutate(age = age_num - min(age_num))
+# 
+# so_run_iteration <- global_params%>%
+#   spread(parameter, value)
+# 
+# so_run_summary <- so_run_iteration%>%
+#   group_by(Chain)%>%
+#   summarise(overall_int = estimate_mode(int),
+#             overall_slope = estimate_mode(slope))
+# 
+# so_run <- so_run_iteration %>%
+#   left_join(so_run_summary)
+# 
+# so_run_comp <-so_run%>%
+#   group_by(Chain,Iteration)%>%
+#   tidyr::expand(int,slope,overall_int,overall_slope,age = unique(me_model_data$age))%>%
+#   mutate(so_ci = int + slope * age,
+#          so = overall_int + overall_slope * age) %>%
+#   group_by(Chain, age) %>%
+#   summarise(so = estimate_mode(so), 
+#             so_uci = hdi_upper(so_ci),
+#             so_lci = hdi_lower(so_ci))
+# 
+# ggplot(so_run_comp, aes(x = age+2, y= so, fill = factor(Chain)))+
+#   geom_line(size = .4, aes(col = factor(Chain)))+
+#   geom_ribbon(aes(ymin=so_lci, ymax = so_uci), alpha = .05)+
+#   ylab("speaker optimality")+
+#   xlab("Age")+
+#   #facet_grid(~run)+
+#   theme_few()+
+#   scale_colour_discrete()+
+#   scale_fill_discrete()
+# 
+# ggsave("../graphs/so_by_chain.pdf", width = 4, height = 3, scale = 1.5)
 ```
@@
 
-sem_know_cor_params  <- readRDS("../saves/run_correlations.rds")%>%
-  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
-  filter(parameter == "parameter", type == "items")%>%
-  separate(value, into = c("int", "slope"),sep = ", ")%>%
-  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]")))%>%
-  gather(parameter, value, int, slope)
-
-sem_know_cor_params <- sem_know_cor_params%>%
-  filter(Chain != "15",
-         Chain != "1",
-         Chain != "30",
-         Chain != "6",
-         Chain != "5",
-         Chain != "7",
-         Chain != "3")
-
-```
-
-```{r}
-ggplot(sem_know_cor_params%>%filter(parameter == "int"), aes(x = value))+
+# sem_know_cor_params  <- readRDS("../saves/run_correlations.rds")%>%
+#   separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
+#   filter(parameter == "parameter", type == "items")%>%
+#   separate(value, into = c("int", "slope"),sep = ", ")%>%
+#   mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+#          slope = as.numeric(str_remove(slope, "[)]")))%>%
+#   gather(parameter, value, int, slope)
+# 
+# 
+# sem_know_cor_params <- sem_know_cor_params%>%
+#   filter(Chain != "15",
+#          Chain != "1",
+#          Chain != "30",
+#          Chain != "6",
+#          Chain != "5",
+#          Chain != "7",
+#          Chain != "3")
+
+```
+
+```{r}
+ggplot(item_params%>%filter(parameter == "int"), aes(x = value))+
   geom_density(alpha = 0.3)+
@@
 ```{r}
-item_params_cor <- sem_know_cor_params %>%
+item_params_cor <- item_params %>%
   group_by(Chain,item, parameter)%>%
@@
 ```{r}
-me_data <- read_csv("../data/child_basic_me.csv")%>%
+me_data <- read_csv("../data/me.csv")%>%
     filter(trial != "train1",
@@
 
-age_me_effect <- as_tibble(ranef$familiar, rownames = "familiar")%>%
+age_me_effect <- as_data_frame(ranef$familiar, rownames = "familiar")%>%
   mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
@@
   group_by(familiar) %>%
-  expand(Estimate.Intercept,Estimate.z_age,grand_intercept,grand_slope,z_age = me_data$age_num - mean(me_data$age_num), mean_age = mean(me_data$age_num))%>%
+  tidyr::expand(Estimate.Intercept,Estimate.z_age,grand_intercept,grand_slope,z_age = me_data$age_num - mean(me_data$age_num), mean_age = mean(me_data$age_num))%>%
   mutate(me_effect = plogis(grand_intercept + Estimate.Intercept+(Estimate.z_age+grand_slope)*z_age), 
@@
   mutate(item = fct_reorder(factor(item), mean_aoa),
-         age = age + min(me_data$age_num))
+         age = age + min(me_data$age_num),
+         source = "Model")
 
@@
 ```{r}
-ggplot(comb_model_predictions, aes(x=age,y = me_effect, col = item))+
+p_comb_model <- ggplot(comb_model_predictions, aes(x=age,y = me_effect, col = item))+
   geom_hline(yintercept = 0.5, lty=2)+
@@
 
+```{r}
+
+data_comb <- read_csv("../data/combination.csv") %>%
+  filter(condition != "train")%>%
+  mutate(alignment = condition,
+         item = familiarObject)%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(familiarObject), mean_aoa), 
+         source = "Data")
+
+p_comb_data <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = item, fill = item)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
+  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(~alignment)+
+  ggtitle("Combination Data")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d()+
+  scale_fill_viridis_d()
+```
+
+```{r}
+ggarrange(p_comb_model,p_comb_data, common.legend = T, legend = "right", nrow = 2, ncol = 1)
+```
+
+```{r}
+#ggsave("../graphs/combination_model_data.pdf", width = 7, height = 7, scale = 1)
+```
+
+```{r}
+ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
+  geom_smooth(method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source), size = 1)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  #facet_grid(condition~familiarObject)+
+  facet_grid(alignment~item)+
+  #ggtitle("Combination Data")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+```
+
+```{r}
+#ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 2, scale = 1.5)
+```
+
+```{r}
+binnned_data <- data_comb%>%
+  group_by(subage, alignment, item)%>%
+  summarize(k = sum(correct), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         data_mean = (a-1)/(a+b-2),
+         data_ci_lower  = qbeta(.025, a, b),
+         data_ci_upper = qbeta(.975, a, b),
+         subage = factor(subage))%>%
+  select(-a,-b,-n,-k)
+
+binned_model <- comb_model_predictions %>%
+  mutate(subage = cut(age, 
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(subage, alignment, item)%>%
+  summarise(model_mean = estimate_mode(me_effect),
+            model_ci_lower = hdi_lower(me_effect),
+            model_ci_upper = hdi_upper(me_effect))
+
+cor_plot <- left_join(
+  binnned_data,
+  binned_model)
+
+ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
+  geom_point(size = 2,  stroke = 1)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  #ggtitle("3-year-olds")+
+  facet_grid(~subage)+
+  theme_few() + 
+  scale_colour_viridis_d(name ="Item")
+```
+
+```{r}
+#ggsave("../graphs/combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
+```
+
 #### WORK IN PROGRESS: nesting within participant

### 2019-08-25 stats/model.Rmd
add third model run

@@
     intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 3, width: 0.5})
+    slope: uniformDrift({a: 0, b: 2, width: 0.5})
   }
@@
 # load this for model parameters
-sem_know_model <- readRDS("../saves/sem_know_new_model.rds")#%>%
-
-# load this for model parameters with wider prior on so_slope
-#saveRDS(sem_know_model, "../saves/sem_know_new_model_2.rds")
+sem_know_model <- readRDS("../saves/sem_know_new_model.rds")
+
+# load this for model parameters with wider prior on so_slope (0:3)
+#sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")
+
+# load this for model parameters with even wider prior on so_slope (0:4)
+#sem_know_model <- readRDS("../saves/sem_know_new_model_3.rds")
+
+#saveRDS(sem_know_model, "../saves/sem_know_new_model_3.rds")
 

### 2019-08-25 stats/model.Rmd
add third model run

@@
 
-# load this for model parameters with wider prior on so_slope (0:3)
-#sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")
-
-# load this for model parameters with even wider prior on so_slope (0:4)
-#sem_know_model <- readRDS("../saves/sem_know_new_model_3.rds")
+# # load this for model parameters with wider prior on so_slope (0:3)
+# sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")
+# 
+# # load this for model parameters with even wider prior on so_slope (0:4)
+# sem_know_model <- readRDS("../saves/sem_know_new_model_3.rds")
 
@@
 
-summary(novel_bm)
+#summary(novel_bm)
 
@@
 )
-# 
-# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
-# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
-# 
+
 comb_model_predictions <- comb_model_pred %>%
@@
 
- tail(comb_model_data)
 ```
@@
 ```{r}
-ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source)) +
+ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
   geom_hline(yintercept = 0.5, lty=2)+
@@
   #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
-  geom_smooth(method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source), size = 1)+
+  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
+  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
   labs(x="Age",y="Mutual Exclusivity effect")+
   #facet_grid(condition~familiarObject)+
-  facet_grid(alignment~item)+
+  facet_grid(~item)+
   #ggtitle("Combination Data")+
@@
 ```{r}
-#ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 2, scale = 1.5)
+ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 3, scale = 1.5)
 ```

### 2019-08-27 stats/model.Rmd
add 2 more model runs

@@
 
-# sem_know_model<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-#   data = list(data = me_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 10,
-#   cores = 10,
-#   inference_opts = list(method = "incrementalMH",
-#                         samples = 4000,
-#                         burn = 2000,
-#                         verbose = T,
-#                         lag = 1,
-#                         verboseLag = 500)
-# )
-
-# load this for model parameters
-sem_know_model <- readRDS("../saves/sem_know_new_model.rds")
+sem_know_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
+  data = list(data = me_model_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 10,
+  cores = 10,
+  inference_opts = list(method = "incrementalMH",
+                        samples = 4000,
+                        burn = 2000,
+                        verbose = T,
+                        lag = 1,
+                        verboseLag = 500)
+)
+
+# load this for model parameters with so_slope (0:2)
+#sem_know_model <- readRDS("../saves/sem_know_new_model.rds")
 
@@
 # sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")
-# 
+
+# # load this for model parameters with wider prior on so_slope (0:3) (second run)
+# sem_know_model <- readRDS("../saves/sem_know_new_model_2_2.rds")%>%
+#   filter(Chain != 2)
+
 # # load this for model parameters with even wider prior on so_slope (0:4)
@@
 
-#saveRDS(sem_know_model, "../saves/sem_know_new_model_3.rds")
+# # load this for model parameters with wider prior on so_slope (0:4), so_int, as well as on global paramters of semantic knowledge
+sem_know_model <- readRDS("../saves/sem_know_new_model_4.rds")%>%
+  filter(Chain !=9)
+
+#saveRDS(sem_know_model, "../saves/sem_know_new_model_4.rds")
 

### 2019-08-28 stats/kids_basic_me.Rmd
fix reference to datafiles

@@
 # import data
-d <- read_csv("../data/child_basic_me.csv")%>%
+d <- read_csv("../data/me.csv")%>%
   mutate(subage = factor(subage))
@@
   ggtitle("Model")+
-  labs(x="Age",y="Proportion correct")+
+  labs(x="Age",y="Mutual Exclusivity effect")+
   theme_few() +

### 2019-08-28 stats/kids_combination.Rmd
fix reference to datafiles

@@
             data_points = n())
+
+#length(unique(d$subid))
 ```
@@
 
-model <- brm(correct ~ familiarObject * age_num * condition,
+model <- brm(correct ~ familiarObject * age_num * condition + (condition|subid),
                     data = d_model, family = bernoulli(),
-          control = list(adapt_delta = 0.95),
+          control = list(adapt_delta = 0.99),
           sample_prior = F,
           save_all_pars = TRUE,
-          iter = 5000)
+          iter = 8000)
 
@@
 
-plot(model)
-
 ```

### 2019-08-28 stats/model.Rmd
new model with subject intercepts

@@
         }),
-        slope: gaussianDrift({
+        slope: Math.pow(gaussianDrift({
           mu: globalLineParameters.slope, 
@@
           width: 0.5
-        })
+        }), 2)
       }
@@
 # load this for model parameters with so_slope (0:2)
-#sem_know_model <- readRDS("../saves/sem_know_new_model.rds")
+sem_know_model <- readRDS("../saves/sem_know_new_model.rds")
 
@@
 
+subj | item | response
+1    |  A  |   1
+1    |  B  |   1
+2    |  A  |   1
+2    |  B  |   0
+
+```{js}
+
+var sampleItemParameters = function() { 
+  return {
+      intercept: gaussianDrift({
+        mu: globalLineParameters.intercept, 
+        sigma: itemVariability.intercept, 
+        width: 0.5
+      }),
+      slope: Math.pow(gaussianDrift({
+        mu: globalLineParameters.slope, 
+        sigma: itemVariability.slope, 
+        width: 0.5
+      }), 2)
+    }   
+}
+
+// want something that favors smaller values
+var subject_sigma = uniform(0, 1)
+
+var sampleLinguisticCompetence = function(age){
+  return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.5 })
+}
+
+// [ carrot, duck, bread, ...]  (slope and intercept)
+var all_item_parameters = repeat(n_items, sampleItemParameters)
+// [s1, s2, s3, ...] (intercept)
+var all_subject_parameters = map(sampleLinguisticCompetence, subjects)
+
+var sem_knowledge = logistic(item.intercept +  item.slope * linguistic_competence)
+```
+
 ```{r work in progress}
-semStr <- '
+sem_subj_str <- '
 var data = dataFromR.data
@@
 var familiars = levels(data, "familiar")
+var subjects = levels(data, "subid")
 
@@
 
-  // global parameters
-  var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
-  var so_int = uniformDrift({a: -2, b: 2, width: 0.2})
-
-  var sem_slope_global = uniformDrift({a: -2, b: 2, width: 0.2})
-  var sem_int_global = uniformDrift({a: 0, b: 5, width: 0.2})
-
-  var item_slope_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
-  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})
-
-  var participant_age_adjust = gaussianDrift({mu: 0, sigma: 1, width: 0.2})
-
-  var sem_slope_item = repeat(familiars.length, function(){
-    gaussianDrift({mu: sem_slope_global, sigma: item_slope_sigma, width: 0.5} )
-  })
-
-  var sem_int_item = gaussianDrift({mu: sem_int_global, 
-        sigma: item_int_sigma, width: 0.5})
-
-  foreach(function(cndtn){
-
-    var conditionData = _.filter(data, {familiar: cndtn})
-
+  var speakerOptimalityParameters = {
+    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
+    slope: uniformDrift({a: 0, b: 2, width: 0.5})
+  }
+
+  var globalLineParameters = {
+    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
+    slope: uniformDrift({a: 0, b: 2, width: 0.5})
+  }
+
+  var itemVariability = {
+    intercept: uniformDrift({a: 0, b: 1, width: 0.2}),
+    slope: uniformDrift({a: 0, b: 1, width: 0.2})
+  }
+
+  // conceptually it might not make sense to have two sigmas, but maybe it does
+  // intercept sigma probably will be smaller than slope sigma
+  // var item_int_sigma = uniformDrift({a: 0, b: 3, width: 0.2})
+
+  var sampleItemParameters = function(itemName) { 
+    return [itemName, {
+        intercept: gaussianDrift({
+          mu: globalLineParameters.intercept, 
+          sigma: itemVariability.intercept, 
+          width: 0.5
+        }),
+        slope: Math.pow(gaussianDrift({
+          mu: globalLineParameters.slope, 
+          sigma: itemVariability.slope, 
+          width: 0.5
+        }), 2)
+      }]
+  }
+
+  // {papaya: {int, slope}, bread: {int, slope}, ... }
+  var all_item_parameters = _.fromPairs(map(sampleItemParameters, familiars))
+
+  // want something that favors smaller values
+  var subject_sigma = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var sampleLinguisticCompetence = function(age){
+    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
+  }
+
+  foreach(function(subid){
+      var subjectData = _.filter(data, {subid: subid})
+      var subj_age = subjectData[0].age
+      var subj_linguistic_competence = sampleLinguisticCompetence(subj_age)
+
+      // question: should we use age here instead of the random intercept? or a different random intercept?
+      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_linguistic_competence
+
+      // each row is a different item
       foreach(function(row){
 
-      var age = row.age
-
-      var sem_knowledge = logistic(sem_int_item + sem_slope_item * age)
-
-      var speakerOptimality = so_int  + so_slope * age
+        var itemLineParameters = all_item_parameters[row.familiar]
+
+        var sem_knowledge = logistic(itemLineParameters.intercept + 
+            itemLineParameters.slope * subj_linguistic_competence)
 
@@
 
-      query.add(["modelPrediction", cndtn], [age, Math.exp(modelPredictions.score(1))])
-
-    }, conditionData)
-
-    query.add(["parameter", cndtn], [sem_int_item, sem_slope_item])
-
+        // if you want to save predictions, make sure to record subid because these predictions are for this particular subid
+        // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
+
+      }, subjectData)
+
+    // comment out to save memory
+    query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])
+
+  }, subjects)
+
+  foreach(function(item){
+    var itemLineParameters = all_item_parameters[item]
+    query.add(["parameter","items", item], [itemLineParameters.intercept, itemLineParameters.slope])
   }, familiars)
 
-  query.add(["parameter", "speaker_optimality"], [so_int, so_slope])
-  query.add(["parameter", "global_sem"], [sem_int_global, sem_slope_global])
-  query.add(["parameter", "global_sem_sigmas"], [item_int_sigma, item_slope_sigma])
+  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
+  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
+  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
+  query.add(["parameter","sigma", "global_subject_sigmas"], ["NA", subject_sigma])
 
@@
 ```
+
+```{r}
+me_model_data <- read_csv("../data/me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
+
+sem_know_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
+  data = list(data = me_model_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 1,
+  cores = 1,
+  inference_opts = list(method = "incrementalMH",
+                        samples = 5,
+                        burn = 1,
+                        verbose = T,
+                        lag = 1,
+                        verboseLag = 1)
+)
+
+```

### 2019-08-30 stats/kids_basic_me.Rmd
add model runs with random intercept for individuals

@@
 aoa_ratings <- aoa_ratings_all %>%
-  filter(Word %in% d_raw$familiar )%>%
+  filter(Word %in% d$familiar )%>%
   mutate(mean_aoa = as.numeric(Rating.Mean),
@@
   geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
+  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
+  geom_smooth(method = "loess", se = F, alpha = .5)+
   labs(x="Age",y="Mutual Exclusivity effect")+

### 2019-08-30 stats/model.Rmd
add model runs with random intercept for individuals

@@
     intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 2, width: 0.5})
+    slope: uniformDrift({a: 0, b: 4, width: 0.5})
   }
@@
   var itemVariability = {
-    intercept: uniformDrift({a: 0, b: 1, width: 0.2}),
+    intercept: uniformDrift({a: 0, b: 2, width: 0.2}),
     slope: uniformDrift({a: 0, b: 1, width: 0.2})
@@
         }),
-        slope: Math.pow(gaussianDrift({
+        slope: gaussianDrift({
           mu: globalLineParameters.slope, 
@@
           width: 0.5
-        }), 2)
+        })
       }
@@
   model_var = "model",
-  chains = 10,
-  cores = 10,
+  chains = 4,
+  cores = 4,
   inference_opts = list(method = "incrementalMH",
@@
                         lag = 1,
-                        verboseLag = 500)
+                        verboseLag = 1000)
 )
 
+```
+
+# Model runs
+
+```{r}
 # load this for model parameters with so_slope (0:2)
-sem_know_model <- readRDS("../saves/sem_know_new_model.rds")
-
-# # load this for model parameters with wider prior on so_slope (0:3)
-# sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")
-
-# # load this for model parameters with wider prior on so_slope (0:3) (second run)
-# sem_know_model <- readRDS("../saves/sem_know_new_model_2_2.rds")%>%
-#   filter(Chain != 2)
-
-# # load this for model parameters with even wider prior on so_slope (0:4)
-# sem_know_model <- readRDS("../saves/sem_know_new_model_3.rds")
-
-# # load this for model parameters with wider prior on so_slope (0:4), so_int, as well as on global paramters of semantic knowledge
-sem_know_model <- readRDS("../saves/sem_know_new_model_4.rds")%>%
-  filter(Chain !=9)
-
-#saveRDS(sem_know_model, "../saves/sem_know_new_model_4.rds")
+#sem_know_model <- readRDS("../saves/sem_know_new_model.rds")
+
+# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int
+#sem_know_model <- readRDS("../saves/sem_know_model_wide_sig.rds")
+
+# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int and forced positive slope for semantic knowledge
+#sem_know_model <- readRDS("../saves/sem_know_model_pos_slope.rds")
+
+# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int and with random intercepts for subjects
+#sem_know_model <- readRDS("../saves/sem_know_model_wide_sig_ind.rds")
+
+# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int, forced positive slope for semantic knowledge and with random intercepts for subjects
+sem_know_model <- readRDS("../saves/sem_know_model_wide_sig_pos_slope_ind.rds")
+
+#saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_ind.rds")
 
@@
   separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
-  filter(parameter == "parameter", type == "sigma")%>%
+  filter(parameter == "parameter", type == "sigma", token != "global_subject_sigmas")%>%
     separate(value, into = c("sigma_int", "sigma_slope"),sep = ", ")%>%
@@
     gather(parameter, value, sigma_int, sigma_slope)
+
+subj_sigma<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
+  filter(parameter == "parameter", token == "global_subject_sigmas")%>%
+  separate(value, into = c("na", "sigma"),sep = ", ")%>%
+  select(-na)%>%
+  mutate(sigma = as.numeric(str_remove(sigma, "[)]")))
+
+subject_params<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type","id"), sep = ",")%>%
+  filter(parameter == "parameter", type == "subj_intercept")%>%
+  separate(value, into = c("na", "int"),sep = ", ")%>%
+  select(-na)%>%
+  mutate(int = as.numeric(str_remove(int, "[)]")))
 
@@
 ```{r}
-ggplot(item_params, aes(x = value, fill = factor(Chain)))+
+plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(Chain)))+
   geom_density(alpha = 0.3)+
@@
   theme_few()
+
+plot_item_params
 ```
@@
 
-ggplot(global_params, aes(x = value, fill = factor(Chain)))+
+plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(Chain)))+
   geom_density(alpha = 0.3)+
@@
   theme_few()
-```
-
-```{r}
-ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
+
+plot_global_params
+```
+```{r}
+plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
   geom_density(alpha = 0.3)+
@@
   theme_few()
+
+plot_global_sigma
+```
+
+```{r}
+plotg_subj_sigma <- ggplot(subj_sigma, aes(x = sigma, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Subject Sigma")+
+  theme_few()
+
+plotg_subj_sigma
+```
+
+```{r}
+
+select_id <- me_model_data %>%
+  filter(age < 1.3,
+         age >1)%>%
+  group_by(age,subid)%>%
+  summarise(mean = mean(correct))%>%
+  mutate(id = subid)
+
+subject_params <- subject_params %>%
+  left_join(select_id)%>%
+  filter(mean != "NA")%>%
+  ungroup()
+
+ggplot(subject_params, aes(x = int, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  geom_vline(aes(xintercept = age), size = 1.5)+
+  #geom_vline(aes(xintercept = mean), size = 1.5, col = "red")+
+  facet_grid(id+ round(mean,2)~.)+
+  xlab("Subject Intercept")+
+  theme_few()
+
+ggsave("../graphs/subj_intercept.pdf", width = 5, height = 8, scale = 1.5)
+
 ```
@@
 ```
-
+# Correlate model predictions and data 
 ```{r}
@@
 
-ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
+cor_plot_age <- ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
@@
   ylab("Data")+
-  #ggtitle("3-year-olds")+
   facet_grid(~subage)+
@@
 #ggsave("../graphs/combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
+```
+
+```{r}
+ggarrange(
+plot_item_params,plotg_subj_sigma,
+plot_global_params,plot_subject_params,
+cor_plot_age, plot_global_sigma,
+ncol = 2, nrow = 3, common.legend = T, widths = c(1.7,1))
+
+ggsave("../graphs/overview_wide_slope_wide_sigma_pos_slope_ind.png", width = 12, height = 10, scale = 1.2)
+
 ```
@@
   model_var = "model",
-  chains = 1,
-  cores = 1,
+  chains = 8,
+  cores = 8,
   inference_opts = list(method = "incrementalMH",
-                        samples = 5,
-                        burn = 1,
+                        samples = 4000,
+                        burn = 2000,
                         verbose = T,
                         lag = 1,
-                        verboseLag = 1)
+                        verboseLag = 1000)
 )
 
-```
+saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_pos_slope_ind.rds")
+
+```

### 2019-09-04 stats/model.Rmd
record full distribution of predictions; change sopt to be a function of age rather than random intercept

@@
 
+     // display("age = " + subj_age + " ... intercept = " + subj_linguistic_competence)
+
       // question: should we use age here instead of the random intercept? or a different random intercept?
-      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_linguistic_competence
+      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * age
 
@@
   }, subjects)
+
+  foreach(function(row){
+      var prior = [row.prior, 1-row.prior]
+      foreach(function(item){
+        var itemLineParameters = all_item_parameters[item]
+        var sem_knowledge = logistic(itemLineParameters.intercept + 
+            itemLineParameters.slope * row.age)
+        var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age
+
+        var modelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)
+        query.add(["prediction", item, row.age], [row.alignment, Math.exp(modelPredictions.score(1))])
+
+      }, familiars)
+   }, dataFromR.comb_data)
 
@@
 ```{r}
+
+novel_bm <- readRDS("../saves/novelty_model.rds")
+
+#summary(novel_bm)
+
+novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
+  select(term,Estimate)%>%
+  spread(term, Estimate)
+
 me_model_data <- read_csv("../data/me.csv")%>%
@@
            trial != "train2")%>%
-  mutate(age = age_num - min(age_num))
+  mutate(age = age_num - min(age_num),
+         nov_int = novel_params$Intercept,
+         nov_slope = novel_params$age_num,
+         prior = plogis(nov_int + age * nov_slope))
+
+comb_model_data <- bind_rows(
+  me_model_data %>%
+    distinct(age, prior) %>%
+    mutate(alignment = "congruent"),
+  me_model_data %>%
+    distinct(age, prior) %>%
+    mutate(prior = 1 - prior, 
+         alignment = "incongruent")
+)
 
@@
   program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
-  data = list(data = me_model_data),
+  data = list(data = me_model_data, comb_data = comb_model_data),
   data_var = "dataFromR",
   model_var = "model",
-  chains = 8,
-  cores = 8,
+  chains = 1,
+  cores = 1,
   inference_opts = list(method = "incrementalMH",
-                        samples = 4000,
-                        burn = 2000,
+                        samples = 1,
+                        burn = 1,
                         verbose = T,
                         lag = 1,
-                        verboseLag = 1000)
+                        verboseLag = 10)
 )
 
-saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_pos_slope_ind.rds")
-
-```
+# saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_pos_slope_ind.rds")
+
+```
+
+```{r}
+# novelty data
+
+novel_data <- read_csv("../data/novelty.csv")%>%
+  mutate(age_num = age_num-min(age_num))
+
+# novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
+#           data = novel_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.95),
+#           sample_prior = F,
+#           save_all_pars = F,
+#           iter = 10000)
+# 
+# saveRDS(novel_bm, "../saves/novelty_model.rds")
+
+comb_model_data_incon <- inv_model_data %>%
+  mutate(nov_int = novel_params$Intercept,
+         nov_slope = novel_params$age_num,
+         prior = 1- plogis(nov_int + age * nov_slope),
+         alignment = "incongruent")
+
+comb_model_data <- bind_rows(
+  comb_model_data_con,
+  comb_model_data_incon)
+```

### 2019-09-04 stats/model.Rmd
update model

@@
 
+# Summarizing parameters
+
 ```{r}
@@
 
+model_pred<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "item","age"), sep = ",")%>%
+  filter(parameter == "prediction")%>%
+  separate(value, into = c("alignment", "me_effect"),sep = ", ")%>%
+  mutate(age = as.numeric(age),
+         me_effect =str_remove(me_effect,"[)]"),
+         me_effect =str_remove(me_effect,'"'),
+         me_effect =as.numeric(str_remove(me_effect,'"')),
+         alignment = str_remove(alignment,'c[(]'),
+         alignment =str_remove(alignment,'"'),
+         alignment =str_remove(alignment,'"'))
+
 #### summaries
@@
 ```
+
 ```{r}
@@
 
-to do:
-- bookkeeping: index correct participant/item variables at relevant part of code
-- inference: try HMC, variational
-
-subj | item | response
-1    |  A  |   1
-1    |  B  |   1
-2    |  A  |   1
-2    |  B  |   0
-
-```{js}
-
-var sampleItemParameters = function() { 
-  return {
-      intercept: gaussianDrift({
-        mu: globalLineParameters.intercept, 
-        sigma: itemVariability.intercept, 
-        width: 0.5
-      }),
-      slope: Math.pow(gaussianDrift({
-        mu: globalLineParameters.slope, 
-        sigma: itemVariability.slope, 
-        width: 0.5
-      }), 2)
-    }   
-}
-
-// want something that favors smaller values
-var subject_sigma = uniform(0, 1)
-
-var sampleLinguisticCompetence = function(age){
-  return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.5 })
-}
-
-// [ carrot, duck, bread, ...]  (slope and intercept)
-var all_item_parameters = repeat(n_items, sampleItemParameters)
-// [s1, s2, s3, ...] (intercept)
-var all_subject_parameters = map(sampleLinguisticCompetence, subjects)
-
-var sem_knowledge = logistic(item.intercept +  item.slope * linguistic_competence)
-```
-
 ```{r work in progress}
@@
       // question: should we use age here instead of the random intercept? or a different random intercept?
-      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * age
+
+  var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_age
 
@@
         var modelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)
+
+display(row.alignment)
+
         query.add(["prediction", item, row.age], [row.alignment, Math.exp(modelPredictions.score(1))])
@@
   inference_opts = list(method = "incrementalMH",
-                        samples = 1,
+                        samples = 10,
                         burn = 1,
@@
                         lag = 1,
-                        verboseLag = 10)
+                        verboseLag = 1000)
 )
 
-# saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_pos_slope_ind.rds")
-
-```
-
-```{r}
-# novelty data
-
-novel_data <- read_csv("../data/novelty.csv")%>%
-  mutate(age_num = age_num-min(age_num))
-
-# novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
-#           data = novel_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.95),
-#           sample_prior = F,
-#           save_all_pars = F,
-#           iter = 10000)
-# 
-# saveRDS(novel_bm, "../saves/novelty_model.rds")
-
-comb_model_data_incon <- inv_model_data %>%
-  mutate(nov_int = novel_params$Intercept,
-         nov_slope = novel_params$age_num,
-         prior = 1- plogis(nov_int + age * nov_slope),
-         alignment = "incongruent")
-
-comb_model_data <- bind_rows(
-  comb_model_data_con,
-  comb_model_data_incon)
-```
+# run variants
+# start with variant 3
+# 3 cores, 3 chains 
+# see how long it takes and then run over night
+
+# saveRDS(sem_know_model, "../saves/sem_know_model_save pred.rds")
+
+```
+
+#### plotting predictions
+
+```{r}
+comb_model_pred_agg <- model_pred%>%
+  group_by(alignment,item,age)%>%
+  summarise(mean = estimate_mode(me_effect),
+            uci = hdi_upper(me_effect),
+            lci = hdi_lower(me_effect))%>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         age = age + min(me_data$age_num))
+
+ggplot(comb_model_pred_agg, aes(x=age,y = mean, col = item))+
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(size = 1)+
+  ggtitle("Combination Model Predictions")+
+  labs(x="Age",y="Proportion correct")+
+  facet_grid(~alignment)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d()
+
+```

### 2019-09-06 stats/model.Rmd
add model runs

@@
 ```{r}
-# load this for model parameters with so_slope (0:2)
-#sem_know_model <- readRDS("../saves/sem_know_new_model.rds")
-
-# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int
-#sem_know_model <- readRDS("../saves/sem_know_model_wide_sig.rds")
-
-# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int and forced positive slope for semantic knowledge
-#sem_know_model <- readRDS("../saves/sem_know_model_pos_slope.rds")
-
-# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int and with random intercepts for subjects
-#sem_know_model <- readRDS("../saves/sem_know_model_wide_sig_ind.rds")
-
-# load this for model parameters with wider so_slope (0:4) and wider sigma on sem_int, forced positive slope for semantic knowledge and with random intercepts for subjects
-sem_know_model <- readRDS("../saves/sem_know_model_wide_sig_pos_slope_ind.rds")
+
+sem_know_model <- readRDS("../saves/sem_know_model_variant3_50k.rds")
 
@@
 model_pred<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "item","age"), sep = ",")%>%
+  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
   filter(parameter == "prediction")%>%
-  separate(value, into = c("alignment", "me_effect"),sep = ", ")%>%
+  separate(value, into = c("na", "me_effect"),sep = ",")%>%
+  select(-na)%>%
   mutate(age = as.numeric(age),
-         me_effect =str_remove(me_effect,"[)]"),
-         me_effect =str_remove(me_effect,'"'),
-         me_effect =as.numeric(str_remove(me_effect,'"')),
-         alignment = str_remove(alignment,'c[(]'),
-         alignment =str_remove(alignment,'"'),
-         alignment =str_remove(alignment,'"'))
+         me_effect =as.numeric(str_remove(me_effect,"[)]")))
 
@@
 ```
+# Plotting model parameters
 
@@
 
-ggsave("../graphs/subj_intercept.pdf", width = 5, height = 8, scale = 1.5)
+#ggsave("../graphs/subj_intercept.pdf", width = 5, height = 8, scale = 1.5)
 
@@
 
+model_plot
 ```
@@
   scale_colour_viridis_d()
-```
-
-```{r}
-
+
+p_comb_model
+```
+
+```{r}
 data_comb <- read_csv("../data/combination.csv") %>%
@@
 ```{r}
-ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
+p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
   geom_hline(yintercept = 0.5, lty=2)+
@@
   scale_fill_ptol(name = NULL)
+
+p_data_model
 ```
@@
 
-cor_plot_age <- ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
+ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
@@
 ggarrange(
-plot_item_params,plotg_subj_sigma,
-plot_global_params,plot_subject_params,
-cor_plot_age, plot_global_sigma,
-ncol = 2, nrow = 3, common.legend = T, widths = c(1.7,1))
-
-ggsave("../graphs/overview_wide_slope_wide_sigma_pos_slope_ind.png", width = 12, height = 10, scale = 1.2)
+plot_item_params,
+plot_global_params,
+p_data_model, plot_global_sigma,
+ncol = 2, nrow = 2, common.legend = F, widths = c(3,1))
+
+ggsave("../graphs/overview_variant_3_50k.png", width = 12, height = 4, scale = 1.2)
 
@@
           width: 0.5
-        }), 2)
+        })
       }]
@@
     // comment out to save memory
-    query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])
+  //  query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])
 
@@
 
-display(row.alignment)
-
-        query.add(["prediction", item, row.age], [row.alignment, Math.exp(modelPredictions.score(1))])
+      //  query.add(["prediction", item, row.age, row.alignment], ["NA", Math.exp(modelPredictions.score(1))])
 
@@
     distinct(age, prior) %>%
-    mutate(alignment = "congruent"),
+    mutate(prior = 1 - prior, 
+         alignment = "incongruent"),
+
    me_model_data %>%
     distinct(age, prior) %>%
-    mutate(prior = 1 - prior, 
-         alignment = "incongruent")
+    mutate(alignment = "congruent")
 )
@@
   model_var = "model",
-  chains = 1,
-  cores = 1,
+  chains = 3,
+  cores = 3,
   inference_opts = list(method = "incrementalMH",
-                        samples = 10,
-                        burn = 1,
+                        samples = 50000,
+                        burn = 25000,
                         verbose = T,
                         lag = 1,
-                        verboseLag = 1000)
+                        verboseLag = 100)
 )
@@
 
-# saveRDS(sem_know_model, "../saves/sem_know_model_save pred.rds")
+saveRDS(sem_know_model, "../saves/sem_know_model_variant3_50k.rds")
+
+model_pred<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
+  filter(parameter == "prediction")%>%
+  separate(value, into = c("na", "me_effect"),sep = ",")%>%
+  select(-na)%>%
+  mutate(age = as.numeric(age),
+         me_effect =as.numeric(str_remove(me_effect,"[)]")))
 
@@
 comb_model_pred_agg <- model_pred%>%
-  group_by(alignment,item,age)%>%
+  group_by(Chain, alignment,item,age)%>%
   summarise(mean = estimate_mode(me_effect),
@@
   mutate(item = fct_reorder(factor(item), mean_aoa),
-         age = age + min(me_data$age_num))
-
-ggplot(comb_model_pred_agg, aes(x=age,y = mean, col = item))+
+         age = age + min(me_data$age_num),
+         Chain = factor(Chain))
+
+ggplot(comb_model_pred_agg, aes(x=age,y = mean, col = item, fill = item))+
+  geom_ribbon(aes(ymin = lci, ymax = uci), alpha = .5, colour = NA)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   labs(x="Age",y="Proportion correct")+
-  facet_grid(~alignment)+
+  facet_grid(Chain~alignment)+
   theme_few() +
@@
   guides(alpha = F)+ 
-  scale_colour_viridis_d()
-
-```
+  scale_colour_viridis_d()+
+  scale_fill_viridis_d()
+
+```

### 2019-09-06 saves/rwebppl/bash/install-dev-webppl.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+RWEBPPL=$1
+COMMIT=$2
+
+cd $RWEBPPL/js
+git clone https://github.com/probmods/webppl.git
+cd webppl
+git checkout $COMMIT
+npm install

### 2019-09-06 saves/rwebppl/bash/install-webppl.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+RWEBPPL=$1
+
+cd $RWEBPPL/js
+npm install

### 2019-09-06 saves/rwebppl/bash/install_package.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+INST=$1
+PKG=$2
+RWEBPPL=$3
+
+mkdir -p $INST
+cd $INST
+if [ ! -a ./package.json ]
+  then
+    cp "${RWEBPPL}/json/webppl-packages.json" ./package.json
+fi
+npm install $PKG

### 2019-09-06 saves/rwebppl/bash/rearrange-webppl.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+RWEBPPL=$1
+
+cd $RWEBPPL/js
+
+mv node_modules/webppl/ .
+mv node_modules webppl/node_modules

### 2019-09-06 saves/rwebppl/bash/uninstall_package.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+INST=$1
+PKG=$2
+
+if [ -d $INST ]
+  then
+    cd $INST
+    npm uninstall $PKG
+fi

### 2019-09-06 saves/rwebppl/js/webppl/Gruntfile.js

@@ -1,0 +1,173 @@
+'use strict';
+
+var _ = require('lodash');
+var open = require('open');
+var child_process = require('child_process');
+var path = require('path');
+var fs = require('fs');
+
+function isCodeGenFile(fn) {
+  return isPlainJsFile(fn) && fs.existsSync(adSource(fn));
+}
+
+function isPlainJsFile(fn) {
+  return path.extname(fn) === '.js' &&
+         path.extname(path.parse(fn).name) !== '.ad';
+}
+
+function adSource(fn) {
+  return fn.slice(0, -3) + '.ad.js';
+}
+
+module.exports = function(grunt) {
+  grunt.initConfig({
+    nodeunit: {
+      all: ['tests/test-*.js']
+    },
+    eslint: {
+      lib: {
+        src: [
+          'Gruntfile.js',
+          'src/**/*.js'
+        ],
+        filter: _.negate(isCodeGenFile)
+      },
+      test: {
+        src: ['tests/**/*.js']
+      },
+      wppl: {
+        src: [
+          'src/header.wppl',
+          'examples/*.wppl',
+          'tests/test-data/**/*.wppl'
+        ],
+        options: {
+          configFile: '.eslintrc.wppl.js'
+        }
+      },
+      options: {fix: "<%= grunt.option('fix') %>"}
+    },
+    jshint: {
+      all: {
+        src: [
+          'Gruntfile.js',
+          'src/header.wppl',
+          'src/**/*.js',
+          'tests/**/*.js'
+        ],
+        filter: _.negate(isCodeGenFile)
+      },
+      options: {
+        maxerr: 500,
+        camelcase: true,
+        nonew: true,
+        curly: true,
+        noarg: true,
+        trailing: true,
+        forin: true,
+        noempty: true,
+        node: true,
+        eqeqeq: true,
+        strict: false,
+        evil: true,
+        undef: true,
+        bitwise: true,
+        browser: true,
+        gcl: true,
+        newcap: false
+      }
+    },
+    clean: ['bundle/*.js'],
+    watch: {
+      ad: {
+        files: ['**/*.ad.js'],
+        tasks: ['build-ad']
+      },
+      dist: {
+        files: ['src/dists.ad.js'],
+        tasks: ['build-dist-header']
+      }
+    }
+  });
+
+  function browserifyArgs(args) {
+    var pkgArg = '';
+    var requires = _.chain(_.toArray(args))
[…]

### 2019-09-06 saves/rwebppl/js/webppl/docs/conf.py

@@ -1,0 +1,289 @@
+# -*- coding: utf-8 -*-
+#
+# webppl documentation build configuration file, created by
+# sphinx-quickstart on Tue Sep 22 10:28:38 2015.
+#
+# This file is execfile()d with the current directory set to its
+# containing dir.
+#
+# Note that not all possible configuration values are present in this
+# autogenerated file.
+#
+# All configuration values have a default; values that are commented out
+# serve to show the default.
+
+import sys
+import os
+import shlex
+import json
+
+on_rtd = os.environ.get('READTHEDOCS', None) == 'True'
+
+if not on_rtd:
+    import sphinx_rtd_theme
+    html_theme = 'sphinx_rtd_theme'
+    html_theme_path = [sphinx_rtd_theme.get_html_theme_path()]
+
+def setup(app):
+    app.add_stylesheet("css/custom.css")
+
+# If extensions (or modules to document with autodoc) are in another directory,
+# add these directories to sys.path here. If the directory is relative to the
+# documentation root, use os.path.abspath to make it absolute, like shown here.
+#sys.path.insert(0, os.path.abspath('.'))
+
+# -- General configuration ------------------------------------------------
+
+# If your documentation needs a minimal Sphinx version, state it here.
+#needs_sphinx = '1.0'
+
+# Add any Sphinx extension module names here, as strings. They can be
+# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
+# ones.
+extensions = []
+
+# Add any paths that contain templates here, relative to this directory.
+templates_path = ['_templates']
+
+# The suffix(es) of source filenames.
+# You can specify multiple suffix as a list of string:
+# source_suffix = ['.rst', '.md']
+source_suffix = '.rst'
+
+# The encoding of source files.
+#source_encoding = 'utf-8-sig'
+
+# The master toctree document.
+master_doc = 'index'
+
+# General information about the project.
+project = u'webppl'
+copyright = u'2015, the webppl contributors'
+author = u'the webppl contributors'
+
+# The version info for the project you're documenting, acts as replacement for
+# |version| and |release|, also used in various other places throughout the
+# built documents.
+#
+with open('../package.json') as f:
+    pkg = json.load(f)
+# The short X.Y version.
+version = pkg['version']
+# The full version, including alpha/beta/rc tags.
+release = pkg['version']
+
+# The language for content autogenerated by Sphinx. Refer to documentation
+# for a list of supported languages.
+#
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/aggregation/ScoreAggregator.js

@@ -1,0 +1,45 @@
+'use strict';
+var ad = require('../ad');
+var assert = require('assert');
+var _ = require('lodash');
+var dists = require('../dists');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var ScoreAggregator = function () {
+    this.dist = {};
+};
+Object.defineProperties(ScoreAggregator.prototype, {
+    size: {
+        get: function () {
+            return _.size(this.dist);
+        }
+    }
+});
+ScoreAggregator.prototype.add = function (value, score) {
+    if (ad.scalar.peq(score, ad.scalar.neg(Infinity))) {
+        return;
+    }
+    var key = util.serialize(value);
+    if (ad.scalar.peq(this.dist[key], undefined)) {
+        this.dist[key] = {
+            score: ad.scalar.neg(Infinity),
+            val: value
+        };
+    }
+    this.dist[key].score = numeric.logaddexp(this.dist[key].score, score);
+};
+function normalize(dist) {
+    var logNorm = _.reduce(dist, function (acc, obj) {
+        return numeric.logaddexp(acc, obj.score);
+    }, ad.scalar.neg(Infinity));
+    return _.mapValues(dist, function (obj) {
+        return {
+            val: obj.val,
+            prob: ad.scalar.exp(ad.scalar.sub(obj.score, logNorm))
+        };
+    });
+}
+ScoreAggregator.prototype.toDist = function () {
+    return new dists.Marginal({ dist: normalize(this.dist) });
+};
+module.exports = ScoreAggregator;

### 2019-09-06 saves/rwebppl/js/webppl/src/browser.js

@@ -1,0 +1,72 @@
+// Entry point for browserify.
+
+'use strict';
+
+var _ = require('lodash');
+var fs = require('fs');
+var esprima = require('esprima');
+var escodegen = require('escodegen');
+var webppl = require('./main');
+var optimize = require('./transforms/optimize').optimize;
+var naming = require('./transforms/naming').naming;
+var thunkify = require('./syntax').thunkify;
+var cps = require('./transforms/cps').cps;
+var errors = require('./errors/browser');
+var util = require('./util');
+
+// These are populated by the bundle.js browserify transform.
+var version = '';
+var packages = [];
+
+var load = _.once(function() {
+  // Load JS and headers from packages.
+  packages.forEach(function(pkg) {
+    if (pkg.js) { global[pkg.js.identifier] = pkg.js.path; }
+    pkg.headers.forEach(webppl.requireHeaderWrapper);
+  });
+  var bundles = webppl.parsePackageCode(packages);
+  return bundles;
+});
+
+function prepare(codeAndAssets, k, options) {
+  options = util.mergeDefaults(options, {
+    filename: 'webppl:program',
+    errorHandlers: []
+  });
+  var extraHandlers = options.debug ? [errors.debugHandler(options.filename)] : [];
+  options.errorHandlers = extraHandlers.concat(options.errorHandlers);
+  return webppl.prepare(codeAndAssets, k, options);
+}
+
+function run(code, k, options) {
+  var codeAndAssets = compile(code, options);
+  prepare(codeAndAssets, k, options).run();
+}
+
+function compile(code, options) {
+  options = options || {};
+  var optionsExtended = _.extend({bundles: load()}, options);
+  return webppl.compile(code, optionsExtended);
+}
+
+function webpplCPS(code) {
+  var programAst = esprima.parse(code);
+  var newProgramAst = optimize(cps(thunkify(programAst)));
+  return escodegen.generate(newProgramAst);
+}
+
+function webpplNaming(code) {
+  var programAst = esprima.parse(code);
+  var newProgramAst = naming(thunkify(programAst)).ast;
+  return escodegen.generate(newProgramAst);
+}
+
+global.webppl = {
+  prepare: prepare,
+  run: run,
+  compile: compile,
+  cps: webpplCPS,
+  naming: webpplNaming,
+  version: version,
+  packages: packages
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/bundle.js

@@ -1,0 +1,68 @@
+// A browserify plugin to include packages and version information in
+// the browser bundle.
+
+'use strict';
+
+var path = require('path');
+var assert = require('assert');
+var through = require('through2');
+var esprima = require('esprima');
+var estraverse = require('estraverse');
+var escodegen = require('escodegen');
+var _ = require('lodash');
+
+var pkg = require('./pkg');
+var pkginfo = require('./pkginfo');
+var util = require('./util');
+
+var parseExpr = function(s) {
+  return esprima.parse('(' + s + ')').body[0].expression;
+};
+
+var transform = function(code, version, opts) {
+
+  var replace = _.partial(estraverse.replace, _, {
+    enter: function(node, parent) {
+
+      if (node.type === 'ArrayExpression' &&
+          parent.type === 'VariableDeclarator' &&
+          parent.id.type === 'Identifier' &&
+          parent.id.name === 'packages') {
+        assert(node.elements.length === 0);
+        var exprs = util.asArray(opts.require).map(function(name_or_path) {
+          return _.flowRight(parseExpr, pkg.stringify, pkg.read)(name_or_path);
+        });
+
+        return { type: node.type, elements: exprs };
+      }
+
+      if (node.type === 'Literal' &&
+          node.value === '' &&
+          parent.type === 'VariableDeclarator' &&
+          parent.id.type === 'Identifier' &&
+          parent.id.name === 'version') {
+        return { type: node.type, value: version };
+      }
+
+    }
+  });
+
+  var pipeline = _.flowRight(escodegen.generate, replace, esprima.parse);
+  return pipeline(code);
+};
+
+
+module.exports = function(file, opts) {
+  if (path.basename(file) !== 'browser.js') { return through(); }
+
+  var code = '';
+  return through(
+      function(buf, enc, next) {
+        code += buf;
+        next();
+      },
+      function(next) {
+        this.push(transform(code, pkginfo.version(), opts));
+        next();
+      });
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/base.js

@@ -1,0 +1,155 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var util = require('../util');
+var inspect = require('util').inspect;
+function Distribution() {
+}
+Distribution.prototype = {
+    toJSON: function () {
+        throw new Error('Not implemented');
+    },
+    inspect: function (depth, options) {
+        if (_.has(this, 'params')) {
+            if (this.print) {
+                return this.print();
+            } else {
+                return [
+                    this.meta.name,
+                    '(',
+                    inspect(this.params),
+                    ')'
+                ].join('');
+            }
+        } else {
+            var opts = options ? _.clone(options) : {};
+            opts.customInspect = false;
+            return inspect(this, opts);
+        }
+    },
+    toString: function () {
+        return this.inspect();
+    },
+    isContinuous: false,
+    constructor: Distribution
+};
+function isDist(x) {
+    return x instanceof Distribution;
+}
+function clone(dist) {
+    return new dist.constructor(dist.params);
+}
+var finiteSupport = {
+    MAP: function () {
+        var map = { score: -Infinity };
+        this.support().forEach(function (val) {
+            var score = this.score(val);
+            if (score > map.score) {
+                map = {
+                    val: val,
+                    score: score
+                };
+            }
+        }, this);
+        return map;
+    },
+    entropy: function () {
+        return _.reduce(this.support(), function (memo, x) {
+            var score = this.score(x);
+            return ad.scalar.sub(memo, ad.scalar.peq(score, ad.scalar.neg(Infinity)) ? 0 : ad.scalar.mul(ad.scalar.exp(score), score));
+        }.bind(this), 0);
+    },
+    toJSON: function () {
+        var support = this.support();
+        var probs = support.map(function (s) {
+            return Math.exp(this.score(s));
+        }, this);
+        return {
+            probs: probs,
+            support: support
+        };
+    }
+};
+var continuousSupport = { isContinuous: true };
+var noHMC = { noHMC: true };
+var methodNames = [
+    'sample',
+    'score',
+    'support',
+    'print',
+    'base',
+    'transform'
+];
+function makeDistributionType(options) {
+    options = util.mergeDefaults(options, { mixins: [] });
+    [
+        'name',
+        'params'
+    ].forEach(function (name) {
+        if (!_.has(options, name)) {
+            console.log(options);
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/bernoulli.js

@@ -1,0 +1,32 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var util = require('../util');
+var types = require('../types');
+var Bernoulli = base.makeDistributionType({
+    name: 'Bernoulli',
+    desc: 'Distribution over ``{true, false}``',
+    params: [{
+            name: 'p',
+            desc: 'success probability',
+            type: types.unitInterval
+        }],
+    wikipedia: true,
+    mixins: [base.finiteSupport],
+    sample: function () {
+        return util.random() < ad.value(this.params.p);
+    },
+    score: function (val) {
+        if (ad.scalar.pneq(val, true) && ad.scalar.pneq(val, false)) {
+            return ad.scalar.neg(Infinity);
+        }
+        return val ? ad.scalar.log(this.params.p) : ad.scalar.log(ad.scalar.sub(1, this.params.p));
+    },
+    support: function () {
+        return [
+            true,
+            false
+        ];
+    }
+});
+module.exports = { Bernoulli: Bernoulli };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/beta.js

@@ -1,0 +1,88 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var gaussian = require('./gaussian');
+function expGammaSample(shape, scale) {
+    if (shape < 1) {
+        var r;
+        r = expGammaSample(1 + shape, scale) + Math.log(util.random()) / shape;
+        if (r === -Infinity) {
+            util.warn('log gamma sample underflow, rounded to nearest representable support value');
+            return -Number.MAX_VALUE;
+        }
+        return r;
+    }
+    var x, v, u, log_v;
+    var d = shape - 1 / 3;
+    var c = 1 / Math.sqrt(9 * d);
+    while (true) {
+        do {
+            x = gaussian.sample(0, 1);
+            v = 1 + c * x;
+        } while (v <= 0);
+        log_v = 3 * Math.log(v);
+        v = v * v * v;
+        u = util.random();
+        if (u < 1 - 0.331 * x * x * x * x || Math.log(u) < 0.5 * x * x + d * (1 - v + Math.log(v))) {
+            return Math.log(scale) + Math.log(d) + log_v;
+        }
+    }
+}
+function expGammaScore(shape, scale, val) {
+    var x = val;
+    return ad.scalar.sub(ad.scalar.sub(ad.scalar.sub(ad.scalar.mul(ad.scalar.sub(shape, 1), x), ad.scalar.div(ad.scalar.exp(x), scale)), ad.scalar.logGamma(shape)), ad.scalar.mul(shape, ad.scalar.log(scale)));
+}
+function logBeta(a, b) {
+    return ad.scalar.sub(ad.scalar.add(ad.scalar.logGamma(a), ad.scalar.logGamma(b)), ad.scalar.logGamma(ad.scalar.add(a, b)));
+}
+function sample(a, b) {
+    var log_x = expGammaSample(a, 1);
+    var log_y = expGammaSample(b, 1);
+    var v = 1 / (1 + Math.exp(log_y - log_x));
+    if (v === 0) {
+        util.warn('beta sample underflow, rounded to nearest representable support value');
+        v = Number.MIN_VALUE;
+    } else if (v === 1) {
+        util.warn('beta sample overflow, rounded to nearest representable support value');
+        v = 1 - Number.EPSILON / 2;
+    }
+    return v;
+}
+var Beta = base.makeDistributionType({
+    name: 'Beta',
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/binomial.js

@@ -1,0 +1,96 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var beta = require('./beta');
+function lnfactExact(x) {
+    if (ad.scalar.lt(x, 0)) {
+        throw new Error(ad.scalar.add('lnfactExact called on negative argument ', x));
+    }
+    if (ad.scalar.lt(x, 1)) {
+        x = 1;
+    }
+    var t = 0;
+    while (ad.scalar.gt(x, 1)) {
+        t = ad.scalar.add(t, ad.scalar.log(x));
+        x = ad.scalar.sub(x, 1);
+    }
+    return t;
+}
+function sample(p, n) {
+    var k = 0;
+    var N = 10;
+    var a, b;
+    while (n > N) {
+        a = Math.floor(1 + n / 2);
+        b = 1 + n - a;
+        var x = beta.sample(a, b);
+        if (x >= p) {
+            n = a - 1;
+            p /= x;
+        } else {
+            k += a;
+            n = b - 1;
+            p = (p - x) / (1 - x);
+        }
+    }
+    var u;
+    for (var i = 0; i < n; i++) {
+        u = util.random();
+        if (u < p) {
+            k++;
+        }
+    }
+    return k || 0;
+}
+var Binomial = base.makeDistributionType({
+    name: 'Binomial',
+    desc: 'Distribution over the number of successes for ``n`` independent ``Bernoulli({p: p})`` trials.',
+    params: [
+        {
+            name: 'p',
+            desc: 'success probability',
+            type: types.unitInterval
+        },
+        {
+            name: 'n',
+            desc: 'number of trials',
+            type: types.positiveInt
+        }
+    ],
+    wikipedia: true,
+    mixins: [base.finiteSupport],
+    sample: function () {
+        return sample(ad.value(this.params.p), this.params.n);
+    },
+    score: function (val) {
+        var p = this.params.p;
+        var n = this.params.n;
+        if (!(ad.scalar.peq(typeof val, 'number') && ad.scalar.geq(val, 0) && ad.scalar.leq(val, n) && ad.scalar.peq(val % 1, 0))) {
+            return ad.scalar.neg(Infinity);
+        }
+        var logNumPermutations = 0;
+        var m, o;
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/categorical.js

@@ -1,0 +1,68 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var Marginal = require('./marginal').Marginal;
+var T = ad.tensor;
+var Categorical = base.makeDistributionType({
+    name: 'Categorical',
+    desc: 'Distribution over elements of ``vs`` with ``P(vs[i])`` proportional to ``ps[i]``. ' + '``ps`` may be omitted, in which case a uniform distribution over ``vs`` is returned.',
+    params: [
+        {
+            name: 'ps',
+            desc: 'probabilities (can be unnormalized)',
+            type: types.nonNegativeVectorOrRealArray,
+            optional: true
+        },
+        {
+            name: 'vs',
+            desc: 'support',
+            type: types.array(types.any)
+        }
+    ],
+    wikipedia: true,
+    mixins: [base.finiteSupport],
+    constructor: function () {
+        if (ad.scalar.peq(this.params.ps, undefined)) {
+            this.params = {
+                ps: _.fill(Array(this.params.vs.length), 1),
+                vs: this.params.vs
+            };
+        }
+        var ps = this.params.ps;
+        var vs = this.params.vs;
+        if (ad.scalar.pneq(vs.length, ad.value(ps).length)) {
+            throw new Error('Parameters ps and vs should have the same length.');
+        }
+        if (ad.scalar.peq(vs.length, 0)) {
+            throw new Error('Parameters ps and vs should have length > 0.');
+        }
+        var dist = {};
+        var norm = _.isArray(ps) ? numeric.sum(ps) : T.sumreduce(ps);
+        for (var i in vs) {
+            var val = vs[i];
+            var k = util.serialize(val);
+            if (!_.has(dist, k)) {
+                dist[k] = {
+                    val: val,
+                    prob: 0
+                };
+            }
+            dist[k].prob = ad.scalar.add(dist[k].prob, ad.scalar.div(_.isArray(ps) ? ps[i] : T.get(ps, i), norm));
+        }
+        this.marginal = new Marginal({ dist: dist });
+    },
+    sample: function () {
+        return this.marginal.sample();
+    },
+    score: function (val) {
+        return this.marginal.score(val);
+    },
+    support: function () {
+        return this.marginal.support();
+    }
+});
+module.exports = { Categorical: Categorical };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/cauchy.js

@@ -1,0 +1,47 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var Uniform = require('./uniform').Uniform;
+var LOG_PI = numeric.LOG_PI;
+var Cauchy = base.makeDistributionType({
+    name: 'Cauchy',
+    desc: 'Distribution over ``[-Infinity, Infinity]``',
+    params: [
+        {
+            name: 'location',
+            desc: '',
+            type: types.unboundedReal
+        },
+        {
+            name: 'scale',
+            desc: '',
+            type: types.positiveReal
+        }
+    ],
+    wikipedia: true,
+    mixins: [base.continuousSupport],
+    sample: function () {
+        var u = util.random();
+        return ad.value(this.params.location) + ad.value(this.params.scale) * Math.tan(Math.PI * (u - 0.5));
+    },
+    score: function (x) {
+        var scale = this.params.scale;
+        var location = this.params.location;
+        return ad.scalar.sub(ad.scalar.sub(ad.scalar.neg(LOG_PI), ad.scalar.log(scale)), ad.scalar.log(ad.scalar.add(1, ad.scalar.pow(ad.scalar.div(ad.scalar.sub(x, location), scale), 2))));
+    },
+    base: function () {
+        return new Uniform({
+            a: 0,
+            b: 1
+        });
+    },
+    transform: function (x) {
+        var location = this.params.location;
+        var scale = this.params.scale;
+        return ad.scalar.add(location, ad.scalar.mul(scale, ad.scalar.tan(ad.scalar.mul(ad.scalar.PI, ad.scalar.sub(x, 0.5)))));
+    }
+});
+module.exports = { Cauchy: Cauchy };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/delta.js

@@ -1,0 +1,30 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var Delta = base.makeDistributionType({
+    name: 'Delta',
+    desc: 'Discrete distribution that assigns probability one to the single ' + 'element in its support. This is only useful in special circumstances as sampling ' + 'from ``Delta({v: val})`` can be replaced with ``val`` itself. Furthermore, a ``Delta`` ' + 'distribution parameterized by a random choice should not be used with MCMC based inference, ' + 'as doing so produces incorrect results.',
+    params: [{
+            name: 'v',
+            desc: 'support element',
+            type: types.any
+        }],
+    mixins: [base.finiteSupport],
+    sample: function () {
+        return ad.value(this.params.v);
+    },
+    score: function (val) {
+        return ad.value(val) === ad.value(this.params.v) ? 0 : -Infinity;
+    },
+    support: function () {
+        return [this.params.v];
+    },
+    base: function () {
+        return this;
+    },
+    transform: function (x) {
+        return this.params.v;
+    }
+});
+module.exports = { Delta: Delta };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/diagCovGaussian.js

@@ -1,0 +1,79 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var Tensor = require('../tensor');
+var numeric = require('../math/numeric');
+var gaussian = require('./gaussian');
+var TensorGaussian = require('./tensorGaussian').TensorGaussian;
+var LOG_2PI = numeric.LOG_2PI;
+function sample(mu, sigma) {
+    var dims = mu.dims;
+    var x = new Tensor(dims);
+    var n = x.length;
+    while (n--) {
+        x.data[n] = gaussian.sample(mu.data[n], sigma.data[n]);
+    }
+    return x;
+}
+function score(mu, sigma, x) {
+    var _x = ad.value(x);
+    var _mu = ad.value(mu);
+    if (!util.isTensor(_x) || !util.tensorEqDims(_x, _mu)) {
+        return -Infinity;
+    }
+    var d = _mu.length;
+    var dLog2Pi = d * LOG_2PI;
+    var logDetCov = ad.scalar.mul(2, ad.tensor.sumreduce(ad.tensor.log(sigma)));
+    var z = ad.tensor.div(ad.tensor.sub(x, mu), sigma);
+    return ad.scalar.mul(-0.5, ad.scalar.add(dLog2Pi, ad.scalar.add(logDetCov, ad.tensor.sumreduce(ad.tensor.mul(z, z)))));
+}
+var DiagCovGaussian = base.makeDistributionType({
+    name: 'DiagCovGaussian',
+    desc: 'A distribution over tensors in which each element is independent and Gaussian distributed, ' + 'with its own mean and standard deviation. i.e. A multivariate Gaussian distribution with ' + 'diagonal covariance matrix. The distribution is over tensors that have the same shape as the ' + 'parameters ``mu`` and ``sigma``, which in turn must have the same shape as each other.',
+    params: [
+        {
+            name: 'mu',
+            desc: 'mean',
+            type: types.unboundedTensor
+        },
+        {
+            name: 'sigma',
+            desc: 'standard deviations',
+            type: types.positiveTensor
+        }
+    ],
+    mixins: [base.continuousSupport],
+    constructor: function () {
+        var _mu = ad.value(this.params.mu);
+        var _sigma = ad.value(this.params.sigma);
+        if (!util.tensorEqDims(_mu, _sigma)) {
+            throw new Error(this.meta.name + ': mu and sigma should be the same shape.');
+        }
+    },
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/dirichlet.js

@@ -1,0 +1,60 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var Tensor = require('../tensor');
+var gamma = require('./gamma');
+function sample(alpha) {
+    var n = alpha.dims[0];
+    var ssum = 0;
+    var theta = new Tensor([
+        n,
+        1
+    ]);
+    var t;
+    for (var i = 0; i < n; i++) {
+        t = gamma.sample(alpha.data[i], 1);
+        theta.data[i] = t;
+        ssum += t;
+    }
+    for (var j = 0; j < n; j++) {
+        theta.data[j] /= ssum;
+        if (theta.data[j] === 0) {
+            theta.data[j] = Number.MIN_VALUE;
+        }
+        if (theta.data[j] === 1) {
+            theta.data[j] = 1 - Number.EPSILON / 2;
+        }
+    }
+    return theta;
+}
+function score(alpha, val) {
+    var _val = ad.value(val);
+    var _alpha = ad.value(alpha);
+    if (!util.isVector(_val) || !util.tensorEqDim0(_val, _alpha)) {
+        return -Infinity;
+    }
+    return ad.scalar.add(ad.tensor.sumreduce(ad.tensor.sub(ad.tensor.mul(ad.tensor.sub(alpha, 1), ad.tensor.log(val)), ad.tensor.logGamma(alpha))), ad.scalar.logGamma(ad.tensor.sumreduce(alpha)));
+}
+var Dirichlet = base.makeDistributionType({
+    name: 'Dirichlet',
+    desc: 'Distribution over probability vectors. ' + 'If ``alpha`` has length ``d`` then the distribution ' + 'is over probability vectors of length ``d``.',
+    params: [{
+            name: 'alpha',
+            desc: 'concentration',
+            type: types.positiveVector
+        }],
+    wikipedia: true,
+    mixins: [
+        base.continuousSupport,
+        base.noHMC
+    ],
+    sample: function () {
+        return sample(ad.value(this.params.alpha));
+    },
+    score: function (val) {
+        return score(this.params.alpha, val);
+    }
+});
+module.exports = { Dirichlet: Dirichlet };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/discrete.js

@@ -1,0 +1,74 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var T = ad.tensor;
+function sample(theta, thetaSum) {
+    if (thetaSum === undefined) {
+        thetaSum = numeric._sum(theta);
+    }
+    var x = util.random() * thetaSum;
+    var k = theta.length;
+    var probAccum = 0;
+    for (var i = 0; i < k; i++) {
+        probAccum += theta[i];
+        if (x < probAccum) {
+            return i;
+        }
+    }
+    return k - 1;
+}
+function scoreVector(val, probs, norm) {
+    return ad.scalar.log(ad.scalar.div(T.get(probs, val), norm));
+}
+function scoreArray(val, probs, norm) {
+    return ad.scalar.log(ad.scalar.div(probs[val], norm));
+}
+function inSupport(val, dim) {
+    return val === Math.floor(val) && 0 <= val && val < dim;
+}
+function toUnliftedArray(x) {
+    return _.isArray(x) ? x.map(ad.value) : ad.value(x).data;
+}
+var Discrete = base.makeDistributionType({
+    name: 'Discrete',
+    desc: 'Distribution over ``{0,1,...,ps.length-1}`` with P(i) proportional to ``ps[i]``',
+    params: [{
+            name: 'ps',
+            desc: 'probabilities (can be unnormalized)',
+            type: types.nonNegativeVectorOrRealArray
+        }],
+    wikipedia: 'Categorical_distribution',
+    mixins: [base.finiteSupport],
+    constructor: function () {
+        if (_.isArray(this.params.ps)) {
+            this.norm = numeric.sum(this.params.ps);
+            this.scoreFn = scoreArray;
+            this.dim = this.params.ps.length;
+        } else {
+            this.norm = T.sumreduce(this.params.ps);
+            this.scoreFn = scoreVector;
+            this.dim = ad.value(this.params.ps).length;
+        }
+    },
+    sample: function () {
+        return sample(toUnliftedArray(this.params.ps), ad.value(this.norm));
+    },
+    score: function (val) {
+        if (inSupport(val, this.dim)) {
+            return this.scoreFn(val, this.params.ps, this.norm);
+        } else {
+            return -Infinity;
+        }
+    },
+    support: function () {
+        return _.range(this.dim);
+    }
+});
+module.exports = {
+    Discrete: Discrete,
+    sample: sample
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/exponential.js

@@ -1,0 +1,40 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var Uniform = require('./uniform').Uniform;
+var Exponential = base.makeDistributionType({
+    name: 'Exponential',
+    desc: 'Distribution over ``[0, Infinity]``',
+    params: [{
+            name: 'a',
+            desc: 'rate',
+            type: types.positiveReal
+        }],
+    wikipedia: true,
+    mixins: [base.continuousSupport],
+    sample: function () {
+        var u = util.random();
+        return Math.log(u) / (-1 * ad.value(this.params.a));
+    },
+    score: function (val) {
+        return ad.scalar.geq(val, 0) ? ad.scalar.sub(ad.scalar.log(this.params.a), ad.scalar.mul(this.params.a, val)) : ad.scalar.neg(Infinity);
+    },
+    base: function () {
+        return new Uniform({
+            a: 0,
+            b: 1
+        });
+    },
+    transform: function (x) {
+        return ad.scalar.div(ad.scalar.log(x), ad.scalar.neg(this.params.a));
+    },
+    support: function () {
+        return {
+            lower: 0,
+            upper: Infinity
+        };
+    }
+});
+module.exports = { Exponential: Exponential };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/gamma.js

@@ -1,0 +1,67 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var gaussian = require('./gaussian');
+function sample(shape, scale) {
+    if (shape < 1) {
+        var r;
+        r = sample(1 + shape, scale) * Math.pow(util.random(), 1 / shape);
+        if (r === 0) {
+            util.warn('gamma sample underflow, rounded to nearest representable support value');
+            return Number.MIN_VALUE;
+        }
+        return r;
+    }
+    var x, v, u;
+    var d = shape - 1 / 3;
+    var c = 1 / Math.sqrt(9 * d);
+    while (true) {
+        do {
+            x = gaussian.sample(0, 1);
+            v = 1 + c * x;
+        } while (v <= 0);
+        v = v * v * v;
+        u = util.random();
+        if (u < 1 - 0.331 * x * x * x * x || Math.log(u) < 0.5 * x * x + d * (1 - v + Math.log(v))) {
+            return scale * d * v;
+        }
+    }
+}
+var Gamma = base.makeDistributionType({
+    name: 'Gamma',
+    desc: 'Distribution over positive reals.',
+    params: [
+        {
+            name: 'shape',
+            desc: '',
+            type: types.positiveReal
+        },
+        {
+            name: 'scale',
+            desc: '',
+            type: types.positiveReal
+        }
+    ],
+    wikipedia: true,
+    mixins: [base.continuousSupport],
+    sample: function () {
+        return sample(ad.value(this.params.shape), ad.value(this.params.scale));
+    },
+    score: function (x) {
+        var shape = this.params.shape;
+        var scale = this.params.scale;
+        return ad.scalar.sub(ad.scalar.sub(ad.scalar.sub(ad.scalar.mul(ad.scalar.sub(shape, 1), ad.scalar.log(x)), ad.scalar.div(x, scale)), ad.scalar.logGamma(shape)), ad.scalar.mul(shape, ad.scalar.log(scale)));
+    },
+    support: function () {
+        return {
+            lower: 0,
+            upper: Infinity
+        };
+    }
+});
+module.exports = {
+    Gamma: Gamma,
+    sample: sample
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/gaussian.js

@@ -1,0 +1,61 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var LOG_2PI = numeric.LOG_2PI;
+function sample(mu, sigma) {
+    var u, v, x, y, q;
+    do {
+        u = 1 - util.random();
+        v = 1.7156 * (util.random() - 0.5);
+        x = u - 0.449871;
+        y = Math.abs(v) + 0.386595;
+        q = x * x + y * (0.196 * y - 0.25472 * x);
+    } while (q >= 0.27597 && (q > 0.27846 || v * v > -4 * u * u * Math.log(u)));
+    return mu + sigma * v / u;
+}
+function score(mu, sigma, x) {
+    return ad.scalar.mul(ad.scalar.neg(0.5), ad.scalar.add(ad.scalar.add(LOG_2PI, ad.scalar.mul(2, ad.scalar.log(sigma))), ad.scalar.div(ad.scalar.mul(ad.scalar.sub(x, mu), ad.scalar.sub(x, mu)), ad.scalar.mul(sigma, sigma))));
+}
+var Gaussian = base.makeDistributionType({
+    name: 'Gaussian',
+    desc: 'Distribution over reals.',
+    params: [
+        {
+            name: 'mu',
+            desc: 'mean',
+            type: types.unboundedReal
+        },
+        {
+            name: 'sigma',
+            desc: 'standard deviation',
+            type: types.positiveReal
+        }
+    ],
+    wikipedia: 'Normal_distribution',
+    mixins: [base.continuousSupport],
+    sample: function () {
+        return sample(ad.value(this.params.mu), ad.value(this.params.sigma));
+    },
+    score: function (x) {
+        return score(this.params.mu, this.params.sigma, x);
+    },
+    base: function () {
+        return new Gaussian({
+            mu: 0,
+            sigma: 1
+        });
+    },
+    transform: function (x) {
+        var mu = this.params.mu;
+        var sigma = this.params.sigma;
+        return ad.scalar.add(ad.scalar.mul(sigma, x), mu);
+    }
+});
+module.exports = {
+    Gaussian: Gaussian,
+    sample: sample,
+    score: score
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/improperUniform.js

@@ -1,0 +1,18 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var ImproperUniform = base.makeDistributionType({
+    name: 'ImproperUniform',
+    desc: 'Improper continuous uniform distribution which has probability one everywhere.',
+    params: [],
+    nodoc: true,
+    nohelper: true,
+    mixins: [base.continuousSupport],
+    sample: function () {
+        throw new Error('cannot sample from this improper distribution.');
+    },
+    score: function (val) {
+        return 0;
+    }
+});
+module.exports = { ImproperUniform: ImproperUniform };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/index.js

@@ -1,0 +1,168 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var util = require('../util');
+var base = require('./base');
+var distributions = _.chain([
+    [
+        'Bernoulli',
+        require('./bernoulli')
+    ],
+    [
+        'Beta',
+        require('./beta')
+    ],
+    [
+        'Binomial',
+        require('./binomial')
+    ],
+    [
+        'Categorical',
+        require('./categorical')
+    ],
+    [
+        'Cauchy',
+        require('./cauchy')
+    ],
+    [
+        'Delta',
+        require('./delta')
+    ],
+    [
+        'DiagCovGaussian',
+        require('./diagCovGaussian')
+    ],
+    [
+        'Dirichlet',
+        require('./dirichlet')
+    ],
+    [
+        'Discrete',
+        require('./discrete')
+    ],
+    [
+        'Exponential',
+        require('./exponential')
+    ],
+    [
+        'Gamma',
+        require('./gamma')
+    ],
+    [
+        'Gaussian',
+        require('./gaussian')
+    ],
+    [
+        'ImproperUniform',
+        require('./improperUniform')
+    ],
+    [
+        'IspNormal',
+        require('./ispNormal')
+    ],
+    [
+        'KDE',
+        require('./kde')
+    ],
+    [
+        'Laplace',
+        require('./laplace')
+    ],
+    [
+        'LogisticNormal',
+        require('./logisticNormal')
+    ],
+    [
+        'LogitNormal',
+        require('./logitNormal')
+    ],
+    [
+        'LogNormal',
+        require('./logNormal')
+    ],
+    [
+        'Marginal',
+        require('./marginal')
+    ],
+    [
+        'Mixture',
+        require('./mixture')
+    ],
+    [
+        'Multinomial',
+        require('./multinomial')
+    ],
+    [
+        'MultivariateBernoulli',
+        require('./multivariateBernoulli')
+    ],
+    [
+        'MultivariateGaussian',
+        require('./multivariateGaussian')
+    ],
+    [
+        'Poisson',
+        require('./poisson')
+    ],
+    [
+        'RandomInteger',
+        require('./randomInteger')
+    ],
+    [
+        'SampleBasedMarginal',
+        require('./sampleBasedMarginal')
+    ],
+    [
+        'TensorGaussian',
+        require('./tensorGaussian')
+    ],
+    [
+        'TensorLaplace',
+        require('./tensorLaplace')
+    ],
+    [
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/ispNormal.js

@@ -1,0 +1,53 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var gaussian = require('./gaussian');
+var Gaussian = gaussian.Gaussian;
+var IspNormal = base.makeDistributionType({
+    name: 'IspNormal',
+    nodoc: true,
+    desc: 'A distribution over positive reals obtained by mapping a Gaussian ' + 'distributed variable through the softplus function.',
+    params: [
+        {
+            name: 'mu',
+            desc: 'location',
+            type: types.unboundedReal
+        },
+        {
+            name: 'sigma',
+            desc: 'scale',
+            type: types.positiveReal
+        }
+    ],
+    mixins: [base.continuousSupport],
+    sample: function () {
+        var mu = ad.value(this.params.mu);
+        var sigma = ad.value(this.params.sigma);
+        return Math.log(Math.exp(gaussian.sample(mu, sigma)) + 1);
+    },
+    score: function (val) {
+        var mu = this.params.mu;
+        var sigma = this.params.sigma;
+        var x = ad.scalar.log(ad.scalar.sub(ad.scalar.exp(val), 1));
+        return ad.scalar.sub(ad.scalar.add(gaussian.score(mu, sigma, x), val), x);
+    },
+    base: function () {
+        return new Gaussian({
+            mu: 0,
+            sigma: 1
+        });
+    },
+    transform: function (x) {
+        var mu = this.params.mu;
+        var sigma = this.params.sigma;
+        return ad.scalar.log(ad.scalar.add(ad.scalar.exp(ad.scalar.add(ad.scalar.mul(x, sigma), mu)), 1));
+    },
+    support: function () {
+        return {
+            lower: 0,
+            upper: Infinity
+        };
+    }
+});
+module.exports = { IspNormal: IspNormal };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/kde.js

@@ -1,0 +1,94 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var Tensor = require('../tensor');
+var stats = require('../math/statistics');
+var numeric = require('../math/numeric');
+var gaussian = require('./gaussian');
+var diagCovGaussian = require('./diagCovGaussian');
+var kernels = {
+    gaussian: {
+        dataType: types.unboundedReal,
+        widthType: types.positiveReal,
+        sample: gaussian.sample,
+        score: gaussian.score,
+        defaultWidth: function (data) {
+            var sd = stats.sd(data);
+            var n = data.length;
+            var width = 1.06 * sd * Math.pow(n, -0.2);
+            return width;
+        }
+    },
+    mvGaussian: {
+        dataType: types.unboundedVector,
+        widthType: types.positiveVectorCB,
+        sample: diagCovGaussian.sample,
+        score: diagCovGaussian.score,
+        defaultWidth: function (data) {
+            var d = data[0].dims[0];
+            var n = data.length;
+            var mean = data.reduce(function (acc, x) {
+                return acc.add(x);
+            }).div(n);
+            var sd = data.reduce(function (acc, x) {
+                return acc.add(x.sub(mean).pow(2));
+            }, new Tensor(data[0].dims)).div(n).sqrt();
+            return sd.mul(Math.pow(4 / (d + 2), 1 / (d + 4)) * Math.pow(n, -1 / (d + 4)));
+        }
+    }
+};
+var KDE = base.makeDistributionType({
+    name: 'KDE',
+    desc: 'A distribution based on a kernel density estimate of ``data``. ' + 'A Gaussian kernel is used, and both real and vector valued data are supported. ' + 'When the data are vector valued, ``width`` should be a vector specifying the kernel ' + 'width for each dimension of the data. ' + 'When ``width`` is omitted, Silverman\'s rule of thumb ' + 'is used to select a kernel width. This rule assumes the data are ' + 'approximately Gaussian distributed. When this assumption does not hold, a ``width`` ' + 'should be specified in order to obtain sensible results.',
+    params: [
+        {
+            name: 'data',
+            desc: 'data array'
+        },
+        {
+            name: 'width',
+            desc: 'kernel width',
+            optional: true
+        }
+    ],
+    wikipedia: 'Kernel_density_estimation',
+    nohelper: true,
+    mixins: [base.continuousSupport],
+    constructor: function () {
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/laplace.js

@@ -1,0 +1,58 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+function sample(location, scale) {
+    var z = util.random();
+    var u = z - 0.5;
+    return location - scale * Math.sign(u) * Math.log(1 - 2 * Math.abs(u));
+}
+function score(location, scale, x) {
+    return ad.scalar.mul(ad.scalar.neg(1), ad.scalar.add(ad.scalar.log(ad.scalar.mul(2, scale)), ad.scalar.div(ad.scalar.abs(ad.scalar.sub(x, location)), scale)));
+}
+var Laplace = base.makeDistributionType({
+    name: 'Laplace',
+    desc: 'Distribution over ``[-Infinity, Infinity]``',
+    params: [
+        {
+            name: 'location',
+            desc: '',
+            type: types.unboundedReal
+        },
+        {
+            name: 'scale',
+            desc: '',
+            type: types.positiveReal
+        }
+    ],
+    wikipedia: true,
+    mixins: [base.continuousSupport],
+    sample: function () {
+        return sample(ad.value(this.params.location), ad.value(this.params.scale));
+    },
+    score: function (val) {
+        return score(this.params.location, this.params.scale, val);
+    },
+    base: function () {
+        return new Laplace({
+            location: 0,
+            scale: 1
+        });
+    },
+    transform: function (x) {
+        var location = this.params.location;
+        var scale = this.params.scale;
+        return ad.scalar.add(ad.scalar.mul(scale, x), location);
+    },
+    support: function () {
+        return {
+            lower: -Infinity,
+            upper: Infinity
+        };
+    }
+});
+module.exports = {
+    Laplace: Laplace,
+    sample: sample
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/logNormal.js

@@ -1,0 +1,51 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var gaussian = require('./gaussian');
+var LOG_2PI = numeric.LOG_2PI;
+function score(mu, sigma, x) {
+    var logx = ad.scalar.log(x);
+    return ad.scalar.sub(ad.scalar.sub(ad.scalar.neg(logx), ad.scalar.log(sigma)), ad.scalar.mul(0.5, ad.scalar.add(LOG_2PI, ad.scalar.div(ad.scalar.mul(ad.scalar.sub(logx, mu), ad.scalar.sub(logx, mu)), ad.scalar.mul(sigma, sigma)))));
+}
+function sample(mu, sigma) {
+    var gaussian_sample = gaussian.sample(mu, sigma);
+    return Math.exp(gaussian_sample);
+}
+var LogNormal = base.makeDistributionType({
+    name: 'LogNormal',
+    desc: 'Distribution over non-negative reals where the log of the random ' + 'variable is normally distributed.',
+    params: [
+        {
+            name: 'mu',
+            desc: 'mean',
+            type: types.unboundedReal
+        },
+        {
+            name: 'sigma',
+            desc: 'standard deviation',
+            type: types.positiveReal
+        }
+    ],
+    wikipedia: 'Log-normal_distribution',
+    mixins: [base.continuousSupport],
+    sample: function () {
+        return sample(ad.value(this.params.mu), ad.value(this.params.sigma));
+    },
+    score: function (x) {
+        return score(this.params.mu, this.params.sigma, x);
+    },
+    support: function () {
+        return {
+            lower: 0,
+            upper: Infinity
+        };
+    }
+});
+module.exports = {
+    LogNormal: LogNormal,
+    sample: sample,
+    score: score
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/logisticNormal.js

@@ -1,0 +1,71 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var diagCovGaussian = require('./diagCovGaussian');
+var TensorGaussian = require('./tensorGaussian').TensorGaussian;
+var LogisticNormal = base.makeDistributionType({
+    name: 'LogisticNormal',
+    desc: 'A distribution over probability vectors obtained by transforming a random variable ' + 'drawn from ``DiagCovGaussian({mu: mu, sigma: sigma})``. If ``mu`` and ``sigma`` have length ``d`` ' + 'then the distribution is over probability vectors of length ``d+1``.',
+    params: [
+        {
+            name: 'mu',
+            desc: 'mean',
+            type: types.unboundedVector
+        },
+        {
+            name: 'sigma',
+            desc: 'standard deviations',
+            type: types.positiveVector
+        }
+    ],
+    wikipedia: 'Logit-normal_distribution#Multivariate_generalization',
+    mixins: [
+        base.continuousSupport,
+        base.noHMC
+    ],
+    constructor: function () {
+        var _mu = ad.value(this.params.mu);
+        var _sigma = ad.value(this.params.sigma);
+        if (!util.tensorEqDim0(_mu, _sigma)) {
+            throw new Error(this.meta.name + ': mu and sigma should have the same length.');
+        }
+    },
+    sample: function () {
+        return numeric.squishToProbSimplex(diagCovGaussian.sample(ad.value(this.params.mu), ad.value(this.params.sigma)));
+    },
+    score: function (val) {
+        var mu = this.params.mu;
+        var sigma = this.params.sigma;
+        var _mu = ad.value(mu);
+        var _val = ad.value(val);
+        if (!util.isVector(_val) || _val.dims[0] - 1 !== _mu.dims[0]) {
+            return -Infinity;
+        }
+        var d = _mu.dims[0];
+        var u = ad.tensor.reshape(ad.tensor.range(val, 0, d), [
+            d,
+            1
+        ]);
+        var u_last = ad.tensor.get(val, d);
+        var inv = ad.tensor.log(ad.tensor.div(u, u_last));
+        var normScore = diagCovGaussian.score(mu, sigma, inv);
+        return ad.scalar.sub(normScore, ad.tensor.sumreduce(ad.tensor.log(val)));
+    },
+    base: function () {
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/logitNormal.js

@@ -1,0 +1,70 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var gaussian = require('./gaussian');
+var Gaussian = gaussian.Gaussian;
+var LogitNormal = base.makeDistributionType({
+    name: 'LogitNormal',
+    desc: 'A distribution over ``(a,b)`` obtained by scaling and shifting a standard logit-normal.',
+    params: [
+        {
+            name: 'mu',
+            desc: 'location',
+            type: types.unboundedReal
+        },
+        {
+            name: 'sigma',
+            desc: 'scale',
+            type: types.positiveReal
+        },
+        {
+            name: 'a',
+            desc: 'lower bound',
+            type: types.unboundedReal
+        },
+        {
+            name: 'b',
+            desc: 'upper bound (>a)',
+            type: types.unboundedReal
+        }
+    ],
+    wikipedia: 'Logit-normal_distribution',
+    mixins: [base.continuousSupport],
+    sample: function () {
+        var a = ad.value(this.params.a);
+        var b = ad.value(this.params.b);
+        var mu = ad.value(this.params.mu);
+        var sigma = ad.value(this.params.sigma);
+        var x = gaussian.sample(mu, sigma);
+        return ad.scalar.sigmoid(x) * (b - a) + a;
+    },
+    score: function (val) {
+        var a = this.params.a;
+        var b = this.params.b;
+        var y = ad.scalar.div(ad.scalar.sub(val, a), ad.scalar.sub(b, a));
+        var x = ad.scalar.log(ad.scalar.div(y, ad.scalar.sub(1, y)));
+        var gaussScore = gaussian.score(this.params.mu, this.params.sigma, x);
+        return ad.scalar.sub(gaussScore, ad.scalar.log(ad.scalar.mul(ad.scalar.mul(y, ad.scalar.sub(1, y)), ad.scalar.sub(b, a))));
+    },
+    base: function () {
+        return new Gaussian({
+            mu: 0,
+            sigma: 1
+        });
+    },
+    transform: function (x) {
+        var a = this.params.a;
+        var b = this.params.b;
+        var mu = this.params.mu;
+        var sigma = this.params.sigma;
+        return ad.scalar.add(ad.scalar.mul(ad.scalar.sigmoid(ad.scalar.add(ad.scalar.mul(x, sigma), mu)), ad.scalar.sub(b, a)), a);
+    },
+    support: function () {
+        return {
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/marginal.js

@@ -1,0 +1,65 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var assert = require('assert');
+var util = require('../util');
+var base = require('./base');
+var Marginal = base.makeDistributionType({
+    name: 'Marginal',
+    nodoc: true,
+    nohelper: true,
+    params: [{ name: 'dist' }],
+    mixins: [base.finiteSupport],
+    constructor: function () {
+        var norm = _.reduce(this.params.dist, function (acc, obj) {
+            return ad.scalar.add(acc, obj.prob);
+        }, 0);
+        assert.ok(ad.scalar.lt(ad.scalar.abs(ad.scalar.sub(1, norm)), 1e-8), 'Expected marginal distribution to be normalized.');
+        this.supp = _.map(this.params.dist, function (obj) {
+            return obj.val;
+        });
+        this.getDist = function () {
+            return this.params.dist;
+        };
+    },
+    sample: function () {
+        var x = util.random();
+        var dist = this.params.dist;
+        var probAccum = 0;
+        for (var i in dist) {
+            if (dist.hasOwnProperty(i)) {
+                probAccum = ad.scalar.add(probAccum, dist[i].prob);
+                if (ad.scalar.lt(x, probAccum)) {
+                    return dist[i].val;
+                }
+            }
+        }
+        return this.params.dist[i].val;
+    },
+    score: function (val) {
+        var obj = this.params.dist[util.serialize(val)];
+        return obj ? ad.scalar.log(obj.prob) : ad.scalar.neg(Infinity);
+    },
+    support: function () {
+        return this.supp;
+    },
+    print: function () {
+        return print(this.params.dist);
+    }
+});
+function print(dist) {
+    return 'Marginal:\n' + _.map(dist, function (obj, val) {
+        return [
+            val,
+            obj.prob
+        ];
+    }).sort(function (a, b) {
+        return b[1] - a[1];
+    }).map(function (pair) {
+        return '    ' + pair[0] + ' : ' + pair[1];
+    }).join('\n');
+}
+module.exports = {
+    Marginal: Marginal,
+    print: print
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/mixture.js

@@ -1,0 +1,84 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var base = require('./base');
+var types = require('../types');
+var numeric = require('../math/numeric');
+var util = require('../util');
+var Discrete = require('./discrete').Discrete;
+function continuousSupportEq(s1, s2) {
+    return s1 === s2 || s1 !== undefined && s2 !== undefined && s1.lower === s2.lower && s1.upper === s2.upper;
+}
+function unionDiscreteSupports(supports) {
+    return _.chain(supports).flatten().uniqWith(supportElemEq).value();
+}
+function supportElemEq(x, y) {
+    return util.serialize(x) === util.serialize(y);
+}
+var Mixture = base.makeDistributionType({
+    name: 'Mixture',
+    desc: 'A finite mixture of distributions. ' + 'The component distributions should be either all discrete or all continuous. ' + 'All continuous distributions should share a common support.',
+    params: [
+        {
+            name: 'dists',
+            desc: 'array of component distributions'
+        },
+        {
+            name: 'ps',
+            desc: 'component probabilities (can be unnormalized)',
+            type: types.nonNegativeVectorOrRealArray
+        }
+    ],
+    wikipedia: false,
+    constructor: function () {
+        var dists = this.params.dists;
+        var ps = this.params.ps;
+        if (!_.isArray(dists)) {
+            throw new Error('Parameter dists should be an array.');
+        }
+        if (dists.length !== ad.value(ps).length) {
+            throw new Error('Parameters ps and dists should have the same length.');
+        }
+        if (dists.length === 0) {
+            throw new Error('Parameters ps and dists should be non-empty.');
+        }
+        if (!_.every(dists, base.isDist)) {
+            throw new Error('Parameter dists should be an array of distributions.');
+        }
+        this.isContinuous = dists[0].isContinuous;
+        var support_0 = this.isContinuous ? dists[0].support && dists[0].support() : undefined;
+        for (var i = 1; i < dists.length; i++) {
+            var dist_i = dists[i];
+            if (dist_i.isContinuous !== this.isContinuous) {
+                throw new Error('Mixtures combining discrete and continuous distributions are not supported.');
+            }
+            if (this.isContinuous) {
+                var support_i = dist_i.support && dist_i.support();
+                if (!continuousSupportEq(support_0, support_i)) {
+                    throw new Error('All continuous distributions should have the same support.');
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/multinomial.js

@@ -1,0 +1,89 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var base = require('./base');
+var types = require('../types');
+var numeric = require('../math/numeric');
+var discrete = require('./discrete');
+function zeros(n) {
+    var a = new Array(n);
+    for (var i = 0; i < n; i++) {
+        a[i] = 0;
+    }
+    return a;
+}
+function sample(theta, n) {
+    var a = zeros(theta.length);
+    for (var i = 0; i < n; i++) {
+        a[discrete.sample(theta)]++;
+    }
+    return a;
+}
+var Multinomial = base.makeDistributionType({
+    name: 'Multinomial',
+    desc: 'Distribution over counts for ``n`` independent ``Discrete({ps: ps})`` trials.',
+    params: [
+        {
+            name: 'ps',
+            desc: 'probabilities',
+            type: types.probabilityArray
+        },
+        {
+            name: 'n',
+            desc: 'number of trials',
+            type: types.positiveInt
+        }
+    ],
+    wikipedia: true,
+    mixins: [base.finiteSupport],
+    sample: function () {
+        return sample(this.params.ps.map(ad.value), this.params.n);
+    },
+    score: function (val) {
+        if (ad.scalar.pneq(numeric.sum(val), this.params.n)) {
+            return ad.scalar.neg(Infinity);
+        }
+        var x = [];
+        var y = [];
+        for (var i = 0; ad.scalar.lt(i, this.params.ps.length); i++) {
+            x[i] = numeric.lnfact(val[i]);
+            y[i] = ad.scalar.peq(val[i], 0) ? 0 : ad.scalar.mul(val[i], ad.scalar.log(this.params.ps[i]));
+        }
+        return ad.scalar.add(ad.scalar.sub(numeric.lnfact(this.params.n), numeric.sum(x)), numeric.sum(y));
+    },
+    support: function () {
+        var combinations = allDiscreteCombinations(this.params.n, this.params.ps, [], 0);
+        var toHist = function (l) {
+            return buildHistogramFromCombinations(l, this.params.ps);
+        }.bind(this);
+        var hists = combinations.map(toHist);
+        return hists;
+    }
+});
+function allDiscreteCombinations(k, states, got, pos) {
+    var support = [];
+    if (got.length == k) {
+        return [_.clone(got)];
+    }
+    for (var i = pos; i < states.length; i++) {
+        got.push(i);
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/multivariateBernoulli.js

@@ -1,0 +1,62 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var assert = require('assert');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var Tensor = require('../tensor');
+function mvBernoulliScore(ps, x) {
+    var _x = ad.value(x);
+    var _ps = ad.value(ps);
+    if (!util.isVector(_x) || !util.tensorEqDim0(_x, _ps)) {
+        return -Infinity;
+    }
+    var xSub1 = ad.tensor.sub(x, 1);
+    var pSub1 = ad.tensor.sub(ps, 1);
+    return ad.tensor.sumreduce(ad.tensor.log(ad.tensor.add(ad.tensor.mul(x, ps), ad.tensor.mul(xSub1, pSub1))));
+}
+var MultivariateBernoulli = base.makeDistributionType({
+    name: 'MultivariateBernoulli',
+    desc: 'Distribution over a vector of independent Bernoulli variables. Each element ' + 'of the vector takes on a value in ``{0, 1}``. Note that this differs from ``Bernoulli`` which ' + 'has support ``{true, false}``.',
+    params: [{
+            name: 'ps',
+            desc: 'probabilities',
+            type: types.unitIntervalVector
+        }],
+    mixins: [base.finiteSupport],
+    sample: function () {
+        var ps = ad.value(this.params.ps);
+        var d = ps.dims[0];
+        var x = new Tensor([
+            d,
+            1
+        ]);
+        var n = x.length;
+        while (n--) {
+            x.data[n] = util.random() < ps.data[n];
+        }
+        return x;
+    },
+    score: function (x) {
+        return mvBernoulliScore(this.params.ps, x);
+    },
+    support: function () {
+        var dims = this.params.ps.dims;
+        var d = dims[0];
+        var n = Math.pow(2, d);
+        return _.times(n, function (x) {
+            return new Tensor(dims).fromFlatArray(toBinaryArray(x, d));
+        });
+    }
+});
+function toBinaryArray(x, length) {
+    assert.ok(x >= 0 && x < Math.pow(2, length));
+    var arr = [];
+    for (var i = 0; i < length; i++) {
+        arr.push(x % 2);
+        x = x >> 1;
+    }
+    return arr;
+}
+module.exports = { MultivariateBernoulli: MultivariateBernoulli };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/multivariateGaussian.js

@@ -1,0 +1,87 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var Tensor = require('../tensor');
+var numeric = require('../math/numeric');
+var gaussian = require('./gaussian');
+var TensorGaussian = require('./tensorGaussian').TensorGaussian;
+var T = ad.tensor;
+var LOG_2PI = numeric.LOG_2PI;
+function sample(mu, cov) {
+    var d = mu.dims[0];
+    var z = new Tensor([
+        d,
+        1
+    ]);
+    for (var i = 0; i < d; i++) {
+        z.data[i] = gaussian.sample(0, 1);
+    }
+    var L = cov.cholesky();
+    return L.dot(z).add(mu);
+}
+function score(mu, cov, x) {
+    var _x = ad.value(x);
+    var _mu = ad.value(mu);
+    if (!util.isVector(_x) || !util.tensorEqDim0(_x, _mu)) {
+        return -Infinity;
+    }
+    var d = _mu.dims[0];
+    var dLog2Pi = d * LOG_2PI;
+    var det = ad.tensor.determinant(cov);
+    if (ad.value(det) <= 0) {
+        throw new Error('The covariance matrix is not positive definite.');
+    }
+    var logDetCov = ad.scalar.log(det);
+    var z = ad.tensor.sub(x, mu);
+    var zT = ad.tensor.transpose(z);
+    var prec = ad.tensor.inverse(cov);
+    return ad.scalar.mul(-0.5, ad.scalar.add(dLog2Pi, ad.scalar.add(logDetCov, ad.tensor.get(ad.tensor.dot(ad.tensor.dot(zT, prec), z), 0))));
+}
+var MultivariateGaussian = base.makeDistributionType({
+    name: 'MultivariateGaussian',
+    desc: 'Multivariate Gaussian distribution with full covariance matrix. ' + 'If ``mu`` has length d and ``cov`` is a ``d``-by-``d`` matrix, ' + 'then the distribution is over vectors of length ``d``.',
+    params: [
+        {
+            name: 'mu',
+            desc: 'mean',
+            type: types.unboundedVector
+        },
+        {
+            name: 'cov',
+            desc: 'covariance',
+            type: types.posDefMatrix
+        }
+    ],
+    wikipedia: 'Multivariate_normal_distribution',
+    mixins: [base.continuousSupport],
+    constructor: function () {
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/poisson.js

@@ -1,0 +1,48 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var gamma = require('./gamma');
+var binomial = require('./binomial');
+function sample(mu) {
+    var k = 0;
+    while (mu > 10) {
+        var m = Math.floor(7 / 8 * mu);
+        var x = gamma.sample(m, 1);
+        if (x >= mu) {
+            return k + binomial.sample(mu / x, m - 1);
+        } else {
+            mu -= x;
+            k += m;
+        }
+    }
+    var emu = Math.exp(-mu);
+    var p = 1;
+    do {
+        p *= util.random();
+        k++;
+    } while (p > emu);
+    return k - 1;
+}
+var Poisson = base.makeDistributionType({
+    name: 'Poisson',
+    desc: 'Distribution over integers.',
+    params: [{
+            name: 'mu',
+            desc: 'mean',
+            type: types.positiveReal
+        }],
+    wikipedia: true,
+    sample: function () {
+        return sample(ad.value(this.params.mu));
+    },
+    score: function (val) {
+        return ad.scalar.sub(ad.scalar.sub(ad.scalar.mul(val, ad.scalar.log(this.params.mu)), this.params.mu), numeric.lnfact(val));
+    }
+});
+module.exports = {
+    Poisson: Poisson,
+    sample: sample
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/randomInteger.js

@@ -1,0 +1,28 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var RandomInteger = base.makeDistributionType({
+    name: 'RandomInteger',
+    desc: 'Uniform distribution over ``{0,1,...,n-1}``',
+    params: [{
+            name: 'n',
+            desc: 'number of possible values',
+            type: types.positiveInt
+        }],
+    wikipedia: 'Uniform_distribution_(discrete)',
+    mixins: [base.finiteSupport],
+    sample: function () {
+        return Math.floor(util.random() * this.params.n);
+    },
+    score: function (val) {
+        var inSupport = ad.scalar.peq(val, ad.scalar.floor(val)) && ad.scalar.leq(0, val) && ad.scalar.lt(val, this.params.n);
+        return inSupport ? ad.scalar.neg(ad.scalar.log(this.params.n)) : ad.scalar.neg(Infinity);
+    },
+    support: function () {
+        return _.range(this.params.n);
+    }
+});
+module.exports = { RandomInteger: RandomInteger };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/sampleBasedMarginal.js

@@ -1,0 +1,67 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var base = require('./base');
+var util = require('../util');
+var marginal = require('./marginal');
+var SampleBasedMarginal = base.makeDistributionType({
+    name: 'SampleBasedMarginal',
+    nodoc: true,
+    nohelper: true,
+    params: [{ name: 'samples' }],
+    mixins: [base.finiteSupport],
+    constructor: function () {
+        if (!_.isArray(this.params.samples) || this.params.samples.length === 0) {
+            throw new Error('Expected samples to be a non-empty array.');
+        }
+        this.samples = this.params.samples;
+        this.getDist = function () {
+            if (this._cacheddist) {
+                return this._cacheddist;
+            } else {
+                var dist = {};
+                this.params.samples.forEach(function (obj) {
+                    var val = obj.value;
+                    var key = util.serialize(val);
+                    if (dist[key] === undefined) {
+                        dist[key] = {
+                            val: val,
+                            prob: 0
+                        };
+                    }
+                    dist[key].prob += 1;
+                });
+                var n = this.params.samples.length;
+                _.each(dist, function (obj) {
+                    obj.prob /= n;
+                });
+                this._cacheddist = dist;
+                return dist;
+            }
+        };
+    },
+    sample: function () {
+        var n = this.params.samples.length;
+        return this.params.samples[Math.floor(util.random() * n)].value;
+    },
+    score: function (val) {
+        var key = util.serialize(val);
+        var obj = this.getDist()[key];
+        return obj === undefined ? -Infinity : Math.log(obj.prob);
+    },
+    support: function () {
+        if (this.params.samples.length === 1) {
+            return [this.params.samples[0].value];
+        } else if (this._cachedsupport) {
+            return this._cachedsupport;
+        } else {
+            var support = _.map(this.getDist(), _.property('val'));
+            this._cachedsupport = support;
+            return support;
+        }
+    },
+    print: function () {
+        return marginal.print(this.getDist());
+    }
+});
+module.exports = { SampleBasedMarginal: SampleBasedMarginal };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/tensorGaussian.js

@@ -1,0 +1,79 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var Tensor = require('../tensor');
+var numeric = require('../math/numeric');
+var gaussian = require('./gaussian');
+var LOG_2PI = numeric.LOG_2PI;
+function sample(mu, sigma, dims) {
+    var x = new Tensor(dims);
+    var n = x.length;
+    while (n--) {
+        x.data[n] = gaussian.sample(mu, sigma);
+    }
+    return x;
+}
+function score(mu, sigma, dims, x) {
+    var _x = ad.value(x);
+    if (!util.isTensor(_x) || !_.isEqual(_x.dims, dims)) {
+        return -Infinity;
+    }
+    var d = _x.length;
+    var dLog2Pi = d * LOG_2PI;
+    var _2dLogSigma = ad.scalar.mul(2 * d, ad.scalar.log(sigma));
+    var sigma2 = ad.scalar.pow(sigma, 2);
+    var xSubMu = ad.tensor.sub(x, mu);
+    var z = ad.scalar.div(ad.tensor.sumreduce(ad.tensor.mul(xSubMu, xSubMu)), sigma2);
+    return ad.scalar.mul(-0.5, ad.scalar.sum(dLog2Pi, _2dLogSigma, z));
+}
+var TensorGaussian = base.makeDistributionType({
+    name: 'TensorGaussian',
+    desc: 'Distribution over a tensor of independent Gaussian variables.',
+    params: [
+        {
+            name: 'mu',
+            desc: 'mean',
+            type: types.unboundedReal
+        },
+        {
+            name: 'sigma',
+            desc: 'standard deviation',
+            type: types.positiveReal
+        },
+        {
+            name: 'dims',
+            desc: 'dimension of tensor',
+            type: types.array(types.positiveInt)
+        }
+    ],
+    mixins: [base.continuousSupport],
+    sample: function () {
+        var mu = ad.value(this.params.mu);
+        var sigma = ad.value(this.params.sigma);
+        var dims = this.params.dims;
+        return sample(mu, sigma, dims);
+    },
+    score: function (x) {
+        return score(this.params.mu, this.params.sigma, this.params.dims, x);
+    },
+    base: function () {
+        var dims = this.params.dims;
+        return new TensorGaussian({
+            mu: 0,
+            sigma: 1,
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/tensorLaplace.js

@@ -1,0 +1,72 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var Tensor = require('../tensor');
+var laplace = require('./laplace');
+var T = ad.tensor;
+function sample(location, scale, dims) {
+    var x = new Tensor(dims);
+    var n = x.length;
+    while (n--) {
+        x.data[n] = laplace.sample(location, scale);
+    }
+    return x;
+}
+function score(location, scale, dims, x) {
+    var _x = ad.value(x);
+    if (!util.isTensor(_x) || !_.isEqual(_x.dims, dims)) {
+        return ad.scalar.neg(Infinity);
+    }
+    var l = _x.length;
+    var ln2b = ad.scalar.mul(l, ad.scalar.log(ad.scalar.mul(2, scale)));
+    var xMuB = ad.scalar.div(T.sumreduce(T.abs(T.sub(x, location))), scale);
+    return ad.scalar.mul(ad.scalar.neg(1), ad.scalar.add(ln2b, xMuB));
+}
+var TensorLaplace = base.makeDistributionType({
+    name: 'TensorLaplace',
+    desc: 'Distribution over a tensor of independent Laplace variables.',
+    params: [
+        {
+            name: 'location',
+            desc: '',
+            type: types.unboundedReal
+        },
+        {
+            name: 'scale',
+            desc: '',
+            type: types.positiveReal
+        },
+        {
+            name: 'dims',
+            desc: 'dimension of tensor',
+            type: types.array(types.positiveInt)
+        }
+    ],
+    mixins: [base.continuousSupport],
+    sample: function () {
+        var location = ad.value(this.params.location);
+        var scale = ad.value(this.params.scale);
+        var dims = this.params.dims;
+        return sample(location, scale, dims);
+    },
+    score: function (x) {
+        return score(this.params.location, this.params.scale, this.params.dims, x);
+    },
+    base: function () {
+        var dims = this.params.dims;
+        return new TensorLaplace({
+            location: 0,
+            scale: 1,
+            dims: dims
+        });
+    },
+    transform: function (x) {
+        var location = this.params.location;
+        var scale = this.params.scale;
+        return ad.tensor.add(ad.tensor.mul(x, scale), location);
+    }
+});
+module.exports = { TensorLaplace: TensorLaplace };

### 2019-09-06 saves/rwebppl/js/webppl/src/dists/uniform.js

@@ -1,0 +1,40 @@
+'use strict';
+var ad = require('../ad');
+var base = require('./base');
+var types = require('../types');
+var util = require('../util');
+var Uniform = base.makeDistributionType({
+    name: 'Uniform',
+    desc: 'Continuous uniform distribution over ``[a, b]``',
+    params: [
+        {
+            name: 'a',
+            desc: 'lower bound',
+            type: types.unboundedReal
+        },
+        {
+            name: 'b',
+            desc: 'upper bound (>a)',
+            type: types.unboundedReal
+        }
+    ],
+    wikipedia: 'Uniform_distribution_(continuous)',
+    mixins: [base.continuousSupport],
+    sample: function () {
+        var u = util.random();
+        return (1 - u) * ad.value(this.params.a) + u * ad.value(this.params.b);
+    },
+    score: function (val) {
+        if (ad.scalar.lt(val, this.params.a) || ad.scalar.gt(val, this.params.b)) {
+            return ad.scalar.neg(Infinity);
+        }
+        return ad.scalar.neg(ad.scalar.log(ad.scalar.sub(this.params.b, this.params.a)));
+    },
+    support: function () {
+        return {
+            lower: this.params.a,
+            upper: this.params.b
+        };
+    }
+});
+module.exports = { Uniform: Uniform };

### 2019-09-06 saves/rwebppl/js/webppl/src/hashtable.js

@@ -1,0 +1,439 @@
+/**
+ * @license jahashtable, a JavaScript implementation of a hash table. It creates a single constructor function called
+ * Hashtable in the global scope.
+ *
+ * http://www.timdown.co.uk/jshashtable/
+ * Copyright %%build:year%% Tim Down.
+ * Version: %%build:version%%
+ * Build date: %%build:date%%
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *      http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+// Don't force use of strict mode in this 3rd party module, as the use
+// of sloppy mode may be intentional.
+/* eslint strict: 'off' */
+
+var util = require('./util');
+
+var FUNCTION = 'function', STRING = 'string', UNDEFINED = undefined;
+
+// // Require Array.prototype.splice, Object.prototype.hasOwnProperty and encodeURIComponent. In environments not
+// // having these (e.g. IE <= 5), we bail out now and leave Hashtable null.
+// if (typeof encodeURIComponent == UNDEFINED ||
+//         Array.prototype.splice === UNDEFINED ||
+//         Object.prototype.hasOwnProperty === UNDEFINED) {
+//     return null;
+// }
+
+function toStr(obj) {
+  return (typeof obj == STRING) ? obj : '' + obj;
+}
+
+function hashObject(obj) {
+  var hashCode;
+  if (typeof obj == STRING) {
+    return obj;
+  } else if (typeof obj.hashCode == FUNCTION) {
+    // Check the hashCode method really has returned a string
+    hashCode = obj.hashCode();
+    return (typeof hashCode == STRING) ? hashCode : hashObject(hashCode);
+  } else {
+    return toStr(obj);
+  }
+}
+
+function merge(o1, o2) {
+  for (var i in o2) {
+    if (o2.hasOwnProperty(i)) {
+      o1[i] = o2[i];
+    }
+  }
+}
+
+function equals_fixedValueHasEquals(fixedValue, variableValue) {
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/header.js

@@ -1,0 +1,199 @@
+////////////////////////////////////////////////////////////////////
+// Inference interface
+//
+// An inference function takes the current continuation and a WebPPL
+// thunk (which itself has been transformed to take a
+// continuation). It does some kind of inference and returns a distribution
+// representing the normalized marginal distribution on return values.
+//
+// The inference function should install a coroutine object that
+// provides sample, factor, and exit.
+//
+// sample and factor are the co-routine handlers: they get call/cc'ed
+// from the wppl code to handle random stuff.
+//
+// The inference function passes exit to the wppl fn, so that it gets
+// called when the fn is exited, it can call the inference cc when
+// inference is done to contintue the program.
+
+'use strict';
+
+var assert = require('assert');
+var _ = require('lodash');
+var nn = require('adnn/nn');
+
+try {
+  var util = require('./util');
+  var dists = require('./dists');
+  var enumerate = require('./inference/enumerate');
+  var mcmc = require('./inference/mcmc');
+  var asyncpf = require('./inference/asyncpf');
+  var pmcmc = require('./inference/pmcmc');
+  var smc = require('./inference/smc');
+  var rejection = require('./inference/rejection');
+  var incrementalmh = require('./inference/incrementalmh');
+  var ais = require('./inference/ais');
+  var optimize = require('./inference/optimize');
+  var forwardSample = require('./inference/forwardSample');
+  var checkSampleAfterFactor = require('./inference/checkSampleAfterFactor');
+  var dreamSample = require('./inference/dream/sample');
+  var headerUtils = require('./headerUtils');
+  var params = require('./params/header');
+  var Query = require('./query').Query;
+  var ad = require('./ad');
+  var Tensor = require('./tensor');
+  var numeric = require('./math/numeric');
+} catch (e) {
+  if (e.code === 'MODULE_NOT_FOUND') {
+    console.error(e.message);
+    console.error('Run ./scripts/adify and try again.');
+    process.exit();
+  } else {
+    throw e;
+  }
+}
+
+module.exports = function(env) {
+
+  // Inference interface
+
+  env.defaultCoroutine = {
+    sample: function(s, k, a, dist) {
+      return k(s, dist.sample());
+    },
+    factor: function() {
+      throw new Error('factor allowed only inside inference.');
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/headerUtils.js

@@ -1,0 +1,236 @@
+'use strict';
+
+var _ = require('lodash');
+var serialize = require('./util').serialize
+var Tensor = require('./tensor');
+var LRU = require('lru-cache');
+var ad = require('./ad');
+var assert = require('assert');
+var runThunk = require('./guide').runThunk;
+
+module.exports = function(env) {
+
+  function display(s, k, a, x) {
+    return k(s, console.log(ad.valueRec(x)));
+  }
+
+  var dp = {};
+
+  // Caching for a wppl function f.
+  //
+  // Caution: if f isn't deterministic weird stuff can happen, since
+  // caching is across all uses of f, even in different execution
+  // paths.
+  dp.cache = function(f, maxSize) {
+    var c = LRU(maxSize);
+    var cf = function(s, k, a) {
+      var args = Array.prototype.slice.call(arguments, 3);
+
+      if (_.some(args, ad.isLifted)) {
+        throw new Error('Cannot cache functions of scalar/tensor arguments ' +
+                        'when performing automatic differentiation.');
+      }
+
+      var stringedArgs = serialize(args);
+      if (c.has(stringedArgs)) {
+        return k(s, c.get(stringedArgs));
+      } else {
+        var newk = function(s, r) {
+          if (c.has(stringedArgs)) {
+            // This can happen when cache is used on recursive functions
+            console.log('Already in cache:', stringedArgs);
+            if (serialize(c.get(stringedArgs)) !== serialize(r)) {
+              console.log('OLD AND NEW CACHE VALUE DIFFER!');
+              console.log('Old value:', c.get(stringedArgs));
+              console.log('New value:', r);
+            }
+          }
+          c.set(stringedArgs, r);
+          if (!maxSize && c.length === 1e4) {
+            console.log(c.length + ' function calls have been cached.');
+            console.log('The size of the cache can be limited by calling cache(f, maxSize).');
+          }
+          return k(s, r);
+        };
+        return f.apply(this, [s, newk, a].concat(args));
+      }
+    };
+    // Make the cache publicly available to facilitate checking the
+    // complexity of algorithms.
+    cf.cache = c;
+    return cf;
+  };
+
+  function cache(s, k, a, f, maxSize) {
+    return k(s, dp.cache(f, maxSize));
+  }
+
+  function apply(s, k, a, wpplFn, args) {
+    return wpplFn.apply(global, [s, k, a].concat(args));
+  }
+
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/asyncpf.js

@@ -1,0 +1,209 @@
+////////////////////////////////////////////////////////////////////
+// Asynchronous Anytime SMC.
+// http://arxiv.org/abs/1407.2864
+// bufferSize: queue size
+// numParticles: total number of particles to run
+
+'use strict';
+
+var _ = require('lodash');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var CountAggregator = require('../aggregation/CountAggregator');
+
+module.exports = function(env) {
+
+  function copyOneParticle(particle) {
+    return {
+      continuation: particle.continuation,
+      weight: particle.weight,
+      completed: particle.completed,
+      factorIndex: particle.factorIndex,
+      value: particle.value,
+      numChildrenToSpawn: 1,
+      multiplicity: particle.multiplicity,
+      store: _.clone(particle.store)
+    };
+  }
+
+  function initParticle(s, cont) {
+    return {
+      continuation: cont,
+      weight: 0,
+      completed: false,
+      factorIndex: undefined,
+      value: undefined,
+      numChildrenToSpawn: 0,
+      multiplicity: 1,
+      store: _.clone(s)
+    };
+  }
+
+  function AsyncPF(s, k, a, wpplFn, options) {
+    this.numParticles = 0;      // K_0 -- initialized here, set in run
+    this.bufferSize = options.bufferSize == undefined ? options.particles : options.bufferSize; // \rho
+    this.initNumParticles = Math.floor(this.bufferSize * (1 / 2));         // \rho_0
+    this.exitK = function(s) {return wpplFn(s, env.exit, a);};
+    this.store = s;
+    this.buffer = [];
+    for (var i = 0; i < this.initNumParticles; i++) {
+      this.buffer.push(initParticle(this.store, this.exitK));
+    }
+
+    this.obsWeights = {};
+    this.exitedParticles = 0;
+    this.hist = new CountAggregator();
+
+    // Move old coroutine out of the way and install this as current handler.
+    this.k = k;
+    this.oldCoroutine = env.coroutine;
+    env.coroutine = this;
+    this.oldStore = _.clone(s); // will be reinstated at the end
+  }
+
+  AsyncPF.prototype.run = function(numP) {
+    // allows for continuing pf
+    this.numParticles = (numP == undefined) ? this.numParticles : this.numParticles + numP;
+
+    // launch a new particle OR continue an existing one
+    var p, launchP;
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/dream/gradients.js

@@ -1,0 +1,80 @@
+'use strict';
+var ad = require('../../ad');
+var assert = require('assert');
+var _ = require('lodash');
+var guide = require('../../guide');
+module.exports = function (env) {
+    function dreamGradients(wpplFn, record, s, a, cont) {
+        this.wpplFn = wpplFn;
+        this.record = record;
+        this.s = s;
+        this.a = a;
+        this.cont = cont;
+        this.guideRequired = true;
+        this.isParamBase = true;
+        this.insideMapData = false;
+        this.oldCoroutine = env.coroutine;
+        env.coroutine = this;
+    }
+    dreamGradients.prototype = {
+        run: function () {
+            return this.estimateGradient(function (grad, objVal) {
+                env.coroutine = this.oldCoroutine;
+                return this.cont(grad, objVal);
+            }.bind(this));
+        },
+        estimateGradient: function (cont) {
+            this.paramsSeen = {};
+            this.logq = 0;
+            return this.wpplFn(_.clone(this.s), function (s, val) {
+                var objective = ad.scalar.neg(this.logq);
+                if (ad.isLifted(objective)) {
+                    objective.backprop();
+                }
+                var grads = _.mapValues(this.paramsSeen, ad.derivative);
+                return cont(grads, ad.scalar.neg(ad.value(this.logq)));
+            }.bind(this), this.a);
+        },
+        sample: function (s, k, a, dist, options) {
+            options = options || {};
+            var choice = this.record.trace.findChoice(a);
+            assert.ok(ad.scalar.pneq(choice, undefined), 'dream: No entry for this choice in the trace.');
+            var val = choice.val;
+            if (this.insideMapData) {
+                return guide.getDist(options.guide, options.noAutoGuide, dist, env, s, a, function (s, guideDist) {
+                    if (!guideDist) {
+                        throw new Error('dream: No guide distribution specified.');
+                    }
+                    this.logq = ad.scalar.add(this.logq, guideDist.score(val));
+                    return k(s, val);
+                }.bind(this));
+            } else {
+                return k(s, val);
+            }
+        },
+        factor: function (s, k, a, score) {
+            return k(s);
+        },
+        mapDataFetch: function (data, opts, a) {
+            if (this.insideMapData) {
+                throw new Error('dream: nested mapData is not supported by this estimator.');
+            }
+            this.insideMapData = true;
+            return {
+                data: this.record.data,
+                ix: null,
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/elbo.js

@@ -1,0 +1,260 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var assert = require('assert');
+var fs = require('fs');
+var util = require('../util');
+var paramStruct = require('../params/struct');
+var guide = require('../guide');
+var graph = require('./elbograph');
+var RootNode = graph.RootNode;
+var SampleNode = graph.SampleNode;
+var FactorNode = graph.FactorNode;
+var SplitNode = graph.SplitNode;
+var JoinNode = graph.JoinNode;
+module.exports = function (env) {
+    function makeELBOEstimator(options) {
+        options = util.mergeDefaults(options, {
+            samples: 1,
+            avgBaselines: true,
+            avgBaselineDecay: 0.9,
+            dumpGraph: false,
+            debugWeights: false
+        }, 'ELBO');
+        return function (wpplFn, s, a, state, step, cont) {
+            return new ELBO(wpplFn, s, a, options, state, step, cont).run();
+        };
+    }
+    function ELBO(wpplFn, s, a, options, state, step, cont) {
+        this.opts = options;
+        this.step = step;
+        this.state = state;
+        this.cont = cont;
+        this.wpplFn = wpplFn;
+        this.s = s;
+        this.a = a;
+        this.guideRequired = true;
+        this.isParamBase = true;
+        this.mapDataStack = [{ multiplier: 1 }];
+        this.mapDataIx = {};
+        if (!_.has(this.state, 'baselines')) {
+            this.state.baselines = {};
+        }
+        this.baselineUpdates = {};
+        this.oldCoroutine = env.coroutine;
+        env.coroutine = this;
+    }
+    function top(stack) {
+        return stack[stack.length - 1];
+    }
+    function checkScoreIsFinite(score, source) {
+        var _score = ad.value(score);
+        if (!isFinite(_score)) {
+            var msg = 'ELBO: The score of the previous sample under the ' + source + ' program was ' + _score + '.';
+            if (_.isNaN(_score)) {
+                msg += ' Reducing the step size may help.';
+            }
+            throw new Error(msg);
+        }
+    }
+    ELBO.prototype = {
+        run: function () {
+            var elbo = 0;
+            var grad = {};
+            return util.cpsLoop(this.opts.samples, function (i, next) {
+                this.iter = i;
+                return this.estimateGradient(function (g, elbo_i) {
+                    paramStruct.addEq(grad, g);
+                    elbo += elbo_i;
+                    return next();
+                });
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/enumerate.js

@@ -1,0 +1,178 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var PriorityQueue = require('priorityqueuejs');
+var util = require('../util');
+var ScoreAggregator = require('../aggregation/ScoreAggregator');
+module.exports = function (env) {
+    function Enumerate(store, k, a, wpplFn, options) {
+        options = util.mergeDefaults(options, {
+            maxExecutions: Infinity,
+            strategy: undefined,
+            throwOnError: true,
+            maxRuntimeInMS: Infinity,
+            maxEnumTreeSize: Infinity
+        }, 'Enumerate');
+        this.throwOnError = options.throwOnError;
+        this.maxRuntimeInMS = options.maxRuntimeInMS;
+        this.startTime = Date.now();
+        this.firstPath = true;
+        this.levelSizes = [];
+        this.maxExecutions = options.maxExecutions;
+        this.score = 0;
+        this.marginal = new ScoreAggregator();
+        this.numCompletedExecutions = 0;
+        this.store = store;
+        this.k = k;
+        this.a = a;
+        this.wpplFn = wpplFn;
+        var strategy = strategies[options.strategy] || defaultStrategy(options.maxExecutions);
+        this.queue = strategy.makeQ();
+        this.oldCoroutine = env.coroutine;
+        env.coroutine = this;
+    }
+    Enumerate.prototype.run = function () {
+        return this.wpplFn(_.clone(this.store), env.exit, this.a);
+    };
+    Enumerate.prototype.error = function (errType) {
+        var err = new Error(errType);
+        if (this.throwOnError) {
+            throw err;
+        } else {
+            return this.k(this.store, err);
+        }
+    };
+    Enumerate.prototype.nextInQueue = function () {
+        var nextState = this.queue.deq();
+        this.score = nextState.score;
+        return nextState.continuation(nextState.store, nextState.value);
+    };
+    Enumerate.prototype.enqueueContinuation = function (continuation, value, score, store) {
+        var state = {
+            continuation: continuation,
+            value: value,
+            score: score,
+            store: _.clone(store)
+        };
+        this.queue.enq(state);
+    };
+    var getSupport = function (dist, cont) {
+        if (dist.isContinuous || !dist.support) {
+            console.error(dist);
+            return env.coroutine.error('Enumerate can only be used with distributions that have finite support.');
+        }
+        var supp = dist.support();
+        if (ad.scalar.peq(supp.length, 0)) {
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/eubo.js

@@ -1,0 +1,100 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var assert = require('assert');
+var util = require('../util');
+var paramStruct = require('../params/struct');
+var guide = require('../guide');
+module.exports = function (env) {
+    function makeEUBOEstimator(options) {
+        options = util.mergeDefaults(options, {
+            batchSize: 1,
+            traces: undefined
+        }, 'EUBO');
+        if (!options.traces) {
+            throw 'Example traces required.';
+        }
+        if (options.batchSize <= 0 || options.batchSize > options.traces.length) {
+            throw 'Invalid batchSize.';
+        }
+        return function (wpplFn, s, a, state, step, cont) {
+            return new EUBO(wpplFn, s, a, options, state, step, cont).run();
+        };
+    }
+    function EUBO(wpplFn, s, a, options, state, step, cont) {
+        this.opts = options;
+        this.traces = this.opts.traces;
+        this.cont = cont;
+        this.wpplFn = wpplFn;
+        this.s = s;
+        this.a = a;
+        this.guideRequired = true;
+        this.isParamBase = true;
+        this.oldCoroutine = env.coroutine;
+        env.coroutine = this;
+    }
+    EUBO.prototype = {
+        run: function () {
+            var eubo = 0;
+            var grad = {};
+            var traces = sampleMiniBatch(this.traces, this.opts.batchSize);
+            return util.cpsForEach(function (trace, i, traces, next) {
+                return this.estimateGradient(trace, function (g, eubo_i) {
+                    paramStruct.addEq(grad, g);
+                    eubo += eubo_i;
+                    return next();
+                });
+            }.bind(this), function () {
+                paramStruct.divEq(grad, traces.length);
+                eubo /= traces.length;
+                env.coroutine = this.oldCoroutine;
+                return this.cont(grad, eubo);
+            }.bind(this), traces);
+        },
+        estimateGradient: function (trace, cont) {
+            this.trace = trace;
+            this.paramsSeen = {};
+            this.logq = 0;
+            return this.wpplFn(_.clone(this.s), function () {
+                var objective = ad.scalar.neg(this.logq);
+                objective.backprop();
+                var grads = _.mapValues(this.paramsSeen, ad.derivative);
+                var logp = ad.value(trace.score);
+                var logq = ad.value(this.logq);
+                return cont(grads, ad.scalar.sub(logp, logq));
+            }.bind(this), this.a);
+        },
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/forwardSample.js

@@ -1,0 +1,136 @@
+// Coroutine to sample from the target (ignoring factor statements) or
+// guide program.
+
+'use strict';
+
+var _ = require('lodash');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var CountAggregator = require('../aggregation/CountAggregator');
+var ad = require('../ad');
+var guide = require('../guide');
+var cb = require('./callbacks');
+
+module.exports = function(env) {
+
+  function RunForward(s, k, a, wpplFn, sampleGuide) {
+    this.s = s;
+    this.k = k;
+    this.a = a;
+    this.wpplFn = wpplFn;
+    this.sampleGuide = sampleGuide;
+
+    // Indicate that guide thunks should run.
+    this.guideRequired = sampleGuide;
+    this.isParamBase = true;
+
+    this.score = 0;
+    this.logWeight = 0;
+
+    this.oldCoroutine = env.coroutine;
+    env.coroutine = this;
+  }
+
+  RunForward.prototype = {
+
+    run: function() {
+      return this.wpplFn(_.clone(this.s), function(s, val) {
+        env.coroutine = this.oldCoroutine;
+        var ret = {val: val, score: this.score, logWeight: this.logWeight};
+        return this.k(this.s, ret);
+      }.bind(this), this.a);
+    },
+
+    sample: function(s, k, a, dist, options) {
+      var cont = function(s, dist) {
+        var val = dist.sample();
+        this.score += dist.score(val);
+        return k(s, val);
+      }.bind(this);
+
+      if (this.sampleGuide) {
+        options = options || {};
+        return guide.getDist(
+            options.guide, options.noAutoGuide, dist, env, s, a,
+            function(s, maybeGuideDist) {
+              return cont(s, maybeGuideDist || dist);
+            });
+      } else {
+        return cont(s, dist);
+      }
+    },
+
+    factor: function(s, k, a, score) {
+      if (!this.sampleGuide) {
+        var msg = 'Note that factor, condition and observe statements are ' +
+            'ignored when forward sampling.';
+        util.warn(msg, true);
+      }
+      this.logWeight += ad.value(score);
+      return k(s);
+    },
+
+    incrementalize: env.defaultCoroutine.incrementalize,
+    constructor: RunForward
+
+  };
+
+  function runForward() {
+    var coroutine = Object.create(RunForward.prototype);
+    RunForward.apply(coroutine, arguments);
+    return coroutine.run();
+  }
+
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/hmckernel.js

@@ -1,0 +1,269 @@
+// Neal, Radford M. "MCMC using Hamiltonian dynamics." Handbook of
+// Markov Chain Monte Carlo 2 (2011).
+// http://arxiv.org/abs/1206.1901
+
+'use strict';
+
+var _ = require('lodash');
+var assert = require('assert');
+var util = require('../util');
+var gaussian = require('../dists/gaussian');
+var tensorGaussian = require('../dists/tensorGaussian');
+var Trace = require('../trace');
+var ad = require('../ad');
+var Tensor = require('../tensor');
+var generic = require('../math/genericArithmetic');
+
+var addEq = generic.addEq;
+var add = generic.add;
+var mul = generic.mul;
+var sum = generic.sum;
+
+module.exports = function(env) {
+
+  function makeHMCKernel(options) {
+    options = util.mergeDefaults(options, {
+      steps: 5,
+      stepSize: 0.1
+    }, 'HMC kernel');
+    assert.ok(options.steps > 0);
+    var kernel = function(cont, oldTrace, runOpts) {
+      return new HMCKernel(cont, oldTrace, options, runOpts).run();
+    };
+    kernel.adRequired = true;
+    return kernel;
+  }
+
+  function HMCKernel(cont, oldTrace, options, runOpts) {
+    this.steps = options.steps;
+    this.stepSize = options.stepSize;
+
+    runOpts = util.mergeDefaults(runOpts, {
+      exitFactor: 0
+    });
+
+    this.exitFactor = runOpts.exitFactor;
+
+    this.cont = cont;
+    this.oldTrace = oldTrace;
+    this.a = oldTrace.baseAddress; // Support relative addressing.
+
+    this.oldCoroutine = env.coroutine;
+    env.coroutine = this;
+  }
+
+  HMCKernel.prototype.sample = function(s, k, a, dist, options) {
+    var prevChoice = this.prevTrace.findChoice(a);
+    if (!prevChoice) {
+      throw new Error('HMC does not support structural continuous variables.');
+    }
+
+    var val;
+    if (dist.isContinuous) {
+      if (dist.noHMC) {
+        throw new Error('HMC does not yet support the ' + dist.meta.name + ' distribution');
+      }
+
+      var prevVal = ad.value(prevChoice.val);
+      var _val = add(prevVal, mul(this.momentum[a], this.stepSize));
+
+      // Handle constraints.
+
+      // We only have constraints on scalar valued distributions at
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/incrementalmh.js

@@ -1,0 +1,1128 @@
+////////////////////////////////////////////////////////////////////
+// Incrementalized (i.e. caching) Lightweight MH
+
+'use strict';
+
+var _ = require('lodash');
+var assert = require('assert');
+var util = require('../util');
+var Hashtable = require('../hashtable').Hashtable
+var Query = require('../query').Query;
+var CountAggregator = require('../aggregation/CountAggregator');
+var cb = require('./callbacks');
+
+module.exports = function(env) {
+
+  var drift = require('./driftKernel')(env);
+
+  // ------------------------------------------------------------------
+
+  // Debugging output
+
+  var DEBUG = 0;
+  function debuglog(debuglevel) {
+    if (DEBUG >= debuglevel) {
+      var args = Array.prototype.slice.call(arguments, 1);
+      console.log.apply(console, args);
+    }
+  }
+
+  function tabbedlog(debuglevel, depth) {
+    if (DEBUG >= debuglevel) {
+      var args = Array.prototype.slice.call(arguments, 2);
+      var pad = '';
+      for (var i = 0; i < depth; i++) pad += '  ';
+      pad += '[' + depth + '] ';
+      console.log.apply(console, [pad].concat(args));
+    }
+  }
+
+  // ------------------------------------------------------------------
+
+  // A sort of 'copy on write' system for cache nodes
+
+  function touch(node) {
+    if (!node.__snapshot) {
+      node.coroutine.touch(node);
+      node.__snapshot = { reachable: true };
+    }
+  }
+
+  function updateProperty(node, prop, val) {
+    touch(node);
+    if (!node.__snapshot[prop])
+      node.__snapshot[prop] = node[prop];
+    node[prop] = val;
+  }
+
+  function hasSnapshotForProperty(node, prop) {
+    return node.__snapshot !== undefined &&
+           node.__snapshot[prop] !== undefined;
+  }
+
+  function restoreSnapshot(node) {
+    for (var prop in node.__snapshot) {
+      node[prop] = node.__snapshot[prop];
+    }
+    node.__snapshot = undefined;
+  }
+
+  function discardSnapshot(node) {
+    node.__snapshot = undefined;
+  }
+
+  // ------------------------------------------------------------------
+
+  // A cached distribution call
+  function DistNode(coroutine, parent, s, k, a, dist, args) {
+    this.coroutine = coroutine;
+
+    this.store = _.clone(s);
+    this.continuation = k;
+    this.address = a;
+    this.dist = dist;
+    this.args = args;
+
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/initialize.js

@@ -1,0 +1,75 @@
+'use strict';
+
+var _ = require('lodash');
+var assert = require('assert');
+var Trace = require('../trace');
+var ad = require('../ad');
+
+module.exports = function(env) {
+
+  // Returns a trace which has a non-zero probability.
+
+  var warnAfter = [1e3, 1e4, 1e5, 1e6];
+
+  function Initialize(cont, wpplFn, s, k, a, options) {
+    this.cont = cont;
+
+    this.wpplFn = wpplFn;
+    this.s = s;
+    this.k = k;
+    this.a = a;
+
+    this.ad = options.ad;
+    this.failures = 0;
+    this.oldCoroutine = env.coroutine;
+    env.coroutine = this;
+  }
+
+  Initialize.prototype.run = function() {
+    this.trace = new Trace(this.wpplFn, this.s, this.k, this.a);
+    env.query.clear();
+    return this.trace.continue();
+  };
+
+  Initialize.prototype.sample = function(s, k, a, dist, options) {
+    var _val = dist.sample();
+    var val = this.ad && dist.isContinuous ? ad.lift(_val) : _val;
+    this.trace.addChoice(dist, val, a, s, k, options);
+    return k(s, val);
+  };
+
+  Initialize.prototype.factor = function(s, k, a, score) {
+    if (ad.value(score) === -Infinity) {
+      return this.fail();
+    }
+    this.trace.score = ad.scalar.add(this.trace.score, score);
+    return k(s);
+  };
+
+  Initialize.prototype.fail = function() {
+    this.failures += 1;
+    var ix = warnAfter.indexOf(this.failures);
+    if (ix >= 0) {
+      console.log(['Initialization warning [', (ix + 1), '/', warnAfter.length,
+                   ']: Trace not initialized after ', this.failures, ' attempts.'].join(''));
+    }
+    return this.run();
+  };
+
+  Initialize.prototype.exit = function(s, val) {
+    assert.notStrictEqual(this.trace.score, -Infinity);
+    this.trace.complete(val);
+    if (this.trace.value === env.query) {
+      this.trace.value = env.query.getTable();
+    }
+    env.coroutine = this.oldCoroutine;
+    return this.cont(this.trace);
+  };
+
+  Initialize.prototype.incrementalize = env.defaultCoroutine.incrementalize;
+
+  return function(cont, wpplFn, s, k, a, options) {
+    return new Initialize(cont, wpplFn, s, k, a, options).run();
+  };
+
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/mcmc.js

@@ -1,0 +1,129 @@
+'use strict';
+
+var _ = require('lodash');
+var util = require('../util');
+var CountAggregator = require('../aggregation/CountAggregator');
+var ad = require('../ad');
+var cb = require('./callbacks');
+
+module.exports = function(env) {
+
+  var Initialize = require('./initialize')(env);
+  var kernels = require('./kernels')(env);
+
+  function MCMC(s, k, a, wpplFn, options) {
+    var options = util.mergeDefaults(options, {
+      samples: 100,
+      kernel: 'MH',
+      lag: 0,
+      burn: 0,
+      verbose: false,
+      onlyMAP: false,
+      callbacks: []
+    }, 'MCMC');
+
+    options.kernel = kernels.parseOptions(options.kernel);
+
+    var callbacks = cb.prepare(options.verbose ?
+                               [makeVMCallbackForPlatform()].concat(options.callbacks) :
+                               options.callbacks);
+    callbacks.setup(numIters(options));
+
+    var aggregator = new CountAggregator(options.onlyMAP);
+
+    var getValAndScore = options.kernel.adRequired ?
+        function(trace) {
+          return {
+            value: ad.valueRec(trace.value),
+            score: ad.value(trace.score)
+          };
+        } : _.identity;
+
+    var initialize, run, finish;
+
+    initialize = function() {
+      callbacks.initialize();
+      return Initialize(run, wpplFn, s, env.exit, a, { ad: options.kernel.adRequired });
+    };
+
+    run = function(initialTrace) {
+      initialTrace.info = { accepted: 0, total: 0 };
+      var callback = kernels.tap(function(trace) { callbacks.iteration(trace); });
+      var collectSample = kernels.tap(function(trace) {
+        var obj = getValAndScore(trace);
+        aggregator.add(obj.value, obj.score);
+        callbacks.sample({value: obj.value, score: obj.score});
+      });
+      var kernel = kernels.sequence(options.kernel, callback);
+      var chain = kernels.sequence(
+          kernels.repeat(options.burn, kernel),
+          kernels.repeat(options.samples,
+              kernels.sequence(
+                  kernels.repeat(options.lag + 1, kernel),
+                  collectSample)));
+      return chain(finish, initialTrace);
+    };
+
+    finish = function(trace) {
+      callbacks.finish(trace);
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/mh-diagnostics/diagnostics.js

@@ -1,0 +1,43 @@
+'use strict';
+
+var stats = require('../../math/statistics');
+var fs = require('fs');
+var os = require('os');
+
+// Geweke convergence test
+function geweke(traces, first, last, intervals) {
+  var first = typeof first !== 'undefined' ? first : 0.1;
+  var last = typeof last !== 'undefined' ? last : 0.5;
+  var intervals = typeof intervals !== 'undefined' ? intervals : 20;
+  if (first + last >= 1.0) {
+    throw new Error('Error: Intervals should sum to less than 1.0.');
+  }
+  var zscores = [];
+  var end = traces.length;
+  for (var i = 0; i < traces.length / 2; i = i + Math.floor((traces.length / 2) / (intervals - 1))) {
+    var firstSlice = traces.slice(i, i + Math.floor(first * (end - i)));
+    var lastSlice = traces.slice(Math.floor(end - last * (end - i)), traces.length);
+    var mu = (stats.mean(firstSlice) - stats.mean(lastSlice));
+    var zscore = mu / Math.sqrt(stats.variance(firstSlice) + stats.variance(lastSlice));
+    zscores.push([i, zscore]);
+  }
+  return zscores;
+}
+
+function run(traces) {
+  //var scores = geweke(traces);
+  //console.log('Geweke Zscores:');
+  //for (var i = 0; i < scores.length; i++) {
+  //  console.log(scores[i]);
+  //}
+
+  fs.writeFile(os.tmpdir() + 'trace.json', JSON.stringify(traces), function(err) {
+    if (err) {
+      return console.log(err);
+    }
+  });
+}
+
+module.exports = {
+  run: run
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/mhkernel.js

@@ -1,0 +1,249 @@
+'use strict';
+
+var _ = require('lodash');
+var assert = require('assert');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var ad = require('../ad');
+
+module.exports = function(env) {
+
+  var drift = require('./driftKernel')(env);
+
+  function makeMHKernel(options) {
+    options = util.mergeDefaults(options, {
+      adRequired: false,
+      permissive: false,
+      discreteOnly: false
+    }, 'MH kernel');
+    return function(cont, oldTrace, runOpts) {
+      return new MHKernel(cont, oldTrace, options, runOpts).run();
+    };
+  }
+
+  function MHKernel(cont, oldTrace, options, runOpts) {
+    this.discreteOnly = options.discreteOnly;
+    this.adRequired = options.adRequired;
+    if (!options.permissive) {
+      assert.notStrictEqual(oldTrace.score, -Infinity);
+    }
+
+    runOpts = util.mergeDefaults(runOpts, {
+      proposalBoundary: 0,
+      exitFactor: 0,
+      factorCoeff: 1,
+      allowHardFactors: true
+    });
+
+    this.proposalBoundary = runOpts.proposalBoundary;
+    this.exitFactor = runOpts.exitFactor;
+
+    this.factorCoeff = runOpts.factorCoeff;
+    assert.ok(0 <= this.factorCoeff && this.factorCoeff <= 1);
+    this.allowHardFactors = runOpts.allowHardFactors;
+
+    this.cont = cont;
+    this.oldTrace = oldTrace;
+    this.a = oldTrace.baseAddress; // Support relative addressing.
+    this.reused = {};
+
+    this.oldCoroutine = env.coroutine;
+    env.coroutine = this;
+  }
+
+  MHKernel.prototype.run = function() {
+    this.regenFrom = this.sampleRegenChoice(this.oldTrace);
+    if (this.regenFrom < 0) {
+      // Immediately return from coroutine if there are no random
+      // choices to propose to.
+      return this.continue(this.oldTrace);
+    }
+    env.query.clear();
+    this.trace = this.oldTrace.upto(this.regenFrom);
+    var regen = this.oldTrace.choiceAtIndex(this.regenFrom);
+    return this.resample(_.clone(regen.store), regen.k, regen.address, regen.dist, regen.options);
+  };
+
+  MHKernel.prototype.factor = function(s, k, a, score) {
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/pmcmc.js

@@ -1,0 +1,208 @@
+////////////////////////////////////////////////////////////////////
+// PMCMC
+
+'use strict';
+
+var _ = require('lodash');
+var discrete = require('../dists/discrete');
+var util = require('../util')
+var CountAggregator = require('../aggregation/CountAggregator');
+
+module.exports = function(env) {
+
+  function last(xs) {
+    return xs[xs.length - 1];
+  }
+
+
+  function PMCMC(s, cc, a, wpplFn, options) {
+    // Move old coroutine out of the way and install this as the
+    // current handler.
+    this.oldCoroutine = env.coroutine;
+    env.coroutine = this;
+
+    // Store continuation (will be passed dist at the end)
+    this.k = cc;
+
+    this.oldStore = s;
+
+    // Setup inference variables
+    this.particleIndex = 0;  // marks the active particle
+    this.retainedParticle = undefined;
+    this.numSweeps = options.sweeps;
+    this.sweep = 0;
+    this.wpplFn = wpplFn;
+    this.address = a;
+    this.numParticles = options.particles;
+    this.resetParticles();
+    this.hist = new CountAggregator();
+  }
+
+  PMCMC.prototype.run = function() {
+    // Run first particle
+    return this.activeContinuationWithStore();
+  };
+
+  PMCMC.prototype.resetParticles = function() {
+    var that = this;
+    // Create initial particles
+    this.particles = [];
+    var exitK = function(s) {
+      return that.wpplFn(s, env.exit, that.address);
+    };
+    for (var i = 0; i < this.numParticles; i++) {
+      var particle = {
+        continuations: [exitK],
+        stores: [that.oldStore],
+        weights: [0],
+        value: undefined
+      };
+      this.particles.push(_.clone(particle));
+    }
+  };
+
+  PMCMC.prototype.activeParticle = function() {
+    return this.particles[this.particleIndex];
+  };
+
+  PMCMC.prototype.activeContinuation = function() {
+    return last(this.activeParticle().continuations);
+  };
+
+  PMCMC.prototype.activeContinuationWithStore = function() {
+    var k = last(this.activeParticle().continuations);
+    var s = _.clone(last(this.activeParticle().stores));
+    return function() {
+      return k(s);
+    };
+  };
+
+  PMCMC.prototype.allParticlesAdvanced = function() {
+    return ((this.particleIndex + 1) === this.particles.length);
+  };
+
+  PMCMC.prototype.sample = function(s, cc, a, dist) {
+    return cc(s, dist.sample());
+  };
+
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/rejection.js

@@ -1,0 +1,135 @@
+// Rejection sampling
+//
+// maxScore: An upper bound on the total factor score per-execution.
+//
+// incremental: When true, improves efficiency by rejecting samples at factor
+// statements where possible. Requires score <= 0 for all factors across all
+// possible executions.
+
+'use strict';
+
+var _ = require('lodash');
+var util = require('../util');
+var CountAggregator = require('../aggregation/CountAggregator');
+var cb = require('./callbacks');
+
+module.exports = function(env) {
+
+  function Rejection(s, k, a, wpplFn, options) {
+    options = util.mergeDefaults(options, {
+      samples: 100,
+      maxScore: 0,
+      incremental: false,
+      throwOnError: true,
+      minSampleRate: 0,
+      callbacks: []
+    }, 'Rejection');
+
+    this.throwOnError = options.throwOnError;
+    this.minSampleRate = options.minSampleRate;
+    this.numSamplesTotal = options.samples;
+    this.startTime = Date.now();
+
+    this.numSamples = options.samples;
+    this.maxScore = options.maxScore;
+    this.incremental = options.incremental;
+    this.callbacks = cb.prepare(options.callbacks);
+    this.s = s;
+    this.k = k;
+    this.a = a;
+    this.wpplFn = wpplFn;
+    this.hist = new CountAggregator();
+    this.oldCoroutine = env.coroutine;
+    env.coroutine = this;
+
+    if (this.incremental && this.maxScore > 0) {
+      util.warn('Rejection: Reduce maxScore to zero for better performance.');
+    }
+  }
+
+  Rejection.prototype.run = function() {
+    if (!_.isNumber(this.numSamples) || this.numSamples <= 0) {
+      return this.error('"samples" should be a positive integer.');
+    }
+    var elapseSec = (Date.now() - this.startTime) / 1000.0;
+    if (this.minSampleRate > 0 && elapseSec > 2) {
+      // count the number of samples collected in ~2 secs
+      // compute number of samples per sec
+      var sampleRate = (this.numSamplesTotal - this.numSamples) / elapseSec;
+      if (sampleRate < this.minSampleRate) {
+        return this.error(sampleRate.toFixed(2) + ' samples/sec is below threshold.')
+      }
+      this.minSampleRate = 0;
+    }
+    this.scoreSoFar = 0;
+    this.threshold = this.maxScore + Math.log(util.random());
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/inference/smc.js

@@ -1,0 +1,384 @@
+'use strict';
+
+var _ = require('lodash');
+var util = require('../util');
+var numeric = require('../math/numeric');
+var discrete = require('../dists/discrete');
+var Trace = require('../trace');
+
+var assert = require('assert');
+var CountAggregator = require('../aggregation/CountAggregator');
+var ad = require('../ad');
+var guide = require('../guide');
+var cb = require('./callbacks');
+
+module.exports = function(env) {
+
+  var kernels = require('./kernels')(env);
+
+  var validImportanceOptVals = ['default', 'ignoreGuide', 'autoGuide'];
+
+  function SMC(s, k, a, wpplFn, options) {
+    var options = util.mergeDefaults(options, {
+      particles: 100,
+      rejuvSteps: 0,
+      rejuvKernel: 'MH',
+      finalRejuv: true,
+      saveTraces: false,
+      importance: 'default',
+      onlyMAP: false,
+      throwOnError: true,
+      callbacks: []
+    }, 'SMC');
+
+    if (!_.includes(validImportanceOptVals, options.importance)) {
+      var msg = options.importance + ' is not a valid importance option. ' +
+          'Valid options are: ' + validImportanceOptVals;
+      throw new Error(msg);
+    }
+    this.throwOnError = options.throwOnError;
+
+    this.rejuvKernel = kernels.parseOptions(options.rejuvKernel);
+    this.rejuvSteps = options.rejuvSteps;
+
+    this.performRejuv = this.rejuvSteps > 0;
+    this.adRequired = this.performRejuv && this.rejuvKernel.adRequired;
+    this.performFinalRejuv = this.performRejuv && options.finalRejuv;
+    this.numParticles = options.particles;
+    this.debug = options.debug;
+    this.saveTraces = options.saveTraces;
+    this.importanceOpt = options.importance;
+    this.guideRequired = options.importance !== 'ignoreGuide';
+    this.isParamBase = true;
+    this.onlyMAP = options.onlyMAP;
+    this.callbacks = cb.prepare(options.callbacks);
+
+    this.particles = [];
+    this.completeParticles = [];
+    this.particleIndex = 0;
+
+    this.step = 0;
+
+    // Create initial particles.
+    for (var i = 0; i < this.numParticles; i++) {
+      var trace = new Trace(wpplFn, s, env.exit, a);
+      this.particles.push(new Particle(trace));
+    }
+
+    this.s = s;
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/main.js

@@ -1,0 +1,307 @@
+'use strict';
+
+var fs = require('fs');
+var types = require('ast-types');
+var build = types.builders;
+var esprima = require('esprima');
+var escodegen = require('escodegen');
+var assert = require('assert');
+var _ = require('lodash');
+
+var ad = require('./transforms/ad').ad;
+var cps = require('./transforms/cps').cps;
+var addFilename = require('./transforms/addFilename').addFilename;
+var optimize = require('./transforms/optimize').optimize;
+var naming = require('./transforms/naming').naming;
+var store = require('./transforms/store').store;
+var stack = require('./transforms/stack');
+var varargs = require('./transforms/varargs').varargs;
+var trampoline = require('./transforms/trampoline').trampoline;
+var freevars = require('./transforms/freevars').freevars;
+var caching = require('./transforms/caching');
+var thunkify = require('./syntax').thunkify;
+var util = require('./util');
+var errors = require('./errors/errors');
+var params = require('./params/params');
+
+// Container for coroutine object and shared top-level
+// functions (sample, factor, exit)
+var env = {};
+
+// Make header functions globally available:
+function requireHeader(path) { requireHeaderWrapper(require(path)); }
+function requireHeaderWrapper(wrapper) { makePropertiesGlobal(wrapper(env)); }
+
+function makePropertiesGlobal(obj) {
+  for (var prop in obj) {
+    if (obj.hasOwnProperty(prop)) {
+      global[prop] = obj[prop];
+    }
+  }
+}
+
+// Explicitly call require here to ensure that browserify notices that the
+// header should be bundled.
+requireHeaderWrapper(require('./header'));
+
+function concatPrograms(programs) {
+  assert.ok(_.isArray(programs));
+  var concat = function(p0, p1) {
+    return build.program(p0.body.concat(p1.body));
+  };
+  var emptyProgram = esprima.parse('');
+  return programs.reduce(concat, emptyProgram);
+}
+
+function parse(code, filename) {
+  var ast = esprima.parse(code, {loc: true});
+  return addFilename(ast, filename);
+}
+
+function parseAll(bundles) {
+  return bundles.map(function(bundle) {
+    var ast = parse(bundle.code, bundle.filename);
+    return _.assign({ ast: ast }, bundle);
+  });
+}
+
+function headerPackage() {
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/math/numeric.js

@@ -1,0 +1,92 @@
+'use strict';
+var ad = require('../ad');
+var _ = require('lodash');
+var LOG_PI = 1.1447298858494002;
+var LOG_2PI = 1.8378770664093453;
+function sum(xs) {
+    return xs.reduce(function (a, b) {
+        return ad.scalar.add(a, b);
+    }, 0);
+}
+function _sum(xs) {
+    if (xs.length === 0) {
+        return 0;
+    } else {
+        var total = _.reduce(xs, function (a, b) {
+            return a + b;
+        });
+        return total;
+    }
+}
+function product(xs) {
+    var result = 1;
+    for (var i = 0, n = xs.length; ad.scalar.lt(i, n); i++) {
+        result = ad.scalar.mul(result, xs[i]);
+    }
+    return result;
+}
+function fact(x) {
+    var t = 1;
+    while (ad.scalar.gt(x, 1)) {
+        t = ad.scalar.mul(t, x);
+        x = ad.scalar.sub(x, 1);
+    }
+    return t;
+}
+function lnfact(x) {
+    if (ad.scalar.lt(x, 1)) {
+        x = 1;
+    }
+    if (ad.scalar.lt(x, 12)) {
+        return ad.scalar.log(fact(ad.scalar.round(x)));
+    }
+    var invx = ad.scalar.div(1, x);
+    var invx2 = ad.scalar.mul(invx, invx);
+    var invx3 = ad.scalar.mul(invx2, invx);
+    var invx5 = ad.scalar.mul(invx3, invx2);
+    var invx7 = ad.scalar.mul(invx5, invx2);
+    var sum = ad.scalar.sub(ad.scalar.mul(ad.scalar.add(x, 0.5), ad.scalar.log(x)), x);
+    sum = ad.scalar.add(sum, ad.scalar.div(ad.scalar.log(ad.scalar.mul(2, ad.scalar.PI)), 2));
+    sum = ad.scalar.add(sum, ad.scalar.sub(ad.scalar.div(invx, 12), ad.scalar.div(invx3, 360)));
+    sum = ad.scalar.add(sum, ad.scalar.sub(ad.scalar.div(invx5, 1260), ad.scalar.div(invx7, 1680)));
+    return sum;
+}
+function squishToProbSimplex(x) {
+    var d = ad.value(x).dims[0];
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/pkg.js

@@ -1,0 +1,155 @@
+'use strict';
+
+var path = require('path');
+var fs = require('fs');
+var _ = require('lodash');
+var pkginfo = require('./pkginfo');
+
+var isJsModule = function(path) {
+  try {
+    require.resolve(path);
+    return true;
+  } catch (e) {
+    return false;
+  }
+};
+
+var isNodeCoreModule = function(name) {
+  try {
+    return name === require.resolve(name);
+  } catch (e) {
+    return false;
+  }
+};
+
+var globalPkgDir = function() {
+  // USERPROFILE is intended to support Windows. This is un-tested.
+  var home = process.env.HOME || process.env.USERPROFILE;
+  return home ? path.join(home, '.webppl', 'node_modules') : '';
+};
+
+var isPath = function(s) {
+  // This isn't expected to classify any valid NPM package names as paths.
+  // https://github.com/npm/validate-npm-package-name
+  return s.indexOf(path.sep) >= 0 || s.substr(0, 1) === '.';
+};
+
+var toCamelCase = function(name) {
+  return _.chain(name.split('-')).compact().map(function(s, i) {
+    return i > 0 ? upcaseInitial(s) : s;
+  }).value().join('');
+};
+
+var upcaseInitial = function(s) {
+  if (s.length === 0) return s;
+  return s[0].toUpperCase() + s.slice(1);
+};
+
+var read = function(name_or_path, paths, verbose) {
+  var log = verbose ? function(x) { console.warn(x); return x; } : _.identity;
+
+  // Check if this is a Node core module. If so, use it.
+  if (!isPath(name_or_path) && isNodeCoreModule(name_or_path)) {
+    return log({
+      name: name_or_path,
+      js: { identifier: name_or_path, path: name_or_path },
+      headers: [],
+      wppl: []
+    });
+  }
+
+  var readFirst = function(candidates) {
+    if (candidates.length > 0) {
+      var candidate = path.resolve(candidates[0]);
+      var candidatePackagePath = path.join(candidate, 'package.json');
+      if (fs.existsSync(candidatePackagePath)) {
+        var manifest = require(candidatePackagePath);
+        manifest.webppl = manifest.webppl || {};
+        var name = manifest.name;
+        log('Loading module "' + name + '" from "' + candidate + '"');
+        var joinPath = function(fn) { return path.join(candidate, fn); };
+        return {
+          name: name,
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/query.js

@@ -1,0 +1,35 @@
+'use strict';
+
+// Inference query table
+// Simple abstraction over js objects that provides a
+//   write-only interface
+
+function Query() {
+  this.table = {};
+}
+
+Query.prototype.add = function(key, val) {
+  this.table[key] = val;
+};
+
+Query.prototype.addAll = function(other) {
+  for (var key in other.table)
+    this.table[key] = other.table[key];
+};
+
+Query.prototype.clear = function() {
+  this.table = {};
+};
+
+// Returns a copy
+Query.prototype.getTable = function() {
+  var tbl = {};
+  for (var key in this.table)
+    tbl[key] = this.table[key];
+  return tbl;
+};
+
+
+module.exports = {
+  Query: Query
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/syntax.js

@@ -1,0 +1,172 @@
+'use strict';
+
+var types = require('ast-types').namedTypes;
+var build = require('ast-types').builders;
+var keys = require('estraverse').VisitorKeys;
+var Syntax = require('estraverse').Syntax;
+
+
+function makeGenvar() {
+  var gensym = require('./util').makeGensym();
+  return function(name) {
+    return build.identifier('_'.concat(gensym(name)));
+  };
+}
+
+function fail(message, node) {
+  return function() {
+    console.log(node);
+    console.log(message);
+    throw new Error(message);
+  };
+}
+
+// a clause matches a node type and calls a destructor with constituents
+// a clause is a function from a node and failure thunk to a result
+function clause(type, destructor) {
+  return function(node, fail) {
+    if (types.hasOwnProperty(type)) {
+      if (types[type].check(node)) {
+        return destructor.apply(this, keys[type].map(function(key) {
+          return node[key];
+        }));
+      }
+      else {
+        return fail();
+      }
+    }
+    else {
+      throw new Error('no type ' + type);
+    }
+  };
+}
+
+function match(node, clauses, fail) {
+  for (var i = 0; i < clauses.length; i++) {
+    var failed = false;
+    var value = clauses[i](node, function() {failed = true});
+    if (!failed) {
+      return value;
+    }
+  }
+  return fail();
+}
+
+function failSafe(who, fail) {
+  if (typeof fail === 'function') {
+    return fail();
+  }
+  else {
+    throw new Error(who + ': fail is not a function');
+  }
+}
+
+function inProgram(f, fail) {
+  return function(node) {
+    if (types.Program.check(node) &&
+        node.body.length === 1 &&
+        types.ExpressionStatement.check(node.body[0])) {
+      return build.program([
+        build.expressionStatement(f(node.body[0].expression))
+      ]);
+    }
+    else {
+      return failSafe('inProgram', fail);
+    }
+  };
+}
+
+function inBody(f, fail) {
+  return inProgram(function(node) {
+    if (types.FunctionExpression.check(node)) {
+      return build.functionExpression(
+          node.id,
+          node.params,
+          build.blockStatement(f(build.program(node.body.body)).body));
+    }
+    else {
+      return failSafe('inBody', fail);
+    }
+  }, fail);
+}
+
+function returnify(nodes) {
+  if (nodes.length === 0) {
+    return nodes;
+  }
+  else {
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/trace.js

@@ -1,0 +1,151 @@
+'use strict';
+
+var _ = require('lodash');
+var assert = require('assert');
+var isDist = require('./dists').isDist;
+var ad = require('./ad');
+
+var Trace = function(wpplFn, s, k, a) {
+  // The program we're doing inference in, and the store, continuation
+  // and address required to run it.
+  this.wpplFn = wpplFn;
+  this.initialStore = s;
+  this.exitK = k; // env.exit
+  this.baseAddress = a;
+
+  this.choices = [];
+  this.addressMap = {}; // Maps addresses => choices.
+  this.length = 0;
+  this.score = 0;
+  this.numFactors = 0; // The number of factors encountered so far.
+  // this.checkConsistency();
+};
+
+Trace.prototype.fresh = function() {
+  // Create a new trace using wpplFn etc. from this Trace.
+  return new Trace(this.wpplFn, this.initialStore, this.exitK, this.baseAddress);
+};
+
+Trace.prototype.choiceAtIndex = function(index) {
+  return this.choices[index];
+};
+
+Trace.prototype.findChoice = function(address) {
+  return this.addressMap[address];
+};
+
+Trace.prototype.saveContinuation = function(s, k) {
+  this.store = s;
+  this.k = k;
+  // this.checkConsistency();
+};
+
+Trace.prototype.continue = function() {
+  // If saveContinuation has been called continue, otherwise run from
+  // beginning.
+  if (this.k && this.store) {
+    return this.k(this.store);
+  } else {
+    return this.wpplFn(_.clone(this.initialStore), this.exitK, this.baseAddress);
+  }
+};
+
+Trace.prototype.addChoice = function(dist, val, address, store, continuation, options) {
+  // Called at sample statements.
+  // Adds the choice to the DB and updates current score.
+
+  // assert(isDist(dist));
+  // assert(_.isString(address));
+  // assert(_.isObject(store));
+  // assert(_.isFunction(continuation));
+
+  var choiceScore = dist.score(val);
+
+  var choice = {
+    k: continuation,
+    address: address,
+    dist: dist,
+    options: options, // the options argument passed to sample
+    // Record the score without adding the choiceScore. This is the score we'll
+    // need if we regen from this choice.
+    score: this.score,
+    choiceScore: choiceScore,
+    val: val,
+    store: _.clone(store),
+    numFactors: this.numFactors
+  };
+
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/transforms/caching.js

@@ -1,0 +1,119 @@
+'use strict';
+
+var _ = require('lodash');
+
+var estraverse = require('estraverse');
+var build = require('ast-types').builders;
+var types = require('ast-types').types;
+var isPrimitive = require('../syntax').isPrimitive;
+
+var Syntax = estraverse.Syntax;
+
+var cacheExempt = [
+  'flip',
+  'categorical',
+  'uniformDraw',
+  'bernoulli',
+  'beta',
+  'binomial',
+  'cauchy',
+  'delta',
+  'diagCovGaussian',
+  'dirichlet',
+  'discrete',
+  'exponential',
+  'gamma',
+  'gaussian',
+  'ispNormal',
+  'laplace',
+  'logisticNormal',
+  'logitNormal',
+  'multinomial',
+  'multivariateBernoulli',
+  'multivariateGaussian',
+  'poisson',
+  'randomInteger',
+  'tensorGaussian',
+  'tensorLaplace',
+  'uniform',
+  'factor',
+  'sample',
+  'observe',
+  'sampleWithFactor'
+];
+var cacheExemptTable = {};
+_.each(cacheExempt, function(funcName) {
+  cacheExemptTable[funcName] = true;
+});
+cacheExempt = cacheExemptTable;
+
+function shouldCache(callee) {
+  // Don't cache 'primitive' functions. It actually could be beneficial to cache
+  //    these in some cases, but correctly binding 'this' will require some
+  //    systemic changes that I don't want to deal with right now.
+  if (isPrimitive(callee))
+    return false;
+  // Don't cache sampling helpers or other coroutine functions that
+  // deal with distributions.
+  // Why do this? If the cache adaptation decides to remove one of these functions,
+  //    then that function will have the same address as the distribution it's dealing with,
+  //    so the adapter will also try to remove the distribution.
+  // Basically, a core assumption of IncrementalMH is that all cache nodes have unique
+  //    addresses.
+  if (callee.type === Syntax.Identifier && cacheExempt[callee.name])
+    return false;
+  // Otherwise, go ahead
+  return true;
+}
+
+function exit(node) {
+  if (node.type === Syntax.CallExpression &&
+      shouldCache(node.callee)) {
+    return build.callExpression(
+      build.identifier('incrementalize'),
+      [node.callee, build.arrayExpression(node.arguments)]
+    );
+  }
+}
+
+function cachingMain(node) {
+  return estraverse.replace(node, { leave: exit });
+}
+
+
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/transforms/cps.js

@@ -1,0 +1,355 @@
+'use strict';
+
+var build = require('./builders');
+var types = require('ast-types').namedTypes;
+var Syntax = require('estraverse').Syntax;
+
+var match = require('../syntax').match;
+var clause = require('../syntax').clause;
+var fail = require('../syntax').fail;
+var inProgram = require('../syntax').inProgram;
+var isPrimitive = require('../syntax').isPrimitive;
+var makeGenvar = require('../syntax').makeGenvar;
+
+
+var genvar = null;
+
+function buildFunction(params, body, id) {
+  return build.functionExpression(id || null, params,
+                                  build.blockStatement([build.expressionStatement(body)]));
+}
+
+function buildCall(callee, args) {
+  return build.callExpression(callee, args);
+}
+
+function buildContinuation(param, body) {
+  return buildFunction([param], body);
+}
+
+function buildContinuationCall(callee, arg) {
+  return buildCall(callee, [arg]);
+}
+
+function cpsFunction(id, params, body) {
+  var k = genvar('k');
+  return buildFunction([k].concat(params), cpsFinalStatement(body, k, k), id);
+}
+
+function bindContinuation(k, metaK) {
+  if (types.Identifier.check(k)) {
+    return metaK(k);
+  }
+  else {
+    var k0 = genvar('k');
+    return buildCall(buildFunction([k0], metaK(k0)), [k]);
+  }
+}
+
+function atomize(node, metaK) {
+  return match(node, [
+    clause(Syntax.ArrayExpression, function(elements) {
+      return atomizeStar(elements, function(elements) {
+        return metaK(build.arrayExpression(elements));
+      });
+    }),
+    clause(Syntax.AssignmentExpression, function(left, right) {
+      var err = false, line, msg;
+      if (left.type === Syntax.MemberExpression) {
+        if (!(left.object.name === 'globalStore')) {
+          err = true;
+          msg = 'You tried to assign to a field of ' + left.object.name +
+              ', but you can only assign to fields of globalStore';
+        }
+      } else {
+        err = true;
+        if (left.name === 'globalStore') {
+          msg = 'You must assign to a field of globalStore, not globalStore itself';
+        } else {
+          msg = 'Did you mean var ' + left.name + ' = ?'
+        }
+      }
+      if (err) {
+        line = left.loc.start.line;
+        throw new Error('Line ' + line + ': ' + msg);
+      }
+      return atomize(left, function(left) {
+        return atomize(right, function(right) {
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/transforms/freevars.js

@@ -1,0 +1,108 @@
+'use strict';
+
+var _ = require('lodash');
+
+var Syntax = require('estraverse').Syntax;
+var replace = require('estraverse').replace;
+var build = require('ast-types').builders;
+var types = require('ast-types').types;
+var makeGensym = require('../util').makeGensym;
+
+
+// filter out:
+// -- member expression properties
+
+
+var genid = null;
+var boundVarsStack = null;
+var freeVarsStack = null;
+
+var literalIdentifiers = {
+  undefined: true,
+  NaN: true,
+  Infinity: true
+};
+
+function identifierIsVar(node, parent) {
+  // esprima represents some special literals as Identifer nodes; skip those
+  if (literalIdentifiers[node.name]) return false;
+  // exprima also represents non-computed object member access with an
+  //    Identifer node, so skip those as well.
+  if (parent.type === Syntax.MemberExpression && !parent.computed &&
+      node === parent.property) return false;
+  // Property keys in object literal expressions are also Identifer nodes
+  if (parent.type === Syntax.Property && node === parent.key) return false;
+  return true;
+}
+
+function enter(node, parent) {
+  switch (node.type) {
+    case Syntax.FunctionExpression:
+      // Bind the formal parameters of the function
+      var boundVars = {};
+      for (var i = 0; i < node.params.length; i++)
+        boundVars[node.params[i].name] = true;
+      boundVarsStack.push(boundVars);
+      // Create a new (empty) set of free vars for this function body
+      freeVarsStack.push({});
+      break;
+    case Syntax.VariableDeclarator:
+      // Bind any vars that are declared locally
+      if (boundVarsStack.length > 0)
+        boundVarsStack[boundVarsStack.length - 1][node.id.name] = true;
+      break;
+    case Syntax.Identifier:
+      if (boundVarsStack.length > 0 && identifierIsVar(node, parent)) {
+        // If the Identifier isn't already bound, then it's a free var
+        if (!boundVarsStack[boundVarsStack.length - 1][node.name])
+          freeVarsStack[freeVarsStack.length - 1][node.name] = true;
+      }
+      break;
+    default:
+  }
+}
+
+function exit(node) {
+  switch (node.type) {
+    case Syntax.FunctionExpression:
+      // Wrap the function expression in a call to _Fn.tag,
+      //    which tags the function with a lexically-unique id and a list
+      //    of its free variable values.
[…]

### 2019-09-06 saves/rwebppl/js/webppl/src/transforms/naming.js

@@ -1,0 +1,83 @@
+'use strict';
+
+var _ = require('lodash');
+var Syntax = require('estraverse').Syntax;
+var replace = require('estraverse').replace;
+var build = require('./builders');
+
+
+var makeGensym = require('../util').makeGensym;
+var makeGenvar = require('../syntax').makeGenvar;
+var inProgram = require('../syntax').inProgram;
+var fail = require('../syntax').fail;
+var isPrimitive = require('../syntax').isPrimitive;
+
+
+function makeGenlit() {
+  var gensym = makeGensym();
+  return function() {
+    return build.literal(gensym('_'));
+  };
+}
+
+var genlit = null;
+var genvar = null;
+
+var addresses = [];
+
+function makeAddressExtension(address, literal) {
+  return build.callExpression(
+      build.memberExpression(address,
+                             build.identifier('concat'),
+                             false),
+      [literal]);
+}
+
+function generating(node) {
+  switch (node.type) {
+    case Syntax.FunctionExpression:
+      addresses.unshift(genvar('address'));
+      break;
+    default:
+  }
+}
+
+function naming(node, map) {
+  switch (node.type) {
+    case Syntax.FunctionExpression:
+      return build.functionExpression(node.id,
+          [addresses.shift()].concat(node.params),
+          node.body);
+
+    // add a gensym onto the address variable
+    case Syntax.CallExpression:
+      if (isPrimitive(node.callee)) {
+        return node;
+      } else {
+        var lit = genlit();
+        var name = node.callee.type === Syntax.Identifier ? node.callee.name : null;
+        map[lit.value] = _.assign({name: name}, node.loc);
+        return build.callExpression(node.callee,
+            [makeAddressExtension(addresses[0], lit)].concat(node.arguments), node.loc);
+      }
+
+    default:
+  }
+}
+
+function namingMain(node) {
+  genlit = makeGenlit();
+  genvar = makeGenvar();
+  var map = {};
+  var ast = inProgram(function(node) {
+    return replace(node, {
+      enter: generating,
+      leave: function(node) { return naming(node, map); }
+    });
+  })(node, fail('naming: inProgram', node));
+  return {ast: ast, map: map};
+}
+
+module.exports = {
+  naming: namingMain
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/transforms/trampoline.js

@@ -1,0 +1,76 @@
+'use strict';
+
+var replace = require('estraverse').replace;
+var Syntax = require('estraverse').Syntax;
+var build = require('ast-types').builders;
+var types = require('ast-types').namedTypes;
+var parse = require('esprima').parse;
+
+var fail = require('../syntax').fail;
+var inProgram = require('../syntax').inProgram;
+var isPrimitive = require('../syntax').isPrimitive;
+var util = require('../util');
+var _ = require('lodash');
+
+function thunkify(node) {
+  return build.functionExpression(
+      null, [],
+      build.blockStatement([
+        build.returnStatement(node)
+      ]), false, false);
+}
+
+function skip(node) {
+  if (types.ReturnStatement.check(node)) {
+    this.skip();
+  }
+}
+
+function trampoline(node) {
+  switch (node.type) {
+
+    // re-direct all non-primitive calls through trampoline
+    // this is only okay in cps where no implicit stack is used!
+    case Syntax.ExpressionStatement:
+      switch (node.expression.type) {
+        case Syntax.CallExpression:
+          if (isPrimitive(node.expression.callee)) {
+            return node;
+          }
+          else {
+            return build.returnStatement(thunkify(node.expression));
+          }
+        default:
+          return build.returnStatement(thunkify(node.expression));
+      }
+    default:
+      return node;
+  }
+}
+
+var driverFn = function(p) {
+  return function(runTrampoline) {
+    return function(s, k, a) {
+      runTrampoline(function() {
+        return p(s, k, a);
+      });
+    }
+  }
+}
+
+var driver = parse('(' + driverFn.toString() + ')').body[0].expression;
+
+function trampolineMain(node) {
+  var r = inProgram(function(node) {
+    return build.callExpression(driver, [replace(node, {
+      enter: skip,
+      leave: trampoline
+    })]);
+  })(node, fail('trampoline', node));
+
+  return r;
+}
+
+module.exports = {
+  trampoline: trampolineMain
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/transforms/varargs.js

@@ -1,0 +1,85 @@
+'use strict';
+
+var assert = require('assert');
+var estraverse = require('estraverse');
+var types = require('ast-types');
+var esprima = require('esprima');
+
+var Syntax = estraverse.Syntax;
+
+var argumentsIdCounter = 0;
+function makeArgumentsIdentifier() {
+  argumentsIdCounter += 1;
+  return '_arguments' + argumentsIdCounter;
+}
+
+var fnStack = [];
+
+function pushFn(node) {
+  if (node.type === Syntax.FunctionExpression) {
+    fnStack.push(node);
+  }
+}
+
+function popFn(node) {
+  if (node.type === Syntax.FunctionExpression) {
+    assert.strictEqual(node, fnStack[fnStack.length - 1]);
+    fnStack.pop();
+  }
+}
+
+function getEnclosingFunctionNode() {
+  if (fnStack.length === 0) {
+    throw new Error('Used "arguments" outside of function context!');
+  }
+  return fnStack[fnStack.length - 1];
+}
+
+function varargs(node) {
+
+  switch (node.type) {
+
+    // assign 'arguments' as first statement in body, rename to make it
+    // survive subsequent trampoline closure introduction
+    case Syntax.Identifier:
+      if (node.name !== 'arguments') {
+        return node;
+      }
+      var functionNode = getEnclosingFunctionNode();
+      var argumentsId = functionNode.argumentsId || makeArgumentsIdentifier();
+      node.name = argumentsId;
+      if (functionNode.argumentsId === undefined) {
+        functionNode.argumentsId = argumentsId;
+        assert.equal(functionNode.body.type, 'BlockStatement');
+        var argsDeclaration = (
+            esprima.parse('var REPLACEME = Array.prototype.slice.call(arguments, 3);').body[0]);
+        argsDeclaration.declarations[0].id.name = argumentsId;
+        functionNode.body.body = [argsDeclaration].concat(functionNode.body.body);
+      }
+      return node;
+
+    default:
+      return node;
+
+  }
+
+
+}
+
+function varargsMain(node) {
+  node = estraverse.replace(
+      node, {
+        enter: function(node) {
+          pushFn(node);
+          return varargs(node);
+        },
+        leave: function(node) {
+          popFn(node);
+        }
+      });
+  return node;
+}
+
+module.exports = {
+  varargs: varargsMain
+};

### 2019-09-06 saves/rwebppl/js/webppl/src/util.js

@@ -1,0 +1,390 @@
+'use strict';
+
+var _ = require('lodash');
+var assert = require('assert');
+var seedrandom = require('seedrandom');
+var ad = require('./ad');
+var Tensor = require('./tensor');
+var numeric = require('./math/numeric');
+
+var rng = Math.random;
+
+// Re-export sum & logsumexp from this module, as expected by
+// webppl-viz.
+var sum = numeric._sum;
+var logsumexp = numeric._logsumexp;
+
+var trampolineRunners = {
+  web: function(yieldEvery) {
+    yieldEvery = yieldEvery || 100;
+    var f = function(t, wrappedF) {
+      var lastPauseTime = Date.now();
+
+      if (f.__cancel__) {
+        f.__cancel__ = false;
+      } else {
+        while (t) {
+          var currTime = Date.now();
+          if (currTime - lastPauseTime > yieldEvery) {
+            // NB: return is crucial here as it exits the while loop
+            // and i'm using return rather than break because we might
+            // one day want to cancel the timer
+            return setTimeout(function() { wrappedF(t, wrappedF); }, 0);
+          } else {
+            t = t();
+          }
+        }
+      }
+    };
+    return f;
+  },
+  cli: function() {
+    return function(t) {
+      while (t) {
+        t = t()
+      }
+    };
+  }
+}
+
+
+
+function random() {
+  return rng();
+}
+
+function seedRNG(seed) {
+  rng = seedrandom(seed);
+}
+
+function resetRNG() {
+  rng = Math.random;
+}
+
+function assertValidRandomSeed(seed) {
+  var msg = 'Random seed should be a positive integer.';
+  assert(_.isFinite(seed) && seed >= 0, msg);
+}
+
+function runningInBrowser() {
+  return (typeof window !== 'undefined');
+}
+
+function makeGensym() {
+  var seq = 0;
+  return function(prefix) {
+    var result = prefix + seq;
+    seq += 1;
+    return result;
+  };
+}
+
+var gensym = makeGensym();
+
+function prettyJSON(obj) {
+  console.log(JSON.stringify(obj, null, 2));
+}
+
+function asArray(arg) {
+  return arg ? [].concat(arg) : [];
+}
+
+var deleteIndex = function(arr, i) {
+  return arr.slice(0, i).concat(arr.slice(i + 1))
+}
+
+// func(x, i, xs, cont)
[…]

### 2019-09-06 saves/rwebppl/js/webppl/tests/browser/tests.js

@@ -1,0 +1,99 @@
+'use strict';
+
+/*global QUnit webppl util _*/
+
+QUnit.test('run', function(test) {
+  var done = test.async();
+  webppl.run('Infer({model: flip})', function(s, dist) {
+    test.ok(_.isEqual([false, true], dist.support().sort()));
+    done();
+  });
+});
+
+QUnit.test('run twice', function(test) {
+  var done = test.async(2);
+  _.times(2, function() {
+    webppl.run('Infer({model: flip})', function(s, dist) {
+      test.ok(_.isEqual([false, true], dist.support().sort()));
+      done();
+    });
+  });
+});
+
+QUnit.test('run resets env', function(test) {
+  var done = test.async();
+  try {
+    webppl.run('Infer({model() { assert.ok(false); }})');
+  } catch (e) {
+  }
+  // Attempting to sample from a continuous distribution will raise an
+  // error if Enumerate is still installed as the current coroutine.
+  webppl.run('gaussian(0, 1)', function(s, val) {
+    test.ok(_.isNumber(val));
+    done();
+  });
+});
+
+function errorTest(code, debug, performChecks) {
+  return function(test) {
+    var done = test.async();
+    var handler = function(error) {
+      performChecks(done, test, error);
+    };
+    // Have the runner yield frequently to be sure the error occurs from
+    // a setTimeout.
+    var runner = util.trampolineRunners.web(1);
+    var allCode = 'Infer({model: flip, method: "MCMC", samples: 1000});\n' + code;
+    webppl.run(allCode, null, {runner: runner, debug: debug, errorHandlers: [handler]});
+  };
+}
+
+QUnit.test(
+    'handling throw Error, debug=true',
+    errorTest('null[0]', true, function(done, test, error) {
+      test.ok(error instanceof Error);
+      test.ok(error.wpplRuntimeError);
+      done();
+    }));
+
+QUnit.test(
+    'handling throw Error, debug=false',
+    errorTest('null[0]', false, function(done, test, error) {
+      test.ok(error instanceof Error);
+      test.ok(error.wpplRuntimeError);
+      done();
+    }));
+
+QUnit.test(
+    'handling throw string, debug=true',
+    errorTest('util.jsthrow("fail")', true, function(done, test, error) {
+      test.ok(typeof error === 'string');
+      test.ok(error === 'fail');
+      done();
+    }));
+
+QUnit.test(
[…]

### 2019-09-06 saves/rwebppl/js/webppl/tests/test-caching.js

@@ -1,0 +1,39 @@
+'use strict';
+
+var _ = require('lodash');
+var parse = require('esprima').parse;
+var caching = require('../src/transforms/caching');
+
+var hasCachingDirectiveTests = {
+  test1: { code: "'no caching'", expected: true },
+  test2: { code: '"no caching";\n', expected: true },
+  test3: { code: '\n"no caching";\n1+1', expected: true },
+  test4: { code: '1 + 1', expected: false },
+  test5: { code: "1 + 1;\n'no caching'", expected: false },
+  test6: { code: '', expected: false }
+};
+
+var transformRequiredTests = {
+  test1: { code: 'IncrementalMH(model, 0);', expected: true },
+  test2: { code: 'Enumerate(model);', expected: false },
+  test3: { code: 'Infer({model, method: "incrementalMH"});', expected: true },
+  test4: { code: 'Infer({model, method: "enumerate"});', expected: false },
+  test5: { code: '({method: "incrementalMH"})', expected: true },
+  test6: { code: '({method: "enumerate"})', expected: false },
+  test7: { code: '({"method": "incrementalMH"})', expected: true },
+  test8: { code: '({"method": "enumerate"})', expected: false }
+};
+
+function generateTests(cases, testFn) {
+  return _.mapValues(cases, function(caseDef) {
+    return function(test) {
+      test.strictEqual(testFn(parse(caseDef.code)), caseDef.expected);
+      test.done();
+    };
+  });
+}
+
+module.exports = {
+  hasNoCachingDirective: generateTests(hasCachingDirectiveTests, caching.hasNoCachingDirective),
+  transformRequired: generateTests(transformRequiredTests, caching.transformRequired)
+};

### 2019-09-06 saves/rwebppl/js/webppl/tests/test-deterministic.js

@@ -1,0 +1,34 @@
+'use strict';
+
+// Tests for deterministic code written in webppl (e.g., preamble functions)
+
+var webppl = require('../src/main');
+var helpers = require('./helpers/helpers');
+
+var testDataDir = './tests/test-data/deterministic/';
+
+var generateTestCases = function() {
+  var modelNames = helpers.getModelNames(testDataDir);
+  modelNames.forEach(function(modelName) {
+    var model = helpers.loadModel(testDataDir, modelName);
+    var expected = helpers.loadExpected(testDataDir, modelName);
+    exports[modelName] = function(test) {
+      var result;
+      webppl.run(model, function(s, val) { result = val; });
+      helpers.testEqual(test, result, expected.result, 'result');
+      test.done();
+    };
+  });
+  var oldSuppressWarnings;
+  exports.setUp = function(callback) {
+    oldSuppressWarnings = global.suppressWarnings;
+    global.suppressWarnings = true;
+    callback();
+  };
+  exports.tearDown = function(callback) {
+    global.suppressWarnings = oldSuppressWarnings;
+    callback();
+  };
+};
+
+generateTestCases();

### 2019-09-06 saves/rwebppl/js/webppl/tests/test-examples.js

@@ -1,0 +1,45 @@
+'use strict';
+
+var _ = require('lodash');
+var fs = require('fs');
+var webppl = require('../src/main');
+var dists = require('../src/dists');
+
+var examplesDir = './examples/';
+
+var examples = [
+  'binomial',
+  'geometric',
+  'hmm',
+  'hmmIncremental',
+  'lda',
+  'ldaCollapsed',
+  'linearRegression',
+  'logisticRegression',
+  'multivariateRegression',
+  'pcfg',
+  'pcfgIncremental',
+  'scalarImplicature',
+  'semanticParsing',
+  'pragmaticsWithSemanticParsing'
+];
+
+var loadExample = function(example) {
+  var filename = examplesDir + example + '.wppl';
+  return fs.readFileSync(filename, 'utf-8');
+};
+
+var generateTestCases = function() {
+  _.each(examples, function(example) {
+    exports[example] = function(test) {
+      test.doesNotThrow(function() {
+        webppl.run(loadExample(example), function(s, val) {
+          test.ok(dists.isDist(val));
+        });
+      });
+      test.done();
+    };
+  });
+};
+
+generateTestCases();

### 2019-09-06 saves/rwebppl/js/webppl/tests/test-inference.js

@@ -1,0 +1,879 @@
+'use strict';
+
+var _ = require('lodash');
+var seedrandom = require('seedrandom');
+var fs = require('fs');
+var assert = require('assert');
+var util = require('../src/util');
+var webppl = require('../src/main');
+var helpers = require('./helpers/helpers');
+
+var testDataDir = './tests/test-data/stochastic/';
+
+var tests = [
+  {
+    name: 'ForwardSample',
+    method: 'forward',
+    settings: {
+      args: { samples: 3000 },
+      hist: { tol: 0.05 },
+      mean: { tol: 0.2 },
+      std: { tol: 0.2 }
+    },
+    models: {
+      deterministic: { args: { samples: 10 }, hist: { tol: 0 } },
+      flips: true,
+      geometric: true,
+      randomInteger: true,
+      gaussian: { args: { samples: 10000 } },
+      uniform: { args: { samples: 10000 } },
+      uniformSampledSupport: true,
+      beta: true,
+      exponential: true,
+      laplace: { args: { samples: 10000 } },
+      tensorLaplace: { args: { samples: 10000 } },
+      binomial: true,
+      multinomial: true,
+      poisson: true,
+      cauchy: true,
+      logNormal: { args: { samples: 10000 } },
+      delta: { args: { samples: 10 }, hist: { exact: true } },
+      discreteArr: true,
+      discreteVec: true,
+      categoricalArr: true,
+      categoricalVec: true,
+      dirichlet: true,
+      multivariateGaussian: true,
+      multivariateGaussian2: true,
+      multivariateBernoulli: true,
+      diagCovGaussian: true,
+      tensorGaussian: true,
+      mixed1: true,
+      mixed2: true,
+      mixed3: true,
+      mixed4: true,
+      bivariateGaussian: true,
+      indirectDependency: true,
+      guidedFlip: true,
+      onlyMAP: {
+        mean: { tol: 0.1 },
+        std: { tol: 0 },
+        args: { samples: 150, onlyMAP: true }
+      }
+    }
+  },
+  {
+    name: 'Enumerate',
+    method: 'enumerate',
+    settings: {
+      args: {},
+      MAP: { check: true }
+    },
+    models: {
+      simple: true,
+      simpleSoft: true,
[…]

### 2019-09-06 saves/rwebppl/js/webppl/tests/test-samplers.js

@@ -1,0 +1,210 @@
+// In this file, we test our samplers by running them a bunch for various
+// sample values and comparing the resulting *sample* statistics against mathematically
+// derived *population* statistics. We also check that every sample is in the
+// support of the distribution, so that users aren't bit by underflow or overflow
+
+'use strict';
+
+var _ = require('lodash');
+var seedrandom = require('seedrandom');
+var util = require('../src/util');
+var webppl = require('../src/main');
+var helpers = require('./helpers/helpers');
+var statistics = require('../src/math/statistics');
+
+var repeat = function(n, f) {
+  // used typedarray because node can run out of memory easily with lots of big arrays
+  var a = new Float64Array(n);
+  for (var i = 0; i < n; i++) {
+    a[i] = f()
+  }
+  return a;
+}
+
+var ln = Math.log,
+    pow = Math.pow,
+    sqrt = Math.sqrt,
+    abs = Math.abs;
+
+var mean = statistics.mean;
+var variance = statistics.variance;
+var sd = statistics.sd;
+var skew = statistics.skew;
+var kurtosis = statistics.kurtosis;
+var mode = statistics.kdeMode;
+
+var sampleStatisticFunctions = {
+  mean: mean,
+  variance: variance,
+  skew: skew,
+  kurtosis: kurtosis,
+  mode: mode
+}
+
+var distMetadataList = [
+  require('./test-data/sampler/gamma'),
+  require('./test-data/sampler/binomial'),
+  require('./test-data/sampler/beta'),
+  require('./test-data/sampler/gaussian'),
+  require('./test-data/sampler/poisson'),
+  require('./test-data/sampler/logNormal')
+];
+
+var generateSettingTest = function(seed, distMetadata, settings) {
+  // settings includes:
+  // - params to the dist
+  // - inference params (e.g., number of samples)
+  // - test params (e.g., relative tolerance)
+  var params = settings.params;
+  var n = settings.n;
+
+  // only test the stats that aren't blacklisted
+  var populationStatisticFunctions = _.pickBy(distMetadata.populationStatisticFunctions,
+                                              function(v, k) {
+                                                return !_.includes(settings.skip, k)
+                                              });
+  var group = {};
+
+  var moment = distMetadata.moment;
+
+  group['test'] = function(test) {
+    var samples = repeat(n, function() {
+      return distMetadata.sampler.apply(null, params);
+    });
+
[…]

### 2019-09-06 saves/rwebppl/js/webppl/tests/test-transforms.js

@@ -1,0 +1,724 @@
+'use strict';
+
+var webppl = require('../src/main');
+
+var _ = require('lodash');
+var parse = require('esprima').parse;
+var unparse = require('escodegen').generate;
+var thunkify = require('../src/syntax').thunkify;
+var fail = require('../src/syntax').fail;
+var naming = require('../src/transforms/naming').naming;
+var cps = require('../src/transforms/cps').cps;
+var store = require('../src/transforms/store').store;
+var optimize = require('../src/transforms/optimize').optimize;
+var trampoline = require('../src/transforms/trampoline').trampoline;
+var varargs = require('../src/transforms/varargs').varargs;
+var freevars = require('../src/transforms/freevars').freevars;
+var util = require('../src/util');
+
+var fooObj = {
+  bar: 1,
+  baz: {
+    blubb: 2,
+    bla: 3
+  }
+};
+
+var plus, minus, times, and, plusTwo;
+
+function compose() {
+  var fs = Array.prototype.concat.apply([], arguments);
+
+  return function(x) {
+    return fs.reduceRight(function(x, f) {
+      return f(x);
+    }, x);
+  };
+}
+
+function runTest(test, code, expected, transformAst, run) {
+  var newCode = unparse(transformAst(parse(code)));
+
+  try {
+    run(test, code, newCode, expected);
+  }
+  catch (e) {
+    console.log('Exception:', e);
+    console.log(newCode);
+    test.ok(false);
+    test.done();
+  }
+}
+
+function check(test, code, newCode, expected, actual) {
+  var success = _.isEqual(expected, actual);
+
+  test.ok(success);
+
+  if (!success) {
+    console.log(code);
+    console.log(newCode);
+    console.log('Expected:', expected);
+    console.log('Actual:', actual);
+  }
+
+  test.done();
+}
+
+var transformAstNaming = compose(_.property('ast'), naming, function(node) {
+  return thunkify(node, fail('transform', node));
+});
+function runNaming(test, code, newCode, expected) {
+  check(test, code, newCode, expected, eval(newCode)(''));
+}
+
+var transformAstCps = compose(cps, varargs, transformAstNaming);
+function runCps(test, code, newCode, expected) {
+  eval(newCode)(function(actual) {
+    check(test, code, newCode, expected, actual);
+  }, '');
+}
+
[…]

### 2019-09-06 saves/rwebppl/js/webppl/tests/test-util.js

@@ -1,0 +1,113 @@
+'use strict';
+
+var util = require('../src/util');
+var numeric = require('../src/math/numeric');
+
+function testAlmostEqual(test, x, y, epsilon) {
+  if (x === y) {
+    test.equal(x, y);
+  } else {
+    test.ok(Math.abs(x - y) < epsilon);
+  }
+}
+
+module.exports = {
+
+  testLogSumExp: {
+
+    test1: function(test) {
+      var epsilon = 0.0000000001;
+      var xs = [-Infinity, -100, -30, -1, 0, 1, 10];
+      xs.forEach(
+          function(x) {
+            testAlmostEqual(test, x, numeric._logsumexp([x]), epsilon);
+            xs.forEach(
+                function(y) {
+                  var targetVal = Math.log(Math.exp(x) + Math.exp(y));
+                  var actualVal = numeric._logsumexp([x, y]);
+                  testAlmostEqual(test, targetVal, actualVal, epsilon);
+                });
+          });
+      test.done();
+    }
+
+  },
+
+  testLogAddExp: {
+    test1: function(test) {
+      testAlmostEqual(test, Math.exp(numeric.logaddexp(Math.log(1), Math.log(2))), 3, 1e-6);
+      test.done();
+    },
+    test2: function(test) {
+      testAlmostEqual(test, Math.exp(numeric.logaddexp(Math.log(2), Math.log(1))), 3, 1e-6);
+      test.done();
+    },
+    test3: function(test) {
+      testAlmostEqual(test, Math.exp(numeric.logaddexp(-Infinity, Math.log(1))), 1, 1e-6);
+      test.done();
+    },
+    test4: function(test) {
+      testAlmostEqual(test, Math.exp(numeric.logaddexp(Math.log(1), -Infinity)), 1, 1e-6);
+      test.done();
+    },
+    test5: function(test) {
+      testAlmostEqual(test, Math.exp(numeric.logaddexp(-Infinity, -Infinity)), 0, 1e-6);
+      test.done();
+    }
+  },
+
+  testCpsIterate: {
+
+    test1: function(test) {
+      var result = util.cpsIterate(5, 3,
+          function(k, val) { return k(val + 2); },
+          function(finalVal) { return finalVal; });
+      // Trampoline.
+      while (typeof result === 'function') { result = result(); }
+      test.equal(result, 13);
+      test.done();
+    }
+
+  },
+
+  testIsObject: {
+    test1: function(test) {
[…]

### 2019-09-06 saves/rwebppl/tests/testthat.R

@@ -1,0 +1,4 @@
+library(testthat)
+library(rwebppl)
+
+test_check("rwebppl")

### 2019-09-06 saves/rwebppl/tests/testthat/testOutputFormat.R

@@ -1,0 +1,92 @@
+library(rwebppl)
+context("Output format")
+
+test_that("enumerate returns probability table", {
+	expect_true(all(names(webppl('
+		var model = function() {
+			var p = uniformDraw([0.2,0.5,0.8,0.99] )
+      var q = uniformDraw([0.2,0.5,0.8,0.99] )
+      var theta = p*q;
+			observe(Binomial( {p : theta, n: 5 } ), 4)
+      return {p, q}
+		}',
+    inference_opts = list(method = "enumerate"),
+    model_var = "model")) == c("p", "q", "prob")))
+})
+
+test_that("rejection returns tidy df", {
+	expect_true(all(names(webppl('
+		var model = function() {
+			var p = uniform( {a:0, b:1} );
+      var q = uniform( {a:0, b:1} );
+      var theta = p*q;
+			observe(Binomial( {p : theta, n: 5 } ), 4)
+			return {p, q}
+		}',
+    inference_opts = list(method = "rejection", samples = 100),
+    model_var = "model")) == c("Iteration", "Chain", "Parameter", "value")))
+})
+
+test_that("MCMC returns tidy df", {
+	expect_true(all(names(webppl('
+		var model = function() {
+			var p = uniform( {a:0, b:1} );
+      var q = uniform( {a:0, b:1} );
+      var theta = p*q;
+			observe(Binomial( {p : theta, n: 5 } ), 4)
+			return {p, q}
+      }',
+      inference_opts = list(method = "MCMC", samples = 100),
+			model_var = "model")) == c("Iteration", "Chain", "Parameter", "value")))
+})
+
+test_that("incrementalMH returns tidy df", {
+	expect_true(all(names(webppl('
+		var model = function() {
+			var p = uniform( {a:0, b:1} );
+      var q = uniform( {a:0, b:1} );
+      var theta = p*q;
+			observe(Binomial( {p : theta, n: 5 } ), 4)
+			return {p, q}
+      }',
+    inference_opts = list(method = "incrementalMH", samples = 100),
+		model_var = "model")) == c("Iteration", "Chain", "Parameter", "value")))
+})
+
+test_that("forward returns tidy df", {
+	expect_true(all(names(webppl('
+		var model = function() {
+			var p = uniform( {a:0, b:1} );
+      var q = uniform( {a:0, b:1} );
+      var theta = p*q;
+			return {p, q}
+      }',
+    inference_opts = list(method = "forward", samples = 100),
[…]

### 2019-09-06 saves/rwebppl/tests/testthat/testdata.R

@@ -1,0 +1,9 @@
+library(rwebppl)
+context("Passing data")
+
+test_that("list passing from r to webppl and back", {
+	expect_equal(webppl("data",
+             data = list(a = 5, b = 7),
+             data_var = "data"),
+		list(a = 5, b = 7))
+	})

### 2019-09-06 saves/rwebppl/tests/testthat/testmain.R

@@ -1,0 +1,13 @@
+library(rwebppl)
+context("Basic WebPPL call")
+
+test_that("webppl call returns data frame", {
+	expect_true(is.data.frame(webppl('
+		var model = function() {
+			var p = uniform( {a:0, b:1} )
+			factor(Binomial( {p : 0.5, n: 5 } ).score(4) )
+			return {p: p}
+		}
+		Infer({method:"rejection", samples:1000}, model)
+		')))
+})

### 2019-09-08 stats/model.Rmd
add model runs with more iterations

@@
         })
+  //     slope: Math.pow(gaussianDrift({
+  //       mu: globalLineParameters.slope, 
+  //      sigma: itemVariability.slope, 
+  //       width: 0.5
+  //    }), 2)
       }
@@
   model_var = "model",
-  chains = 4,
-  cores = 4,
+  chains = 3,
+  cores = 3,
   inference_opts = list(method = "incrementalMH",
-                        samples = 4000,
-                        burn = 2000,
+                        samples = 50000,
+                        burn = 25000,
                         verbose = T,
@@
 
-sem_know_model <- readRDS("../saves/sem_know_model_variant3_50k.rds")
+sem_know_model <- readRDS("../saves/sem_know_model_variant2_50k.rds")
 
@@
   #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
-  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
+  geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
   geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
@@
   #facet_grid(condition~familiarObject)+
-  facet_grid(~item)+
+  facet_wrap(~item, nrow = 2)+
   #ggtitle("Combination Data")+
@@
 
-ggsave("../graphs/overview_variant_3_50k.png", width = 12, height = 4, scale = 1.2)
+ggsave("../graphs/overview_variant_3_100k.png", width = 12, height = 4, scale = 1.2)
 
@@
   inference_opts = list(method = "incrementalMH",
-                        samples = 50000,
-                        burn = 25000,
+                        samples = 100000,
+                        burn = 50000,
                         verbose = T,
                         lag = 1,
-                        verboseLag = 100)
+                        verboseLag = 5000)
 )
@@
 
-saveRDS(sem_know_model, "../saves/sem_know_model_variant3_50k.rds")
+saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k.rds")
 

### 2019-09-10 stats/model.Rmd
add 100k model runs

@@
   inference_opts = list(method = "incrementalMH",
-                        samples = 50000,
-                        burn = 25000,
+                        samples = 100000,
+                        burn = 50000,
                         verbose = T,
                         lag = 1,
-                        verboseLag = 1000)
+                        verboseLag = 5000)
 )
@@
 
-sem_know_model <- readRDS("../saves/sem_know_model_variant2_50k.rds")
+sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k.rds")
 
@@
 
-saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k.rds")
+saveRDS(sem_know_model, "../saves/sem_know_model_variant1_100k.rds")
 

### 2019-09-10 stats/model.Rmd
add 100k model runs

@@
         }),
-        slope: gaussianDrift({
+     //   slope: gaussianDrift({
+     //     mu: globalLineParameters.slope, 
+      //    sigma: itemVariability.slope, 
+      //    width: 0.5
+     //   })
+      slope: Math.pow(gaussianDrift({
          mu: globalLineParameters.slope, 
@@
          width: 0.5
-        })
-  //     slope: Math.pow(gaussianDrift({
-  //       mu: globalLineParameters.slope, 
-  //      sigma: itemVariability.slope, 
-  //       width: 0.5
-  //    }), 2)
+      }), 2)
       }
@@
 
+#saveRDS(sem_know_model, "../saves/sem_know_model_variant2_100k.rds")
 ```
@@
   #facet_grid(condition~familiarObject)+
-  facet_wrap(~item, nrow = 2)+
+  facet_grid(~item)+
   #ggtitle("Combination Data")+
@@
 
-saveRDS(sem_know_model, "../saves/sem_know_model_variant1_100k.rds")
+#saveRDS(sem_know_model, "../saves/sem_know_model_variant2_100k.rds")
 

### 2019-09-16 stats/kids_combination.Rmd
fix dob on comb data file

@@
 
-## importing data
-# files <- dir("~/Work/Spin/raw_data/kids/combination/")
-# 
-# raw_data <- data_frame()
-# for (f in files) {
-#   jf <- paste("~/Work/Spin/raw_data/kids/combination/",f,sep="")
-#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-#   date <- str_sub(jf,56,str_length(jf)-11)
-#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
-#   raw_data <- bind_rows(raw_data, id)
-# }
-# 
-# d_raw <- raw_data %>%
-#   mutate(discourseNovel = str_sub(discourseNovel,11),
-#          mutExNovel = str_sub(mutExNovel, 10),
-#          subid = ifelse(subid == "190726_6_come", "190726_6_com", subid))
-# 
-# d_raw %>%
-#   filter(subid == "190727_1_com")
-# 
-# 
-# log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
-#   filter(Condition == "com")%>%
-#   mutate(dob = as.character(dob),
-# #         dob = ifelse(subid == "190313_7_me", "2015-11-15",dob),
-#          dob = as.Date(dob))%>%
-#   select(subid,experimenter,keep_drop,sex,dob)
-# 
-#  
-# d_raw%>%
-#   group_by(subid)%>%
-#   summarise(n())%>%
-#   filter(!(subid %in% unique(log$subid)))
-# 
-#  
-# d <- left_join(d_raw,log, by = "subid")%>%
-#   filter(keep_drop == "keep")%>%
-#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-#          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
-# 
-# 
-# write_csv(d, "../data/combination.csv")
+# importing data
+files <- dir("~/Work/Spin/raw_data/kids/combination/")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/Spin/raw_data/kids/combination/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,56,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+d_raw <- raw_data %>%
+  mutate(discourseNovel = str_sub(discourseNovel,11),
+         mutExNovel = str_sub(mutExNovel, 10),
+         subid = ifelse(subid == "190726_6_come", "190726_6_com", subid))
+
+d_raw %>%
+  filter(subid == "190727_1_com")
+
+log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
+  filter(Condition == "com")%>%
+  mutate(dob = as.character(dob),
+         dob = ifelse(subid == "190620_7_com", "2016-06-20",dob),
+         dob = ifelse(subid == "190620_8_com", "2014-10-04",dob),
+         dob = ifelse(subid == "190620_14_com", "2016-12-16",dob),
+         dob = ifelse(subid == "190711_4_com", "2017-12-11",dob),
+         dob = ifelse(subid == "190516_03_com", "2016-05-16",dob),
+         dob = ifelse(subid == "190711_4_com", "2016-12-11",dob),
+
+         dob = as.Date(dob))%>%
+  select(subid,experimenter,keep_drop,sex,dob)
+
+d_raw%>%
+  group_by(subid)%>%
+  summarise(n())%>%
+  filter(!(subid %in% unique(log$subid)))
+
+d <- left_join(d_raw,log, by = "subid")%>%
+  filter(keep_drop == "keep")%>%
+  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+
+d%>%
+  filter(check_age == F)%>%
+  select(subid, subage,test_date,dob,age_num,check_age)
+
+write_csv(d, "../data/combination.csv")
 

### 2019-09-16 stats/model.Rmd
fix dob on comb data file

@@
 library(stringr)
+library(matrixStats)
 
@@
 
-#### WORK IN PROGRESS: nesting within participant
+# Nesting within participant
+
+```{r}
+novel_bm <- readRDS("../saves/novelty_model.rds")
+
+#summary(novel_bm)
+
+novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
+  select(term,Estimate)%>%
+  spread(term, Estimate)
+
+data_comb_log <- read_csv("../data/combination.csv") %>%
+  filter(condition != "train")%>%
+  mutate(alignment = condition,
+         item = familiarObject, 
+         age = age_num - (min(age_num))) %>%
+  mutate(nov_int = novel_params$Intercept,
+         nov_slope = novel_params$age_num,
+         prior = ifelse(alignment == "congruent", plogis(nov_int + nov_slope* age),1-plogis(nov_int + age * nov_slope)))
+
+data_comb_log
+
+```
+
+## Pragmatics model
 
@@
 
-  foreach(function(row){
+var all_log_likes = map(function(row) { 
       var prior = [row.prior, 1-row.prior]
-      foreach(function(item){
-        var itemLineParameters = all_item_parameters[item]
+        var itemLineParameters = all_item_parameters[row.item]
         var sem_knowledge = logistic(itemLineParameters.intercept + 
@@
 
+        return modelPredictions.score(row.correct)
+
     //  query.add(["prediction", item, row.age, row.alignment], ["NA", Math.exp(modelPredictions.score(1))])
-
-      }, familiars)
+  // return loglike
    }, dataFromR.comb_data)
+
+  var log_likelihood = sum(all_log_likes)
+  query.add(["log_like", "NA", "NA"], ["NA", log_likelihood])
 
@@
 
-novel_bm <- readRDS("../saves/novelty_model.rds")
-
-#summary(novel_bm)
-
-novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
-  select(term,Estimate)%>%
-  spread(term, Estimate)
-
-me_model_data <- read_csv("../data/me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(age = age_num - min(age_num),
-         nov_int = novel_params$Intercept,
-         nov_slope = novel_params$age_num,
-         prior = plogis(nov_int + age * nov_slope))
-
-comb_model_data <- bind_rows(
-  me_model_data %>%
-    distinct(age, prior) %>%
-    mutate(prior = 1 - prior, 
-         alignment = "incongruent"),
-
-   me_model_data %>%
-    distinct(age, prior) %>%
-    mutate(alignment = "congruent")
-)
-
 sem_know_model<- webppl(
   program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
-  data = list(data = me_model_data, comb_data = comb_model_data),
+  data = list(data = me_model_data, comb_data = data_comb_log),
   data_var = "dataFromR",
@@
                         lag = 1,
-                        verboseLag = 5000)
+                        verboseLag = 1000)
 )
 
-# run variants
-# start with variant 3
-# 3 cores, 3 chains 
-# see how long it takes and then run over night
-
-#saveRDS(sem_know_model, "../saves/sem_know_model_variant2_100k.rds")
+#saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_log_like.rds")
 
@@
          me_effect =as.numeric(str_remove(me_effect,"[)]")))
+
+log_like<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
+  filter(parameter == "log_like")%>%
+  separate(value, into = c("na", "log_like"),sep = ",")%>%
+  select(-na, -item, -age, -alignment)%>%
+  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
+  group_by(Chain)%>%
+  summarize(logP = logSumExp(log_like))
+
+```
+
+## Flat prior model
+
+```{r work in progress}
+flat_prior <- '
+var data = dataFromR.data
+
+var priorProbs = [.5,.5]
+
+var familiars = levels(data, "familiar")
+var subjects = levels(data, "subid")
+
+var model  = function(){
+
+  var speakerOptimalityParameters = {
+    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
+    slope: uniformDrift({a: 0, b: 4, width: 0.5})
+  }
+
+  var globalLineParameters = {
+    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
+    slope: uniformDrift({a: 0, b: 2, width: 0.5})
+  }
+
+  var itemVariability = {
+    intercept: uniformDrift({a: 0, b: 2, width: 0.2}),
+    slope: uniformDrift({a: 0, b: 1, width: 0.2})
+  }
+
+  // conceptually it might not make sense to have two sigmas, but maybe it does
+  // intercept sigma probably will be smaller than slope sigma
+  // var item_int_sigma = uniformDrift({a: 0, b: 3, width: 0.2})
+
+  var sampleItemParameters = function(itemName) { 
+    return [itemName, {
+        intercept: gaussianDrift({
+          mu: globalLineParameters.intercept, 
+          sigma: itemVariability.intercept, 
+          width: 0.5
+        }),
+        slope: gaussianDrift({
+          mu: globalLineParameters.slope, 
+          sigma: itemVariability.slope, 
+          width: 0.5
+        })
+      }]
+  }
+
+  // {papaya: {int, slope}, bread: {int, slope}, ... }
+  var all_item_parameters = _.fromPairs(map(sampleItemParameters, familiars))
+
+  // want something that favors smaller values
+  var subject_sigma = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var sampleLinguisticCompetence = function(age){
+    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
+  }
+
+  foreach(function(subid){
+      var subjectData = _.filter(data, {subid: subid})
+      var subj_age = subjectData[0].age
+      var subj_linguistic_competence = sampleLinguisticCompetence(subj_age)
+
+     // display("age = " + subj_age + " ... intercept = " + subj_linguistic_competence)
+
+      // question: should we use age here instead of the random intercept? or a different random intercept?
+
+  var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_age
+
+      // each row is a different item
+      foreach(function(row){
+
+        var itemLineParameters = all_item_parameters[row.familiar]
+
+        var sem_knowledge = logistic(itemLineParameters.intercept + 
+            itemLineParameters.slope * subj_linguistic_competence)
+
+        var modelPredictions = pragmaticListener({label: "novel_word"}, 
+              priorProbs, speakerOptimality, sem_knowledge)
+        // display(modelPredictions.score(row.correct))
+
+        observe(modelPredictions, row.correct)
+
+        // if you want to save predictions, make sure to record subid because these predictions are for this particular subid
+        // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
+
+      }, subjectData)
+
+    // comment out to save memory
+  //  query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])
+
+  }, subjects)
+
+var all_log_likes = map(function(row) { 
+      var prior = [row.prior, 1-row.prior]
+        var itemLineParameters = all_item_parameters[row.item]
+        var sem_knowledge = logistic(itemLineParameters.intercept + 
+            itemLineParameters.slope * row.age)
+        var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age
+
+        var modelPredictions = pragmaticListener({label: "novel_word"}, [.5,.5], speakerOptimality, sem_knowledge)
+
+    //    display(modelPredictions.score(row.correct))
+
+        return modelPredictions.score(row.correct)
+
+    //  query.add(["prediction", item, row.age, row.alignment], ["NA", Math.exp(modelPredictions.score(1))])
+  // return loglike
+   }, dataFromR.comb_data)
+
+  var log_likelihood = sum(all_log_likes)
+  query.add(["log_like", "NA", "NA"], ["NA", log_likelihood])
+
+  foreach(function(item){
+    var itemLineParameters = all_item_parameters[item]
+    query.add(["parameter","items", item], [itemLineParameters.intercept, itemLineParameters.slope])
+  }, familiars)
+
+  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
+  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
+  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
+  query.add(["parameter","sigma", "global_subject_sigmas"], ["NA", subject_sigma])
+
+  return query 
+}
+'
+```
+
+```{r}
+
+sem_know_model_flat_prior<- webppl(
+  program_code = paste(rsaUtils, rsaModel, flat_prior , sep='\n'),
+  data = list(data = me_model_data, comb_data = data_comb_log),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 3,
+  cores = 3,
+  inference_opts = list(method = "incrementalMH",
+                        samples = 100000,
+                        burn = 50000,
+                        verbose = T,
+                        lag = 1,
+                        verboseLag = 1000)
+)
+
+saveRDS(sem_know_model_flat_prior, "../saves/sem_know_model_variant3_100k_flat_prior_log_like.rds")
+
+model_pred<- sem_know_model_flat_prior %>%
+  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
+  filter(parameter == "prediction")%>%
+  separate(value, into = c("na", "me_effect"),sep = ",")%>%
+  select(-na)%>%
+  mutate(age = as.numeric(age),
+         me_effect =as.numeric(str_remove(me_effect,"[)]")))
+
+log_like_flat_prior<- sem_know_model_flat_prior %>%
+  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
+  filter(parameter == "log_like")%>%
+  separate(value, into = c("na", "log_like"),sep = ",")%>%
+  select(-na, -item, -age, -alignment)%>%
+  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
+  group_by(Chain)%>%
+  summarize(logP = logSumExp(log_like))
 
@@
   geom_ribbon(aes(ymin = lci, ymax = uci), alpha = .5, colour = NA)+
+  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col), col = "black", fill = "grey",  method = "loess", se = F, alpha = .2, span = 2)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   labs(x="Age",y="Proportion correct")+
-  facet_grid(Chain~alignment)+
+  facet_grid(Chain ~item)+
   theme_few() +
@@
 ```
+
+```{r}
+ggsave("../graphs/model_pred_data.pdf", width = 20, height = 8, scale = 1.2)
+```

### 2019-09-17 stats/kids_combination.Rmd
draft model comparison

@@
 ```
+
+```{r}
+fixef <- as_tibble(readRDS("../saves/fixef_brm_model_item_random_only.rds"), rownames = "term")
+
+ranef <-  readRDS("../saves/ranef_brm_model_item_random_only.rds")
+
+model_plot <- bind_rows(
+  as_tibble(ranef$familiar, rownames = "familiar")%>%
+  mutate(condition = "congruent",
+         condition_code = 0),
+  as_tibble(ranef$familiar, rownames = "familiar")%>%
+  mutate(condition = "incongruent",
+         condition_code = 1))%>%
+  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
+         grand_age = fixef%>%filter(term=="age_num")%>%pull(Estimate),
+         grand_cond = fixef%>%filter(term=="conditionincongruent")%>%pull(Estimate),
+         grand_intact = fixef%>%filter(term=="age_num:conditionincongruent")%>%pull(Estimate))%>%
+  group_by(familiar, condition, condition_code) %>%
+  expand(Estimate.Intercept,Estimate.conditionincongruent,Estimate.age_num,`Estimate.age_num:conditionincongruent`,grand_intercept,grand_age,grand_cond,grand_intact,age = d$age_num - mean(d$age_num))%>%
+  mutate(y = plogis(grand_intercept + 
+                      Estimate.Intercept +
+                      grand_cond * condition_code +
+                      Estimate.conditionincongruent * condition_code +
+                      grand_age * age +
+                      Estimate.age_num * age +
+                      grand_intact * (condition_code * age) +
+                      `Estimate.age_num:conditionincongruent` * (condition_code * age)),
+         age = age+mean(d$age_num))%>%
+  left_join(aoa_ratings%>%mutate(familiar = familiarObject))%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(familiar), mean_aoa))
+
+ggplot(model_plot, aes(x=age,y = y, col = familiar))+
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(size = 1)+
+  ggtitle("Model")+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(~condition)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d(name = "familiar object")
+```

### 2019-09-17 stats/model.Rmd
draft model comparison

@@
 
-sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k.rds")
+sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k_log_like.rds")
 
@@
 ```{r}
+me_model_data <- read_csv("../data/me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
+
 novel_bm <- readRDS("../saves/novelty_model.rds")
@@
 
-var all_log_likes = map(function(row) { 
+var all_log_likes_prag = map(function(row) { 
       var prior = [row.prior, 1-row.prior]
@@
             itemLineParameters.slope * row.age)
+
      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age
 
-        var modelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)
-
-        return modelPredictions.score(row.correct)
+        var pragModelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)
+
+        return pragModelPredictions.score(row.correct)
 
@@
 
-  var log_likelihood = sum(all_log_likes)
-  query.add(["log_like", "NA", "NA"], ["NA", log_likelihood])
+  var log_likelihood_prag = sum(all_log_likes_prag)
+  query.add(["log_like", "pragmatics", "NA"], ["NA", log_likelihood_prag])
+
+var all_log_likes_flat = map(function(row) { 
+      var prior = [row.prior, 1-row.prior]
+        var itemLineParameters = all_item_parameters[row.item]
+        var sem_knowledge = logistic(itemLineParameters.intercept + 
+            itemLineParameters.slope * row.age)
+
+     var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age
+
+        var flatModelPredictions = pragmaticListener({label: "novel_word"}, [.5, .5], speakerOptimality, sem_knowledge)
+
+        return flatModelPredictions.score(row.correct)
+
+    //  query.add(["prediction", item, row.age, row.alignment], ["NA", Math.exp(modelPredictions.score(1))])
+  // return loglike
+   }, dataFromR.comb_data)
+
+  var log_likelihood_flat = sum(all_log_likes_flat)
+  query.add(["log_like", "flat_prior", "NA"], ["NA", log_likelihood_flat])
 
@@
   inference_opts = list(method = "incrementalMH",
-                        samples = 100000,
-                        burn = 50000,
+                        samples = 100,
+                        burn = 100,
                         verbose = T,
@@
 log_like<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
+  separate(Parameter, into = c("parameter", "model","age","alignment"), sep = ",")%>%
   filter(parameter == "log_like")%>%
   separate(value, into = c("na", "log_like"),sep = ",")%>%
-  select(-na, -item, -age, -alignment)%>%
+  select(-na, -age, -alignment)%>%
   mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
-  group_by(Chain)%>%
+  group_by(model,Chain)%>%
   summarize(logP = logSumExp(log_like))

### 2019-09-18 stats/model.Rmd
update model file

--- 2019-09-16 stats/model.Rmd
@@
 data_comb_log
-
 ```
@@
                                itemLineParameters.slope * row.age)
-        var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age
-
-        var modelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)
-
-        return modelPredictions.score(row.correct)
-
-    //  query.add(["prediction", item, row.age, row.alignment], ["NA", Math.exp(modelPredictions.score(1))])
-  // return loglike
+
+  var global_sem_knowledge = logistic(globalLineParameters.intercept + 
+                               globalLineParameters.slope * row.age)
+
+  var speakerOptimality = speakerOptimalityParameters.intercept  + 
+      speakerOptimalityParameters.slope * row.age
+
+  var pragModelPredictions = pragmaticListener({label: "novel_word"}, 
+                                               prior, speakerOptimality, 
+                                               sem_knowledge)
+
+  var globalPragModelPredictions = pragmaticListener({label: "novel_word"}, 
+                                               prior, speakerOptimality, 
+                                               global_sem_knowledge)
+
+  var flatModelPredictions = pragmaticListener({label: "novel_word"}, 
+                                               [.5, .5], speakerOptimality, 
+                                               sem_knowledge)
+
+  return {
+    prag: pragModelPredictions.score(row.correct),
+    globalPrag: globalPragModelPredictions.score(row.correct),
+    flat: flatModelPredictions.score(row.correct),
+    priorOnly: Math.log(row.correct == 1 ? row.prior : 1 - row.prior)
+  }
+
 }, dataFromR.comb_data)
 
-  var log_likelihood = sum(all_log_likes)
-  query.add(["log_like", "NA", "NA"], ["NA", log_likelihood])
+var log_likelihood_prag = sum(_.map(all_log_likes, "prag"))
+var log_likelihood_prag_global = sum(_.map(all_log_likes, "globalPrag"))
+var log_likelihood_flat = sum(_.map(all_log_likes, "flat"))
+var log_likelihood_prior_only = sum(_.map(all_log_likes, "priorOnly"))
+
+query.add(["log_like", "pragmatics", "NA"], ["NA", log_likelihood_prag])
+query.add(["log_like", "pragmatics_global", "NA"], ["NA", log_likelihood_prag_global])
+query.add(["log_like", "flat_prior", "NA"], ["NA", log_likelihood_flat])
+query.add(["log_like", "prior_only", "NA"], ["NA", log_likelihood_prior_only])
 
@@
                         lag = 1,
-                        verboseLag = 1000)
+                        verboseLag = 5000)
 )
 
-#saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_log_like.rds")
+saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_model_comparison.rds")
 
@@
 log_like<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
+  separate(Parameter, into = c("parameter", "model","age","alignment"), sep = ",")%>%
   filter(parameter == "log_like")%>%
   separate(value, into = c("na", "log_like"),sep = ",")%>%
-  select(-na, -item, -age, -alignment)%>%
+  select(-na, -age, -alignment)%>%
   mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
-  group_by(Chain)%>%
-  summarize(logP = logSumExp(log_like))
-
-```
-
-## Flat prior model
-
-```{r work in progress}
-flat_prior <- '
-var data = dataFromR.data
-
-var priorProbs = [.5,.5]
-
-var familiars = levels(data, "familiar")
-var subjects = levels(data, "subid")
-
-var model  = function(){
-
-  var speakerOptimalityParameters = {
-    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 4, width: 0.5})
-  }
-
-  var globalLineParameters = {
-    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 2, width: 0.5})
-  }
-
-  var itemVariability = {
-    intercept: uniformDrift({a: 0, b: 2, width: 0.2}),
-    slope: uniformDrift({a: 0, b: 1, width: 0.2})
-  }
-
-  // conceptually it might not make sense to have two sigmas, but maybe it does
-  // intercept sigma probably will be smaller than slope sigma
-  // var item_int_sigma = uniformDrift({a: 0, b: 3, width: 0.2})
-
-  var sampleItemParameters = function(itemName) { 
-    return [itemName, {
-        intercept: gaussianDrift({
-          mu: globalLineParameters.intercept, 
-          sigma: itemVariability.intercept, 
-          width: 0.5
-        }),
-        slope: gaussianDrift({
-          mu: globalLineParameters.slope, 
-          sigma: itemVariability.slope, 
-          width: 0.5
-        })
-      }]
-  }
-
-  // {papaya: {int, slope}, bread: {int, slope}, ... }
-  var all_item_parameters = _.fromPairs(map(sampleItemParameters, familiars))
-
-  // want something that favors smaller values
-  var subject_sigma = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var sampleLinguisticCompetence = function(age){
-    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
-  }
-
-  foreach(function(subid){
-      var subjectData = _.filter(data, {subid: subid})
-      var subj_age = subjectData[0].age
-      var subj_linguistic_competence = sampleLinguisticCompetence(subj_age)
-
-     // display("age = " + subj_age + " ... intercept = " + subj_linguistic_competence)
-
-      // question: should we use age here instead of the random intercept? or a different random intercept?
-
-  var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_age
-
-      // each row is a different item
-      foreach(function(row){
-
-        var itemLineParameters = all_item_parameters[row.familiar]
-
-        var sem_knowledge = logistic(itemLineParameters.intercept + 
-            itemLineParameters.slope * subj_linguistic_competence)
-
-        var modelPredictions = pragmaticListener({label: "novel_word"}, 
-              priorProbs, speakerOptimality, sem_knowledge)
-        // display(modelPredictions.score(row.correct))
-
-        observe(modelPredictions, row.correct)
-
-        // if you want to save predictions, make sure to record subid because these predictions are for this particular subid
-        // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
-
-      }, subjectData)
-
-    // comment out to save memory
-  //  query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])
-
-  }, subjects)
-
-var all_log_likes = map(function(row) { 
-      var prior = [row.prior, 1-row.prior]
-        var itemLineParameters = all_item_parameters[row.item]
-        var sem_knowledge = logistic(itemLineParameters.intercept + 
-            itemLineParameters.slope * row.age)
-        var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age
-
-        var modelPredictions = pragmaticListener({label: "novel_word"}, [.5,.5], speakerOptimality, sem_knowledge)
-
-    //    display(modelPredictions.score(row.correct))
-
-        return modelPredictions.score(row.correct)
-
-    //  query.add(["prediction", item, row.age, row.alignment], ["NA", Math.exp(modelPredictions.score(1))])
-  // return loglike
-   }, dataFromR.comb_data)
-
-  var log_likelihood = sum(all_log_likes)
-  query.add(["log_like", "NA", "NA"], ["NA", log_likelihood])
-
-  foreach(function(item){
-    var itemLineParameters = all_item_parameters[item]
-    query.add(["parameter","items", item], [itemLineParameters.intercept, itemLineParameters.slope])
-  }, familiars)
-
-  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
-  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
-  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
-  query.add(["parameter","sigma", "global_subject_sigmas"], ["NA", subject_sigma])
-
-  return query 
-}
-'
-```
-
-```{r}
-
-sem_know_model_flat_prior<- webppl(
-  program_code = paste(rsaUtils, rsaModel, flat_prior , sep='\n'),
-  data = list(data = me_model_data, comb_data = data_comb_log),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "incrementalMH",
-                        samples = 100000,
-                        burn = 50000,
-                        verbose = T,
-                        lag = 1,
-                        verboseLag = 1000)
-)
-
-saveRDS(sem_know_model_flat_prior, "../saves/sem_know_model_variant3_100k_flat_prior_log_like.rds")
-
-model_pred<- sem_know_model_flat_prior %>%
-  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
-  filter(parameter == "prediction")%>%
-  separate(value, into = c("na", "me_effect"),sep = ",")%>%
-  select(-na)%>%
-  mutate(age = as.numeric(age),
-         me_effect =as.numeric(str_remove(me_effect,"[)]")))
-
-log_like_flat_prior<- sem_know_model_flat_prior %>%
-  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
-  filter(parameter == "log_like")%>%
-  separate(value, into = c("na", "log_like"),sep = ",")%>%
-  select(-na, -item, -age, -alignment)%>%
-  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
-  group_by(Chain)%>%
+  group_by(model, Chain)%>%
   summarize(logP = logSumExp(log_like))

### 2019-09-19 stats/model.Rmd
clean up model file and add model run

@@
 
-## Model utilities
+# Model utilities
 
@@
 
-# Inferring semantic knowledge
+# Model (nesting within participant)
+
+## Prepare data
+
+```{r}
+me_model_data <- read_csv("../data/me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
+
+novel_bm <- readRDS("../saves/novelty_model.rds")
+
+#summary(novel_bm)
+
+novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
+  select(term,Estimate)%>%
+  spread(term, Estimate)
+
+data_comb_log <- read_csv("../data/combination.csv") %>%
+  filter(condition != "train")%>%
+  mutate(alignment = condition,
+         item = familiarObject, 
+         age = age_num - (min(age_num))) %>%
+  mutate(nov_int = novel_params$Intercept,
+         nov_slope = novel_params$age_num,
+         prior = ifelse(alignment == "congruent", plogis(nov_int + nov_slope* age),1-plogis(nov_int + age * nov_slope)))
+
+data_comb_log
+```
+
+## Model code
+
+```{r work in progress}
+sem_subj_str <- '
+var data = dataFromR.data
+
+var priorProbs = [.5,.5]
+
+var familiars = levels(data, "familiar")
+var subjects = levels(data, "subid")
+
+var model  = function(){
+
+  var speakerOptimalityParameters = {
+    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
+    slope: uniformDrift({a: 0, b: 4, width: 0.5})
+  }
+
+  var globalLineParameters = {
+    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
+    slope: uniformDrift({a: 0, b: 2, width: 0.5})
+  }
+
+  var itemVariability = {
+    intercept: uniformDrift({a: 0, b: 2, width: 0.2}),
+    slope: uniformDrift({a: 0, b: 1, width: 0.2})
+  }
+
+  // conceptually it might not make sense to have two sigmas, but maybe it does
+  // intercept sigma probably will be smaller than slope sigma
+  // var item_int_sigma = uniformDrift({a: 0, b: 3, width: 0.2})
+
+  var sampleItemParameters = function(itemName) { 
+    return [itemName, {
+        intercept: gaussianDrift({
+          mu: globalLineParameters.intercept, 
+          sigma: itemVariability.intercept, 
+          width: 0.5
+        }),
+        slope: gaussianDrift({
+          mu: globalLineParameters.slope, 
+          sigma: itemVariability.slope, 
+          width: 0.5
+        })
+      }]
+  }
+
+  // {papaya: {int, slope}, bread: {int, slope}, ... }
+  var all_item_parameters = _.fromPairs(map(sampleItemParameters, familiars))
+
+  // want something that favors smaller values
+  var subject_sigma = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var sampleLinguisticCompetence = function(age){
+    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
+  }
+
+  foreach(function(subid){
+      var subjectData = _.filter(data, {subid: subid})
+      var subj_age = subjectData[0].age
+      var subj_linguistic_competence = sampleLinguisticCompetence(subj_age)
+
+     // display("age = " + subj_age + " ... intercept = " + subj_linguistic_competence)
+
+      // question: should we use age here instead of the random intercept? or a different random intercept?
+
+  var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_age
+
+      // each row is a different item
+      foreach(function(row){
+
+        var itemLineParameters = all_item_parameters[row.familiar]
+
+        var sem_knowledge = logistic(itemLineParameters.intercept + 
+            itemLineParameters.slope * subj_linguistic_competence)
+
+        var modelPredictions = pragmaticListener({label: "novel_word"}, 
+              priorProbs, speakerOptimality, sem_knowledge)
+        // display(modelPredictions.score(row.correct))
+
+        observe(modelPredictions, row.correct)
+
+        // if you want to save predictions, make sure to record subid because these predictions are for this particular subid
+        // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
+
+      }, subjectData)
+
+    // comment out to save memory
+  //  query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])
+
+  }, subjects)
+
+var all_log_likes = map(function(row) { 
+  var prior = [row.prior, 1-row.prior]
+  var itemLineParameters = all_item_parameters[row.item]
+  var sem_knowledge = logistic(itemLineParameters.intercept + 
+                               itemLineParameters.slope * row.age)
+
+  var global_sem_knowledge = logistic(globalLineParameters.intercept + 
+                               globalLineParameters.slope * row.age)
+
+  var speakerOptimality = speakerOptimalityParameters.intercept  + 
+      speakerOptimalityParameters.slope * row.age
+
+  var pragModelPredictions = pragmaticListener({label: "novel_word"}, 
+                                               prior, speakerOptimality, 
+                                               sem_knowledge)
+
+  var globalPragModelPredictions = pragmaticListener({label: "novel_word"}, 
+                                               prior, speakerOptimality, 
+                                               global_sem_knowledge)
+
+  var flatModelPredictions = pragmaticListener({label: "novel_word"}, 
+                                               [.5, .5], speakerOptimality, 
+                                               sem_knowledge)
+
+  return {
+    prag: pragModelPredictions.score(row.correct),
+    globalPrag: globalPragModelPredictions.score(row.correct),
+    flat: flatModelPredictions.score(row.correct),
+    priorOnly: Math.log(row.correct == 1 ? row.prior : 1 - row.prior)
+  }
+
+}, dataFromR.comb_data)
+
+var log_likelihood_prag = sum(_.map(all_log_likes, "prag"))
+var log_likelihood_prag_global = sum(_.map(all_log_likes, "globalPrag"))
+var log_likelihood_flat = sum(_.map(all_log_likes, "flat"))
+var log_likelihood_prior_only = sum(_.map(all_log_likes, "priorOnly"))
+
+query.add(["log_like", "pragmatics", "NA"], ["NA", log_likelihood_prag])
+query.add(["log_like", "pragmatics_global", "NA"], ["NA", log_likelihood_prag_global])
+query.add(["log_like", "flat_prior", "NA"], ["NA", log_likelihood_flat])
+query.add(["log_like", "prior_only", "NA"], ["NA", log_likelihood_prior_only])
+
+  foreach(function(item){
+    var itemLineParameters = all_item_parameters[item]
+    query.add(["parameter","items", item], [itemLineParameters.intercept, itemLineParameters.slope])
+  }, familiars)
+
+  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
+  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
+  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
+  query.add(["parameter","sigma", "global_subject_sigmas"], ["NA", subject_sigma])
+
+  return query 
+}
+'
+```
+
+## Model run
+
+```{r}
+
+sem_know_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
+  data = list(data = me_model_data, comb_data = data_comb_log),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 3,
+  cores = 3,
+  inference_opts = list(method = "incrementalMH",
+                        samples = 100000,
+                        burn = 50000,
+                        verbose = T,
+                        lag = 1,
+                        verboseLag = 1000)
+)
+
+saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_model_comparison.rds")
+
+sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k_model_comparison.rds")
+
+```
+
+## Summarizing parameters
+
+```{r}
+
+# model_pred <- sem_know_model %>%
+#   separate(Parameter, into = c("type", "item","x"))%>%
+#   filter(type == "modelPrediction")%>%
+#   separate(value, into = c("age", "pred"),sep = ", ")%>%
+#   mutate(age = as.numeric(str_remove_all(age, "[(c]")),
+#          pred = as.numeric(str_remove(pred, "[)]")))%>%
+#   select(-x)
+
+item_params<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
+  filter(parameter == "parameter", type == "items")%>%
+  separate(value, into = c("int", "slope"),sep = ", ")%>%
+  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]")))%>%
+  gather(parameter, value, int, slope)
+
+global_params <- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
+  filter(parameter == "parameter", type == "parameters")%>%
+    separate(value, into = c("int", "slope"),sep = ", ")%>%
+    mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]")))%>%
+    gather(parameter, value, int, slope)
+
+global_sigma<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
+  filter(parameter == "parameter", type == "sigma", token != "global_subject_sigmas")%>%
+    separate(value, into = c("sigma_int", "sigma_slope"),sep = ", ")%>%
+    mutate(sigma_int = as.numeric(str_remove_all(sigma_int, "[(c]")),
+         sigma_slope = as.numeric(str_remove(sigma_slope, "[)]")))%>%
+    gather(parameter, value, sigma_int, sigma_slope)
+
+subj_sigma<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
+  filter(parameter == "parameter", token == "global_subject_sigmas")%>%
+  separate(value, into = c("na", "sigma"),sep = ", ")%>%
+  select(-na)%>%
+  mutate(sigma = as.numeric(str_remove(sigma, "[)]")))
+
+subject_params<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "type","id"), sep = ",")%>%
+  filter(parameter == "parameter", type == "subj_intercept")%>%
+  separate(value, into = c("na", "int"),sep = ", ")%>%
+  select(-na)%>%
+  mutate(int = as.numeric(str_remove(int, "[)]")))
+
+model_pred<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
+  filter(parameter == "prediction")%>%
+  separate(value, into = c("na", "me_effect"),sep = ",")%>%
+  select(-na)%>%
+  mutate(age = as.numeric(age),
+         me_effect =as.numeric(str_remove(me_effect,"[)]")))
+
+#### summaries
+
+# model_pred_summary <- model_pred %>%
+#   group_by(item,age)%>%
+#   summarise(mode = estimate_mode(pred),
+#             uci = hdi_upper(pred),
+#             lci = hdi_lower(pred))
+
+item_params_summary <- item_params %>%
+  group_by(item, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+global_params_summary <- global_params %>%
+  group_by(token, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+```
+## Plotting model parameters
+
+### Semantic knowledge
+
+```{r}
+plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(parameter~item, scales = 'free')+
+  theme_few()
+
+plot_item_params
+```
+
+```{r}
+#ggsave("../graphs/item_params_by_chain.pdf", width = 8, height = 3, scale = 1.5)
+```
+
+### Global parameters
+
+```{r}
+
+plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(parameter~token, scales = 'free')+
+  theme_few()
+
+plot_global_params
+```
+
+### Global sigmas
+
+```{r}
+plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Sigma")+
+  facet_grid(~parameter, scales = 'free')+
+  theme_few()
+
+plot_global_sigma
+```
+
+```{r}
+plotg_subj_sigma <- ggplot(subj_sigma, aes(x = sigma, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Subject Sigma")+
+  theme_few()
+
+plotg_subj_sigma
+```
+
+```{r}
+
+select_id <- me_model_data %>%
+  filter(age < 1.3,
+         age >1)%>%
+  group_by(age,subid)%>%
+  summarise(mean = mean(correct))%>%
+  mutate(id = subid)
+
+subject_params <- subject_params %>%
+  left_join(select_id)%>%
+  filter(mean != "NA")%>%
+  ungroup()
+
+ggplot(subject_params, aes(x = int, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  geom_vline(aes(xintercept = age), size = 1.5)+
+  #geom_vline(aes(xintercept = mean), size = 1.5, col = "red")+
+  facet_grid(id+ round(mean,2)~.)+
+  xlab("Subject Intercept")+
+  theme_few()
+
+#ggsave("../graphs/subj_intercept.pdf", width = 5, height = 8, scale = 1.5)
+
+```
+
+## Plotting semantic knowledge
+
+```{r}
+aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
+
+aoa_ratings <- aoa_ratings_all %>%
+  filter(Word %in% item_params_summary$item )%>%
+  mutate(mean_aoa = as.numeric(Rating.Mean),
+         item = Word)%>%
+  select(item,mean_aoa)
+
+plot_sem_know <- item_params_summary%>%
+  select(-uci,-lci)%>%
+  spread(parameter, -item) %>%
+  left_join(expand.grid(
+      age = unique(me_model_data$age),
+      item = unique(me_model_data$familiar)), .) %>%
+  mutate(sem_know = plogis(int + slope * age)) %>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+ggplot(plot_sem_know, aes(x = age+2, y= sem_know, col = item, group = item))+
+  geom_line(size = 1)+
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_few()+
+  scale_colour_viridis_d(name = "familiar object")
+```
+
+# MAP based inverse predictions for ME data
+
+```{r}
+# speak_opt_params <- speak_opt %>%
+#   group_by(parameter)%>%
+#   summarise(mode = estimate_mode(value),
+#             uci = hdi_upper(value),
+#             lci = hdi_lower(value))
+#
+
+inv_model_data <- item_params_summary%>%
+  select(-uci,-lci)%>%
+  spread(parameter, mode)%>%
+  tidyr::expand(item, int,slope,age = unique(me_model_data$age- min(me_model_data$age)))%>%
+  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
+         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode))%>%
+  mutate(speaker_optimality = so_int + so_slope * age,
+         semantic_knowledge = plogis(int + slope * age))
+
+```
+
+```{r}
+invPred <- '
+var allData = dataFromR.data
+
+var priorProbs = [.5,.5]
+
+var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, row.speaker_optimality,row.semantic_knowledge)
+
+    return extend([row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])
+
+}, allData)
+
+output
+
+'
+```
+
+```{r predictions pragmatic model ex 3 adults}
+inv_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
+  data =list(data = inv_model_data),
+  data_var = "dataFromR"
+)
+# 
+# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
+# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
+# 
+inv_predictions <- inv_model_pred %>%
+  separate(`0`, into = c("item", "age"), sep="/")%>%
+  mutate(age = as.numeric(age))%>%
+  dplyr::rename( me_effect = `1`)%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         age = age + min(me_data$age_num))
+```
+
+```{r}
+# plot_model_pred <- model_pred_summary%>%
+#   left_join(aoa_ratings) %>%
+#   ungroup()%>%
+#   mutate(item = fct_reorder(factor(item), mean_aoa))
+
+model_plot <- ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(size = 1)+
+  ggtitle("Inverse Model Predictions")+
+  labs(x="Age",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d()
+
+model_plot
+```
+
+```{r}
+p2 <- read_csv("../data/me.csv")%>%
+  filter(trial != "train1",
+         trial != "train2")%>%
+  mutate(item = familiar)%>%
+    left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(familiar = fct_reorder(factor(item), mean_aoa))
+
+data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  #facet_grid(~familiar)+
+  ggtitle("Data")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d(name = "familiar object")+
+  scale_fill_viridis_d(name = "familiar object")
+
+```
+
+```{r}
+ggarrange(data_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
+```
+
+## For comparison: GLMM for ME effect and data
+
+```{r}
+me_data <- read_csv("../data/me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(z_age = age_num - mean(age_num))
+
+# me_model <- brm(correct ~ z_age + (1|subid) + (z_age | familiar),
+#                 data = me_data,
+#                 family = bernoulli(),
+#                 control = list(adapt_delta = 0.95),
+#                 sample_prior = F,
+#                 save_all_pars = TRUE,
+#                 iter = 2000)
+
+#saveRDS(me_model, "../saves/me_effect_model.rds")
+
+me_model <- readRDS("../saves/me_effect_model.rds")
+
+summary(me_model)
+
+fixef <- as_tibble(fixef(me_model), rownames = "term")
+
+ranef <-  ranef(me_model)
+
+age_me_effect <- as_data_frame(ranef$familiar, rownames = "familiar")%>%
+  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
+         grand_slope = fixef%>%filter(term=="z_age")%>%pull(Estimate))%>%
+  group_by(familiar) %>%
+  tidyr::expand(Estimate.Intercept,Estimate.z_age,grand_intercept,grand_slope,z_age = me_data$age_num - mean(me_data$age_num), mean_age = mean(me_data$age_num))%>%
+  mutate(me_effect = plogis(grand_intercept + Estimate.Intercept+(Estimate.z_age+grand_slope)*z_age), 
+         age = z_age+mean_age,
+         item = familiar)%>%
+  select(item, me_effect, age)%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+glmm_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = item))+
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(size = 1)+
+  ggtitle("GLMM")+
+  labs(x="Age",y="Proportion correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d(name = "familiar object")
+
+```
+
+```{r}
+ggarrange(data_plot,model_plot,glmm_plot, common.legend = T, legend = "right", nrow = 1, ncol = 3)
+```
+
+# MAP based Model predictions for combination
+
+```{r}
+# novelty data
+
+novel_data <- read_csv("../data/novelty.csv")%>%
+  mutate(age_num = age_num-min(age_num))
+
+# novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
+#           data = novel_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.95),
+#           sample_prior = F,
+#           save_all_pars = F,
+#           iter = 10000)
+# 
+# saveRDS(novel_bm, "../saves/novelty_model.rds")
+
+novel_bm <- readRDS("../saves/novelty_model.rds")
+
+#summary(novel_bm)
+
+novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
+  select(term,Estimate)%>%
+  spread(term, Estimate)
+
+comb_model_data_con <- inv_model_data %>%
+  mutate(nov_int = novel_params$Intercept,
+         nov_slope = novel_params$age_num,
+         prior = plogis(nov_int + age * nov_slope),
+         alignment = "congruent")
+
+comb_model_data_incon <- inv_model_data %>%
+  mutate(nov_int = novel_params$Intercept,
+         nov_slope = novel_params$age_num,
+         prior = 1- plogis(nov_int + age * nov_slope),
+         alignment = "incongruent")
+
+comb_model_data <- bind_rows(
+  comb_model_data_con,
+  comb_model_data_incon)
+```
+
+```{r}
+combPred <- '
+var allData = dataFromR.data
+
+var output = map(function(row){
+
+    var prior = [row.prior, 1-row.prior]
+
+    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.semantic_knowledge)
+
+    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])
+
+}, allData)
+
+output
+
+'
+```
+
+```{r predictions pragmatic model ex 3 adults}
+comb_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
+  data =list(data = comb_model_data),
+  data_var = "dataFromR"
+)
+
+comb_model_predictions <- comb_model_pred %>%
+  separate(`0`, into = c("alignment","item", "age"), sep="/")%>%
+  mutate(age = as.numeric(age))%>%
+  dplyr::rename( me_effect = `1`)%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         age = age + min(me_data$age_num),
+         source = "Model")
+
+```
+
+```{r}
+p_comb_model <- ggplot(comb_model_predictions, aes(x=age,y = me_effect, col = item))+
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(size = 1)+
+  ggtitle("Combination Model Predictions")+
+  labs(x="Age",y="Proportion correct")+
+  facet_grid(~alignment)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d()
+
+p_comb_model
+```
+
+```{r}
+data_comb <- read_csv("../data/combination.csv") %>%
+  filter(condition != "train")%>%
+  mutate(alignment = condition,
+         item = familiarObject)%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(familiarObject), mean_aoa), 
+         source = "Data")
+
+p_comb_data <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = item, fill = item)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
+  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(~alignment)+
+  ggtitle("Combination Data")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d()+
+  scale_fill_viridis_d()
+```
+
+```{r}
+ggarrange(p_comb_model,p_comb_data, common.legend = T, legend = "right", nrow = 2, ncol = 1)
+```
+
+```{r}
+#ggsave("../graphs/combination_model_data.pdf", width = 7, height = 7, scale = 1)
+```
+
+```{r}
+p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
+  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
+  geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
+  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  #facet_grid(condition~familiarObject)+
+  facet_grid(~item)+
+  #ggtitle("Combination Data")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+
+p_data_model
+```
+
+```{r}
+ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 3, scale = 1.5)
+```
+
+## Correlate model predictions and data
+
+```{r}
+binnned_data <- data_comb%>%
+  group_by(subage, alignment, item)%>%
+  summarize(k = sum(correct), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         data_mean = (a-1)/(a+b-2),
+         data_ci_lower  = qbeta(.025, a, b),
+         data_ci_upper = qbeta(.975, a, b),
+         subage = factor(subage))%>%
+  select(-a,-b,-n,-k)
+
+binned_model <- comb_model_predictions %>%
+  mutate(subage = cut(age, 
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(subage, alignment, item)%>%
+  summarise(model_mean = estimate_mode(me_effect),
+            model_ci_lower = hdi_lower(me_effect),
+            model_ci_upper = hdi_upper(me_effect))
+
+cor_plot <- left_join(
+  binnned_data,
+  binned_model)
+
+ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
+  geom_point(size = 2,  stroke = 1)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(~subage)+
+  theme_few() + 
+  scale_colour_viridis_d(name ="Item")
+```
+
+```{r}
+#ggsave("../graphs/combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
+```
+
+```{r}
+ggarrange(
+plot_item_params,
+plot_global_params,
+p_data_model, plot_global_sigma,
+ncol = 2, nrow = 2, common.legend = F, widths = c(3,1))
+
+ggsave("../graphs/overview_variant_3_100k.png", width = 12, height = 4, scale = 1.2)
+
+```
+
+## Model compatison
+
+```{r}
+log_like<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "model","age","alignment"), sep = ",")%>%
+  filter(parameter == "log_like")%>%
+  separate(value, into = c("na", "log_like"),sep = ",")%>%
+  select(-na, -age, -alignment)%>%
+  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
+  group_by(model,Chain)%>%
+  summarize(logP = logSumExp(log_like))
+```
+
+## Plotting model predictions
+
+```{r}
+model_pred<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
+  filter(parameter == "prediction")%>%
+  separate(value, into = c("na", "me_effect"),sep = ",")%>%
+  select(-na)%>%
+  mutate(age = as.numeric(age),
+         me_effect =as.numeric(str_remove(me_effect,"[)]")))
+
+comb_model_pred_agg <- model_pred%>%
+  group_by(Chain, alignment,item,age)%>%
+  summarise(mean = estimate_mode(me_effect),
+            uci = hdi_upper(me_effect),
+            lci = hdi_lower(me_effect))%>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         age = age + min(me_data$age_num),
+         Chain = factor(Chain))
+
+ggplot(comb_model_pred_agg, aes(x=age,y = mean, col = item, fill = item))+
+  geom_ribbon(aes(ymin = lci, ymax = uci), alpha = .5, colour = NA)+
+  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col), col = "black", fill = "grey",  method = "loess", se = F, alpha = .2, span = 2)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(size = 1)+
+  ggtitle("Combination Model Predictions")+
+  labs(x="Age",y="Proportion correct")+
+  facet_grid(Chain ~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_viridis_d()+
+  scale_fill_viridis_d()
+
+```
+
+```{r}
+ggsave("../graphs/model_pred_data.pdf", width = 20, height = 8, scale = 1.2)
+```
+
+# OLD: Comparing parameters between model runs
+
+## sem knowledge
+
+```{r}
+
+sem_know_run_summary <- item_params%>%
+  spread(parameter,value)%>%
+  group_by(Chain,item)%>%
+  summarise(overall_int = estimate_mode(int),
+            overall_slope = estimate_mode(slope))
+
+sem_know_run_iteration <- item_params%>%
+  spread(parameter,value)
+
+sem_know_chain <- sem_know_run_iteration %>%
+  left_join(sem_know_run_summary)
+
+chain_comp <- sem_know_chain %>%
+  left_join(expand.grid(
+      age = unique(me_model_data$age),
+      item = unique(me_model_data$familiar)), .) %>%
+  mutate(sem_know_ci = plogis(int + slope * age),
+         sem_know = plogis(overall_int + overall_slope * age)) %>%
+  group_by(Chain,item, age) %>%
+  summarise(sem_know = estimate_mode(sem_know),
+            sem_know_uci = hdi_upper(sem_know_ci),
+            sem_know_lci = hdi_lower(sem_know_ci))
+
+ggplot(chain_comp, aes(x = age+2, y= sem_know, fill = factor(Chain)))+
+  geom_line(size = .3, aes(col = factor(Chain)))+
+  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .05)+
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  facet_wrap(~item, nrow = 3)+
+  theme_few()+
+  scale_colour_discrete()+
+  scale_fill_discrete()
+
+```
+
+## speaker optimality
+
+```{r}
+
+so_run_iteration <- global_params%>%
+  spread(parameter, value)
+
+so_run_summary <- so_run_iteration%>%
+  group_by(Chain)%>%
+  summarise(overall_int = estimate_mode(int),
+            overall_slope = estimate_mode(slope))
+
+so_run <- so_run_iteration %>%
+  left_join(so_run_summary)
+
+so_run_comp <-so_run%>%
+  group_by(Chain,Iteration)%>%
+  tidyr::expand(int,slope,overall_int,overall_slope,age = unique(me_model_data$age))%>%
+  mutate(so_ci = int + slope * age,
+         so = overall_int + overall_slope * age) %>%
+  group_by(Chain, age) %>%
+  summarise(so = estimate_mode(so),
+            so_uci = hdi_upper(so_ci),
+            so_lci = hdi_lower(so_ci))
+
+ggplot(so_run_comp, aes(x = age+2, y= so, fill = factor(Chain)))+
+  geom_line(size = .4, aes(col = factor(Chain)))+
+  geom_ribbon(aes(ymin=so_lci, ymax = so_uci), alpha = .05)+
+  ylab("speaker optimality")+
+  xlab("Age")+
+  #facet_grid(~run)+
+  theme_few()+
+  scale_colour_discrete()+
+  scale_fill_discrete()
+
+```
+
+## Correlations between parameters for semantic knowledge
+
+```{r}
+ggplot(item_params%>%filter(parameter == "int"), aes(x = value))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(Chain~item, scales = 'free')+
+  theme_few()
+
+#ggsave("../graphs/item_by_chain.pdf", width = 15, height = 15, scale = 1.5)
+```
+
+```{r}
+item_params_cor <- item_params %>%
+  group_by(Chain,item, parameter)%>%
+  summarise(mode = estimate_mode(value))
+```
+
+```{r}
+library(corrr)
+library(corrplot)
+
+## correaltion at 2
+cor_int_2 <- item_params_cor%>%
+  spread(Chain, mode) %>%
+  filter(parameter == "int")%>%
+  select(-parameter)%>%
+  ungroup()%>%
+  select(-item)%>%
+  correlate(method = "spearman")%>%
+  gather(key, value)%>%
+  filter(key !="rowname")%>%
+  na.omit()%>%
+  mutate(value = as.numeric(value),
+         age = "2")
+
+cor_int_3 <- item_params_cor%>%
+  spread(parameter, mode)%>%
+  mutate(mode = int + slope)%>%
+  select(Chain, item, mode)%>%
+  spread(Chain, mode)%>%
+  ungroup()%>%
+  select(-item)%>%
+  correlate(method = "spearman")%>%
+  gather(key, value)%>%
+  filter(key !="rowname")%>%
+  na.omit()%>%
+  mutate(value = as.numeric(value),
+         age = "3")
+
+cor_int_4 <- item_params_cor%>%
+  spread(parameter, mode)%>%
+  mutate(mode = int + 2*slope)%>%
+  select(Chain, item, mode)%>%
+  spread(Chain, mode)%>%
+  ungroup()%>%
+  select(-item)%>%
+  correlate(method = "spearman")%>%
+  gather(key, value)%>%
+  filter(key !="rowname")%>%
+  na.omit()%>%
+  mutate(value = as.numeric(value),
+         age = "4")
+
+cor_int_5 <- item_params_cor%>%
+  spread(parameter, mode)%>%
+  mutate(mode = int + 3*slope)%>%
+  select(Chain, item, mode)%>%
+  spread(Chain, mode)%>%
+  ungroup()%>%
+  select(-item)%>%
+  correlate(method = "spearman")%>%
+  gather(key, value)%>%
+  filter(key !="rowname")%>%
+  na.omit()%>%
+  mutate(value = as.numeric(value),
+         age = "5")
+
+cor_hist <- 
+bind_rows(
+  cor_int_2,
+  cor_int_3,
+  cor_int_4,
+  cor_int_5
+)
+
+ggplot(cor_hist, aes(x = value, fill =age))+
+  geom_density(alpha = .5)+
+  xlim(-1,1)+
+  xlab("Correlation")+
+  theme_few()
+
+#ggsave("../graphs/corr_int_by_age.pdf", width = 5, height = 4, scale = 1.5)
+
+```
+
+# Model (No nesting within participants)
 ```{r}
@@
 ```
-
-# Model runs
-
-```{r}
-
-sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k_log_like.rds")
-
-#saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_ind.rds")
-
-```
-
-# Summarizing parameters
-
-```{r}
-
-# model_pred <- sem_know_model %>%
-#   separate(Parameter, into = c("type", "item","x"))%>%
-#   filter(type == "modelPrediction")%>%
-#   separate(value, into = c("age", "pred"),sep = ", ")%>%
-#   mutate(age = as.numeric(str_remove_all(age, "[(c]")),
-#          pred = as.numeric(str_remove(pred, "[)]")))%>%
-#   select(-x)
-
-item_params<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
-  filter(parameter == "parameter", type == "items")%>%
-  separate(value, into = c("int", "slope"),sep = ", ")%>%
-  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]")))%>%
-  gather(parameter, value, int, slope)
-
-global_params <- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
-  filter(parameter == "parameter", type == "parameters")%>%
-    separate(value, into = c("int", "slope"),sep = ", ")%>%
-    mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]")))%>%
-    gather(parameter, value, int, slope)
-
-global_sigma<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
-  filter(parameter == "parameter", type == "sigma", token != "global_subject_sigmas")%>%
-    separate(value, into = c("sigma_int", "sigma_slope"),sep = ", ")%>%
-    mutate(sigma_int = as.numeric(str_remove_all(sigma_int, "[(c]")),
-         sigma_slope = as.numeric(str_remove(sigma_slope, "[)]")))%>%
-    gather(parameter, value, sigma_int, sigma_slope)
-
-subj_sigma<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
-  filter(parameter == "parameter", token == "global_subject_sigmas")%>%
-  separate(value, into = c("na", "sigma"),sep = ", ")%>%
-  select(-na)%>%
-  mutate(sigma = as.numeric(str_remove(sigma, "[)]")))
-
-subject_params<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","id"), sep = ",")%>%
-  filter(parameter == "parameter", type == "subj_intercept")%>%
-  separate(value, into = c("na", "int"),sep = ", ")%>%
-  select(-na)%>%
-  mutate(int = as.numeric(str_remove(int, "[)]")))
-
-model_pred<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
-  filter(parameter == "prediction")%>%
-  separate(value, into = c("na", "me_effect"),sep = ",")%>%
-  select(-na)%>%
-  mutate(age = as.numeric(age),
-         me_effect =as.numeric(str_remove(me_effect,"[)]")))
-
-#### summaries
-
-# model_pred_summary <- model_pred %>%
-#   group_by(item,age)%>%
-#   summarise(mode = estimate_mode(pred),
-#             uci = hdi_upper(pred),
-#             lci = hdi_lower(pred))
-
-item_params_summary <- item_params %>%
-  group_by(item, parameter)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
-global_params_summary <- global_params %>%
-  group_by(token, parameter)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
-```
-# Plotting model parameters
-
-```{r}
-plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Parameter")+
-  facet_grid(parameter~item, scales = 'free')+
-  theme_few()
-
-plot_item_params
-```
-
-```{r}
-#ggsave("../graphs/item_params_by_chain.pdf", width = 8, height = 3, scale = 1.5)
-```
-
-```{r}
-
-plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Parameter")+
-  facet_grid(parameter~token, scales = 'free')+
-  theme_few()
-
-plot_global_params
-```
-
-```{r}
-plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Sigma")+
-  facet_grid(~parameter, scales = 'free')+
-  theme_few()
-
-plot_global_sigma
-```
-
-```{r}
-plotg_subj_sigma <- ggplot(subj_sigma, aes(x = sigma, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Subject Sigma")+
-  theme_few()
-
-plotg_subj_sigma
-```
-
-```{r}
-
-select_id <- me_model_data %>%
-  filter(age < 1.3,
-         age >1)%>%
-  group_by(age,subid)%>%
-  summarise(mean = mean(correct))%>%
-  mutate(id = subid)
-
-subject_params <- subject_params %>%
-  left_join(select_id)%>%
-  filter(mean != "NA")%>%
-  ungroup()
-
-ggplot(subject_params, aes(x = int, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  geom_vline(aes(xintercept = age), size = 1.5)+
-  #geom_vline(aes(xintercept = mean), size = 1.5, col = "red")+
-  facet_grid(id+ round(mean,2)~.)+
-  xlab("Subject Intercept")+
-  theme_few()
-
-#ggsave("../graphs/subj_intercept.pdf", width = 5, height = 8, scale = 1.5)
-
-```
-
-## Plotting semantic knowledge
-```{r}
-aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
-
-aoa_ratings <- aoa_ratings_all %>%
-  filter(Word %in% item_params_summary$item )%>%
-  mutate(mean_aoa = as.numeric(Rating.Mean),
-         item = Word)%>%
-  select(item,mean_aoa)
-
-plot_sem_know <- item_params_summary%>%
-  select(-uci,-lci)%>%
-  spread(parameter, -item) %>%
-  left_join(expand.grid(
-      age = unique(me_model_data$age),
-      item = unique(me_model_data$familiar)), .) %>%
-  mutate(sem_know = plogis(int + slope * age)) %>%
-  left_join(aoa_ratings) %>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-ggplot(plot_sem_know, aes(x = age+2, y= sem_know, col = item, group = item))+
-  geom_line(size = 1)+
-  ylab("Semantic knowledge")+
-  xlab("Age")+
-  ylim(0,1)+
-  theme_few()+
-  scale_colour_viridis_d(name = "familiar object")
-```
-
-### Comparing parameters between model runs
-
-#### sem knowledge
-
-```{r}
-# me_model_data <- read_csv("../data/me.csv")%>%
-#     filter(trial != "train1",
-#            trial != "train2")%>%
-#   mutate(age = age_num - min(age_num))
-# 
-# sem_know_run_summary <- item_params%>%
-#   spread(parameter,value)%>%
-#   group_by(Chain,item)%>%
-#   summarise(overall_int = estimate_mode(int),
-#             overall_slope = estimate_mode(slope))
-# 
-# 
-# sem_know_run_iteration <- item_params%>%
-#   spread(parameter,value)
-# 
-# sem_know_chain <- sem_know_run_iteration %>%
-#   left_join(sem_know_run_summary)
-# 
-# chain_comp <- sem_know_chain %>%
-#   left_join(expand.grid(
-#       age = unique(me_model_data$age),
-#       item = unique(me_model_data$familiar)), .) %>%
-#   mutate(sem_know_ci = plogis(int + slope * age),
-#          sem_know = plogis(overall_int + overall_slope * age)) %>%
-#   group_by(Chain,item, age) %>%
-#   summarise(sem_know = estimate_mode(sem_know), 
-#             sem_know_uci = hdi_upper(sem_know_ci),
-#             sem_know_lci = hdi_lower(sem_know_ci))
-# 
-# ggplot(chain_comp, aes(x = age+2, y= sem_know, fill = factor(Chain)))+
-#   geom_line(size = .3, aes(col = factor(Chain)))+
-#   geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .05)+
-#   ylab("Semantic knowledge")+
-#   xlab("Age")+
-#   ylim(0,1)+
-#   facet_wrap(~item, nrow = 3)+
-#   theme_few()+
-#   scale_colour_discrete()+
-#   scale_fill_discrete()
-
-#ggsave("../graphs/model_by_chain.pdf", width = 5, height = 4, scale = 1.5)
-```
-
-#### speaker optimality
-
-```{r}
-# me_model_data <- read_csv("../data/me.csv")%>%
-#     filter(trial != "train1",
-#            trial != "train2")%>%
-#   mutate(age = age_num - min(age_num))
-# 
-# so_run_iteration <- global_params%>%
-#   spread(parameter, value)
-# 
-# so_run_summary <- so_run_iteration%>%
-#   group_by(Chain)%>%
-#   summarise(overall_int = estimate_mode(int),
-#             overall_slope = estimate_mode(slope))
-# 
-# so_run <- so_run_iteration %>%
-#   left_join(so_run_summary)
-# 
-# so_run_comp <-so_run%>%
-#   group_by(Chain,Iteration)%>%
-#   tidyr::expand(int,slope,overall_int,overall_slope,age = unique(me_model_data$age))%>%
-#   mutate(so_ci = int + slope * age,
-#          so = overall_int + overall_slope * age) %>%
-#   group_by(Chain, age) %>%
-#   summarise(so = estimate_mode(so), 
-#             so_uci = hdi_upper(so_ci),
-#             so_lci = hdi_lower(so_ci))
-# 
-# ggplot(so_run_comp, aes(x = age+2, y= so, fill = factor(Chain)))+
-#   geom_line(size = .4, aes(col = factor(Chain)))+
-#   geom_ribbon(aes(ymin=so_lci, ymax = so_uci), alpha = .05)+
-#   ylab("speaker optimality")+
-#   xlab("Age")+
-#   #facet_grid(~run)+
-#   theme_few()+
-#   scale_colour_discrete()+
-#   scale_fill_discrete()
-# 
-# ggsave("../graphs/so_by_chain.pdf", width = 4, height = 3, scale = 1.5)
-```
-
-#### Correlations between parameters for semantic knowledge
-
-```{r}
-# sem_know_model_1<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-#   data = list(data = me_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 10,
-#   cores = 10,
-#   inference_opts = list(method = "incrementalMH",
-#                         samples = 4000,
-#                         burn = 2000,
-#                         verbose = T,
-#                         lag = 1,
-#                         verboseLag = 1000)
-# )
-# 
-# sem_know_model_2<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-#   data = list(data = me_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 10,
-#   cores = 10,
-#   inference_opts = list(method = "incrementalMH",
-#                         samples = 4000,
-#                         burn = 2000,
-#                         verbose = T,
-#                         lag = 1,
-#                         verboseLag = 1000)
-# )%>%
-#   mutate(Chain = Chain +10)
-# 
-# sem_know_model_3<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-#   data = list(data = me_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 10,
-#   cores = 10,
-#   inference_opts = list(method = "incrementalMH",
-#                         samples = 4000,
-#                         burn = 2000,
-#                         verbose = T,
-#                         lag = 1,
-#                         verboseLag = 1000)
-# )%>%
-#   mutate(Chain = Chain +20)
-# 
-# 
-# sem_know_cor_params <- bind_rows(
-#   sem_know_model_1,
-#   sem_know_model_2,
-#   sem_know_model_3
-# )%>%
-#   saveRDS(.,"../saves/run_correlations.rds")
-
-# sem_know_cor_params  <- readRDS("../saves/run_correlations.rds")%>%
-#   separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
-#   filter(parameter == "parameter", type == "items")%>%
-#   separate(value, into = c("int", "slope"),sep = ", ")%>%
-#   mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-#          slope = as.numeric(str_remove(slope, "[)]")))%>%
-#   gather(parameter, value, int, slope)
-# 
-# 
-# sem_know_cor_params <- sem_know_cor_params%>%
-#   filter(Chain != "15",
-#          Chain != "1",
-#          Chain != "30",
-#          Chain != "6",
-#          Chain != "5",
-#          Chain != "7",
-#          Chain != "3")
-
-```
-
-```{r}
-ggplot(item_params%>%filter(parameter == "int"), aes(x = value))+
-  geom_density(alpha = 0.3)+
-  xlab("Parameter")+
-  facet_grid(Chain~item, scales = 'free')+
-  theme_few()
-
-#ggsave("../graphs/item_by_chain.pdf", width = 15, height = 15, scale = 1.5)
-```
-
-```{r}
-item_params_cor <- item_params %>%
-  group_by(Chain,item, parameter)%>%
-  summarise(mode = estimate_mode(value))
-```
-
-```{r}
-library(corrr)
-library(corrplot)
-
-## correaltion at 2
-cor_int_2 <- item_params_cor%>%
-  spread(Chain, mode) %>%
-  filter(parameter == "int")%>%
-  select(-parameter)%>%
-  ungroup()%>%
-  select(-item)%>%
-  correlate(method = "spearman")%>%
-  gather(key, value)%>%
-  filter(key !="rowname")%>%
-  na.omit()%>%
-  mutate(value = as.numeric(value),
-         age = "2")
-
-cor_int_3 <- item_params_cor%>%
-  spread(parameter, mode)%>%
-  mutate(mode = int + slope)%>%
-  select(Chain, item, mode)%>%
-  spread(Chain, mode)%>%
-  ungroup()%>%
-  select(-item)%>%
-  correlate(method = "spearman")%>%
-  gather(key, value)%>%
-  filter(key !="rowname")%>%
-  na.omit()%>%
-  mutate(value = as.numeric(value),
-         age = "3")
-
-cor_int_4 <- item_params_cor%>%
-  spread(parameter, mode)%>%
-  mutate(mode = int + 2*slope)%>%
-  select(Chain, item, mode)%>%
-  spread(Chain, mode)%>%
-  ungroup()%>%
-  select(-item)%>%
-  correlate(method = "spearman")%>%
-  gather(key, value)%>%
-  filter(key !="rowname")%>%
-  na.omit()%>%
-  mutate(value = as.numeric(value),
-         age = "4")
-
-cor_int_5 <- item_params_cor%>%
-  spread(parameter, mode)%>%
-  mutate(mode = int + 3*slope)%>%
-  select(Chain, item, mode)%>%
-  spread(Chain, mode)%>%
-  ungroup()%>%
-  select(-item)%>%
-  correlate(method = "spearman")%>%
-  gather(key, value)%>%
-  filter(key !="rowname")%>%
-  na.omit()%>%
-  mutate(value = as.numeric(value),
-         age = "5")
-
-cor_hist <- 
-bind_rows(
-  cor_int_2,
-  cor_int_3,
-  cor_int_4,
-  cor_int_5
-)
-
-ggplot(cor_hist, aes(x = value, fill =age))+
-  geom_density(alpha = .5)+
-  xlim(-1,1)+
-  xlab("Correlation")+
-  theme_few()
-
-#ggsave("../graphs/corr_int_by_age.pdf", width = 5, height = 4, scale = 1.5)
-
-```
-
-# Inverse predictions
-
-```{r}
-# speak_opt_params <- speak_opt %>%
-#   group_by(parameter)%>%
-#   summarise(mode = estimate_mode(value),
-#             uci = hdi_upper(value),
-#             lci = hdi_lower(value))
-#
-
-inv_model_data <- item_params_summary%>%
-  select(-uci,-lci)%>%
-  spread(parameter, mode)%>%
-  tidyr::expand(item, int,slope,age = unique(me_model_data$age- min(me_model_data$age)))%>%
-  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
-         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode))%>%
-  mutate(speaker_optimality = so_int + so_slope * age,
-         semantic_knowledge = plogis(int + slope * age))
-
-```
-
-```{r}
-invPred <- '
-var allData = dataFromR.data
-
-var priorProbs = [.5,.5]
-
-var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, row.speaker_optimality,row.semantic_knowledge)
-
-    return extend([row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions pragmatic model ex 3 adults}
-inv_model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
-  data =list(data = inv_model_data),
-  data_var = "dataFromR"
-)
-# 
-# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
-# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
-# 
-inv_predictions <- inv_model_pred %>%
-  separate(`0`, into = c("item", "age"), sep="/")%>%
-  mutate(age = as.numeric(age))%>%
-  rename( me_effect = `1`)%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         age = age + min(me_data$age_num))
-```
-
-```{r}
-# plot_model_pred <- model_pred_summary%>%
-#   left_join(aoa_ratings) %>%
-#   ungroup()%>%
-#   mutate(item = fct_reorder(factor(item), mean_aoa))
-
-model_plot <- ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(size = 1)+
-  ggtitle("Inverse Model Predictions")+
-  labs(x="Age",y="Proportion correct")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d()
-
-model_plot
-```
-
-```{r}
-p2 <- read_csv("../data/me.csv")%>%
-  filter(trial != "train1",
-         trial != "train2")%>%
-  mutate(item = familiar)%>%
-    left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(familiar = fct_reorder(factor(item), mean_aoa))
-
-data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  #facet_grid(~familiar)+
-  ggtitle("Data")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d(name = "familiar object")+
-  scale_fill_viridis_d(name = "familiar object")
-
-```
-
-```{r}
-ggarrange(data_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
-```
-
-## For comparison: GLMM for ME effect and data
-```{r}
-me_data <- read_csv("../data/me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(z_age = age_num - mean(age_num))
-
-# me_model <- brm(correct ~ z_age + (1|subid) + (z_age | familiar),
-#                 data = me_data,
-#                 family = bernoulli(),
-#                 control = list(adapt_delta = 0.95),
-#                 sample_prior = F,
-#                 save_all_pars = TRUE,
-#                 iter = 2000)
-
-#saveRDS(me_model, "../saves/me_effect_model.rds")
-
-me_model <- readRDS("../saves/me_effect_model.rds")
-
-summary(me_model)
-
-fixef <- as_tibble(fixef(me_model), rownames = "term")
-
-ranef <-  ranef(me_model)
-
-age_me_effect <- as_data_frame(ranef$familiar, rownames = "familiar")%>%
-  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
-         grand_slope = fixef%>%filter(term=="z_age")%>%pull(Estimate))%>%
-  group_by(familiar) %>%
-  tidyr::expand(Estimate.Intercept,Estimate.z_age,grand_intercept,grand_slope,z_age = me_data$age_num - mean(me_data$age_num), mean_age = mean(me_data$age_num))%>%
-  mutate(me_effect = plogis(grand_intercept + Estimate.Intercept+(Estimate.z_age+grand_slope)*z_age), 
-         age = z_age+mean_age,
-         item = familiar)%>%
-  select(item, me_effect, age)%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-glmm_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = item))+
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(size = 1)+
-  ggtitle("GLMM")+
-  labs(x="Age",y="Proportion correct")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d(name = "familiar object")
-
-```
-
-```{r}
-ggarrange(data_plot,model_plot,glmm_plot, common.legend = T, legend = "right", nrow = 1, ncol = 3)
-```
-
-## Model predictions for combination
-
-```{r}
-# novelty data
-
-novel_data <- read_csv("../data/novelty.csv")%>%
-  mutate(age_num = age_num-min(age_num))
-
-# novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
-#           data = novel_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.95),
-#           sample_prior = F,
-#           save_all_pars = F,
-#           iter = 10000)
-# 
-# saveRDS(novel_bm, "../saves/novelty_model.rds")
-
-novel_bm <- readRDS("../saves/novelty_model.rds")
-
-#summary(novel_bm)
-
-novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
-  select(term,Estimate)%>%
-  spread(term, Estimate)
-
-comb_model_data_con <- inv_model_data %>%
-  mutate(nov_int = novel_params$Intercept,
-         nov_slope = novel_params$age_num,
-         prior = plogis(nov_int + age * nov_slope),
-         alignment = "congruent")
-
-comb_model_data_incon <- inv_model_data %>%
-  mutate(nov_int = novel_params$Intercept,
-         nov_slope = novel_params$age_num,
-         prior = 1- plogis(nov_int + age * nov_slope),
-         alignment = "incongruent")
-
-comb_model_data <- bind_rows(
-  comb_model_data_con,
-  comb_model_data_incon)
-```
-
-```{r}
-combPred <- '
-var allData = dataFromR.data
-
-var output = map(function(row){
-
-    var prior = [row.prior, 1-row.prior]
-
-    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.semantic_knowledge)
-
-    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions pragmatic model ex 3 adults}
-comb_model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
-  data =list(data = comb_model_data),
-  data_var = "dataFromR"
-)
-
-comb_model_predictions <- comb_model_pred %>%
-  separate(`0`, into = c("alignment","item", "age"), sep="/")%>%
-  mutate(age = as.numeric(age))%>%
-  rename( me_effect = `1`)%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         age = age + min(me_data$age_num),
-         source = "Model")
-
-```
-
-```{r}
-p_comb_model <- ggplot(comb_model_predictions, aes(x=age,y = me_effect, col = item))+
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(size = 1)+
-  ggtitle("Combination Model Predictions")+
-  labs(x="Age",y="Proportion correct")+
-  facet_grid(~alignment)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d()
-
-p_comb_model
-```
-
-```{r}
-data_comb <- read_csv("../data/combination.csv") %>%
-  filter(condition != "train")%>%
-  mutate(alignment = condition,
-         item = familiarObject)%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(familiarObject), mean_aoa), 
-         source = "Data")
-
-p_comb_data <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = item, fill = item)) +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
-  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(~alignment)+
-  ggtitle("Combination Data")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d()+
-  scale_fill_viridis_d()
-```
-
-```{r}
-ggarrange(p_comb_model,p_comb_data, common.legend = T, legend = "right", nrow = 2, ncol = 1)
-```
-
-```{r}
-#ggsave("../graphs/combination_model_data.pdf", width = 7, height = 7, scale = 1)
-```
-
-```{r}
-p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
-  geom_hline(yintercept = 0.5, lty=2)+
-  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
-  geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
-  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  #facet_grid(condition~familiarObject)+
-  facet_grid(~item)+
-  #ggtitle("Combination Data")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-
-p_data_model
-```
-
-```{r}
-ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 3, scale = 1.5)
-```
-# Correlate model predictions and data 
-```{r}
-binnned_data <- data_comb%>%
-  group_by(subage, alignment, item)%>%
-  summarize(k = sum(correct), n = n())%>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         data_mean = (a-1)/(a+b-2),
-         data_ci_lower  = qbeta(.025, a, b),
-         data_ci_upper = qbeta(.975, a, b),
-         subage = factor(subage))%>%
-  select(-a,-b,-n,-k)
-
-binned_model <- comb_model_predictions %>%
-  mutate(subage = cut(age, 
-                      breaks = c(2,3,4,5),
-                      labels = c(2,3,4)))%>%
-  group_by(subage, alignment, item)%>%
-  summarise(model_mean = estimate_mode(me_effect),
-            model_ci_lower = hdi_lower(me_effect),
-            model_ci_upper = hdi_upper(me_effect))
-
-cor_plot <- left_join(
-  binnned_data,
-  binned_model)
-
-ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
-  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
-  geom_point(size = 2,  stroke = 1)+
-  coord_fixed()+
- stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  ylab("Data")+
-  facet_grid(~subage)+
-  theme_few() + 
-  scale_colour_viridis_d(name ="Item")
-```
-
-```{r}
-#ggsave("../graphs/combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
-```
-
-```{r}
-ggarrange(
-plot_item_params,
-plot_global_params,
-p_data_model, plot_global_sigma,
-ncol = 2, nrow = 2, common.legend = F, widths = c(3,1))
-
-ggsave("../graphs/overview_variant_3_100k.png", width = 12, height = 4, scale = 1.2)
-
-```
-
-# Nesting within participant
-
-```{r}
-me_model_data <- read_csv("../data/me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(age = age_num - min(age_num))
-
-novel_bm <- readRDS("../saves/novelty_model.rds")
-
-#summary(novel_bm)
-
-novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
-  select(term,Estimate)%>%
-  spread(term, Estimate)
-
-data_comb_log <- read_csv("../data/combination.csv") %>%
-  filter(condition != "train")%>%
-  mutate(alignment = condition,
-         item = familiarObject, 
-         age = age_num - (min(age_num))) %>%
-  mutate(nov_int = novel_params$Intercept,
-         nov_slope = novel_params$age_num,
-         prior = ifelse(alignment == "congruent", plogis(nov_int + nov_slope* age),1-plogis(nov_int + age * nov_slope)))
-
-data_comb_log
-```
-
-## Pragmatics model
-
-```{r work in progress}
-sem_subj_str <- '
-var data = dataFromR.data
-
-var priorProbs = [.5,.5]
-
-var familiars = levels(data, "familiar")
-var subjects = levels(data, "subid")
-
-var model  = function(){
-
-  var speakerOptimalityParameters = {
-    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 4, width: 0.5})
-  }
-
-  var globalLineParameters = {
-    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 2, width: 0.5})
-  }
-
-  var itemVariability = {
-    intercept: uniformDrift({a: 0, b: 2, width: 0.2}),
-    slope: uniformDrift({a: 0, b: 1, width: 0.2})
-  }
-
-  // conceptually it might not make sense to have two sigmas, but maybe it does
-  // intercept sigma probably will be smaller than slope sigma
-  // var item_int_sigma = uniformDrift({a: 0, b: 3, width: 0.2})
-
-  var sampleItemParameters = function(itemName) { 
-    return [itemName, {
-        intercept: gaussianDrift({
-          mu: globalLineParameters.intercept, 
-          sigma: itemVariability.intercept, 
-          width: 0.5
-        }),
-        slope: gaussianDrift({
-          mu: globalLineParameters.slope, 
-          sigma: itemVariability.slope, 
-          width: 0.5
-        })
-      }]
-  }
-
-  // {papaya: {int, slope}, bread: {int, slope}, ... }
-  var all_item_parameters = _.fromPairs(map(sampleItemParameters, familiars))
-
-  // want something that favors smaller values
-  var subject_sigma = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var sampleLinguisticCompetence = function(age){
-    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
-  }
-
-  foreach(function(subid){
-      var subjectData = _.filter(data, {subid: subid})
-      var subj_age = subjectData[0].age
-      var subj_linguistic_competence = sampleLinguisticCompetence(subj_age)
-
-     // display("age = " + subj_age + " ... intercept = " + subj_linguistic_competence)
-
-      // question: should we use age here instead of the random intercept? or a different random intercept?
-
-  var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_age
-
-      // each row is a different item
-      foreach(function(row){
-
-        var itemLineParameters = all_item_parameters[row.familiar]
-
-        var sem_knowledge = logistic(itemLineParameters.intercept + 
-            itemLineParameters.slope * subj_linguistic_competence)
-
-        var modelPredictions = pragmaticListener({label: "novel_word"}, 
-              priorProbs, speakerOptimality, sem_knowledge)
-        // display(modelPredictions.score(row.correct))
-
-        observe(modelPredictions, row.correct)
-
-        // if you want to save predictions, make sure to record subid because these predictions are for this particular subid
-        // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
-
-      }, subjectData)
-
-    // comment out to save memory
-  //  query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])
-
-  }, subjects)
-
-var all_log_likes = map(function(row) { 
-  var prior = [row.prior, 1-row.prior]
-  var itemLineParameters = all_item_parameters[row.item]
-  var sem_knowledge = logistic(itemLineParameters.intercept + 
-                               itemLineParameters.slope * row.age)
-
-  var global_sem_knowledge = logistic(globalLineParameters.intercept + 
-                               globalLineParameters.slope * row.age)
-
-  var speakerOptimality = speakerOptimalityParameters.intercept  + 
-      speakerOptimalityParameters.slope * row.age
-
-  var pragModelPredictions = pragmaticListener({label: "novel_word"}, 
-                                               prior, speakerOptimality, 
-                                               sem_knowledge)
-
-  var globalPragModelPredictions = pragmaticListener({label: "novel_word"}, 
-                                               prior, speakerOptimality, 
-                                               global_sem_knowledge)
-
-  var flatModelPredictions = pragmaticListener({label: "novel_word"}, 
-                                               [.5, .5], speakerOptimality, 
-                                               sem_knowledge)
-
-  return {
-    prag: pragModelPredictions.score(row.correct),
-    globalPrag: globalPragModelPredictions.score(row.correct),
-    flat: flatModelPredictions.score(row.correct),
-    priorOnly: Math.log(row.correct == 1 ? row.prior : 1 - row.prior)
-  }
-
-}, dataFromR.comb_data)
-
-var log_likelihood_prag = sum(_.map(all_log_likes, "prag"))
-var log_likelihood_prag_global = sum(_.map(all_log_likes, "globalPrag"))
-var log_likelihood_flat = sum(_.map(all_log_likes, "flat"))
-var log_likelihood_prior_only = sum(_.map(all_log_likes, "priorOnly"))
-
-query.add(["log_like", "pragmatics", "NA"], ["NA", log_likelihood_prag])
-query.add(["log_like", "pragmatics_global", "NA"], ["NA", log_likelihood_prag_global])
-query.add(["log_like", "flat_prior", "NA"], ["NA", log_likelihood_flat])
-query.add(["log_like", "prior_only", "NA"], ["NA", log_likelihood_prior_only])
-
-  foreach(function(item){
-    var itemLineParameters = all_item_parameters[item]
-    query.add(["parameter","items", item], [itemLineParameters.intercept, itemLineParameters.slope])
-  }, familiars)
-
-  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
-  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
-  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
-  query.add(["parameter","sigma", "global_subject_sigmas"], ["NA", subject_sigma])
-
-  return query 
-}
-'
-```
-
-```{r}
-
-sem_know_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
-  data = list(data = me_model_data, comb_data = data_comb_log),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "incrementalMH",
-                        samples = 100000,
-                        burn = 50000,
-                        verbose = T,
-                        lag = 1,
-                        verboseLag = 5000)
-)
-
-saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_model_comparison.rds")
-
-model_pred<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
-  filter(parameter == "prediction")%>%
-  separate(value, into = c("na", "me_effect"),sep = ",")%>%
-  select(-na)%>%
-  mutate(age = as.numeric(age),
-         me_effect =as.numeric(str_remove(me_effect,"[)]")))
-
-log_like<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "model","age","alignment"), sep = ",")%>%
-  filter(parameter == "log_like")%>%
-  separate(value, into = c("na", "log_like"),sep = ",")%>%
-  select(-na, -age, -alignment)%>%
-  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
-  group_by(model, Chain)%>%
-  summarize(logP = logSumExp(log_like))
-
-```
-
-#### plotting predictions
-
-```{r}
-comb_model_pred_agg <- model_pred%>%
-  group_by(Chain, alignment,item,age)%>%
-  summarise(mean = estimate_mode(me_effect),
-            uci = hdi_upper(me_effect),
-            lci = hdi_lower(me_effect))%>%
-  left_join(aoa_ratings) %>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         age = age + min(me_data$age_num),
-         Chain = factor(Chain))
-
-ggplot(comb_model_pred_agg, aes(x=age,y = mean, col = item, fill = item))+
-  geom_ribbon(aes(ymin = lci, ymax = uci), alpha = .5, colour = NA)+
-  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col), col = "black", fill = "grey",  method = "loess", se = F, alpha = .2, span = 2)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(size = 1)+
-  ggtitle("Combination Model Predictions")+
-  labs(x="Age",y="Proportion correct")+
-  facet_grid(Chain ~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d()+
-  scale_fill_viridis_d()
-
-```
-
-```{r}
-ggsave("../graphs/model_pred_data.pdf", width = 20, height = 8, scale = 1.2)
-```

### 2019-09-20 stats/model.Rmd
draft model comparison with noise parameter

@@
 var LexiconPrior = Categorical({vs: ["novel_word = novel_object","novel_word = familiar_object" ], ps: [1, 1]})
+
+var addNoise = function(dist, noiseParam){
+   Infer({model: function(){ 
+      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
+    }
+   })
+}
 
@@
 
+var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
 var all_log_likes = map(function(row) { 
@@
 
+  var noisyPragModelPredictions = addNoise(pragModelPredictions, noise)
+
   var globalPragModelPredictions = pragmaticListener({label: "novel_word"}, 
@@
 
+   var noisyGlobalPragModelPredictions = addNoise(globalPragModelPredictions, noise)
+
    var flatModelPredictions = pragmaticListener({label: "novel_word"}, 
@@
 
+   var noisyFlatModelPredictions = addNoise(flatModelPredictions, noise)
+
+  var priorOnlyModelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: prior}));
+      return obj.shape == "novel_object" ? 1 : 0
+       }})
+
+  var noisyPriorOnlyModelPredictions = addNoise(priorOnlyModelPredictions, noise)
+
   return {
     prag: pragModelPredictions.score(row.correct),
+    noisePrag: noisyPragModelPredictions.score(row.correct),
+
     globalPrag: globalPragModelPredictions.score(row.correct),
+    noiseGlobalPrag: noisyGlobalPragModelPredictions.score(row.correct),
+
     flat: flatModelPredictions.score(row.correct),
-    priorOnly: Math.log(row.correct == 1 ? row.prior : 1 - row.prior)
+    noiseFlat: noisyFlatModelPredictions.score(row.correct),
+
+    priorOnly: priorOnlyModelPredictions.score(row.correct),
+    noisePriorOnly: noisyPriorOnlyModelPredictions.score(row.correct)
   }
@@
 var log_likelihood_prag = sum(_.map(all_log_likes, "prag"))
+var log_likelihood_prag_noise = sum(_.map(all_log_likes, "noisePrag"))
+
 var log_likelihood_prag_global = sum(_.map(all_log_likes, "globalPrag"))
+var log_likelihood_prag_global_noise = sum(_.map(all_log_likes, "noiseGlobalPrag"))
+
 var log_likelihood_flat = sum(_.map(all_log_likes, "flat"))
+var log_likelihood_flat_noise = sum(_.map(all_log_likes, "noiseFlat"))
+
 var log_likelihood_prior_only = sum(_.map(all_log_likes, "priorOnly"))
-
-query.add(["log_like", "pragmatics", "NA"], ["NA", log_likelihood_prag])
-query.add(["log_like", "pragmatics_global", "NA"], ["NA", log_likelihood_prag_global])
-query.add(["log_like", "flat_prior", "NA"], ["NA", log_likelihood_flat])
-query.add(["log_like", "prior_only", "NA"], ["NA", log_likelihood_prior_only])
+var log_likelihood_prior_only_noise = sum(_.map(all_log_likes, "noisePriorOnly"))
+
+query.add(["log_like", "pragmatics", "parameter_free"], ["NA", log_likelihood_prag])
+query.add(["log_like", "pragmatics", "noise"], ["NA", log_likelihood_prag_noise])
+
+query.add(["log_like", "pragmatics_global", "parameter_free"], ["NA", log_likelihood_prag_global])
+query.add(["log_like", "pragmatics_global", "noise"], ["NA", log_likelihood_prag_global_noise])
+
+query.add(["log_like", "flat_prior", "parameter_free"], ["NA", log_likelihood_flat])
+query.add(["log_like", "flat_prior", "noise"], ["NA", log_likelihood_flat_noise])
+
+query.add(["log_like", "prior_only", "parameter_free"], ["NA", log_likelihood_prior_only])
+query.add(["log_like", "prior_only", "noise"], ["NA", log_likelihood_prior_only_noise])
 
@@
   inference_opts = list(method = "incrementalMH",
-                        samples = 100000,
-                        burn = 50000,
+                        samples = 25000,
+                        burn = 20000,
                         verbose = T,
@@
 
-saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_model_comparison.rds")
+saveRDS(sem_know_model, "../saves/sem_know_model_variant3_25k_model_comparison_noise.rds")
 
@@
 
+```
+
+## Model compatison
+
+```{r}
+log_like<- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
+  filter(parameter == "log_like")%>%
+  separate(value, into = c("na", "log_like"),sep = ",")%>%
+  select(-na, -alignment)%>%
+  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
+  group_by(model,noise)%>%
+  summarize(logP = logSumExp(log_like))
 ```
@@
 ```{r}
-p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
+p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source)) +
   geom_hline(yintercept = 0.5, lty=2)+
@@
   geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
-  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
+  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = alignment, lty = source), size = 1)+
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
 
-```
-
-## Model compatison
-
-```{r}
-log_like<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "model","age","alignment"), sep = ",")%>%
-  filter(parameter == "log_like")%>%
-  separate(value, into = c("na", "log_like"),sep = ",")%>%
-  select(-na, -age, -alignment)%>%
-  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
-  group_by(model,Chain)%>%
-  summarize(logP = logSumExp(log_like))
 ```
@@
 ggsave("../graphs/model_pred_data.pdf", width = 20, height = 8, scale = 1.2)
+```
+
+# MAP based predictions with noise parameter
+
+## Preparing data
+
+```{r}
+noise_model_data <- item_params_summary%>%
+  select(-uci,-lci)%>%
+  spread(parameter, mode) %>%
+  left_join(read_csv("../data/combination.csv") %>%
+  filter(condition != "train")%>%
+  mutate(alignment = condition,
+         item = familiarObject,
+         age = age_num - (min(age_num))))%>%
+  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
+         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode),
+    glob_sem_know_int = global_params_summary%>%filter(token == "global_sem", parameter == "int")%>%pull(mode),
+         glob_sem_know_slope = global_params_summary%>%filter(token == "global_sem", parameter == "slope")%>%pull(mode),
+         speaker_optimality = so_int + so_slope * age,
+         semantic_knowledge = plogis(int + slope * age),
+         global_semantic_knowledge = plogis(glob_sem_know_int + glob_sem_know_slope * age),
+         nov_int = novel_params$Intercept,
+         nov_slope = novel_params$age_num,
+         prior = ifelse(alignment == "congruent", plogis(nov_int + nov_slope* age),1-plogis(nov_int + age * nov_slope)))%>%
+  select(item, alignment,age, speaker_optimality, semantic_knowledge,global_semantic_knowledge, prior, correct)
+
+```
+
+## Pragmatics model
+
+```{r}
+pragNoise <- '
+var allData = dataFromR.data
+
+var model = function(){
+
+  var noise = uniform({a: 0, b: 1})
+
+  var output = map(function(row){
+
+    var prior = [row.prior, 1-row.prior]
+
+    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.semantic_knowledge)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct)
+
+    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(noisyModelPredictions.score(1))])
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise: noise})
+
+}
+'
+```
+
+```{r predictions pragmatic model ex 3 adults}
+prag_model_noise<- webppl(
+  program_code = paste(rsaUtils, rsaModel, pragNoise , sep='\n'),
+  data =list(data = noise_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
+)
+
+saveRDS(prag_model_noise, "../saves/prag_model_noise.rds")
+
+prag_model_noise <- readRDS("../saves/prag_model_noise.rds")
+
+# noise parameter
+prag_model_noise_noise_param_summary <- prag_model_noise %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+# model predictions
+prag_model_noise_predictions <- prag_model_noise %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
+  mutate(model = "pragmatic_noise")%>%
+  group_by(model,age,item, alignment) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         source = "Model")
+
+```
+
+### Plot model predictions
+
+```{r}
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source), method = "loess", se = F, alpha = .2, span = 2)+
+  geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = alignment, lty = source), size = 1)+
+  geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_wrap(~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+
+```
+
+## Pragmatics model global semantic knnowledge
+
+```{r}
+globalPragNoise <- '
+var allData = dataFromR.data
+
+var model = function(){
+
+  var noise = uniform({a: 0, b: 1})
+
+  var output = map(function(row){
+
+    var prior = [row.prior, 1-row.prior]
+
+    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.global_semantic_knowledge)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct)
+
+    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(noisyModelPredictions.score(1))])
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise: noise})
+
+}
+'
+```
+
+```{r predictions pragmatic model ex 3 adults}
+global_prag_model_noise<- webppl(
+  program_code = paste(rsaUtils, rsaModel, globalPragNoise , sep='\n'),
+  data =list(data = noise_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
+)
+
+saveRDS(global_prag_model_noise, "../saves/global_prag_model_noise.rds")
+
+global_prag_model_noise <- readRDS("../saves/global_prag_model_noise.rds")
+
+# noise parameter
+global_prag_model_noise_noise_param_summary <- global_prag_model_noise %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+# model predictions
+global_prag_model_noise_predictions <- global_prag_model_noise %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
+  mutate(model = "global_pragmatic_noise")%>%
+  group_by(model,age,item, alignment) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         source = "Model")
+
+```
+
+### Plot model predictions
+
+```{r}
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source), method = "loess", se = F, alpha = .2, span = 2)+
+  geom_line(data = global_prag_model_noise_predictions, aes(x=age+2,y = mean, col = alignment, lty = source), size = 1)+
+  geom_ribbon(data = global_prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_wrap(~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+
+```
+
+## Flat prior model
+
+```{r}
+flatNoise <- '
+var allData = dataFromR.data
+
+var model = function(){
+
+  var noise = uniform({a: 0, b: 1})
+
+  var output = map(function(row){
+
+    var prior = [row.prior, 1-row.prior]
+
+    var modelPredictions = pragmaticListener({label: "novel_word"}, [.5,.5], row.speaker_optimality,row.semantic_knowledge)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct)
+
+    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(noisyModelPredictions.score(1))])
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise: noise})
+
+}
+'
+```
+
+```{r predictions pragmatic model ex 3 adults}
+flat_model_noise<- webppl(
+  program_code = paste(rsaUtils, rsaModel, flatNoise , sep='\n'),
+  data =list(data = noise_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
+)
+
+saveRDS(flat_model_noise, "../saves/flat_model_noise.rds")
+
+flat_model_noise <- readRDS("../saves/flat_model_noise.rds")
+
+# noise parameter
+flat_model_noise_noise_param_summary <- flat_model_noise %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+# model predictions
+flat_model_noise_predictions <- flat_model_noise %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
+  mutate(model = "flat_prior_noise")%>%
+  group_by(model,age,item, alignment) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         source = "Model")
+
+```
+
+### Plot model predictions
+
+```{r}
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source), method = "loess", se = F, alpha = .2, span = 2)+
+  geom_line(data = flat_model_noise_predictions, aes(x=age+2,y = mean, col = alignment, lty = source), size = 1)+
+  geom_ribbon(data = flat_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_wrap(~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+```
+
+## Prior only model
+
+```{r}
+priorOnlyNoise <- '
+var allData = dataFromR.data
+
+var model = function(){
+
+  var noise = uniform({a: 0, b: 1})
+
+  var output = map(function(row){
+
+    var prior = [row.prior, 1-row.prior]
+
+      var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: prior}));
+      return obj.shape == "novel_object" ? 1 : 0
+       }})
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct)
+
+    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(noisyModelPredictions.score(1))])
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise: noise})
+
+}
+'
+```
+
+```{r predictions pragmatic model ex 3 adults}
+prior_only_model_noise<- webppl(
+  program_code = paste(rsaUtils, rsaModel, priorOnlyNoise , sep='\n'),
+  data =list(data = noise_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
+)
+
+saveRDS(prior_only_model_noise, "../saves/prior_only_model_noise.rds")
+
+prior_only_model_noise <- readRDS("../saves/prior_only_model_noise.rds")
+
+# noise parameter
+prior_only_model_noise_noise_param_summary <- prior_only_model_noise %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+# model predictions
+prior_only_model_noise_predictions <- prior_only_model_noise %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
+  mutate(model = "prior_only_noise")%>%
+  group_by(model,age,item, alignment) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         source = "Model")
+
+```
+
+### Plot model predictions
+
+```{r}
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source), method = "loess", se = F, alpha = .2, span = 2)+
+  geom_line(data = prior_only_model_noise_predictions, aes(x=age+2,y = mean, col = alignment, lty = source), size = 1)+
+  geom_ribbon(data = prior_only_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_wrap(~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+```
+
+## Compare noise parameters
+
+```{r}
+noise_plot <- bind_rows(
+  prag_model_noise %>%
+    filter(Parameter %in% c("noise"))%>%
+    mutate(Model = "Pragmatic"),
+  global_prag_model_noise %>%
+    filter(Parameter %in% c("noise"))%>%
+    mutate(Model = "Pragmatic no word knowledge"),
+  flat_model_noise %>%
+    filter(Parameter %in% c("noise"))%>%
+    mutate(Model = "Flat Prior"),
+  prior_only_model_noise %>%
+    filter(Parameter %in% c("noise"))%>%
+    mutate(Model = "Prior Only")
+)
+
+ggplot(noise_plot, aes(x = value, col = Model, fill = Model))+
+  geom_density(alpha = .7)+
+  theme_few()+
+  xlim(0,1)+
+  scale_color_ptol()+
+  scale_fill_ptol()+
+  theme(legend.position = "bottom")
+
+```
+
+## Compare predictions
+
+```{r}
+
+noise_model_pred <- bind_rows(
+  prag_model_noise_predictions,
+  global_prag_model_noise_predictions,
+  prior_only_model_noise_predictions,
+  flat_model_noise_predictions
+)
+
+data_comb_plot<-data_comb%>%
+  mutate(model = "data")
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct, col = "black", fill = model), method = "loess", se = F, alpha = .2, span = 2)+
+  geom_line(data = noise_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
+  geom_ribbon(data = noise_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
 ```

### 2019-10-13 stats/model.Rmd
update model
add 200k 8chain model comparison

@@
 ```{r}
-
 sem_know_model<- webppl(
@@
   model_var = "model",
-  chains = 3,
-  cores = 3,
+  chains = 8,
+  cores = 8,
   inference_opts = list(method = "incrementalMH",
-                        samples = 25000,
-                        burn = 20000,
+                        samples =200000,
+                        burn = 100000,
                         verbose = T,
                         lag = 1,
-                        verboseLag = 1000)
+                        verboseLag = 5000)
 )
 
-saveRDS(sem_know_model, "../saves/sem_know_model_variant3_25k_model_comparison_noise.rds")
-
-sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k_model_comparison.rds")
+saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_model_comparison_noise.rds")
+
+#sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k_model_comparison.rds")
 

### 2019-10-15 stats/model.Rmd
add sampler to save memory

--- 2019-09-20 stats/model.Rmd
@@
 me_data <- read_csv("../data/me.csv")
+
+devtools::install_github("https://github.com/mhtess/webppl-sample-writer")
 
@@
 }
+
+var header = "iteration,a,b,c,d,e,f"
+var callback = webpplSampleWriter.streamQueryCSV("../saves/samples.csv", header);
+
+Infer({model,
+      samples: 2,
+      burn: 1,
+      verbose: T,
+      lag: 1,
+      verboseLag: 1,
+      method: "incrementalMH",
+      onlyMAP: true,
+      callbacks: [callback]});
 '
@@
   model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "incrementalMH",
-                        samples = 25000,
-                        burn = 20000,
-                        verbose = T,
-                        lag = 1,
-                        verboseLag = 1000)
+  chains = 1,
+  cores = 1,
+  packages = c("utils/webppl-sample-writer")
 )
 
-saveRDS(sem_know_model, "../saves/sem_know_model_variant3_25k_model_comparison_noise.rds")
-
-sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k_model_comparison.rds")
+#saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_model_comparison_noise.rds")
+
+sem_know_model <- readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")
+
+model <- read_csv("../saves/samples.csv")
 
@@
 ```{r}
-log_like<- sem_know_model %>%
+log_like <- model %>%
+  filter(a == "log_like")%>%
+  select(-f, -d)%>%
+  rename(type = a, 
+         model =b,
+         parameter = c, 
+         log_like = e)
+
+log_like_chain<- sem_know_model %>%
   separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
@@
   mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
-  group_by(model,noise)%>%
-  summarize(logP = logSumExp(log_like))
+  group_by(model,Chain, noise)%>%
+  summarize(logP = logSumExp(log_like))%>%
+  spread(noise, logP)
+
+log_like_chain %>%
+  group_by(model)%>%
+  mutate(noise = round(noise,2),
+         parameter_free = round(parameter_free,2))%>%
+  summarise(range_noise = paste(range(noise)[1],range(noise)[2], sep = " / "))
 ```
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct, col = "black", fill = model), method = "loess", se = F, alpha = .2, span = 2)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
   geom_line(data = noise_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
@@
   xlim(2,5)+
-  guides(alpha = F)+ 
+  guides(alpha = F, fill = F)+ 
   scale_colour_ptol(name = NULL)+
   scale_fill_ptol(name = NULL)
+```
+
+## Correlate predictions with data
+
+```{r}
+binned_noise_model <- prag_model_noise %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
+  mutate(age = as.numeric(age) + min(me_data$age_num),
+         subage = cut(age, 
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(subage, alignment, item)%>%
+  summarise(model_mean = estimate_mode(value),
+            model_ci_lower = hdi_lower(value),
+            model_ci_upper = hdi_upper(value))
+
+cor_plot_2 <- bind_rows(
+left_join(binned_model, binnned_data)%>%mutate(model = "Parameter free"), 
+left_join(binned_noise_model,binnned_data)%>%mutate(model = "Noise")
+)
+
+ggplot(data = cor_plot_2,aes(x = model_mean, y = data_mean, col = item)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
+  geom_point(size = 2,  stroke = 1)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(model~subage)+
+  theme_few() + 
+  scale_colour_viridis_d(name ="Item")
 ```

### 2019-10-15 stats/model.Rmd
add sampler to save memory

@@
 
+  query.add(["pragmaticModelPredictions","parameterFree", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])
+
   var noisyPragModelPredictions = addNoise(pragModelPredictions, noise)
+
+  query.add(["pragmaticModelPredictions","noise", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(noisyPragModelPredictions.score(1))])
 
@@
 
-var header = "iteration,a,b,c,d,e,f"
+var header = "iteration,a,b,c,d,e,f,g,h"
 var callback = webpplSampleWriter.streamQueryCSV("../saves/samples.csv", header);

### 2019-10-16 stats/model.Rmd
new way of savinf predictions

@@
 library(matrixStats)
+library(data.table)
 
@@
 me_data <- read_csv("../data/me.csv")
-
-devtools::install_github("https://github.com/mhtess/webppl-sample-writer")
 
@@
 var header = "iteration,a,b,c,d,e,f,g,h"
-var callback = webpplSampleWriter.streamQueryCSV("../saves/samples.csv", header);
+
+var randomNumberForFile = Math.round(uniform(0, 1000))
+
+var callback = webpplSampleWriter.streamQueryCSV("../saves/model/samples"+randomNumberForFile+".csv", header);
 
 Infer({model,
-      samples: 2,
-      burn: 1,
+      samples: 100,
+      burn: 100,
       verbose: T,
       lag: 1,
-      verboseLag: 1,
+      verboseLag: 5000,
       method: "incrementalMH",
@@
   model_var = "model",
-  chains = 1,
-  cores = 1,
+  chains = 4,
+  cores = 4,
   packages = c("utils/webppl-sample-writer")
@@
 
-model <- read_csv("../saves/samples.csv")
+model <- bind_rows(
+  read_csv("../saves/model/samples126.csv")%>%mutate(chain = 1),
+  read_csv("../saves/model/samples551.csv")%>%mutate(chain = 2),
+  read_csv("../saves/model/samples661.csv")%>%mutate(chain = 3),
+  read_csv("../saves/model/samples950.csv")%>%mutate(chain = 4)
+)
 
@@
   filter(a == "log_like")%>%
-  select(-f, -d)%>%
+  select(-f, -d, -g, -h)%>%
   rename(type = a, 
@@
          parameter = c, 
-         log_like = e)
+         log_like = e)%>%
+  mutate(log_like = as.numeric(log_like))
 

### 2019-10-16 stats/model.Rmd
update model code

@@
 
-  query.add(["pragmaticModelPredictions","parameterFree", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])
-
   var noisyPragModelPredictions = addNoise(pragModelPredictions, noise)
-
-  query.add(["pragmaticModelPredictions","noise", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(noisyPragModelPredictions.score(1))])
 
@@
 
+    query.add(["modelPrediction","pragmatic","noise", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(noisyPragModelPredictions.score(1))])
+
+  query.add(["modelPrediction","pragmatic","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])
+
+  query.add(["modelPrediction","globalPrag","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(globalPragModelPredictions.score(1))])
+
+  query.add(["modelPrediction","globalPrag","noise", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(noisyGlobalPragModelPredictions.score(1))])
+
   return {
@@
 Infer({model,
-      samples: 100,
-      burn: 100,
+      samples: 10,
+      burn: 10,
       verbose: T,
-      lag: 1,
+      lag: 4,
       verboseLag: 5000,
@@
   cores = 4,
-  packages = c("utils/webppl-sample-writer")
+  packages = c("webppl_packages/webppl-sample-writer")
 )
 
-#saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_model_comparison_noise.rds")
-
-sem_know_model <- readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")
-
-model <- bind_rows(
-  read_csv("../saves/model/samples126.csv")%>%mutate(chain = 1),
-  read_csv("../saves/model/samples551.csv")%>%mutate(chain = 2),
-  read_csv("../saves/model/samples661.csv")%>%mutate(chain = 3),
-  read_csv("../saves/model/samples950.csv")%>%mutate(chain = 4)
-)
-
+#saveRDS(sem_know_model, "../saves/model1.rds")
+
+sem_know_model <- readRDS("../saves/model1.rds")
 ```
@@
 ```{r}
-log_like <- model %>%
-  filter(a == "log_like")%>%
-  select(-f, -d, -g, -h)%>%
-  rename(type = a, 
-         model =b,
-         parameter = c, 
-         log_like = e)%>%
-  mutate(log_like = as.numeric(log_like))
+log_like <- sem_know_model %>%
+  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
+  filter(parameter == "log_like")%>%
+  separate(value, into = c("na", "log_like"),sep = ",")%>%
+  select(-na, -alignment)%>%
+  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))
 
@@
 
-# model_pred <- sem_know_model %>%
-#   separate(Parameter, into = c("type", "item","x"))%>%
-#   filter(type == "modelPrediction")%>%
-#   separate(value, into = c("age", "pred"),sep = ", ")%>%
-#   mutate(age = as.numeric(str_remove_all(age, "[(c]")),
-#          pred = as.numeric(str_remove(pred, "[)]")))%>%
-#   select(-x)
+model_pred <- sem_know_model %>%
+  separate(Parameter, into = c("type", "model","parameter","alignment","item"))%>%
+  filter(type == "modelPrediction")%>%
+  separate(value, into = c("age", "pred"),sep = ", ")%>%
+  mutate(age = as.numeric(str_remove_all(age, "[(c]")),
+         pred = as.numeric(str_remove(pred, "[)]")))
 
@@
   scale_colour_viridis_d(name = "familiar object")
+```
+
+## Plotting model predictions
+
+```{r}
+
+plot_model_pred <- model_pred%>%
+  mutate(model = paste(model, parameter, sep = "_"))%>%
+  group_by(model, alignment, item, age)%>%
+  summarise(mean = estimate_mode(pred),
+            ci_lower = hdi_lower(pred),
+            ci_upper = hdi_upper(pred))
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
+  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+```
+
+## Correlate model predictions
+
+```{r}
+binnned_data <- data_comb%>%
+  group_by(subage, alignment, item)%>%
+  summarize(k = sum(correct), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         data_mean = (a-1)/(a+b-2),
+         data_ci_lower  = qbeta(.025, a, b),
+         data_ci_upper = qbeta(.975, a, b),
+         age = factor(subage))%>%
+  select(-a,-b,-n,-k)
+
+cor_model_pred <- model_pred%>%
+  mutate(model = paste(model, parameter, sep = "_"))%>%
+  mutate(age = as.numeric(age) + min(me_data$age_num),
+         age = cut(age, 
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(model, alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
+
+plot_cor_model_pred <- cor_model_pred %>%
+  left_join(
+    bind_rows(
+      binnned_data%>%mutate(model = "globalPrag_free"),
+      binnned_data%>%mutate(model = "globalPrag_noise"),
+      binnned_data%>%mutate(model = "pragmatic_free"),
+      binnned_data%>%mutate(model = "pragmatic_noise")
+      )
+  )
+
+ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = item)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
+  geom_point(size = 1,  stroke = 1)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(age~model)+
+  theme_few() + 
+  scale_colour_viridis_d(name ="Item")
 ```

### 2019-10-17 stats/model.Rmd
update model processing)

@@
 me_data <- read_csv("../data/me.csv")
+
+data_comb_pre <- read_csv("../data/combination.csv")
+
+aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
+
+aoa_ratings <- aoa_ratings_all %>%
+  filter(Word %in% data_comb_pre$item )%>%
+  mutate(mean_aoa = as.numeric(Rating.Mean),
+         item = Word)%>%
+  select(item,mean_aoa)
+
+data_comb <- data_comb_pre%>%
+  filter(condition != "train")%>%
+  mutate(alignment = condition,
+         item = familiarObject)%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(familiarObject), mean_aoa), 
+         source = "Data")
 
@@
 
-#saveRDS(sem_know_model, "../saves/model1.rds")
-
-sem_know_model <- readRDS("../saves/model1.rds")
-```
-
-## Model compatison
+bind_rows(
+sem_know_model <- read_csv("../saves/model/samples628.csv")%>%mutate(chain =1)
+)
+
+saveRDS(sem_know_model, "../saves/model_complete.rds")
+
+sem_know_model <- readRDS("../saves/model_complete.rds")
+
+```
+## Model comparison
 
@@
 log_like <- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
-  filter(parameter == "log_like")%>%
-  separate(value, into = c("na", "log_like"),sep = ",")%>%
-  select(-na, -alignment)%>%
-  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))
-
-log_like_chain<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
-  filter(parameter == "log_like")%>%
-  separate(value, into = c("na", "log_like"),sep = ",")%>%
-  select(-na, -alignment)%>%
-  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
-  group_by(model,Chain, noise)%>%
+  filter(a == "log_like")%>%
+  select(b,c,e)%>%
+  rename(model = b, 
+         parameter = c,
+         log_like = e)
+
+saveRDS(log_like, "../saves/log_like.rds")
+log_like <- readRDS("../saves/log_like.rds")
+
+log_like_model<- log_like %>%
+  group_by(model,parameter)%>%
   summarize(logP = logSumExp(log_like))%>%
-  spread(noise, logP)
+  spread(parameter, logP)
+
+saveRDS(log_like_model, "../saves/log_like_model.rds")
+log_like_model <- readRDS("../saves/log_like_model.rds")
+
+log_like_chain<- log_like %>%
+  group_by(chain, model,parameter)%>%
+  summarize(logP = logSumExp(log_like))%>%
+  spread(parameter, logP)
+
+saveRDS(log_like_chain, "../saves/log_like_chain.rds")
+log_like_chain <- readRDS("../saves/log_like_chain.rds")
 
@@
 model_pred <- sem_know_model %>%
-  separate(Parameter, into = c("type", "model","parameter","alignment","item"))%>%
-  filter(type == "modelPrediction")%>%
-  separate(value, into = c("age", "pred"),sep = ", ")%>%
-  mutate(age = as.numeric(str_remove_all(age, "[(c]")),
-         pred = as.numeric(str_remove(pred, "[)]")))
-
-item_params<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
-  filter(parameter == "parameter", type == "items")%>%
-  separate(value, into = c("int", "slope"),sep = ", ")%>%
-  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]")))%>%
+  filter(a == "modelPrediction")%>%
+  select(-a, -f)%>%
+  rename(model = b, 
+         parameter = c,
+         alignment = d,
+         item = e,
+         age = g, 
+         pred = h)
+
+saveRDS(model_pred, "../saves/model_pred.rds")
+model_pred <- readRDS("../saves/model_pred.rds")
+
+model_params<- sem_know_model %>%
+  filter(a == "parameter")
+
+saveRDS(model_params, "../saves/model_params.rds")
+model_params <- readRDS("../saves/model_params.rds")
+
+item_params <-  model_params %>%
+  filter(b == "items")%>%
+  select(-a,-b, -g,-h, -f)%>%
+    rename(item = c,
+         int = d,
+         slope = e)%>%
+  mutate(slope = as.numeric(slope),
+         int = as.numeric(int))%>%
   gather(parameter, value, int, slope)
 
-global_params <- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
-  filter(parameter == "parameter", type == "parameters")%>%
-    separate(value, into = c("int", "slope"),sep = ", ")%>%
-    mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]")))%>%
+saveRDS(item_params, "../saves/item_params.rds")
+item_params <- readRDS("../saves/item_params.rds")
+
+global_params <- model_params %>%
+  filter(b == "parameters")%>%
+  select(-a,-b, -g,-h, -f)%>%
+    rename(token = c,
+         int = d,
+         slope = e)%>%
+  mutate(slope = as.numeric(slope),
+         int = as.numeric(int))%>%
   gather(parameter, value, int, slope)
 
+saveRDS(global_params, "../saves/global_params.rds")
+global_params <- readRDS("../saves/global_params.rds")
+
 global_sigma<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
-  filter(parameter == "parameter", type == "sigma", token != "global_subject_sigmas")%>%
-    separate(value, into = c("sigma_int", "sigma_slope"),sep = ", ")%>%
-    mutate(sigma_int = as.numeric(str_remove_all(sigma_int, "[(c]")),
-         sigma_slope = as.numeric(str_remove(sigma_slope, "[)]")))%>%
-    gather(parameter, value, sigma_int, sigma_slope)
-
-subj_sigma<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
-  filter(parameter == "parameter", token == "global_subject_sigmas")%>%
-  separate(value, into = c("na", "sigma"),sep = ", ")%>%
-  select(-na)%>%
-  mutate(sigma = as.numeric(str_remove(sigma, "[)]")))
-
-subject_params<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "type","id"), sep = ",")%>%
-  filter(parameter == "parameter", type == "subj_intercept")%>%
-  separate(value, into = c("na", "int"),sep = ", ")%>%
-  select(-na)%>%
-  mutate(int = as.numeric(str_remove(int, "[)]")))
-
-model_pred<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
-  filter(parameter == "prediction")%>%
-  separate(value, into = c("na", "me_effect"),sep = ",")%>%
-  select(-na)%>%
-  mutate(age = as.numeric(age),
-         me_effect =as.numeric(str_remove(me_effect,"[)]")))
+  filter(b == "sigma")%>%
+  select(-a,-b, -g,-h, -f)%>%
+    rename(token = c,
+         int = d,
+         slope = e)%>%
+  mutate(slope = as.numeric(slope),
+         int = as.numeric(int))%>%
+  gather(parameter, value, int, slope)
+
+saveRDS(global_sigma, "../saves/global_sigma.rds")
+global_sigma <- readRDS("../saves/global_sigma.rds")
 
 #### summaries
-
-# model_pred_summary <- model_pred %>%
-#   group_by(item,age)%>%
-#   summarise(mode = estimate_mode(pred),
-#             uci = hdi_upper(pred),
-#             lci = hdi_lower(pred))
 
@@
 ```{r}
-plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(Chain)))+
+plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(chain)))+
   geom_density(alpha = 0.3)+
@@
 
-plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(Chain)))+
+plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(chain)))+
   geom_density(alpha = 0.3)+
@@
 ```{r}
-plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
+plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(chain)))+
   geom_density(alpha = 0.3)+
@@
   labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(alignment~item)+
+  facet_grid(model + alignment~item)+
   theme_few() +

### 2019-10-17 stats/model.Rmd
prepare model file for run

@@
 Infer({model,
-      samples: 10,
-      burn: 10,
+      samples: 50000,
+      burn: 250000,
       verbose: T,
-      lag: 4,
+      lag: 10,
       verboseLag: 5000,
@@
   model_var = "model",
-  chains = 4,
-  cores = 4,
+  chains = 2,
+  cores = 2,
   packages = c("webppl_packages/webppl-sample-writer")
@@
 
-bind_rows(
-sem_know_model <- read_csv("../saves/model/samples628.csv")%>%mutate(chain =1)
+read_csv("../saves/model/samples434.csv")%>%mutate(chain =1)%>%
+  saveRDS("../saves/model/chain_1.rds")
+
+read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
+  saveRDS("../saves/model/chain_2.rds")
+
+read_csv("../saves/model/samples434.csv")%>%mutate(chain =1)%>%
+  saveRDS("../saves/model/chain_3.rds")
+
+read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
+  saveRDS("../saves/model/chain_4.rds")
+
+read_csv("../saves/model/samples434.csv")%>%mutate(chain =1)%>%
+  saveRDS("../saves/model/chain_5.rds")
+
+read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
+  saveRDS("../saves/model/chain_6.rds")
+
+read_csv("../saves/model/samples434.csv")%>%mutate(chain =1)%>%
+  saveRDS("../saves/model/chain_7.rds")
+
+read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
+  saveRDS("../saves/model/chain_8.rds")
+
+read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
+  saveRDS("../saves/model/chain_9.rds")
+
+read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
+  saveRDS("../saves/model/chain_10.rds")
+
+sem_know_model <- bind_rows(
+  readRDS("../saves/model/chain_1.rds"),
+  readRDS("../saves/model/chain_2.rds"),
+  readRDS("../saves/model/chain_3.rds"),
+  readRDS("../saves/model/chain_4.rds"),
+  readRDS("../saves/model/chain_5.rds"),
+  readRDS("../saves/model/chain_6.rds"),
+  readRDS("../saves/model/chain_7.rds"),
+  readRDS("../saves/model/chain_8.rds"),
+  readRDS("../saves/model/chain_9.rds"),
+  readRDS("../saves/model/chain_10.rds")
 )
@@
 saveRDS(sem_know_model, "../saves/model_complete.rds")
-
-sem_know_model <- readRDS("../saves/model_complete.rds")
 

### 2019-11-13 stats/kids_basic_me.Rmd
first draft prior model

@@
   geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
-  geom_smooth(method = "loess", se = F, alpha = .5)+
+  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
+  #geom_smooth(method = "loess", se = F, alpha = .5)+
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
 
-ggsave("../graphs/me_by_item.png", width = 6, height = 3, scale = 1.2)
+ggsave("../graphs/me_by_item.png", width = 5, height = 4, scale = 1.2)
 ```

### 2019-11-13 stats/kids_novelty.Rmd
first draft prior model

@@
 
-d <- read_csv("../data/novelty.csv")%>%
+d_spin <- read_csv("../data/novelty.csv")%>%
   mutate(subage = factor(subage))
@@
 ## sanity checks
-d %>%
+d_spin %>%
   group_by(experiment,subage) %>%
@@
 
-ggsave("../graphs/novelty.png", width = 5, height = 3, scale = 1.2)
+ggsave("../graphs/novelty.png", width = , height = 4, scale = 1.2)
 ```

### 2019-11-13 stats/model.Rmd
first draft prior model

--- 2019-10-17 stats/model.Rmd
@@
 library(data.table)
+library(bigmemory)
+library(langcog)
 
@@
 
-data_comb_log
 ```
@@
 ## Model code
+
+### Prior model
+
+```{r}
+prior_params <- '
+
+var priorData = dataFromR.data
+
+var subjects = levels(priorData, "subid")
+
+//display(subjects)
+
+var model  = function(){
+
+  var prior_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+  var prior_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+  var subject_sigma = uniformDrift({a: 0, b:3, width: 0.2})
+
+  var sampleSub = function(age){
+    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
+  }
+
+  foreach(function(subid){
+      var subjectData = _.filter(priorData, {subid: subid})
+
+      display(subjects)
+
+      var subj_age = subjectData[0].age
+      var subjectPrior = sampleSub(subj_age)
+
+    foreach(function(row){
+
+      var priorReg = logistic(prior_int + prior_slope * subjectPrior)
+
+      var prior = [priorReg, 1-priorReg]
+
+      var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: prior}));
+      return obj.shape == "novel_object" ? 1 : 0
+       }})
+
+     observe(modelPredictions, row.correct)
+
+    }, subjectData)
+
+  }, subjects)
+
+  query.add(["intercept"], [prior_int])
+  query.add(["slope"], [prior_slope])
+  query.add(["sigma"], [subject_sigma])
+
+  return query
+
+}
+
+'
+```
+
+```{r}
+
+prior_data <- read_csv("../data/novelty.csv")%>%
+  mutate(age = age_num - min(age_num))
+
+prior_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, prior_params , sep='\n'),
+  data = list(data = prior_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 3,
+  cores = 3,
+  inference_opts = list(method = "MCMC", samples = 10000, burn = 5000, verbose = T)
+)
+
+prior <- prior_model%>%
+  mutate(value = unlist(value))%>%
+  filter(Chain !=2)
+
+prior_summary <- prior%>%
+  group_by(Parameter)%>%
+  summarise(param_map = estimate_mode(value))
+
+```
+
+```{r}
+ggplot(prior, aes(x = value, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(Parameter~., scales = 'free')+
+  theme_few()
+
+```
+
+```{r}
+novel_bm <- readRDS("../saves/novelty_model.rds")
+summary(novel_bm)
+```
 
@@
 
-bind_rows(
-sem_know_model <- read_csv("../saves/model/samples628.csv")%>%mutate(chain =1)
+```
+## Model comparison
+
+```{r}
+log_like <- bind_rows(
+  readRDS("../saves/log_like_chain1.rds")%>%mutate(chain = 1),
+  readRDS("../saves/log_like_chain2.rds")%>%mutate(chain = 2),
+  readRDS("../saves/log_like_chain3.rds")%>%mutate(chain = 3),
+  readRDS("../saves/log_like_chain4.rds")%>%mutate(chain = 4),
+  readRDS("../saves/log_like_chain5.rds")%>%mutate(chain = 5)
 )
-
-saveRDS(sem_know_model, "../saves/model_complete.rds")
-
-sem_know_model <- readRDS("../saves/model_complete.rds")
-
-```
-## Model comparison
-
-```{r}
-log_like <- sem_know_model %>%
-  filter(a == "log_like")%>%
-  select(b,c,e)%>%
-  rename(model = b, 
-         parameter = c,
-         log_like = e)
-
-saveRDS(log_like, "../saves/log_like.rds")
-log_like <- readRDS("../saves/log_like.rds")
 
@@
 
-saveRDS(log_like_model, "../saves/log_like_model.rds")
-log_like_model <- readRDS("../saves/log_like_model.rds")
-
 log_like_chain<- log_like %>%
@@
 
-saveRDS(log_like_chain, "../saves/log_like_chain.rds")
-log_like_chain <- readRDS("../saves/log_like_chain.rds")
-
 log_like_chain %>%
@@
          parameter_free = round(parameter_free,2))%>%
-  summarise(range_noise = paste(range(noise)[1],range(noise)[2], sep = " / "))
+  summarise(range_param_free = paste(range(parameter_free)[1],range(parameter_free)[2], sep = " / "),
+            range_noise = paste(range(noise)[1],range(noise)[2], sep = " / "))
+
+log_like_2 <-  readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")%>%
+  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
+  filter(parameter == "log_like")%>%
+  separate(value, into = c("na", "log_like"),sep = ",")%>%
+  select(-na, -alignment)%>%
+  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))
+
+log_like_model_2 <- log_like_2%>%
+  group_by(model,noise)%>%
+  summarize(logP = logSumExp(log_like))
+
+model_comp <- log_like_2%>%
+  spread(model,log_like)%>%
+  mutate(prag_vs_prag_global = pragmatics - pragmatics_global,
+         prag_vs_flat_prior = pragmatics - flat_prior,
+         prag_vs_prior_only = pragmatics - prior_only)%>%
+  group_by(noise)%>%
+  summarize(prag_vs_prag_global = logSumExp(prag_vs_prag_global),
+            prag_vs_flat_prior = logSumExp(prag_vs_flat_prior),
+            prag_vs_prior_only = logSumExp(prag_vs_prior_only))
+
+```
+
+```{r}
+ggplot(log_like_model, aes(x = model, y = logP, col = model))+
+  geom_segment( aes(x=model, xend=model, y=-1150, yend=logP), col = "black", size = 1)+
+  geom_point(size = 7)+
+  theme_few()+ 
+  xlab("")+
+  ylab("Log-likelihood")+
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  facet_grid(~parameter)+
+  ylim(-1750,-1150)+
+  scale_color_ptol(breaks=c("pragmatics","pragmatics_global","prior_only","flat_prior"),
+                     labels=c("Pragmatic", "Pragmatic global","Prior only","Flat prior"))+
+    theme(axis.text.x=element_blank(), 
+        axis.ticks.x=element_blank())
+```
+
+```{r}
+ggsave("../graphs/like.png", width = 6, height = 2.5, scale = 1.5)
 ```
@@
 
-model_params<- sem_know_model %>%
-  filter(a == "parameter")
-
-saveRDS(model_params, "../saves/model_params.rds")
-model_params <- readRDS("../saves/model_params.rds")
+model_params <- bind_rows(
+  readRDS("../saves/model_params_chain1.rds")%>%mutate(chain = 1),
+  readRDS("../saves/model_params_chain2.rds")%>%mutate(chain = 2),
+  readRDS("../saves/model_params_chain3.rds")%>%mutate(chain = 3),
+  readRDS("../saves/model_params_chain4.rds")%>%mutate(chain = 4),
+  readRDS("../saves/model_params_chain5.rds")%>%mutate(chain = 5)
+
+)
 
@@
 
-saveRDS(item_params, "../saves/item_params.rds")
-item_params <- readRDS("../saves/item_params.rds")
-
 global_params <- model_params %>%
@@
 
-saveRDS(global_params, "../saves/global_params.rds")
-global_params <- readRDS("../saves/global_params.rds")
-
-global_sigma<- sem_know_model %>%
+global_sigma<- model_params %>%
   filter(b == "sigma")%>%
@@
   gather(parameter, value, int, slope)
-
-saveRDS(global_sigma, "../saves/global_sigma.rds")
-global_sigma <- readRDS("../saves/global_sigma.rds")
 
@@
 
-```{r}
-
-plot_model_pred <- model_pred%>%
+### Pragmatic free model
+
+```{r}
+data_comb_plot<-data_comb%>%
+  mutate(model = "data")
+
+model_pred_prag_free<- bind_rows(
+  readRDS("../saves/model_pred_pragmatic_free_chain1.rds")%>%mutate(chain = 1),
+  readRDS("../saves/model_pred_pragmatic_free_chain2.rds")%>%mutate(chain = 2),
+  readRDS("../saves/model_pred_pragmatic_free_chain3.rds")%>%mutate(chain = 3),
+  readRDS("../saves/model_pred_pragmatic_free_chain4.rds")%>%mutate(chain = 4),
+  readRDS("../saves/model_pred_pragmatic_free_chain5.rds")%>%mutate(chain = 5)
+)
+
+plot_model_pred_prag_free <- model_pred_prag_free%>%
   mutate(model = paste(model, parameter, sep = "_"))%>%
@@
 
+saveRDS(plot_model_pred_prag_free, "../saves/plot_model_pred_prag_free.rds")
+plot_model_pred_prag_free <- readRDS("../saves/plot_model_pred_prag_free.rds")
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_pred_prag_free, aes(x=age+2,y = mean, col = model), size = 1)+
+  geom_ribbon(data = plot_model_pred_prag_free, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F, col = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+
+x <- sample(1:48000, 500)
+
+plot_model_prag_noise_line <- model_pred_prag_free%>%
+  filter(iteration %in% x)
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(data = plot_model_prag_noise_line, aes(x=age+2,y = pred, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .05)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol(name = NULL)
+```
+
+```{r}
+ggsave("../graphs/pred_model_data.pdf", width = 10, height = 4, scale = 1)
+```
+
+### Pragmatic noise model
+
+```{r}
+
+model_pred_prag_noise<- bind_rows(
+  readRDS("../saves/model_pred_pragmatic_noise_chain1.rds")%>%mutate(chain = 1),
+  readRDS("../saves/model_pred_pragmatic_noise_chain2.rds")%>%mutate(chain = 2),
+  readRDS("../saves/model_pred_pragmatic_noise_chain3.rds")%>%mutate(chain = 3),
+  readRDS("../saves/model_pred_pragmatic_noise_chain4.rds")%>%mutate(chain = 4),
+  readRDS("../saves/model_pred_pragmatic_noise_chain5.rds")%>%mutate(chain = 5)
+)
+
+plot_model_pred_prag_noise <- model_pred_prag_noise%>%
+  mutate(model = paste(model, parameter, sep = "_"))%>%
+  group_by(model, alignment, item, age)%>%
+  summarise(mean = estimate_mode(pred),
+            ci_lower = hdi_lower(pred),
+            ci_upper = hdi_upper(pred))
+
+saveRDS(plot_model_pred_prag_noise, "../saves/plot_model_pred_prag_noise.rds")
+plot_model_pred_prag_noise <- readRDS("../saves/plot_model_pred_prag_noise.rds")
+
+plot_model_pred_prag_noise_chain <- model_pred_prag_noise%>%
+  mutate(model = paste(model, parameter, sep = "_"))%>%
+  group_by(model, alignment, item,chain, age)%>%
+  summarise(mean = estimate_mode(pred),
+            ci_lower = hdi_lower(pred),
+            ci_upper = hdi_upper(pred))
+
+saveRDS(plot_model_pred_prag_noise_chain, "../saves/plot_model_pred_prag_noise_chain.rds")
+plot_model_pred_prag_noise_chain <- readRDS("../saves/plot_model_pred_prag_noise_chain.rds")
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_ribbon(data = plot_model_pred_prag_noise, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .3) +
+  geom_line(data = plot_model_pred_prag_noise, aes(x=age+2,y = mean, col = model), size = 1, alpha = .5)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+
+x <- sample(1:48000, 500)
+
+plot_model_prag_noise_line <- model_pred_prag_noise%>%
+  filter(iteration %in% x)
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .4, span = 2)+
+  geom_line(data = plot_model_prag_noise_line, aes(x=age+2,y = pred, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .075)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol(name = NULL)
+```
+
+```{r}
+ggsave("../graphs/model_pred_noise_ribbon.pdf", width = 10, height = 4, scale = 1.2)
+```
+
+### Global pragmatic free model
+
+```{r}
+
+model_pred_global_free<- bind_rows(
+  readRDS("../saves/model_pred_globalPrag_free_chain1.rds")%>%mutate(chain = 1),
+  readRDS("../saves/model_pred_globalPrag_free_chain2.rds")%>%mutate(chain = 2)
+)
+
+plot_model_pred_global_free <- model_pred_global_free%>%
+  mutate(model = paste(model, parameter, sep = "_"))%>%
+  group_by(model, alignment, item, age)%>%
+  summarise(mean = estimate_mode(pred),
+            ci_lower = hdi_lower(pred),
+            ci_upper = hdi_upper(pred))
+
+saveRDS(plot_model_pred_global_free, "../saves/plot_model_pred_global_free.rds")
+plot_model_pred_global_free <- readRDS("../saves/plot_model_pred_global_free.rds")
+
 ggplot() +
@@
   #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
-  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  geom_line(data = plot_model_pred_global_free, aes(x=age+2,y = mean, col = model), size = 1)+
+  geom_ribbon(data = plot_model_pred_global_free, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
 
-## Correlate model predictions
+### Global pragmatic noise model
+
+```{r}
+
+model_pred_global_noise<- bind_rows(
+  readRDS("../saves/model_pred_globalPrag_noise_chain1.rds")%>%mutate(chain = 1),
+  readRDS("../saves/model_pred_globalPrag_noise_chain2.rds")%>%mutate(chain = 2)
+)
+
+plot_model_pred_global_noise <- model_pred_global_noise%>%
+  mutate(model = paste(model, parameter, sep = "_"))%>%
+  group_by(model, alignment, item, age)%>%
+  summarise(mean = estimate_mode(pred),
+            ci_lower = hdi_lower(pred),
+            ci_upper = hdi_upper(pred))
+
+saveRDS(plot_model_pred_global_noise, "../saves/plot_model_pred_global_noise.rds")
+plot_model_pred_global_noise <- readRDS("../saves/plot_model_pred_global_noise.rds")
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_pred_global_noise, aes(x=age+2,y = mean, col = model), size = 1)+
+  geom_ribbon(data = plot_model_pred_global_noise, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(model + alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+```
+
+## Correlate model predictions and data
 
@@
 
-cor_model_pred <- model_pred%>%
+cor_prag_free <- model_pred_prag_free%>%
   mutate(model = paste(model, parameter, sep = "_"))%>%
@@
 
+saveRDS(cor_prag_free, "../saves/cor_prag_free.rds")
+cor_prag_free <- readRDS( "../saves/cor_prag_free.rds")
+
+cor_prag_noise <- model_pred_prag_noise%>%
+  mutate(model = paste(model, parameter, sep = "_"))%>%
+  mutate(age = as.numeric(age) + min(me_data$age_num),
+         age = cut(age, 
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(model, alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
+
+saveRDS(cor_prag_noise, "../saves/cor_prag_noise.rds")
+cor_prag_noise <- readRDS( "../saves/cor_prag_noise.rds")
+
+cor_global_free <- model_pred_global_free%>%
+  mutate(model = paste(model, parameter, sep = "_"))%>%
+  mutate(age = as.numeric(age) + min(me_data$age_num),
+         age = cut(age, 
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(model, alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
+
+cor_global_noise <- model_global_noise%>%
+  mutate(model = paste(model, parameter, sep = "_"))%>%
+  mutate(age = as.numeric(age) + min(me_data$age_num),
+         age = cut(age, 
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(model, alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
+
+cor_model_pred <- bind_rows(
+  cor_prag_free,
+  cor_prag_noise
+ # cor_global_free,
+#  cor_global_noise
+)
+
 plot_cor_model_pred <- cor_model_pred %>%
@@
     bind_rows(
-      binnned_data%>%mutate(model = "globalPrag_free"),
-      binnned_data%>%mutate(model = "globalPrag_noise"),
+      #binnned_data%>%mutate(model = "globalPrag_free"),
+      #binnned_data%>%mutate(model = "globalPrag_noise"),
       binnned_data%>%mutate(model = "pragmatic_free"),
@@
 
+saveRDS(plot_cor_model_pred, "../saves/model_cor.rds")
+plot_cor_model_pred <- readRDS( "../saves/model_cor.rds")
+
 ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = item)) +
@@
   geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
-  geom_point(size = 1,  stroke = 1)+
+  geom_point(size = 1.5, stroke = 1)+
   coord_fixed()+
@@
   ylab("Data")+
-  facet_grid(age~model)+
+  facet_grid(model~age)+
   theme_few() + 
   scale_colour_viridis_d(name ="Item")
+```
+
+```{r}
+ggsave("../graphs/cor_model_data.pdf", width = 8, height = 3.5, scale = 1)
 ```
@@
 
-#summary(novel_bm)
+summary(novel_bm)
 
@@
   labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_wrap(~item)+
+  facet_grid(alignment~item)+
   theme_few() +
@@
   scale_fill_ptol(name = NULL)
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+geom_smooth(data = data_comb_plot, 
+            aes(x = age_num, y = correct), 
+            col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5)+
+  geom_pointrange(data = p1, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper))+
+  geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .6) +
+  geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = model), size = 1, alpha = 1)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_wrap(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol(name = NULL)+
+  scale_fill_ptol(name = NULL)
+
+p1 <- data_comb%>%
+  mutate(alignment = condition)%>%
+  group_by(alignment, item ,subage)%>%
+  multi_boot_standard(col = "correct")
+
+ggplot(p1, aes(x = subage, y = mean))+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))+
+  facet_grid(condition ~familiarObject)+
+  geom_line(aes(group=condition))+
+  geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = model), size = 1, alpha = 1)+
+  geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .5) +
+  theme_few() +
 
@@
     filter(Parameter %in% c("noise"))%>%
-    mutate(Model = "Pragmatic no word knowledge"),
+    mutate(Model = "Pragmatic global"),
   flat_model_noise %>%
@@
 ggplot(noise_plot, aes(x = value, col = Model, fill = Model))+
-  geom_density(alpha = .7)+
+  geom_density(alpha = .7, bw = .01)+
   theme_few()+
@@
   scale_fill_ptol()+
-  theme(legend.position = "bottom")
-
+  theme()
+
+```
+
+```{r}
+ggsave("../graphs/noise.pdf", width = 6, height = 3, scale = 1.2)
 ```
@@
   mutate(age = as.numeric(age) + min(me_data$age_num),
-         subage = cut(age, 
+         subage = factor(cut(age, 
                       breaks = c(2,3,4,5),
-                      labels = c(2,3,4)))%>%
+                      labels = c(2,3,4))))%>%
   group_by(subage, alignment, item)%>%
@@
   ylab("Data")+
-  facet_grid(model~subage)+
+  facet_grid(~subage)+
   theme_few() + 
   scale_colour_viridis_d(name ="Item")
+```
+
+```{r}
+ggsave("../graphs/cor_plot_noise.pdf", width = 10, height = 4, scale = .8)
 ```

### 2019-11-13 stats/model.Rmd
first draft prior model
prior model update

@@
 
-      display(subjects)
+      //display(subjects)
 
       var subj_age = subjectData[0].age
+
       var subjectPrior = sampleSub(subj_age)
+
+      display(subjectPrior)
 
@@
   model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 10000, burn = 5000, verbose = T)
-)
+  chains = 1,
+  cores = 1,
+  inference_opts = list(method = "MCMC", samples = 1, burn = 1, verbose = T)
+)
+
+saveRDS(prior_model, "../saves/prior_model.rds")
 
 prior <- prior_model%>%
-  mutate(value = unlist(value))%>%
-  filter(Chain !=2)
+  mutate(value = unlist(value))
 
@@
 ```
+
+#### Visualizing parameters
 
@@
 
-```{r}
-novel_bm <- readRDS("../saves/novelty_model.rds")
+#### Comparison to brm models
+
+```{r}
+
+# same model as webppl model  implemented in brms
+
+novel_bm <- brm(correct ~ age + (1 | subid), 
+          data = prior_data, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 20000)
+
 summary(novel_bm)
+
+saveRDS(novel_bm, "../saves/novelty_model_brm.rds")
+```
+
+```{r}
+# brm model from last chunk
+novel_bm <- readRDS("../saves/novelty_model_brm.rds")
+
+brm_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
+  select(term,Estimate)%>%
+  spread(term, Estimate)
+
+brm_plot <- tibble(
+  age = prior_data$age,
+  y = plogis(brm_params$Intercept + brm_params$age * age),
+  model = "brm"
+)
+
+#brm model with additional random intercept and slope for item
+novel_bm_full <- readRDS("../saves/novelty_model.rds")
+
+brm_full_params <- as_tibble(fixef(novel_bm_full), rownames = "term")%>%
+  select(term,Estimate)%>%
+  spread(term, Estimate)
+
+brm_full_plot <- tibble(
+  age = prior_data$age,
+  y = plogis(brm_full_params$Intercept + brm_full_params$age_num * age),
+  model = "brm_full"
+)
+
+# webppl model
+webppl_plot <- tibble(
+  age = prior_data$age,
+  y = plogis(prior_summary%>%filter(Parameter == "intercept")%>%pull(param_map) + prior_summary%>%filter(Parameter == "slope")%>%pull(param_map) * age),
+  model = "webppl"
+)
+
+prior_comp_plot <- bind_rows(
+  brm_plot,
+  webppl_plot,
+  brm_full_plot
+
+)
+```
+
+```{r}
+ggplot(prior_comp_plot, aes(x = age, y = y, col = model))+
+  geom_line()+
+  ylim(0,1)+
+  theme_few()+
+  scale_color_ptol()
 ```

### 2019-11-14 stats/model.Rmd
update model with prior estimation integrated

@@
 
+prior_data <- read_csv("../data/novelty.csv")
+
+prior_model_data <- read_csv("../data/novelty.csv")%>%
+  mutate(age = age_num - min(age_num))
+
+me_model_data <- read_csv("../data/me.csv")%>%
+    filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(age = age_num - min(age_num))
+
+data_comb_plot<-data_comb%>%
+  mutate(model = "data")
+
 ```
@@
 ```{r}
-me_model_data <- read_csv("../data/me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(age = age_num - min(age_num))
 
@@
 
-var subjects = levels(priorData, "subid")
+var priorSubjects = levels(priorData, "subid")
 
@@
 
-  var subject_sigma = uniformDrift({a: 0, b:3, width: 0.2})
-
-  var sampleSub = function(age){
-    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
+  var prior_subject_sigma = uniformDrift({a: 0, b:3, width: 0.2})
+
+  var priorSampleSub = function(age){
+    return gaussianDrift({ mu: age, sigma: prior_subject_sigma, width: 0.1 })
   }
@@
   foreach(function(subid){
-      var subjectData = _.filter(priorData, {subid: subid})
+      var priorSubjectData = _.filter(priorData, {subid: subid})
 
@@
 
-      var subj_age = subjectData[0].age
-
-      var subjectPrior = sampleSub(subj_age)
-
-      display(subjectPrior)
+      var subj_age = priorSubjectData[0].age
+
+      var subjectPrior = priorSampleSub(subj_age)
 
@@
 
-    }, subjectData)
-
-  }, subjects)
+    }, priorSubjectData)
+
+  }, priorSubjects)
 
@@
   query.add(["slope"], [prior_slope])
-  query.add(["sigma"], [subject_sigma])
+  query.add(["sigma"], [prior_subject_sigma])
 
@@
 ```{r}
-
-prior_data <- read_csv("../data/novelty.csv")%>%
-  mutate(age = age_num - min(age_num))
 
@@
   program_code = paste(rsaUtils, rsaModel, prior_params , sep='\n'),
-  data = list(data = prior_data),
+  data = list(data = prior_model_data),
   data_var = "dataFromR",
@@
 
+prior_model <- readRDS("../saves/prior_model.rds")
+
 prior <- prior_model%>%
@@
 novel_bm <- brm(correct ~ age + (1 | subid), 
-          data = prior_data, family = bernoulli(),
+          data = prior_model_data, family = bernoulli(),
           control = list(adapt_delta = 0.95),
@@
 brm_plot <- tibble(
-  age = prior_data$age,
+  age = prior_model_data$age,
   y = plogis(brm_params$Intercept + brm_params$age * age),
@@
 brm_full_plot <- tibble(
-  age = prior_data$age,
+  age = prior_model_data$age,
   y = plogis(brm_full_params$Intercept + brm_full_params$age_num * age),
@@
 webppl_plot <- tibble(
-  age = prior_data$age,
+  age = prior_model_data$age,
   y = plogis(prior_summary%>%filter(Parameter == "intercept")%>%pull(param_map) + prior_summary%>%filter(Parameter == "slope")%>%pull(param_map) * age),
@@
 
+### Combination Model
+
 ```{r work in progress}
 sem_subj_str <- '
+
 var data = dataFromR.data
+var priorData = dataFromR.data
 
@@
 var subjects = levels(data, "subid")
+var priorSubjects = levels(priorData, "subid")
 
 var model  = function(){
+
+//////////////// Prior ////////////////////////
+
+ var prior_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+  var prior_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+  var prior_subject_sigma = uniformDrift({a: 0, b:3, width: 0.2})
+
+  var priorSampleSub = function(age){
+    return gaussianDrift({ mu: age, sigma: prior_subject_sigma, width: 0.1 })
+  }
+
+  foreach(function(subid){
+      var priorSubjectData = _.filter(priorData, {subid: subid})
+
+      //display(subjects)
+
+      var subj_age = priorSubjectData[0].age
+
+      var subjectPrior = priorSampleSub(subj_age)
+
+    foreach(function(row){
+
+      var priorReg = logistic(prior_int + prior_slope * subjectPrior)
+
+      var prior = [priorReg, 1-priorReg]
+
+      var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: prior}));
+      return obj.shape == "novel_object" ? 1 : 0
+       }})
+
+     observe(modelPredictions, row.correct)
+
+    }, priorSubjectData)
+
+  }, priorSubjects)
+
+  query.add(["parameter","parameters", "prior"], [prior_int, prior_slope])
+  query.add(["parameter","sigma", "prior"], ["NA", prior_subject_sigma])
+
+//////////////// Semantic knowledge and speaker optimality ////////////////////////
 
@@
 
+//////////////// Model predictions and combination ////////////////////////
+
 var noise = uniformDrift({a: 0, b:1, width: 0.1})
@@
 var all_log_likes = map(function(row) {
-  var prior = [row.prior, 1-row.prior]
+
+  var priorReg = logistic(prior_int + prior_slope * row.age)
+
+  var cond = row.condition
+
+  var prior = function(cnd){
+    var cndPrior = cnd == "congruent" ? [priorReg, 1-priorReg] : [1-priorReg, priorReg] ;
+    return cndPrior
+  }
+
+  var priorComb = prior(cond)
+
   var itemLineParameters = all_item_parameters[row.item]
+
   var sem_knowledge = logistic(itemLineParameters.intercept + 
@@
   var pragModelPredictions = pragmaticListener({label: "novel_word"}, 
-                                               prior, speakerOptimality, 
+                                               priorComb, speakerOptimality, 
                                                sem_knowledge)
@@
   var globalPragModelPredictions = pragmaticListener({label: "novel_word"}, 
-                                               prior, speakerOptimality, 
+                                               priorComb, speakerOptimality, 
                                                global_sem_knowledge)
@@
   var priorOnlyModelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: prior}));
+      var obj = sample( Categorical({vs: all_objects, ps: priorComb}));
       return obj.shape == "novel_object" ? 1 : 0
@@
 
-    query.add(["modelPrediction","pragmatic","noise", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(noisyPragModelPredictions.score(1))])
-
   query.add(["modelPrediction","pragmatic","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])
 
-  query.add(["modelPrediction","globalPrag","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(globalPragModelPredictions.score(1))])
-
-  query.add(["modelPrediction","globalPrag","noise", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(noisyGlobalPragModelPredictions.score(1))])
+//  query.add(["modelPrediction","globalPrag","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(globalPragModelPredictions.score(1))])
 
@@
       samples: 50000,
-      burn: 250000,
+      burn: 50000,
       verbose: T,
-      lag: 10,
-      verboseLag: 5000,
+      lag: 1,
+      verboseLag: 1000,
       method: "incrementalMH",
@@
   program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
-  data = list(data = me_model_data, comb_data = data_comb_log),
+  data = list(data = me_model_data, comb_data = data_comb_log, prior_data = prior_model_data),
   data_var = "dataFromR",
@@
 
-model_pred <- sem_know_model %>%
+model_pred <- read_csv("../saves/model/samples78.csv") %>%
   filter(a == "modelPrediction")%>%
-  select(-a, -f)%>%
+  select(-a)%>%
   rename(model = b, 
@@
          alignment = d,
+         id = f,
          item = e,
@@
 
+model_pred %>%
+  filter(item == "pawn")%>%
+  arrange(age)
 ```
@@
 ```{r}
-data_comb_plot<-data_comb%>%
-  mutate(model = "data")
 
@@
 
-plot_model_pred_prag_free <- model_pred_prag_free%>%
+plot_model_pred_prag_free <- model_pred%>%
   mutate(model = paste(model, parameter, sep = "_"))%>%

### 2019-11-18 stats/kids_basic_me.Rmd
add model to run in command line

@@
 
-# files <- dir("~/Work/Spin/raw_data/kids/basic_me/")
-# 
-# raw_data <- data_frame()
-# for (f in files) {
-#   jf <- paste("~/Work/Spin/raw_data/kids/basic_me/",f,sep="")
-#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-#   date <- str_sub(jf,44,str_length(jf)-11)
-#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
-#   raw_data <- bind_rows(raw_data, id)
-# }
-# 
-# 
-# length(unique(raw_data$subid))
-#  
-# d_raw <-raw_data %>%
-#   mutate(subid = ifelse(subid == "190314_3", "190314_3_me",subid),
-#          subid = ifelse(subid == "190221_6_me", "190321_6_me",subid),
-#          subid = ifelse(subid == "192203_4_me", "190322_4_me",subid),
-#          subage = ifelse(subid == "190313_5_me", "3",subage),
-#          test_date = as.Date(test_date))
-# 
-# 
-# log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
-#   filter(Condition == "me")%>%
-#   mutate(dob = as.character(dob),
-#          dob = ifelse(subid == "190313_7_me", "2015-11-15",dob),
-#          dob = ifelse(subid == "190313_11_me", "2016-04-18",dob),
-#          dob = ifelse(subid == "190320_8_me", "2014-04-28",dob),
-#          dob = as.Date(dob))%>%
-#   select(subid,experimenter,keep_drop,sex,dob)
-# 
-#  
-# d_raw%>%
-#   group_by(subid)%>%
-#   summarise(n())%>%
-#   filter(!(subid %in% unique(log$subid)))
-# 
-#  
-# d <- left_join(d_raw,log, by = "subid")%>%
-#   filter(keep_drop == "keep")%>%
-#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-#          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
-# 
-# write_csv(d, "../data/me.csv")
+files <- dir("~/Work/Spin/raw_data/kids/basic_me/")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/Spin/raw_data/kids/basic_me/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,44,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+length(unique(raw_data$subid))
+
+d_raw <-raw_data %>%
+  mutate(subid = ifelse(subid == "190314_3", "190314_3_me",subid),
+         subid = ifelse(subid == "190221_6_me", "190321_6_me",subid),
+         subid = ifelse(subid == "192203_4_me", "190322_4_me",subid),
+         subage = ifelse(subid == "190313_5_me", "3",subage),
+         test_date = as.Date(test_date))
+
+log <- read_excel("../../SPIN-subject_log.xlsx", 1)%>%
+  filter(Condition == "me")%>%
+  mutate(dob = as.character(dob),
+         dob = ifelse(subid == "190313_7_me", "2015-11-15",dob),
+         dob = ifelse(subid == "190313_11_me", "2016-04-18",dob),
+         dob = ifelse(subid == "190320_8_me", "2014-04-28",dob),
+         dob = as.Date(dob))%>%
+  select(subid,experimenter,keep_drop,sex,dob)
+
+d_raw%>%
+  group_by(subid)%>%
+  summarise(n())%>%
+  filter(!(subid %in% unique(log$subid)))
+
+d <- left_join(d_raw,log, by = "subid")%>%
+  filter(keep_drop == "keep")%>%
+  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
+  filter(trial != "train1",
+           trial != "train2")%>%
+  mutate(item = familiar,
+         age = age_num - min(age_num))%>%
+  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiar, -rt)
+
+write_csv(d, "../data/me.csv")
+write_json(d, "../data/me.json")
 

### 2019-11-18 stats/kids_combination.Rmd
add model to run in command line

@@
   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
+    mutate(age = age_num - min(age_num))%>%
+  filter(condition != "train")%>%
+  mutate(alignment = condition,
+         item = familiarObject)%>%
+  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiarObject, -rt)
 
@@
 write_csv(d, "../data/combination.csv")
+write_json(d, "../data/combination.json")
 

### 2019-11-18 stats/kids_novelty.Rmd
add model to run in command line

--- 2019-06-21 stats/kids_novelty.Rmd
@@
          experiment = condition)%>%
-  select(-pick_src)
+  mutate(age = age_num - min(age_num))%>%
+  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -rt)
+# 
+# 
+# ## import mcc data
+# 
+# files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")
+# 
+# raw_data_mcc <- data_frame()
+# for (f in files) {
+#   jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
+#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+#   date <- str_sub(jf,51,str_length(jf)-11)
+#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+#   raw_data_mcc <- bind_rows(raw_data_mcc, id)
+# }
+# 
+# d_raw_mcc <-raw_data_mcc %>%
+#   mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
+#          test_date = as.Date(test_date))
+# 
+# 
+# log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
+#   filter(Condition == "nov")%>%
+#   mutate(dob = as.numeric(dob),
+#          dob = as.Date(dob,origin = "1899-12-30"))%>%
+#   select(subid,experimenter,keep_drop,sex,dob)
+# 
+# 
+# d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
+#   filter(keep_drop == "keep")%>%
+#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
+#          leftObject = leftFruit,
+#          rightObject = rightFruit,
+#          pick = str_sub(pick,72,str_length(pick)-4),
+#          agent = ifelse(speakerChange == "false", agent,altAgent),
+#          experiment = "dis_novelty_mcc")%>%
+#   filter(speakerChange == "false", trial != "train")%>%
+#   select(-speakerChange,-altAgent,-leftFruit,-rightFruit)
+# 
+# 
+# # join datasets
+# 
+# d <- bind_rows(d_spin, d_mcc)
+# 
+write_csv(d_spin, "../data/novelty.csv")
 
-## import mcc data
+write_json(d_spin, "../data/novelty.json")
+#write_csv(d, "../data/child_novelty.csv")
 
-files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")
+d_spin <- read_csv("../data/novelty.csv")%>%
+  mutate(subage = factor(subage))
 
-raw_data_mcc <- data_frame()
-for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
-  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,51,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
-  raw_data_mcc <- bind_rows(raw_data_mcc, id)
-}
-
-d_raw_mcc <-raw_data_mcc %>%
-  mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
-         test_date = as.Date(test_date))
-
-log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
-  filter(Condition == "nov")%>%
-  mutate(dob = as.numeric(dob),
-         dob = as.Date(dob,origin = "1899-12-30"))%>%
-  select(subid,experimenter,keep_drop,sex,dob)
-
-d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
-  filter(keep_drop == "keep")%>%
-  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
-         leftObject = leftFruit,
-         rightObject = rightFruit, 
-         pick = str_sub(pick,72,str_length(pick)-4),
-         agent = ifelse(speakerChange == "false", agent,altAgent),
-         experiment = "dis_novelty_mcc")%>%
-  filter(speakerChange == "false", trial != "train")%>%
-  select(-speakerChange,-altAgent,-leftFruit,-rightFruit)
-
-# join datasets
-
-d <- bind_rows(d_spin, d_mcc)
-
-write_csv(d_spin, "../data/child_spin_novelty.csv")
-write_csv(d, "../data/child_novelty.csv")
 ```
@@
 
-d <- read_csv("../data/child_novelty.csv")%>%
-  mutate(subage = factor(subage))
-
 ## sanity checks
-d %>%
+d_spin %>%
   group_by(experiment,subage) %>%
@@
   ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
+  guides(alpha = F, col = F)+ 
   #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
   scale_colour_solarized()
+
+ggsave("../graphs/novelty.png", width = , height = 4, scale = 1.2)
 ```

### 2019-11-18 stats/model.Rmd
minor update model file
add model to run in command line

@@
 data_comb <- data_comb_pre%>%
-  filter(condition != "train")%>%
-  mutate(alignment = condition,
-         item = familiarObject)%>%
   left_join(aoa_ratings)%>%
   ungroup()%>%
-  mutate(item = fct_reorder(factor(familiarObject), mean_aoa), 
+  mutate(item = fct_reorder(factor(item), mean_aoa), 
          source = "Data")
@@
 
-prior_model_data <- read_csv("../data/novelty.csv")%>%
-  mutate(age = age_num - min(age_num))
-
-me_model_data <- read_csv("../data/me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(age = age_num - min(age_num))
+prior_model_data <- read_csv("../data/novelty.csv")
+
+me_model_data <- read_csv("../data/me.csv")
 
@@
 data_comb_log <- read_csv("../data/combination.csv") %>%
-  filter(condition != "train")%>%
-  mutate(alignment = condition,
-         item = familiarObject, 
-         age = age_num - (min(age_num))) %>%
   mutate(nov_int = novel_params$Intercept,
@@
 
-//display(subjects)
+display(priorData)
 
@@
   group_by(Parameter)%>%
-  summarise(param_map = estimate_mode(value))
+  summarise(param_map = estimate_mode(value),
+            param_uci = hdi_upper(value),
+            param_lci = hdi_lower(value))
 
@@
 
+#summary(novel_bm)
+
 brm_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
@@
 novel_bm_full <- readRDS("../saves/novelty_model.rds")
+
+#summary(novel_bm_full)
 

### 2019-11-18 stats/model.Rmd
update model

@@
 
-```{r}
-baseMeModel <- '
-
-var sem_knowledge = 1
-
-var priorProbs = [.5,.5]
-
-var speakerOptimality = 1
-
-var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality, sem_knowledge)
-
-  modelPredictions
-
-'
-```
-
-```{r}
-webppl(program_code = paste(rsaUtils, rsaModel, baseMeModel,sep='\n'))
-```
-
-# Model (nesting within participant)
-
-## Prepare data
-
-```{r}
-
-novel_bm <- readRDS("../saves/novelty_model.rds")
-
-#summary(novel_bm)
-
-novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
-  select(term,Estimate)%>%
-  spread(term, Estimate)
-
-data_comb_log <- read_csv("../data/combination.csv") %>%
-  mutate(nov_int = novel_params$Intercept,
-         nov_slope = novel_params$age_num,
-         prior = ifelse(alignment == "congruent", plogis(nov_int + nov_slope* age),1-plogis(nov_int + age * nov_slope)))
-
-```
-
-## Model code
-
-### Prior model
-
-```{r}
-prior_params <- '
-
-var priorData = dataFromR.data
-
-var priorSubjects = levels(priorData, "subid")
-
-display(priorData)
-
-var model  = function(){
-
-  var prior_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var prior_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-  var prior_subject_sigma = uniformDrift({a: 0, b:3, width: 0.2})
-
-  var priorSampleSub = function(age){
-    return gaussianDrift({ mu: age, sigma: prior_subject_sigma, width: 0.1 })
-  }
-
-  foreach(function(subid){
-      var priorSubjectData = _.filter(priorData, {subid: subid})
-
-      //display(subjects)
-
-      var subj_age = priorSubjectData[0].age
-
-      var subjectPrior = priorSampleSub(subj_age)
-
-    foreach(function(row){
-
-      var priorReg = logistic(prior_int + prior_slope * subjectPrior)
-
-      var prior = [priorReg, 1-priorReg]
-
-      var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: prior}));
-      return obj.shape == "novel_object" ? 1 : 0
-       }})
-
-     observe(modelPredictions, row.correct)
-
-    }, priorSubjectData)
-
-  }, priorSubjects)
-
-  query.add(["intercept"], [prior_int])
-  query.add(["slope"], [prior_slope])
-  query.add(["sigma"], [prior_subject_sigma])
-
-  return query
-
-}
-
-'
-```
-
-```{r}
-
-prior_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, prior_params , sep='\n'),
-  data = list(data = prior_model_data),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 1,
-  cores = 1,
-  inference_opts = list(method = "MCMC", samples = 1, burn = 1, verbose = T)
-)
-
-saveRDS(prior_model, "../saves/prior_model.rds")
-
-prior_model <- readRDS("../saves/prior_model.rds")
-
-prior <- prior_model%>%
-  mutate(value = unlist(value))
-
-prior_summary <- prior%>%
-  group_by(Parameter)%>%
-  summarise(param_map = estimate_mode(value),
-            param_uci = hdi_upper(value),
-            param_lci = hdi_lower(value))
-
-```
-
-#### Visualizing parameters
-
-```{r}
-ggplot(prior, aes(x = value, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Parameter")+
-  facet_grid(Parameter~., scales = 'free')+
-  theme_few()
-
-```
-
-#### Comparison to brm models
-
-```{r}
-
-# same model as webppl model  implemented in brms
-
-novel_bm <- brm(correct ~ age + (1 | subid), 
-          data = prior_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.95),
-          sample_prior = F,
-          save_all_pars = TRUE,
-          iter = 20000)
-
-summary(novel_bm)
-
-saveRDS(novel_bm, "../saves/novelty_model_brm.rds")
-```
-
-```{r}
-# brm model from last chunk
-novel_bm <- readRDS("../saves/novelty_model_brm.rds")
-
-#summary(novel_bm)
-
-brm_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
-  select(term,Estimate)%>%
-  spread(term, Estimate)
-
-brm_plot <- tibble(
-  age = prior_model_data$age,
-  y = plogis(brm_params$Intercept + brm_params$age * age),
-  model = "brm"
-)
-
-#brm model with additional random intercept and slope for item
-novel_bm_full <- readRDS("../saves/novelty_model.rds")
-
-#summary(novel_bm_full)
-
-brm_full_params <- as_tibble(fixef(novel_bm_full), rownames = "term")%>%
-  select(term,Estimate)%>%
-  spread(term, Estimate)
-
-brm_full_plot <- tibble(
-  age = prior_model_data$age,
-  y = plogis(brm_full_params$Intercept + brm_full_params$age_num * age),
-  model = "brm_full"
-)
-
-# webppl model
-webppl_plot <- tibble(
-  age = prior_model_data$age,
-  y = plogis(prior_summary%>%filter(Parameter == "intercept")%>%pull(param_map) + prior_summary%>%filter(Parameter == "slope")%>%pull(param_map) * age),
-  model = "webppl"
-)
-
-prior_comp_plot <- bind_rows(
-  brm_plot,
-  webppl_plot,
-  brm_full_plot
-
-)
-```
-
-```{r}
-ggplot(prior_comp_plot, aes(x = age, y = y, col = model))+
-  geom_line()+
-  ylim(0,1)+
-  theme_few()+
-  scale_color_ptol()
-```
-
-### Combination Model
+# Model
+
+## Combination Model
 
@@
 
-var familiars = levels(data, "familiar")
+var familiars = levels(data, "item")
 var subjects = levels(data, "subid")
@@
 
-        var itemLineParameters = all_item_parameters[row.familiar]
+        var itemLineParameters = all_item_parameters[row.item]
 
@@
 Infer({model,
-      samples: 50000,
-      burn: 50000,
+      samples: 1,
+      burn: 1,
       verbose: T,
@@
   program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
-  data = list(data = me_model_data, comb_data = data_comb_log, prior_data = prior_model_data),
+  data = list(data = me_model_data, comb_data = data_comb, prior_data = prior_model_data),
   data_var = "dataFromR",
@@
 )
-
-```
+```
+
+# Ignore below for now
+
 ## Model comparison
@@
 
+## Base model
+
+```{r}
+baseMeModel <- '
+
+var sem_knowledge = 1
+
+var priorProbs = [.5,.5]
+
+var speakerOptimality = 1
+
+var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality, sem_knowledge)
+
+  modelPredictions
+
+'
+```
+
+```{r}
+webppl(program_code = paste(rsaUtils, rsaModel, baseMeModel,sep='\n'))
+```
+
+## Prior model
+
+```{r}
+prior_params <- '
+
+var priorData = dataFromR.data
+
+var priorSubjects = levels(priorData, "subid")
+
+display(priorData)
+
+var model  = function(){
+
+  var prior_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+  var prior_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+  var prior_subject_sigma = uniformDrift({a: 0, b:3, width: 0.2})
+
+  var priorSampleSub = function(age){
+    return gaussianDrift({ mu: age, sigma: prior_subject_sigma, width: 0.1 })
+  }
+
+  foreach(function(subid){
+      var priorSubjectData = _.filter(priorData, {subid: subid})
+
+      //display(subjects)
+
+      var subj_age = priorSubjectData[0].age
+
+      var subjectPrior = priorSampleSub(subj_age)
+
+    foreach(function(row){
+
+      var priorReg = logistic(prior_int + prior_slope * subjectPrior)
+
+      var prior = [priorReg, 1-priorReg]
+
+      var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: prior}));
+      return obj.shape == "novel_object" ? 1 : 0
+       }})
+
+     observe(modelPredictions, row.correct)
+
+    }, priorSubjectData)
+
+  }, priorSubjects)
+
+  query.add(["intercept"], [prior_int])
+  query.add(["slope"], [prior_slope])
+  query.add(["sigma"], [prior_subject_sigma])
+
+  return query
+
+}
+
+'
+```
+
+```{r}
+
+prior_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, prior_params , sep='\n'),
+  data = list(data = prior_model_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 1,
+  cores = 1,
+  inference_opts = list(method = "MCMC", samples = 1, burn = 1, verbose = T)
+)
+
+saveRDS(prior_model, "../saves/prior_model.rds")
+
+prior_model <- readRDS("../saves/prior_model.rds")
+
+prior <- prior_model%>%
+  mutate(value = unlist(value))
+
+prior_summary <- prior%>%
+  group_by(Parameter)%>%
+  summarise(param_map = estimate_mode(value),
+            param_uci = hdi_upper(value),
+            param_lci = hdi_lower(value))
+
+```
+
+#### Visualizing parameters
+
+```{r}
+ggplot(prior, aes(x = value, fill = factor(Chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(Parameter~., scales = 'free')+
+  theme_few()
+
+```
+
+#### Comparison to brm models
+
+```{r}
+
+# same model as webppl model  implemented in brms
+
+novel_bm <- brm(correct ~ age + (1 | subid), 
+          data = prior_model_data, family = bernoulli(),
+          control = list(adapt_delta = 0.95),
+          sample_prior = F,
+          save_all_pars = TRUE,
+          iter = 20000)
+
+summary(novel_bm)
+
+saveRDS(novel_bm, "../saves/novelty_model_brm.rds")
+```
+
+```{r}
+# brm model from last chunk
+novel_bm <- readRDS("../saves/novelty_model_brm.rds")
+
+#summary(novel_bm)
+
+brm_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
+  select(term,Estimate)%>%
+  spread(term, Estimate)
+
+brm_plot <- tibble(
+  age = prior_model_data$age,
+  y = plogis(brm_params$Intercept + brm_params$age * age),
+  model = "brm"
+)
+
+#brm model with additional random intercept and slope for item
+novel_bm_full <- readRDS("../saves/novelty_model.rds")
+
+#summary(novel_bm_full)
+
+brm_full_params <- as_tibble(fixef(novel_bm_full), rownames = "term")%>%
+  select(term,Estimate)%>%
+  spread(term, Estimate)
+
+brm_full_plot <- tibble(
+  age = prior_model_data$age,
+  y = plogis(brm_full_params$Intercept + brm_full_params$age_num * age),
+  model = "brm_full"
+)
+
+# webppl model
+webppl_plot <- tibble(
+  age = prior_model_data$age,
+  y = plogis(prior_summary%>%filter(Parameter == "intercept")%>%pull(param_map) + prior_summary%>%filter(Parameter == "slope")%>%pull(param_map) * age),
+  model = "webppl"
+)
+
+prior_comp_plot <- bind_rows(
+  brm_plot,
+  webppl_plot,
+  brm_full_plot
+
+)
+```
+
+```{r}
+ggplot(prior_comp_plot, aes(x = age, y = y, col = model))+
+  geom_line()+
+  ylim(0,1)+
+  theme_few()+
+  scale_color_ptol()
+```
+
 ## sem knowledge

### 2019-11-18 stats/model.Rmd
fix model bug

@@
 
-  query.add(["modelPrediction","pragmatic","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])
-
-//  query.add(["modelPrediction","globalPrag","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(globalPragModelPredictions.score(1))])
+  query.add(["modelPrediction","pragmatic","free", row.alignment, row.item, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])
+
+//  query.add(["modelPrediction","globalPrag","free", row.alignment, row.item, row.subid], [row.age, Math.exp(globalPragModelPredictions.score(1))])
 

### 2019-11-26 stats/kids_basic_me.Rmd
make age discrete in month

@@
   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+          age_month = lubridate::time_length(difftime(test_date,dob), "month"),
+         age_month = round(age_month),
          check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
@@
 aoa_ratings <- aoa_ratings_all %>%
-  filter(Word %in% d$familiar )%>%
+  filter(Word %in% d$item )%>%
   mutate(mean_aoa = as.numeric(Rating.Mean),
-         familiar = Word)%>%
-  select(familiar,mean_aoa)
+         item = Word)%>%
+  select(item,mean_aoa)
 ```
@@
 ```{r}
-d_model <- d %>%
-    filter(trial != "train1",
-         trial != "train2")%>%
-  mutate(age_num = age_num - mean(age_num))
 
-model <- brm(correct ~ age_num + (1|subid) + (age_num | familiar),
-                    data = d_model, family = bernoulli(),
+model <- brm(correct ~ age + (1|subid) + (age | item),
+                    data = d, family = bernoulli(),
           control = list(adapt_delta = 0.95),
           sample_prior = F,
+          cores = 4, 
+          chains = 4,
           save_all_pars = TRUE,
@@
 
-ranef_plot <- as_tibble(ranef$familiar, rownames = "familiar")%>%
+ranef_plot <- as_tibble(ranef$item, rownames = "item")%>%
   mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
-         grand_slope = fixef%>%filter(term=="age_num")%>%pull(Estimate))%>%
-  group_by(familiar) %>%
-  expand(Estimate.Intercept,Estimate.age_num,grand_intercept,grand_slope,age = d$age_num - mean(d$age_num))%>%
-  mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age_num+grand_slope)*age), 
-         age = age+mean(d$age_num))%>%
+         grand_slope = fixef%>%filter(term=="age")%>%pull(Estimate))%>%
+  group_by(item) %>%
+  expand(Estimate.Intercept,Estimate.age,grand_intercept,grand_slope, age = d$age)%>%
+  mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age+grand_slope)*age), 
+         age = age+min(d$age_num))%>%
   left_join(aoa_ratings)%>%
   ungroup()%>%
-  mutate(familiar = fct_reorder(factor(familiar), mean_aoa))
+  mutate(item = fct_reorder(factor(item), mean_aoa))
 
-model_plot <- ggplot(ranef_plot, aes(x=age,y = y, col = familiar))+
+model_plot <- ggplot(ranef_plot, aes(x=age,y = y, col = item))+
   geom_hline(yintercept = 0.5, lty=2)+
@@
 
-cor_plot <- as_tibble(ranef$familiar, rownames = "familiar") %>%
+cor_plot <- as_tibble(ranef$item, rownames = "item") %>%
   left_join(aoa_ratings)
@@
   geom_smooth(method = "lm")+
-  xlab("Age of acquisition rating")+
+  xlab("Rated age of acquisition")+
   ylab("ME effect (model intercept)")+
-  stat_cor(method = "pearson", label.x = 8, label.y = .99)+
-  coord_fixed(ratio = 2)+
+  stat_cor(method = "pearson", label.x = 5, label.y = .99)+
+  coord_fixed(ratio = 3)+
   theme_few()
 
+```
+
+```{r}
+ggsave("../graphs/talk_me_rating_cor.pdf", width = 4, height = 4, scale = 1)
 ```

### 2019-11-26 stats/kids_combination.Rmd
make age discrete in month

--- 2019-09-17 stats/kids_combination.Rmd
@@
   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+         age_month = lubridate::time_length(difftime(test_date,dob), "month"),
+         age_month = round(age_month),
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
+    mutate(age = age_num - min(age_num))%>%
+  filter(condition != "train")%>%
+  mutate(alignment = condition,
+         item = familiarObject)%>%
+  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiarObject, -rt)
 

### 2019-11-26 stats/kids_novelty.Rmd
make age discrete in month

@@
   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+         age_month = lubridate::time_length(difftime(test_date,dob), "month"),
+         age_month = round(age_month),
          check_age = ifelse(substr(age_num,1,1) == subage, T, F),

### 2019-11-26 stats/model.Rmd
fix model bug
make age discrete in month

@@
 Infer({model,
-      samples: 1,
-      burn: 1,
+      samples: 10,
+      burn: 10,
       verbose: T,
@@
             prag_vs_flat_prior = logSumExp(prag_vs_flat_prior),
-            prag_vs_prior_only = logSumExp(prag_vs_prior_only))
-
-```
-
-```{r}
-ggplot(log_like_model, aes(x = model, y = logP, col = model))+
+            prag_vs_prior_only = logSumExp(prag_vs_prior_only))%>%
+  gather(model,logP,-noise)
+
+log_like_model_2_free <- log_like_model_2%>%
+  filter(noise == "parameter_free")
+
+```
+
+```{r}
+ggplot(log_like_model_2_free, aes(x = model, y = logP, col = model))+
   geom_segment( aes(x=model, xend=model, y=-1150, yend=logP), col = "black", size = 1)+
@@
   theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
-  facet_grid(~parameter)+
-  ylim(-1750,-1150)+
+  #facet_grid(~parameter)+
+  #ylim(-1750,-1150)+
   scale_color_ptol(breaks=c("pragmatics","pragmatics_global","prior_only","flat_prior"),
@@
 ```{r}
-ggsave("../graphs/like.png", width = 6, height = 2.5, scale = 1.5)
+ggsave("../graphs/like_talk_free.png", width = 4, height = 2.5, scale = 1.5)
 ```
@@
 #### summaries
-
 item_params_summary <- item_params %>%
@@
 # MAP based inverse predictions for ME data
+
+```{r}
+model <- readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")
+
+item_params<- model %>%
+  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
+  filter(parameter == "parameter", type == "items")%>%
+  separate(value, into = c("int", "slope"),sep = ", ")%>%
+  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]")))%>%
+  gather(parameter, value, int, slope)
+
+global_params <- model %>%
+  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
+  filter(parameter == "parameter", type == "parameters")%>%
+    separate(value, into = c("int", "slope"),sep = ", ")%>%
+    mutate(int = as.numeric(str_remove_all(int, "[(c]")),
+         slope = as.numeric(str_remove(slope, "[)]")))%>%
+    gather(parameter, value, int, slope)
+
+#### summaries
+
+item_params_summary <- item_params %>%
+  group_by(item, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+global_params_summary <- global_params %>%
+  group_by(token, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+```
 
@@
   data_var = "dataFromR"
-)
+) %>%
+saveRDS("../saves/prag_model.rds")
+
+comb_model_pred <- readRDS("../saves/prag_model.rds")
 
@@
 data_comb <- read_csv("../data/combination.csv") %>%
-  filter(condition != "train")%>%
-  mutate(alignment = condition,
-         item = familiarObject)%>%
   left_join(aoa_ratings)%>%
   ungroup()%>%
-  mutate(item = fct_reorder(factor(familiarObject), mean_aoa), 
+  mutate(item = fct_reorder(factor(item), mean_aoa), 
          source = "Data")
@@
   #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
-  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
+  geom_smooth(method = "glm", se = F, alpha = .5, span = 2)+
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
   #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
-  geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
+  #geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
   geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = alignment, lty = source), size = 1)+
@@
 
-p_data_model
-```
-
-```{r}
-ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 3, scale = 1.5)
+p1 <- data_comb%>%
+  group_by(source, alignment, item ,subage)%>%
+  multi_boot_standard(col = "correct")
+
+ggplot(p1, aes(x = subage+0.5, y = mean))+
+  #geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, col = source))+
+  facet_grid(alignment ~item)+
+  #geom_line(aes(group=alignment,col = source))+
+  #geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = source),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .2, span = 2)+
+  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source), size = 1)+
+  #geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = source), size = 1, alpha = 1)+
+  #geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = source), alpha = .5) +
+  theme_few()+
+  labs(x ="Age", y = "Mutual Exclusivity effect")+
+  scale_color_manual(name = "",
+                     values = c("#117733", "#117733", "#CC6677"))+
+  scale_fill_manual(values = c("#CC6677"))+
+  guides(fill = F)+
+  theme(legend.position = "bottom")
+
+```
+
+```{r}
+ggsave("../graphs/data_model_talk_00.pdf", width = 12, height = 3.5, scale = 1.2)
 ```
@@
   theme_few() + 
-  scale_colour_viridis_d(name ="Item")
-```
-
-```{r}
-#ggsave("../graphs/combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
+  scale_colour_viridis_d(name ="Familiar object")
+```
+
+```{r}
+ggsave("../graphs/talk_combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
 ```
@@
   mutate(item = fct_reorder(factor(item), mean_aoa),
-         source = "Model")
+         age = age + min(me_data$age_num),
+         source = "noisy Model")
 
@@
 
+### Correlate model predictions and data
+
+```{r}
+binnned_data <- data_comb%>%
+  group_by(subage, alignment, item)%>%
+  summarize(k = sum(correct), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         data_mean = (a-1)/(a+b-2),
+         data_ci_lower  = qbeta(.025, a, b),
+         data_ci_upper = qbeta(.975, a, b),
+         subage = factor(subage))%>%
+  select(-a,-b,-n,-k)
+
+binned_noise_model <- prag_model_noise_predictions %>%
+  mutate(subage = cut(age, 
+                      breaks = c(-0.1,1,2,3),
+                      labels = c(2,3,4)))%>%
+  group_by(subage, alignment, item)%>%
+  summarise(model_mean = estimate_mode(mean),
+            model_ci_lower = hdi_lower(mean),
+            model_ci_upper = hdi_upper(mean))
+
+cor_plot <- left_join(
+  binnned_data,
+  binned_noise_model)
+
+ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
+  geom_point(size = 2,  stroke = 1)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(~subage)+
+  theme_few() + 
+  scale_colour_viridis_d(name ="Familiar object")
+```
+
+```{r}
+ggsave("../graphs/talk_noise_combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
+```
+
 ## Pragmatics model global semantic knnowledge

### 2019-11-26 stats/kids_basic_me.Rmd
make age discrete in month

@@
   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-          age_month = lubridate::time_length(difftime(test_date,dob), "month"),
-         age_month = round(age_month),
+         age_num_month = lubridate::time_length(difftime(test_date,dob), "month"),
+         age_num_month = round(age_num_month),
+         age_month = age_num_month - min(age_num_month),
          check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%

### 2019-11-26 stats/kids_combination.Rmd
make age discrete in month

--- 2019-09-17 stats/kids_combination.Rmd
@@
   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
-
-d%>%
-  filter(check_age == F)%>%
-  select(subid, subage,test_date,dob,age_num,check_age)
+         age_num_month = lubridate::time_length(difftime(test_date,dob), "month"),
+         age_num_month = round(age_num_month),
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
+    mutate(age = age_num - min(age_num),
+           age_month = age_num_month - min(age_num_month))%>%
+  filter(condition != "train")%>%
+  mutate(alignment = condition,
+         item = familiarObject)%>%
+  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiarObject, -rt)
 
 write_csv(d, "../data/combination.csv")
+write_json(d, "../data/combination.json")
 

### 2019-11-26 stats/kids_novelty.Rmd
make age discrete in month

--- 2019-11-18 stats/kids_novelty.Rmd
@@
 library(here)
-library(brmstools)
+#library(brmstools)
 library(ggpubr)
@@
   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+         age_num_month = lubridate::time_length(difftime(test_date,dob), "month"),
+         age_num_month = round(age_num_month),
+         age_month = age_num_month - min(age_num_month),
          check_age = ifelse(substr(age_num,1,1) == subage, T, F),

### 2019-11-26 stats/kids_combination.Rmd
update age by month

--- 2019-11-18 stats/kids_combination.Rmd
@@
   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+         age_num_month = lubridate::time_length(difftime(test_date,dob), "month"),
+         age_num_month = round(age_num_month)/12,
          check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
-    mutate(age = age_num - min(age_num))%>%
+    mutate(age = age_num - min(age_num),
+           age_month = age_num_month - min(age_num_month))%>%
   filter(condition != "train")%>%
@@
   select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiarObject, -rt)
-
- d%>%
-  filter(check_age == F)%>%
-  select(subid, subage,test_date,dob,age_num,check_age)
 

### 2019-11-26 stats/kids_basic_me.Rmd

--- 2019-11-26 stats/kids_basic_me.Rmd
@@
   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-          age_month = lubridate::time_length(difftime(test_date,dob), "month"),
-         age_month = round(age_month),
+         age_num_month = lubridate::time_length(difftime(test_date,dob), "month"),
+         age_num_month = round(age_num_month)/12,
+         age_month = age_num_month - min(age_num_month),
          check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%

### 2019-11-26 stats/kids_familiar_words.Rmd
update fam picture plot

@@
 d_select <- d %>%
-  mutate(select = if_else(d$Word %in% select, 1.5,-1),
+  mutate(select = if_else(d$Word %in% spin_select, 1.5,-1),
          image = paste("../experiments/kids/images/",Word,".png", sep=""))
@@
 ```
+
+```{r}
+ggsave("../graphs/talk_items_selection.pdf", width = 12, height = 8, scale = 1.5)
+```

### 2019-11-26 stats/kids_novelty.Rmd

@@
          age_num_month = lubridate::time_length(difftime(test_date,dob), "month"),
-         age_num_month = round(age_num_month),
+         age_num_month = round(age_num_month)/12,
          age_month = age_num_month - min(age_num_month),

### 2019-11-26 stats/model_sample_processing.Rmd

---
title: "Model Samples Processing"
author: "M. Bohn"
date: "18 11 2019"
output: html_document
---

# Read in raw filed

```{r}

model <- bind_rows(
  read_csv("../saves/model/samples340.csv")%>%mutate(chain = 1),
  read_csv("../saves/model/samples561.csv")%>%mutate(chain = 2)
)

```

# Model predictions
```{r}
model_pred <- model %>%
  filter(a == "modelPrediction")%>%
  select(-a)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         id = f,
         item = e,
         age = g, 
         pred = h)

saveRDS(model_pred, "../saves/model_pred.rds")
model_pred <- readRDS("../saves/model_pred.rds")
```

# Model Parameters

```{r}
item_params <-  model %>%
  filter(b == "items")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(item = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

global_params <- model %>%
  filter(b == "parameters")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(token = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

global_sigma<- model %>%
  filter(b == "sigma")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(token = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)
```

### 2020-01-20 stats/model.Rmd
push model after test run

@@
 
-model_pred <- read_csv("../saves/model/samples78.csv") %>%
+model <- read_csv("../webppl/output/samples-reFactor-noRandomEffects_mcmc-2_burn1_lag1_chain1.csv")
+
+model_pred <- model %>%
   filter(a == "modelPrediction")%>%
-  select(-a)%>%
   rename(model = b, 
@@
          alignment = d,
-         id = f,
          item = e,
-         age = g, 
-         pred = h)
+         age = f, 
+         pred = g)
 

### 2020-01-21 stats/model.Rmd
update model output processing

--- 2019-11-26 stats/model.Rmd
@@
 
-model_pred <- read_csv("../saves/model/samples78.csv") %>%
-  filter(a == "modelPrediction")%>%
-  select(-a)%>%
-  rename(model = b, 
-         parameter = c,
-         alignment = d,
-         id = f,
-         item = e,
-         age = g, 
-         pred = h)
-
-saveRDS(model_pred, "../saves/model_pred.rds")
 model_pred <- readRDS("../saves/model_pred.rds")
 
-model_params <- bind_rows(
-  readRDS("../saves/model_params_chain1.rds")%>%mutate(chain = 1),
-  readRDS("../saves/model_params_chain2.rds")%>%mutate(chain = 2),
-  readRDS("../saves/model_params_chain3.rds")%>%mutate(chain = 3),
-  readRDS("../saves/model_params_chain4.rds")%>%mutate(chain = 4),
-  readRDS("../saves/model_params_chain5.rds")%>%mutate(chain = 5)
-
-)
-
-item_params <-  model_params %>%
-  filter(b == "items")%>%
-  select(-a,-b, -g,-h, -f)%>%
-    rename(item = c,
-         int = d,
-         slope = e)%>%
-  mutate(slope = as.numeric(slope),
-         int = as.numeric(int))%>%
-  gather(parameter, value, int, slope)
-
-global_params <- model_params %>%
-  filter(b == "parameters")%>%
-  select(-a,-b, -g,-h, -f)%>%
-    rename(token = c,
-         int = d,
-         slope = e)%>%
-  mutate(slope = as.numeric(slope),
-         int = as.numeric(int))%>%
-  gather(parameter, value, int, slope)
-
-global_sigma<- model_params %>%
-  filter(b == "sigma")%>%
-  select(-a,-b, -g,-h, -f)%>%
-    rename(token = c,
-         int = d,
-         slope = e)%>%
-  mutate(slope = as.numeric(slope),
-         int = as.numeric(int))%>%
-  gather(parameter, value, int, slope)
+item_params <- readRDS("../saves/item_params.rds")
+
+global_params <- readRDS("../saves/global_params.rds")
+
+global_sigma <- readRDS("../saves/global_sigma.rds")
 
@@
 
-model_pred %>%
-  filter(item == "pawn")%>%
-  arrange(age)
 ```

### 2020-01-21 stats/model_sample_processing.Rmd
update model output processing

@@
 
-# Read in raw filed
+```{r}
+library(tidyverse)
+library(rwebppl)
+library(brms)
+library(coda)
+library(ggthemes)
+library(readxl)
+library(ggpubr)
+library(stringr)
+library(matrixStats)
+library(data.table)
+library(bigmemory)
+library(langcog)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+```
+
+# Read in raw file
 
@@
 model <- bind_rows(
-  read_csv("../saves/model/samples340.csv")%>%mutate(chain = 1),
-  read_csv("../saves/model/samples561.csv")%>%mutate(chain = 2)
+  read_csv("../webppl/output/model/samples-reFactor-noRandomEffects_mcmc-50000_burn25000_lag5_chain1.csv")%>%mutate(chain = 1),
+  read_csv("../saves/model/samples-reFactor-noRandomEffects_mcmc-50000_burn25000_lag5_chain2.csv")%>%mutate(chain = 2)
 )
@@
 # Model predictions
+
 ```{r}
@@
   filter(a == "modelPrediction")%>%
-  select(-a)%>%
+  select(-a, -h)%>%
   rename(model = b, 
@@
          alignment = d,
-         id = f,
          item = e,
-         age = g, 
-         pred = h)
+         age = f, 
+         pred = g)
 
 saveRDS(model_pred, "../saves/model_pred.rds")
-model_pred <- readRDS("../saves/model_pred.rds")
+
 ```
@@
   filter(b == "items")%>%
-  select(-a,-b, -g,-h, -f)%>%
+  select(-a,-b, -e, -f, -h)%>%
     rename(item = c,
-         int = d,
-         slope = e)%>%
-  mutate(slope = as.numeric(slope),
-         int = as.numeric(int))%>%
-  gather(parameter, value, int, slope)
+         parameter = d,
+         value = g)
+
+saveRDS(item_params, "../saves/item_params.rds")
 
@@
   filter(b == "parameters")%>%
-  select(-a,-b, -g,-h, -f)%>%
-    rename(token = c,
-         int = d,
-         slope = e)%>%
-  mutate(slope = as.numeric(slope),
-         int = as.numeric(int))%>%
-  gather(parameter, value, int, slope)
+  select(-a,-b, -e,-f, -h)%>%
+    rename(parameter = c,
+         type = d,
+         value = g)
+
+saveRDS(global_params, "../saves/global_params.rds")
 
@@
   filter(b == "sigma")%>%
-  select(-a,-b, -g,-h, -f)%>%
-    rename(token = c,
-         int = d,
-         slope = e)%>%
-  mutate(slope = as.numeric(slope),
-         int = as.numeric(int))%>%
-  gather(parameter, value, int, slope)
+  select(-a,-b, -e,-f,-h)%>%
+    rename(parameter = c,
+         type = d,
+         value = g)
+
+saveRDS(global_sigma, "../saves/global_sigma.rds")
 ```

### 2020-01-22 stats/model.Rmd
add model with RE

@@
 global_params_summary <- global_params %>%
-  group_by(token, parameter)%>%
+  group_by (parameter,type)%>%
   summarise(mode = estimate_mode(value),
@@
   xlab("Parameter")+
-  facet_grid(parameter~token, scales = 'free')+
+  facet_grid(type~parameter, scales = 'free')+
   theme_few()
@@
 plot_global_params
+
+plot_global_params %>%
+  group_by(parameter, type)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
 ```
@@
 
-model_pred_prag_free<- bind_rows(
-  readRDS("../saves/model_pred_pragmatic_free_chain1.rds")%>%mutate(chain = 1),
-  readRDS("../saves/model_pred_pragmatic_free_chain2.rds")%>%mutate(chain = 2),
-  readRDS("../saves/model_pred_pragmatic_free_chain3.rds")%>%mutate(chain = 3),
-  readRDS("../saves/model_pred_pragmatic_free_chain4.rds")%>%mutate(chain = 4),
-  readRDS("../saves/model_pred_pragmatic_free_chain5.rds")%>%mutate(chain = 5)
-)
-
-plot_model_pred_prag_free <- model_pred%>%
-  mutate(model = paste(model, parameter, sep = "_"))%>%
+plot_model_pred <- model_pred%>%
   group_by(model, alignment, item, age)%>%
@@
 
-saveRDS(plot_model_pred_prag_free, "../saves/plot_model_pred_prag_free.rds")
-plot_model_pred_prag_free <- readRDS("../saves/plot_model_pred_prag_free.rds")
-
 ggplot() +
@@
   geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = plot_model_pred_prag_free, aes(x=age+2,y = mean, col = model), size = 1)+
-  geom_ribbon(data = plot_model_pred_prag_free, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
+  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
   xlim(2,5)+
-  guides(alpha = F, fill = F, col = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-
-x <- sample(1:48000, 500)
-
-plot_model_prag_noise_line <- model_pred_prag_free%>%
-  filter(iteration %in% x)
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol()+
+  scale_fill_ptol()
+
+length(unique(model_pred$iteration))
+
+x <- sample(1:10000, 500)
+
+plot_model_prag__line <- model_pred%>%
+  filter(model == "pragmatic", iteration %in% x)
 
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(data = plot_model_prag_noise_line, aes(x=age+2,y = pred, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .05)+
-  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_prag__line, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .05)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 2)+
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
 
-cor_prag_free <- model_pred_prag_free%>%
-  mutate(model = paste(model, parameter, sep = "_"))%>%
-  mutate(age = as.numeric(age) + min(me_data$age_num),
+cor_prag <- model_pred%>%
+  filter(model == "pragmatic")%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
          age = cut(age, 
@@
 
-saveRDS(cor_prag_free, "../saves/cor_prag_free.rds")
-cor_prag_free <- readRDS( "../saves/cor_prag_free.rds")
-
-cor_prag_noise <- model_pred_prag_noise%>%
-  mutate(model = paste(model, parameter, sep = "_"))%>%
-  mutate(age = as.numeric(age) + min(me_data$age_num),
+cor_global <- model_pred%>%
+  filter(model == "global")%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
          age = cut(age, 
@@
 
-saveRDS(cor_prag_noise, "../saves/cor_prag_noise.rds")
-cor_prag_noise <- readRDS( "../saves/cor_prag_noise.rds")
-
-cor_global_free <- model_pred_global_free%>%
-  mutate(model = paste(model, parameter, sep = "_"))%>%
-  mutate(age = as.numeric(age) + min(me_data$age_num),
+cor_flat <- model_pred%>%
+  filter(model == "flat")%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
          age = cut(age, 
@@
 
-cor_global_noise <- model_global_noise%>%
-  mutate(model = paste(model, parameter, sep = "_"))%>%
-  mutate(age = as.numeric(age) + min(me_data$age_num),
+cor_prior <- model_pred%>%
+  filter(model == "prior")%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
          age = cut(age, 
@@
 cor_model_pred <- bind_rows(
-  cor_prag_free,
-  cor_prag_noise
- # cor_global_free,
-#  cor_global_noise
+  cor_prag,
+  cor_global,
+  cor_flat,
+  cor_prior
 )
@@
     bind_rows(
-      #binnned_data%>%mutate(model = "globalPrag_free"),
-      #binnned_data%>%mutate(model = "globalPrag_noise"),
-      binnned_data%>%mutate(model = "pragmatic_free"),
-      binnned_data%>%mutate(model = "pragmatic_noise")
+      binnned_data%>%mutate(model = "pragmatic"),
+      binnned_data%>%mutate(model = "global"),
+      binnned_data%>%mutate(model = "flat"),
+      binnned_data%>%mutate(model = "prior")
       )
@@
 
-saveRDS(plot_cor_model_pred, "../saves/model_cor.rds")
-plot_cor_model_pred <- readRDS( "../saves/model_cor.rds")
-
-ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = item)) +
+# saveRDS(plot_cor_model_pred, "../saves/model_cor.rds")
+# plot_cor_model_pred <- readRDS( "../saves/model_cor.rds")
+
+ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
-  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
-  geom_point(size = 1.5, stroke = 1)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
+  geom_point(size = 1.5, stroke = 1, pch = 5)+
   coord_fixed()+
@@
   theme_few() + 
-  scale_colour_viridis_d(name ="Item")
+  scale_colour_ptol(name ="Alignment")
 ```

### 2020-01-22 stats/model_sample_processing.Rmd
add model with RE

@@
 library(bigmemory)
-library(langcog)
 

### 2020-01-22 stats/model.Rmd
update model processing

@@
 plot_global_params
-
-plot_global_params %>%
-  group_by(parameter, type)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
 ```
@@
   xlab("Sigma")+
-  facet_grid(~parameter, scales = 'free')+
+  facet_grid(type~parameter, scales = 'free')+
   theme_few()

### 2020-01-22 stats/model_sample_processing.Rmd
update model processing

@@
 model <- bind_rows(
-  read_csv("../webppl/output/model/samples-reFactor-noRandomEffects_mcmc-50000_burn25000_lag5_chain1.csv")%>%mutate(chain = 1),
-  read_csv("../saves/model/samples-reFactor-noRandomEffects_mcmc-50000_burn25000_lag5_chain2.csv")%>%mutate(chain = 2)
+  read_csv("../webppl/output/samples-reFactor-RE_mcmc-10_burn0_lag0_chain1.csv")%>%mutate(chain = 1)
 )
@@
 
-global_sigma<- model %>%
-  filter(b == "sigma")%>%
+item_sigma<- model %>%
+  filter(b == "sigma",
+         c == "global_sem_sigmas")%>%
   select(-a,-b, -e,-f,-h)%>%
@@
 
-saveRDS(global_sigma, "../saves/global_sigma.rds")
+saveRDS(item_sigma, "../saves/item_sigma.rds")
+
+subject_sigma<- model %>%
+  filter(b == "sigma", 
+         c != "global_sem_sigmas")%>%
+  select(-a,-b, -e,-f,-h, -d)%>%
+    rename(parameter = c,
+         value = g)
+
+saveRDS(subject_sigma, "../saves/subject_sigma.rds")
 ```

### 2020-01-24 stats/model_sample_processing.Rmd
add mode run with random effects

@@
 model <- bind_rows(
-  read_csv("../webppl/output/samples-reFactor-RE_mcmc-10_burn0_lag0_chain1.csv")%>%mutate(chain = 1)
+  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain1.csv")%>%mutate(chain = 1),
+  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain2.csv")%>%mutate(chain = 2)
 )
@@
 
-saveRDS(model_pred, "../saves/model_pred.rds")
+saveRDS(model_pred, "../saves/model_pred_re.rds")
 
@@
 
-saveRDS(item_params, "../saves/item_params.rds")
+saveRDS(item_params, "../saves/item_params_re.rds")
 
@@
 
-saveRDS(global_params, "../saves/global_params.rds")
+saveRDS(global_params, "../saves/global_params_re.rds")
 
@@
 
-saveRDS(item_sigma, "../saves/item_sigma.rds")
+saveRDS(item_sigma, "../saves/item_sigma_re.rds")
 
@@
 
-saveRDS(subject_sigma, "../saves/subject_sigma.rds")
+saveRDS(subject_sigma, "../saves/subject_sigma_re.rds")
 ```

### 2020-01-24 stats/model.Rmd
prep model for long run

@@
 
-global_sigma <- readRDS("../saves/global_sigma.rds")
+item_sigma <- readRDS("../saves/item_sigma.rds")
+
+subject_sigma <- readRDS("../saves/subject_sigma_re.rds")
+
+item_params <- bind_rows(
+  readRDS("../saves/item_params.rds")%>%mutate(run = "no re"),
+  readRDS("../saves/item_params_re.rds")%>%mutate(run = "re")
+)
+
+global_params <- bind_rows(
+  readRDS("../saves/global_params.rds")%>%mutate(run = "no re"),
+  readRDS("../saves/global_params_re.rds")%>%mutate(run = "re")
+)
+
+item_sigma <- bind_rows(
+  readRDS("../saves/item_sigmas.rds")%>%mutate(run = "no re"),
+  readRDS("../saves/item_sigma_re.rds")%>%mutate(run = "re")
+)
+
+model_pred <- bind_rows(
+    readRDS("../saves/model_pred.rds")%>%mutate(run = "no re")%>%filter(model == "pragmatic"),
+    readRDS("../saves/model_pred_re.rds")%>%mutate(run = "re")%>%filter(model == "pragmatic")
+)
 
@@
 item_params_summary <- item_params %>%
-  group_by(item, parameter)%>%
+  group_by(run, item, parameter)%>%
   summarise(mode = estimate_mode(value),
@@
 global_params_summary <- global_params %>%
-  group_by (parameter,type)%>%
+  group_by (run,parameter,type)%>%
   summarise(mode = estimate_mode(value),
@@
 
+subject_sigma_summary <- subject_sigma %>%
+  group_by (parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
 ```
@@
   xlab("Parameter")+
-  facet_grid(parameter~item, scales = 'free')+
+  facet_grid(run ~parameter + item, scales = 'free')+
   theme_few()
@@
   xlab("Parameter")+
-  facet_grid(type~parameter, scales = 'free')+
+  facet_grid(run~type + parameter, scales = 'free')+
   theme_few()
@@
 ```{r}
-plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(chain)))+
+plot_item_sigma <- ggplot(item_sigma, aes(x = value, fill = factor(chain)))+
   geom_density(alpha = 0.3)+
   xlab("Sigma")+
-  facet_grid(type~parameter, scales = 'free')+
+  facet_grid(run ~type + parameter, scales = 'free')+
   theme_few()
 
-plot_global_sigma
-```
-
-```{r}
-plotg_subj_sigma <- ggplot(subj_sigma, aes(x = sigma, fill = factor(Chain)))+
+plot_item_sigma
+```
+
+```{r}
+plotg_subj_sigma <- ggplot(subject_sigma, aes(x = value, fill = factor(chain)))+
   geom_density(alpha = 0.3)+
@@
 plot_model_pred <- model_pred%>%
-  group_by(model, alignment, item, age)%>%
+  filter(model == "pragmatic")%>%
+  group_by(run, model, alignment, item, age)%>%
   summarise(mean = estimate_mode(pred),
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
-  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = run), size = 1)+
+  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = run), alpha = .4) +
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
 cor_prag <- model_pred%>%
-  filter(model == "pragmatic")%>%
+  filter(model == "pragmatic",
+         run == "no re")%>%
   mutate(age = as.numeric(age) + min(data_comb$age_num),
@@
                       labels = c(2,3,4)))%>%
-  group_by(model, alignment, item, age)%>%
+  group_by(run, alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
+
+cor_prag_re <- model_pred%>%
+  filter(model == "pragmatic",
+         run == "re")%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
+         age = cut(age, 
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(run, alignment, item, age)%>%
   summarise(model_mean = estimate_mode(pred),
@@
   cor_prag,
-  cor_global,
-  cor_flat,
-  cor_prior
+  cor_prag_re,
+  #cor_global,
+  #cor_flat,
+  #cor_prior
 )
@@
     bind_rows(
-      binnned_data%>%mutate(model = "pragmatic"),
-      binnned_data%>%mutate(model = "global"),
-      binnned_data%>%mutate(model = "flat"),
-      binnned_data%>%mutate(model = "prior")
+      binnned_data%>%mutate(run = "no re"),
+      binnned_data%>%mutate(run = "re"),
+      # binnned_data%>%mutate(model = "flat"),
+      # binnned_data%>%mutate(model = "prior")
       )
@@
   ylab("Data")+
-  facet_grid(model~age)+
+  facet_grid(run~age)+
   theme_few() + 

### 2020-01-24 stats/model_sample_processing.Rmd
prep model for long run

--- 2020-01-22 stats/model_sample_processing.Rmd
@@
 model <- bind_rows(
-  read_csv("../webppl/output/samples-reFactor-RE_mcmc-10_burn0_lag0_chain1.csv")%>%mutate(chain = 1)
+  read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn25000_lag5_chain1.csv")%>%mutate(chain = 1),
+  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain2.csv")%>%mutate(chain = 2),
+  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain3.csv")%>%mutate(chain = 3),
+  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain4.csv")%>%mutate(chain = 4),
+  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain4.csv")%>%mutate(chain = 5),
+  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain4.csv")%>%mutate(chain = 6)
 )

### 2020-02-02 stats/model.Rmd
update model processing code

@@
 
-# Ignore below for now
-
-## Model comparison
-
-```{r}
-log_like <- bind_rows(
-  readRDS("../saves/log_like_chain1.rds")%>%mutate(chain = 1),
-  readRDS("../saves/log_like_chain2.rds")%>%mutate(chain = 2),
-  readRDS("../saves/log_like_chain3.rds")%>%mutate(chain = 3),
-  readRDS("../saves/log_like_chain4.rds")%>%mutate(chain = 4),
-  readRDS("../saves/log_like_chain5.rds")%>%mutate(chain = 5)
-)
-
-log_like_model<- log_like %>%
-  group_by(model,parameter)%>%
-  summarize(logP = logSumExp(log_like))%>%
-  spread(parameter, logP)
-
-log_like_chain<- log_like %>%
-  group_by(chain, model,parameter)%>%
-  summarize(logP = logSumExp(log_like))%>%
-  spread(parameter, logP)
-
-log_like_chain %>%
-  group_by(model)%>%
-  mutate(noise = round(noise,2),
-         parameter_free = round(parameter_free,2))%>%
-  summarise(range_param_free = paste(range(parameter_free)[1],range(parameter_free)[2], sep = " / "),
-            range_noise = paste(range(noise)[1],range(noise)[2], sep = " / "))
-
-log_like_2 <-  readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")%>%
-  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
-  filter(parameter == "log_like")%>%
-  separate(value, into = c("na", "log_like"),sep = ",")%>%
-  select(-na, -alignment)%>%
-  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))
-
-log_like_model_2 <- log_like_2%>%
-  group_by(model,noise)%>%
-  summarize(logP = logSumExp(log_like))
-
-model_comp <- log_like_2%>%
-  spread(model,log_like)%>%
-  mutate(prag_vs_prag_global = pragmatics - pragmatics_global,
-         prag_vs_flat_prior = pragmatics - flat_prior,
-         prag_vs_prior_only = pragmatics - prior_only)%>%
-  group_by(noise)%>%
-  summarize(prag_vs_prag_global = logSumExp(prag_vs_prag_global),
-            prag_vs_flat_prior = logSumExp(prag_vs_flat_prior),
-            prag_vs_prior_only = logSumExp(prag_vs_prior_only))%>%
-  gather(model,logP,-noise)
-
-log_like_model_2_free <- log_like_model_2%>%
-  filter(noise == "parameter_free")
-
-```
-
 ```{r}
@@
 
+x <- readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")
+
+xx <- x %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
+  mutate(model = "prior_only_noise")%>%
+  group_by(model,age,item, alignment) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))%>%
+  left_join(aoa_ratings)%>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa),
+         source = "Model")
+
 #### summaries
@@
 
-### Pragmatic free model
-
-```{r}
-
-plot_model_pred <- model_pred%>%
-  filter(model == "pragmatic")%>%
-  group_by(run, model, alignment, item, age)%>%
+### Pragmatic model
+
+```{r}
+
+model_pred_prag <- readRDS("../saves/model_pred_prag.rds")
+
+plot_model_pred_prag <- model_pred_prag%>%
+  group_by(alignment, item, age)%>%
   summarise(mean = estimate_mode(pred),
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = run), size = 1)+
-  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = run), alpha = .4) +
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_pred_prag, aes(x=age+2,y = mean, col = alignment), size = 1)+
+  geom_ribbon(data = plot_model_pred_prag, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
 
-length(unique(model_pred$iteration))
-
-x <- sample(1:10000, 500)
-
-plot_model_prag__line <- model_pred%>%
-  filter(model == "pragmatic", iteration %in% x)
+x <- sample(1:length(unique(model_pred_prag$iteration)), 100)
+
+plot_model_prag_line <- model_pred_prag%>%
+  filter(iteration %in% x)
 
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(data = plot_model_prag__line, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .05)+
+  geom_line(data = plot_model_prag_line, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .05)+
   geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 2)+
@@
   scale_colour_ptol(name = NULL)
+
 ```
@@
 
-### Pragmatic noise model
-
-```{r}
-
-model_pred_prag_noise<- bind_rows(
-  readRDS("../saves/model_pred_pragmatic_noise_chain1.rds")%>%mutate(chain = 1),
-  readRDS("../saves/model_pred_pragmatic_noise_chain2.rds")%>%mutate(chain = 2),
-  readRDS("../saves/model_pred_pragmatic_noise_chain3.rds")%>%mutate(chain = 3),
-  readRDS("../saves/model_pred_pragmatic_noise_chain4.rds")%>%mutate(chain = 4),
-  readRDS("../saves/model_pred_pragmatic_noise_chain5.rds")%>%mutate(chain = 5)
-)
-
-plot_model_pred_prag_noise <- model_pred_prag_noise%>%
-  mutate(model = paste(model, parameter, sep = "_"))%>%
-  group_by(model, alignment, item, age)%>%
+### Global pragmatic model
+
+```{r}
+
+model_pred_global<- readRDS("../saves/model_pred_global.rds")
+
+plot_model_pred_global <- model_pred_global%>%
+  group_by(alignment, item, age)%>%
   summarise(mean = estimate_mode(pred),
@@
 
-saveRDS(plot_model_pred_prag_noise, "../saves/plot_model_pred_prag_noise.rds")
-plot_model_pred_prag_noise <- readRDS("../saves/plot_model_pred_prag_noise.rds")
-
-plot_model_pred_prag_noise_chain <- model_pred_prag_noise%>%
-  mutate(model = paste(model, parameter, sep = "_"))%>%
-  group_by(model, alignment, item,chain, age)%>%
-  summarise(mean = estimate_mode(pred),
-            ci_lower = hdi_lower(pred),
-            ci_upper = hdi_upper(pred))
-
-saveRDS(plot_model_pred_prag_noise_chain, "../saves/plot_model_pred_prag_noise_chain.rds")
-plot_model_pred_prag_noise_chain <- readRDS("../saves/plot_model_pred_prag_noise_chain.rds")
-
 ggplot() +
@@
   geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_ribbon(data = plot_model_pred_prag_noise, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .3) +
-  geom_line(data = plot_model_pred_prag_noise, aes(x=age+2,y = mean, col = model), size = 1, alpha = .5)+
+  geom_line(data = plot_model_pred_global, aes(x=age+2,y = mean, col = alignment), size = 1)+
+  geom_ribbon(data = plot_model_pred_global, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
   guides(alpha = F, fill = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-
-x <- sample(1:48000, 500)
-
-plot_model_prag_noise_line <- model_pred_prag_noise%>%
-  filter(iteration %in% x)
-
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .4, span = 2)+
-  geom_line(data = plot_model_prag_noise_line, aes(x=age+2,y = pred, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .075)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(alignment~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F)+ 
-  scale_colour_ptol(name = NULL)
-```
-
-```{r}
-ggsave("../graphs/model_pred_noise_ribbon.pdf", width = 10, height = 4, scale = 1.2)
-```
-
-### Global pragmatic free model
-
-```{r}
-
-model_pred_global_free<- bind_rows(
-  readRDS("../saves/model_pred_globalPrag_free_chain1.rds")%>%mutate(chain = 1),
-  readRDS("../saves/model_pred_globalPrag_free_chain2.rds")%>%mutate(chain = 2)
-)
-
-plot_model_pred_global_free <- model_pred_global_free%>%
-  mutate(model = paste(model, parameter, sep = "_"))%>%
-  group_by(model, alignment, item, age)%>%
-  summarise(mean = estimate_mode(pred),
-            ci_lower = hdi_lower(pred),
-            ci_upper = hdi_upper(pred))
-
-saveRDS(plot_model_pred_global_free, "../saves/plot_model_pred_global_free.rds")
-plot_model_pred_global_free <- readRDS("../saves/plot_model_pred_global_free.rds")
-
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = plot_model_pred_global_free, aes(x=age+2,y = mean, col = model), size = 1)+
-  geom_ribbon(data = plot_model_pred_global_free, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(model + alignment~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-```
-
-### Global pragmatic noise model
-
-```{r}
-
-model_pred_global_noise<- bind_rows(
-  readRDS("../saves/model_pred_globalPrag_noise_chain1.rds")%>%mutate(chain = 1),
-  readRDS("../saves/model_pred_globalPrag_noise_chain2.rds")%>%mutate(chain = 2)
-)
-
-plot_model_pred_global_noise <- model_pred_global_noise%>%
-  mutate(model = paste(model, parameter, sep = "_"))%>%
-  group_by(model, alignment, item, age)%>%
-  summarise(mean = estimate_mode(pred),
-            ci_lower = hdi_lower(pred),
-            ci_upper = hdi_upper(pred))
-
-saveRDS(plot_model_pred_global_noise, "../saves/plot_model_pred_global_noise.rds")
-plot_model_pred_global_noise <- readRDS("../saves/plot_model_pred_global_noise.rds")
-
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = plot_model_pred_global_noise, aes(x=age+2,y = mean, col = model), size = 1)+
-  geom_ribbon(data = plot_model_pred_global_noise, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(model + alignment~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
+  scale_colour_ptol()+
+  scale_fill_ptol()
 ```
@@
 
-cor_prag <- model_pred%>%
-  filter(model == "pragmatic",
-         run == "no re")%>%
+cor_prag <- model_pred_prag%>%
   mutate(age = as.numeric(age) + min(data_comb$age_num),
@@
                       labels = c(2,3,4)))%>%
-  group_by(run, alignment, item, age)%>%
+  group_by(model,alignment, item, age)%>%
   summarise(model_mean = estimate_mode(pred),
@@
 
-cor_prag_re <- model_pred%>%
-  filter(model == "pragmatic",
-         run == "re")%>%
-  mutate(age = as.numeric(age) + min(data_comb$age_num),
-         age = cut(age, 
-                      breaks = c(2,3,4,5),
-                      labels = c(2,3,4)))%>%
-  group_by(run, alignment, item, age)%>%
-  summarise(model_mean = estimate_mode(pred),
-            model_ci_lower = hdi_lower(pred),
-            model_ci_upper = hdi_upper(pred))
-
-cor_global <- model_pred%>%
-  filter(model == "global")%>%
+# cor_prag_chain <- model_pred_prag%>%
+#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#          age = cut(age, 
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(chain, alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
+
+cor_global <- model_pred_global%>%
   mutate(age = as.numeric(age) + min(data_comb$age_num),
@@
 
-cor_flat <- model_pred%>%
-  filter(model == "flat")%>%
+model_pred_flat<- readRDS("../saves/model_pred_flat.rds")
+
+cor_flat <- model_pred_flat%>%
   mutate(age = as.numeric(age) + min(data_comb$age_num),
@@
 
-cor_prior <- model_pred%>%
-  filter(model == "prior")%>%
-  mutate(age = as.numeric(age) + min(data_comb$age_num),
-         age = cut(age, 
-                      breaks = c(2,3,4,5),
-                      labels = c(2,3,4)))%>%
-  group_by(model, alignment, item, age)%>%
-  summarise(model_mean = estimate_mode(pred),
-            model_ci_lower = hdi_lower(pred),
-            model_ci_upper = hdi_upper(pred))
+model_pred_prior<- readRDS("../saves/model_pred_prior.rds")
+
+# cor_prior <- model_pred_prior%>%
+#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#          age = cut(age, 
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(model, alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
 
 cor_model_pred <- bind_rows(
+  #cor_prag_chain,
   cor_prag,
-  cor_prag_re,
-  #cor_global,
-  #cor_flat,
-  #cor_prior
+  cor_global,
+  cor_flat,
+  cor_prior
 )
@@
     bind_rows(
-      binnned_data%>%mutate(run = "no re"),
-      binnned_data%>%mutate(run = "re"),
-      # binnned_data%>%mutate(model = "flat"),
-      # binnned_data%>%mutate(model = "prior")
+      # binnned_data%>%mutate(model = "pragmatic", chain = 1),
+      # binnned_data%>%mutate(model = "pragmatic", chain = 2),
+      # binnned_data%>%mutate(model = "pragmatic", chain = 3),
+      # binnned_data%>%mutate(model = "pragmatic", chain = 4),
+      # binnned_data%>%mutate(model = "pragmatic", chain = 5),
+      # binnned_data%>%mutate(model = "pragmatic", chain = 6)
+      binnned_data%>%mutate(model = "pragmatic"),
+      binnned_data%>%mutate(model = "global"),
+      binnned_data%>%mutate(model = "flat"),
+      binnned_data%>%mutate(model = "prior")
       )
@@
   ylab("Data")+
-  facet_grid(run~age)+
+  facet_grid(model~age)+
   theme_few() + 
-  scale_colour_ptol(name ="Alignment")
+  scale_colour_ptol(name ="Alignment")+
+  guides(col = F)
 ```
@@
 ggsave("../graphs/cor_model_data.pdf", width = 8, height = 3.5, scale = 1)
+```
+
+## Model comparison
+
+```{r}
+
+plot_model_pred_flat <- model_pred_flat%>%
+  group_by(alignment, item, age)%>%
+  summarise(mean = estimate_mode(pred),
+            ci_lower = hdi_lower(pred),
+            ci_upper = hdi_upper(pred))
+
+log_like_prag <- data_comb %>%
+  select(-age)%>%
+  mutate(age = age_month)%>%
+  left_join(plot_model_pred_prag)%>%
+  mutate(like = ifelse(correct == 1, mean, 1 - mean),
+         log_like_prag = log(like))%>%
+  select(age, alignment,item,log_like_prag)
+
+log_like_global <- data_comb %>%
+  select(-age)%>%
+  mutate(age = age_month)%>%
+  left_join(plot_model_pred_global)%>%
+  mutate(like = ifelse(correct == 1, mean, 1 - mean),
+         log_like_global = log(like))%>%
+  select(age, alignment,item,log_like_global)
+
+log_like_flat <- data_comb %>%
+  select(-age)%>%
+  mutate(age = age_month)%>%
+  left_join(plot_model_pred_flat)%>%
+  mutate(like = ifelse(correct == 1, mean, 1 - mean),
+         log_like_flat = log(like))%>%
+  select(age, alignment,item,log_like_flat)
+
+model_comp <- log_like_prag%>%
+  left_join(log_like_global)%>%
+  left_join(log_like_flat)%>%
+  mutate(prag_vs_global = log_like_prag - log_like_global,
+         prag_vs_flat = log_like_prag - log_like_flat)%>%
+  na.omit(prag_vs_global,prag_vs_flat)%>%
+  summarize(prag_vs_global = logSumExp(prag_vs_global),
+            prag_vs_flat = logSumExp(prag_vs_flat))
+
+log_like <- bind_rows(
+  readRDS("../saves/log_like_chain1.rds")%>%mutate(chain = 1),
+  readRDS("../saves/log_like_chain2.rds")%>%mutate(chain = 2),
+  readRDS("../saves/log_like_chain3.rds")%>%mutate(chain = 3),
+  readRDS("../saves/log_like_chain4.rds")%>%mutate(chain = 4),
+  readRDS("../saves/log_like_chain5.rds")%>%mutate(chain = 5)
+)
+
+log_like_model<- log_like %>%
+  group_by(model,parameter)%>%
+  summarize(logP = logSumExp(log_like))%>%
+  spread(parameter, logP)
+
+log_like_chain<- log_like %>%
+  group_by(chain, model,parameter)%>%
+  summarize(logP = logSumExp(log_like))%>%
+  spread(parameter, logP)
+
+log_like_chain %>%
+  group_by(model)%>%
+  mutate(noise = round(noise,2),
+         parameter_free = round(parameter_free,2))%>%
+  summarise(range_param_free = paste(range(parameter_free)[1],range(parameter_free)[2], sep = " / "),
+            range_noise = paste(range(noise)[1],range(noise)[2], sep = " / "))
+
+log_like_2 <-  readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")%>%
+  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
+  filter(parameter == "log_like")%>%
+  separate(value, into = c("na", "log_like"),sep = ",")%>%
+  select(-na, -alignment)%>%
+  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))
+
+log_like_model_2 <- log_like_2%>%
+  group_by(model,noise)%>%
+  summarize(logP = logSumExp(log_like))
+
+model_comp <- log_like_2%>%
+  spread(model,log_like)%>%
+  mutate(prag_vs_prag_global = pragmatics - pragmatics_global,
+         prag_vs_flat_prior = pragmatics - flat_prior,
+         prag_vs_prior_only = pragmatics - prior_only)%>%
+  group_by(noise)%>%
+  summarize(prag_vs_prag_global = logSumExp(prag_vs_prag_global),
+            prag_vs_flat_prior = logSumExp(prag_vs_flat_prior),
+            prag_vs_prior_only = logSumExp(prag_vs_prior_only))%>%
+  gather(model,logP,-noise)
+
+log_like_model_2_free <- log_like_model_2%>%
+  filter(noise == "parameter_free")
+
 ```

### 2020-02-02 stats/model_sample_processing.Rmd
add model runs

--- 2020-01-22 stats/model_sample_processing.Rmd
@@
 
+  m1 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain1.csv")%>%mutate(chain = 1)
+  m2 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain2.csv")%>%mutate(chain = 2)
+  m3 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain3.csv")%>%mutate(chain = 3)
+  m4 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain4.csv")%>%mutate(chain = 4)
+  m5 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain5.csv")%>%mutate(chain = 5)
+  m6 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain6.csv")%>%mutate(chain = 6)
+
 model <- bind_rows(
-  read_csv("../webppl/output/samples-reFactor-RE_mcmc-10_burn0_lag0_chain1.csv")%>%mutate(chain = 1)
+  m1,m2,m3,m4,m5,m6
+)
+
+saveRDS(m6, "../saves/m6.rds")
+
+model <- bind_rows(
+  readRDS("../saves/m1.rds"),
+  readRDS("../saves/m2.rds"),
+  readRDS("../saves/m3.rds"),
+  readRDS("../saves/m4.rds"),
+  readRDS("../saves/m5.rds"),
+  readRDS("../saves/m6.rds")
 )
@@
 ```{r}
-model_pred <- model %>%
-  filter(a == "modelPrediction")%>%
+model_pred_prag <- model %>%
+  filter(a == "modelPrediction",
+         b == "pragmatic")%>%
   select(-a, -h)%>%
@@
 
-saveRDS(model_pred, "../saves/model_pred.rds")
+saveRDS(model_pred_prag, "../saves/model_pred_prag.rds")
+
+model_pred <- model %>%
+  filter(a == "modelPrediction",
+         b == "global")%>%
+  select(-a, -h)%>%
+  rename(model = b, 
+         parameter = c,
+         alignment = d,
+         item = e,
+         age = f, 
+         pred = g)
+
+saveRDS(model_pred, "../saves/model_pred_global.rds")
+
+model_pred_flat <- model %>%
+  filter(a == "modelPrediction",
+         b == "flat")%>%
+  select(-a, -h)%>%
+  rename(model = b, 
+         parameter = c,
+         alignment = d,
+         item = e,
+         age = f, 
+         pred = g)
+
+saveRDS(model_pred_flat, "../saves/model_pred_flat.rds")
+
+model_pred_prior <- model %>%
+  filter(a == "modelPrediction",
+         b == "prior")%>%
+  select(-a, -h)%>%
+  rename(model = b, 
+         parameter = c,
+         alignment = d,
+         item = e,
+         age = f, 
+         pred = g)
+
+saveRDS(model_pred_prior, "../saves/model_pred_prior.rds")
 

### 2020-02-09 stats/model_sample_processing.Rmd
new model run no random effects

--- 2020-01-24 stats/model_sample_processing.Rmd
@@
 library(tidyverse)
-library(rwebppl)
-library(brms)
-library(coda)
-library(ggthemes)
+#library(rwebppl)
+#library(brms)
+#library(coda)
+#library(ggthemes)
 library(readxl)
-library(ggpubr)
+#library(ggpubr)
 library(stringr)
@@
 library(data.table)
-library(bigmemory)
+#library(bigmemory)
 
@@
 model <- bind_rows(
-  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain1.csv")%>%mutate(chain = 1),
-  read_csv("../webppl/output/samples-reFactor-RE_mcmc-50000_burn25000_lag5_chain2.csv")%>%mutate(chain = 2)
+ fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
+ fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
+ fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
 )
-
-```
-
-# Model predictions
-
-```{r}
-model_pred <- model %>%
-  filter(a == "modelPrediction")%>%
-  select(-a, -h)%>%
-  rename(model = b, 
-         parameter = c,
-         alignment = d,
-         item = e,
-         age = f, 
-         pred = g)
-
-saveRDS(model_pred, "../saves/model_pred_re.rds")
-
-```
 
@@
 
-```{r}
 item_params <-  model %>%
@@
 
-saveRDS(item_params, "../saves/item_params_re.rds")
+saveRDS(item_params, "../saves/item_params_2.rds")
 
@@
 
-saveRDS(global_params, "../saves/global_params_re.rds")
+saveRDS(global_params, "../saves/global_params_2.rds")
 
@@
 
-saveRDS(item_sigma, "../saves/item_sigma_re.rds")
+saveRDS(item_sigma, "../saves/item_sigma_2.rds")
 
-subject_sigma<- model %>%
-  filter(b == "sigma", 
-         c != "global_sem_sigmas")%>%
-  select(-a,-b, -e,-f,-h, -d)%>%
-    rename(parameter = c,
-         value = g)
+#subject_sigma<- model %>%
+#  filter(b == "sigma", 
+#         c != "global_sem_sigmas")%>%
+#  select(-a,-b, -e,-f,-h, -d)%>%
+#    rename(parameter = c,
+#         value = g)
 
-saveRDS(subject_sigma, "../saves/subject_sigma_re.rds")
+#saveRDS(subject_sigma, "../saves/subject_sigma.rds")
+
+# Model predictions
+
+model_pred_prag <- model %>%
+  filter(a == "modelPrediction",
+         b == "pragmatic")%>%
+  select(-a, -h)%>%
+  rename(model = b, 
+         parameter = c,
+         alignment = d,
+         item = e,
+         age = f, 
+         pred = g)
+
+saveRDS(model_pred_prag, "../saves/model_pred_prag_2.rds")
+
+model_pred <- model %>%
+  filter(a == "modelPrediction",
+         b == "global")%>%
+  select(-a, -h)%>%
+  rename(model = b, 
+         parameter = c,
+         alignment = d,
+         item = e,
+         age = f, 
+         pred = g)
+
+saveRDS(model_pred, "../saves/model_pred_global_2.rds")
+
+model_pred_flat <- model %>%
+  filter(a == "modelPrediction",
+         b == "flat")%>%
+  select(-a, -h)%>%
+  rename(model = b, 
+         parameter = c,
+         alignment = d,
+         item = e,
+         age = f, 
+         pred = g)
+
+saveRDS(model_pred_flat, "../saves/model_pred_flat_2.rds")
+
+model_pred_prior <- model %>%
+  filter(a == "modelPrediction",
+         b == "prior")%>%
+  select(-a, -h)%>%
+  rename(model = b, 
+         parameter = c,
+         alignment = d,
+         item = e,
+         age = f, 
+         pred = g)
+
+saveRDS(model_pred_prior, "../saves/model_pred_prior_2.rds")
+
 ```
+
+```{r}
+bind_rows(
+  readRDS("../saves/item_params_1.rds"),
+  readRDS("../saves/item_params_2.rds")
+)%>%
+  saveRDS(., "../saves/item_params.rds")
+
+bind_rows(
+  readRDS("../saves/global_params_1.rds"),
+  readRDS("../saves/global_params_2.rds")
+)%>%
+  saveRDS(., "../saves/global_params.rds")
+
+bind_rows(
+  readRDS("../saves/item_sigma_1.rds"),
+  readRDS("../saves/item_sigma_2.rds")
+)%>%
+  saveRDS(., "../saves/item_sigma.rds")
+
+bind_rows(
+  readRDS("../saves/model_pred_prag_1.rds"),
+  readRDS("../saves/model_pred_prag_2.rds")
+)%>%
+  saveRDS(., "../saves/model_pred_prag.rds")
+
+bind_rows(
+  readRDS("../saves/model_pred_global_1.rds"),
+  readRDS("../saves/model_pred_global_2.rds")
+)%>%
+  saveRDS(., "../saves/model_pred_global.rds")
+
+bind_rows(
+  readRDS("../saves/model_pred_flat_1.rds"),
+  readRDS("../saves/model_pred_flat_2.rds")
+)%>%
+  saveRDS(., "../saves/model_pred_flat.rds")
+
+bind_rows(
+  readRDS("../saves/model_pred_prior_1.rds"),
+  readRDS("../saves/model_pred_prior_2.rds")
+)%>%
+  saveRDS(., "../saves/model_pred_prior.rds")
+```

### 2020-02-10 stats/model.Rmd
update model file for comparison

@@
 
-model_pred <- readRDS("../saves/model_pred.rds")
-
 item_params <- readRDS("../saves/item_params.rds")
 
-global_params <- readRDS("../saves/global_params.rds")
+global_params <- readRDS("../saves/global_params.rds")%>%
+  filter(chain != 6)
 
@@
 
-subject_sigma <- readRDS("../saves/subject_sigma_re.rds")
+#subject_sigma <- readRDS("../saves/subject_sigma.rds")
 
@@
   xlab("Parameter")+
-  facet_grid(run ~parameter + item, scales = 'free')+
-  theme_few()
+  facet_grid(parameter ~ item, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
 
@@
   xlab("Parameter")+
-  facet_grid(run~type + parameter, scales = 'free')+
-  theme_few()
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
 
@@
   xlab("Sigma")+
-  facet_grid(run ~type + parameter, scales = 'free')+
+  facet_grid(type ~ parameter, scales = 'free')+
   theme_few()
@@
   xlab("Subject Sigma")+
+  facet_grid(~parameter)+
   theme_few()
@@
 
-# cor_prag_chain <- model_pred_prag%>%
-#   mutate(age = as.numeric(age) + min(data_comb$age_num),
-#          age = cut(age, 
-#                       breaks = c(2,3,4,5),
-#                       labels = c(2,3,4)))%>%
-#   group_by(chain, alignment, item, age)%>%
-#   summarise(model_mean = estimate_mode(pred),
-#             model_ci_lower = hdi_lower(pred),
-#             model_ci_upper = hdi_upper(pred))
+cor_prag_chain <- model_pred_prag%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
+         age = cut(age,
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(chain, alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
+
+model_pred_global<- readRDS("../saves/model_pred_global.rds")
 
@@
 
-# cor_prior <- model_pred_prior%>%
-#   mutate(age = as.numeric(age) + min(data_comb$age_num),
-#          age = cut(age, 
-#                       breaks = c(2,3,4,5),
-#                       labels = c(2,3,4)))%>%
-#   group_by(model, alignment, item, age)%>%
-#   summarise(model_mean = estimate_mode(pred),
-#             model_ci_lower = hdi_lower(pred),
-#             model_ci_upper = hdi_upper(pred))
+cor_prior <- model_pred_prior%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
+         age = cut(age,
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(model, alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
 
 cor_model_pred <- bind_rows(
-  #cor_prag_chain,
-  cor_prag,
-  cor_global,
-  cor_flat,
-  cor_prior
+  cor_prag_chain,
+  # cor_prag,
+  # cor_global,
+  # cor_flat,
+  # cor_prior
 )
@@
     bind_rows(
-      # binnned_data%>%mutate(model = "pragmatic", chain = 1),
-      # binnned_data%>%mutate(model = "pragmatic", chain = 2),
-      # binnned_data%>%mutate(model = "pragmatic", chain = 3),
-      # binnned_data%>%mutate(model = "pragmatic", chain = 4),
-      # binnned_data%>%mutate(model = "pragmatic", chain = 5),
-      # binnned_data%>%mutate(model = "pragmatic", chain = 6)
-      binnned_data%>%mutate(model = "pragmatic"),
-      binnned_data%>%mutate(model = "global"),
-      binnned_data%>%mutate(model = "flat"),
-      binnned_data%>%mutate(model = "prior")
+      binnned_data%>%mutate(model = "pragmatic", chain = 1),
+      binnned_data%>%mutate(model = "pragmatic", chain = 2),
+      binnned_data%>%mutate(model = "pragmatic", chain = 3),
+      binnned_data%>%mutate(model = "pragmatic", chain = 4),
+      binnned_data%>%mutate(model = "pragmatic", chain = 5),
+      binnned_data%>%mutate(model = "pragmatic", chain = 6)
+      # binnned_data%>%mutate(model = "pragmatic"),
+      # binnned_data%>%mutate(model = "global"),
+      # binnned_data%>%mutate(model = "flat"),
+      # binnned_data%>%mutate(model = "prior")
       )
@@
   ylab("Data")+
-  facet_grid(model~age)+
+  facet_grid(chain~age)+
   theme_few() + 
@@
 
-log_like_prag <- data_comb %>%
+data_comb %>%
   select(-age)%>%
-  mutate(age = age_month)%>%
-  left_join(plot_model_pred_prag)%>%
-  mutate(like = ifelse(correct == 1, mean, 1 - mean),
+  mutate(age = age_month,
+         item = as.character(item))%>%
+  left_join(model_pred_prag)%>%
+  mutate(like = ifelse(correct == 1, pred, 1 - pred),
          log_like_prag = log(like))%>%
-  select(age, alignment,item,log_like_prag)
+  select(chain, iteration, age, alignment,item,log_like_prag)%>%
+  saveRDS(.,"../saves/log_like_prag")
 
@@
   select(-age)%>%
-  mutate(age = age_month)%>%
-  left_join(plot_model_pred_global)%>%
-  mutate(like = ifelse(correct == 1, mean, 1 - mean),
+  mutate(age = age_month,
+         item = as.character(item))%>%
+  left_join(model_pred_global)%>%
+  mutate(like = ifelse(correct == 1, pred, 1 - pred),
          log_like_global = log(like))%>%
-  select(age, alignment,item,log_like_global)
+  select(chain,iteration, age, alignment,item,log_like_global)
 
@@
   select(-age)%>%
-  mutate(age = age_month)%>%
-  left_join(plot_model_pred_flat)%>%
-  mutate(like = ifelse(correct == 1, mean, 1 - mean),
+  mutate(age = age_month,
+         item = as.character(item))%>%
+  left_join(model_pred_flat)%>%
+  mutate(like = ifelse(correct == 1, pred, 1 - pred),
          log_like_flat = log(like))%>%
-  select(age, alignment,item,log_like_flat)
+  select(chain,iteration,age, alignment,item,log_like_flat)
 

### 2020-02-10 stats/model.Rmd
update model run

@@
 library(rwebppl)
-library(brms)
+#library(brms)
 library(coda)
@@
 library(bigmemory)
-library(langcog)
+#library(langcog)
 
@@
 ```{r}
-
-plot_model_pred_flat <- model_pred_flat%>%
-  group_by(alignment, item, age)%>%
-  summarise(mean = estimate_mode(pred),
-            ci_lower = hdi_lower(pred),
-            ci_upper = hdi_upper(pred))
-
-data_comb %>%
+log_like_prag <- data_comb %>%
   select(-age)%>%
@@
          item = as.character(item))%>%
-  left_join(model_pred_prag)%>%
+  left_join(readRDS("../saves/model_pred_prag.rds"))%>%
   mutate(like = ifelse(correct == 1, pred, 1 - pred),
-         log_like_prag = log(like))%>%
-  select(chain, iteration, age, alignment,item,log_like_prag)%>%
-  saveRDS(.,"../saves/log_like_prag")
+         log_like = log(like),
+         model = "prag",
+         id = 1:length(log_like))%>%
+  select(id, model,chain, iteration, age, alignment,item,log_like)
+
+gc()
 
@@
          item = as.character(item))%>%
-  left_join(model_pred_global)%>%
+  left_join(readRDS("../saves/model_pred_global.rds"))%>%
   mutate(like = ifelse(correct == 1, pred, 1 - pred),
-         log_like_global = log(like))%>%
-  select(chain,iteration, age, alignment,item,log_like_global)
+         log_like = log(like),
+         model = "global",
+         id = 1:length(log_like))%>%
+  select(id, model,chain,iteration, age, alignment,item,log_like)
+
+gc()
+
+saveRDS(log_like_global, "../saves/log_like_global.rds")
+
+comp <- bind_rows(
+  readRDS("../saves/log_like_prag.rds")%>%mutate(id = 1:length(log_like)), 
+  readRDS("../saves/log_like_global.rds")%>%mutate(id = 1:length(log_like))
+)%>%
+  spread(model, log_like)%>%
+  mutate(prag_vs_global = prag - global)
 
@@
          item = as.character(item))%>%
-  left_join(model_pred_flat)%>%
+  left_join(readRDS("../saves/model_pred_flat.rds"))%>%
   mutate(like = ifelse(correct == 1, pred, 1 - pred),
@@
 
-model_comp <- log_like_prag%>%
+gc()
+
+log_like_prior <- data_comb %>%
+  select(-age)%>%
+  mutate(age = age_month,
+         item = as.character(item))%>%
+  left_join(readRDS("../saves/model_pred_prior.rds"))%>%
+  mutate(like = ifelse(correct == 1, pred, 1 - pred),
+         log_like_prior = log(like))%>%
+  select(chain,iteration,age, alignment,item,log_like_prior)
+
+gc()
+
+prag_vs_global <- log_like_prag%>%
   left_join(log_like_global)%>%
-  left_join(log_like_flat)%>%
-  mutate(prag_vs_global = log_like_prag - log_like_global,
-         prag_vs_flat = log_like_prag - log_like_flat)%>%
-  na.omit(prag_vs_global,prag_vs_flat)%>%
-  summarize(prag_vs_global = logSumExp(prag_vs_global),
-            prag_vs_flat = logSumExp(prag_vs_flat))
+  mutate(prag_vs_global = log_like_prag - log_like_global)%>%
+  na.omit(prag_vs_global)%>%
+  summarize(prag_vs_global = logSumExp(prag_vs_global))%>%
+  saveRDS(.,"../saves/model_comp_prag_vs_global.rds")
 
@@
   filter(noise == "parameter_free")
+
+xx %>%
+  spread(model, log_like)
+
+comp <- comp%>%
+  na.omit(prag_vs_global)
+
+p_g_comp <- comp %>%
+  summarize(prag_vs_global = logSumExp(prag_vs_global))
+
+model_pred_prag
+
+bind_rows(
+
+  data_comb %>%
+    mutate(age = age_month,
+    item = as.character(item))%>%
+    left_join(model_pred_prag)%>%
+    mutate(like = ifelse(correct == 1, pred, 1 - pred),
+         log_like = log(like),
+         model = "prag",
+         id = 1:length(log_like))%>%
+  select(id, model,chain,iteration, age, alignment,item,log_like),
+
+  data_comb %>%
+    left_join(model_pred_prag)%>%
+    mutate(like = ifelse(correct == 1, pred, 1 - pred),
+         log_like = log(like),
+         model = "global")
+)%>%
+  spread(model, log_like)%>%
+  mutate(prag_vs_global = prag - global)
+
+%>%
+  summarise(logBF = logSumExp(prag_vs_global))
 

### 2020-02-10 stats/model_comparison.Rmd
update model run

---
title: "Model Comparison"
output: html_document
---

```{r}
library(tidyverse)
#library(rwebppl)
#library(brms)
#library(coda)
#library(ggthemes)
library(readxl)
#library(ggpubr)
library(matrixStats)
library(data.table)
#library(bigmemory)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```
# Data

```{r}
data_comb_pre <- read_csv("../data/combination.csv")

aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)

aoa_ratings <- aoa_ratings_all %>%
  filter(Word %in% data_comb_pre$item )%>%
  mutate(mean_aoa = as.numeric(Rating.Mean),
         item = Word)%>%
  select(item,mean_aoa)

data_comb <- data_comb_pre%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa), 
         source = "Data")
```

# Model comparison

# Pragmatic vs Global

```{r}
prag_global <- bind_rows(

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_prag.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "prag",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_global.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "global",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_global = prag - global) %>%
  na.omit(prag_vs_global) %>%
  summarise(prag_vs_global = logSumExp(prag_vs_global))
```

# Pragmatic vs Flat

```{r}

comp <- bind_rows(

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_prag.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "prag",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_flat.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "flat",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like)
)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_flat = prag - flat)

```

# Pragmatic vs prior

```{r}

comp <- bind_rows(

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_prag.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "prag",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_prior.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "prior",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_prior = prag - prior)

```

### 2020-02-10 stats/model_sample_processing.Rmd
update model run

@@
 ```
+```{r}
+
+```
+
+# remove chain 6
+
+```{r}
+readRDS("../saves/item_params.rds")%>%
+  filter(chain != 6)%>%
+  saveRDS(., "../saves/item_params.rds")
+
+readRDS("../saves/global_params.rds")%>%
+  filter(chain != 6)%>%
+  saveRDS(., "../saves/global_params.rds")
+
+readRDS("../saves/item_sigma.rds")%>%
+  filter(chain != 6)%>%
+  saveRDS(., "../saves/item_sigma.rds")
+
+readRDS("../saves/model_pred_prag.rds")%>%
+  filter(chain != 6)%>%
+  saveRDS(., "../saves/model_pred_prag.rds")
+
+readRDS("../saves/model_pred_global.rds")%>%
+  filter(chain != 6)%>%
+  saveRDS(., "../saves/model_pred_global.rds")
+
+readRDS("../saves/model_pred_flat.rds")%>%
+  filter(chain != 6)%>%
+  saveRDS(., "../saves/model_pred_flat.rds")
+
+readRDS("../saves/model_pred_prior.rds")%>%
+  filter(chain != 6)%>%
+  saveRDS(., "../saves/model_pred_prior.rds")
+
+```
 
@@
 model <- bind_rows(
- fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
- fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
- fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
+ fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 1),
+fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 2), 
+fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 3),
+ fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 4),
+ fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 5)
 )
@@
 
-saveRDS(item_params, "../saves/item_params_2.rds")
+saveRDS(item_params, "../saves/item_params.rds")
 

### 2020-02-11 stats/model.Rmd
model comparison example for MH to check

--- 2020-02-02 stats/model.Rmd
@@
 
-# Model utilities
+# Packages & data
 
@@
 
-```{r rsaUtils}
-rsaUtils <- '
-var all_objects = [
-{ shape: "novel_object"},  
-{ shape: "familiar_object"}
-]
-
-var labels = ["novel_word","familiar_word"]
-
-var lexicon1 = function(utterance, obj, sem_knowledge){
-  utterance.label == "novel_word" ? obj.shape == "novel_object" :
-  utterance.label == "familiar_word" ? flip(sem_knowledge) ? 
-    obj.shape == "familiar_object" :  
-  flip() ? obj.shape == "familiar_object" : obj.shape == "novel_object" : 
-  true
-}
-
-var lexicon2 = function(utterance, obj, sem_knowledge){
-  utterance.label == "novel_word" ? obj.shape == "familiar_object" :
-  utterance.label == "familiar_word" ? flip(sem_knowledge) ? 
-    obj.shape == "familiar_object" : 
-  flip() ? obj.shape == "familiar_object" : obj.shape == "novel_object" : 
-  true
-}
-
-var lexiconObjects = {
-"novel_word = novel_object": {
-novel_object: "novel_word", familiar_object: "familiar_word"
-},
-"novel_word = familiar_object": {
-novel_object: "familiar_word", familiar_object: "familiar_word"
-},
-}
-
-var lexiconObject = {
-"novel_word = novel_object": lexicon1,
-"novel_word = familiar_object" : lexicon2
-}
-
-var utterancePrior = function(){ return uniformDraw([ {label: "novel_word"}, {label: "familiar_word"}]) }
-
-var LexiconPrior = Categorical({vs: ["novel_word = novel_object","novel_word = familiar_object" ], ps: [1, 1]})
-
-var addNoise = function(dist, noiseParam){
-   Infer({model: function(){ 
-      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
-    }
-   })
-}
-
-var foreach = function(fn, lst) {
-    var foreach_ = function(i) {
-        if (i < lst.length) {
-            fn(lst[i]);
-            foreach_(i + 1);
-        }
-    };
-    foreach_(0);
-};
-
-var logistic = function(x) {1 / (1 + Math.exp(-x))}
-
-var levels = function(df, label){
-  return _.uniq(_.map(df, label));
-}
-'
-```
-
-```{r rsa model}
-rsaModel <- '
-var literalListener = cache(function(utterance, priorProbs, sem_knowledge){
-  Infer({method: "enumerate", model: function(){
-    var lexiconName = sample(LexiconPrior); 
-    var lexicon = lexiconObject[lexiconName];
-    var obj = sample( Categorical({vs: all_objects, ps: [.5,.5]}));
-    if ("label" in utterance) {
-      var truthValue = lexicon(utterance, obj, sem_knowledge);
-      condition(truthValue)
-    }
-    return obj.shape 
-  }})
-}, 10000)
-
-var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality, sem_knowledge){
-  Infer({method: "enumerate", model: function(){
-    var utterance = utterancePrior();
-    var L0 = literalListener(utterance, priorProbs, sem_knowledge);
-    factor(speakerOptimality * L0.score(obj.shape))
-    return utterance
-  }})
-}, 10000)
-
-var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality, sem_knowledge){
-  Infer({method: "enumerate", model: function(){
-    var lexiconName = sample(LexiconPrior);
-    var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
-    var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality, sem_knowledge);
-    observe(S1, utterance)
-    return obj.shape == "novel_object" ? 1 : 0
-  }})
-}, 10000)
-
-'
-```
-
-# Model
-
-## Combination Model
-
-```{r work in progress}
-sem_subj_str <- '
-
-var data = dataFromR.data
-var priorData = dataFromR.data
-
-var priorProbs = [.5,.5]
-
-var familiars = levels(data, "item")
-var subjects = levels(data, "subid")
-var priorSubjects = levels(priorData, "subid")
-
-var model  = function(){
-
-//////////////// Prior ////////////////////////
-
- var prior_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var prior_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-  var prior_subject_sigma = uniformDrift({a: 0, b:3, width: 0.2})
-
-  var priorSampleSub = function(age){
-    return gaussianDrift({ mu: age, sigma: prior_subject_sigma, width: 0.1 })
-  }
-
-  foreach(function(subid){
-      var priorSubjectData = _.filter(priorData, {subid: subid})
-
-      //display(subjects)
-
-      var subj_age = priorSubjectData[0].age
-
-      var subjectPrior = priorSampleSub(subj_age)
-
-    foreach(function(row){
-
-      var priorReg = logistic(prior_int + prior_slope * subjectPrior)
-
-      var prior = [priorReg, 1-priorReg]
-
-      var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: prior}));
-      return obj.shape == "novel_object" ? 1 : 0
-       }})
-
-     observe(modelPredictions, row.correct)
-
-    }, priorSubjectData)
-
-  }, priorSubjects)
-
-  query.add(["parameter","parameters", "prior"], [prior_int, prior_slope])
-  query.add(["parameter","sigma", "prior"], ["NA", prior_subject_sigma])
-
-//////////////// Semantic knowledge and speaker optimality ////////////////////////
-
-  var speakerOptimalityParameters = {
-    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 4, width: 0.5})
-  }
-
-  var globalLineParameters = {
-    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 2, width: 0.5})
-  }
-
-  var itemVariability = {
-    intercept: uniformDrift({a: 0, b: 2, width: 0.2}),
-    slope: uniformDrift({a: 0, b: 1, width: 0.2})
-  }
-
-  // conceptually it might not make sense to have two sigmas, but maybe it does
-  // intercept sigma probably will be smaller than slope sigma
-  // var item_int_sigma = uniformDrift({a: 0, b: 3, width: 0.2})
-
-  var sampleItemParameters = function(itemName) { 
-    return [itemName, {
-        intercept: gaussianDrift({
-          mu: globalLineParameters.intercept, 
-          sigma: itemVariability.intercept, 
-          width: 0.5
-        }),
-        slope: gaussianDrift({
-          mu: globalLineParameters.slope, 
-          sigma: itemVariability.slope, 
-          width: 0.5
-        })
-      }]
-  }
-
-  // {papaya: {int, slope}, bread: {int, slope}, ... }
-  var all_item_parameters = _.fromPairs(map(sampleItemParameters, familiars))
-
-  // want something that favors smaller values
-  var subject_sigma = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var sampleLinguisticCompetence = function(age){
-    return gaussianDrift({ mu: age, sigma: subject_sigma, width: 0.1 })
-  }
-
-  foreach(function(subid){
-      var subjectData = _.filter(data, {subid: subid})
-      var subj_age = subjectData[0].age
-      var subj_linguistic_competence = sampleLinguisticCompetence(subj_age)
-
-     // display("age = " + subj_age + " ... intercept = " + subj_linguistic_competence)
-
-      // question: should we use age here instead of the random intercept? or a different random intercept?
-
-  var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_age
-
-      // each row is a different item
-      foreach(function(row){
-
-        var itemLineParameters = all_item_parameters[row.item]
-
-        var sem_knowledge = logistic(itemLineParameters.intercept + 
-            itemLineParameters.slope * subj_linguistic_competence)
-
-        var modelPredictions = pragmaticListener({label: "novel_word"}, 
-              priorProbs, speakerOptimality, sem_knowledge)
-        // display(modelPredictions.score(row.correct))
-
-        observe(modelPredictions, row.correct)
-
-        // if you want to save predictions, make sure to record subid because these predictions are for this particular subid
-        // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
-
-      }, subjectData)
-
-    // comment out to save memory
-  //  query.add(["parameter","subj_intercept", subid], [subjectData[0].age, subj_linguistic_competence])
-
-  }, subjects)
-
-//////////////// Model predictions and combination ////////////////////////
-
-var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-var all_log_likes = map(function(row) {
-
-  var priorReg = logistic(prior_int + prior_slope * row.age)
-
-  var cond = row.condition
-
-  var prior = function(cnd){
-    var cndPrior = cnd == "congruent" ? [priorReg, 1-priorReg] : [1-priorReg, priorReg] ;
-    return cndPrior
-  }
-
-  var priorComb = prior(cond)
-
-  var itemLineParameters = all_item_parameters[row.item]
-
-  var sem_knowledge = logistic(itemLineParameters.intercept + 
-                               itemLineParameters.slope * row.age)
-
-  var global_sem_knowledge = logistic(globalLineParameters.intercept + 
-                               globalLineParameters.slope * row.age)
-
-  var speakerOptimality = speakerOptimalityParameters.intercept  + 
-      speakerOptimalityParameters.slope * row.age
-
-  var pragModelPredictions = pragmaticListener({label: "novel_word"}, 
-                                               priorComb, speakerOptimality, 
-                                               sem_knowledge)
-
-  var noisyPragModelPredictions = addNoise(pragModelPredictions, noise)
-
-  var globalPragModelPredictions = pragmaticListener({label: "novel_word"}, 
-                                               priorComb, speakerOptimality, 
-                                               global_sem_knowledge)
-
-   var noisyGlobalPragModelPredictions = addNoise(globalPragModelPredictions, noise)
-
-   var flatModelPredictions = pragmaticListener({label: "novel_word"}, 
-                                               [.5, .5], speakerOptimality, 
-                                               sem_knowledge)
-
-   var noisyFlatModelPredictions = addNoise(flatModelPredictions, noise)
-
-  var priorOnlyModelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: priorComb}));
-      return obj.shape == "novel_object" ? 1 : 0
-       }})
-
-  var noisyPriorOnlyModelPredictions = addNoise(priorOnlyModelPredictions, noise)
-
-  query.add(["modelPrediction","pragmatic","free", row.alignment, row.item, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])
-
-//  query.add(["modelPrediction","globalPrag","free", row.alignment, row.item, row.subid], [row.age, Math.exp(globalPragModelPredictions.score(1))])
-
-  return {
-    prag: pragModelPredictions.score(row.correct),
-    noisePrag: noisyPragModelPredictions.score(row.correct),
-
-    globalPrag: globalPragModelPredictions.score(row.correct),
-    noiseGlobalPrag: noisyGlobalPragModelPredictions.score(row.correct),
-
-    flat: flatModelPredictions.score(row.correct),
-    noiseFlat: noisyFlatModelPredictions.score(row.correct),
-
-    priorOnly: priorOnlyModelPredictions.score(row.correct),
-    noisePriorOnly: noisyPriorOnlyModelPredictions.score(row.correct)
-  }
-
-}, dataFromR.comb_data)
-
-var log_likelihood_prag = sum(_.map(all_log_likes, "prag"))
-var log_likelihood_prag_noise = sum(_.map(all_log_likes, "noisePrag"))
-
-var log_likelihood_prag_global = sum(_.map(all_log_likes, "globalPrag"))
-var log_likelihood_prag_global_noise = sum(_.map(all_log_likes, "noiseGlobalPrag"))
-
-var log_likelihood_flat = sum(_.map(all_log_likes, "flat"))
-var log_likelihood_flat_noise = sum(_.map(all_log_likes, "noiseFlat"))
-
-var log_likelihood_prior_only = sum(_.map(all_log_likes, "priorOnly"))
-var log_likelihood_prior_only_noise = sum(_.map(all_log_likes, "noisePriorOnly"))
-
-query.add(["log_like", "pragmatics", "parameter_free"], ["NA", log_likelihood_prag])
-query.add(["log_like", "pragmatics", "noise"], ["NA", log_likelihood_prag_noise])
-
-query.add(["log_like", "pragmatics_global", "parameter_free"], ["NA", log_likelihood_prag_global])
-query.add(["log_like", "pragmatics_global", "noise"], ["NA", log_likelihood_prag_global_noise])
-
-query.add(["log_like", "flat_prior", "parameter_free"], ["NA", log_likelihood_flat])
-query.add(["log_like", "flat_prior", "noise"], ["NA", log_likelihood_flat_noise])
-
-query.add(["log_like", "prior_only", "parameter_free"], ["NA", log_likelihood_prior_only])
-query.add(["log_like", "prior_only", "noise"], ["NA", log_likelihood_prior_only_noise])
-
-  foreach(function(item){
-    var itemLineParameters = all_item_parameters[item]
-    query.add(["parameter","items", item], [itemLineParameters.intercept, itemLineParameters.slope])
-  }, familiars)
-
-  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
-  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
-  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
-  query.add(["parameter","sigma", "global_subject_sigmas"], ["NA", subject_sigma])
-
-  return query 
-}
-
-var header = "iteration,a,b,c,d,e,f,g,h"
-
-var randomNumberForFile = Math.round(uniform(0, 1000))
-
-var callback = webpplSampleWriter.streamQueryCSV("../saves/model/samples"+randomNumberForFile+".csv", header);
-
-Infer({model,
-      samples: 10,
-      burn: 10,
-      verbose: T,
-      lag: 1,
-      verboseLag: 1000,
-      method: "incrementalMH",
-      onlyMAP: true,
-      callbacks: [callback]});
-'
-```
-
-## Model run
-
-```{r}
-sem_know_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
-  data = list(data = me_model_data, comb_data = data_comb, prior_data = prior_model_data),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 2,
-  cores = 2,
-  packages = c("webppl_packages/webppl-sample-writer")
-)
-```
-
-```{r}
-ggplot(log_like_model_2_free, aes(x = model, y = logP, col = model))+
-  geom_segment( aes(x=model, xend=model, y=-1150, yend=logP), col = "black", size = 1)+
-  geom_point(size = 7)+
-  theme_few()+ 
-  xlab("")+
-  ylab("Log-likelihood")+
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
-  #facet_grid(~parameter)+
-  #ylim(-1750,-1150)+
-  scale_color_ptol(breaks=c("pragmatics","pragmatics_global","prior_only","flat_prior"),
-                     labels=c("Pragmatic", "Pragmatic global","Prior only","Flat prior"))+
-    theme(axis.text.x=element_blank(), 
-        axis.ticks.x=element_blank())
-```
-
-```{r}
-ggsave("../graphs/like_talk_free.png", width = 4, height = 2.5, scale = 1.5)
-```
-
-## Summarizing parameters
-
-```{r}
-
-model_pred <- readRDS("../saves/model_pred.rds")
+# Model parameters
+
+```{r}
 
@@
 item_sigma <- readRDS("../saves/item_sigma.rds")
-
-subject_sigma <- readRDS("../saves/subject_sigma_re.rds")
-
-item_params <- bind_rows(
-  readRDS("../saves/item_params.rds")%>%mutate(run = "no re"),
-  readRDS("../saves/item_params_re.rds")%>%mutate(run = "re")
-)
-
-global_params <- bind_rows(
-  readRDS("../saves/global_params.rds")%>%mutate(run = "no re"),
-  readRDS("../saves/global_params_re.rds")%>%mutate(run = "re")
-)
-
-item_sigma <- bind_rows(
-  readRDS("../saves/item_sigmas.rds")%>%mutate(run = "no re"),
-  readRDS("../saves/item_sigma_re.rds")%>%mutate(run = "re")
-)
-
-model_pred <- bind_rows(
-    readRDS("../saves/model_pred.rds")%>%mutate(run = "no re")%>%filter(model == "pragmatic"),
-    readRDS("../saves/model_pred_re.rds")%>%mutate(run = "re")%>%filter(model == "pragmatic")
-)
-
-x <- readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")
-
-xx <- x %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
-  mutate(model = "prior_only_noise")%>%
-  group_by(model,age,item, alignment) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         source = "Model")
 
@@
 item_params_summary <- item_params %>%
-  group_by(run, item, parameter)%>%
+  group_by(item, parameter)%>%
   summarise(mode = estimate_mode(value),
@@
 global_params_summary <- global_params %>%
-  group_by (run,parameter,type)%>%
+  group_by (parameter,type)%>%
   summarise(mode = estimate_mode(value),
@@
 
-subject_sigma_summary <- subject_sigma %>%
-  group_by (parameter)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
 ```
@@
 
-```{r}
-plotg_subj_sigma <- ggplot(subject_sigma, aes(x = value, fill = factor(chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Subject Sigma")+
-  theme_few()
-
-plotg_subj_sigma
-```
-
-```{r}
-
-select_id <- me_model_data %>%
-  filter(age < 1.3,
-         age >1)%>%
-  group_by(age,subid)%>%
-  summarise(mean = mean(correct))%>%
-  mutate(id = subid)
-
-subject_params <- subject_params %>%
-  left_join(select_id)%>%
-  filter(mean != "NA")%>%
-  ungroup()
-
-ggplot(subject_params, aes(x = int, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  geom_vline(aes(xintercept = age), size = 1.5)+
-  #geom_vline(aes(xintercept = mean), size = 1.5, col = "red")+
-  facet_grid(id+ round(mean,2)~.)+
-  xlab("Subject Intercept")+
-  theme_few()
-
-#ggsave("../graphs/subj_intercept.pdf", width = 5, height = 8, scale = 1.5)
-
-```
-
 ## Plotting semantic knowledge
@@
 ```{r}
-aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
-
-aoa_ratings <- aoa_ratings_all %>%
-  filter(Word %in% item_params_summary$item )%>%
-  mutate(mean_aoa = as.numeric(Rating.Mean),
-         item = Word)%>%
-  select(item,mean_aoa)
-
 plot_sem_know <- item_params_summary%>%
@@
       age = unique(me_model_data$age),
-      item = unique(me_model_data$familiar)), .) %>%
-  mutate(sem_know = plogis(int + slope * age)) %>%
+      item = unique(me_model_data$item)), .) %>%
+  mutate(sem_know = plogis(intercept + slope * age)) %>%
   left_join(aoa_ratings) %>%
@@
 ```{r}
-
 model_pred_prag <- readRDS("../saves/model_pred_prag.rds")
@@
 
-x <- sample(1:length(unique(model_pred_prag$iteration)), 100)
+x <- sample(1:length(unique(model_pred_prag$iteration)), 200)
 
 plot_model_prag_line <- model_pred_prag%>%
-  filter(iteration %in% x)
+  filter(iteration %in% x)%>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
 
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(data = plot_model_prag_line, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .05)+
-  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_prag_line, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
   xlim(2,5)+
-  guides(alpha = F, fill = F)+ 
+  guides(alpha = F, fill = F, col = F)+ 
   scale_colour_ptol(name = NULL)
@@
 ```{r}
-ggsave("../graphs/pred_model_data.pdf", width = 10, height = 4, scale = 1)
-```
-
-### Global pragmatic model
-
-```{r}
-
-model_pred_global<- readRDS("../saves/model_pred_global.rds")
-
-plot_model_pred_global <- model_pred_global%>%
-  group_by(alignment, item, age)%>%
-  summarise(mean = estimate_mode(pred),
-            ci_lower = hdi_lower(pred),
-            ci_upper = hdi_upper(pred))
-
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = plot_model_pred_global, aes(x=age+2,y = mean, col = alignment), size = 1)+
-  geom_ribbon(data = plot_model_pred_global, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(alignment~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F)+ 
-  scale_colour_ptol()+
-  scale_fill_ptol()
+ggsave("../graphs/pred_model_data.pdf", width = 10, height = 3, scale = 1)
 ```
@@
 ```{r}
-binnned_data <- data_comb%>%
-  group_by(subage, alignment, item)%>%
-  summarize(k = sum(correct), n = n())%>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         data_mean = (a-1)/(a+b-2),
-         data_ci_lower  = qbeta(.025, a, b),
-         data_ci_upper = qbeta(.975, a, b),
-         age = factor(subage))%>%
-  select(-a,-b,-n,-k)
-
-cor_prag <- model_pred_prag%>%
-  mutate(age = as.numeric(age) + min(data_comb$age_num),
-         age = cut(age, 
-                      breaks = c(2,3,4,5),
-                      labels = c(2,3,4)))%>%
-  group_by(model,alignment, item, age)%>%
-  summarise(model_mean = estimate_mode(pred),
-            model_ci_lower = hdi_lower(pred),
-            model_ci_upper = hdi_upper(pred))
-
-# cor_prag_chain <- model_pred_prag%>%
+# binnned_data <- data_comb%>%
+#   group_by(subage, alignment, item)%>%
+#   summarize(k = sum(correct), n = n())%>%
+#   ungroup() %>%
+#   mutate(a = 1 + k,
+#          b = 1 + n - k,
+#          data_mean = (a-1)/(a+b-2),
+#          data_ci_lower  = qbeta(.025, a, b),
+#          data_ci_upper = qbeta(.975, a, b),
+#          age = factor(subage))%>%
+#   select(-a,-b,-n,-k)
+# 
+# 
+# cor_prag <- readRDS("../saves/model_pred_prag.rds")%>%
 #   mutate(age = as.numeric(age) + min(data_comb$age_num),
@@
 #                       labels = c(2,3,4)))%>%
-#   group_by(chain, alignment, item, age)%>%
+#   group_by(model,alignment, item, age)%>%
 #   summarise(model_mean = estimate_mode(pred),
@@
 #             model_ci_upper = hdi_upper(pred))
-
-cor_global <- model_pred_global%>%
-  mutate(age = as.numeric(age) + min(data_comb$age_num),
-         age = cut(age, 
-                      breaks = c(2,3,4,5),
-                      labels = c(2,3,4)))%>%
-  group_by(model, alignment, item, age)%>%
-  summarise(model_mean = estimate_mode(pred),
-            model_ci_lower = hdi_lower(pred),
-            model_ci_upper = hdi_upper(pred))
-
-model_pred_flat<- readRDS("../saves/model_pred_flat.rds")
-
-cor_flat <- model_pred_flat%>%
-  mutate(age = as.numeric(age) + min(data_comb$age_num),
-         age = cut(age, 
-                      breaks = c(2,3,4,5),
-                      labels = c(2,3,4)))%>%
-  group_by(model, alignment, item, age)%>%
-  summarise(model_mean = estimate_mode(pred),
-            model_ci_lower = hdi_lower(pred),
-            model_ci_upper = hdi_upper(pred))
-
-model_pred_prior<- readRDS("../saves/model_pred_prior.rds")
-
-# cor_prior <- model_pred_prior%>%
+# 
+# cor_global <- readRDS("../saves/model_pred_global.rds")%>%
 #   mutate(age = as.numeric(age) + min(data_comb$age_num),
@@
 #             model_ci_upper = hdi_upper(pred))
-
-cor_model_pred <- bind_rows(
-  #cor_prag_chain,
-  cor_prag,
-  cor_global,
-  cor_flat,
-  cor_prior
-)
-
-plot_cor_model_pred <- cor_model_pred %>%
-  left_join(
-    bind_rows(
-      # binnned_data%>%mutate(model = "pragmatic", chain = 1),
-      # binnned_data%>%mutate(model = "pragmatic", chain = 2),
-      # binnned_data%>%mutate(model = "pragmatic", chain = 3),
-      # binnned_data%>%mutate(model = "pragmatic", chain = 4),
-      # binnned_data%>%mutate(model = "pragmatic", chain = 5),
-      # binnned_data%>%mutate(model = "pragmatic", chain = 6)
-      binnned_data%>%mutate(model = "pragmatic"),
-      binnned_data%>%mutate(model = "global"),
-      binnned_data%>%mutate(model = "flat"),
-      binnned_data%>%mutate(model = "prior")
-      )
-  )
-
-# saveRDS(plot_cor_model_pred, "../saves/model_cor.rds")
-# plot_cor_model_pred <- readRDS( "../saves/model_cor.rds")
+# 
+# cor_flat <- readRDS("../saves/model_pred_flat.rds")%>%
+#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#          age = cut(age, 
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(model, alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
+# 
+# cor_prior <- readRDS("../saves/model_pred_prior.rds")%>%
+#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#          age = cut(age,
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(model, alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
+# 
+# cor_model_pred <- bind_rows(
+#    cor_prag,
+#    cor_global,
+#    cor_flat,
+#    cor_prior
+# )
+# 
+# 
+# plot_cor_model_pred <- cor_model_pred %>%
+#   left_join(
+#     bind_rows(
+#        binnned_data%>%mutate(model = "pragmatic"),
+#        binnned_data%>%mutate(model = "global"),
+#        binnned_data%>%mutate(model = "flat"),
+#        binnned_data%>%mutate(model = "prior")
+#       )
+#   )
+
+# saveRDS(plot_cor_model_pred, "../saves/corr_model_data.rds")
+
+ plot_cor_model_pred <- readRDS( "../saves/model_cor.rds")
 
@@
 ```{r}
-
-plot_model_pred_flat <- model_pred_flat%>%
-  group_by(alignment, item, age)%>%
-  summarise(mean = estimate_mode(pred),
-            ci_lower = hdi_lower(pred),
-            ci_upper = hdi_upper(pred))
-
-log_like_prag <- data_comb %>%
+d_model_comp <- data_comb%>%
   select(-age)%>%
-  mutate(age = age_month)%>%
-  left_join(plot_model_pred_prag)%>%
-  mutate(like = ifelse(correct == 1, mean, 1 - mean),
-         log_like_prag = log(like))%>%
-  select(age, alignment,item,log_like_prag)
-
-log_like_global <- data_comb %>%
+  mutate(age = round(age_month,2),
+         item = as.character(item))%>%
+  select(alignment, item, age, correct)
+
+test_prag <- readRDS("../saves/model_pred_prag.rds")%>%
+  filter(iteration == 1286 | iteration == 7185)%>%
+  mutate(age = round(age,2))
+
+saveRDS(test_prag,"../saves/test_prag.rds")
+
+test_global <- readRDS("../saves/model_pred_global.rds")%>%
+  filter(iteration == 1286 | iteration == 7185)%>%
+  mutate(age = round(age,2))
+
+saveRDS(test_global,"../saves/test_global.rds")
+
+test_flat <- readRDS("../saves/model_pred_flat.rds")%>%
+  filter(iteration == 1286 | iteration == 7185)%>%
+  mutate(age = round(age,2))
+
+saveRDS(test_flat,"../saves/test_flat.rds")
+
+d_model_comp <- data_comb%>%
   select(-age)%>%
-  mutate(age = age_month)%>%
-  left_join(plot_model_pred_global)%>%
-  mutate(like = ifelse(correct == 1, mean, 1 - mean),
-         log_like_global = log(like))%>%
-  select(age, alignment,item,log_like_global)
-
-log_like_flat <- data_comb %>%
-  select(-age)%>%
-  mutate(age = age_month)%>%
-  left_join(plot_model_pred_flat)%>%
-  mutate(like = ifelse(correct == 1, mean, 1 - mean),
-         log_like_flat = log(like))%>%
-  select(age, alignment,item,log_like_flat)
-
-model_comp <- log_like_prag%>%
-  left_join(log_like_global)%>%
-  left_join(log_like_flat)%>%
-  mutate(prag_vs_global = log_like_prag - log_like_global,
-         prag_vs_flat = log_like_prag - log_like_flat)%>%
-  na.omit(prag_vs_global,prag_vs_flat)%>%
-  summarize(prag_vs_global = logSumExp(prag_vs_global),
-            prag_vs_flat = logSumExp(prag_vs_flat))
-
-log_like <- bind_rows(
-  readRDS("../saves/log_like_chain1.rds")%>%mutate(chain = 1),
-  readRDS("../saves/log_like_chain2.rds")%>%mutate(chain = 2),
-  readRDS("../saves/log_like_chain3.rds")%>%mutate(chain = 3),
-  readRDS("../saves/log_like_chain4.rds")%>%mutate(chain = 4),
-  readRDS("../saves/log_like_chain5.rds")%>%mutate(chain = 5)
-)
-
-log_like_model<- log_like %>%
-  group_by(model,parameter)%>%
-  summarize(logP = logSumExp(log_like))%>%
-  spread(parameter, logP)
-
-log_like_chain<- log_like %>%
-  group_by(chain, model,parameter)%>%
-  summarize(logP = logSumExp(log_like))%>%
-  spread(parameter, logP)
-
-log_like_chain %>%
-  group_by(model)%>%
-  mutate(noise = round(noise,2),
-         parameter_free = round(parameter_free,2))%>%
-  summarise(range_param_free = paste(range(parameter_free)[1],range(parameter_free)[2], sep = " / "),
-            range_noise = paste(range(noise)[1],range(noise)[2], sep = " / "))
-
-log_like_2 <-  readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")%>%
-  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
-  filter(parameter == "log_like")%>%
-  separate(value, into = c("na", "log_like"),sep = ",")%>%
-  select(-na, -alignment)%>%
-  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))
-
-log_like_model_2 <- log_like_2%>%
-  group_by(model,noise)%>%
-  summarize(logP = logSumExp(log_like))
-
-model_comp <- log_like_2%>%
-  spread(model,log_like)%>%
-  mutate(prag_vs_prag_global = pragmatics - pragmatics_global,
-         prag_vs_flat_prior = pragmatics - flat_prior,
-         prag_vs_prior_only = pragmatics - prior_only)%>%
-  group_by(noise)%>%
-  summarize(prag_vs_prag_global = logSumExp(prag_vs_prag_global),
-            prag_vs_flat_prior = logSumExp(prag_vs_flat_prior),
-            prag_vs_prior_only = logSumExp(prag_vs_prior_only))%>%
-  gather(model,logP,-noise)
-
-log_like_model_2_free <- log_like_model_2%>%
-  filter(noise == "parameter_free")
+  mutate(age = round(age_month,2),
+         item = as.character(item))%>%
+  select(alignment, item, age, correct)
+
+xxg <- xxg %>%
+  mutate(age = round(age,2))
+
+sort(unique(d_model_comp$age))
+
+sort(unique(xx$age))
+
+y <- xx %>%
+  right_join(d_model_comp)
+
+tail(y)
+
+bind_rows(
+
+  xx %>%
+    right_join(d_model_comp)%>%
+    mutate(like = ifelse(correct == 1, pred, 1 - pred),
+           log_like = log(like),
+           model = "prag",
+           id = 1:length(log_like))%>%
+  select(id, model,chain,iteration, age, alignment,item,log_like),
+
+xxf %>%
+    right_join(d_model_comp)%>%
+    mutate(like = ifelse(correct == 1, pred, 1 - pred),
+           log_like = log(like),
+           model = "global",
+           id = 1:length(log_like))%>%
+  select(id, model,chain,iteration, age, alignment,item,log_like)
+
+)%>%
+  spread(model, log_like)%>%
+  mutate(prag_vs_global = prag - global) %>%
+  summarise(prag_vs_global = sum(prag_vs_global))
 
@@
 
-novel_bm <- readRDS("../saves/novelty_model.rds")
+novel_bm <- readRDS("../saves_old/novelty_model.rds")
 

### 2020-02-11 stats/model_comparison.Rmd
model comparison example for MH to check

@@
 library(tidyverse)
-#library(rwebppl)
-#library(brms)
-#library(coda)
-#library(ggthemes)
 library(readxl)
-#library(ggpubr)
 library(matrixStats)
 library(data.table)
-#library(bigmemory)
 
@@
          source = "Data")
+
+d_model_comp <- data_comb%>%
+  select(-age)%>%
+  mutate(age = round(age_month,2),
+         item = as.character(item))%>%
+  select(alignment, item, age, correct)
+
 ```
@@
 
-# Pragmatic vs Global
+## Dummy example for MH
 
 ```{r}
-prag_global <- bind_rows(
+# Model prediction files are very large - can't put them on github as is 
+# files below contain the two iterations for each model (1286 & 7185)
 
-  data_comb %>%
-    select(-age)%>%
-    mutate(age = age_month,
-           item = as.character(item))%>%
-    left_join(readRDS("../saves/model_pred_prag.rds"))%>%
-    mutate(like = ifelse(correct == 1, pred, 1 - pred),
-           log_like = log(like),
-           model = "prag",
-           id = 1:length(log_like))%>%
-  select(id, model,chain,iteration, age, alignment,item,log_like),
+# load model predicitons
+test_prag <- readRDS("../saves/test_prag.rds")
+test_global <- readRDS("../saves/test_global.rds")
+test_flat <- readRDS("../saves/test_flat.rds")
 
-  data_comb %>%
-    select(-age)%>%
-    mutate(age = age_month,
-           item = as.character(item))%>%
-    left_join(readRDS("../saves/model_pred_global.rds"))%>%
-    mutate(like = ifelse(correct == 1, pred, 1 - pred),
-           log_like = log(like),
-           model = "global",
-           id = 1:length(log_like))%>%
-  select(id, model,chain,iteration, age, alignment,item,log_like),
+# join predictions with the data
 
+bind_rows(
+
+  test_prag %>%
+    right_join(d_model_comp)%>%
+    mutate(id = 1:length(pred))%>%
+    select(id, model,chain,iteration, age, alignment,item,pred, correct),
+
+  test_global %>%
+    right_join(d_model_comp)%>%
+    mutate(id = 1:length(pred))%>%
+    select(id, model,chain,iteration, age, alignment,item,pred, correct),
+
+   test_flat %>%
+    right_join(d_model_comp)%>%
+    mutate(id = 1:length(pred))%>%
+    select(id, model,chain,iteration, age, alignment,item,pred, correct)
 )%>%
+  mutate(log_like = log(ifelse(correct == 1, pred, 1 - pred)))%>% # calculate log likelihood
+  select(-pred, - correct)%>%
   spread(model, log_like)%>%
-  mutate(prag_vs_global = prag - global) %>%
-  na.omit(prag_vs_global) %>%
-  summarise(prag_vs_global = logSumExp(prag_vs_global))
-```
-
-# Pragmatic vs Flat
-
-```{r}
-
-comp <- bind_rows(
-
-  data_comb %>%
-    select(-age)%>%
-    mutate(age = age_month,
-           item = as.character(item))%>%
-    left_join(readRDS("../saves/model_pred_prag.rds"))%>%
-    mutate(like = ifelse(correct == 1, pred, 1 - pred),
-           log_like = log(like),
-           model = "prag",
-           id = 1:length(log_like))%>%
-  select(id, model,chain,iteration, age, alignment,item,log_like),
-
-  data_comb %>%
-    select(-age)%>%
-    mutate(age = age_month,
-           item = as.character(item))%>%
-    left_join(readRDS("../saves/model_pred_flat.rds"))%>%
-    mutate(like = ifelse(correct == 1, pred, 1 - pred),
-           log_like = log(like),
-           model = "flat",
-           id = 1:length(log_like))%>%
-  select(id, model,chain,iteration, age, alignment,item,log_like)
-)%>%
-  spread(model, log_like)%>%
-  mutate(prag_vs_flat = prag - flat)
+  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
+         prag_vs_flat= pragmatic - flat,
+         global_vs_flat = global - flat) %>%
+  summarise(prag_vs_global = sum(prag_vs_global), # sum up likelihood difference to get log Bayes factor
+            prag_vs_flat = sum(prag_vs_flat),
+            global_vs_flat = sum(global_vs_flat))%>%
+  gather(model, logBF)
 
 ```
-
-# Pragmatic vs prior
-
-```{r}
-
-comp <- bind_rows(
-
-  data_comb %>%
-    select(-age)%>%
-    mutate(age = age_month,
-           item = as.character(item))%>%
-    left_join(readRDS("../saves/model_pred_prag.rds"))%>%
-    mutate(like = ifelse(correct == 1, pred, 1 - pred),
-           log_like = log(like),
-           model = "prag",
-           id = 1:length(log_like))%>%
-  select(id, model,chain,iteration, age, alignment,item,log_like),
-
-  data_comb %>%
-    select(-age)%>%
-    mutate(age = age_month,
-           item = as.character(item))%>%
-    left_join(readRDS("../saves/model_pred_prior.rds"))%>%
-    mutate(like = ifelse(correct == 1, pred, 1 - pred),
-           log_like = log(like),
-           model = "prior",
-           id = 1:length(log_like))%>%
-  select(id, model,chain,iteration, age, alignment,item,log_like),
-
-)%>%
-  spread(model, log_like)%>%
-  mutate(prag_vs_prior = prag - prior)
-
-```

### 2020-02-11 stats/model_comparison.Rmd
update model comparison example

@@
 test_prag <- readRDS("../saves/test_prag.rds")
+
 test_global <- readRDS("../saves/test_global.rds")
+
 test_flat <- readRDS("../saves/test_flat.rds")
 
-# join predictions with the data
-
 bind_rows(
-
-  test_prag %>%
+  test_prag, 
+  test_global, 
+  test_flat
+)%>%
+  spread(model, pred)%>%
   right_join(d_model_comp)%>%
-    mutate(id = 1:length(pred))%>%
-    select(id, model,chain,iteration, age, alignment,item,pred, correct),
-
-  test_global %>%
-    right_join(d_model_comp)%>%
-    mutate(id = 1:length(pred))%>%
-    select(id, model,chain,iteration, age, alignment,item,pred, correct),
-
-   test_flat %>%
-    right_join(d_model_comp)%>%
-    mutate(id = 1:length(pred))%>%
-    select(id, model,chain,iteration, age, alignment,item,pred, correct)
-)%>%
-  mutate(log_like = log(ifelse(correct == 1, pred, 1 - pred)))%>% # calculate log likelihood
-  select(-pred, - correct)%>%
-  spread(model, log_like)%>%
-  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
-         prag_vs_flat= pragmatic - flat,
-         global_vs_flat = global - flat) %>%
+  mutate(log_like_prag = log(ifelse(correct == 1, pragmatic, 1 - pragmatic)),
+         log_like_global = log(ifelse(correct == 1, global, 1 - global)),
+         log_like_flat = log(ifelse(correct == 1, flat, 1 - flat)))%>%
+  mutate(prag_vs_global = log_like_prag - log_like_global, # subtract likelihood for each predictions and model
+         prag_vs_flat= log_like_prag - log_like_flat,
+         global_vs_flat = log_like_global - log_like_flat) %>%
   summarise(prag_vs_global = sum(prag_vs_global), # sum up likelihood difference to get log Bayes factor

### 2020-02-11 stats/model_comparison.Rmd
fix model comparison chunk

--- 2020-02-11 stats/model_comparison.Rmd
@@
 
+d_model_comp.summarized <- d_model_comp %>% 
+  group_by(alignment, item, age) %>% 
+  summarize(n=n(), k = sum(correct))
+
 # join predictions with the data
@@
   test_prag %>%
-    right_join(d_model_comp)%>%
+    right_join(d_model_comp.summarized) %>%
     mutate(id = 1:length(pred))%>%
-    select(id, model,chain,iteration, age, alignment,item,pred, correct),
+    select(id, model,chain,iteration, age, alignment,item,pred, n, k),
 
   test_global %>%
-    right_join(d_model_comp)%>%
+    right_join(d_model_comp.summarized)%>%
     mutate(id = 1:length(pred))%>%
-    select(id, model,chain,iteration, age, alignment,item,pred, correct),
+    select(id, model,chain,iteration, age, alignment,item,pred, n, k),
 
    test_flat %>%
-    right_join(d_model_comp)%>%
+    right_join(d_model_comp.summarized)%>%
     mutate(id = 1:length(pred))%>%
-    select(id, model,chain,iteration, age, alignment,item,pred, correct)
-)%>%
-  mutate(log_like = log(ifelse(correct == 1, pred, 1 - pred)))%>% # calculate log likelihood
-  select(-pred, - correct)%>%
-  spread(model, log_like)%>%
+    select(id, model,chain,iteration, age, alignment,item,pred, n, k)
+) %>%
+  mutate(
+    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
+  ) %>%
+  group_by(chain, model, iteration) %>%
+  summarize(total_likelihood_sample = sum(log_like)) %>%
+  group_by(chain, model) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  spread(model, marginal_likelihood) %>%
   mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
@@
          global_vs_flat = global - flat) %>%
-  summarise(prag_vs_global = sum(prag_vs_global), # sum up likelihood difference to get log Bayes factor
-            prag_vs_flat = sum(prag_vs_flat),
-            global_vs_flat = sum(global_vs_flat))%>%
-  gather(model, logBF)
+  select(-pragmatic, -global, -flat) %>%
+  gather(model, logBF, -chain)
 

### 2020-02-11 stats/model_comparison.Rmd

--- 2020-02-11 stats/model_comparison.Rmd
@@
 
+d_model_comp.summarized <- d_model_comp %>% 
+  group_by(alignment, item, age) %>% 
+  summarize(n=n(), k = sum(correct))
+
+# join predictions with the data
+
 bind_rows(
-  test_prag, 
-  test_global, 
-  test_flat
-)%>%
-  spread(model, pred)%>%
-  right_join(d_model_comp)%>%
-  mutate(log_like_prag = log(ifelse(correct == 1, pragmatic, 1 - pragmatic)),
-         log_like_global = log(ifelse(correct == 1, global, 1 - global)),
-         log_like_flat = log(ifelse(correct == 1, flat, 1 - flat)))%>%
-  mutate(prag_vs_global = log_like_prag - log_like_global, # subtract likelihood for each predictions and model
-         prag_vs_flat= log_like_prag - log_like_flat,
-         global_vs_flat = log_like_global - log_like_flat) %>%
-  summarise(prag_vs_global = sum(prag_vs_global), # sum up likelihood difference to get log Bayes factor
-            prag_vs_flat = sum(prag_vs_flat),
-            global_vs_flat = sum(global_vs_flat))%>%
-  gather(model, logBF)
+
+  test_prag %>%
+    right_join(d_model_comp.summarized) %>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k),
+
+  test_global %>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k),
+
+   test_flat %>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k)
+) %>%
+  mutate(
+    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
+  ) %>%
+  group_by(chain, model, iteration) %>%
+  summarize(total_likelihood_sample = sum(log_like)) %>%
+  group_by(chain, model) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  spread(model, marginal_likelihood) %>%
+  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
+         prag_vs_flat= pragmatic - flat,
+         global_vs_flat = global - flat) %>%
+  select(-pragmatic, -global, -flat) %>%
+  gather(model, logBF, -chain)
 

### 2020-02-11 stats/model_comparison.Rmd
add model comparison and test run fully bayesian model

--- 2020-02-11 stats/model_comparison.Rmd
@@
 
-## Dummy example for MH
+```{r}
 
-```{r}
-# Model prediction files are very large - can't put them on github as is 
-# files below contain the two iterations for each model (1286 & 7185)
+d_model_comp.summarized <- d_model_comp %>% 
+  group_by(alignment, item, age) %>% 
+  summarize(n=n(), k = sum(correct))
 
-# load model predicitons
-test_prag <- readRDS("../saves/test_prag.rds")
+# join predictions with the data
 
-test_global <- readRDS("../saves/test_global.rds")
+model_comp <- bind_rows(
 
-test_flat <- readRDS("../saves/test_flat.rds")
+  readRDS("../saves/model_pred_prag.rds") %>%
+    right_join(d_model_comp.summarized) %>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k),
 
-bind_rows(
-  test_prag, 
-  test_global, 
-  test_flat
-)%>%
-  spread(model, pred)%>%
-  right_join(d_model_comp)%>%
-  mutate(log_like_prag = log(ifelse(correct == 1, pragmatic, 1 - pragmatic)),
-         log_like_global = log(ifelse(correct == 1, global, 1 - global)),
-         log_like_flat = log(ifelse(correct == 1, flat, 1 - flat)))%>%
-  mutate(prag_vs_global = log_like_prag - log_like_global, # subtract likelihood for each predictions and model
-         prag_vs_flat= log_like_prag - log_like_flat,
-         global_vs_flat = log_like_global - log_like_flat) %>%
-  summarise(prag_vs_global = sum(prag_vs_global), # sum up likelihood difference to get log Bayes factor
-            prag_vs_flat = sum(prag_vs_flat),
-            global_vs_flat = sum(global_vs_flat))%>%
-  gather(model, logBF)
+  readRDS("../saves/model_pred_global.rds") %>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k),
+
+   readRDS("../saves/model_pred_flat.rds") %>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k),
+
+  readRDS("../saves/model_pred_prior.rds") %>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k)
+) %>%
+  mutate(
+    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
+  ) %>%
+  group_by(chain, model, iteration) %>%
+  summarize(total_likelihood_sample = sum(log_like)) %>%
+  group_by(chain, model) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  spread(model, marginal_likelihood)%>%
+  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
+         prag_vs_flat= pragmatic - flat,
+         prag_vs_prior= pragmatic - prior,
+         global_vs_flat = global - flat,
+         global_vs_prior = global - prior,
+         flat_vs_prior = flat - prior) %>%
+  select(-pragmatic, -global, -flat, - prior) %>%
+  gather(model, logBF, -chain)
 

### 2020-02-12 stats/model_sample_processing.Rmd
update sample processing

@@
 model <- bind_rows(
- fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 1),
-fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 2), 
-fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 3),
- fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 4),
- fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 5)
+ fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain1.csv",header = T)%>%mutate(chain = 1),
+ fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
+ read("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
+  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
+  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
+  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
 )
@@
 
-saveRDS(item_params, "../saves/item_params.rds")
+saveRDS(item_params, "../saves/item_params_fb.rds")
 
@@
 
-saveRDS(global_params, "../saves/global_params_2.rds")
+saveRDS(global_params, "../saves/global_params_fb.rds")
 
@@
 
-saveRDS(item_sigma, "../saves/item_sigma_2.rds")
+saveRDS(item_sigma, "../saves/item_sigma_fb.rds")
 
@@
 
-saveRDS(model_pred_prag, "../saves/model_pred_prag_2.rds")
+saveRDS(model_pred_prag, "../saves/model_pred_prag_fb.rds")
 
-model_pred <- model %>%
-  filter(a == "modelPrediction",
-         b == "global")%>%
-  select(-a, -h)%>%
-  rename(model = b, 
-         parameter = c,
-         alignment = d,
-         item = e,
-         age = f, 
-         pred = g)
-
-saveRDS(model_pred, "../saves/model_pred_global_2.rds")
-
-model_pred_flat <- model %>%
-  filter(a == "modelPrediction",
-         b == "flat")%>%
-  select(-a, -h)%>%
-  rename(model = b, 
-         parameter = c,
-         alignment = d,
-         item = e,
-         age = f, 
-         pred = g)
-
-saveRDS(model_pred_flat, "../saves/model_pred_flat_2.rds")
-
-model_pred_prior <- model %>%
-  filter(a == "modelPrediction",
-         b == "prior")%>%
-  select(-a, -h)%>%
-  rename(model = b, 
-         parameter = c,
-         alignment = d,
-         item = e,
-         age = f, 
-         pred = g)
-
-saveRDS(model_pred_prior, "../saves/model_pred_prior_2.rds")
+# model_pred <- model %>%
+#   filter(a == "modelPrediction",
+#          b == "global")%>%
+#   select(-a, -h)%>%
+#   rename(model = b, 
+#          parameter = c,
+#          alignment = d,
+#          item = e,
+#          age = f, 
+#          pred = g)
+# 
+# saveRDS(model_pred, "../saves/model_pred_global_2.rds")
+# 
+# model_pred_flat <- model %>%
+#   filter(a == "modelPrediction",
+#          b == "flat")%>%
+#   select(-a, -h)%>%
+#   rename(model = b, 
+#          parameter = c,
+#          alignment = d,
+#          item = e,
+#          age = f, 
+#          pred = g)
+# 
+# saveRDS(model_pred_flat, "../saves/model_pred_flat_2.rds")
+# 
+# model_pred_prior <- model %>%
+#   filter(a == "modelPrediction",
+#          b == "prior")%>%
+#   select(-a, -h)%>%
+#   rename(model = b, 
+#          parameter = c,
+#          alignment = d,
+#          item = e,
+#          age = f, 
+#          pred = g)
+# 
+# saveRDS(model_pred_prior, "../saves/model_pred_prior_2.rds")
 

### 2020-02-12 stats/model.Rmd
test run mixture model

@@
 
-# Model parameters
+# Parameter free model
 
@@
 ## Plotting model predictions
-
-### Pragmatic model
 
@@
 
-## Model comparison
-
-```{r}
-d_model_comp <- data_comb%>%
-  select(-age)%>%
-  mutate(age = round(age_month,2),
-         item = as.character(item))%>%
-  select(alignment, item, age, correct)
-
-test_prag <- readRDS("../saves/model_pred_prag.rds")%>%
-  filter(iteration == 1286 | iteration == 7185)%>%
-  mutate(age = round(age,2))
-
-saveRDS(test_prag,"../saves/test_prag.rds")
-
-test_global <- readRDS("../saves/model_pred_global.rds")%>%
-  filter(iteration == 1286 | iteration == 7185)%>%
-  mutate(age = round(age,2))
-
-saveRDS(test_global,"../saves/test_global.rds")
-
-test_flat <- readRDS("../saves/model_pred_flat.rds")%>%
-  filter(iteration == 1286 | iteration == 7185)%>%
-  mutate(age = round(age,2))
-
-saveRDS(test_flat,"../saves/test_flat.rds")
-
-d_model_comp <- data_comb%>%
-  select(-age)%>%
-  mutate(age = round(age_month,2),
-         item = as.character(item))%>%
-  select(alignment, item, age, correct)
-
-xxg <- xxg %>%
-  mutate(age = round(age,2))
-
-sort(unique(d_model_comp$age))
-
-sort(unique(xx$age))
-
-y <- xx %>%
-  right_join(d_model_comp)
-
-tail(y)
-
-bind_rows(
-
-  xx %>%
-    right_join(d_model_comp)%>%
-    mutate(like = ifelse(correct == 1, pred, 1 - pred),
-           log_like = log(like),
-           model = "prag",
-           id = 1:length(log_like))%>%
-  select(id, model,chain,iteration, age, alignment,item,log_like),
-
-xxf %>%
-    right_join(d_model_comp)%>%
-    mutate(like = ifelse(correct == 1, pred, 1 - pred),
-           log_like = log(like),
-           model = "global",
-           id = 1:length(log_like))%>%
-  select(id, model,chain,iteration, age, alignment,item,log_like)
-
-)%>%
-  spread(model, log_like)%>%
-  mutate(prag_vs_global = prag - global) %>%
-  summarise(prag_vs_global = sum(prag_vs_global))
-
-```
-
-# MAP based inverse predictions for ME data
-
-```{r}
-model <- readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")
-
-item_params<- model %>%
-  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
-  filter(parameter == "parameter", type == "items")%>%
-  separate(value, into = c("int", "slope"),sep = ", ")%>%
-  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]")))%>%
-  gather(parameter, value, int, slope)
-
-global_params <- model %>%
-  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
-  filter(parameter == "parameter", type == "parameters")%>%
-    separate(value, into = c("int", "slope"),sep = ", ")%>%
-    mutate(int = as.numeric(str_remove_all(int, "[(c]")),
-         slope = as.numeric(str_remove(slope, "[)]")))%>%
-    gather(parameter, value, int, slope)
+# Fully Bayesian model
+
+```{r}
+
+item_params_fb <- readRDS("../saves/item_params_fb.rds")
+
+global_params_fb <- readRDS("../saves/global_params_fb.rds")
+
+item_sigma_fb <- readRDS("../saves/item_sigma_fb.rds")
 
 #### summaries
-
-item_params_summary <- item_params %>%
+item_params_summary_fb <- item_params_fb %>%
   group_by(item, parameter)%>%
@@
 
-global_params_summary <- global_params %>%
-  group_by(token, parameter)%>%
+global_params_summary_fb <- global_params_fb %>%
+  group_by (parameter,type)%>%
   summarise(mode = estimate_mode(value),
@@
             lci = hdi_lower(value))
-```
-
-```{r}
-# speak_opt_params <- speak_opt %>%
-#   group_by(parameter)%>%
-#   summarise(mode = estimate_mode(value),
-#             uci = hdi_upper(value),
-#             lci = hdi_lower(value))
-#
-
-inv_model_data <- item_params_summary%>%
+
+```
+## Plotting model parameters
+
+### Semantic knowledge
+
+```{r}
+plot_item_params_fb <- ggplot(item_params_fb, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(parameter ~ item, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
+
+plot_item_params_fb
+```
+
+```{r}
+#ggsave("../graphs/item_params_by_chain.pdf", width = 8, height = 3, scale = 1.5)
+```
+
+### Global parameters
+
+```{r}
+
+plot_global_params_fb <- ggplot(global_params_fb, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
+
+plot_global_params_fb
+```
+
+### Global sigmas
+
+```{r}
+plot_item_sigma_fb <- ggplot(item_sigma_fb, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Sigma")+
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()
+
+plot_item_sigma_fb
+```
+
+## Plotting semantic knowledge
+
+```{r}
+plot_sem_know_fb <- item_params_summary_fb%>%
   select(-uci,-lci)%>%
-  spread(parameter, mode)%>%
-  tidyr::expand(item, int,slope,age = unique(me_model_data$age- min(me_model_data$age)))%>%
-  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
-         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode))%>%
-  mutate(speaker_optimality = so_int + so_slope * age,
-         semantic_knowledge = plogis(int + slope * age))
-
-```
-
-```{r}
-invPred <- '
-var allData = dataFromR.data
-
-var priorProbs = [.5,.5]
-
-var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, row.speaker_optimality,row.semantic_knowledge)
-
-    return extend([row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions pragmatic model ex 3 adults}
-inv_model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
-  data =list(data = inv_model_data),
-  data_var = "dataFromR"
-)
-# 
-# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
-# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
-# 
-inv_predictions <- inv_model_pred %>%
-  separate(`0`, into = c("item", "age"), sep="/")%>%
-  mutate(age = as.numeric(age))%>%
-  dplyr::rename( me_effect = `1`)%>%
-  left_join(aoa_ratings)%>%
+  spread(parameter, -item) %>%
+  left_join(expand.grid(
+      age = unique(me_model_data$age),
+      item = unique(me_model_data$item)), .) %>%
+  mutate(sem_know = plogis(intercept + slope * age)) %>%
+  left_join(aoa_ratings) %>%
   ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         age = age + min(me_data$age_num))
-```
-
-```{r}
-# plot_model_pred <- model_pred_summary%>%
-#   left_join(aoa_ratings) %>%
-#   ungroup()%>%
-#   mutate(item = fct_reorder(factor(item), mean_aoa))
-
-model_plot <- ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+ggplot(plot_sem_know_fb, aes(x = age+2, y= sem_know, col = item, group = item))+
+  geom_line(size = 1)+
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_few()+
+  scale_colour_viridis_d(name = "familiar object")
+```
+
+## Plotting model predictions
+
+```{r}
+model_pred_prag_fb <- readRDS("../saves/model_pred_prag_fb.rds")
+
+plot_model_pred_prag_fb <- model_pred_prag_fb%>%
+  group_by(alignment, item, age)%>%
+  summarise(mean = estimate_mode(pred),
+            ci_lower = hdi_lower(pred),
+            ci_upper = hdi_upper(pred))
+
+ggplot() +
   geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(size = 1)+
-  ggtitle("Inverse Model Predictions")+
-  labs(x="Age",y="Proportion correct")+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_pred_prag_fb, aes(x=age+2,y = mean, col = alignment), size = 1)+
+  geom_ribbon(data = plot_model_pred_prag_fb, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
   theme_few() +
@@
   xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d()
-
-model_plot
-```
-
-```{r}
-p2 <- read_csv("../data/me.csv")%>%
-  filter(trial != "train1",
-         trial != "train2")%>%
-  mutate(item = familiar)%>%
-    left_join(aoa_ratings)%>%
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol()+
+  scale_fill_ptol()
+
+x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 200)
+
+plot_model_prag_line_fb <- model_pred_prag_fb%>%
+  filter(iteration %in% x_fb)%>%
+  left_join(aoa_ratings) %>%
   ungroup()%>%
-  mutate(familiar = fct_reorder(factor(item), mean_aoa))
-
-data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+ggplot() +
   geom_hline(yintercept = 0.5, lty=2)+
-  geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
+  geom_line(data = plot_model_prag_line_fb, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
   labs(x="Age",y="Mutual Exclusivity effect")+
-  #facet_grid(~familiar)+
-  ggtitle("Data")+
+  facet_grid(alignment~item)+
   theme_few() +
@@
   xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d(name = "familiar object")+
-  scale_fill_viridis_d(name = "familiar object")
-
-```
-
-```{r}
-ggarrange(data_plot,model_plot, common.legend = T, legend = "right", nrow = 1, ncol = 2)
-```
-
-## For comparison: GLMM for ME effect and data
-
-```{r}
-me_data <- read_csv("../data/me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(z_age = age_num - mean(age_num))
-
-# me_model <- brm(correct ~ z_age + (1|subid) + (z_age | familiar),
-#                 data = me_data,
-#                 family = bernoulli(),
-#                 control = list(adapt_delta = 0.95),
-#                 sample_prior = F,
-#                 save_all_pars = TRUE,
-#                 iter = 2000)
-
-#saveRDS(me_model, "../saves/me_effect_model.rds")
-
-me_model <- readRDS("../saves/me_effect_model.rds")
-
-summary(me_model)
-
-fixef <- as_tibble(fixef(me_model), rownames = "term")
-
-ranef <-  ranef(me_model)
-
-age_me_effect <- as_data_frame(ranef$familiar, rownames = "familiar")%>%
-  mutate(grand_intercept = fixef%>%filter(term=="Intercept")%>%pull(Estimate),
-         grand_slope = fixef%>%filter(term=="z_age")%>%pull(Estimate))%>%
-  group_by(familiar) %>%
-  tidyr::expand(Estimate.Intercept,Estimate.z_age,grand_intercept,grand_slope,z_age = me_data$age_num - mean(me_data$age_num), mean_age = mean(me_data$age_num))%>%
-  mutate(me_effect = plogis(grand_intercept + Estimate.Intercept+(Estimate.z_age+grand_slope)*z_age), 
-         age = z_age+mean_age,
-         item = familiar)%>%
-  select(item, me_effect, age)%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-glmm_plot <- ggplot(age_me_effect, aes(x=age,y = me_effect, col = item))+
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(size = 1)+
-  ggtitle("GLMM")+
-  labs(x="Age",y="Proportion correct")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d(name = "familiar object")
-
-```
-
-```{r}
-ggarrange(data_plot,model_plot,glmm_plot, common.legend = T, legend = "right", nrow = 1, ncol = 3)
-```
-
-# MAP based Model predictions for combination
-
-```{r}
-# novelty data
-
-novel_data <- read_csv("../data/novelty.csv")%>%
-  mutate(age_num = age_num-min(age_num))
-
-# novel_bm <- brm(correct ~ age_num + (1 | subid) + (age_num | agent), 
-#           data = novel_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.95),
-#           sample_prior = F,
-#           save_all_pars = F,
-#           iter = 10000)
-# 
-# saveRDS(novel_bm, "../saves/novelty_model.rds")
-
-novel_bm <- readRDS("../saves_old/novelty_model.rds")
-
-summary(novel_bm)
-
-novel_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
-  select(term,Estimate)%>%
-  spread(term, Estimate)
-
-comb_model_data_con <- inv_model_data %>%
-  mutate(nov_int = novel_params$Intercept,
-         nov_slope = novel_params$age_num,
-         prior = plogis(nov_int + age * nov_slope),
-         alignment = "congruent")
-
-comb_model_data_incon <- inv_model_data %>%
-  mutate(nov_int = novel_params$Intercept,
-         nov_slope = novel_params$age_num,
-         prior = 1- plogis(nov_int + age * nov_slope),
-         alignment = "incongruent")
-
-comb_model_data <- bind_rows(
-  comb_model_data_con,
-  comb_model_data_incon)
-```
-
-```{r}
-combPred <- '
-var allData = dataFromR.data
-
-var output = map(function(row){
-
-    var prior = [row.prior, 1-row.prior]
-
-    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.semantic_knowledge)
-
-    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions pragmatic model ex 3 adults}
-comb_model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
-  data =list(data = comb_model_data),
-  data_var = "dataFromR"
-) %>%
-saveRDS("../saves/prag_model.rds")
-
-comb_model_pred <- readRDS("../saves/prag_model.rds")
-
-comb_model_predictions <- comb_model_pred %>%
-  separate(`0`, into = c("alignment","item", "age"), sep="/")%>%
-  mutate(age = as.numeric(age))%>%
-  dplyr::rename( me_effect = `1`)%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         age = age + min(me_data$age_num),
-         source = "Model")
-
-```
-
-```{r}
-p_comb_model <- ggplot(comb_model_predictions, aes(x=age,y = me_effect, col = item))+
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(size = 1)+
-  ggtitle("Combination Model Predictions")+
-  labs(x="Age",y="Proportion correct")+
-  facet_grid(~alignment)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d()
-
-p_comb_model
-```
-
-```{r}
-data_comb <- read_csv("../data/combination.csv") %>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa), 
-         source = "Data")
-
-p_comb_data <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = item, fill = item)) +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
-  geom_smooth(method = "glm", se = F, alpha = .5, span = 2)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(~alignment)+
-  ggtitle("Combination Data")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d()+
-  scale_fill_viridis_d()
-```
-
-```{r}
-ggarrange(p_comb_model,p_comb_data, common.legend = T, legend = "right", nrow = 2, ncol = 1)
-```
-
-```{r}
-#ggsave("../graphs/combination_model_data.pdf", width = 7, height = 7, scale = 1)
-```
-
-```{r}
-p_data_model <- ggplot(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source)) +
-  geom_hline(yintercept = 0.5, lty=2)+
-  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
-  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
-  #geom_smooth(method = "loess", se = F, alpha = .2, span = 2)+
-  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = alignment, lty = source), size = 1)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  #facet_grid(condition~familiarObject)+
-  facet_grid(~item)+
-  #ggtitle("Combination Data")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-
-p1 <- data_comb%>%
-  group_by(source, alignment, item ,subage)%>%
-  multi_boot_standard(col = "correct")
-
-ggplot(p1, aes(x = subage+0.5, y = mean))+
-  #geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper, col = source))+
-  facet_grid(alignment ~item)+
-  #geom_line(aes(group=alignment,col = source))+
-  #geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = source),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .2, span = 2)+
-  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source), size = 1)+
-  #geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = source), size = 1, alpha = 1)+
-  #geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = source), alpha = .5) +
-  theme_few()+
-  labs(x ="Age", y = "Mutual Exclusivity effect")+
-  scale_color_manual(name = "",
-                     values = c("#117733", "#117733", "#CC6677"))+
-  scale_fill_manual(values = c("#CC6677"))+
-  guides(fill = F)+
-  theme(legend.position = "bottom")
-
-```
-
-```{r}
-ggsave("../graphs/data_model_talk_00.pdf", width = 12, height = 3.5, scale = 1.2)
+  guides(alpha = F, fill = F, col = F)+ 
+  scale_colour_ptol(name = NULL)
+
+```
+
+```{r}
+ggsave("../graphs/pred_model_data.pdf", width = 10, height = 3, scale = 1)
 ```
@@
          data_ci_upper = qbeta(.975, a, b),
-         subage = factor(subage))%>%
+         age = factor(subage))%>%
   select(-a,-b,-n,-k)
 
-binned_model <- comb_model_predictions %>%
-  mutate(subage = cut(age, 
+cor_prag_fb <- readRDS("../saves/model_pred_prag_fb.rds")%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
+         age = cut(age,
                       breaks = c(2,3,4,5),
                       labels = c(2,3,4)))%>%
-  group_by(subage, alignment, item)%>%
-  summarise(model_mean = estimate_mode(me_effect),
-            model_ci_lower = hdi_lower(me_effect),
-            model_ci_upper = hdi_upper(me_effect))
-
-cor_plot <- left_join(
-  binnned_data,
-  binned_model)
-
-ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
+  group_by(model,alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
+
+plot_cor_model_pred_fb <- cor_prag_fb %>%
+  left_join(binnned_data)
+
+ggplot(data = plot_cor_model_pred_fb,aes(x = model_mean, y = data_mean, col = alignment)) +
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
-  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
-  geom_point(size = 2,  stroke = 1)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
+  geom_point(size = 1.5, stroke = 1, pch = 5)+
   coord_fixed()+
@@
   ylab("Data")+
-  facet_grid(~subage)+
-  theme_few() + 
-  scale_colour_viridis_d(name ="Familiar object")
-```
-
-```{r}
-ggsave("../graphs/talk_combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
-```
-
-```{r}
-ggarrange(
-plot_item_params,
-plot_global_params,
-p_data_model, plot_global_sigma,
-ncol = 2, nrow = 2, common.legend = F, widths = c(3,1))
-
-ggsave("../graphs/overview_variant_3_100k.png", width = 12, height = 4, scale = 1.2)
-
-```
-
-## Plotting model predictions
-
-```{r}
-model_pred<- sem_know_model %>%
-  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
-  filter(parameter == "prediction")%>%
-  separate(value, into = c("na", "me_effect"),sep = ",")%>%
-  select(-na)%>%
-  mutate(age = as.numeric(age),
-         me_effect =as.numeric(str_remove(me_effect,"[)]")))
-
-comb_model_pred_agg <- model_pred%>%
-  group_by(Chain, alignment,item,age)%>%
-  summarise(mean = estimate_mode(me_effect),
-            uci = hdi_upper(me_effect),
-            lci = hdi_lower(me_effect))%>%
+  facet_grid(~age)+
+  theme_few() + 
+  scale_colour_ptol(name ="Alignment")+
+  guides(col = F)
+```
+
+```{r}
+ggsave("../graphs/cor_model_data.pdf", width = 8, height = 3.5, scale = 1)
+```
+
+# Mixture model
+
+```{r}
+
+item_params_mm <- readRDS("../saves/item_params_mm.rds")
+
+global_params_mm <- readRDS("../saves/global_params_mm.rds")
+
+item_sigma_mm <- readRDS("../saves/item_sigma_mm.rds")
+
+mixture_mm <- readRDS("../saves/mixture_mm.rds")
+
+#### summaries
+item_params_summary_mm <- item_params_mm %>%
+  group_by(item, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+global_params_summary_mm <- global_params_mm %>%
+  group_by (parameter,type)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+```
+## Plotting model parameters
+
+### Semantic knowledge
+
+```{r}
+plot_item_params_mm <- ggplot(item_params_mm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(parameter ~ item, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
+
+plot_item_params_mm
+```
+
+```{r}
+#ggsave("../graphs/item_params_by_chain.pdf", width = 8, height = 3, scale = 1.5)
+```
+
+### Global parameters
+
+```{r}
+
+plot_global_params_mm <- ggplot(global_params_mm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
+
+plot_global_params_mm
+```
+
+### Global sigmas
+
+```{r}
+plot_item_sigma_mm <- ggplot(item_sigma_mm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Sigma")+
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()
+
+plot_item_sigma_mm
+```
+
+### Mixture
+
+```{r}
+plot_mixture_mm <- ggplot(mixture_mm, aes(x = p_informative, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("p_informative")+
+  xlim(0,1)+
+  theme_few()
+
+plot_mixture_mm
+```
+
+## Plotting semantic knowledge
+
+```{r}
+plot_sem_know_mm <- item_params_summary_mm%>%
+  select(-uci,-lci)%>%
+  spread(parameter, -item) %>%
+  left_join(expand.grid(
+      age = unique(me_model_data$age),
+      item = unique(me_model_data$item)), .) %>%
+  mutate(sem_know = plogis(intercept + slope * age)) %>%
   left_join(aoa_ratings) %>%
   ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         age = age + min(me_data$age_num),
-         Chain = factor(Chain))
-
-ggplot(comb_model_pred_agg, aes(x=age,y = mean, col = item, fill = item))+
-  geom_ribbon(aes(ymin = lci, ymax = uci), alpha = .5, colour = NA)+
-  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col), col = "black", fill = "grey",  method = "loess", se = F, alpha = .2, span = 2)+
-  geom_hline(yintercept = 0.5, lty=2)+
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+ggplot(plot_sem_know_mm, aes(x = age+2, y= sem_know, col = item, group = item))+
   geom_line(size = 1)+
-  ggtitle("Combination Model Predictions")+
-  labs(x="Age",y="Proportion correct")+
-  facet_grid(Chain ~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d()+
-  scale_fill_viridis_d()
-
-```
-
-```{r}
-ggsave("../graphs/model_pred_data.pdf", width = 20, height = 8, scale = 1.2)
-```
-
-# MAP based predictions with noise parameter
-
-## Preparing data
-
-```{r}
-noise_model_data <- item_params_summary%>%
-  select(-uci,-lci)%>%
-  spread(parameter, mode) %>%
-  left_join(read_csv("../data/combination.csv") %>%
-  filter(condition != "train")%>%
-  mutate(alignment = condition,
-         item = familiarObject,
-         age = age_num - (min(age_num))))%>%
-  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
-         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode),
-    glob_sem_know_int = global_params_summary%>%filter(token == "global_sem", parameter == "int")%>%pull(mode),
-         glob_sem_know_slope = global_params_summary%>%filter(token == "global_sem", parameter == "slope")%>%pull(mode),
-         speaker_optimality = so_int + so_slope * age,
-         semantic_knowledge = plogis(int + slope * age),
-         global_semantic_knowledge = plogis(glob_sem_know_int + glob_sem_know_slope * age),
-         nov_int = novel_params$Intercept,
-         nov_slope = novel_params$age_num,
-         prior = ifelse(alignment == "congruent", plogis(nov_int + nov_slope* age),1-plogis(nov_int + age * nov_slope)))%>%
-  select(item, alignment,age, speaker_optimality, semantic_knowledge,global_semantic_knowledge, prior, correct)
-
-```
-
-## Pragmatics model
-
-```{r}
-pragNoise <- '
-var allData = dataFromR.data
-
-var model = function(){
-
-  var noise = uniform({a: 0, b: 1})
-
-  var output = map(function(row){
-
-    var prior = [row.prior, 1-row.prior]
-
-    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.semantic_knowledge)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct)
-
-    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(noisyModelPredictions.score(1))])
-
-}, allData)
-
- return extend(_.fromPairs(output), {noise: noise})
-
-}
-'
-```
-
-```{r predictions pragmatic model ex 3 adults}
-prag_model_noise<- webppl(
-  program_code = paste(rsaUtils, rsaModel, pragNoise , sep='\n'),
-  data =list(data = noise_model_data),
-  data_var = "dataFromR",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
-)
-
-saveRDS(prag_model_noise, "../saves/prag_model_noise.rds")
-
-prag_model_noise <- readRDS("../saves/prag_model_noise.rds")
-
-# noise parameter
-prag_model_noise_noise_param_summary <- prag_model_noise %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-# model predictions
-prag_model_noise_predictions <- prag_model_noise %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
-  mutate(model = "pragmatic_noise")%>%
-  group_by(model,age,item, alignment) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         age = age + min(me_data$age_num),
-         source = "noisy Model")
-
-```
-
-### Plot model predictions
-
-```{r}
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_few()+
+  scale_colour_viridis_d(name = "familiar object")
+```
+
+## Plotting model predictions
+
+```{r}
+model_pred_mm <- readRDS("../saves/model_pred_mm.rds")
+
+plot_model_pred_mm <- model_pred_mm%>%
+  group_by(alignment, item, age)%>%
+  summarise(mean = estimate_mode(pred),
+            ci_lower = hdi_lower(pred),
+            ci_upper = hdi_upper(pred))
+
 ggplot() +
   geom_hline(yintercept = 0.5, lty=2)+
-  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source), method = "loess", se = F, alpha = .2, span = 2)+
-  geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = alignment, lty = source), size = 1)+
-  geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_pred_mm, aes(x=age+2,y = mean, col = alignment), size = 1)+
+  geom_ribbon(data = plot_model_pred_mm, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
   labs(x="Age",y="Mutual Exclusivity effect")+
   facet_grid(alignment~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-geom_smooth(data = data_comb_plot, 
-            aes(x = age_num, y = correct), 
-            col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5)+
-  geom_pointrange(data = p1, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper))+
-  geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .6) +
-  geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = model), size = 1, alpha = 1)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_wrap(alignment~item)+
   theme_few() +
@@
   guides(alpha = F, fill = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-
-p1 <- data_comb%>%
-  mutate(alignment = condition)%>%
-  group_by(alignment, item ,subage)%>%
-  multi_boot_standard(col = "correct")
-
-ggplot(p1, aes(x = subage, y = mean))+
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))+
-  facet_grid(condition ~familiarObject)+
-  geom_line(aes(group=condition))+
-  geom_line(data = prag_model_noise_predictions, aes(x=age+2,y = mean, col = model), size = 1, alpha = 1)+
-  geom_ribbon(data = prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .5) +
-  theme_few() +
-
-```
-
-### Correlate model predictions and data
+  scale_colour_ptol()+
+  scale_fill_ptol()
+
+x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 200)
+
+plot_model_prag_line_fb <- model_pred_prag_fb%>%
+  filter(iteration %in% x_fb)%>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(data = model_pred_mm, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F, col = F)+ 
+  scale_colour_ptol(name = NULL)
+
+```
+
+```{r}
+ggsave("../graphs/pred_model_data.pdf", width = 10, height = 3, scale = 1)
+```
+
+## Correlate model predictions and data
 
@@
          data_ci_upper = qbeta(.975, a, b),
-         subage = factor(subage))%>%
+         age = factor(subage))%>%
   select(-a,-b,-n,-k)
 
-binned_noise_model <- prag_model_noise_predictions %>%
-  mutate(subage = cut(age, 
-                      breaks = c(-0.1,1,2,3),
+cor_mix_mm <- readRDS("../saves/model_pred_mm.rds")%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
+         age = cut(age,
+                      breaks = c(2,3,4,5),
                       labels = c(2,3,4)))%>%
-  group_by(subage, alignment, item)%>%
-  summarise(model_mean = estimate_mode(mean),
-            model_ci_lower = hdi_lower(mean),
-            model_ci_upper = hdi_upper(mean))
-
-cor_plot <- left_join(
-  binnned_data,
-  binned_noise_model)
-
-ggplot(data = cor_plot,aes(x = model_mean, y = data_mean, col = item)) +
+  group_by(model,alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
+
+plot_cor_model_pred_mm <- cor_mix_mm %>%
+  left_join(binnned_data)
+
+ggplot(data = plot_cor_model_pred_mm,aes(x = model_mean, y = data_mean, col = alignment)) +
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
-  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
-  geom_point(size = 2,  stroke = 1)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
+  geom_point(size = 1.5, stroke = 1, pch = 5)+
   coord_fixed()+
@@
   ylab("Data")+
-  facet_grid(~subage)+
-  theme_few() + 
-  scale_colour_viridis_d(name ="Familiar object")
-```
-
-```{r}
-ggsave("../graphs/talk_noise_combination_correlation.pdf", width = 8, height = 4, scale = 1.2)
-```
-
-## Pragmatics model global semantic knnowledge
-
-```{r}
-globalPragNoise <- '
-var allData = dataFromR.data
-
-var model = function(){
-
-  var noise = uniform({a: 0, b: 1})
-
-  var output = map(function(row){
-
-    var prior = [row.prior, 1-row.prior]
-
-    var modelPredictions = pragmaticListener({label: "novel_word"}, prior, row.speaker_optimality,row.global_semantic_knowledge)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct)
-
-    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(noisyModelPredictions.score(1))])
-
-}, allData)
-
- return extend(_.fromPairs(output), {noise: noise})
-
-}
-'
-```
-
-```{r predictions pragmatic model ex 3 adults}
-global_prag_model_noise<- webppl(
-  program_code = paste(rsaUtils, rsaModel, globalPragNoise , sep='\n'),
-  data =list(data = noise_model_data),
-  data_var = "dataFromR",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
-)
-
-saveRDS(global_prag_model_noise, "../saves/global_prag_model_noise.rds")
-
-global_prag_model_noise <- readRDS("../saves/global_prag_model_noise.rds")
-
-# noise parameter
-global_prag_model_noise_noise_param_summary <- global_prag_model_noise %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-# model predictions
-global_prag_model_noise_predictions <- global_prag_model_noise %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
-  mutate(model = "global_pragmatic_noise")%>%
-  group_by(model,age,item, alignment) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         source = "Model")
-
-```
-
-### Plot model predictions
-
-```{r}
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source), method = "loess", se = F, alpha = .2, span = 2)+
-  geom_line(data = global_prag_model_noise_predictions, aes(x=age+2,y = mean, col = alignment, lty = source), size = 1)+
-  geom_ribbon(data = global_prag_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_wrap(~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-
-```
-
-## Flat prior model
-
-```{r}
-flatNoise <- '
-var allData = dataFromR.data
-
-var model = function(){
-
-  var noise = uniform({a: 0, b: 1})
-
-  var output = map(function(row){
-
-    var prior = [row.prior, 1-row.prior]
-
-    var modelPredictions = pragmaticListener({label: "novel_word"}, [.5,.5], row.speaker_optimality,row.semantic_knowledge)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct)
-
-    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(noisyModelPredictions.score(1))])
-
-}, allData)
-
- return extend(_.fromPairs(output), {noise: noise})
-
-}
-'
-```
-
-```{r predictions pragmatic model ex 3 adults}
-flat_model_noise<- webppl(
-  program_code = paste(rsaUtils, rsaModel, flatNoise , sep='\n'),
-  data =list(data = noise_model_data),
-  data_var = "dataFromR",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
-)
-
-saveRDS(flat_model_noise, "../saves/flat_model_noise.rds")
-
-flat_model_noise <- readRDS("../saves/flat_model_noise.rds")
-
-# noise parameter
-flat_model_noise_noise_param_summary <- flat_model_noise %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-# model predictions
-flat_model_noise_predictions <- flat_model_noise %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
-  mutate(model = "flat_prior_noise")%>%
-  group_by(model,age,item, alignment) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         source = "Model")
-
-```
-
-### Plot model predictions
-
-```{r}
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source), method = "loess", se = F, alpha = .2, span = 2)+
-  geom_line(data = flat_model_noise_predictions, aes(x=age+2,y = mean, col = alignment, lty = source), size = 1)+
-  geom_ribbon(data = flat_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_wrap(~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-```
-
-## Prior only model
-
-```{r}
-priorOnlyNoise <- '
-var allData = dataFromR.data
-
-var model = function(){
-
-  var noise = uniform({a: 0, b: 1})
-
-  var output = map(function(row){
-
-    var prior = [row.prior, 1-row.prior]
-
-      var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: prior}));
-      return obj.shape == "novel_object" ? 1 : 0
-       }})
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct)
-
-    return extend([row.alignment + "/" +  row.item + "/" + row.age, Math.exp(noisyModelPredictions.score(1))])
-
-}, allData)
-
- return extend(_.fromPairs(output), {noise: noise})
-
-}
-'
-```
-
-```{r predictions pragmatic model ex 3 adults}
-prior_only_model_noise<- webppl(
-  program_code = paste(rsaUtils, rsaModel, priorOnlyNoise , sep='\n'),
-  data =list(data = noise_model_data),
-  data_var = "dataFromR",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
-)
-
-saveRDS(prior_only_model_noise, "../saves/prior_only_model_noise.rds")
-
-prior_only_model_noise <- readRDS("../saves/prior_only_model_noise.rds")
-
-# noise parameter
-prior_only_model_noise_noise_param_summary <- prior_only_model_noise %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-# model predictions
-prior_only_model_noise_predictions <- prior_only_model_noise %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
-  mutate(model = "prior_only_noise")%>%
-  group_by(model,age,item, alignment) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa),
-         source = "Model")
-
-```
-
-### Plot model predictions
-
-```{r}
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_smooth(data = data_comb, aes(x = age_num, y = correct, col = alignment, fill = alignment, lty = source), method = "loess", se = F, alpha = .2, span = 2)+
-  geom_line(data = prior_only_model_noise_predictions, aes(x=age+2,y = mean, col = alignment, lty = source), size = 1)+
-  geom_ribbon(data = prior_only_model_noise_predictions, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_wrap(~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-```
-
-## Compare noise parameters
-
-```{r}
-noise_plot <- bind_rows(
-  prag_model_noise %>%
-    filter(Parameter %in% c("noise"))%>%
-    mutate(Model = "Pragmatic"),
-  global_prag_model_noise %>%
-    filter(Parameter %in% c("noise"))%>%
-    mutate(Model = "Pragmatic global"),
-  flat_model_noise %>%
-    filter(Parameter %in% c("noise"))%>%
-    mutate(Model = "Flat Prior"),
-  prior_only_model_noise %>%
-    filter(Parameter %in% c("noise"))%>%
-    mutate(Model = "Prior Only")
-)
-
-ggplot(noise_plot, aes(x = value, col = Model, fill = Model))+
-  geom_density(alpha = .7, bw = .01)+
-  theme_few()+
-  xlim(0,1)+
-  scale_color_ptol()+
-  scale_fill_ptol()+
-  theme()
-
-```
-
-```{r}
-ggsave("../graphs/noise.pdf", width = 6, height = 3, scale = 1.2)
-```
-
-## Compare predictions
-
-```{r}
-
-noise_model_pred <- bind_rows(
-  prag_model_noise_predictions,
-  global_prag_model_noise_predictions,
-  prior_only_model_noise_predictions,
-  flat_model_noise_predictions
-)
-
-data_comb_plot<-data_comb%>%
-  mutate(model = "data")
-
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = noise_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
-  geom_ribbon(data = noise_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(alignment~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F)+ 
-  scale_colour_ptol(name = NULL)+
-  scale_fill_ptol(name = NULL)
-```
-
-## Correlate predictions with data
-
-```{r}
-binned_noise_model <- prag_model_noise %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("alignment","item", "age"), sep="/")%>%
-  mutate(age = as.numeric(age) + min(me_data$age_num),
-         subage = factor(cut(age, 
-                      breaks = c(2,3,4,5),
-                      labels = c(2,3,4))))%>%
-  group_by(subage, alignment, item)%>%
-  summarise(model_mean = estimate_mode(value),
-            model_ci_lower = hdi_lower(value),
-            model_ci_upper = hdi_upper(value))
-
-cor_plot_2 <- bind_rows(
-left_join(binned_model, binnned_data)%>%mutate(model = "Parameter free"), 
-left_join(binned_noise_model,binnned_data)%>%mutate(model = "Noise")
-)
-
-ggplot(data = cor_plot_2,aes(x = model_mean, y = data_mean, col = item)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
-  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
-  geom_point(size = 2,  stroke = 1)+
-  coord_fixed()+
- stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  ylab("Data")+
-  facet_grid(~subage)+
-  theme_few() + 
-  scale_colour_viridis_d(name ="Item")
-```
-
-```{r}
-ggsave("../graphs/cor_plot_noise.pdf", width = 10, height = 4, scale = .8)
-```
-
-# OLD: Comparing parameters between model runs
-
-## Base model
-
-```{r}
-baseMeModel <- '
-
-var sem_knowledge = 1
-
-var priorProbs = [.5,.5]
-
-var speakerOptimality = 1
-
-var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality, sem_knowledge)
-
-  modelPredictions
-
-'
-```
-
-```{r}
-webppl(program_code = paste(rsaUtils, rsaModel, baseMeModel,sep='\n'))
-```
-
-## Prior model
-
-```{r}
-prior_params <- '
-
-var priorData = dataFromR.data
-
-var priorSubjects = levels(priorData, "subid")
-
-display(priorData)
-
-var model  = function(){
-
-  var prior_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var prior_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-  var prior_subject_sigma = uniformDrift({a: 0, b:3, width: 0.2})
-
-  var priorSampleSub = function(age){
-    return gaussianDrift({ mu: age, sigma: prior_subject_sigma, width: 0.1 })
-  }
-
-  foreach(function(subid){
-      var priorSubjectData = _.filter(priorData, {subid: subid})
-
-      //display(subjects)
-
-      var subj_age = priorSubjectData[0].age
-
-      var subjectPrior = priorSampleSub(subj_age)
-
-    foreach(function(row){
-
-      var priorReg = logistic(prior_int + prior_slope * subjectPrior)
-
-      var prior = [priorReg, 1-priorReg]
-
-      var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: prior}));
-      return obj.shape == "novel_object" ? 1 : 0
-       }})
-
-     observe(modelPredictions, row.correct)
-
-    }, priorSubjectData)
-
-  }, priorSubjects)
-
-  query.add(["intercept"], [prior_int])
-  query.add(["slope"], [prior_slope])
-  query.add(["sigma"], [prior_subject_sigma])
-
-  return query
-
-}
-
-'
-```
-
-```{r}
-
-prior_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, prior_params , sep='\n'),
-  data = list(data = prior_model_data),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 1,
-  cores = 1,
-  inference_opts = list(method = "MCMC", samples = 1, burn = 1, verbose = T)
-)
-
-saveRDS(prior_model, "../saves/prior_model.rds")
-
-prior_model <- readRDS("../saves/prior_model.rds")
-
-prior <- prior_model%>%
-  mutate(value = unlist(value))
-
-prior_summary <- prior%>%
-  group_by(Parameter)%>%
-  summarise(param_map = estimate_mode(value),
-            param_uci = hdi_upper(value),
-            param_lci = hdi_lower(value))
-
-```
-
-#### Visualizing parameters
-
-```{r}
-ggplot(prior, aes(x = value, fill = factor(Chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Parameter")+
-  facet_grid(Parameter~., scales = 'free')+
-  theme_few()
-
-```
-
-#### Comparison to brm models
-
-```{r}
-
-# same model as webppl model  implemented in brms
-
-novel_bm <- brm(correct ~ age + (1 | subid), 
-          data = prior_model_data, family = bernoulli(),
-          control = list(adapt_delta = 0.95),
-          sample_prior = F,
-          save_all_pars = TRUE,
-          iter = 20000)
-
-summary(novel_bm)
-
-saveRDS(novel_bm, "../saves/novelty_model_brm.rds")
-```
-
-```{r}
-# brm model from last chunk
-novel_bm <- readRDS("../saves/novelty_model_brm.rds")
-
-#summary(novel_bm)
-
-brm_params <- as_tibble(fixef(novel_bm), rownames = "term")%>%
-  select(term,Estimate)%>%
-  spread(term, Estimate)
-
-brm_plot <- tibble(
-  age = prior_model_data$age,
-  y = plogis(brm_params$Intercept + brm_params$age * age),
-  model = "brm"
-)
-
-#brm model with additional random intercept and slope for item
-novel_bm_full <- readRDS("../saves/novelty_model.rds")
-
-#summary(novel_bm_full)
-
-brm_full_params <- as_tibble(fixef(novel_bm_full), rownames = "term")%>%
-  select(term,Estimate)%>%
-  spread(term, Estimate)
-
-brm_full_plot <- tibble(
-  age = prior_model_data$age,
-  y = plogis(brm_full_params$Intercept + brm_full_params$age_num * age),
-  model = "brm_full"
-)
-
-# webppl model
-webppl_plot <- tibble(
-  age = prior_model_data$age,
-  y = plogis(prior_summary%>%filter(Parameter == "intercept")%>%pull(param_map) + prior_summary%>%filter(Parameter == "slope")%>%pull(param_map) * age),
-  model = "webppl"
-)
-
-prior_comp_plot <- bind_rows(
-  brm_plot,
-  webppl_plot,
-  brm_full_plot
-
-)
-```
-
-```{r}
-ggplot(prior_comp_plot, aes(x = age, y = y, col = model))+
-  geom_line()+
-  ylim(0,1)+
-  theme_few()+
-  scale_color_ptol()
-```
-
-## sem knowledge
-
-```{r}
-
-sem_know_run_summary <- item_params%>%
-  spread(parameter,value)%>%
-  group_by(Chain,item)%>%
-  summarise(overall_int = estimate_mode(int),
-            overall_slope = estimate_mode(slope))
-
-sem_know_run_iteration <- item_params%>%
-  spread(parameter,value)
-
-sem_know_chain <- sem_know_run_iteration %>%
-  left_join(sem_know_run_summary)
-
-chain_comp <- sem_know_chain %>%
-  left_join(expand.grid(
-      age = unique(me_model_data$age),
-      item = unique(me_model_data$familiar)), .) %>%
-  mutate(sem_know_ci = plogis(int + slope * age),
-         sem_know = plogis(overall_int + overall_slope * age)) %>%
-  group_by(Chain,item, age) %>%
-  summarise(sem_know = estimate_mode(sem_know),
-            sem_know_uci = hdi_upper(sem_know_ci),
-            sem_know_lci = hdi_lower(sem_know_ci))
-
-ggplot(chain_comp, aes(x = age+2, y= sem_know, fill = factor(Chain)))+
-  geom_line(size = .3, aes(col = factor(Chain)))+
-  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .05)+
-  ylab("Semantic knowledge")+
-  xlab("Age")+
-  ylim(0,1)+
-  facet_wrap(~item, nrow = 3)+
-  theme_few()+
-  scale_colour_discrete()+
-  scale_fill_discrete()
-
-```
-
-## speaker optimality
-
-```{r}
-
-so_run_iteration <- global_params%>%
-  spread(parameter, value)
-
-so_run_summary <- so_run_iteration%>%
-  group_by(Chain)%>%
-  summarise(overall_int = estimate_mode(int),
-            overall_slope = estimate_mode(slope))
-
-so_run <- so_run_iteration %>%
-  left_join(so_run_summary)
-
-so_run_comp <-so_run%>%
-  group_by(Chain,Iteration)%>%
-  tidyr::expand(int,slope,overall_int,overall_slope,age = unique(me_model_data$age))%>%
-  mutate(so_ci = int + slope * age,
-         so = overall_int + overall_slope * age) %>%
-  group_by(Chain, age) %>%
-  summarise(so = estimate_mode(so),
-            so_uci = hdi_upper(so_ci),
-            so_lci = hdi_lower(so_ci))
-
-ggplot(so_run_comp, aes(x = age+2, y= so, fill = factor(Chain)))+
-  geom_line(size = .4, aes(col = factor(Chain)))+
-  geom_ribbon(aes(ymin=so_lci, ymax = so_uci), alpha = .05)+
-  ylab("speaker optimality")+
-  xlab("Age")+
-  #facet_grid(~run)+
-  theme_few()+
-  scale_colour_discrete()+
-  scale_fill_discrete()
-
-```
-
-## Correlations between parameters for semantic knowledge
-
-```{r}
-ggplot(item_params%>%filter(parameter == "int"), aes(x = value))+
-  geom_density(alpha = 0.3)+
-  xlab("Parameter")+
-  facet_grid(Chain~item, scales = 'free')+
-  theme_few()
-
-#ggsave("../graphs/item_by_chain.pdf", width = 15, height = 15, scale = 1.5)
-```
-
-```{r}
-item_params_cor <- item_params %>%
-  group_by(Chain,item, parameter)%>%
-  summarise(mode = estimate_mode(value))
-```
-
-```{r}
-library(corrr)
-library(corrplot)
-
-## correaltion at 2
-cor_int_2 <- item_params_cor%>%
-  spread(Chain, mode) %>%
-  filter(parameter == "int")%>%
-  select(-parameter)%>%
-  ungroup()%>%
-  select(-item)%>%
-  correlate(method = "spearman")%>%
-  gather(key, value)%>%
-  filter(key !="rowname")%>%
-  na.omit()%>%
-  mutate(value = as.numeric(value),
-         age = "2")
-
-cor_int_3 <- item_params_cor%>%
-  spread(parameter, mode)%>%
-  mutate(mode = int + slope)%>%
-  select(Chain, item, mode)%>%
-  spread(Chain, mode)%>%
-  ungroup()%>%
-  select(-item)%>%
-  correlate(method = "spearman")%>%
-  gather(key, value)%>%
-  filter(key !="rowname")%>%
-  na.omit()%>%
-  mutate(value = as.numeric(value),
-         age = "3")
-
-cor_int_4 <- item_params_cor%>%
-  spread(parameter, mode)%>%
-  mutate(mode = int + 2*slope)%>%
-  select(Chain, item, mode)%>%
-  spread(Chain, mode)%>%
-  ungroup()%>%
-  select(-item)%>%
-  correlate(method = "spearman")%>%
-  gather(key, value)%>%
-  filter(key !="rowname")%>%
-  na.omit()%>%
-  mutate(value = as.numeric(value),
-         age = "4")
-
-cor_int_5 <- item_params_cor%>%
-  spread(parameter, mode)%>%
-  mutate(mode = int + 3*slope)%>%
-  select(Chain, item, mode)%>%
-  spread(Chain, mode)%>%
-  ungroup()%>%
-  select(-item)%>%
-  correlate(method = "spearman")%>%
-  gather(key, value)%>%
-  filter(key !="rowname")%>%
-  na.omit()%>%
-  mutate(value = as.numeric(value),
-         age = "5")
-
-cor_hist <- 
-bind_rows(
-  cor_int_2,
-  cor_int_3,
-  cor_int_4,
-  cor_int_5
-)
-
-ggplot(cor_hist, aes(x = value, fill =age))+
-  geom_density(alpha = .5)+
-  xlim(-1,1)+
-  xlab("Correlation")+
-  theme_few()
-
-#ggsave("../graphs/corr_int_by_age.pdf", width = 5, height = 4, scale = 1.5)
-
-```
-
-# Model (No nesting within participants)
-```{r}
-semStr <- '
-var data = dataFromR.data
-
-var priorProbs = [.5,.5]
-
-var familiars = levels(data, "familiar")
-
-var model  = function(){
-
-  var speakerOptimalityParameters = {
-    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 4, width: 0.5})
-  }
-
-  var globalLineParameters = {
-    intercept: uniformDrift({a: -3, b: 3, width: 0.5}),
-    slope: uniformDrift({a: 0, b: 2, width: 0.5})
-  }
-
-  var itemVariability = {
-    intercept: uniformDrift({a: 0, b: 2, width: 0.2}),
-    slope: uniformDrift({a: 0, b: 1, width: 0.2})
-  }
-
-  // conceptually it might not make sense to have two sigmas, but maybe it does
-  // intercept sigma probably will be smaller than slope sigma
-  // var item_int_sigma = uniformDrift({a: 0, b: 3, width: 0.2})
-
-  foreach(function(cndtn){
-
-    var conditionData = _.filter(data, {familiar: cndtn})
-
-      var itemLineParameters = {
-        intercept: gaussianDrift({
-          mu: globalLineParameters.intercept, 
-          sigma: itemVariability.intercept, 
-          width: 0.5
-        }),
-     //   slope: gaussianDrift({
-     //     mu: globalLineParameters.slope, 
-      //    sigma: itemVariability.slope, 
-      //    width: 0.5
-     //   })
-      slope: Math.pow(gaussianDrift({
-         mu: globalLineParameters.slope, 
-        sigma: itemVariability.slope, 
-         width: 0.5
-      }), 2)
-      }
-
-    foreach(function(row){
-
-      var age = row.age
-
-      //display(age)
-
-      var sem_knowledge = logistic(itemLineParameters.intercept + 
-          itemLineParameters.slope * age)
-
-      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * age
-
-      var modelPredictions = pragmaticListener({label: "novel_word"}, 
-            priorProbs, speakerOptimality, sem_knowledge)
-      // display(modelPredictions.score(row.correct))
-
-      observe(modelPredictions, row.correct)
-
-      // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])
-
-    }, conditionData)
-
-    query.add(["parameter","items", cndtn], [itemLineParameters.intercept, itemLineParameters.slope])
-
-  }, familiars)
-
-  query.add(["parameter","parameters","speaker_optimality"], [speakerOptimalityParameters.intercept, speakerOptimalityParameters.slope])
-  query.add(["parameter","parameters", "global_sem"], [globalLineParameters.intercept, globalLineParameters.slope])
-  query.add(["parameter","sigma", "global_sem_sigmas"], [itemVariability.intercept, itemVariability.slope])
-
-  return query 
-}
-'
-```
-
-```{r}
-me_model_data <- read_csv("../data/me.csv")%>%
-    filter(trial != "train1",
-           trial != "train2")%>%
-  mutate(age = age_num - min(age_num))
-
-sem_know_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
-  data = list(data = me_model_data),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "incrementalMH",
-                        samples = 100000,
-                        burn = 50000,
-                        verbose = T,
-                        lag = 1,
-                        verboseLag = 5000)
-)
-
-#saveRDS(sem_know_model, "../saves/sem_know_model_variant2_100k.rds")
-```
+  facet_grid(~age)+
+  theme_few() + 
+  scale_colour_ptol(name ="Alignment")+
+  guides(col = F)
+```
+
+```{r}
+ggsave("../graphs/cor_model_data.pdf", width = 8, height = 3.5, scale = 1)
+```

### 2020-02-12 stats/model_sample_processing.Rmd
test run mixture model

@@
 
+# combine chains into one file
+
 ```{r}
@@
 ```
+
+# mixture model
+
+```{r}
+
+model <- bind_rows(
+ fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-1000_burn500_lag5_chain1.csv",header = T)%>%mutate(chain = 1)
+)
+
+# Model Parameters
+
+item_params <-  model %>%
+  filter(b == "items")%>%
+  select(-a,-b, -e, -f, -h)%>%
+    rename(item = c,
+         parameter = d,
+         value = g)
+
+saveRDS(item_params, "../saves/item_params_mm.rds")
+
+global_params <- model %>%
+  filter(b == "parameters")%>%
+  select(-a,-b, -e,-f, -h)%>%
+    rename(parameter = c,
+         type = d,
+         value = g)
+
+saveRDS(global_params, "../saves/global_params_mm.rds")
+
+item_sigma<- model %>%
+  filter(b == "sigma",
+         c == "global_sem_sigmas")%>%
+  select(-a,-b, -e,-f,-h)%>%
+    rename(parameter = c,
+         type = d,
+         value = g)
+
+saveRDS(item_sigma, "../saves/item_sigma_mm.rds")
+
+mixture<- model %>%
+  filter(b == "mixtureComponent")%>%
+  select(b,g,chain)%>%
+    rename(parameter = b,
+         p_informative = g)
+
+saveRDS(mixture, "../saves/mixture_mm.rds")
+
+model_pred_prag <- model %>%
+  filter(a == "modelPrediction",
+         b == "mixtureModel")%>%
+  select(-a, -h, -c)%>%
+  rename(model = b, 
+         alignment = d,
+         item = e,
+         age = f, 
+         pred = g)
+
+saveRDS(model_pred_prag, "../saves/model_pred_mm.rds")
+
+```

### 2020-02-13 stats/model_comparison.Rmd
update model sample processing file

@@
 
-# Model comparison
+# Model comparison prediction
 
@@
 ```
+
+# Model comparison explanation
+
+```{r}
+
+d_model_comp.summarized <- d_model_comp %>% 
+  group_by(alignment, item, age) %>% 
+  summarize(n=n(), k = sum(correct))
+
+model_like <- bind_rows(
+
+  readRDS("../saves/model_pred_prag.rds") %>%
+    right_join(d_model_comp.summarized) %>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k),
+
+  readRDS("../saves/model_pred_prag_fb.rds") %>%
+    mutate(model = "fullBayes")%>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k)
+
+    # ,readRDS("../saves/model_pred_mm.rds") %>%
+    # mutate(model = "mixture")%>%
+    # right_join(d_model_comp.summarized)%>%
+    # select(model,chain,iteration, age, alignment,item,pred, n, k)
+) %>%
+  mutate(
+    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
+  ) %>%
+  group_by(chain, model, iteration) %>%
+  summarize(total_likelihood_sample = sum(log_like))
+
+# variation across chains
+
+model_by_chain <- model_like %>%
+  na.omit(chain)%>%
+  group_by(model, chain) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  spread(model, marginal_likelihood)
+
+# compare models
+model_comp <- model_like %>%
+  na.omit(chain)%>%
+  group_by(model) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  spread(model, marginal_likelihood)%>%
+  mutate(fb_vs_free = fullBayes - pragmatic
+         # ,fb_vs_mixture= fullBayes - mixture,
+         # free_vs_mixture = pragmatic - mixture
+         ) %>%
+  select(-pragmatic, -fullBayes, -mixture) %>%
+  gather(model, logBF)
+
+```

### 2020-02-13 stats/model_sample_processing.Rmd
update model sample processing file

@@
          age = f, 
-         pred = g)
+         pred = g,
+         model = "fullBayes")
 

### 2020-02-13 stats/model_sample_processing.Rmd
peek at chain 5 fb model

--- 2020-02-12 stats/model_sample_processing.Rmd
@@
          age = f, 
-         pred = g)
+         pred = g)%>%
+mutate(model = "fullBayes")
 

### 2020-02-13 stats/model_sample_processing.Rmd
fb model run

@@
  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
- read("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
+ fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
   fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),

### 2020-02-15 stats/model.Rmd
visualize model comp

@@
 
-x <- sample(1:length(unique(model_pred_prag$iteration)), 200)
+x <- sample(1:length(unique(model_pred_prag$iteration)), 120)
 
@@
 
-x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 200)
+x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 100)
 
@@
 ```{r}
-ggsave("../graphs/pred_model_data.pdf", width = 10, height = 3, scale = 1)
+ggsave("../graphs/pred_.pdf", width = 10, height = 3, scale = 1)
 ```
@@
 ```
+
+# Comparing models
+
+## Parameters
+
+### Semantic knowledge
+
+```{r}
+
+com_item_params <- bind_rows(
+  item_params%>%mutate(model="pragmatic"),
+  item_params_fb%>%mutate(model="fullBayes")
+)
+
+ggplot(com_item_params, aes(x = value, fill = model, group = paste(model,chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(parameter ~ item, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
+
+```
+
+### Global parameters
+
+```{r}
+
+com_global_params <- bind_rows(
+  global_params%>%mutate(model="pragmatic"),
+  global_params_fb%>%mutate(model="fullBayes")
+)
+
+ggplot(com_global_params, aes(x = value, fill = model, group = paste(model,chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
+
+```
+
+```{r}
+ggsave("../graphs/item_params_by_model.pdf", width = 8, height = 3, scale = 1.5)
+```
+
+## Model predictions
+
+```{r}
+plot_model_comp <- bind_rows(
+plot_model_prag_line,
+plot_model_prag_line_fb
+)
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(data = plot_model_comp, aes(x=age+2,y = pred, col = model, group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3, span = 1, size = .5)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol()+
+  theme(legend.position = "bottom")
+```
+
+```{r}
+ggsave("../graphs/predictions_by_model.pdf", width = 8, height = 3, scale = 1.5)
+```

### 2020-02-15 stats/model_comparison.Rmd
add mixture model

--- 2020-02-11 stats/model_comparison.Rmd
@@
 ```
+
+# Model comparison explanation
+
+```{r}
+
+d_model_comp.summarized <- d_model_comp %>% 
+  group_by(alignment, item, age) %>% 
+  summarize(n=n(), k = sum(correct))
+
+model_like <- bind_rows(
+
+  readRDS("../saves/model_pred_prag.rds") %>%
+    right_join(d_model_comp.summarized) %>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k),
+
+  readRDS("../saves/model_pred_prag_fb.rds") %>%
+    mutate(model = "fullBayes")%>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k)
+
+    ,readRDS("../saves/model_pred_mm.rds") %>%
+    mutate(model = "mixture")%>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k)
+) %>%
+  mutate(
+    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
+  ) %>%
+  group_by(chain, model, iteration) %>%
+  summarize(total_likelihood_sample = sum(log_like))
+
+# variation across chains
+
+model_by_chain <- model_like %>%
+  na.omit(chain)%>%
+  group_by(model, chain) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  spread(model, marginal_likelihood)
+
+saveRDS(model_by_chain, "../saves/expl_model_likelihood_chain")
+
+# compare models
+model_comp <- model_like %>%
+  na.omit(chain)%>%
+  group_by(model) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  spread(model, marginal_likelihood)%>%
+  mutate(fb_vs_free = fullBayes - pragmatic
+          ,fb_vs_mixture= fullBayes - mixture,
+          free_vs_mixture = pragmatic - mixture
+         ) %>%
+  select(-pragmatic, -fullBayes, -mixture) %>%
+  gather(model, logBF)
+
+saveRDS(model_comp, "../saves/expl_model_comparison")
+
+```

### 2020-02-15 stats/model_sample_processing.Rmd
add mixture model

@@
 model <- bind_rows(
- fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-1000_burn500_lag5_chain1.csv",header = T)%>%mutate(chain = 1)
+ fread("../webppl/output/samples-webppl-sample-writer-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain1.csv",header = T)%>%mutate(chain = 1),
+ fread("../webppl/output/samples-webppl-sample-writer-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
+ fread("../webppl/output/samples-webppl-sample-writer-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
+ fread("../webppl/output/samples-webppl-sample-writer-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
+ fread("../webppl/output/samples-webppl-sample-writer-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
+ fread("../webppl/output/samples-webppl-sample-writer-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6),
 )

### 2020-02-18 stats/model_sample_processing.Rmd
add model comparison

--- 2020-02-13 stats/model_sample_processing.Rmd
@@
 model <- bind_rows(
- fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-1000_burn500_lag5_chain1.csv",header = T)%>%mutate(chain = 1)
+ fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain1.csv",header = T)%>%mutate(chain = 1),
+ fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
+ fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
+ fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
+ fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
+ fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6),
 )

### 2020-02-18 stats/model.Rmd
add developmental mixture model

@@
 
-x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 200)
+x_mm <- sample(1:length(unique(model_pred_mm$iteration)), 200)
 
-plot_model_prag_line_fb <- model_pred_prag_fb%>%
-  filter(iteration %in% x_fb)%>%
+model_pred_mm_line_mm <- model_pred_mm%>%
+  filter(iteration %in% x_mm)%>%
   left_join(aoa_ratings) %>%
@@
 ```{r}
-ggsave("../graphs/pred_model_data.pdf", width = 10, height = 3, scale = 1)
+ggsave("../graphs/pred_mm_model_data.pdf", width = 10, height = 3, scale = 1)
 ```
@@
 ```{r}
-ggsave("../graphs/cor_model_data.pdf", width = 8, height = 3.5, scale = 1)
+ggsave("../graphs/cor_model_data_mm.pdf", width = 8, height = 3.5, scale = 1)
+```
+
+# Developmental Mixture model
+
+```{r}
+
+item_params_dmm <- readRDS("../saves/item_params_dmm.rds")
+
+global_params_dmm <- readRDS("../saves/global_params_dmm.rds")
+
+item_sigma_dmm <- readRDS("../saves/item_sigma_dmm.rds")
+
+mixture_dmm <- readRDS("../saves/mixture_dmm.rds")
+
+#### summaries
+item_params_summary_dmm <- item_params_dmm %>%
+  group_by(item, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+global_params_summary_dmm <- global_params_dmm %>%
+  group_by (parameter,type)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+```
+## Plotting model parameters
+
+### Semantic knowledge
+
+```{r}
+plot_item_params_dmm <- ggplot(item_params_dmm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(parameter ~ item, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
+
+plot_item_params_dmm
+```
+
+```{r}
+#ggsave("../graphs/item_params_by_chain.pdf", width = 8, height = 3, scale = 1.5)
+```
+
+### Global parameters
+
+```{r}
+
+plot_global_params_dmm <- ggplot(global_params_dmm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
+
+plot_global_params_dmm
+```
+
+### Global sigmas
+
+```{r}
+plot_item_sigma_dmm <- ggplot(item_sigma_dmm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Sigma")+
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()
+
+plot_item_sigma_dmm
+```
+
+### Mixture
+
+```{r}
+plot_mixture_dmm <- ggplot(mixture_dmm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("value")+
+  facet_grid(~type)+
+  xlim(0,1)+
+  theme_few()
+
+plot_mixture_dmm
+```
+
+## Plotting semantic knowledge
+
+```{r}
+plot_sem_know_dmm <- item_params_summary_dmm%>%
+  select(-uci,-lci)%>%
+  spread(parameter, -item) %>%
+  left_join(expand.grid(
+      age = unique(me_model_data$age),
+      item = unique(me_model_data$item)), .) %>%
+  mutate(sem_know = plogis(intercept + slope * age)) %>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+ggplot(plot_sem_know_dmm, aes(x = age+2, y= sem_know, col = item, group = item))+
+  geom_line(size = 1)+
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_few()+
+  scale_colour_viridis_d(name = "familiar object")
+```
+
+## Plotting model predictions
+
+```{r}
+model_pred_dmm <- readRDS("../saves/model_pred_dmm.rds")
+
+plot_model_pred_dmm <- model_pred_dmm%>%
+  group_by(alignment, item, age)%>%
+  summarise(mean = estimate_mode(pred),
+            ci_lower = hdi_lower(pred),
+            ci_upper = hdi_upper(pred))
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_pred_dmm, aes(x=age+2,y = mean, col = alignment), size = 1)+
+  geom_ribbon(data = plot_model_pred_dmm, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol()+
+  scale_fill_ptol()
+
+x_dmm <- sample(1:length(unique(model_pred_dmm$iteration)), 200)
+
+model_pred_line_dmm <- model_pred_dmm%>%
+  filter(iteration %in% x_dmm)%>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(data = model_pred_line_dmm, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F, col = F)+ 
+  scale_colour_ptol(name = NULL)
+
+```
+
+```{r}
+ggsave("../graphs/pred_mm_model_data.pdf", width = 10, height = 3, scale = 1)
+```
+
+## Correlate model predictions and data
+
+```{r}
+binnned_data <- data_comb%>%
+  group_by(subage, alignment, item)%>%
+  summarize(k = sum(correct), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         data_mean = (a-1)/(a+b-2),
+         data_ci_lower  = qbeta(.025, a, b),
+         data_ci_upper = qbeta(.975, a, b),
+         age = factor(subage))%>%
+  select(-a,-b,-n,-k)
+
+cor_mix_dmm <- readRDS("../saves/model_pred_dmm.rds")%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
+         age = cut(age,
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(model,alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
+
+plot_cor_model_pred_dmm <- cor_mix_dmm %>%
+  left_join(binnned_data)
+
+ggplot(data = plot_cor_model_pred_dmm,aes(x = model_mean, y = data_mean, col = alignment)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
+  geom_point(size = 1.5, stroke = 1, pch = 5)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(~age)+
+  theme_few() + 
+  scale_colour_ptol(name ="Alignment")+
+  guides(col = F)
+```
+
+```{r}
+ggsave("../graphs/cor_model_data_mm.pdf", width = 8, height = 3.5, scale = 1)
 ```
@@
   global_params%>%mutate(model="pragmatic"),
-  global_params_fb%>%mutate(model="fullBayes")
+  global_params_fb%>%mutate(model="fullBayes"),
+  global_params_mm%>%mutate(model="mixture")
 )
@@
 plot_model_prag_line,
-plot_model_prag_line_fb
+plot_model_prag_line_fb,
+plot_model_prag_line_mm
 )

### 2020-02-18 stats/model_sample_processing.Rmd
add developmental mixture model

@@
 ```
+
+# developmental mixture model
+
+```{r}
+
+model <- bind_rows(
+ fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-200_burn100_lag1_chain1.csv",header = T)%>%mutate(chain = 1),
+ # fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
+ # fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
+ # fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
+ # fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
+ # fread("../webppl/output/samples-fullBayes-mixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
+)
+
+# Model Parameters
+
+item_params <-  model %>%
+  filter(b == "items")%>%
+  select(-a,-b, -e, -f, -h)%>%
+    rename(item = c,
+         parameter = d,
+         value = g)
+
+saveRDS(item_params, "../saves/item_params_dmm.rds")
+
+global_params <- model %>%
+  filter(b == "parameters")%>%
+  select(-a,-b, -e,-f, -h)%>%
+    rename(parameter = c,
+         type = d,
+         value = g)
+
+saveRDS(global_params, "../saves/global_params_dmm.rds")
+
+item_sigma<- model %>%
+  filter(b == "sigma",
+         c == "global_sem_sigmas")%>%
+  select(-a,-b, -e,-f,-h)%>%
+    rename(parameter = c,
+         type = d,
+         value = g)
+
+saveRDS(item_sigma, "../saves/item_sigma_dmm.rds")
+
+mixture<- model %>%
+  filter(b == "mixtureComponent")%>%
+  select(b,c,g,chain)%>%
+    rename(parameter = b,
+           type = c,
+         value = g)
+
+saveRDS(mixture, "../saves/mixture_dmm.rds")
+
+model_pred_prag <- model %>%
+  filter(a == "modelPrediction",
+         b == "devMixtureModel")%>%
+  select(-a, -h, -c)%>%
+  rename(model = b, 
+         alignment = d,
+         item = e,
+         age = f, 
+         pred = g)
+
+saveRDS(model_pred_prag, "../saves/model_pred_dmm.rds")
+
+```

### 2020-02-20 stats/model_comparison.Rmd
add model comparison
add dev mixture model

--- 2020-02-11 stats/model_comparison.Rmd
@@
 ```
+
+# Model comparison explanation
+
+```{r}
+
+d_model_comp.summarized <- d_model_comp %>% 
+  group_by(alignment, item, age) %>% 
+  summarize(n=n(), k = sum(correct))
+
+model_like <- bind_rows(
+
+  readRDS("../saves/model_pred_prag.rds") %>%
+    right_join(d_model_comp.summarized) %>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k),
+
+  readRDS("../saves/model_pred_prag_fb.rds") %>%
+    mutate(model = "fullBayes")%>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k)
+
+    ,readRDS("../saves/model_pred_mm.rds") %>%
+    mutate(model = "mixture")%>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k)
+
+      ,readRDS("../saves/model_pred_dmm.rds") %>%
+    mutate(model = "dev_mixture")%>%
+    right_join(d_model_comp.summarized)%>%
+    select(model,chain,iteration, age, alignment,item,pred, n, k)
+) %>%
+  mutate(
+    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
+  ) %>%
+  group_by(chain, model, iteration) %>%
+  summarize(total_likelihood_sample = sum(log_like))
+
+# variation across chains
+
+model_by_chain <- model_like %>%
+  na.omit(chain)%>%
+  group_by(model, chain) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  spread(model, marginal_likelihood)
+
+saveRDS(model_by_chain, "../saves/expl_model_likelihood_chain.rds")
+
+# compare models
+model_comp <- model_like %>%
+  na.omit(chain)%>%
+  group_by(model) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  spread(model, marginal_likelihood)%>%
+  mutate(fb_vs_free = fullBayes - pragmatic,
+          fb_vs_mixture= fullBayes - mixture,
+         fb_vs_dev_mixture= fullBayes - dev_mixture,
+          free_vs_mixture = pragmatic - mixture,
+         free_vs_dev_mixture = pragmatic - dev_mixture,
+         dev_mixture_vs_mixture = dev_mixture - mixture
+         ) %>%
+  select(-pragmatic, -fullBayes, -mixture, -dev_mixture) %>%
+  gather(model, logBF)
+
+saveRDS(model_comp, "../saves/expl_model_comparison.rds")
+
+```

### 2020-02-20 stats/model_sample_processing.Rmd
add dev mixture model

--- 2020-02-18 stats/model_sample_processing.Rmd
@@
 ```
+
+# developmental mixture model
+
+```{r}
+
+model <- bind_rows(
+ fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain1.csv",header = T)%>%mutate(chain = 1),
+ fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
+  fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
+  fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
+  fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
+  fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
+)
+
+# Model Parameters
+
+item_params <-  model %>%
+  filter(b == "items")%>%
+  select(-a,-b, -e, -f, -h)%>%
+    rename(item = c,
+         parameter = d,
+         value = g)
+
+saveRDS(item_params, "../saves/item_params_dmm.rds")
+
+global_params <- model %>%
+  filter(b == "parameters")%>%
+  select(-a,-b, -e,-f, -h)%>%
+    rename(parameter = c,
+         type = d,
+         value = g)
+
+saveRDS(global_params, "../saves/global_params_dmm.rds")
+
+item_sigma<- model %>%
+  filter(b == "sigma",
+         c == "global_sem_sigmas")%>%
+  select(-a,-b, -e,-f,-h)%>%
+    rename(parameter = c,
+         type = d,
+         value = g)
+
+saveRDS(item_sigma, "../saves/item_sigma_dmm.rds")
+
+mixture<- model %>%
+  filter(b == "mixtureComponent")%>%
+  select(b,c,g,chain)%>%
+    rename(parameter = b,
+           type = c,
+         value = g)
+
+saveRDS(mixture, "../saves/mixture_dmm.rds")
+
+model_pred_prag <- model %>%
+  filter(a == "modelPrediction",
+         b == "devMixtureModel")%>%
+  select(-a, -h, -c)%>%
+  rename(model = b, 
+         alignment = d,
+         item = e,
+         age = f, 
+         pred = g)
+
+saveRDS(model_pred_prag, "../saves/model_pred_dmm.rds")
+
+```

### 2020-02-20 stats/model.Rmd
update model analysis file

@@
   facet_grid(~type)+
-  xlim(0,1)+
   theme_few()
@@
 plot_mixture_dmm
+```
+
+```{r}
+
+x_dmm <- sample(1:length(unique(mixture_dmm$iteration)), 200)
+
+plot_mixture_line <- mixture_dmm%>%
+  filter(iteration %in% x_dmm) %>%
+  spread(type, value) %>%
+  expand_grid(.,age = unique(data_comb$age)) %>%
+  mutate(mixture = plogis(intercept + slope * age))
+
+ggplot() +
+  geom_line(data = plot_mixture_line, aes(x=age+2,y = mixture, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  labs(x="Age",y="Mixture (proportion me inference)")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)
 ```
@@
 
+## Likelihood
+
+```{r}
+like_chain <- readRDS("../saves/expl_model_likelihood_chain.rds")
+
+model_comp <- readRDS("../saves/expl_model_comparison.rds")%>%
+  mutate(BF = format(round(exp(logBF)),scientific=F))
+```
+
 ## Parameters
@@
   global_params_fb%>%mutate(model="fullBayes"),
-  global_params_mm%>%mutate(model="mixture")
+  global_params_mm%>%mutate(model="mixture"),
+  global_params_dmm%>%mutate(model="mixture_dev")
 )
@@
   theme_few()+
-  theme(legend.position = "bottom")
-
-```
-
-```{r}
-ggsave("../graphs/item_params_by_model.pdf", width = 8, height = 3, scale = 1.5)
+  theme(legend.position = "bottom")+
+  scale_fill_ptol()
+
+```
+
+```{r}
+ggsave("../graphs/global_params_by_model.pdf", width = 8, height = 3, scale = 1.5)
+```
+
+### Prior parameters
+
+```{r}
+
+x_prior <- sample(1:length(unique(com_global_params$iteration)), 200)
+
+plot_prior_line <- com_global_params%>%
+  filter(parameter == "prior")%>%
+  filter(iteration %in% x_prior) %>%
+  spread(type, value) %>%
+  expand_grid(.,age = unique(data_comb$age)) %>%
+  mutate(prior = plogis(intercept + slope * age))
+
+ggplot() +
+  geom_line(data = plot_prior_line, aes(x=age+2,y = prior, col = model, group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  labs(x="Age",y="Prior")+
+  theme_few() +
+  facet_grid(~model)+
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  scale_color_ptol()+
+  guides(alpha = F, fill = F, col = F)
 ```

### 2020-02-20 stats/webppl_packages/webppl-sample-writer/src/header.js
update model analysis file

@@ -1,7 +1,0 @@
-module.exports = function(env) {
-  // Header code goes here
-
-  return {
-    // Adjust exports here
-  };
-};

### 2020-02-20 stats/webppl_packages/webppl-sample-writer/src/library.js

@@ -1,35 +1,0 @@
-// regular JS goes here
-
-var fs = require('fs');
-
-function streamQueryCSV(path, header) {
-  var handle;
-  var sampleCount = 0;
-
-  function append(data) {
-    fs.appendFileSync(handle, data);
-  };
-
-  return {
-    sample(obj) {
-      if (handle === undefined) {
-        handle = fs.openSync(path, 'ax');
-        append(header + '\n');
-        // append('[');
-      }
-      _.map(_.keys(obj.value), function(v){
-        append(sampleCount + ','+ v + ',' + obj.value[v] + ',' + obj.score + '\n');
-      })
-      sampleCount += 1;
-      // append(JSON.stringify({value: obj.value, score: obj.score}));
-    },
-    finish() {
-      // append(']');
-      fs.closeSync(handle);
-    }
-  };
-}
-
-module.exports = {
-  streamQueryCSV: streamQueryCSV
-};

### 2020-03-06 paper/supplementary_material.Rmd
add experiments to supplementary file

---
title: "Word learning at the semantics pragmatics interface"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler and Michael C. Frank"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

```{r, include = F}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(langcog)
library(ggimage)
library(BayesFactor)

knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, size="small")

```

```{r data}
aoa_ratings <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)%>%
  filter(Word %in% c("carrot","duck","bread","apple","kite","horseshoe","plug","garlic","barrel","eggplant","pawn","papaya"))%>%
  mutate(mean_aoa = as.numeric(Rating.Mean),
         item = Word)%>%
  select(item,mean_aoa)

me_data <- read_csv("../data/me.csv")
prior_data <- read_csv("../data/novelty.csv")
comb_data <- read_csv("../data/combination.csv")

```

# Overview

First empirical studies. Then the general modelling framework and the pragmatic model in detail. Then we turn to results. First prediction (i.e. which model makes the best predictions about combination based on only the experiments for the individual inferences) then explanation, that is, if we use all the data that we have, how can we best explain what is happening. Here we fit the models to the combination data. We consider two hypothesis. First our pragmatic model in which the Me inference is conditional on the prior, second a mixture model in which the two inferences are computed separately and mixed by a certain ratio. We also explore a developmental mixture model in which we allow the mixture component to change with age.

# Empirical studies

## Experiment 1: Mutual exclusivity

The first experiment tested the so called mutual exclusivity inference in children between 2 and 5 years of age. The general phenomena is that when presented with a familiar and an unfamiliar object, children expect a novel word to refer to the unfamiliar object [e.g. @markman1988children]. A range of explanations have been put forward for the cogntive basis of this inference [see @lewis2020-me for a discussion]. Here, we treat the mutual exclusivity inference as pragmatic [e.g. @clark1987principle]. The inference process is specified in the model below.

The first goal of this experiment was to quantify developmental change in the age range tested. The second goal of Experiment 1 was to test the role of semantic knowledge [cf. @lewis2020-me]. The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object. That is, when the familiar object is an object for which chldren are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object. To test this, we systematically varied the familair object that was presented with the novel object.

The experiment was preregistered at https://osf.io/gy37b. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_me.html`.

### Participants

We tested a total number of `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls). Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1). All children were recruited from the floor of a Children’s museum in San José, California, USA. This population is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status. Parents consented to their children’s participation and provided demographic information. All experiments were approved by the Stanford Institutional Review Board (protocolno. 19960)

### Procedure

The experiment was presented as an interactive pricture book on a tablet computer [@frank2016using]. Figure \@ref(fig:fig1)A shows the general setup. Children saw an animal between two tables. For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to make requests. Each experiment started with two training trials in which the speaker requested a known object (car and ball).

In Experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for te purpose of the study). The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?". Children responded by touching one of the objects. The location of the novel object (left or right table) and the animal character were counterbalanced. Each child received 12 trials, one with each familiar object. The novel object also chnaged from trial to trial. We coded as correct choice if children chose the novel object as the referent of the novel word.

```{r fig1,echo = F, fig.align = "center", fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
knitr::include_graphics("../graphs/method_overview.png")
```

Each child completed 12 trials, each with a different familiar and a different novel object. Familiar objects were selected to vary along the dimension of how likely children were to know the word for each object. This including objects that most 2-year-olds could name (e.g. a duck) as well as objects that only very few 5-year-olds could name (e.g. a pawn). The selection was based on age of acquition ratings from Kuperman and colleagues [-@kuperman2012age]. While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned. Figure \@ref(fig:fig2)A shows the objects used in the experiment. We induced this variation to estimate the role of semantic knowledge in a mutual excusivity inference.

```{r, include = F}
plot_aoa_ratings <- aoa_ratings%>%
  mutate(image = paste("../experiments/kids/images/",item,".png", sep=""))

plot_aoa <- ggplot(plot_aoa_ratings, aes(x = reorder(item, mean_aoa), y = mean_aoa)) +
  geom_point(size =2, pch = 4)+
  ylab("Mean rated age of acquisition")+
  xlab("Object")+
  ylim(0,15)+
  geom_image(aes(image=image, y = mean_aoa+2), asp = 4)+
  theme_light()+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Results

```{r table1}
chance_me <- me_data %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(Mean= round(mean(unlist(correct)),2),
         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf), scientific = F),
         `Age group` = subage)%>%
  ungroup()%>%
  select(`Age group`, Mean, BayesFactor)

knitr::kable(chance_me, caption = "Proportion of children choosing the novel object compared to a level expected by chance based on a one sample Bayesian t-test. Responses are aggregated for each participant across familiar objects.", digits = 2)
```

As a first step, we evaluated whether children made a mutual exclusivity inference. For this analysis, we aggregated participants' responses across familiar objects. We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes factor (BF) in favor of the hypothesis that children chose the novel object more often than expected by chance (50% correct). Table \@ref(tab:table1) shows that all age groups made the inference.

```{r}

prior_me <- c(prior(normal(0, 10), class = Intercept),
           prior(normal(0, 10), class = b),
           prior(cauchy(0, 1), class = sd))

bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
                    data = me_data, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          prior = prior,
          cores = 4,
          chains = 4,
          iter = 5000)%>%
  saveRDS(.,"../saves/bm_me.rds")

bm_me <- readRDS("../saves/bm_me.rds")

fixef_me <- as_tibble(fixef(bm_me), rownames = "term")

ranef_me <-  ranef(bm_me)

ranef_plot_me <- as_tibble(ranef_me$item, rownames = "item")%>%
  mutate(grand_intercept = fixef_me%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_slope = fixef_me%>%filter(term=="age")%>%pull(Estimate))%>%
  group_by(item) %>%
  tidyr::expand(Estimate.Intercept,Estimate.age,grand_intercept,grand_slope, age = unique(me_data$age))%>%
  mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age+grand_slope)*age), 
         age = age+min(me_data$age_num))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

plot_me <- ggplot(ranef_plot_me, aes(x=age,y = y, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(data = me_data%>%left_join(aoa_ratings), aes(x = age_num, y = correct, col = reorder(item, mean_aoa)), width = 0, height = 0.02, alpha = .2)+
  geom_line(size = 1)+
  labs(x="Age",y="Mutual exclusivity effect")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "Object")

cor_plot_me <- as_tibble(ranef_me$item, rownames = "item") %>%
  left_join(aoa_ratings)%>%
  ggplot(., aes(x = mean_aoa, y = Estimate.Intercept))+
  geom_abline(intercept = 1, slope = -1, lty = 2, alpha = 1, size = .5)+
  geom_point(pch = 4, size = 2)+
  geom_smooth(method = "lm", col = "black", se = F, lty = 2, size = .5)+
  xlab("Rated age of acquisition")+
  ylab("Mutual exclusivity effect (model intercept)")+
  ylim(-1,1)+
  stat_cor(method = "pearson", label.x = 7, label.y = .99)+
  theme_few()
```

As a second step, we investiagted how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a] with default priors. The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`\footnote{We did not pre-register agent as a random effect, but decided to included it to be consistent with Experiment 2 and 3.}. That is, we modeled an overall slope for age (continous, anchored at the minimum) and the object specific developmental trajcetories as deviations from the overall intercept and slope (random effects). The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). Older children were more likely to make a mutual exclusivity inference. Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and shows that there was substantial variation between them. Figure \@ref(fig:fig2)C shows the correaltion between rated age of acquisition and object specific model intercept. The mutual exclusivity effect was stronger for words that were rated to be acquired earlier. Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect. Taken together, the mutual exclusivity inference depended on age as well as the familiar object.

```{r fig2, include = T, fig.align = "center", fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition. B: Developmental trajectories of mututal exclusivity effect by familiar object based on the mean of the model posterior distribution. Dots show individual datapoints. Lighter colors indicate later rated age of acquisition. Dotted line indicates a level of performance expected by chance. C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}

ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1))

```

## Experiment 2: Common ground

Here we tested children's sensitivity to common ground that is build up over the course of a conversation. In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two]. The main goal of the experiment was to measure how children's sensitivity to common grouns changes with age.

The experiment was preregistered at https://osf.io/au5hr. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_novel.html`.

### Participants

We tested `r length(unique(prior_data$subid))` children from the same general population as in Experiment 1, including `r length(unique(prior_data$subid[prior_data$subage == 2]))` 2-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 2]),2), nsmall = 2)`, 7 girls), `r length(unique(prior_data$subid[prior_data$subage == 3]))` 3-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 3]),2), nsmall = 2)`, 14 girls) and  `r length(unique(prior_data$subid[prior_data$subage == 4]))` 4-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 4]),2), nsmall = 2)`, 14 girls). Data from 5 additional children was not included because they were either exposed to less than 75% of English at home (3) or the technical equipment failed (2).

### Procedure

The general setup was the same as in Experiment 1. The speaker was positioned between the tables. There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty. Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object. Then the speaker disappeared. While the speaker was away, a second novel object appeared on the previously empty table. Then the speaker returned and requested an object in the same way as in Experiment 1 (see also Figure \@ref(fig:fig1)B). The positioning of the novel object in the beginning of the experiment as well as the location the speaker turned to first was counterbalanced. Children received five trials, each with a different pair of novel objects. We coded as correct choice if chidlren chose the object that was new to the speaker as the referent of the novel word.

### Results

```{r table2}
chance_prior <- prior_data %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage)%>%
  mutate(Mean= round(mean(unlist(correct)),2),
         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf,2), scientific = F),
         `Age group` = subage)%>%
  ungroup()%>%
  select(`Age group`, Mean, BayesFactor)

knitr::kable(chance_prior, caption = "Proportion of children choosing the object that was new to the speaker compared to a level expected by chance based on a one sample Bayesian t-test. Responses are aggregated for each participant across trials.", digits = 2)
```

Table \@ref(tab:table2) compares children's correct responses to a level expected by chance (50%). We found evidence that, as a group, 3- and 4-year-olds, but not 2-year-olds, inferred that the novel word referred to the object that was new to the speaker.

```{r}
# bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
#                     data = prior_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99, max_treedepth = 20),
#           sample_prior = F,
#           cores = 4,
#           chains = 4,
#           iter = 5000)%>%
#   saveRDS(.,"../saves/bm_cg.rds")

bm_cg <- readRDS("../saves/bm_cg.rds")

fixef_cg <- as_tibble(fixef(bm_cg), rownames = "term")

plot_cg_data <- prior_data %>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct))

plot_cg_samples <- posterior_samples(bm_cg, "^b", subset = 1:200)%>%
  mutate(sample = 1:length(b_age))%>%
  expand_grid(.,unique(prior_data$age))%>%
  mutate(age = `unique(prior_data$age)`,
         y =  plogis(b_Intercept + b_age * age))%>%
  select(-`unique(prior_data$age)`)

plot_cg_map <- as_tibble(fixef(bm_cg), rownames = "term")%>%
  select(term, Estimate)%>%
  spread(term, Estimate)%>%
  expand_grid(.,unique(prior_data$age))%>%
  mutate(slope = age, 
         age = `unique(prior_data$age)`,
         y =  plogis(Intercept + slope * age))%>%
  select(-`unique(prior_data$age)`)

plot_cg <- ggplot() +
  geom_hline(yintercept = 1/2, lty=2, size = 1)+
  geom_jitter(data = plot_cg_data,aes(x = age_num, y= correct), width = .00, height = .01, alpha = .5)+
  geom_line(data = plot_cg_samples, aes(x = age+min(prior_data$age_num), y = y, group = sample), size = .025)+
  geom_line(data = plot_cg_map, aes(x =age+min(prior_data$age_num), y = y), size = 1)+
  labs(x="Age",y="Proportion object new to speaker chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)

```

To directly investiagte whether children's response changed with age, we modeled the trial by trial data using a Bayesian GLMM (formula: `correct ~ age + (1 | id) + (age | speaker)`, specifications see [Experiment 1](#experiment-1-mutual-exclusivity)). The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_cg%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_cg%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_cg%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`, see Figure \@ref(fig:fig3)). Older children were more likely to chose the object that was new to the speaker as the referent of the novel word, suggesting that the sensitivity to common ground in this context increases with age.

## Experiment 3: Combination

Experiment 3 combined the procedures from Experiment 1 and 2. As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but alo the role that each object (novel and familiar) had played in the preceeding interaction. Combining the two procedures created two conditions: In the *congruent* condition, the novel object was also the object that was new to the speaker. In this case, the mutual exclusivity inference as well as the common ground inference pointed to the novel object as the referent. In the *incongurent condition*, the familiar object was new to the speaker. Int his case, the two inferences pointed to different objects. The main focus of the overall study was to model how children integrate and balance these different inforamtion sources. We investigate this question in depth in the [modelling](#model) section below. Here, we limit the discussion to whether children differentiated between the two conditions.

The experiment was preregistered at https://osf.io/4nm8g. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_combination.html`.

### Participants

We tested `r length(unique(comb_data$subid))` children from the same general population as in Experiment 1 and 2, including `r length(unique(comb_data$subid[comb_data$subage == 2]))` 2-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 2]),2), nsmall = 2)`, 7 girls), `r length(unique(comb_data$subid[comb_data$subage == 3]))` 3-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 3]),2), nsmall = 2)`, 14 girls) and  `r length(unique(comb_data$subid[comb_data$subage == 4]))` 4-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 4]),2), nsmall = 2)`, 14 girls). Data from 20 additional children was not included because they were either exposed to less than 75% of English at home (15), did not finish at least half of the test trials (3) or the technical equipment failed (2).

### Procedure

### Results

```{r}

prior_comb <- c(prior(normal(0, 5), class = Intercept),
           prior(normal(0, 5), class = b),
           prior(cauchy(0, 1), class = sd))

bm_comb <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | item)+ (age * alignment | agent),
                    data = comb_data, family = bernoulli(),
          control = list(adapt_delta = 0.99, max_treedepth = 20),
          sample_prior = F,
          prior = prior_comb,
          cores = 4,
          chains = 4,
          inits = 0,
          iter = 5000)%>%
  saveRDS(.,"../saves/bm_comb.rds")

bm_comb <- readRDS("../saves/bm_comb.rds")

fixef_comb <- as_tibble(fixef(bm_comb), rownames = "term")

ranef_comb <-  ranef(bm_comb)

plot_comb_map <- bind_rows(
  as_tibble(ranef_comb$item, rownames = "item")%>%
  mutate(condition = "congruent",
         condition_code = 0),
  as_tibble(ranef_comb$item, rownames = "item")%>%
  mutate(condition = "incongruent",
         condition_code = 1))%>%
  mutate(grand_intercept = fixef_comb%>%filter(term=="Intercept")%>%pull(Estimate),
         grand_age = fixef_comb%>%filter(term=="age")%>%pull(Estimate),
         grand_cond = fixef_comb%>%filter(term=="alignmentincongruent")%>%pull(Estimate),
         grand_intact = fixef_comb%>%filter(term=="age:alignmentincongruent")%>%pull(Estimate))%>%
  group_by(item, condition, condition_code)%>%
  expand_grid(. ,age = unique(comb_data$age))%>%
  mutate(y = plogis(grand_intercept + 
                      Estimate.Intercept +
                      grand_cond * condition_code +
                      Estimate.alignmentincongruent * condition_code +
                      grand_age * age +
                      Estimate.age * age +
                      grand_intact * (condition_code * age) +
                      `Estimate.age:alignmentincongruent` * (condition_code * age)),
         age = age+min(comb_data$age_num))%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

plot_comb <- ggplot(plot_comb_map, aes(x=age,y = y, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(data = comb_data%>%left_join(aoa_ratings)%>%ungroup()%>%mutate(item = fct_reorder(factor(item), mean_aoa)), aes(x = age_num, y= correct, col = item), width = .00, height = .04, alpha = .2)+
  geom_line(size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(~condition)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")

```

```{r fig3, include = T, fig.align = "center", fig.cap = "Proportion of choosing the object that was new to the speaker by age. Dots show the mean response for each participant. The solid black line shows the developmental trajectory based on the mean of the model posterior distribution. Lighter lines show 200 random draws from the posterior distribution to depict uncertainty. Dotted line indicates a level of performance expected by chance.", fig.width=12, fig.height = 4}
ggarrange(plot_cg, plot_comb,  labels = c("A","B"), nrow = 1, widths = c(1,2))
```

Comparison to chance not meaningful

# Model

## loci of development

Semantic Knowledge, Speaker Optimality, Prior sensitivity. Each correspond to an age sensitive parameter in our model. That is they change as a function of age. We assume that the integration process remains constant over time.

### Semantic knowledge

### Expectations about speaker informativeness

### Sensitivity to common ground

## Prediction

Estimate parameters based on me data and prior data. The models considered belwo make differential use of theses parameters. Basically, one full model and the rest are lesion model

### Pragmatic model

[overview fig, all model parameters for all models]

### No word

semantic knowledge is only a function of age and not specific to the item. Roughyl corresponds to. If children are vaguely familiar with an object, the make the ME inference regardless of the individual object

### Model comparison

range of log like accross chains and then model comparison

## Explanation

### Pragmatic model

### Model comparison

[overview fig, correlations for all models]

# Discussion

### 2020-03-06 stats/model.Rmd
add experiments to supplementary file

@@
 library(bigmemory)
-#library(langcog)
+library(langcog)
 
@@
 
-x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 100)
-
-plot_model_prag_line_fb <- model_pred_prag_fb%>%
+x_fb <- sample(1:20000, 50)
+
+plot_model_prag_line_fb <- readRDS("../saves/model_pred_prag_fb.rds")%>%
   filter(iteration %in% x_fb)%>%
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(data = plot_model_prag_line_fb, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  geom_jitter(data = data_comb, aes(x = age_num, y = correct), alpha = .1, height = .025, width = 0)+
+  geom_line(data = plot_model_prag_line_fb, aes(x=age+2,y = pred, col = alignment, group = interaction(alignment,chain,iteration)),size = .2, alpha = .2)+
+  geom_pointrange(data = binned_data, aes(x = subage+0.5, y = data_mean, ymin = data_ci_lower, ymax = data_ci_upper), pch = 5)+
+    geom_line(data = binned_data, aes(x = subage+0.5, y = data_mean))+
+ # geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct, col = alignment, lty = alignment), method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5, span = 1)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.09,1.09)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol()+
+  theme(legend.position = "bottom")
+
+```
+
+```{r}
+ggsave("../graphs/pred_.pdf", width = 10, height = 3, scale = 1)
+```
+
+## Correlate model predictions and data
+
+```{r}
+binned_data <- data_comb%>%
+  group_by(subage, alignment, item)%>%
+  summarize(k = sum(correct), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         data_mean = (a-1)/(a+b-2),
+         data_ci_lower  = qbeta(.025, a, b),
+         data_ci_upper = qbeta(.975, a, b),
+         age = factor(subage))%>%
+  select(-a,-b,-n,-k)
+
+cor_prag_fb <- readRDS("../saves/model_pred_prag_fb.rds")%>%
+  mutate(age = as.numeric(age) + min(data_comb$age_num),
+         age = cut(age,
+                      breaks = c(2,3,4,5),
+                      labels = c(2,3,4)))%>%
+  group_by(model,alignment, item, age)%>%
+  summarise(model_mean = estimate_mode(pred),
+            model_ci_lower = hdi_lower(pred),
+            model_ci_upper = hdi_upper(pred))
+
+plot_cor_model_pred_fb <- cor_prag_fb %>%
+  left_join(binnned_data)
+
+ggplot(data = plot_cor_model_pred_fb,aes(x = model_mean, y = data_mean, col = alignment)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
+  geom_point(size = 1.5, stroke = 1, pch = 5)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(~age)+
+  theme_few() + 
+  scale_colour_ptol(name ="Alignment")+
+  guides(col = F)
+```
+
+```{r}
+ggsave("../graphs/cor_model_data.pdf", width = 8, height = 3.5, scale = 1)
+```
+
+# Mixture model
+
+```{r}
+
+item_params_mm <- readRDS("../saves/item_params_mm.rds")
+
+global_params_mm <- readRDS("../saves/global_params_mm.rds")
+
+item_sigma_mm <- readRDS("../saves/item_sigma_mm.rds")
+
+mixture_mm <- readRDS("../saves/mixture_mm.rds")
+
+#### summaries
+item_params_summary_mm <- item_params_mm %>%
+  group_by(item, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+global_params_summary_mm <- global_params_mm %>%
+  group_by (parameter,type)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+```
+## Plotting model parameters
+
+### Semantic knowledge
+
+```{r}
+plot_item_params_mm <- ggplot(item_params_mm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(parameter ~ item, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
+
+plot_item_params_mm
+```
+
+```{r}
+#ggsave("../graphs/item_params_by_chain.pdf", width = 8, height = 3, scale = 1.5)
+```
+
+### Global parameters
+
+```{r}
+
+plot_global_params_mm <- ggplot(global_params_mm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")
+
+plot_global_params_mm
+```
+
+### Global sigmas
+
+```{r}
+plot_item_sigma_mm <- ggplot(item_sigma_mm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Sigma")+
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()
+
+plot_item_sigma_mm
+```
+
+### Mixture
+
+```{r}
+plot_mixture_mm <- ggplot(mixture_mm, aes(x = p_informative, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("p_informative")+
+  xlim(0,1)+
+  theme_few()
+
+plot_mixture_mm
+```
+
+## Plotting semantic knowledge
+
+```{r}
+plot_sem_know_mm <- item_params_summary_mm%>%
+  select(-uci,-lci)%>%
+  spread(parameter, -item) %>%
+  left_join(expand.grid(
+      age = unique(me_model_data$age),
+      item = unique(me_model_data$item)), .) %>%
+  mutate(sem_know = plogis(intercept + slope * age)) %>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+ggplot(plot_sem_know_mm, aes(x = age+2, y= sem_know, col = item, group = item))+
+  geom_line(size = 1)+
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_few()+
+  scale_colour_viridis_d(name = "familiar object")
+```
+
+## Plotting model predictions
+
+```{r}
+model_pred_mm <- readRDS("../saves/model_pred_mm.rds")
+
+plot_model_pred_mm <- model_pred_mm%>%
+  group_by(alignment, item, age)%>%
+  summarise(mean = estimate_mode(pred),
+            ci_lower = hdi_lower(pred),
+            ci_upper = hdi_upper(pred))
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
+  geom_line(data = plot_model_pred_mm, aes(x=age+2,y = mean, col = alignment), size = 1)+
+  geom_ribbon(data = plot_model_pred_mm, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)+ 
+  scale_colour_ptol()+
+  scale_fill_ptol()
+
+x_mm <- sample(1:length(unique(model_pred_mm$iteration)), 200)
+
+model_pred_mm_line_mm <- model_pred_mm%>%
+  filter(iteration %in% x_mm)%>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+ggplot() +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_line(data = model_pred_mm, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
   geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
@@
 ```{r}
-ggsave("../graphs/pred_.pdf", width = 10, height = 3, scale = 1)
+ggsave("../graphs/pred_mm_model_data.pdf", width = 10, height = 3, scale = 1)
 ```
@@
 
-cor_prag_fb <- readRDS("../saves/model_pred_prag_fb.rds")%>%
+cor_mix_mm <- readRDS("../saves/model_pred_mm.rds")%>%
   mutate(age = as.numeric(age) + min(data_comb$age_num),
@@
 
-plot_cor_model_pred_fb <- cor_prag_fb %>%
+plot_cor_model_pred_mm <- cor_mix_mm %>%
   left_join(binnned_data)
 
-ggplot(data = plot_cor_model_pred_fb,aes(x = model_mean, y = data_mean, col = alignment)) +
+ggplot(data = plot_cor_model_pred_mm,aes(x = model_mean, y = data_mean, col = alignment)) +
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
@@
 ```{r}
-ggsave("../graphs/cor_model_data.pdf", width = 8, height = 3.5, scale = 1)
-```
-
-# Mixture model
-
-```{r}
-
-item_params_mm <- readRDS("../saves/item_params_mm.rds")
-
-global_params_mm <- readRDS("../saves/global_params_mm.rds")
-
-item_sigma_mm <- readRDS("../saves/item_sigma_mm.rds")
-
-mixture_mm <- readRDS("../saves/mixture_mm.rds")
+ggsave("../graphs/cor_model_data_mm.pdf", width = 8, height = 3.5, scale = 1)
+```
+
+# Developmental Mixture model
+
+```{r}
+
+item_params_dmm <- readRDS("../saves/item_params_dmm.rds")
+
+global_params_dmm <- readRDS("../saves/global_params_dmm.rds")
+
+item_sigma_dmm <- readRDS("../saves/item_sigma_dmm.rds")
+
+mixture_dmm <- readRDS("../saves/mixture_dmm.rds")
 
 #### summaries
-item_params_summary_mm <- item_params_mm %>%
+item_params_summary_dmm <- item_params_dmm %>%
   group_by(item, parameter)%>%
@@
 
-global_params_summary_mm <- global_params_mm %>%
+global_params_summary_dmm <- global_params_dmm %>%
   group_by (parameter,type)%>%
@@
 ```{r}
-plot_item_params_mm <- ggplot(item_params_mm, aes(x = value, fill = factor(chain)))+
+plot_item_params_dmm <- ggplot(item_params_dmm, aes(x = value, fill = factor(chain)))+
   geom_density(alpha = 0.3)+
@@
 
-plot_item_params_mm
+plot_item_params_dmm
 ```
@@
 
-plot_global_params_mm <- ggplot(global_params_mm, aes(x = value, fill = factor(chain)))+
+plot_global_params_dmm <- ggplot(global_params_dmm, aes(x = value, fill = factor(chain)))+
   geom_density(alpha = 0.3)+
@@
 
-plot_global_params_mm
+plot_global_params_dmm
 ```
@@
 ```{r}
-plot_item_sigma_mm <- ggplot(item_sigma_mm, aes(x = value, fill = factor(chain)))+
+plot_item_sigma_dmm <- ggplot(item_sigma_dmm, aes(x = value, fill = factor(chain)))+
   geom_density(alpha = 0.3)+
@@
 
-plot_item_sigma_mm
+plot_item_sigma_dmm
 ```
@@
 ```{r}
-plot_mixture_mm <- ggplot(mixture_mm, aes(x = p_informative, fill = factor(chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("p_informative")+
-  xlim(0,1)+
+plot_mixture_dmm <- ggplot(mixture_dmm, aes(x = value, fill = factor(chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("value")+
+  facet_grid(~type)+
   theme_few()
 
-plot_mixture_mm
+plot_mixture_dmm
+```
+
+```{r}
+
+x_dmm <- sample(1:length(unique(mixture_dmm$iteration)), 200)
+
+plot_mixture_line <- mixture_dmm%>%
+  filter(iteration %in% x_dmm) %>%
+  spread(type, value) %>%
+  expand_grid(.,age = unique(data_comb$age)) %>%
+  mutate(mixture = plogis(intercept + slope * age))
+
+ggplot() +
+  geom_line(data = plot_mixture_line, aes(x=age+2,y = mixture, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  labs(x="Age",y="Mixture (proportion me inference)")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)
 ```
@@
 ```{r}
-plot_sem_know_mm <- item_params_summary_mm%>%
+plot_sem_know_dmm <- item_params_summary_dmm%>%
   select(-uci,-lci)%>%
@@
 
-ggplot(plot_sem_know_mm, aes(x = age+2, y= sem_know, col = item, group = item))+
+ggplot(plot_sem_know_dmm, aes(x = age+2, y= sem_know, col = item, group = item))+
   geom_line(size = 1)+
@@
 ```{r}
-model_pred_mm <- readRDS("../saves/model_pred_mm.rds")
-
-plot_model_pred_mm <- model_pred_mm%>%
+model_pred_dmm <- readRDS("../saves/model_pred_dmm.rds")
+
+plot_model_pred_dmm <- model_pred_dmm%>%
   group_by(alignment, item, age)%>%
@@
   geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = plot_model_pred_mm, aes(x=age+2,y = mean, col = alignment), size = 1)+
-  geom_ribbon(data = plot_model_pred_mm, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
+  geom_line(data = plot_model_pred_dmm, aes(x=age+2,y = mean, col = alignment), size = 1)+
+  geom_ribbon(data = plot_model_pred_dmm, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
   labs(x="Age",y="Mutual Exclusivity effect")+
@@
 
-x_mm <- sample(1:length(unique(model_pred_mm$iteration)), 200)
-
-model_pred_mm_line_mm <- model_pred_mm%>%
-  filter(iteration %in% x_mm)%>%
+x_dmm <- sample(1:length(unique(model_pred_dmm$iteration)), 200)
+
+model_pred_line_dmm <- model_pred_dmm%>%
+  filter(iteration %in% x_dmm)%>%
   left_join(aoa_ratings) %>%
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(data = model_pred_mm, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  geom_line(data = model_pred_line_dmm, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
   geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
@@
 
-cor_mix_mm <- readRDS("../saves/model_pred_mm.rds")%>%
-  mutate(age = as.numeric(age) + min(data_comb$age_num),
-         age = cut(age,
-                      breaks = c(2,3,4,5),
-                      labels = c(2,3,4)))%>%
-  group_by(model,alignment, item, age)%>%
-  summarise(model_mean = estimate_mode(pred),
-            model_ci_lower = hdi_lower(pred),
-            model_ci_upper = hdi_upper(pred))
-
-plot_cor_model_pred_mm <- cor_mix_mm %>%
-  left_join(binnned_data)
-
-ggplot(data = plot_cor_model_pred_mm,aes(x = model_mean, y = data_mean, col = alignment)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
-  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
-  geom_point(size = 1.5, stroke = 1, pch = 5)+
-  coord_fixed()+
- stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  ylab("Data")+
-  facet_grid(~age)+
-  theme_few() + 
-  scale_colour_ptol(name ="Alignment")+
-  guides(col = F)
-```
-
-```{r}
-ggsave("../graphs/cor_model_data_mm.pdf", width = 8, height = 3.5, scale = 1)
-```
-
-# Developmental Mixture model
-
-```{r}
-
-item_params_dmm <- readRDS("../saves/item_params_dmm.rds")
-
-global_params_dmm <- readRDS("../saves/global_params_dmm.rds")
-
-item_sigma_dmm <- readRDS("../saves/item_sigma_dmm.rds")
-
-mixture_dmm <- readRDS("../saves/mixture_dmm.rds")
-
-#### summaries
-item_params_summary_dmm <- item_params_dmm %>%
-  group_by(item, parameter)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
-global_params_summary_dmm <- global_params_dmm %>%
-  group_by (parameter,type)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
-```
-## Plotting model parameters
-
-### Semantic knowledge
-
-```{r}
-plot_item_params_dmm <- ggplot(item_params_dmm, aes(x = value, fill = factor(chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Parameter")+
-  facet_grid(parameter ~ item, scales = 'free')+
-  theme_few()+
-  theme(legend.position = "bottom")
-
-plot_item_params_dmm
-```
-
-```{r}
-#ggsave("../graphs/item_params_by_chain.pdf", width = 8, height = 3, scale = 1.5)
-```
-
-### Global parameters
-
-```{r}
-
-plot_global_params_dmm <- ggplot(global_params_dmm, aes(x = value, fill = factor(chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Parameter")+
-  facet_grid(type ~ parameter, scales = 'free')+
-  theme_few()+
-  theme(legend.position = "bottom")
-
-plot_global_params_dmm
-```
-
-### Global sigmas
-
-```{r}
-plot_item_sigma_dmm <- ggplot(item_sigma_dmm, aes(x = value, fill = factor(chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("Sigma")+
-  facet_grid(type ~ parameter, scales = 'free')+
-  theme_few()
-
-plot_item_sigma_dmm
-```
-
-### Mixture
-
-```{r}
-plot_mixture_dmm <- ggplot(mixture_dmm, aes(x = value, fill = factor(chain)))+
-  geom_density(alpha = 0.3)+
-  xlab("value")+
-  facet_grid(~type)+
-  theme_few()
-
-plot_mixture_dmm
-```
-
-```{r}
-
-x_dmm <- sample(1:length(unique(mixture_dmm$iteration)), 200)
-
-plot_mixture_line <- mixture_dmm%>%
-  filter(iteration %in% x_dmm) %>%
-  spread(type, value) %>%
-  expand_grid(.,age = unique(data_comb$age)) %>%
-  mutate(mixture = plogis(intercept + slope * age))
-
-ggplot() +
-  geom_line(data = plot_mixture_line, aes(x=age+2,y = mixture, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .1)+
-  labs(x="Age",y="Mixture (proportion me inference)")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F)
-```
-
-## Plotting semantic knowledge
-
-```{r}
-plot_sem_know_dmm <- item_params_summary_dmm%>%
-  select(-uci,-lci)%>%
-  spread(parameter, -item) %>%
-  left_join(expand.grid(
-      age = unique(me_model_data$age),
-      item = unique(me_model_data$item)), .) %>%
-  mutate(sem_know = plogis(intercept + slope * age)) %>%
-  left_join(aoa_ratings) %>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-ggplot(plot_sem_know_dmm, aes(x = age+2, y= sem_know, col = item, group = item))+
-  geom_line(size = 1)+
-  ylab("Semantic knowledge")+
-  xlab("Age")+
-  ylim(0,1)+
-  theme_few()+
-  scale_colour_viridis_d(name = "familiar object")
-```
-
-## Plotting model predictions
-
-```{r}
-model_pred_dmm <- readRDS("../saves/model_pred_dmm.rds")
-
-plot_model_pred_dmm <- model_pred_dmm%>%
-  group_by(alignment, item, age)%>%
-  summarise(mean = estimate_mode(pred),
-            ci_lower = hdi_lower(pred),
-            ci_upper = hdi_upper(pred))
-
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
-  geom_line(data = plot_model_pred_dmm, aes(x=age+2,y = mean, col = alignment), size = 1)+
-  geom_ribbon(data = plot_model_pred_dmm, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = alignment), alpha = .4) +
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(alignment~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F)+ 
-  scale_colour_ptol()+
-  scale_fill_ptol()
-
-x_dmm <- sample(1:length(unique(model_pred_dmm$iteration)), 200)
-
-model_pred_line_dmm <- model_pred_dmm%>%
-  filter(iteration %in% x_dmm)%>%
-  left_join(aoa_ratings) %>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-ggplot() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_line(data = model_pred_line_dmm, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
-  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(alignment~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F, col = F)+ 
-  scale_colour_ptol(name = NULL)
-
-```
-
-```{r}
-ggsave("../graphs/pred_mm_model_data.pdf", width = 10, height = 3, scale = 1)
-```
-
-## Correlate model predictions and data
-
-```{r}
-binnned_data <- data_comb%>%
-  group_by(subage, alignment, item)%>%
-  summarize(k = sum(correct), n = n())%>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         data_mean = (a-1)/(a+b-2),
-         data_ci_lower  = qbeta(.025, a, b),
-         data_ci_upper = qbeta(.975, a, b),
-         age = factor(subage))%>%
-  select(-a,-b,-n,-k)
-
 cor_mix_dmm <- readRDS("../saves/model_pred_dmm.rds")%>%
@@
   item_params%>%mutate(model="pragmatic"),
-  item_params_fb%>%mutate(model="fullBayes")
+  item_params_fb%>%mutate(model="fullBayes"),
+  item_params_mm%>%mutate(model="mixture"),
+  item_params_dmm%>%mutate(model="mixture_dev")
 )
@@
   theme_few()+
-  theme(legend.position = "bottom")
-
+  theme(legend.position = "bottom")+
+  scale_fill_ptol()
+
+```
+
+```{r}
+ggsave("../graphs/comparison_item_params.pdf", width = 12, height = 8, scale = 1.5)
 ```
@@
 
+### Global sigmas
+
+```{r}
+
+com_global_sigmas <- bind_rows(
+  item_sigma%>%mutate(model="pragmatic"),
+  item_sigma_fb%>%mutate(model="fullBayes"),
+  item_sigma_mm%>%mutate(model="mixture"),
+  item_sigma_dmm%>%mutate(model="mixture_dev")
+)
+
+ggplot(com_global_sigmas, aes(x = value, fill = model, group = paste(model,chain)))+
+  geom_density(alpha = 0.3)+
+  xlab("Parameter")+
+  facet_grid(type ~ ., scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")+
+  scale_fill_ptol()
+```
+
 ## Model predictions

### 2020-03-06 paper/supplementary_material.Rmd
prep model priors

@@
 
-prior_me <- c(prior(normal(0, 10), class = Intercept),
-           prior(normal(0, 10), class = b),
+prior_me <- c(prior(normal(0, 5), class = Intercept),
+           prior(normal(0, 5), class = b),
            prior(cauchy(0, 1), class = sd))
@@
           sample_prior = F,
-          prior = prior,
+          prior = prior_me,
           cores = 4,
@@
 ```{r}
-# bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
-#                     data = prior_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99, max_treedepth = 20),
-#           sample_prior = F,
-#           cores = 4,
-#           chains = 4,
-#           iter = 5000)%>%
-#   saveRDS(.,"../saves/bm_cg.rds")
+prior_cg <- c(prior(normal(0, 5), class = Intercept),
+           prior(normal(0, 5), class = b),
+           prior(cauchy(0, 1), class = sd))
+
+bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
+                    data = prior_data, family = bernoulli(),
+          control = list(adapt_delta = 0.99, max_treedepth = 20),
+          sample_prior = F,
+          prior = prior_cg,
+          cores = 4,
+          chains = 4,
+          iter = 5000)%>%
+  saveRDS(.,"../saves/bm_cg.rds")
 
@@
 ### Procedure
+
+Experiment 3 follwed the same procedure as Experiment 2 but involved the same objects as Experiment 1.
+In the beginning, one table was empty while there was an object (novel or familiar) on the other one.
+After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or novel).
+Next, the speaker re-appeared and made the usual request.
+
+In the congruent condition, the familair object was present in the beginning and the novel object appeared while the speaker was away (Figure \@ref(fig:fig1)C - left).
+In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent.
+In the incongruent condition, the novel object was present in the beginning and the familair object appeared while the speaker was away.
+In this case, the two inferences pointed to different objects (Figure \@ref(fig:fig1)C - right).
+
+Participants received up to 12 test trials, e
 

### 2020-03-10 paper/supplementary_material.Rmd
move supplement forward

--- 2020-03-06 paper/supplementary_material.Rmd
@@
 
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+
 knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, size="small")
@@
 First prediction (i.e.
-which model makes the best predictions about combination based on only the experiments for the individual inferences) then explanation, that is, if we use all the data that we have, how can we best explain what is happening.
-Here we fit the models to the combination data.
+which model makes the best predictions about integration based on only the experiments for the individual inferences) then explanation, that is, if we use all the data that we have, how can we best explain what is happening.
+Here we fit the models to the integration data.
 We consider two hypothesis.
@@
 @markman1988children].
-A range of explanations have been put forward for the cogntive basis of this inference [see @lewis2020-me for a discussion].
+A range of explanations have been put forward for the cognitive basis of this inference [see @lewis2020-me for a discussion].
 Here, we treat the mutual exclusivity inference as pragmatic [e.g.
@@
 The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object.
-That is, when the familiar object is an object for which chldren are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object.
-To test this, we systematically varied the familair object that was presented with the novel object.
+That is, when the familiar object is an object for which children are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object.
+To test this, we systematically varied the familiar object that was presented with the novel object.
 
@@
 Parents consented to their children’s participation and provided demographic information.
-All experiments were approved by the Stanford Institutional Review Board (protocolno.
+All experiments were approved by the Stanford Institutional Review Board (protocol no.
 19960)
@@
 
-The experiment was presented as an interactive pricture book on a tablet computer [@frank2016using].
+The experiment was presented as an interactive picture book on a tablet computer [@frank2016using].
 Figure \@ref(fig:fig1)A shows the general setup.
@@
 
-In Experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for te purpose of the study).
+In Experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study).
 The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?".
@@
 Each child received 12 trials, one with each familiar object.
-The novel object also chnaged from trial to trial.
+The novel object also changed from trial to trial.
 We coded as correct choice if children chose the novel object as the referent of the novel word.
@@
 a pawn).
-The selection was based on age of acquition ratings from Kuperman and colleagues [-@kuperman2012age].
+The selection was based on age of acquisition ratings from Kuperman and colleagues [-@kuperman2012age].
 While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned.
 Figure \@ref(fig:fig2)A shows the objects used in the experiment.
-We induced this variation to estimate the role of semantic knowledge in a mutual excusivity inference.
+We induced this variation to estimate the role of semantic knowledge in a mutual exclusivity inference.
 
@@
 
-prior_me <- c(prior(normal(0, 10), class = Intercept),
-           prior(normal(0, 10), class = b),
-           prior(cauchy(0, 1), class = sd))
-
-bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
-                    data = me_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99, max_treedepth = 20),
-          sample_prior = F,
-          prior = prior,
-          cores = 4,
-          chains = 4,
-          iter = 5000)%>%
-  saveRDS(.,"../saves/bm_me.rds")
+# prior_me <- c(prior(normal(0, 5), class = Intercept),
+#            prior(normal(0, 5), class = b),
+#            prior(cauchy(0, 1), class = sd))
+# 
+# 
+# bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
+#                     data = me_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99, max_treedepth = 20),
+#           sample_prior = F,
+#           prior = prior_me,
+#           cores = 4,
+#           chains = 4,
+#           iter = 5000)%>%
+#   saveRDS(.,"../saves/bm_me.rds")
 
@@
 
-As a second step, we investiagted how the inference changed as a function of age and the familiar object.
+talk about sd around item as evidence for variation
+
+As a second step, we investigated how the inference changed as a function of age and the familiar object.
 We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM).
-We used the function `brm` from the package `brms` [@R-brms_a] with default priors.
+We used the function `brm` from the package `brms` [@R-brms_a].
+As priors we used `normal(0,5)` for fixed effects and `cauchy(0,1)` for standard deviations of random effects\footnote{We pre-registered the use of default priors in all models.
+However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent.}.
 The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`\footnote{We did not pre-register agent as a random effect, but decided to included it to be consistent with Experiment 2 and 3.}.
-That is, we modeled an overall slope for age (continous, anchored at the minimum) and the object specific developmental trajcetories as deviations from the overall intercept and slope (random effects).
+That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects).
 The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`).
@@
 Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and shows that there was substantial variation between them.
-Figure \@ref(fig:fig2)C shows the correaltion between rated age of acquisition and object specific model intercept.
+Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept.
 The mutual exclusivity effect was stronger for words that were rated to be acquired earlier.
@@
 In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two].
-The main goal of the experiment was to measure how children's sensitivity to common grouns changes with age.
+The main goal of the experiment was to measure how children's sensitivity to common ground changes with age.
 
@@
 Children received five trials, each with a different pair of novel objects.
-We coded as correct choice if chidlren chose the object that was new to the speaker as the referent of the novel word.
+We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.
 
@@
 ```{r}
+# prior_cg <- c(prior(normal(0, 5), class = Intercept),
+#            prior(normal(0, 5), class = b),
+#            prior(cauchy(0, 1), class = sd))
+# 
+# 
 # bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
@@
 #           sample_prior = F,
+#           prior = prior_cg,
 #           cores = 4,
@@
 
-To directly investiagte whether children's response changed with age, we modeled the trial by trial data using a Bayesian GLMM (formula: `correct ~ age + (1 | id) + (age | speaker)`, specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).
-The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_cg%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_cg%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_cg%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`, see Figure \@ref(fig:fig3)).
+To directly investigate whether children's response changed with age, we modeled the trial by trial data using a Bayesian GLMM (formula: `correct ~ age + (1 | id) + (age | speaker)`, specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).
+The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_cg%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_cg%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_cg%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`, see Figure \@ref(fig:fig3)A).
 Older children were more likely to chose the object that was new to the speaker as the referent of the novel word, suggesting that the sensitivity to common ground in this context increases with age.
 
-## Experiment 3: Combination
+## Experiment 3: Integration
 
 Experiment 3 combined the procedures from Experiment 1 and 2.
-As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but alo the role that each object (novel and familiar) had played in the preceeding interaction.
+As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but also the role that each object (novel and familiar) had played in the preceding interaction.
 Combining the two procedures created two conditions: In the *congruent* condition, the novel object was also the object that was new to the speaker.
@@
 Int his case, the two inferences pointed to different objects.
-The main focus of the overall study was to model how children integrate and balance these different inforamtion sources.
+The main focus of the overall study was to model how children integrate and balance these different information sources.
 We investigate this question in depth in the [modelling](#model) section below.
@@
 
+Experiment 3 followed the same procedure as Experiment 2 but involved the same objects as Experiment 1.
+In the beginning, one table was empty while there was an object (novel or familiar) on the other one.
+After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or novel).
+Next, the speaker re-appeared and made the usual request.
+
+In the congruent condition, the familiar object was present in the beginning and the novel object appeared while the speaker was away (Figure \@ref(fig:fig1)C - left).
+In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent.
+In the incongruent condition, the novel object was present in the beginning and the familiar object appeared later.
+In this case, the two inferences pointed to different objects (Figure \@ref(fig:fig1)C - right).
+
+Participants received up to 12 test trials, six in each condition, each with a different familiar and novel object.
+Familiar objects were the same as in Experiment 1.
+The positioning of the objects on the tables and the location the speaker first turned to were counterbalanced.
+Participants could stop the experiment after six trials (three per condition).
+If a participant stopped after half of the trials, we tested an additional participant to reach a pre-registered number of data points per cell.
+
 ### Results
+
+All results are reported from the perspective of the mutual exclusivity inference (`correct` in the model formula below).
+In the incongruent condition, high proportions speak to a mutual exclusivity inference and low proportion for a common ground inference.
+In the congruent condition, both inferences pointed in the same direction.
+The focus of this experiment was on information integration and we therefore did not compare the performance to chance.
 
@@
 
-prior_comb <- c(prior(normal(0, 5), class = Intercept),
-           prior(normal(0, 5), class = b),
-           prior(cauchy(0, 1), class = sd))
-
-bm_comb <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | item)+ (age * alignment | agent),
-                    data = comb_data, family = bernoulli(),
-          control = list(adapt_delta = 0.99, max_treedepth = 20),
-          sample_prior = F,
-          prior = prior_comb,
-          cores = 4,
-          chains = 4,
-          inits = 0,
-          iter = 5000)%>%
-  saveRDS(.,"../saves/bm_comb.rds")
+# prior_comb <- c(prior(normal(0, 5), class = Intercept),
+#            prior(normal(0, 5), class = b),
+#            prior(cauchy(0, 1), class = sd))
+# 
+# bm_comb <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | item)+ (age * alignment | agent),
+#                     data = comb_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99, max_treedepth = 20),
+#           sample_prior = F,
+#           prior = prior_comb,
+#           cores = 4,
+#           chains = 4,
+#           inits = 0,
+#           iter = 5000)%>%
+#   saveRDS(.,"../saves/bm_comb.rds")
 
@@
   guides(alpha = F)+ 
-  scale_colour_viridis_d(name = "familiar object")
+  scale_colour_viridis_d(name = "Object")
 
 ```
+
+Use sd on item to say tha items vary substantially and sd on interaction or age to say they differ in their slope
+
+We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | item) + (age * alignment | agent)`\footnote{We pre-registered to include item as a fixed effect in Experiment 3.
+The corresponding model was too complex to be constrained by the data.
+Furthermore, as explained in Experiment 1, items were chosen based on their rated age of acquisition.
+That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge.}, specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).
+The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`).
+The incongruent condition had a strong negative impact (*$\beta$* = `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q97.5)%>%round(2)`), showing that children differentiated between the two conditions.
+The interaction term was weakly - though not entirely - negative, suggesting a shallower slope for age in the incongruent condition (*$\beta$* = `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q97.5)%>%round(2)`).
+Figure \@ref(fig:fig3)B visualizes the model.
+Taken together, the results show that children responded to the way the two inferences were aligned with one another.
+For the remainder of the study, we address the question of how the two inferences might have interacted with one another.
 
@@
 
-Comparison to chance not meaningful
-
 # Model
 
-## loci of development
+The main purpose of the study was to study *how* children integrate different information sources during word learning.
+To address this question, we use Bayesian cognitive models of prgamatic reasoning.
+We first describe an *integration model* which we think best represents the inference and integration processes.
+We then specify how this model captures developmental change.
 
-Semantic Knowledge, Speaker Optimality, Prior sensitivity.
-Each correspond to an age sensitive parameter in our model.
-That is they change as a function of age.
-We assume that the integration process remains constant over time.
+Next, we ask how well this model *predicts* how children integrate the two information sources.
+That is, in a situation in which we know the development trajectories for the mutual exclusivity inference as well as for the common ground inference, what can we say about how they will be comined.
+Importantly, we ask this question before any data on integration has been collected.
+The model offers an answer and also allows us to make quantitative predictions.
+We can then test the predictive power of the model by comparing the model predictions to newly collected data.
+We will use model comparisons to test the *integration model* against a range of alternative models.
+
+Finally, we ask how well our model *explains* the way that children integrate the two information sources.
+For this analysis, we fit the free parameters in the model to all the available data, those from experiment 1 and 2 as well as the integration data from experiment 3.
+We then compare the model to a range of alternative models that make different assumptions about how information is integrated and how this process develops.
+This approach answers the question of how we can best explain how children are integrating the different information sources.
+
+## Modelling framework
+
+We implemented the cognitive models in the Rational Speech Act (RSA) framework [@frank2012predicting; goodman2016pragmatic].
+RSA models are models of pragmatic reasoning in that they treat language understanding as a special case of Bayesian social reasoning.
+A listener interprets an utterance by assuming it was produced by a cooperative speaker who had the goal to be informative.
+Being informative is defined as providing a message that would increase the probability of the listener inferring the speaker’s intended message.
+This notion of contextual informativeness captures the Gricean idea of cooperation between speaker and listener, and provides a first approximation to what we have described above as utterance-level pragmatic information.
+
+--- model in math ---
+
+## Loci of development
+
+We can identify three potential loci of development in the model described above: semantic knowledge, expectations about speaker informativeness and common ground sensitivity.
+Each of theses components is represented by a parameter in the model.
+We capture developmental change by making these parameters a function of age and estimate the developmental trajectory for each parameter.
+These age sensitive parameters are then passed through the model to generate predictions in the form of developmental trajectories for each item in the congruent and the incongruent condition.
 
 ### Semantic knowledge
+
+Semantic knowledge captures the degree of certainty with which the speaker and the (naive) listener know the label for the familiar object.
+The major source of variation in semantic knowledge are the different familiar objects.
+For objects whose labels are generally acquired earlier (e.g.
+carrot) semantic knowledge is high whereas for others (e.g.
+pawn) semantic knowledge is lower.
+However, semantic knowledge also varies with age in that older children are more likely to know the labels for more of the familiar objects compared to younger children.
+As a consequence, each familiar object has a unique developmental trajectory with respect to semantic knowledge.
 
@@
 
+## Model fitting
+
+All models were implemented in `webppl` [@dippl].
+The corresponding model code can be found in the associated online repository.
+Model predictions and model comparison are based on the full posterior distribution for each model parameter.
+
 ## Prediction
 
-Estimate parameters based on me data and prior data. The models considered belwo make differential use of theses parameters. Basically, one full model and the rest are lesion model
+Estimate parameters based on me data and prior data. The models considered below make differential use of theses parameters. Basically, one full model and the rest are lesion model
 
-### Pragmatic model
+### Model parameters
+
+```{r}
+
+# parameter distributions based on model 
+item_params <- readRDS("../saves/item_params.rds")
+global_params <- readRDS("../saves/global_params.rds")
+item_sigma <- readRDS("../saves/item_sigma.rds")
+
+# summaries
+item_params_summary <- item_params %>%
+  group_by(item, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+global_params_summary <- global_params %>%
+  group_by (parameter,type)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+# selection object
+select <- sample(1:length(unique(global_params$iteration)), 30)
+
+# plot for semantic knowledge
+
+sem_know_map <- item_params_summary%>%
+  select(-uci,-lci)%>%
+  spread(parameter, -item) %>%
+  expand_grid(., age = unique(me_data$age)) %>%
+  mutate(sem_know = plogis(intercept + slope * age)) %>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+plot_sem_know <- ggplot()+
+  geom_line(data = sem_know_map, aes(x = age+2, y= sem_know, col = item, group = item),size = 1)+
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_few()+
+  scale_colour_viridis_d(name = "Object")
+
+# plot or speaker optimality
+
+speak_opt <- global_params%>%
+  filter(parameter == "speaker_optimality")
+
+speak_opt_line <- speak_opt%>%
+  filter(iteration %in% select)%>%
+  spread(type, value)%>%
+  expand_grid(., age = unique(me_data$age))%>%
+  mutate(y = intercept + slope * age)
+
+speak_opt_map <- global_params_summary%>%
+  ungroup()%>%
+  filter(parameter == "speaker_optimality")%>%
+  select(type, mode)%>%
+  spread(type, mode)%>%
+  expand_grid(., age = unique(me_data$age))%>%
+  mutate(y = intercept + slope * age)
+
+plot_speak_opt <- ggplot() +
+  geom_line(data = speak_opt_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
+  geom_line(data = speak_opt_map, aes(x=age+2,y = y),size = 1)+
+  labs(x="Age",y="Speaker informativeness")+
+  theme_few() +
+  ylim(0,10)+
+    xlim(2,5)+
+  guides(alpha = F, fill = F, col = F)
+
+# Plot prior sensitivity
+
+prior <- global_params%>%
+  filter(parameter == "prior")
+
+prior_line <- prior%>%
+  filter(iteration %in% select)%>%
+  spread(type, value)%>%
+  expand_grid(., age = unique(me_data$age))%>%
+  mutate(y = plogis(intercept + slope * age))
+
+prior_map <- global_params_summary%>%
+  ungroup()%>%
+  filter(parameter == "prior")%>%
+  select(type, mode)%>%
+  spread(type, mode)%>%
+  expand_grid(., age = unique(me_data$age))%>%
+  mutate(y = plogis(intercept + slope * age))
+
+plot_prior <- ggplot() +
+  geom_line(data = prior_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
+  geom_line(data = prior_map, aes(x=age+2,y = y),size = 1)+
+  labs(x="Age",y="Prior sensitivity")+
+  theme_few() +
+  ylim(0,1)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F, col = F)
+
+```
+
+```{r fig4, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity.
+Solid lines in show the MAP estimate for each parameter.
+Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty.
+(A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
+ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.1,1,1))
+```
+
+### Integration model
 
@@
 semantic knowledge is only a function of age and not specific to the item.
-Roughyl corresponds to.
+Roughly corresponds to.
 If children are vaguely familiar with an object, the make the ME inference regardless of the individual object
@@
 
-range of log like accross chains and then model comparison
+range of log like across chains and then model comparison
 
@@
 
-### Pragmatic model
+### Model parameters
+
+```{r}
+
+# parameter distributions based on model 
+item_params_exp <- readRDS("../saves/item_params_fb.rds")
+global_params_exp <- readRDS("../saves/global_params_fb.rds")
+item_sigma_exp <- readRDS("../saves/item_sigma_fb.rds")
+
+# summaries
+item_params_summary_exp <- item_params_exp %>%
+  group_by(item, parameter)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+global_params_summary_exp <- global_params_exp %>%
+  group_by (parameter,type)%>%
+  summarise(mode = estimate_mode(value),
+            uci = hdi_upper(value),
+            lci = hdi_lower(value))
+
+# selection object
+select_exp <- sample(1:length(unique(global_params_exp$iteration)), 30)
+
+# plot for semantic knowledge
+
+sem_know_map_exp <- item_params_summary_exp%>%
+  select(-uci,-lci)%>%
+  spread(parameter, -item) %>%
+  expand_grid(., age = unique(comb_data$age)) %>%
+  mutate(sem_know = plogis(intercept + slope * age)) %>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
+
+plot_sem_know_exp <- ggplot()+
+  geom_line(data = sem_know_map_exp, aes(x = age+2, y= sem_know, col = item, group = item),size = 1)+
+  ylab("Semantic knowledge")+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_few()+
+  scale_colour_viridis_d(name = "Object")
+
+# plot or speaker optimality
+
+speak_opt_exp <- global_params_exp%>%
+  filter(parameter == "speaker_optimality")
+
+speak_opt_line_exp <- speak_opt_exp%>%
+  filter(iteration %in% select)%>%
+  spread(type, value)%>%
+  expand_grid(., age = unique(comb_data$age))%>%
+  mutate(y = intercept + slope * age)
+
+speak_opt_map_exp <- global_params_summary_exp%>%
+  ungroup()%>%
+  filter(parameter == "speaker_optimality")%>%
+  select(type, mode)%>%
+  spread(type, mode)%>%
+  expand_grid(., age = unique(comb_data$age))%>%
+  mutate(y = intercept + slope * age)
+
+plot_speak_opt_exp <- ggplot() +
+  geom_line(data = speak_opt_line_exp, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
+  geom_line(data = speak_opt_map_exp, aes(x=age+2,y = y),size = 1)+
+  labs(x="Age",y="Speaker informativeness")+
+  theme_few() +
+  ylim(0,10)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F, col = F)
+
+# Plot prior sensitivity
+
+prior_exp <- global_params_exp%>%
+  filter(parameter == "prior")
+
+prior_line_exp <- prior_exp%>%
+  filter(iteration %in% select)%>%
+  spread(type, value)%>%
+  expand_grid(., age = unique(comb_data$age))%>%
+  mutate(y = plogis(intercept + slope * age))
+
+prior_map_exp <- global_params_summary_exp%>%
+  ungroup()%>%
+  filter(parameter == "prior")%>%
+  select(type, mode)%>%
+  spread(type, mode)%>%
+  expand_grid(., age = unique(comb_data$age))%>%
+  mutate(y = plogis(intercept + slope * age))
+
+plot_prior_exp <- ggplot() +
+  geom_line(data = prior_line_exp, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
+  geom_line(data = prior_map_exp, aes(x=age+2,y = y),size = 1)+
+  labs(x="Age",y="Prior sensitivity")+
+  theme_few() +
+  ylim(0,1)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F, col = F)
+
+```
+
+```{r fig4, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity.
+Solid lines in show the MAP estimate for each parameter.
+Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty.
+(A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
+ggarrange(plot_sem_know_exp, plot_speak_opt_exp, plot_prior_exp , labels = c("A","B","C"), nrow = 1, widths = c(1.1,1,1))
+```
+
+```{r fig4, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity.
+Solid lines in show the MAP estimate for each parameter.
+Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty.
+(A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
+ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.1,1,1))
+```
+
+### Integration model
+
+### Mixture model
 
@@
 
+## Comparing model parameters
+
 # Discussion

### 2020-03-11 paper/supplementary_material.Rmd
add verbal model description

@@
 
-We implemented the cognitive models in the Rational Speech Act (RSA) framework [@frank2012predicting; goodman2016pragmatic].
+The cognitive models are situated in the Rational Speech Act (RSA) framework [@frank2012predicting; goodman2016pragmatic].
 RSA models are models of pragmatic reasoning in that they treat language understanding as a special case of Bayesian social reasoning.
@@
 Being informative is defined as providing a message that would increase the probability of the listener inferring the speaker’s intended message.
-This notion of contextual informativeness captures the Gricean idea of cooperation between speaker and listener, and provides a first approximation to what we have described above as utterance-level pragmatic information.
+This notion of contextual informativeness captures the Gricean idea of cooperation between speaker and listener.
 
---- model in math ---
+The model captures the following process.
+A listener is reasoning about the referent of a speaker's utterance while at the same time trying to learn a lexicon (object--word mappings).
+This reasoning is contextualized by the prior probability of each referent.
+This prior probability is thought to be a function of the common ground shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later.
+We assume that the degree to which interactions around objects change their prior probability depend on the child's age.
+
+To decide between referents, the listener reasons about what a rational speaker would say given an intended referent.
+This speaker is assumed to compute the informativity of for each available utterance and then choose the most informative one.
+However, this expectation of speaker informativeness may vary and is caputred by the term alpha.
+In particualr, we take alpha to be a function of the child's age.
+
+The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their literal semantics, would infer upon hearing it.
+Thus, this reasoning depends what kind of word--object mappings the speaker thinks the literal listener knows.
+We assume that knowing the literal semantics of a word is not deterministic but probabilistic.
+That is, for each object involved there is a probability p that the literal listener knows the word for it.
+For each of the novel objects, this semantic knowledge is 0.
+For familiar objects, it depends on the kind of object as well as on the child's age.
 
@@
 
-We can identify three potential loci of development in the model described above: semantic knowledge, expectations about speaker informativeness and common ground sensitivity.
+The model description above points to three potential loci of developmental change: semantic knowledge, expectations about speaker informativeness and common ground sensitivity.
 Each of theses components is represented by a parameter in the model.
-We capture developmental change by making these parameters a function of age and estimate the developmental trajectory for each parameter.
-These age sensitive parameters are then passed through the model to generate predictions in the form of developmental trajectories for each item in the congruent and the incongruent condition.
+We capture developmental change by making these parameters a function of age and therfor estimating a developmental trajectory (intercept and slope) for each parameter.
 
@@
 
-Semantic knowledge captures the degree of certainty with which the speaker and the (naive) listener know the label for the familiar object.
-The major source of variation in semantic knowledge are the different familiar objects.
+Semantic knowledge captures the degree of certainty with which the naive listener is assumed to know the label for the familiar object.
+When faced with the task, we think that children take their own semantic knowledge as the basis.
+As a consequence, semantic knowledge differs between familiar objects.
 For objects whose labels are generally acquired earlier (e.g.
@@
 
+Developmental trajectories are estimated via a model in which we assume th (that only captures the ME task).
+
 ### Expectations about speaker informativeness
+
+Expectations how rational the speaker is change with age. Older children are assumed to expect
 
@@
 All models were implemented in `webppl` [@dippl].
-The corresponding model code can be found in the associated online repository.
-Model predictions and model comparison are based on the full posterior distribution for each model parameter.
+The corresponding model code can be found in the associated online repository (xxxxx).
+To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by item), speaker informativeness and common ground sensitivity and then passed them through the model in line with the different ways in which they can be combined and aligned.
+The resulting predictions come in the form of distributions of developmental trajectories for each item in the congruent and the incongruent condition.
+We compared models based on the full posterior distribution for each model parameter.
 
@@
 
+model parameters are also estimated based in the data from experiment 1 and 2, but then updated based on the data from experiment 3.
+
 ### Model parameters

### 2020-03-13 paper/supplementary_material.Rmd
advance model descriptions

@@
 prior_data <- read_csv("../data/novelty.csv")
-comb_data <- read_csv("../data/combination.csv")
+comb_data <- read_csv("../data/combination.csv")%>%
+  mutate(model = "data")%>%
+  left_join(aoa_ratings) %>%
+  ungroup()%>%
+  mutate(item = fct_reorder(factor(item), mean_aoa))
 
@@
 
-We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | item) + (age * alignment | agent)`\footnote{We pre-registered to include item as a fixed effect in Experiment 3.
+We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | item) + (age * alignment | agent)`.
+We pre-registered to include item as a fixed effect in Experiment 3.
 The corresponding model was too complex to be constrained by the data.
 Furthermore, as explained in Experiment 1, items were chosen based on their rated age of acquisition.
-That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge.}, specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).
+That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge.
+For further model specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).
 The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`).
@@
 As a consequence, each familiar object has a unique developmental trajectory with respect to semantic knowledge.
-
-Developmental trajectories are estimated via a model in which we assume th (that only captures the ME task).
+The likelihood term of the model depends not just the parameter settings for semantic knowledge but also on the value of the parameter capturing expecations about speaker informativeness (alpha - see next section).
+As a consequence, these two parameters are estimated in conjunction and co-vary with one another.
 
@@
 
-Expectations how rational the speaker is change with age. Older children are assumed to expect
+A second locus of developmental change are expectations about speaker informativeness.
+In the context of the model, speaker informativeness corresponds to the degree with which the listener expects the speaker to choose the most informative of all available utterances.
+We assume that children at different ages might have different expectations about how rational or informative speakers are.
+As mentioned above, this parameter jointly estimated with the parameters for semantic knowledge.
 
@@
 
+Sensitivity to common ground refers to the probability that an object is taken to be the referent of the utterance before actually hearing the utterance.
+Thus, it captures the salience of an object due to its role in the social interaction that preceeds the utterance.
+We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects.
+
 ## Model fitting
 
-All models were implemented in `webppl` [@dippl].
-The corresponding model code can be found in the associated online repository (xxxxx).
+All Bayesian cognitive models were implemented in the probabilistic programming language  `WebPPL` [@dippl].
+The corresponding model code can be found in the associated online repository and includes information about the prior distributions for all parameters in the model (file xxxxx).
 To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by item), speaker informativeness and common ground sensitivity and then passed them through the model in line with the different ways in which they can be combined and aligned.
 The resulting predictions come in the form of distributions of developmental trajectories for each item in the congruent and the incongruent condition.
-We compared models based on the full posterior distribution for each model parameter.
+We generated model predictions for each model based on the full posterior distribution for each model parameter.
+Based on these model predictions, we computed the marginal likelihood of the data given each model and compared them via Bayes factors (see file `model_comparison.Rmd` in the associated online repository).
 
@@
 
-Estimate parameters based on me data and prior data. The models considered below make differential use of theses parameters. Basically, one full model and the rest are lesion model
+In this section we evaluate different models in terms of how well they *predict* information integration.
+That is, in a situation in which we know the development of the mutual exclusivity inference as well as the common ground inference, which model best predicts what happens when the two are combined (combination data from Experiment 3).
+Asking this question automatically excludes all models which include parameters that need to be fit to the combination data itself.
+To this end, we estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.
+Next, we combined the parameters according to the four models described below.
+Please note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in how they were combined.
 
-### Model parameters
+To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150 000 samples from each chain and removing the first 50 000 for burn-in.
+We removed samples from one chain because it converged on a local maximum and yielded parameter distributions that were substantially different from the other chains.
+The model outputs can be found in the following online repository: git large file storage.
 
 ```{r}
-
 # parameter distributions based on model 
@@
 (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
-ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.1,1,1))
+ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.,1,1))
 ```
@@
 [overview fig, all model parameters for all models]
+```{r fig5, include = T, fig.align = "center", fig.cap = "Model predictions based on the integration model.
+Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution.
+Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition.
+Familiar objects are ordered based on their rated age of acquisition (left o right).
+Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey).", fig.width=12, fig.height = 4}
+# comb_data_binned <- comb_data%>%
+#   group_by(subage, alignment, item)%>%
+#   summarize(k = sum(correct), n = n())%>%
+#   ungroup() %>%
+#   mutate(a = 1 + k,
+#          b = 1 + n - k,
+#          data_mean = (a-1)/(a+b-2),
+#          data_ci_lower  = qbeta(.025, a, b),
+#          data_ci_upper = qbeta(.975, a, b),
+#          age = factor(subage))%>%
+#   select(-a,-b,-n,-k)%>%
+#   left_join(aoa_ratings) %>%
+#   ungroup()%>%
+#   mutate(item = fct_reorder(factor(item), mean_aoa))
+# 
+# select_pred <- sample(1:20000, 60)
+# 
+# plot_prag_pred <- readRDS("../saves/model_pred_prag.rds")%>%
+#   filter(iteration %in% select_pred)%>%
+#   left_join(aoa_ratings) %>%
+#   ungroup()%>%
+#   mutate(item = fct_reorder(factor(item), mean_aoa))
+# 
+# 
+#  saveRDS(plot_prag_pred, "../saves/plot_prag_pred.rds")
+
+plot_prag_pred <- readRDS( "../saves/plot_prag_pred.rds")
+
+ggplot(data = comb_data, aes(x = age_num, y = correct)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(col = "black", height = .025, alpha = .1)+
+  #geom_pointrange(data = comb_data_binned, aes(x = subage+.5, y = data_mean, ymin =data_ci_lower, ymax = data_ci_upper), stroke = 1, pch = 5)+
+  #geom_line(data = comb_data_binned, aes(x = subage+.5, y = data_mean))+
+  geom_line(data = plot_prag_pred, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)), size = .2, alpha = .25)+
+  geom_smooth(data = comb_data, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .4, lty = 2, size = 1)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F, col = F)+ 
+  scale_colour_ptol(name = NULL)
+```
+
+```{r fig6, include = T, fig.align = "center", fig.cap = "Correlations between model predictions and data binned by year, item and condition.
+Vertical and horizontal error bars show 95\\% HDI.
+Blue diamonds show congruent condition and red ones show the incongruent condition.", fig.width=12, fig.height = 6}
+
+# cor_prag <- readRDS("../saves/model_pred_prag.rds")%>%
+#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#          age = cut(age,
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(model,alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
+# 
+# cor_global <- readRDS("../saves/model_pred_global.rds")%>%
+#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#          age = cut(age,
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(model, alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
+# 
+# cor_flat <- readRDS("../saves/model_pred_flat.rds")%>%
+#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#          age = cut(age,
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(model, alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
+# 
+# cor_prior <- readRDS("../saves/model_pred_prior.rds")%>%
+#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#          age = cut(age,
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(model, alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
+# 
+# cor_model_pred <- bind_rows(
+#    cor_prag,
+#    cor_global,
+#    cor_flat,
+#    cor_prior
+# )
+# 
+# 
+# plot_cor_model_pred <- cor_model_pred %>%
+#   left_join(
+#     bind_rows(
+#        binnned_data%>%mutate(model = "integration"),
+#        binnned_data%>%mutate(model = "no word knowledge"),
+#        binnned_data%>%mutate(model = "no common ground"),
+#        binnned_data%>%mutate(model = "no mutual exclusivity")
+#       )
+#   )%>%
+#   mutate(age = fct_recode(age, 
+#                           "2" = "2-year-olds",
+#                           "3" = "3-year-olds",
+#                           "4" = "4-year-olds"))
+#
+#saveRDS(plot_cor_model_pred, "../saves/corr_model_data_pred.rds")
+
+ plot_cor_model_pred <- readRDS( "../saves/corr_model_data_pred.rds")
+
+ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
+  geom_point(size = 1.5, stroke = 1, pch = 5)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(age~model)+
+  theme_few() + 
+  scale_colour_ptol(name ="Condition")
+
+```
 
@@
 
-```{r fig4, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity.
+```{r fig8, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity.
 Solid lines in show the MAP estimate for each parameter.
@@
 ggarrange(plot_sem_know_exp, plot_speak_opt_exp, plot_prior_exp , labels = c("A","B","C"), nrow = 1, widths = c(1.1,1,1))
-```
-
-```{r fig4, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity.
-Solid lines in show the MAP estimate for each parameter.
-Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty.
-(A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
-ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.1,1,1))
 ```

### 2020-03-14 paper/supplementary_material.Rmd
add molde comparison to suppl file

@@
 The resulting predictions come in the form of distributions of developmental trajectories for each item in the congruent and the incongruent condition.
-We generated model predictions for each model based on the full posterior distribution for each model parameter.
-Based on these model predictions, we computed the marginal likelihood of the data given each model and compared them via Bayes factors (see file `model_comparison.Rmd` in the associated online repository).
 
@@
 Please note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in how they were combined.
+
+Four models, one full model, others lesions. What inforamtion do we need to make good predictions
 
@@
 (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
-ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.,1,1))
+ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1))
 ```
@@
 [overview fig, all model parameters for all models]
-```{r fig5, include = T, fig.align = "center", fig.cap = "Model predictions based on the integration model.
+```{r fig5, include = T, fig.align = "center", fig.cap = "Predicting information integration across development.
+Model predictions based on the integration model.
 Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution.
@@
 Familiar objects are ordered based on their rated age of acquisition (left o right).
-Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey).", fig.width=12, fig.height = 4}
+Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey).
+Light dots are individual data points.", fig.width=12, fig.height = 4}
 # comb_data_binned <- comb_data%>%
@@
 
-```{r fig6, include = T, fig.align = "center", fig.cap = "Correlations between model predictions and data binned by year, item and condition.
+### No word knowledge model
+
+semantic knowledge is only a function of age and not specific to the item.
+Roughly corresponds to.
+If children are vaguely familiar with an object, the make the ME inference regardless of the individual object
+
+### No common ground model
+
+### No mutual exclusivity model
+
+### Model comparison
+
+Compare model prediction in two ways. First is via correlations and second isvia bayes factors.
+
+Based on these model predictions, we computed the marginal likelihood of the data given each model and compared them via Bayes factors (see file `model_comparison.Rmd` in the associated online repository).
+
+range of log like across chains and then model comparison
+
+```{r fig6, include = T, fig.align = "center", fig.cap = "Predicting information integration.
+Correlations between model predictions and data binned by year, item and condition.
 Vertical and horizontal error bars show 95\\% HDI.
@@
 # cor_prag <- readRDS("../saves/model_pred_prag.rds")%>%
-#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#   mutate(age = as.numeric(age) + min(comb_data$age_num),
 #          age = cut(age,
@@
 # cor_global <- readRDS("../saves/model_pred_global.rds")%>%
-#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#   mutate(age = as.numeric(age) + min(comb_data$age_num),
 #          age = cut(age,
@@
 # cor_flat <- readRDS("../saves/model_pred_flat.rds")%>%
-#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#   mutate(age = as.numeric(age) + min(comb_data$age_num),
 #          age = cut(age,
@@
 # cor_prior <- readRDS("../saves/model_pred_prior.rds")%>%
-#   mutate(age = as.numeric(age) + min(data_comb$age_num),
+#   mutate(age = as.numeric(age) + min(comb_data$age_num),
 #          age = cut(age,
@@
   # mutate(age = fct_recode(age,
-#                           "2" = "2-year-olds",
-#                           "3" = "3-year-olds",
-#                           "4" = "4-year-olds"))
+  #                         "2-year-olds" = "2",
+  #                         "3-year-olds" = "3",
+  #                         "4-year-olds" = "4"))
 #
@@
 
-### No word
-
-semantic knowledge is only a function of age and not specific to the item.
-Roughly corresponds to.
-If children are vaguely familiar with an object, the make the ME inference regardless of the individual object
-
-### Model comparison
-
-range of log like across chains and then model comparison
+```{r table3}
+model_comp_pred <- readRDS("../saves/pred_model_comparison.rds")%>%
+  mutate(model = factor(model),
+         `Model comparison` = fct_recode(model, 
+                            "integration vs no word knowledge" = "prag_vs_global",
+                            "integration vs no common ground" = "prag_vs_flat",
+                            "integration vs no mutual exclusivity" = "prag_vs_prior",
+                            "no word knowledge vs no mutual exclusivity" = "global_vs_flat",
+                            "no word knowledge vs no common ground" = "global_vs_prior",
+                            "no mutual exclusivity vs no common ground" = "flat_vs_prior"),
+        `Bayes factor` = format(round(exp(logBF),2), trim = T, justify = "right", digits = 2))%>%
+  select(-logBF, -model)
+
+knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2)
+```
 
@@
 model parameters are also estimated based in the data from experiment 1 and 2, but then updated based on the data from experiment 3.
+
+answer the question: which is the best way to think about information integration
 
@@
 (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
-ggarrange(plot_sem_know_exp, plot_speak_opt_exp, plot_prior_exp , labels = c("A","B","C"), nrow = 1, widths = c(1.1,1,1))
+ggarrange(plot_sem_know_exp, plot_speak_opt_exp, plot_prior_exp , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1))
 ```
@@
 
+```{r fig9, include = T, fig.align = "center", fig.cap = "Explaining information integration across development.
+Model predictions based on the integration model.
+Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution.
+Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition.
+Familiar objects are ordered based on their rated age of acquisition (left o right).
+Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey).
+Light dots are individual data points.", fig.width=12, fig.height = 4}
+
+# select_exp <- sample(1:20000, 50)
+# 
+# plot_prag_exp <- readRDS("../saves/model_pred_prag_fb.rds")%>%
+#   filter(iteration %in% select_pred)%>%
+#   left_join(aoa_ratings) %>%
+#   ungroup()%>%
+#   mutate(item = fct_reorder(factor(item), mean_aoa))
+# 
+# 
+# saveRDS(plot_prag_exp, "../saves/plot_prag_exp.rds")
+
+plot_prag_exp<- readRDS( "../saves/plot_prag_exp.rds")
+
+ggplot(data = comb_data, aes(x = age_num, y = correct)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(col = "black", height = .025, alpha = .1)+
+  #geom_pointrange(data = comb_data_binned, aes(x = subage+.5, y = data_mean, ymin =data_ci_lower, ymax = data_ci_upper), stroke = 1, pch = 5)+
+  #geom_line(data = comb_data_binned, aes(x = subage+.5, y = data_mean))+
+  geom_line(data = plot_prag_exp, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)), size = .2, alpha = .25)+
+  geom_smooth(data = comb_data, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .4, lty = 2, size = 1)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F, col = F)+ 
+  scale_colour_ptol(name = NULL)
+```
+
 ### Mixture model
@@
 
+```{r fig10, include = T, fig.align = "center", fig.cap = "Explaining information integration.
+Correlations between model predictions and data binned by year, item and condition.
+Vertical and horizontal error bars show 95\\% HDI.
+Blue diamonds show congruent condition and red ones show the incongruent condition.", fig.width=12, fig.height = 6}
+
+# cor_prag_exp <- readRDS("../saves/model_pred_prag_fb.rds")%>%
+#   mutate(age = as.numeric(age) + min(comb_data$age_num),
+#          age = cut(age,
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(model,alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
+# 
+# cor_mix_exp <- readRDS("../saves/model_pred_mm.rds")%>%
+#   mutate(age = as.numeric(age) + min(comb_data$age_num),
+#          age = cut(age,
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(model, alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
+# 
+# cor_dev_mix_exp <- readRDS("../saves/model_pred_dmm.rds")%>%
+#   mutate(age = as.numeric(age) + min(comb_data$age_num),
+#          age = cut(age,
+#                       breaks = c(2,3,4,5),
+#                       labels = c(2,3,4)))%>%
+#   group_by(model, alignment, item, age)%>%
+#   summarise(model_mean = estimate_mode(pred),
+#             model_ci_lower = hdi_lower(pred),
+#             model_ci_upper = hdi_upper(pred))
+# 
+# 
+# cor_model_exp <- bind_rows(
+#    cor_prag_exp%>%ungroup()%>%mutate(model = "integration"),
+#    cor_mix_exp%>%ungroup()%>%mutate(model = "mixture"),
+#    cor_dev_mix_exp%>%ungroup()%>%mutate(model = "developmental mixture")
+# )
+# 
+# 
+# plot_cor_model_exp <- cor_model_exp %>%
+#   left_join(
+#     bind_rows(
+#        comb_data_binned%>%mutate(model = "integration"),
+#        comb_data_binned%>%mutate(model = "mixture"),
+#        comb_data_binned%>%mutate(model = "developmental mixture")
+#       )
+#   )%>%
+#   mutate(age = fct_recode(age,
+#                           "2-year-olds" = "2",
+#                           "3-year-olds" = "3",
+#                           "4-year-olds" = "4"))
+# 
+# saveRDS(plot_cor_model_exp, "../saves/corr_model_data_exp.rds")
+
+plot_cor_model_exp <- readRDS( "../saves/corr_model_data_exp.rds")
+
+ggplot(data = plot_cor_model_exp,aes(x = model_mean, y = data_mean, col = alignment)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
+  geom_point(size = 1.5, stroke = 1, pch = 5)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(age~model)+
+  theme_few() + 
+  scale_colour_ptol(name ="Condition")
+
+```
+
+```{r table4}
+model_comp_pred <- readRDS("../saves/expl_model_comparison.rds")%>%
+  mutate(model = factor(model),
+         `Model comparison` = fct_recode(model, 
+                            "integration (explanation) vs integration (prediction)" = "fb_vs_free",
+                            "integration (explanation) vs mixture" = "fb_vs_mixture",
+                            "integration (prediction) vs mixture" = "free_vs_mixture",
+                            "integration (explanation) vs developmental mixture" = "fb_vs_dev_mixture",
+                            "integration (prediction) vs developmental mixture" = "free_vs_dev_mixture",
+                            "developmental mixture vs mixture" = "dev_mixture_vs_mixture"),
+        `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%
+  select(-logBF, -model)
+
+knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2)
+```
+
 [overview fig, correlations for all models]

### 2020-03-14 stats/model_comparison.Rmd
add molde comparison to suppl file

@@
 
-model_comp <- bind_rows(
+model_like <- bind_rows(
 
@@
   group_by(chain, model, iteration) %>%
-  summarize(total_likelihood_sample = sum(log_like)) %>%
+  summarize(total_likelihood_sample = sum(log_like))
+
+model_by_chain <- model_like %>%
+  na.omit(chain)%>%
   group_by(chain, model) %>%
   summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  spread(model, marginal_likelihood)
+
+saveRDS(model_by_chain, "../saves/pred_model_likelihood_chain.rds")
+
+model <- model_like %>%
+  na.omit(chain)%>%
+  group_by(model) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample))
+
+saveRDS(model, "../saves/pred_model_likelihood.rds")
+
+model_comp <- model_like  %>%
+  na.omit(chain)%>%
+  group_by(model) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample))%>%
   spread(model, marginal_likelihood)%>%
@@
   select(-pragmatic, -global, -flat, - prior) %>%
-  gather(model, logBF, -chain)
+  gather(model, logBF)
+
+saveRDS(model_comp, "../saves/pred_model_comparison.rds")
 
@@
 
-# compare models
+model <- model_like %>%
+  na.omit(chain)%>%
+  group_by(model) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample))
+
+saveRDS(model, "../saves/expl_model_likelihood.rds")
+
 model_comp <- model_like  %>%
@@
   group_by(model) %>%
-  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample))%>%
   spread(model, marginal_likelihood)%>%

### 2020-03-16 paper/supplementary_material.Rmd
advance suppl material

@@
 knitr::kable(chance_me, caption = "Proportion of children choosing the novel object compared to a level expected by chance based on a one sample Bayesian t-test.
-Responses are aggregated for each participant across familiar objects.", digits = 2)
+Responses are aggregated for each participant across familiar objects.", digits = 2, align = "l")
 ```
@@
 We used the function `brm` from the package `brms` [@R-brms_a].
-As priors we used `normal(0,5)` for fixed effects and `cauchy(0,1)` for standard deviations of random effects\footnote{We pre-registered the use of default priors in all models.
-However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent.}.
-The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`\footnote{We did not pre-register agent as a random effect, but decided to included it to be consistent with Experiment 2 and 3.}.
+We pre-registered the use of default priors in all models.
+However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent.
+The priors we used were `normal(0,5)` for fixed effects and `cauchy(0,1)` for standard deviations of random effects.
+The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`.
 That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects).
+We did not pre-register agent as a random effect, but decided to included it to be consistent with Experiment 2 and 3.
+
 The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`).
 Older children were more likely to make a mutual exclusivity inference.
-Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and shows that there was substantial variation between them.
+Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and shows that there was substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory.
 Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept.
@@
 knitr::kable(chance_prior, caption = "Proportion of children choosing the object that was new to the speaker compared to a level expected by chance based on a one sample Bayesian t-test.
-Responses are aggregated for each participant across trials.", digits = 2)
+Responses are aggregated for each participant across trials.", digits = 2, align = "l")
 ```
@@
 
-Use sd on item to say tha items vary substantially and sd on interaction or age to say they differ in their slope
-
 We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | item) + (age * alignment | agent)`.
@@
 For further model specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).
+
 The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`).
@@
 Taken together, the results show that children responded to the way the two inferences were aligned with one another.
-For the remainder of the study, we address the question of how the two inferences might have interacted with one another.
 
@@
 
-# Model
-
-The main purpose of the study was to study *how* children integrate different information sources during word learning.
-To address this question, we use Bayesian cognitive models of prgamatic reasoning.
-We first describe an *integration model* which we think best represents the inference and integration processes.
-We then specify how this model captures developmental change.
-
+## Discussion
+
+The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate.
+Experiment 1 showed that children of all age groups are make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented.
+Experiment 2 showed that three- and four-year-olds are sensitive the common ground manipulation we implemented and that this inference increases with age.
+Finally, experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another.
+In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when the two inferences are combined with one another.
+
+# Models
+
+The main purpose of the study was to study *how* children integrate different information sources during word learning and how this process develops with age.
+To do so, we use Bayesian cognitive models of pragmatic reasoning.
+We first describe an *integration model* which we think best represents the inference and integration processes and then specify how this model captures developmental change.
 Next, we ask how well this model *predicts* how children integrate the two information sources.
-That is, in a situation in which we know the development trajectories for the mutual exclusivity inference as well as for the common ground inference, what can we say about how they will be comined.
-Importantly, we ask this question before any data on integration has been collected.
-The model offers an answer and also allows us to make quantitative predictions.
-We can then test the predictive power of the model by comparing the model predictions to newly collected data.
+That is, in a situation in which we know the development trajectories for the mutual exclusivity inference as well as for the common ground inference, what can we say about what happens when they are combined.
+We then test the predictive power of the model by comparing the model predictions to the data from experiment 3.
 We will use model comparisons to test the *integration model* against a range of alternative models.
@@
 
-The cognitive models are situated in the Rational Speech Act (RSA) framework [@frank2012predicting; goodman2016pragmatic].
+The cognitive models are situated in the Rational Speech Act (RSA) framework [@frank2012predicting; @goodman2016pragmatic].
 RSA models are models of pragmatic reasoning in that they treat language understanding as a special case of Bayesian social reasoning.
@@
 This speaker is assumed to compute the informativity of for each available utterance and then choose the most informative one.
-However, this expectation of speaker informativeness may vary and is caputred by the term alpha.
-In particualr, we take alpha to be a function of the child's age.
+However, this expectation of speaker informativeness may vary and is captured by the term alpha.
+In particular, we take alpha to be a function of the child's age.
 
@@
 Each of theses components is represented by a parameter in the model.
-We capture developmental change by making these parameters a function of age and therfor estimating a developmental trajectory (intercept and slope) for each parameter.
+We capture developmental change by making these parameters a function of age and therefore estimating a developmental trajectory (intercept and slope) for each parameter.
 
@@
 As a consequence, each familiar object has a unique developmental trajectory with respect to semantic knowledge.
-The likelihood term of the model depends not just the parameter settings for semantic knowledge but also on the value of the parameter capturing expecations about speaker informativeness (alpha - see next section).
-As a consequence, these two parameters are estimated in conjunction and co-vary with one another.
+Technically, the object specifics parameters are estimated in the form of a random effects model, that is, each object's trajectory is estimated as a deviation from an overall trajectory for semantic.
+This overall trajectory represent an increase in semantic knowledge that is independent of a particular familiar object.
+
+Semantic knowledge enters the likelihood term of the model specified above.
+The likelihood depends not just on the parameter settings for semantic knowledge but also on the value of the parameter capturing expectations about speaker informativeness ($\alpha$ - see next section).
+As a consequence, these parameters are jointly estimated and co-vary with one another.
 
@@
 Sensitivity to common ground refers to the probability that an object is taken to be the referent of the utterance before actually hearing the utterance.
-Thus, it captures the salience of an object due to its role in the social interaction that preceeds the utterance.
+Thus, it captures the salience of an object due to its role in the social interaction that precedes the utterance.
 We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects.
@@
 All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
-The corresponding model code can be found in the associated online repository and includes information about the prior distributions for all parameters in the model (file xxxxx).
-To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by item), speaker informativeness and common ground sensitivity and then passed them through the model in line with the different ways in which they can be combined and aligned.
-The resulting predictions come in the form of distributions of developmental trajectories for each item in the congruent and the incongruent condition.
+The corresponding model code can be found in the associated online repository and includes information about the prior distributions for all parameters (file xxxxx).
+To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and common ground sensitivity and then passed them through the model in line with the different ways in which they can be combined and aligned.
+The resulting predictions come in the form of distributions of developmental trajectories for each object in the congruent and the incongruent condition.
 
@@
 That is, in a situation in which we know the development of the mutual exclusivity inference as well as the common ground inference, which model best predicts what happens when the two are combined (combination data from Experiment 3).
-Asking this question automatically excludes all models which include parameters that need to be fit to the combination data itself.
-To this end, we estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.
+Asking about "pure" prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g.
+mixture model, see below).
+To generate these predictions, we estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.
+
+To estimate the parameters for semantic knowledge and speaker informativeness, we adapted the model described above to a situation in which both objects (novel and familiar) have equal prior probability.
+We used the data from experiment 1 to then infer the parameters.
+That is, we inferred which intercepts and slopes for speaker informativeness and semantic knowledge would generate model predictions that corresponded to the average proportion of correct responses measured in experiment 1.
+To estimate the parameters representing sensitivity to common ground, we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in experiment 1.
+
+To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150 000 samples from each chain and removing the first 50 000 for burn-in.
+We removed samples from one chain because it converged on a local maximum which resulted in parameter distributions that were substantially different from the other chains.
+The model outputs can be found in the following online repository: git large file storage.
+
 Next, we combined the parameters according to the four models described below.
-Please note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in how they were combined.
-
-Four models, one full model, others lesions. What inforamtion do we need to make good predictions
-
-To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150 000 samples from each chain and removing the first 50 000 for burn-in.
-We removed samples from one chain because it converged on a local maximum and yielded parameter distributions that were substantially different from the other chains.
-The model outputs can be found in the following online repository: git large file storage.
+Please note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in which parameters they included.
+The models described below are a full model (*integration model*) and three lesion models, which selectively omit one type of information.
+The following model comparison therefore asks which types of information are necessary to make good predictions about how information is integrated.
+We do not compare models that make different assumptions about how information is integrated.
+We turn to this question in the [explanation](#explanation) section.
 
@@
 ```
-
-### Integration model
-
-[overview fig, all model parameters for all models]
+### Models
+
+#### Integration model
+
+The integration model serves as the full model and takes in all available information.
+That is, it takes in object specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above.
+Figure \@ref(fig:fig5) visualizes the corresponding model predictions in comparison to the data from experiment 3.
+
 ```{r fig5, include = T, fig.align = "center", fig.cap = "Predicting information integration across development.
@@
 
-### No word knowledge model
-
-semantic knowledge is only a function of age and not specific to the item.
-Roughly corresponds to.
-If children are vaguely familiar with an object, the make the ME inference regardless of the individual object
-
-### No common ground model
-
-### No mutual exclusivity model
+#### No word knowledge model
+
+This model is the first lesion model.
+It takes in speaker informativeness and common ground sensitivity as well as general semantic knowledge, but omits semantic knowledge that is specific to the familiar objects.
+We described above that the parameters for semantic knowledge are fitted via a mixed effects model.
+On the one hand, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object specific variation around this trajectory (random effects).
+The *no word knowledge* model takes in the overall trajectory for semantic knowledge but ignores object specific variation.
+That is, the model assumes a listener whose mutual exclusivity inference does not vary depending on the particular familiar object but only depends on the average semantic knowledge.
+
+#### No common ground model
+
+This model takes in object specific semantic knowledge and speaker informativeness but ignores common ground.
+Thus, the prior distribution over objects $P(r)$ in the model described above is flat (e.g.
+[0.5, 0.5].
+This corresponds to a listener who only focuses on the mutual exclusivity inference and ignores the common ground manipulation.
+As a consequence the listener does not differentiate between the two alignment conditions.
+
+#### No mutual exclusivity model
+
+The last lesion model only takes in the common ground sensitivity.
+This corresponds to a listener who only focuses on common ground and ignores the identity of the objects on the tables as well as any inferences their semantic knowledge of the familiar objects license.
+The model predictions therefore correspond to the prior distribution over objects $P(r)$.
 
@@
 
-Compare model prediction in two ways. First is via correlations and second isvia bayes factors.
-
-Based on these model predictions, we computed the marginal likelihood of the data given each model and compared them via Bayes factors (see file `model_comparison.Rmd` in the associated online repository).
-
-range of log like across chains and then model comparison
+We compared the models mentioned above in two ways.
+On the one hand, we used correlations between model predictions and the data.
+For this analysis, we binned the model predictions and the data by year and familiar object.
+Figure \@ref(fig:fig6) visualizes the correlation between model predictions and the data for all models.
+The results shows a very high correlation between the predictions of the *integration model* and the data in all age groups suggesting that the model accurately captures the variation in the data.
+The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds.
+This is probably a consequence of the model making very extreme predictions for the oldest age group.
+Correlations for the *integration model* were also higher compared to the other models considered.
+
+On the other hand, we compared models based on Bayes factors which were calculated from the marginal likelihoods of each model given the data.
+For this analysis, we treated age continuously.
+We first calculated the marginal log-likelihood for each model and then computed Bayes factors by subtracting the log-likelihoods for the models involved in the comparison and then exponentiating the result (see file `model_comparison.Rmd` in the associated online repository).
+Table \@ref(tab:table3) lists the Bayes factors for the different model comparisons.
+The results show that the *integration model*, by far, outperformed all the other models.
+When comparing the lesion models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the *no mutual exclusivity model*.
+
+Taken together, this analysis showed two things.
+First, the *integration model* makes accurate predictions about how mutual exclusivity and common ground inferences are integrated with one another.
+It does so based on knowing the strength and development of each inference alone.
+Second, models that omit one or more type of information (object specific word knowledge, speaker informativeness, common ground sensitivity) make much worse predictions.
+This exemplifies that children across the entire age range flexibly integrate all the available information.
+In the next section we ask whether there are other ways think about the process of information integration than the way formalized in the *integration model*.
 
@@
 
- plot_cor_model_pred <- readRDS( "../saves/corr_model_data_pred.rds")
+plot_cor_model_pred <- readRDS( "../saves/corr_model_data_pred.rds")%>%
+  mutate(model = factor(model, levels = c("integration", "no word knowledge", "no common ground", "no mutual exclusivity")))
 
@@
   scale_colour_ptol(name ="Condition")
-
 ```
@@
 
-knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2)
+knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2, align = "l")
 ```
@@
 
-model parameters are also estimated based in the data from experiment 1 and 2, but then updated based on the data from experiment 3.
-
-answer the question: which is the best way to think about information integration
-
-### Model parameters
+In this section we explore how we can best explain information integration across development.
+We explore alternative ways to think about information integration.
+The *integration model* outlined above operates via Bayesian inference in that the prior probability of a referent - following the common ground manipulation - is updated upon hearing the utterance and computing the mutual exclusivity inference.
+In essence, this model is a multiplicative model because the probability of each referent is proportional to the product of the likelihood and the prior.
+The alternative model we consider here is an additive model.
+This *mixture model* assumes that the two inferences are computed separately and then weighted by some ratio $\phi$.
+
+With respect to developmental change, the *integration model* assumes that the process by which information is integrated remains the same across development.
+What changes is children's semantic knowledge, their expectations about speaker informativeness and their sensitivity to common ground.
+But the way these information sources are combined remains the same across age.
+As an alternative, we explore a *developmental mixture model*.
+This model makes the same assumptions about developmental chnage in the individual information sources but, in addition, also assumes that the way that the the mutual exclusivity and the common ground inference are combined with one another changes over time.
+It is structurally identical to the *mixture model* but the mixture parameter $\phi$ is a function of age.
+
+In this section, we make use of all the available data.
+That is, we ask which process best explains the way that the different information sources are combined in the combination data from experiment 3.
+We use the data from experiment 1 and 2 to compute prior distributions over model parameters which are subsequently updated depending on how well the model predictions they generate fit the data.
+
+### Integration model
 
 ```{r}
-
-# parameter distributions based on model 
 item_params_exp <- readRDS("../saves/item_params_fb.rds")
@@
 item_sigma_exp <- readRDS("../saves/item_sigma_fb.rds")
-
-# summaries
-item_params_summary_exp <- item_params_exp %>%
-  group_by(item, parameter)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
-global_params_summary_exp <- global_params_exp %>%
-  group_by (parameter,type)%>%
-  summarise(mode = estimate_mode(value),
-            uci = hdi_upper(value),
-            lci = hdi_lower(value))
-
-# selection object
-select_exp <- sample(1:length(unique(global_params_exp$iteration)), 30)
-
-# plot for semantic knowledge
-
-sem_know_map_exp <- item_params_summary_exp%>%
-  select(-uci,-lci)%>%
-  spread(parameter, -item) %>%
-  expand_grid(., age = unique(comb_data$age)) %>%
-  mutate(sem_know = plogis(intercept + slope * age)) %>%
-  left_join(aoa_ratings) %>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-plot_sem_know_exp <- ggplot()+
-  geom_line(data = sem_know_map_exp, aes(x = age+2, y= sem_know, col = item, group = item),size = 1)+
-  ylab("Semantic knowledge")+
-  xlab("Age")+
-  ylim(0,1)+
-  theme_few()+
-  scale_colour_viridis_d(name = "Object")
-
-# plot or speaker optimality
-
-speak_opt_exp <- global_params_exp%>%
-  filter(parameter == "speaker_optimality")
-
-speak_opt_line_exp <- speak_opt_exp%>%
-  filter(iteration %in% select)%>%
-  spread(type, value)%>%
-  expand_grid(., age = unique(comb_data$age))%>%
-  mutate(y = intercept + slope * age)
-
-speak_opt_map_exp <- global_params_summary_exp%>%
-  ungroup()%>%
-  filter(parameter == "speaker_optimality")%>%
-  select(type, mode)%>%
-  spread(type, mode)%>%
-  expand_grid(., age = unique(comb_data$age))%>%
-  mutate(y = intercept + slope * age)
-
-plot_speak_opt_exp <- ggplot() +
-  geom_line(data = speak_opt_line_exp, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
-  geom_line(data = speak_opt_map_exp, aes(x=age+2,y = y),size = 1)+
-  labs(x="Age",y="Speaker informativeness")+
-  theme_few() +
-  ylim(0,10)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F, col = F)
-
-# Plot prior sensitivity
-
-prior_exp <- global_params_exp%>%
-  filter(parameter == "prior")
-
-prior_line_exp <- prior_exp%>%
-  filter(iteration %in% select)%>%
-  spread(type, value)%>%
-  expand_grid(., age = unique(comb_data$age))%>%
-  mutate(y = plogis(intercept + slope * age))
-
-prior_map_exp <- global_params_summary_exp%>%
-  ungroup()%>%
-  filter(parameter == "prior")%>%
-  select(type, mode)%>%
-  spread(type, mode)%>%
-  expand_grid(., age = unique(comb_data$age))%>%
-  mutate(y = plogis(intercept + slope * age))
-
-plot_prior_exp <- ggplot() +
-  geom_line(data = prior_line_exp, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
-  geom_line(data = prior_map_exp, aes(x=age+2,y = y),size = 1)+
-  labs(x="Age",y="Prior sensitivity")+
-  theme_few() +
-  ylim(0,1)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F, col = F)
-
-```
-
-```{r fig8, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity.
-Solid lines in show the MAP estimate for each parameter.
-Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty.
-(A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
-ggarrange(plot_sem_know_exp, plot_speak_opt_exp, plot_prior_exp , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1))
-```
-
-### Integration model
+```
+
+The *integration model* in this section differs from the same model in the prediciton section only in the distributions for the parameters representing the different information sources.
+Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the appendix show how the  parameter distributions differ between the prediction and the explanation version of the *integration* model.
+As a quick summary we can say that semantic knowledge and speaker inforamtiveness are rougly similar, the intercept for common ground sensitivity is estimated to be larger and the slope shallower when taking into account all the data comapred to when estiamting these parameters only based on experiment 1 and 2 respectively.
+Figure \@ref(fig:fig9) shows model predicions for the *integration model* in comparison to the data from experiment 3.
 
@@
 
+\begin{equation} 
+P_{L_1}(r, \mathcal{L}|u) = \phi P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)
+\end{equation}
+
+The posterior distribution for the mixture parameter $\phi$ is shown in figure \@ref(fig:fig10)A.
+It suggests that the mutual exclusivity inference is weighted as slightly more important compared to the common ground inference.
+
+```{r}
+item_params_mixture <- readRDS("../saves/item_params_mm.rds")
+
+global_params_mixture <- readRDS("../saves/global_params_mm.rds")
+
+mixture_parameter <- readRDS("../saves/mixture_mm.rds")
+```
+
+```{r}
+plot_mixture <- ggplot(mixture_parameter, aes(x = p_informative))+
+  geom_density(alpha = 0.8, adjust = 2)+
+  xlab("Proportion mutual exclusivity component")+
+  xlim(0,1)+
+  theme_few()
+
+```
+
+### Developmental mixture model
+
+For this model, we make the mixture parameter $\phi$ a function of age and estimate the intercept and slope that result in the best model predictions compared to the data from experiment 3.
+Figure \@ref(fig:fig10)B visualizes the developmental trajectory of the mixture parameter.
+Based on this model, the common ground inference seems to decrease in importance compared to the mutual exclusivity infernence.
+
+```{r}
+item_params_dev_mixture <- readRDS("../saves/item_params_dmm.rds")
+
+global_params_dev_mixture <- readRDS("../saves/global_params_dmm.rds")
+
+developmental_mixture_parameter <- readRDS("../saves/mixture_dmm.rds")
+```
+
+```{r}
+select_dev_mix <- sample(1:20000, 50)
+
+plot_mixture_line <- developmental_mixture_parameter%>%
+  filter(iteration %in% select_dev_mix) %>%
+  spread(type, value) %>%
+  expand_grid(.,age = unique(comb_data$age)) %>%
+  mutate(mixture = plogis(intercept + slope * age))
+
+plot_dev_mixture <- ggplot() +
+  geom_line(data = plot_mixture_line, aes(x=age+2,y = mixture, group = interaction(chain,iteration)),size = .2, alpha = .1)+
+  labs(x="Age",y="Proportion mutual exclusivity component")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F)
+
+```
+
+```{r fig10, include = T, fig.align = "center", fig.cap = "Mixture component for the mixture model (A) and the developmental mixture model (B).
+(A) shows the posterior distribution of the mixture component and (B) shows developmental trajectories for the mixture component based on 300 random draws from the posterior distribution for intercept and slope.", fig.width=12, fig.height = 4}
+ggarrange(plot_mixture, plot_dev_mixture,  labels = c("A","B"), nrow = 1)
+```
+
 ### Model comparison
 
-```{r fig10, include = T, fig.align = "center", fig.cap = "Explaining information integration.
+```{r fig11, include = T, fig.align = "center", fig.cap = "Explaining information integration.
 Correlations between model predictions and data binned by year, item and condition.
@@
 
-plot_cor_model_exp <- readRDS( "../saves/corr_model_data_exp.rds")
+plot_cor_model_exp <- readRDS( "../saves/corr_model_data_exp.rds")%>%
+  mutate(model = factor(model, levels = c("integration", "mixture", "developmental mixture")))
 
@@
 
-knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2)
-```
-
-[overview fig, correlations for all models]
-
-## Comparing model parameters
+knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2, align = "l")
+```
 
 # Discussion
+
+# Appendix: Comparing model parameters
+
+## Semantic knowledge
+
+### Intercept
+
+```{r}
+item_comp <- bind_rows(
+  item_params_exp %>% mutate(model = "integration (explanation)"),
+  item_params %>% mutate(model = "integration (prediction)"),
+  item_params_mixture %>% mutate(model = "mixture"),
+  item_params_dev_mixture %>% mutate(model = "developmental mixture")
+)
+
+```
+
+```{r figa1, include = T, fig.align = "center", fig.cap = "Posterior distribution of intercept term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
+
+item_comp_int <- item_comp %>%
+  filter(parameter == "intercept")
+
+ggplot(item_comp_int, aes(x = value, fill = model, col = model))+
+  geom_density(alpha = 0.8, adjust = 2)+
+  xlab("value")+
+  facet_wrap( ~ item, nrow = 2, scales = 'free')+
+  theme_few()+
+  xlim(-10,5)+
+  theme(legend.position = "bottom")+
+  scale_fill_ptol()+
+  scale_color_ptol()
+```
+
+### Slope
+
+```{r figa2, include = T, fig.align = "center", fig.cap = "Posterior distribution of slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
+
+item_comp_slope <- item_comp %>%
+  filter(parameter == "slope")
+
+ggplot(item_comp_slope, aes(x = value, fill = model, col = model))+
+  geom_density(alpha = 0.8, adjust = 2)+
+  xlab("value")+
+  facet_wrap( ~ item, nrow = 2, scales = 'free_y')+
+  xlim(-1,4)+
+  theme_few()+
+  ggtitle("Semantic knowledge by object - Slope")+
+  theme(legend.position = "bottom")+
+  scale_fill_ptol()+
+  scale_color_ptol()
+```
+
+## Speaker informativeness and common ground sensitivity
+
+```{r figa3, include = T, fig.align = "center", fig.cap = "Posterior distribution of slope and intercept terms for speaker informativeness and sensitivity to common ground by model.", fig.width=8, fig.height = 6, fig.align="center"}
+
+global_comp <- bind_rows(
+  global_params_exp %>% mutate(model = "integration (explanation)"),
+  global_params %>% mutate(model = "integration (prediction)"),
+  global_params_mixture %>% mutate(model = "mixture"),
+  global_params_dev_mixture %>% mutate(model = "developmental mixture")
+)%>%
+  filter(parameter !="global_sem")%>%
+  mutate(parameter = fct_recode(parameter, 
+                               "common ground sensitivity" = "prior",
+                               "speaker informativeness" = "speaker_optimality"))
+
+ggplot(global_comp, aes(x = value, fill = model, col = model))+
+  geom_density(alpha = 0.8, adjust = 2)+
+  xlab("value")+
+  facet_grid(type ~ parameter, scales = 'free')+
+  theme_few()+
+  theme(legend.position = "bottom")+
+  scale_fill_ptol()+
+  scale_color_ptol()
+```

### 2020-03-17 paper/supplementary_material.Rmd
advance supplementary material

@@
 
-knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, size="small")
+knitr::opts_chunk$set(echo=F, warning=FALSE, message=FALSE, size="small")
 
@@
 
-First empirical studies.
-Then the general modelling framework and the pragmatic model in detail.
-Then we turn to results.
-First prediction (i.e.
-which model makes the best predictions about integration based on only the experiments for the individual inferences) then explanation, that is, if we use all the data that we have, how can we best explain what is happening.
-Here we fit the models to the integration data.
-We consider two hypothesis.
-First our pragmatic model in which the Me inference is conditional on the prior, second a mixture model in which the two inferences are computed separately and mixed by a certain ratio.
-We also explore a developmental mixture model in which we allow the mixture component to change with age.
+The goal of this study is to investigate the integration of semantic and pragmatic information during word learning in children between 2 and 5 years of age.
+As a first step, we replicate earlier work showing that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge.
+In a second experiment, we show that children make inferences about word meanings based on common ground.
+In a third experiment, we find that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.
+
+Next, we introduce a computational framework which we use to formalize the process of how the inferences are integrated.
+As a part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground.
+We then use the our modelling framework to ask which of these information sources are necessary to predict children's responses in experiment 3.
+
+In the final section, we turn to the process by which information is integrated.
+We contrast the process of rational Bayesian inference we introduced in our model with a process in which one type of inference is given more weight.
+As part of this, we also explore alternative ways to think about developmental change in the integration process.
 
@@
 
-```{r table1}
+```{r table1, echo=T}
 chance_me <- me_data %>%
@@
 
-```{r}
-
+```{r, echo=T}
 # prior_me <- c(prior(normal(0, 5), class = Intercept),
@@
 bm_me <- readRDS("../saves/bm_me.rds")
-
+```
+
+```{r}
 fixef_me <- as_tibble(fixef(bm_me), rownames = "term")
@@
 
-talk about sd around item as evidence for variation
-
 As a second step, we investigated how the inference changed as a function of age and the familiar object.
@@
 C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}
-
 ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1))
-
 ```
@@
 
-```{r table2}
+```{r table2, echo=T}
 chance_prior <- prior_data %>%
@@
 
-```{r}
+```{r, echo=T}
 # prior_cg <- c(prior(normal(0, 5), class = Intercept),
@@
 bm_cg <- readRDS("../saves/bm_cg.rds")
-
+```
+
+```{r}
 fixef_cg <- as_tibble(fixef(bm_cg), rownames = "term")
@@
 
-```{r}
+```{r, echo=T}
 
@@
 bm_comb <- readRDS("../saves/bm_comb.rds")
-
+```
+
+```{r}
 fixef_comb <- as_tibble(fixef(bm_comb), rownames = "term")
@@
 Vertical and horizontal error bars show 95\\% HDI.
-Blue diamonds show congruent condition and red ones show the incongruent condition.", fig.width=12, fig.height = 6}
+Blue diamonds show congruent condition and red ones show the incongruent condition.", fig.width=12, fig.height = 8}
 
@@
 We explore alternative ways to think about information integration.
-The *integration model* outlined above operates via Bayesian inference in that the prior probability of a referent - following the common ground manipulation - is updated upon hearing the utterance and computing the mutual exclusivity inference.
+The *integration model* outlined above operates via Bayesian inference in that the prior probability of a referent - a consequence of the common ground manipulation - is updated upon hearing the utterance and computing the mutual exclusivity inference.
 In essence, this model is a multiplicative model because the probability of each referent is proportional to the product of the likelihood and the prior.
@@
 This *mixture model* assumes that the two inferences are computed separately and then weighted by some ratio $\phi$.
+Psychologically, $\phi$ may be interpreted as a bias for one type of inference relative to the other.
 
@@
 As an alternative, we explore a *developmental mixture model*.
-This model makes the same assumptions about developmental chnage in the individual information sources but, in addition, also assumes that the way that the the mutual exclusivity and the common ground inference are combined with one another changes over time.
+This model makes the same assumptions about developmental change in the individual information sources but, in addition, also assumes that the way that the the mutual exclusivity and the common ground inference are combined with one another changes over time.
 It is structurally identical to the *mixture model* but the mixture parameter $\phi$ is a function of age.
@@
 In this section, we make use of all the available data.
-That is, we ask which process best explains the way that the different information sources are combined in the combination data from experiment 3.
 We use the data from experiment 1 and 2 to compute prior distributions over model parameters which are subsequently updated depending on how well the model predictions they generate fit the data.
@@
 
-The *integration model* in this section differs from the same model in the prediciton section only in the distributions for the parameters representing the different information sources.
+The *integration model* in this section differs from the same model in the prediction section only in the distributions for the parameters representing the different information sources.
 Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the appendix show how the  parameter distributions differ between the prediction and the explanation version of the *integration* model.
-As a quick summary we can say that semantic knowledge and speaker inforamtiveness are rougly similar, the intercept for common ground sensitivity is estimated to be larger and the slope shallower when taking into account all the data comapred to when estiamting these parameters only based on experiment 1 and 2 respectively.
-Figure \@ref(fig:fig9) shows model predicions for the *integration model* in comparison to the data from experiment 3.
+As a quick summary, we can say that semantic knowledge and speaker informativeness have similar distributions when taking into account all the data compared to when estimating these parameters only based on experiment 1 and 2.
+In contrast, the intercept for common ground sensitivity is estimated to be larger and the slope shallower.
+The code to run the model can be found in the associated online repository (file: xxxxxxx).
+Figure \@ref(fig:fig9) shows model predictions for the *integration model* in comparison to the data from experiment 3.
 
@@
 
+In the *mixture model* the two inferences are computed in the same way as in in the *integration model*. Subsequently, they are weighted by the mixture parameter $\phi$:
+
 \begin{equation} 
@@
 
+To estimate $\phi$ as well as the other parameters, we make use of all the available data.
+The model code can be found in the associated online repository (file: xxxxxxx).
 The posterior distribution for the mixture parameter $\phi$ is shown in figure \@ref(fig:fig10)A.
@@
 
-For this model, we make the mixture parameter $\phi$ a function of age and estimate the intercept and slope that result in the best model predictions compared to the data from experiment 3.
+For this model, we make the mixture parameter $\phi$ a function of age and estimate the intercept and slope that yield the best model predictions compared to the data from experiment 3.
 Figure \@ref(fig:fig10)B visualizes the developmental trajectory of the mixture parameter.
-Based on this model, the common ground inference seems to decrease in importance compared to the mutual exclusivity infernence.
+Based on this model, the common ground inference seems to decrease in importance compared to the mutual exclusivity inference with age.
 
@@
 ```{r fig10, include = T, fig.align = "center", fig.cap = "Mixture component for the mixture model (A) and the developmental mixture model (B).
-(A) shows the posterior distribution of the mixture component and (B) shows developmental trajectories for the mixture component based on 300 random draws from the posterior distribution for intercept and slope.", fig.width=12, fig.height = 4}
+(A) shows the posterior distribution of the mixture component and (B) shows developmental trajectories for the mixture component based on 300 random draws from the posterior distribution for intercept and slope.", fig.width=10, fig.height = 4, fig.align= "center"}
 ggarrange(plot_mixture, plot_dev_mixture,  labels = c("A","B"), nrow = 1)
@@
 ### Model comparison
+
+We compared models based on correlations and Bayes factors.
+Figure \@ref(fig:fig11) shows correlations between model predictions and the data, each binned by year and object.
+Even though model predictions and data are closely aligned for all models, the *integration model* shows the highest correlation in all age groups.
+Next we directly compared models based using Bayes factors (see Table \@ref(tab:table4)).
+We also included the prediction *integration model* into this analysis.
+
+Perhaps unsurprisingly, we see that updating the parameters for semantic knowledge, speaker informativeness and common ground sensitivity greatly improves the model fit (comparison: integration (explanation) vs integration (prediction)).
+We also see that the explanation *integration model* provides, by far, the best fit to the data compared to the two *mixture models*.
+Interestingly, the prediction *integration model* also had a better fit, even though its parameters were not updated based on the data from experiment 3.
+When comparing the two *mixture models* directly, we see that an age sensitive mixture parameter did not result in a substantially better fit.
+
+This analysis shows that the inference and integration process described by the *ingetration model* accurately captures the data and also explains the integration process better compared to the additive *mixture models*.
+As a consequence, we may say that instead of being biased towards one type of inference, children are rationally integrating all the information sources available.
 
@@
 
-# Discussion
-
-# Appendix: Comparing model parameters
+# Summary
+
+Here we studied how 2 to 5 year old children integrate semantic and pragmatic information during word learning.
+In three experiments, we first showed that children make a mutual exclusivity inference and that this inference varied depending on children's familiarity with the objects involved (experiment 1).
+Next, we showed that children make common ground inferences based on their interactions with a speaker (experiment 2).
+When the two inferences were combined, we found that children were sensitive to the way in which they were aligned (experiment 3).
+
+We then introduced a computational model to investigate the process by which children integrated the inferences in experiment 3.
+As a start, we described mutual exclusivity as a pragmatic inference, which takes in children's emerging semantic knowledge and their expectations about how informative a speaker is.
+The *integration model* assumes that this inference is then flexibly integrated with children's developing sensitivity to common ground.
+
+Next, we tested the predictive power of this model.
+That is, we asked how well the model would predict the data of experiment 3, when only knowing the developmental trajectories for mutual exclusivity (based on experiment 1) and common ground (experiment 2).
+We found a very close alignment of the model predictions and the data across the entire age range.
+Furthermore, the *integration model* provided a better fit to the data compared to a number of lesion models, which selectively omitted one type of information.
+This suggests that children flexibly integrate all available information.
+
+In the final section, we studied which process best explained children's information integration.
+We compared the *integration model* to a *mixture model* which assumed that children are biased towards one type of inference.
+We found that the *integration model* better explained the data compared to these alternative model.
+In sum, we found that children's integration of semantic and pragmatic information during word learning is best described as a form of rational social inference.
+
+# Appendix: Model parameters
+
+In the following, we visualize the model parameters for semantic knowledge, speaker informativeness and common ground sensitivity.
+Please note that the alternative lesion models presented in the prediction section used the same parameter distributions as the prediction *integration model*.
 
@@
   item_params_dev_mixture %>% mutate(model = "developmental mixture")
-)
+)%>%
+  mutate(model = factor(model, levels = c("integration (prediction)","integration (explanation)", "mixture","developmental mixture")))
 
@@
   theme(legend.position = "bottom")+
-  scale_fill_ptol()+
-  scale_color_ptol()
+  scale_fill_ptol(name = "Model")+
+  scale_color_ptol(name = "Model")
 ```
@@
   theme_few()+
-  ggtitle("Semantic knowledge by object - Slope")+
   theme(legend.position = "bottom")+
-  scale_fill_ptol()+
-  scale_color_ptol()
+  scale_fill_ptol(name = "Model")+
+  scale_color_ptol(name = "Model")
 ```
@@
                                "common ground sensitivity" = "prior",
-                               "speaker informativeness" = "speaker_optimality"))
+                               "speaker informativeness" = "speaker_optimality"))%>%
+  mutate(model = factor(model, levels = c("integration (prediction)","integration (explanation)", "mixture","developmental mixture")))
 
@@
   theme(legend.position = "bottom")+
-  scale_fill_ptol()+
-  scale_color_ptol()
-```
+  scale_fill_ptol(name = "Model")+
+  scale_color_ptol(name = "Model")
+```

### 2020-03-18 paper/supplementary_material.Rmd
add model comparison to check for item effects in exp 1 and 3

@@
 The goal of this study is to investigate the integration of semantic and pragmatic information during word learning in children between 2 and 5 years of age.
-As a first step, we replicate earlier work showing that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge.
+As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning.
+In experiment 1, we show that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge.
 In a second experiment, we show that children make inferences about word meanings based on common ground.
@@
 In the final section, we turn to the process by which information is integrated.
-We contrast the process of rational Bayesian inference we introduced in our model with a process in which one type of inference is given more weight.
+We contrast the process of rational Bayesian inference we introduced in our model with a biased integration process in which one type of inference is given more weight.
 As part of this, we also explore alternative ways to think about developmental change in the integration process.
@@
 The first goal of this experiment was to quantify developmental change in the age range tested.
-The second goal of Experiment 1 was to test the role of semantic knowledge [cf.
+The second goal was to test the role of semantic knowledge [cf.
 @lewis2020-me].
@@
 That is, when the familiar object is an object for which children are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object.
-To test this, we systematically varied the familiar object that was presented with the novel object.
+To test this, we systematically varied the familiar object that were presented alongside the novel object.
 
@@
 All experiments were approved by the Stanford Institutional Review Board (protocol no.
-19960)
+19960).
 
@@
 Figure \@ref(fig:fig1)A shows the general setup.
-Children saw an animal between two tables.
+Children saw an animal standing on a little hill between two tables.
 For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to make requests.
-Each experiment started with two training trials in which the speaker requested a known object (car and ball).
-
-In Experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study).
+Each experiment started with two training trials in which the speaker requested known objects (car and ball).
+
+In experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study).
 The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?".
@@
 #   saveRDS(.,"../saves/bm_me.rds")
+# 
+# 
+# bm_me2 <- brm(correct ~ age + (1|subid) + (age | agent),
+#                     data = me_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99, max_treedepth = 20),
+#           sample_prior = F,
+#           prior = prior_me,
+#           cores = 4,
+#           chains = 4,
+#           iter = 5000)%>%
+#   saveRDS(.,"../saves/bm_me.rds")
 
 bm_me <- readRDS("../saves/bm_me.rds")
+
+bm_me2 <- readRDS("../saves/bm_me2.rds")
+
 ```
@@
 That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects).
-We did not pre-register agent as a random effect, but decided to included it to be consistent with Experiment 2 and 3.
+We did not pre-register agent as a random effect, but retrospecitvely included it to be consistent with Experiment 2 and 3.
 
@@
 Older children were more likely to make a mutual exclusivity inference.
-Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and shows that there was substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory.
+To assess the variability accross objects, we compared the fit of the above model to a model lacking `object` as a random effect.
+Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights.
+The WAIC score is an indicator of the model’s predictive accuracy for out of sample data; model’s with lower scores are preferred.
+WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data.
+The model including object provided a much better fit compared to the model lacking it (see Table \@ref(tab:table2)).
+Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and illustrates the substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory.
 Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept.
@@
 Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect.
-Taken together, the mutual exclusivity inference depended on age as well as the familiar object.
+Taken together, the strength  of the mutual exclusivity inference depended on age as well as the familiar object.
+
+```{r table2, echo=T}
+
+me_waic <- brms::waic(bm_me, bm_me2, compare = F)
+
+me_weights <- model_weights(bm_me, bm_me2, weights = "waic")
+
+me_comp <- tibble(
+  Model = c("with object as RE", "without object as RE"),
+  WAIC = round(c(me_waic$loos$bm_me$estimates["waic","Estimate"],me_waic$loos$bm_me2$estimates["waic","Estimate"]),2),
+  SE = round(c(me_waic$loos$bm_me$estimates["waic","SE"],me_waic$loos$bm_me2$estimates["waic","SE"]),2),
+  weight = round(c(me_weights[1],me_weights[2]))
+)
+
+knitr::kable(me_comp, caption = "Model comparison in experiment 1 based on WAIC scores and weights.", digits = 2, align = "l")
+```
 
@@
 
-```{r table2, echo=T}
+```{r table3, echo=T}
 chance_prior <- prior_data %>%
@@
 
-Table \@ref(tab:table2) compares children's correct responses to a level expected by chance (50%).
+Table \@ref(tab:table3) compares children's correct responses to a level expected by chance (50%).
 We found evidence that, as a group, 3- and 4-year-olds, but not 2-year-olds, inferred that the novel word referred to the object that was new to the speaker.
@@
 #   saveRDS(.,"../saves/bm_comb.rds")
+# 
+# bm_comb2 <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | agent),
+#                     data = comb_data, family = bernoulli(),
+#           control = list(adapt_delta = 0.99, max_treedepth = 20),
+#           sample_prior = F,
+#           prior = prior_comb,
+#           cores = 4,
+#           chains = 4,
+#           inits = 0,
+#           iter = 5000)%>%
+#   saveRDS(.,"../saves/bm_comb2.rds")
 
 bm_comb <- readRDS("../saves/bm_comb.rds")
+
+bm_comb2 <- readRDS("../saves/bm_comb2.rds")
+
 ```
@@
 The interaction term was weakly - though not entirely - negative, suggesting a shallower slope for age in the incongruent condition (*$\beta$* = `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q97.5)%>%round(2)`).
+A model lacking `object` as a random effect provided a much poorer fit, suggesting substantial variation across objects (see Table \@ref(tab:table4)).
 Figure \@ref(fig:fig3)B visualizes the model.
 Taken together, the results show that children responded to the way the two inferences were aligned with one another.
+
+```{r table4, echo=T}
+
+comb_waic <- brms::waic(bm_comb, bm_comb2, compare = F)
+
+comb_weights <- model_weights(bm_comb, bm_comb2, weights = "waic")
+
+comb_comp <- tibble(
+  Model = c("with object as RE", "without object as RE"),
+  WAIC = round(c(comb_waic$loos$bm_comb$estimates["waic","Estimate"],comb_waic$loos$bm_comb2$estimates["waic","Estimate"]),2),
+  SE = round(c(comb_waic$loos$bm_comb$estimates["waic","SE"],comb_waic$loos$bm_comb2$estimates["waic","SE"]),2),
+  weight = round(c(comb_weights[1],comb_weights[2]))
+)
+
+knitr::kable(comb_comp, caption = "Model comparison in experiment 3 based on WAIC scores and weights.", digits = 2, align = "l")
+```
 
@@
 
-## Modelling framework
+## Modeling framework
 
@@
 We first calculated the marginal log-likelihood for each model and then computed Bayes factors by subtracting the log-likelihoods for the models involved in the comparison and then exponentiating the result (see file `model_comparison.Rmd` in the associated online repository).
-Table \@ref(tab:table3) lists the Bayes factors for the different model comparisons.
+Table \@ref(tab:table5) lists the Bayes factors for the different model comparisons.
 The results show that the *integration model*, by far, outperformed all the other models.
@@
 
-```{r table3}
+```{r table5}
 model_comp_pred <- readRDS("../saves/pred_model_comparison.rds")%>%
@@
 \begin{equation} 
-P_{L_1}(r, \mathcal{L}|u) = \phi P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)
+to be adjusted .... P_{L_1}(r, \mathcal{L}|u) = \phi P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)
 \end{equation}
@@
 Even though model predictions and data are closely aligned for all models, the *integration model* shows the highest correlation in all age groups.
-Next we directly compared models based using Bayes factors (see Table \@ref(tab:table4)).
+Next we directly compared models based using Bayes factors (see Table \@ref(tab:table6)).
 We also included the prediction *integration model* into this analysis.
@@
 
-```{r table4}
+```{r table6}
 model_comp_pred <- readRDS("../saves/expl_model_comparison.rds")%>%

### 2020-03-30 paper/supplementary_material.Rmd
edits upto model comparison, prediction section

@@
 Next, we ask how well this model *predicts* how children integrate the two information sources.
-That is, in a situation in which we know the development trajectories for the mutual exclusivity inference as well as for the common ground inference, what can we say about what happens when they are combined.
+That is, in a situation in which we know the development trajectories for the mutual exclusivity inference as well as for the common ground inference, what can we say about what happens when common ground and mutual exclusivity are combined.
 We then test the predictive power of the model by comparing the model predictions to the data from experiment 3.
-We will use model comparisons to test the *integration model* against a range of alternative models.
+We use formal model comparison methods to test the *integration model* against a range of alternative models.
 
@@
 We then compare the model to a range of alternative models that make different assumptions about how information is integrated and how this process develops.
-This approach answers the question of how we can best explain how children are integrating the different information sources.
+This approach answers the question of how we can best explain how children integrate the different information sources.
 
@@
 
-The model captures the following process.
-A listener is reasoning about the referent of a speaker's utterance while at the same time trying to learn a lexicon (object--word mappings).
+Our model describes a listener jointly reasoning about the referent of a speaker's utterance and trying to learn a lexicon (object--word mappings).
 This reasoning is contextualized by the prior probability of each referent.
 This prior probability is thought to be a function of the common ground shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later.
-We assume that the degree to which interactions around objects change their prior probability depend on the child's age.
+We assume that the degree to which interactions around objects are integrated into the common ground and thus change the prior probability of those objects depends on the child's age.
 
@@
 This speaker is assumed to compute the informativity of for each available utterance and then choose the most informative one.
-However, this expectation of speaker informativeness may vary and is captured by the term alpha.
-In particular, we take alpha to be a function of the child's age.
-
-The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their literal semantics, would infer upon hearing it.
-Thus, this reasoning depends what kind of word--object mappings the speaker thinks the literal listener knows.
-We assume that knowing the literal semantics of a word is not deterministic but probabilistic.
-That is, for each object involved there is a probability p that the literal listener knows the word for it.
-For each of the novel objects, this semantic knowledge is 0.
-For familiar objects, it depends on the kind of object as well as on the child's age.
+However, this expectation of speaker informativeness may vary and is captured by the parameter $\alpha$.
+In particular, we take $\alpha$ to be a function of the child's age.
+
+The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their literal semantics, would infer upon hearing the utterance.
+Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows.
+We assume that a listener's knowledge of a word's semantics is graded (not categorical).
+That is, for each object involved there is a probability $p$ that the literal listener knows the word for it.
+For each of the novel objects, this semantic knowledge is 0, which assumes that there is a no *a priori* reason to associate a particular novel object with a particular novel word.
+(MH: <-- is this what this represents?
+or does it represent the fact that there is no reason to associate a novel object with a familiar word?) For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the kind of object (its expected acquisition trajectory) as well as on the child's age.
 
@@
 
-The model description above points to three potential loci of developmental change: semantic knowledge, expectations about speaker informativeness and common ground sensitivity.
-Each of theses components is represented by a parameter in the model.
+The model description above points to three potential loci of developmental change: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground.
+Each of theses components is represented by a parameter that plays a particular functional role in the model.
 We capture developmental change by making these parameters a function of age and therefore estimating a developmental trajectory (intercept and slope) for each parameter.
@@
 Semantic knowledge captures the degree of certainty with which the naive listener is assumed to know the label for the familiar object.
-When faced with the task, we think that children take their own semantic knowledge as the basis.
-As a consequence, semantic knowledge differs between familiar objects.
+(MH: UNCLEAR --> When faced with the task, we think that children take their own semantic knowledge as the basis.) As a consequence, semantic knowledge differs between familiar objects.
 For objects whose labels are generally acquired earlier (e.g.
-carrot) semantic knowledge is high whereas for others (e.g.
-pawn) semantic knowledge is lower.
-However, semantic knowledge also varies with age in that older children are more likely to know the labels for more of the familiar objects compared to younger children.
+carrot) semantic knowledge should generally be high whereas for others (e.g.
+pawn) semantic knowledge should generally be lower.
+However, semantic knowledge also varies with age such that older children are more likely to know the labels for more of the familiar objects compared to younger children.
 As a consequence, each familiar object has a unique developmental trajectory with respect to semantic knowledge.
-Technically, the object specifics parameters are estimated in the form of a random effects model, that is, each object's trajectory is estimated as a deviation from an overall trajectory for semantic.
-This overall trajectory represent an increase in semantic knowledge that is independent of a particular familiar object.
-
+Technically, the object-specific parameters are estimated in the form of a hierarchical regression (mixed-effects) model; that is, each object's trajectory is estimated as a deviation from an overall trajectory of vocabulary development.
+This overall (vocabulary) trajectory represents the development of semantic knowledge that is independent of a particular familiar object--label pairing.
+
+(MH: This paragraph is opaque)
 Semantic knowledge enters the likelihood term of the model specified above.
@@
 
-A second locus of developmental change are expectations about speaker informativeness.
-In the context of the model, speaker informativeness corresponds to the degree with which the listener expects the speaker to choose the most informative of all available utterances.
-We assume that children at different ages might have different expectations about how rational or informative speakers are.
-As mentioned above, this parameter jointly estimated with the parameters for semantic knowledge.
+A second locus of developmental change is a listener's expectations about speaker informativeness.
+In the context of the model, speaker informativeness corresponds to the degree with which the listener expects the speaker to choose the most informative of the available utterances.
+We assume that children at different ages could have different expectations about how rational or informative speakers are.
+(MH: citation here, kids sensitivity to informativeness?) As mentioned above, this parameter is jointly estimated with the parameters for semantic knowledge.
 
@@
 We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects.
-
-## Model fitting
+(MH: again, citation?)
+
+## Implementation details
 
@@
 The resulting predictions come in the form of distributions of developmental trajectories for each object in the congruent and the incongruent condition.
+(MH: Priors for parameters should be reported here.)
 
@@
 In this section we evaluate different models in terms of how well they *predict* information integration.
-That is, in a situation in which we know the development of the mutual exclusivity inference as well as the common ground inference, which model best predicts what happens when the two are combined (combination data from Experiment 3).
-Asking about "pure" prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g.
-mixture model, see below).
-To generate these predictions, we estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.
-
-To estimate the parameters for semantic knowledge and speaker informativeness, we adapted the model described above to a situation in which both objects (novel and familiar) have equal prior probability.
-We used the data from experiment 1 to then infer the parameters.
-That is, we inferred which intercepts and slopes for speaker informativeness and semantic knowledge would generate model predictions that corresponded to the average proportion of correct responses measured in experiment 1.
-To estimate the parameters representing sensitivity to common ground, we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in experiment 1.
-
-To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150 000 samples from each chain and removing the first 50 000 for burn-in.
-We removed samples from one chain because it converged on a local maximum which resulted in parameter distributions that were substantially different from the other chains.
+That is, in a situation in which we know the development of the mutual exclusivity inference as well as the common ground inference, we look at each model's ability to predict what happens when the two are combined (combination data from Experiment 3).
+Investigating "pure" (or, *a priori*) prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g., a heuristic, non-integrating mixture model, described below).
+To generate *a priori* predictions, we independently estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.
+
+To estimate the parameters for semantic knowledge and speaker informativeness, we adapted the model described above to a situation in which both objects (novel and familiar) have equal prior probability (i.e., no common ground information).
+We used the data from Experiment 1 to then infer the parameters.
+That is, we inferred the intercepts and slopes for speaker informativeness and semantic knowledge that  generated RSA model predictions to match the responses generated in Experiment 1.
+To estimate the parameters representing sensitivity to common ground, we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in Experiment 2.
+
+To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150,000 samples from each chain and removing the first 50,000 for burn-in.
+We excluded samples from one chain because it got stuck on a local maximum which resulted in parameter distributions that were substantially different from the other chains.
 The model outputs can be found in the following online repository: git large file storage.
@@
 Next, we combined the parameters according to the four models described below.
-Please note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in which parameters they included.
-The models described below are a full model (*integration model*) and three lesion models, which selectively omit one type of information.
+Note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in terms of which parameters they included.
+The models described below are a full model (*integration model*) and three lesioned models, which selectively omit one type of information.
 The following model comparison therefore asks which types of information are necessary to make good predictions about how information is integrated.
-We do not compare models that make different assumptions about how information is integrated.
-We turn to this question in the [explanation](#explanation) section.
+We do not compare models that make different assumptions about how information is integrated, since they require additional parameters specific to Experiment 3.
+We consider the question of alternative integration models in the [explanation](#explanation) section.
 
@@
 The integration model serves as the full model and takes in all available information.
-That is, it takes in object specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above.
+That is, it takes in object-specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above.
 Figure \@ref(fig:fig5) visualizes the corresponding model predictions in comparison to the data from experiment 3.
@@
 
-#### No word knowledge model
-
-This model is the first lesion model.
-It takes in speaker informativeness and common ground sensitivity as well as general semantic knowledge, but omits semantic knowledge that is specific to the familiar objects.
-We described above that the parameters for semantic knowledge are fitted via a mixed effects model.
-On the one hand, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object specific variation around this trajectory (random effects).
-The *no word knowledge* model takes in the overall trajectory for semantic knowledge but ignores object specific variation.
+#### No word-specific knowledge model
+
+The first lesionsed model takes in speaker informativeness and common ground sensitivity as well as general semantic knowledge, but omits semantic knowledge that is specific to the familiar objects.
+We described above that the parameters for semantic knowledge are fitted via a hiearchical regression (mixed effects) model.
+In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects).
+The *no word knowledge* model takes in the overall trajectory for semantic knowledge but ignores object-specific variation.
 That is, the model assumes a listener whose mutual exclusivity inference does not vary depending on the particular familiar object but only depends on the average semantic knowledge.
@@
 This model takes in object specific semantic knowledge and speaker informativeness but ignores common ground.
-Thus, the prior distribution over objects $P(r)$ in the model described above is flat (e.g.
-[0.5, 0.5].
+Thus, the prior distribution over objects $P(r)$ in the model described above is uniform (e.g., [0.5, 0.5]).
 This corresponds to a listener who only focuses on the mutual exclusivity inference and ignores the common ground manipulation.
-As a consequence the listener does not differentiate between the two alignment conditions.
+As a consequence, the listener does not differentiate between the two common ground alignment conditions.
 

### 2020-03-31 paper/supplementary_material.Rmd
work on MHs comments

@@
 That is, for each object involved there is a probability $p$ that the literal listener knows the word for it.
-For each of the novel objects, this semantic knowledge is 0, which assumes that there is a no *a priori* reason to associate a particular novel object with a particular novel word.
-(MH: <-- is this what this represents?
-or does it represent the fact that there is no reason to associate a novel object with a familiar word?) For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the kind of object (its expected acquisition trajectory) as well as on the child's age.
+For each of the novel objects, this semantic knowledge is 0, which assumes that the novel word is equaliy likely to refer to the novel object as it is to refer to the familiar object.
+For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the kind of object (its expected acquisition trajectory) as well as on the child's age.
 
@@
 Semantic knowledge captures the degree of certainty with which the naive listener is assumed to know the label for the familiar object.
-(MH: UNCLEAR --> When faced with the task, we think that children take their own semantic knowledge as the basis.) As a consequence, semantic knowledge differs between familiar objects.
+As a consequence, semantic knowledge differs between familiar objects.
 For objects whose labels are generally acquired earlier (e.g.
@@
 In the context of the model, speaker informativeness corresponds to the degree with which the listener expects the speaker to choose the most informative of the available utterances.
-We assume that children at different ages could have different expectations about how rational or informative speakers are.
-(MH: citation here, kids sensitivity to informativeness?) As mentioned above, this parameter is jointly estimated with the parameters for semantic knowledge.
+We assume that children at different ages could have different expectations about how rational or informative speakers are [see e.g.
+@bohn_tessler_merrick_frank_2019; @frank2014inferring; @yoon2019role].
+As mentioned above, this parameter is jointly estimated with the parameters for semantic knowledge.
 
@@
 Thus, it captures the salience of an object due to its role in the social interaction that precedes the utterance.
-We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects.
-(MH: again, citation?)
+We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [akhtar1996role; @diesendruck2004two].
 
@@
 All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
-The corresponding model code can be found in the associated online repository and includes information about the prior distributions for all parameters (file xxxxx).
-To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and common ground sensitivity and then passed them through the model in line with the different ways in which they can be combined and aligned.
+The corresponding model code can be found in the associated online repository (file xxxxx).
+To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned.
 The resulting predictions come in the form of distributions of developmental trajectories for each object in the congruent and the incongruent condition.
-(MH: Priors for parameters should be reported here.)
+
+We used the following prior distributions for model parameters.
+Intercept and slope for sensitivity to common ground: $unif(-2,2)$.
+For the speaker informativeness we used $unif(-3,3)$ for the intercept $unif(-0,4)$ for the slope.
+We restricted the slope to be positive because negative values for speaker informativeness are conceptually implausible.
+For semantic knowledge we used $unif(-3,3)$ for the intercept and $unif(0,2)$ for the slope, again because negative values of semantic knowledge have no meaningful interpretation.
+For the parameter capturing the variability the object specific trajectories around these overall parameters we used $unif(0,2)$ for the intercept and $unif(0,1)$ for the slope.
+Some choices regarding these prior distributions were made to ease model convergence.
+However, please note that all models considered used the same prior distributions.
 

### 2020-03-31 paper/visualizations.Rmd
work on MHs comments

--- 2020-03-18 paper/supplementary_material.Rmd
@@
 title: "Word learning at the semantics pragmatics interface"
-subtitle: "Supplementary material"
-author: "Manuel Bohn, Michael Henry Tessler and Michael C. Frank"
-output: 
-  bookdown::html_document2:
-    toc: yes
-    toc_float: true
-    fig_caption: yes
-    code_folding: hide
-    number_sections: false
-bibliography: library.bib
-#csl: pnas.csl
-header-includes:
-  \usepackage{caption}
-  \renewcommand{\thetable}{S\arabic{table}} 
-  \renewcommand{\thefigure}{S\arabic{figure}}
+output: html_document
 ---
@@
 library(rwebppl)
-library(brms)
+library(gridExtra)
 library(coda)
@@
 library(BayesFactor)
+
+library(cowplot)
+library(magick)
 
@@
 ```
-
-# Overview
-
-The goal of this study is to investigate the integration of semantic and pragmatic information during word learning in children between 2 and 5 years of age.
-As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning.
-In experiment 1, we show that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge.
-In a second experiment, we show that children make inferences about word meanings based on common ground.
-In a third experiment, we find that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.
-
-Next, we introduce a computational framework which we use to formalize the process of how the inferences are integrated.
-As a part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground.
-We then use the our modelling framework to ask which of these information sources are necessary to predict children's responses in experiment 3.
-
-In the final section, we turn to the process by which information is integrated.
-We contrast the process of rational Bayesian inference we introduced in our model with a biased integration process in which one type of inference is given more weight.
-As part of this, we also explore alternative ways to think about developmental change in the integration process.
-
-# Empirical studies
-
-## Experiment 1: Mutual exclusivity
-
-The first experiment tested the so called mutual exclusivity inference in children between 2 and 5 years of age.
-The general phenomena is that when presented with a familiar and an unfamiliar object, children expect a novel word to refer to the unfamiliar object [e.g.
-@markman1988children].
-A range of explanations have been put forward for the cognitive basis of this inference [see @lewis2020-me for a discussion].
-Here, we treat the mutual exclusivity inference as pragmatic [e.g.
-@clark1987principle].
-The inference process is specified in the model below.
-
-The first goal of this experiment was to quantify developmental change in the age range tested.
-The second goal was to test the role of semantic knowledge [cf.
-@lewis2020-me].
-The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object.
-That is, when the familiar object is an object for which children are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object.
-To test this, we systematically varied the familiar object that were presented alongside the novel object.
-
-The experiment was preregistered at https://osf.io/gy37b. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_me.html`.
-
-### Participants
-
-We tested a total number of `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls).
-Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1).
-All children were recruited from the floor of a Children’s museum in San José, California, USA.
-This population is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status.
-Parents consented to their children’s participation and provided demographic information.
-All experiments were approved by the Stanford Institutional Review Board (protocol no.
-19960).
-
-### Procedure
-
-The experiment was presented as an interactive picture book on a tablet computer [@frank2016using].
-Figure \@ref(fig:fig1)A shows the general setup.
-Children saw an animal standing on a little hill between two tables.
-For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to make requests.
-Each experiment started with two training trials in which the speaker requested known objects (car and ball).
-
-In experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study).
-The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?".
-Children responded by touching one of the objects.
-The location of the novel object (left or right table) and the animal character were counterbalanced.
-Each child received 12 trials, one with each familiar object.
-The novel object also changed from trial to trial.
-We coded as correct choice if children chose the novel object as the referent of the novel word.
-
-```{r fig1,echo = F, fig.align = "center", fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
-knitr::include_graphics("../graphs/method_overview.png")
-```
-
-Each child completed 12 trials, each with a different familiar and a different novel object.
-Familiar objects were selected to vary along the dimension of how likely children were to know the word for each object.
-This including objects that most 2-year-olds could name (e.g.
-a duck) as well as objects that only very few 5-year-olds could name (e.g.
-a pawn).
-The selection was based on age of acquisition ratings from Kuperman and colleagues [-@kuperman2012age].
-While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned.
-Figure \@ref(fig:fig2)A shows the objects used in the experiment.
-We induced this variation to estimate the role of semantic knowledge in a mutual exclusivity inference.
-
-```{r, include = F}
-plot_aoa_ratings <- aoa_ratings%>%
-  mutate(image = paste("../experiments/kids/images/",item,".png", sep=""))
-
-plot_aoa <- ggplot(plot_aoa_ratings, aes(x = reorder(item, mean_aoa), y = mean_aoa)) +
-  geom_point(size =2, pch = 4)+
-  ylab("Mean rated age of acquisition")+
-  xlab("Object")+
-  ylim(0,15)+
-  geom_image(aes(image=image, y = mean_aoa+2), asp = 4)+
-  theme_light()+
-    theme(axis.text.x = element_text(angle = 45, hjust = 1))
-```
-
-### Results
-
-```{r table1, echo=T}
-chance_me <- me_data %>%
-  group_by(subage, subid) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(subage)%>%
-  mutate(Mean= round(mean(unlist(correct)),2),
-         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf), scientific = F),
-         `Age group` = subage)%>%
-  ungroup()%>%
-  select(`Age group`, Mean, BayesFactor)
-
-knitr::kable(chance_me, caption = "Proportion of children choosing the novel object compared to a level expected by chance based on a one sample Bayesian t-test.
-Responses are aggregated for each participant across familiar objects.", digits = 2, align = "l")
-```
-
-As a first step, we evaluated whether children made a mutual exclusivity inference.
-For this analysis, we aggregated participants' responses across familiar objects.
-We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes factor (BF) in favor of the hypothesis that children chose the novel object more often than expected by chance (50% correct).
-Table \@ref(tab:table1) shows that all age groups made the inference.
-
-```{r, echo=T}
-# prior_me <- c(prior(normal(0, 5), class = Intercept),
-#            prior(normal(0, 5), class = b),
-#            prior(cauchy(0, 1), class = sd))
-# 
-# 
-# bm_me <- brm(correct ~ age + (1|subid) + (age | item) + (age | agent),
-#                     data = me_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99, max_treedepth = 20),
-#           sample_prior = F,
-#           prior = prior_me,
-#           cores = 4,
-#           chains = 4,
-#           iter = 5000)%>%
-#   saveRDS(.,"../saves/bm_me.rds")
-# 
-# 
-# bm_me2 <- brm(correct ~ age + (1|subid) + (age | agent),
-#                     data = me_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99, max_treedepth = 20),
-#           sample_prior = F,
-#           prior = prior_me,
-#           cores = 4,
-#           chains = 4,
-#           iter = 5000)%>%
-#   saveRDS(.,"../saves/bm_me.rds")
-
-bm_me <- readRDS("../saves/bm_me.rds")
-
-bm_me2 <- readRDS("../saves/bm_me2.rds")
-
-```
-
-```{r}
-fixef_me <- as_tibble(fixef(bm_me), rownames = "term")
-
-ranef_me <-  ranef(bm_me)
-
-ranef_plot_me <- as_tibble(ranef_me$item, rownames = "item")%>%
-  mutate(grand_intercept = fixef_me%>%filter(term=="Intercept")%>%pull(Estimate),
-         grand_slope = fixef_me%>%filter(term=="age")%>%pull(Estimate))%>%
-  group_by(item) %>%
-  tidyr::expand(Estimate.Intercept,Estimate.age,grand_intercept,grand_slope, age = unique(me_data$age))%>%
-  mutate(y = plogis(grand_intercept + Estimate.Intercept+(Estimate.age+grand_slope)*age), 
-         age = age+min(me_data$age_num))%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-plot_me <- ggplot(ranef_plot_me, aes(x=age,y = y, col = item))+
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_jitter(data = me_data%>%left_join(aoa_ratings), aes(x = age_num, y = correct, col = reorder(item, mean_aoa)), width = 0, height = 0.02, alpha = .2)+
-  geom_line(size = 1)+
-  labs(x="Age",y="Mutual exclusivity effect")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d(name = "Object")
-
-cor_plot_me <- as_tibble(ranef_me$item, rownames = "item") %>%
-  left_join(aoa_ratings)%>%
-  ggplot(., aes(x = mean_aoa, y = Estimate.Intercept))+
-  geom_abline(intercept = 1, slope = -1, lty = 2, alpha = 1, size = .5)+
-  geom_point(pch = 4, size = 2)+
-  geom_smooth(method = "lm", col = "black", se = F, lty = 2, size = .5)+
-  xlab("Rated age of acquisition")+
-  ylab("Mutual exclusivity effect (model intercept)")+
-  ylim(-1,1)+
-  stat_cor(method = "pearson", label.x = 7, label.y = .99)+
-  theme_few()
-```
-
-As a second step, we investigated how the inference changed as a function of age and the familiar object.
-We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM).
-We used the function `brm` from the package `brms` [@R-brms_a].
-We pre-registered the use of default priors in all models.
-However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent.
-The priors we used were `normal(0,5)` for fixed effects and `cauchy(0,1)` for standard deviations of random effects.
-The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`.
-That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects).
-We did not pre-register agent as a random effect, but retrospecitvely included it to be consistent with Experiment 2 and 3.
-
-The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_me%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_me%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_me%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`).
-Older children were more likely to make a mutual exclusivity inference.
-To assess the variability accross objects, we compared the fit of the above model to a model lacking `object` as a random effect.
-Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights.
-The WAIC score is an indicator of the model’s predictive accuracy for out of sample data; model’s with lower scores are preferred.
-WAIC weights are an estimate of the probability that this model (compared to all other models considered) will make the best predictions on new data.
-The model including object provided a much better fit compared to the model lacking it (see Table \@ref(tab:table2)).
-Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and illustrates the substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory.
-Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept.
-The mutual exclusivity effect was stronger for words that were rated to be acquired earlier.
-Objects for which children were less likely to know the word produced a weaker mutual exclusivity effect.
-Taken together, the strength  of the mutual exclusivity inference depended on age as well as the familiar object.
-
-```{r table2, echo=T}
-
-me_waic <- brms::waic(bm_me, bm_me2, compare = F)
-
-me_weights <- model_weights(bm_me, bm_me2, weights = "waic")
-
-me_comp <- tibble(
-  Model = c("with object as RE", "without object as RE"),
-  WAIC = round(c(me_waic$loos$bm_me$estimates["waic","Estimate"],me_waic$loos$bm_me2$estimates["waic","Estimate"]),2),
-  SE = round(c(me_waic$loos$bm_me$estimates["waic","SE"],me_waic$loos$bm_me2$estimates["waic","SE"]),2),
-  weight = round(c(me_weights[1],me_weights[2]))
-)
-
-knitr::kable(me_comp, caption = "Model comparison in experiment 1 based on WAIC scores and weights.", digits = 2, align = "l")
-```
-
-```{r fig2, include = T, fig.align = "center", fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition.
-B: Developmental trajectories of mututal exclusivity effect by familiar object based on the mean of the model posterior distribution.
-Dots show individual datapoints.
-Lighter colors indicate later rated age of acquisition.
-Dotted line indicates a level of performance expected by chance.
-C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}
-ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1))
-```
-
-## Experiment 2: Common ground
-
-Here we tested children's sensitivity to common ground that is build up over the course of a conversation.
-In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two].
-The main goal of the experiment was to measure how children's sensitivity to common ground changes with age.
-
-The experiment was preregistered at https://osf.io/au5hr. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_novel.html`.
-
-### Participants
-
-We tested `r length(unique(prior_data$subid))` children from the same general population as in Experiment 1, including `r length(unique(prior_data$subid[prior_data$subage == 2]))` 2-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 2]),2), nsmall = 2)`, 7 girls), `r length(unique(prior_data$subid[prior_data$subage == 3]))` 3-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 3]),2), nsmall = 2)`, 14 girls) and  `r length(unique(prior_data$subid[prior_data$subage == 4]))` 4-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 4]),2), nsmall = 2)`, 14 girls).
-Data from 5 additional children was not included because they were either exposed to less than 75% of English at home (3) or the technical equipment failed (2).
-
-### Procedure
-
-The general setup was the same as in Experiment 1.
-The speaker was positioned between the tables.
-There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty.
-Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object.
-Then the speaker disappeared.
-While the speaker was away, a second novel object appeared on the previously empty table.
-Then the speaker returned and requested an object in the same way as in Experiment 1 (see also Figure \@ref(fig:fig1)B).
-The positioning of the novel object in the beginning of the experiment as well as the location the speaker turned to first was counterbalanced.
-Children received five trials, each with a different pair of novel objects.
-We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.
-
-### Results
-
-```{r table3, echo=T}
-chance_prior <- prior_data %>%
-  group_by(subage, subid) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(subage)%>%
-  mutate(Mean= round(mean(unlist(correct)),2),
-         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf,2), scientific = F),
-         `Age group` = subage)%>%
-  ungroup()%>%
-  select(`Age group`, Mean, BayesFactor)
-
-knitr::kable(chance_prior, caption = "Proportion of children choosing the object that was new to the speaker compared to a level expected by chance based on a one sample Bayesian t-test.
-Responses are aggregated for each participant across trials.", digits = 2, align = "l")
-```
-
-Table \@ref(tab:table3) compares children's correct responses to a level expected by chance (50%).
-We found evidence that, as a group, 3- and 4-year-olds, but not 2-year-olds, inferred that the novel word referred to the object that was new to the speaker.
-
-```{r, echo=T}
-# prior_cg <- c(prior(normal(0, 5), class = Intercept),
-#            prior(normal(0, 5), class = b),
-#            prior(cauchy(0, 1), class = sd))
-# 
-# 
-# bm_cg <- brm(correct ~ age + (1|subid) + (age | agent),
-#                     data = prior_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99, max_treedepth = 20),
-#           sample_prior = F,
-#           prior = prior_cg,
-#           cores = 4,
-#           chains = 4,
-#           iter = 5000)%>%
-#   saveRDS(.,"../saves/bm_cg.rds")
-
-bm_cg <- readRDS("../saves/bm_cg.rds")
-```
-
-```{r}
-fixef_cg <- as_tibble(fixef(bm_cg), rownames = "term")
-
-plot_cg_data <- prior_data %>%
-  group_by(age_num, subid) %>%
-  summarise(correct = mean(correct))
-
-plot_cg_samples <- posterior_samples(bm_cg, "^b", subset = 1:200)%>%
-  mutate(sample = 1:length(b_age))%>%
-  expand_grid(.,unique(prior_data$age))%>%
-  mutate(age = `unique(prior_data$age)`,
-         y =  plogis(b_Intercept + b_age * age))%>%
-  select(-`unique(prior_data$age)`)
-
-plot_cg_map <- as_tibble(fixef(bm_cg), rownames = "term")%>%
-  select(term, Estimate)%>%
-  spread(term, Estimate)%>%
-  expand_grid(.,unique(prior_data$age))%>%
-  mutate(slope = age, 
-         age = `unique(prior_data$age)`,
-         y =  plogis(Intercept + slope * age))%>%
-  select(-`unique(prior_data$age)`)
-
-plot_cg <- ggplot() +
-  geom_hline(yintercept = 1/2, lty=2, size = 1)+
-  geom_jitter(data = plot_cg_data,aes(x = age_num, y= correct), width = .00, height = .01, alpha = .5)+
-  geom_line(data = plot_cg_samples, aes(x = age+min(prior_data$age_num), y = y, group = sample), size = .025)+
-  geom_line(data = plot_cg_map, aes(x =age+min(prior_data$age_num), y = y), size = 1)+
-  labs(x="Age",y="Proportion object new to speaker chosen")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)
-
-```
-
-To directly investigate whether children's response changed with age, we modeled the trial by trial data using a Bayesian GLMM (formula: `correct ~ age + (1 | id) + (age | speaker)`, specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).
-The estimate for age was positive and reliably different from zero (*$\beta$* = `r fixef_cg%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_cg%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_cg%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`, see Figure \@ref(fig:fig3)A).
-Older children were more likely to chose the object that was new to the speaker as the referent of the novel word, suggesting that the sensitivity to common ground in this context increases with age.
-
-## Experiment 3: Integration
-
-Experiment 3 combined the procedures from Experiment 1 and 2.
-As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but also the role that each object (novel and familiar) had played in the preceding interaction.
-Combining the two procedures created two conditions: In the *congruent* condition, the novel object was also the object that was new to the speaker.
-In this case, the mutual exclusivity inference as well as the common ground inference pointed to the novel object as the referent.
-In the *incongurent condition*, the familiar object was new to the speaker.
-Int his case, the two inferences pointed to different objects.
-The main focus of the overall study was to model how children integrate and balance these different information sources.
-We investigate this question in depth in the [modelling](#model) section below.
-Here, we limit the discussion to whether children differentiated between the two conditions.
-
-The experiment was preregistered at https://osf.io/4nm8g. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_combination.html`.
-
-### Participants
-
-We tested `r length(unique(comb_data$subid))` children from the same general population as in Experiment 1 and 2, including `r length(unique(comb_data$subid[comb_data$subage == 2]))` 2-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 2]),2), nsmall = 2)`, 7 girls), `r length(unique(comb_data$subid[comb_data$subage == 3]))` 3-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 3]),2), nsmall = 2)`, 14 girls) and  `r length(unique(comb_data$subid[comb_data$subage == 4]))` 4-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 4]),2), nsmall = 2)`, 14 girls).
-Data from 20 additional children was not included because they were either exposed to less than 75% of English at home (15), did not finish at least half of the test trials (3) or the technical equipment failed (2).
-
-### Procedure
-
-Experiment 3 followed the same procedure as Experiment 2 but involved the same objects as Experiment 1.
-In the beginning, one table was empty while there was an object (novel or familiar) on the other one.
-After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or novel).
-Next, the speaker re-appeared and made the usual request.
-
-In the congruent condition, the familiar object was present in the beginning and the novel object appeared while the speaker was away (Figure \@ref(fig:fig1)C - left).
-In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent.
-In the incongruent condition, the novel object was present in the beginning and the familiar object appeared later.
-In this case, the two inferences pointed to different objects (Figure \@ref(fig:fig1)C - right).
-
-Participants received up to 12 test trials, six in each condition, each with a different familiar and novel object.
-Familiar objects were the same as in Experiment 1.
-The positioning of the objects on the tables and the location the speaker first turned to were counterbalanced.
-Participants could stop the experiment after six trials (three per condition).
-If a participant stopped after half of the trials, we tested an additional participant to reach a pre-registered number of data points per cell.
-
-### Results
-
-All results are reported from the perspective of the mutual exclusivity inference (`correct` in the model formula below).
-In the incongruent condition, high proportions speak to a mutual exclusivity inference and low proportion for a common ground inference.
-In the congruent condition, both inferences pointed in the same direction.
-The focus of this experiment was on information integration and we therefore did not compare the performance to chance.
-
-```{r, echo=T}
-
-# prior_comb <- c(prior(normal(0, 5), class = Intercept),
-#            prior(normal(0, 5), class = b),
-#            prior(cauchy(0, 1), class = sd))
-# 
-# bm_comb <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | item)+ (age * alignment | agent),
-#                     data = comb_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99, max_treedepth = 20),
-#           sample_prior = F,
-#           prior = prior_comb,
-#           cores = 4,
-#           chains = 4,
-#           inits = 0,
-#           iter = 5000)%>%
-#   saveRDS(.,"../saves/bm_comb.rds")
-# 
-# bm_comb2 <- brm(correct ~ age * alignment + (alignment | subid) + (age * alignment | agent),
-#                     data = comb_data, family = bernoulli(),
-#           control = list(adapt_delta = 0.99, max_treedepth = 20),
-#           sample_prior = F,
-#           prior = prior_comb,
-#           cores = 4,
-#           chains = 4,
-#           inits = 0,
-#           iter = 5000)%>%
-#   saveRDS(.,"../saves/bm_comb2.rds")
-
-bm_comb <- readRDS("../saves/bm_comb.rds")
-
-bm_comb2 <- readRDS("../saves/bm_comb2.rds")
-
-```
-
-```{r}
-fixef_comb <- as_tibble(fixef(bm_comb), rownames = "term")
-
-ranef_comb <-  ranef(bm_comb)
-
-plot_comb_map <- bind_rows(
-  as_tibble(ranef_comb$item, rownames = "item")%>%
-  mutate(condition = "congruent",
-         condition_code = 0),
-  as_tibble(ranef_comb$item, rownames = "item")%>%
-  mutate(condition = "incongruent",
-         condition_code = 1))%>%
-  mutate(grand_intercept = fixef_comb%>%filter(term=="Intercept")%>%pull(Estimate),
-         grand_age = fixef_comb%>%filter(term=="age")%>%pull(Estimate),
-         grand_cond = fixef_comb%>%filter(term=="alignmentincongruent")%>%pull(Estimate),
-         grand_intact = fixef_comb%>%filter(term=="age:alignmentincongruent")%>%pull(Estimate))%>%
-  group_by(item, condition, condition_code)%>%
-  expand_grid(. ,age = unique(comb_data$age))%>%
-  mutate(y = plogis(grand_intercept + 
-                      Estimate.Intercept +
-                      grand_cond * condition_code +
-                      Estimate.alignmentincongruent * condition_code +
-                      grand_age * age +
-                      Estimate.age * age +
-                      grand_intact * (condition_code * age) +
-                      `Estimate.age:alignmentincongruent` * (condition_code * age)),
-         age = age+min(comb_data$age_num))%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa))
-
-plot_comb <- ggplot(plot_comb_map, aes(x=age,y = y, col = item))+
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_jitter(data = comb_data%>%left_join(aoa_ratings)%>%ungroup()%>%mutate(item = fct_reorder(factor(item), mean_aoa)), aes(x = age_num, y= correct, col = item), width = .00, height = .04, alpha = .2)+
-  geom_line(size = 1)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(~condition)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F)+ 
-  scale_colour_viridis_d(name = "Object")
-
-```
-
-We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | item) + (age * alignment | agent)`.
-We pre-registered to include item as a fixed effect in Experiment 3.
-The corresponding model was too complex to be constrained by the data.
-Furthermore, as explained in Experiment 1, items were chosen based on their rated age of acquisition.
-That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge.
-For further model specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).
-
-The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`).
-The incongruent condition had a strong negative impact (*$\beta$* = `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q97.5)%>%round(2)`), showing that children differentiated between the two conditions.
-The interaction term was weakly - though not entirely - negative, suggesting a shallower slope for age in the incongruent condition (*$\beta$* = `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q97.5)%>%round(2)`).
-A model lacking `object` as a random effect provided a much poorer fit, suggesting substantial variation across objects (see Table \@ref(tab:table4)).
-Figure \@ref(fig:fig3)B visualizes the model.
-Taken together, the results show that children responded to the way the two inferences were aligned with one another.
-
-```{r table4, echo=T}
-
-comb_waic <- brms::waic(bm_comb, bm_comb2, compare = F)
-
-comb_weights <- model_weights(bm_comb, bm_comb2, weights = "waic")
-
-comb_comp <- tibble(
-  Model = c("with object as RE", "without object as RE"),
-  WAIC = round(c(comb_waic$loos$bm_comb$estimates["waic","Estimate"],comb_waic$loos$bm_comb2$estimates["waic","Estimate"]),2),
-  SE = round(c(comb_waic$loos$bm_comb$estimates["waic","SE"],comb_waic$loos$bm_comb2$estimates["waic","SE"]),2),
-  weight = round(c(comb_weights[1],comb_weights[2]))
-)
-
-knitr::kable(comb_comp, caption = "Model comparison in experiment 3 based on WAIC scores and weights.", digits = 2, align = "l")
-```
-
-```{r fig3, include = T, fig.align = "center", fig.cap = "Proportion of choosing the object that was new to the speaker by age.
-Dots show the mean response for each participant.
-The solid black line shows the developmental trajectory based on the mean of the model posterior distribution.
-Lighter lines show 200 random draws from the posterior distribution to depict uncertainty.
-Dotted line indicates a level of performance expected by chance.", fig.width=12, fig.height = 4}
-ggarrange(plot_cg, plot_comb,  labels = c("A","B"), nrow = 1, widths = c(1,2))
-```
-
-## Discussion
-
-The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate.
-Experiment 1 showed that children of all age groups are make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented.
-Experiment 2 showed that three- and four-year-olds are sensitive the common ground manipulation we implemented and that this inference increases with age.
-Finally, experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another.
-In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when the two inferences are combined with one another.
-
-# Models
-
-The main purpose of the study was to study *how* children integrate different information sources during word learning and how this process develops with age.
-To do so, we use Bayesian cognitive models of pragmatic reasoning.
-We first describe an *integration model* which we think best represents the inference and integration processes and then specify how this model captures developmental change.
-Next, we ask how well this model *predicts* how children integrate the two information sources.
-That is, in a situation in which we know the development trajectories for the mutual exclusivity inference as well as for the common ground inference, what can we say about what happens when they are combined.
-We then test the predictive power of the model by comparing the model predictions to the data from experiment 3.
-We will use model comparisons to test the *integration model* against a range of alternative models.
-
-Finally, we ask how well our model *explains* the way that children integrate the two information sources.
-For this analysis, we fit the free parameters in the model to all the available data, those from experiment 1 and 2 as well as the integration data from experiment 3.
-We then compare the model to a range of alternative models that make different assumptions about how information is integrated and how this process develops.
-This approach answers the question of how we can best explain how children are integrating the different information sources.
-
-## Modeling framework
-
-The cognitive models are situated in the Rational Speech Act (RSA) framework [@frank2012predicting; @goodman2016pragmatic].
-RSA models are models of pragmatic reasoning in that they treat language understanding as a special case of Bayesian social reasoning.
-A listener interprets an utterance by assuming it was produced by a cooperative speaker who had the goal to be informative.
-Being informative is defined as providing a message that would increase the probability of the listener inferring the speaker’s intended message.
-This notion of contextual informativeness captures the Gricean idea of cooperation between speaker and listener.
-
-The model captures the following process.
-A listener is reasoning about the referent of a speaker's utterance while at the same time trying to learn a lexicon (object--word mappings).
-This reasoning is contextualized by the prior probability of each referent.
-This prior probability is thought to be a function of the common ground shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later.
-We assume that the degree to which interactions around objects change their prior probability depend on the child's age.
-
-To decide between referents, the listener reasons about what a rational speaker would say given an intended referent.
-This speaker is assumed to compute the informativity of for each available utterance and then choose the most informative one.
-However, this expectation of speaker informativeness may vary and is captured by the term alpha.
-In particular, we take alpha to be a function of the child's age.
-
-The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their literal semantics, would infer upon hearing it.
-Thus, this reasoning depends what kind of word--object mappings the speaker thinks the literal listener knows.
-We assume that knowing the literal semantics of a word is not deterministic but probabilistic.
-That is, for each object involved there is a probability p that the literal listener knows the word for it.
-For each of the novel objects, this semantic knowledge is 0.
-For familiar objects, it depends on the kind of object as well as on the child's age.
-
-## Loci of development
-
-The model description above points to three potential loci of developmental change: semantic knowledge, expectations about speaker informativeness and common ground sensitivity.
-Each of theses components is represented by a parameter in the model.
-We capture developmental change by making these parameters a function of age and therefore estimating a developmental trajectory (intercept and slope) for each parameter.
-
-### Semantic knowledge
-
-Semantic knowledge captures the degree of certainty with which the naive listener is assumed to know the label for the familiar object.
-When faced with the task, we think that children take their own semantic knowledge as the basis.
-As a consequence, semantic knowledge differs between familiar objects.
-For objects whose labels are generally acquired earlier (e.g.
-carrot) semantic knowledge is high whereas for others (e.g.
-pawn) semantic knowledge is lower.
-However, semantic knowledge also varies with age in that older children are more likely to know the labels for more of the familiar objects compared to younger children.
-As a consequence, each familiar object has a unique developmental trajectory with respect to semantic knowledge.
-Technically, the object specifics parameters are estimated in the form of a random effects model, that is, each object's trajectory is estimated as a deviation from an overall trajectory for semantic.
-This overall trajectory represent an increase in semantic knowledge that is independent of a particular familiar object.
-
-Semantic knowledge enters the likelihood term of the model specified above.
-The likelihood depends not just on the parameter settings for semantic knowledge but also on the value of the parameter capturing expectations about speaker informativeness ($\alpha$ - see next section).
-As a consequence, these parameters are jointly estimated and co-vary with one another.
-
-### Expectations about speaker informativeness
-
-A second locus of developmental change are expectations about speaker informativeness.
-In the context of the model, speaker informativeness corresponds to the degree with which the listener expects the speaker to choose the most informative of all available utterances.
-We assume that children at different ages might have different expectations about how rational or informative speakers are.
-As mentioned above, this parameter jointly estimated with the parameters for semantic knowledge.
-
-### Sensitivity to common ground
-
-Sensitivity to common ground refers to the probability that an object is taken to be the referent of the utterance before actually hearing the utterance.
-Thus, it captures the salience of an object due to its role in the social interaction that precedes the utterance.
-We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects.
-
-## Model fitting
-
-All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
-The corresponding model code can be found in the associated online repository and includes information about the prior distributions for all parameters (file xxxxx).
-To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and common ground sensitivity and then passed them through the model in line with the different ways in which they can be combined and aligned.
-The resulting predictions come in the form of distributions of developmental trajectories for each object in the congruent and the incongruent condition.
-
-## Prediction
-
-In this section we evaluate different models in terms of how well they *predict* information integration.
-That is, in a situation in which we know the development of the mutual exclusivity inference as well as the common ground inference, which model best predicts what happens when the two are combined (combination data from Experiment 3).
-Asking about "pure" prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g.
-mixture model, see below).
-To generate these predictions, we estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.
-
-To estimate the parameters for semantic knowledge and speaker informativeness, we adapted the model described above to a situation in which both objects (novel and familiar) have equal prior probability.
-We used the data from experiment 1 to then infer the parameters.
-That is, we inferred which intercepts and slopes for speaker informativeness and semantic knowledge would generate model predictions that corresponded to the average proportion of correct responses measured in experiment 1.
-To estimate the parameters representing sensitivity to common ground, we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in experiment 1.
-
-To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150 000 samples from each chain and removing the first 50 000 for burn-in.
-We removed samples from one chain because it converged on a local maximum which resulted in parameter distributions that were substantially different from the other chains.
-The model outputs can be found in the following online repository: git large file storage.
-
-Next, we combined the parameters according to the four models described below.
-Please note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in which parameters they included.
-The models described below are a full model (*integration model*) and three lesion models, which selectively omit one type of information.
-The following model comparison therefore asks which types of information are necessary to make good predictions about how information is integrated.
-We do not compare models that make different assumptions about how information is integrated.
-We turn to this question in the [explanation](#explanation) section.
 
@@
 ```
+```{r}
+plot_cor_model_pred <- readRDS( "../saves/corr_model_data_pred.rds")%>%
+  mutate(model = factor(model, levels = c("integration", "no word knowledge", "no common ground", "no mutual exclusivity")))%>%
+  filter(model == "integration")
 
-```{r fig4, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity.
-Solid lines in show the MAP estimate for each parameter.
-Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty.
-(A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
-ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1))
+pred_cor <- ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
+  geom_point(size = 1.5, stroke = 1, pch = 5)+
+  #coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(~age)+
+  theme_few() + 
+  scale_colour_ptol(name ="Condition")
 ```
-### Models
 
-#### Integration model
-
-The integration model serves as the full model and takes in all available information.
-That is, it takes in object specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above.
-Figure \@ref(fig:fig5) visualizes the corresponding model predictions in comparison to the data from experiment 3.
-
-```{r fig5, include = T, fig.align = "center", fig.cap = "Predicting information integration across development.
-Model predictions based on the integration model.
-Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution.
-Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition.
-Familiar objects are ordered based on their rated age of acquisition (left o right).
-Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey).
-Light dots are individual data points.", fig.width=12, fig.height = 4}
-# comb_data_binned <- comb_data%>%
-#   group_by(subage, alignment, item)%>%
-#   summarize(k = sum(correct), n = n())%>%
-#   ungroup() %>%
-#   mutate(a = 1 + k,
-#          b = 1 + n - k,
-#          data_mean = (a-1)/(a+b-2),
-#          data_ci_lower  = qbeta(.025, a, b),
-#          data_ci_upper = qbeta(.975, a, b),
-#          age = factor(subage))%>%
-#   select(-a,-b,-n,-k)%>%
-#   left_join(aoa_ratings) %>%
-#   ungroup()%>%
-#   mutate(item = fct_reorder(factor(item), mean_aoa))
-# 
-# select_pred <- sample(1:20000, 60)
-# 
-# plot_prag_pred <- readRDS("../saves/model_pred_prag.rds")%>%
-#   filter(iteration %in% select_pred)%>%
-#   left_join(aoa_ratings) %>%
-#   ungroup()%>%
-#   mutate(item = fct_reorder(factor(item), mean_aoa))
-# 
-# 
-#  saveRDS(plot_prag_pred, "../saves/plot_prag_pred.rds")
-
+```{r}
 plot_prag_pred <- readRDS( "../saves/plot_prag_pred.rds")
 
-ggplot(data = comb_data, aes(x = age_num, y = correct)) +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_jitter(col = "black", height = .025, alpha = .1)+
+pred_pred <- ggplot(data = comb_data, aes(x = age_num, y = correct)) +
+  #geom_hline(yintercept = 0.5, lty=2)+
+  #geom_jitter(col = "black", height = .025, alpha = .1)+
   #geom_pointrange(data = comb_data_binned, aes(x = subage+.5, y = data_mean, ymin =data_ci_lower, ymax = data_ci_upper), stroke = 1, pch = 5)+
@@
 
-#### No word knowledge model
+```{r}
 
-This model is the first lesion model.
-It takes in speaker informativeness and common ground sensitivity as well as general semantic knowledge, but omits semantic knowledge that is specific to the familiar objects.
-We described above that the parameters for semantic knowledge are fitted via a mixed effects model.
-On the one hand, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object specific variation around this trajectory (random effects).
-The *no word knowledge* model takes in the overall trajectory for semantic knowledge but ignores object specific variation.
-That is, the model assumes a listener whose mutual exclusivity inference does not vary depending on the particular familiar object but only depends on the average semantic knowledge.
+ggarrange(
+ggarrange(plot_speak_opt, plot_prior,plot_sem_know, labels = c("A","B","C"), nrow = 1, widths = c(1,1,1.5)),
+ggarrange(pred_cor, labels = c("D"), nrow = 1 ),
+nrow= 2,
+heights = c(1,1)
+)
 
-#### No common ground model
-
-This model takes in object specific semantic knowledge and speaker informativeness but ignores common ground.
-Thus, the prior distribution over objects $P(r)$ in the model described above is flat (e.g.
-[0.5, 0.5].
-This corresponds to a listener who only focuses on the mutual exclusivity inference and ignores the common ground manipulation.
-As a consequence the listener does not differentiate between the two alignment conditions.
-
-#### No mutual exclusivity model
-
-The last lesion model only takes in the common ground sensitivity.
-This corresponds to a listener who only focuses on common ground and ignores the identity of the objects on the tables as well as any inferences their semantic knowledge of the familiar objects license.
-The model predictions therefore correspond to the prior distribution over objects $P(r)$.
-
-### Model comparison
-
-We compared the models mentioned above in two ways.
-On the one hand, we used correlations between model predictions and the data.
-For this analysis, we binned the model predictions and the data by year and familiar object.
-Figure \@ref(fig:fig6) visualizes the correlation between model predictions and the data for all models.
-The results shows a very high correlation between the predictions of the *integration model* and the data in all age groups suggesting that the model accurately captures the variation in the data.
-The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds.
-This is probably a consequence of the model making very extreme predictions for the oldest age group.
-Correlations for the *integration model* were also higher compared to the other models considered.
-
-On the other hand, we compared models based on Bayes factors which were calculated from the marginal likelihoods of each model given the data.
-For this analysis, we treated age continuously.
-We first calculated the marginal log-likelihood for each model and then computed Bayes factors by subtracting the log-likelihoods for the models involved in the comparison and then exponentiating the result (see file `model_comparison.Rmd` in the associated online repository).
-Table \@ref(tab:table5) lists the Bayes factors for the different model comparisons.
-The results show that the *integration model*, by far, outperformed all the other models.
-When comparing the lesion models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the *no mutual exclusivity model*.
-
-Taken together, this analysis showed two things.
-First, the *integration model* makes accurate predictions about how mutual exclusivity and common ground inferences are integrated with one another.
-It does so based on knowing the strength and development of each inference alone.
-Second, models that omit one or more type of information (object specific word knowledge, speaker informativeness, common ground sensitivity) make much worse predictions.
-This exemplifies that children across the entire age range flexibly integrate all the available information.
-In the next section we ask whether there are other ways think about the process of information integration than the way formalized in the *integration model*.
-
-```{r fig6, include = T, fig.align = "center", fig.cap = "Predicting information integration.
-Correlations between model predictions and data binned by year, item and condition.
-Vertical and horizontal error bars show 95\\% HDI.
-Blue diamonds show congruent condition and red ones show the incongruent condition.", fig.width=12, fig.height = 8}
-
-# cor_prag <- readRDS("../saves/model_pred_prag.rds")%>%
-#   mutate(age = as.numeric(age) + min(comb_data$age_num),
-#          age = cut(age,
-#                       breaks = c(2,3,4,5),
-#                       labels = c(2,3,4)))%>%
-#   group_by(model,alignment, item, age)%>%
-#   summarise(model_mean = estimate_mode(pred),
-#             model_ci_lower = hdi_lower(pred),
-#             model_ci_upper = hdi_upper(pred))
-# 
-# cor_global <- readRDS("../saves/model_pred_global.rds")%>%
-#   mutate(age = as.numeric(age) + min(comb_data$age_num),
-#          age = cut(age,
-#                       breaks = c(2,3,4,5),
-#                       labels = c(2,3,4)))%>%
-#   group_by(model, alignment, item, age)%>%
-#   summarise(model_mean = estimate_mode(pred),
-#             model_ci_lower = hdi_lower(pred),
-#             model_ci_upper = hdi_upper(pred))
-# 
-# cor_flat <- readRDS("../saves/model_pred_flat.rds")%>%
-#   mutate(age = as.numeric(age) + min(comb_data$age_num),
-#          age = cut(age,
-#                       breaks = c(2,3,4,5),
-#                       labels = c(2,3,4)))%>%
-#   group_by(model, alignment, item, age)%>%
-#   summarise(model_mean = estimate_mode(pred),
-#             model_ci_lower = hdi_lower(pred),
-#             model_ci_upper = hdi_upper(pred))
-# 
-# cor_prior <- readRDS("../saves/model_pred_prior.rds")%>%
-#   mutate(age = as.numeric(age) + min(comb_data$age_num),
-#          age = cut(age,
-#                       breaks = c(2,3,4,5),
-#                       labels = c(2,3,4)))%>%
-#   group_by(model, alignment, item, age)%>%
-#   summarise(model_mean = estimate_mode(pred),
-#             model_ci_lower = hdi_lower(pred),
-#             model_ci_upper = hdi_upper(pred))
-# 
-# cor_model_pred <- bind_rows(
-#    cor_prag,
-#    cor_global,
-#    cor_flat,
-#    cor_prior
-# )
-# 
-# 
-# plot_cor_model_pred <- cor_model_pred %>%
-#   left_join(
-#     bind_rows(
-#        binnned_data%>%mutate(model = "integration"),
-#        binnned_data%>%mutate(model = "no word knowledge"),
-#        binnned_data%>%mutate(model = "no common ground"),
-#        binnned_data%>%mutate(model = "no mutual exclusivity")
-#       )
-#   )%>%
-  # mutate(age = fct_recode(age,
-  #                         "2-year-olds" = "2",
-  #                         "3-year-olds" = "3",
-  #                         "4-year-olds" = "4"))
-#
-#saveRDS(plot_cor_model_pred, "../saves/corr_model_data_pred.rds")
-
-plot_cor_model_pred <- readRDS( "../saves/corr_model_data_pred.rds")%>%
-  mutate(model = factor(model, levels = c("integration", "no word knowledge", "no common ground", "no mutual exclusivity")))
-
-ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
-  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
-  geom_point(size = 1.5, stroke = 1, pch = 5)+
-  coord_fixed()+
- stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  ylab("Data")+
-  facet_grid(age~model)+
-  theme_few() + 
-  scale_colour_ptol(name ="Condition")
-```
-
-```{r table5}
-model_comp_pred <- readRDS("../saves/pred_model_comparison.rds")%>%
-  mutate(model = factor(model),
-         `Model comparison` = fct_recode(model, 
-                            "integration vs no word knowledge" = "prag_vs_global",
-                            "integration vs no common ground" = "prag_vs_flat",
-                            "integration vs no mutual exclusivity" = "prag_vs_prior",
-                            "no word knowledge vs no mutual exclusivity" = "global_vs_flat",
-                            "no word knowledge vs no common ground" = "global_vs_prior",
-                            "no mutual exclusivity vs no common ground" = "flat_vs_prior"),
-        `Bayes factor` = format(round(exp(logBF),2), trim = T, justify = "right", digits = 2))%>%
-  select(-logBF, -model)
-
-knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2, align = "l")
-```
-
-## Explanation
-
-In this section we explore how we can best explain information integration across development.
-We explore alternative ways to think about information integration.
-The *integration model* outlined above operates via Bayesian inference in that the prior probability of a referent - a consequence of the common ground manipulation - is updated upon hearing the utterance and computing the mutual exclusivity inference.
-In essence, this model is a multiplicative model because the probability of each referent is proportional to the product of the likelihood and the prior.
-The alternative model we consider here is an additive model.
-This *mixture model* assumes that the two inferences are computed separately and then weighted by some ratio $\phi$.
-Psychologically, $\phi$ may be interpreted as a bias for one type of inference relative to the other.
-
-With respect to developmental change, the *integration model* assumes that the process by which information is integrated remains the same across development.
-What changes is children's semantic knowledge, their expectations about speaker informativeness and their sensitivity to common ground.
-But the way these information sources are combined remains the same across age.
-As an alternative, we explore a *developmental mixture model*.
-This model makes the same assumptions about developmental change in the individual information sources but, in addition, also assumes that the way that the the mutual exclusivity and the common ground inference are combined with one another changes over time.
-It is structurally identical to the *mixture model* but the mixture parameter $\phi$ is a function of age.
-
-In this section, we make use of all the available data.
-We use the data from experiment 1 and 2 to compute prior distributions over model parameters which are subsequently updated depending on how well the model predictions they generate fit the data.
-
-### Integration model
-
-```{r}
-item_params_exp <- readRDS("../saves/item_params_fb.rds")
-global_params_exp <- readRDS("../saves/global_params_fb.rds")
-item_sigma_exp <- readRDS("../saves/item_sigma_fb.rds")
-```
-
-The *integration model* in this section differs from the same model in the prediction section only in the distributions for the parameters representing the different information sources.
-Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the appendix show how the  parameter distributions differ between the prediction and the explanation version of the *integration* model.
-As a quick summary, we can say that semantic knowledge and speaker informativeness have similar distributions when taking into account all the data compared to when estimating these parameters only based on experiment 1 and 2.
-In contrast, the intercept for common ground sensitivity is estimated to be larger and the slope shallower.
-The code to run the model can be found in the associated online repository (file: xxxxxxx).
-Figure \@ref(fig:fig9) shows model predictions for the *integration model* in comparison to the data from experiment 3.
-
-```{r fig9, include = T, fig.align = "center", fig.cap = "Explaining information integration across development.
-Model predictions based on the integration model.
-Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution.
-Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition.
-Familiar objects are ordered based on their rated age of acquisition (left o right).
-Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey).
-Light dots are individual data points.", fig.width=12, fig.height = 4}
-
-# select_exp <- sample(1:20000, 50)
-# 
-# plot_prag_exp <- readRDS("../saves/model_pred_prag_fb.rds")%>%
-#   filter(iteration %in% select_pred)%>%
-#   left_join(aoa_ratings) %>%
-#   ungroup()%>%
-#   mutate(item = fct_reorder(factor(item), mean_aoa))
-# 
-# 
-# saveRDS(plot_prag_exp, "../saves/plot_prag_exp.rds")
-
-plot_prag_exp<- readRDS( "../saves/plot_prag_exp.rds")
-
-ggplot(data = comb_data, aes(x = age_num, y = correct)) +
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_jitter(col = "black", height = .025, alpha = .1)+
-  #geom_pointrange(data = comb_data_binned, aes(x = subage+.5, y = data_mean, ymin =data_ci_lower, ymax = data_ci_upper), stroke = 1, pch = 5)+
-  #geom_line(data = comb_data_binned, aes(x = subage+.5, y = data_mean))+
-  geom_line(data = plot_prag_exp, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)), size = .2, alpha = .25)+
-  geom_smooth(data = comb_data, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .4, lty = 2, size = 1)+
-  labs(x="Age",y="Mutual Exclusivity effect")+
-  facet_grid(alignment~item)+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F, col = F)+ 
-  scale_colour_ptol(name = NULL)
-```
-
-### Mixture model
-
-In the *mixture model* the two inferences are computed in the same way as in in the *integration model*. Subsequently, they are weighted by the mixture parameter $\phi$:
-
-\begin{equation} 
-to be adjusted .... P_{L_1}(r, \mathcal{L}|u) = \phi P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)
-\end{equation}
-
-To estimate $\phi$ as well as the other parameters, we make use of all the available data.
-The model code can be found in the associated online repository (file: xxxxxxx).
-The posterior distribution for the mixture parameter $\phi$ is shown in figure \@ref(fig:fig10)A.
-It suggests that the mutual exclusivity inference is weighted as slightly more important compared to the common ground inference.
-
-```{r}
-item_params_mixture <- readRDS("../saves/item_params_mm.rds")
-
-global_params_mixture <- readRDS("../saves/global_params_mm.rds")
-
-mixture_parameter <- readRDS("../saves/mixture_mm.rds")
 ```
@@
 ```{r}
-plot_mixture <- ggplot(mixture_parameter, aes(x = p_informative))+
-  geom_density(alpha = 0.8, adjust = 2)+
-  xlab("Proportion mutual exclusivity component")+
-  xlim(0,1)+
-  theme_few()
-
+ggsave("../graphs/paper_figure2.png", width = 5, height = 3.5, scale = 2)
 ```
-
-### Developmental mixture model
-
-For this model, we make the mixture parameter $\phi$ a function of age and estimate the intercept and slope that yield the best model predictions compared to the data from experiment 3.
-Figure \@ref(fig:fig10)B visualizes the developmental trajectory of the mixture parameter.
-Based on this model, the common ground inference seems to decrease in importance compared to the mutual exclusivity inference with age.
-
-```{r}
-item_params_dev_mixture <- readRDS("../saves/item_params_dmm.rds")
-
-global_params_dev_mixture <- readRDS("../saves/global_params_dmm.rds")
-
-developmental_mixture_parameter <- readRDS("../saves/mixture_dmm.rds")
-```
-
-```{r}
-select_dev_mix <- sample(1:20000, 50)
-
-plot_mixture_line <- developmental_mixture_parameter%>%
-  filter(iteration %in% select_dev_mix) %>%
-  spread(type, value) %>%
-  expand_grid(.,age = unique(comb_data$age)) %>%
-  mutate(mixture = plogis(intercept + slope * age))
-
-plot_dev_mixture <- ggplot() +
-  geom_line(data = plot_mixture_line, aes(x=age+2,y = mixture, group = interaction(chain,iteration)),size = .2, alpha = .1)+
-  labs(x="Age",y="Proportion mutual exclusivity component")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  xlim(2,5)+
-  guides(alpha = F, fill = F)
-
-```
-
-```{r fig10, include = T, fig.align = "center", fig.cap = "Mixture component for the mixture model (A) and the developmental mixture model (B).
-(A) shows the posterior distribution of the mixture component and (B) shows developmental trajectories for the mixture component based on 300 random draws from the posterior distribution for intercept and slope.", fig.width=10, fig.height = 4, fig.align= "center"}
-ggarrange(plot_mixture, plot_dev_mixture,  labels = c("A","B"), nrow = 1)
-```
-
-### Model comparison
-
-We compared models based on correlations and Bayes factors.
-Figure \@ref(fig:fig11) shows correlations between model predictions and the data, each binned by year and object.
-Even though model predictions and data are closely aligned for all models, the *integration model* shows the highest correlation in all age groups.
-Next we directly compared models based using Bayes factors (see Table \@ref(tab:table6)).
-We also included the prediction *integration model* into this analysis.
-
-Perhaps unsurprisingly, we see that updating the parameters for semantic knowledge, speaker informativeness and common ground sensitivity greatly improves the model fit (comparison: integration (explanation) vs integration (prediction)).
-We also see that the explanation *integration model* provides, by far, the best fit to the data compared to the two *mixture models*.
-Interestingly, the prediction *integration model* also had a better fit, even though its parameters were not updated based on the data from experiment 3.
-When comparing the two *mixture models* directly, we see that an age sensitive mixture parameter did not result in a substantially better fit.
-
-This analysis shows that the inference and integration process described by the *ingetration model* accurately captures the data and also explains the integration process better compared to the additive *mixture models*.
-As a consequence, we may say that instead of being biased towards one type of inference, children are rationally integrating all the information sources available.
-
-```{r fig11, include = T, fig.align = "center", fig.cap = "Explaining information integration.
-Correlations between model predictions and data binned by year, item and condition.
-Vertical and horizontal error bars show 95\\% HDI.
-Blue diamonds show congruent condition and red ones show the incongruent condition.", fig.width=12, fig.height = 8}
-
-# cor_prag_exp <- readRDS("../saves/model_pred_prag_fb.rds")%>%
-#   mutate(age = as.numeric(age) + min(comb_data$age_num),
-#          age = cut(age,
-#                       breaks = c(2,3,4,5),
-#                       labels = c(2,3,4)))%>%
-#   group_by(model,alignment, item, age)%>%
-#   summarise(model_mean = estimate_mode(pred),
-#             model_ci_lower = hdi_lower(pred),
-#             model_ci_upper = hdi_upper(pred))
-# 
-# cor_mix_exp <- readRDS("../saves/model_pred_mm.rds")%>%
-#   mutate(age = as.numeric(age) + min(comb_data$age_num),
-#          age = cut(age,
-#                       breaks = c(2,3,4,5),
-#                       labels = c(2,3,4)))%>%
-#   group_by(model, alignment, item, age)%>%
-#   summarise(model_mean = estimate_mode(pred),
-#             model_ci_lower = hdi_lower(pred),
-#             model_ci_upper = hdi_upper(pred))
-# 
-# cor_dev_mix_exp <- readRDS("../saves/model_pred_dmm.rds")%>%
-#   mutate(age = as.numeric(age) + min(comb_data$age_num),
-#          age = cut(age,
-#                       breaks = c(2,3,4,5),
-#                       labels = c(2,3,4)))%>%
-#   group_by(model, alignment, item, age)%>%
-#   summarise(model_mean = estimate_mode(pred),
-#             model_ci_lower = hdi_lower(pred),
-#             model_ci_upper = hdi_upper(pred))
-# 
-# 
-# cor_model_exp <- bind_rows(
-#    cor_prag_exp%>%ungroup()%>%mutate(model = "integration"),
-#    cor_mix_exp%>%ungroup()%>%mutate(model = "mixture"),
-#    cor_dev_mix_exp%>%ungroup()%>%mutate(model = "developmental mixture")
-# )
-# 
-# 
-# plot_cor_model_exp <- cor_model_exp %>%
-#   left_join(
-#     bind_rows(
-#        comb_data_binned%>%mutate(model = "integration"),
-#        comb_data_binned%>%mutate(model = "mixture"),
-#        comb_data_binned%>%mutate(model = "developmental mixture")
-#       )
-#   )%>%
-#   mutate(age = fct_recode(age,
-#                           "2-year-olds" = "2",
-#                           "3-year-olds" = "3",
-#                           "4-year-olds" = "4"))
-# 
-# saveRDS(plot_cor_model_exp, "../saves/corr_model_data_exp.rds")
-
-plot_cor_model_exp <- readRDS( "../saves/corr_model_data_exp.rds")%>%
-  mutate(model = factor(model, levels = c("integration", "mixture", "developmental mixture")))
-
-ggplot(data = plot_cor_model_exp,aes(x = model_mean, y = data_mean, col = alignment)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
-  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
-  geom_point(size = 1.5, stroke = 1, pch = 5)+
-  coord_fixed()+
- stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  ylab("Data")+
-  facet_grid(age~model)+
-  theme_few() + 
-  scale_colour_ptol(name ="Condition")
-```
-
-```{r table6}
-model_comp_pred <- readRDS("../saves/expl_model_comparison.rds")%>%
-  mutate(model = factor(model),
-         `Model comparison` = fct_recode(model, 
-                            "integration (explanation) vs integration (prediction)" = "fb_vs_free",
-                            "integration (explanation) vs mixture" = "fb_vs_mixture",
-                            "integration (prediction) vs mixture" = "free_vs_mixture",
-                            "integration (explanation) vs developmental mixture" = "fb_vs_dev_mixture",
-                            "integration (prediction) vs developmental mixture" = "free_vs_dev_mixture",
-                            "developmental mixture vs mixture" = "dev_mixture_vs_mixture"),
-        `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%
-  select(-logBF, -model)
-
-knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2, align = "l")
-```
-
-# Summary
-
-Here we studied how 2 to 5 year old children integrate semantic and pragmatic information during word learning.
-In three experiments, we first showed that children make a mutual exclusivity inference and that this inference varied depending on children's familiarity with the objects involved (experiment 1).
-Next, we showed that children make common ground inferences based on their interactions with a speaker (experiment 2).
-When the two inferences were combined, we found that children were sensitive to the way in which they were aligned (experiment 3).
-
-We then introduced a computational model to investigate the process by which children integrated the inferences in experiment 3.
-As a start, we described mutual exclusivity as a pragmatic inference, which takes in children's emerging semantic knowledge and their expectations about how informative a speaker is.
-The *integration model* assumes that this inference is then flexibly integrated with children's developing sensitivity to common ground.
-
-Next, we tested the predictive power of this model.
-That is, we asked how well the model would predict the data of experiment 3, when only knowing the developmental trajectories for mutual exclusivity (based on experiment 1) and common ground (experiment 2).
-We found a very close alignment of the model predictions and the data across the entire age range.
-Furthermore, the *integration model* provided a better fit to the data compared to a number of lesion models, which selectively omitted one type of information.
-This suggests that children flexibly integrate all available information.
-
-In the final section, we studied which process best explained children's information integration.
-We compared the *integration model* to a *mixture model* which assumed that children are biased towards one type of inference.
-We found that the *integration model* better explained the data compared to these alternative model.
-In sum, we found that children's integration of semantic and pragmatic information during word learning is best described as a form of rational social inference.
-
-# Appendix: Model parameters
-
-In the following, we visualize the model parameters for semantic knowledge, speaker informativeness and common ground sensitivity.
-Please note that the alternative lesion models presented in the prediction section used the same parameter distributions as the prediction *integration model*.
-
-## Semantic knowledge
-
-### Intercept
-
-```{r}
-item_comp <- bind_rows(
-  item_params_exp %>% mutate(model = "integration (explanation)"),
-  item_params %>% mutate(model = "integration (prediction)"),
-  item_params_mixture %>% mutate(model = "mixture"),
-  item_params_dev_mixture %>% mutate(model = "developmental mixture")
-)%>%
-  mutate(model = factor(model, levels = c("integration (prediction)","integration (explanation)", "mixture","developmental mixture")))
-
-```
-
-```{r figa1, include = T, fig.align = "center", fig.cap = "Posterior distribution of intercept term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
-
-item_comp_int <- item_comp %>%
-  filter(parameter == "intercept")
-
-ggplot(item_comp_int, aes(x = value, fill = model, col = model))+
-  geom_density(alpha = 0.8, adjust = 2)+
-  xlab("value")+
-  facet_wrap( ~ item, nrow = 2, scales = 'free')+
-  theme_few()+
-  xlim(-10,5)+
-  theme(legend.position = "bottom")+
-  scale_fill_ptol(name = "Model")+
-  scale_color_ptol(name = "Model")
-```
-
-### Slope
-
-```{r figa2, include = T, fig.align = "center", fig.cap = "Posterior distribution of slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
-
-item_comp_slope <- item_comp %>%
-  filter(parameter == "slope")
-
-ggplot(item_comp_slope, aes(x = value, fill = model, col = model))+
-  geom_density(alpha = 0.8, adjust = 2)+
-  xlab("value")+
-  facet_wrap( ~ item, nrow = 2, scales = 'free_y')+
-  xlim(-1,4)+
-  theme_few()+
-  theme(legend.position = "bottom")+
-  scale_fill_ptol(name = "Model")+
-  scale_color_ptol(name = "Model")
-```
-
-## Speaker informativeness and common ground sensitivity
-
-```{r figa3, include = T, fig.align = "center", fig.cap = "Posterior distribution of slope and intercept terms for speaker informativeness and sensitivity to common ground by model.", fig.width=8, fig.height = 6, fig.align="center"}
-
-global_comp <- bind_rows(
-  global_params_exp %>% mutate(model = "integration (explanation)"),
-  global_params %>% mutate(model = "integration (prediction)"),
-  global_params_mixture %>% mutate(model = "mixture"),
-  global_params_dev_mixture %>% mutate(model = "developmental mixture")
-)%>%
-  filter(parameter !="global_sem")%>%
-  mutate(parameter = fct_recode(parameter, 
-                               "common ground sensitivity" = "prior",
-                               "speaker informativeness" = "speaker_optimality"))%>%
-  mutate(model = factor(model, levels = c("integration (prediction)","integration (explanation)", "mixture","developmental mixture")))
-
-ggplot(global_comp, aes(x = value, fill = model, col = model))+
-  geom_density(alpha = 0.8, adjust = 2)+
-  xlab("value")+
-  facet_grid(type ~ parameter, scales = 'free')+
-  theme_few()+
-  theme(legend.position = "bottom")+
-  scale_fill_ptol(name = "Model")+
-  scale_color_ptol(name = "Model")
-```

### 2020-04-01 paper/supplementary_material.Rmd
play around with visuals

@@
 To decide between referents, the listener reasons about what a rational speaker would say given an intended referent.
-This speaker is assumed to compute the informativity of for each available utterance and then choose the most informative one.
+This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one.
 However, this expectation of speaker informativeness may vary and is captured by the parameter $\alpha$.
@@
   coord_fixed()+
- stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean, label = paste(..rr.label..)), inherit.aes = F, size = 3)+
   xlim(0,1)+ylim(0,1)+

### 2020-04-01 paper/visualizations.Rmd
play around with visuals

@@
 library(BayesFactor)
+library(xkcd)
 
@@
 
+sel_items <- c("apple", "pawn", "garlic", "bread")
+
 sem_know_map <- item_params_summary%>%
+  filter(item %in% sel_items)%>%
   select(-uci,-lci)%>%
@@
   xlab("Age")+
-  ylim(0,1)+
-  theme_few()+
-  scale_colour_viridis_d(name = "Object")
+  theme_xkcd()+ 
+  scale_y_continuous(
+    breaks = c(0,0.9),
+    labels= c("no idea", "very sure"))+
+  guides(col = guide_legend(title="Object"))
 
+```
+
+```{r}
 # plot or speaker optimality
@@
 plot_speak_opt <- ggplot() +
-  geom_line(data = speak_opt_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
+  #geom_line(data = speak_opt_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
   geom_line(data = speak_opt_map, aes(x=age+2,y = y),size = 1)+
   labs(x="Age",y="Speaker informativeness")+
-  theme_few() +
-  ylim(0,10)+
     xlim(2,5)+
-  guides(alpha = F, fill = F, col = F)
+  guides(alpha = F, fill = F, col = F)+
+  theme_xkcd()+
+  scale_y_continuous(
+    limits = c(1,6),
+    breaks = c(1,6),
+    labels= c("OK", "very high"))
 
@@
 plot_prior <- ggplot() +
-  geom_line(data = prior_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
+  #geom_line(data = prior_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
   geom_line(data = prior_map, aes(x=age+2,y = y),size = 1)+
-  labs(x="Age",y="Prior sensitivity")+
-  theme_few() +
-  ylim(0,1)+
+  labs(x="Age",y="Sensitivity to common ground")+
   xlim(2,5)+
-  guides(alpha = F, fill = F, col = F)
+  guides(alpha = F, fill = F, col = F)+
+  theme_xkcd()+
+  scale_y_continuous(
+    limits = c(0.5,1),
+    breaks = c(0.5,1),
+    labels= c("absent", "high"))
 
 ```
+
+```{r}
+ggsave(plot = plot_speak_opt,"../graphs/speak_inf.png", width = 2.5, height = 2.5, scale = 1.5)
+```
+
+```{r}
+plot_prag_pred <- readRDS( "../saves/plot_prag_pred.rds")
+
+ggplot(data = comb_data, aes(x = age_num, y = correct)) +
+  #geom_hline(yintercept = 0.5, lty=2)+
+  #geom_jitter(col = "black", height = .025, alpha = .1)+
+  #geom_pointrange(data = comb_data_binned, aes(x = subage+.5, y = data_mean, ymin =data_ci_lower, ymax = data_ci_upper), stroke = 1, pch = 5)+
+  #geom_line(data = comb_data_binned, aes(x = subage+.5, y = data_mean))+
+  geom_line(data = plot_prag_pred, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)), size = .2, alpha = .25)+
+  #geom_smooth(data = comb_data, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .4, lty = 2, size = 1)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  theme_xkcd()+
+  guides(alpha = F, fill = F, col = F)+
+  scale_y_continuous(
+    limits = c(0,1),
+    breaks = c(0,1),
+    labels= c("low", "high"))
+```
+
+```{r}
+ggsave("../graphs/pred_cartoon.png", width = 7.5, height = 2, scale = 1.5)
+```
+
 ```{r}
@@
 
-pred_cor <- ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
+pred_cor <- ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean)) +
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
@@
   geom_point(size = 1.5, stroke = 1, pch = 5)+
-  #coord_fixed()+
- stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean, label = paste(..rr.label..)), inherit.aes = F, size = 3)+
   xlim(0,1)+ylim(0,1)+
@@
   theme_few() + 
-  scale_colour_ptol(name ="Condition")
+  theme(legend.position = c(.9,.2), 
+        legend.background = element_blank())
+```
+
+```{r}
+ggsave(plot = pred_cor,"../graphs/cor_pred.png", width = 6, height = 2, scale = 1.5)
 ```
@@
 ```
+
+```{r}
+plot_prag_exp<- readRDS( "../saves/plot_prag_exp.rds")
+
+ggplot(data = comb_data, aes(x = age_num, y = correct)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  #geom_jitter(col = "black", height = .025, alpha = .1)+
+  #geom_pointrange(data = comb_data_binned, aes(x = subage+.5, y = data_mean, ymin =data_ci_lower, ymax = data_ci_upper), stroke = 1, pch = 5)+
+  #geom_line(data = comb_data_binned, aes(x = subage+.5, y = data_mean))+
+  geom_line(data = plot_prag_exp, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)), size = .2, alpha = .25)+
+  geom_smooth(data = comb_data, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .4, lty = 2, size = 1)+
+  labs(x="Age",y="Mutual Exclusivity effect")+
+  facet_grid(alignment~item)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  xlim(2,5)+
+  guides(alpha = F, fill = F, col = F)+ 
+  scale_colour_ptol(name = NULL)
+```
+
+```{r}
+ggsave("../graphs/paper_figure3.png", width = 6, height = 2, scale = 1.5)
+ ```
+
+```{r}
+plot_cor_model_exp <- readRDS( "../saves/corr_model_data_exp.rds")%>%
+  filter(model == "integration")
+
+plot_cor_exp <- ggplot(data = plot_cor_model_exp,aes(x = model_mean, y = data_mean, col = alignment)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
+  geom_point(size = 1.5, stroke = 1, pch = 5)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(~age)+
+  theme_few() + 
+  scale_colour_ptol(name = "")
+```
+
+```{r}
+ggarrange(
+ggarrange(plot_speak_opt, plot_prior,plot_sem_know, labels = c("A","B","C"), nrow = 1, widths = c(1,1,1.5)),
+ggarrange(pred_cor, labels = c("D"), nrow = 1 ),
+nrow= 2,
+heights = c(1,1)
+)
+```

### 2020-04-01 paper/supplementary_material.Rmd
play around with visuals

@@
 We first describe an *integration model* which we think best represents the inference and integration processes and then specify how this model captures developmental change.
-Next, we ask how well this model *predicts* how children integrate the two information sources.
-That is, in a situation in which we know the development trajectories for the mutual exclusivity inference as well as for the common ground inference, what can we say about what happens when common ground and mutual exclusivity are combined.
+Next, we ask how well this model *predicts* how children integrate information.
+That is, in a situation in which we know the development trajectories for the mutual exclusivity inference (for a particualr familiar object) as well as for the common ground inference, what can we say about what happens when they are combined.
 We then test the predictive power of the model by comparing the model predictions to the data from experiment 3.
@@
 
-Finally, we ask how well our model *explains* the way that children integrate the two information sources.
+Finally, we ask how well our model *explains* the way that children integrate the different information sources.
 For this analysis, we fit the free parameters in the model to all the available data, those from experiment 1 and 2 as well as the integration data from experiment 3.

### 2020-04-03 paper/supplementary_material.Rmd
clean repo

@@
 
-We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | item) + (age * alignment | agent)`.
+We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | object) + (age * alignment | agent)`.
 We pre-registered to include item as a fixed effect in Experiment 3.
@@
 The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate.
-Experiment 1 showed that children of all age groups are make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented.
-Experiment 2 showed that three- and four-year-olds are sensitive the common ground manipulation we implemented and that this inference increases with age.
+Experiment 1 showed that children of all age groups make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented.
+Experiment 2 showed that children are sensitive the common ground manipulation we implemented and that this inference increases with age.
 Finally, experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another.
-In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when the two inferences are combined with one another.
+In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when inferences are combined with one another.
 
@@
 Top row (blue) shows the congruent condition and the bottom row (red) shows the inconguent condition.
-Familiar objects are ordered based on their rated age of acquisition (left o right).
+Familiar objects are ordered based on their rated age of acquisition (left to right).
 Dashed black lines show smoothed conditional mean of the data with 95\\% CI (in grey).
@@
                             "no mutual exclusivity vs no common ground" = "flat_vs_prior"),
-        `Bayes factor` = format(round(exp(logBF),2), trim = T, justify = "right", digits = 2))%>%
+        `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%
   select(-logBF, -model)

### 2020-04-03 paper/supplementary_material.Rmd
small chnages to supplement

@@
 plot_aoa <- ggplot(plot_aoa_ratings, aes(x = reorder(item, mean_aoa), y = mean_aoa)) +
-  geom_point(size =2, pch = 4)+
+  geom_point(size =2, pch = 4, aes(col = item))+
   ylab("Mean rated age of acquisition")+
@@
   theme_light()+
-    theme(axis.text.x = element_text(angle = 45, hjust = 1))
+    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
+  scale_colour_viridis_d()+
+  guides(col = F)
+
 ```
@@
   ggplot(., aes(x = mean_aoa, y = Estimate.Intercept))+
-  geom_abline(intercept = 1, slope = -1, lty = 2, alpha = 1, size = .5)+
-  geom_point(pch = 4, size = 2)+
+  geom_point(pch = 4, size = 2, aes(col = item))+
   geom_smooth(method = "lm", col = "black", se = F, lty = 2, size = .5)+
@@
   ylim(-1,1)+
-  stat_cor(method = "pearson", label.x = 7, label.y = .99)+
-  theme_few()
+  stat_cor(method = "pearson", label.x = 6, label.y = .99)+
+  theme_few()+
+  scale_colour_viridis_d()+
+  guides(col = F)
 ```
@@
 C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}
-ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1))
+ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
 ```

### 2020-04-08 paper/supplementary_material.Rmd
finish prediction section

@@
 On the one hand, we used correlations between model predictions and the data.
-For this analysis, we binned the model predictions and the data by year and familiar object.
+For this analysis, we binned the model predictions and the data by age in years and familiar object.
 Figure \@ref(fig:fig6) visualizes the correlation between model predictions and the data for all models.
@@
 The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds.
-This is probably a consequence of the model making very extreme predictions for the oldest age group.
-Correlations for the *integration model* were also higher compared to the other models considered.
-
-On the other hand, we compared models based on Bayes factors which were calculated from the marginal likelihoods of each model given the data.
+The mis-match for the oldest age group is probably a consequence of the model making very extreme predictions for this group.
+[MH: Do we know why the model makes extreme predictions for the older age?
+Is it because they are at ceiling on the ME and/or common ground task, and our model posits no integration cost?] Correlations for the *integration model* were also higher compared to the other models considered.
+
+We additionally compared models based on the marginal likelihood of the data under each model -- the likelihood of the data averaging over ("marginalizing over") the prior distribution on parameters; the pair-wise ratio of marginal likelihoods for two models is known as the Bayes Factor (see file `model_comparison.Rmd` in the associated online repository).
+Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by their prior probability); by averaging over the prior distribution on parameters, Bayes Factor implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the possible better predictions that a model with more parameters can achieve (CITE: Lee & Wagenmakers 2014 Bayesian Cognitive Modeling).
 For this analysis, we treated age continuously.
-We first calculated the marginal log-likelihood for each model and then computed Bayes factors by subtracting the log-likelihoods for the models involved in the comparison and then exponentiating the result (see file `model_comparison.Rmd` in the associated online repository).
 Table \@ref(tab:table5) lists the Bayes factors for the different model comparisons.
@@
 
-Taken together, this analysis showed two things.
-First, the *integration model* makes accurate predictions about how mutual exclusivity and common ground inferences are integrated with one another.
-It does so based on knowing the strength and development of each inference alone.
-Second, models that omit one or more type of information (object specific word knowledge, speaker informativeness, common ground sensitivity) make much worse predictions.
-This exemplifies that children across the entire age range flexibly integrate all the available information.
+Taken together, these analyses showed two things.
+First, the *integration model* makes accurate predictions about how mutual exclusivity and common ground inferences are integrated.
+It does so based on knowing the strength and development of each inference alone, and incorporating them into a structured probabilistic model of pragmatic reasoning.
+Second, models that omit one or more types of information (object specific word knowledge, speaker informativeness, common ground sensitivity) make appreciably worse predictions.
+This result exemplifies that children across the entire age range flexibly integrate all the available information.
 In the next section we ask whether there are other ways think about the process of information integration than the way formalized in the *integration model*.

### 2020-04-08 paper/supplementary_material.Rmd
edits until mixture model math in explanation section

@@
 We explore alternative ways to think about information integration.
-The *integration model* outlined above operates via Bayesian inference in that the prior probability of a referent - a consequence of the common ground manipulation - is updated upon hearing the utterance and computing the mutual exclusivity inference.
-In essence, this model is a multiplicative model because the probability of each referent is proportional to the product of the likelihood and the prior.
-The alternative model we consider here is an additive model.
-This *mixture model* assumes that the two inferences are computed separately and then weighted by some ratio $\phi$.
-Psychologically, $\phi$ may be interpreted as a bias for one type of inference relative to the other.
-
-With respect to developmental change, the *integration model* assumes that the process by which information is integrated remains the same across development.
-What changes is children's semantic knowledge, their expectations about speaker informativeness and their sensitivity to common ground.
-But the way these information sources are combined remains the same across age.
-As an alternative, we explore a *developmental mixture model*.
-This model makes the same assumptions about developmental change in the individual information sources but, in addition, also assumes that the way that the the mutual exclusivity and the common ground inference are combined with one another changes over time.
-It is structurally identical to the *mixture model* but the mixture parameter $\phi$ is a function of age.
-
-In this section, we make use of all the available data.
-We use the data from experiment 1 and 2 to compute prior distributions over model parameters which are subsequently updated depending on how well the model predictions they generate fit the data.
+The *integration model* outlined above operates via Bayesian inference in that the prior probability of a referent (a consequence of the common ground manipulation) is updated via the likelihood of hearing the utterance heard from a speaker, which is used to derive the mutual exclusivity inference.
+In essence, this model is a multiplicative model because the posterior probability of each referent given the utterance is proportional to the product of the likelihood of a speaker saying that utterance and the prior probability of that referent.
+
+Information sources need not be integrated in a Bayesian manner.
+Rather than be part of the same pragmatic reasoning architecture, the common ground and mutual exclusitivity inferences we consider could be computed separately and then combined.
+A listener could integrate these two independent inferences in an additive manner, weighting the sources of information by some ratio $\phi$.
+$\phi$ is then a bias to prefer one type of inference relative to the other.
+We formalize this alternative hypothesis as a  *mixture model*.
+
+The *integration* and *mixture* models have different implications for developmental change.
+The *integration model* assumes that the process by which information is integrated remains constant across development.
+What changes is children's semantic knowledge, their expectations about speaker informativeness, and their sensitivity to common ground, but the way these information sources are combined remains the same across age.
+The *mixture model* alternatively posits that there is some bias or preference for one information source, and this bias could across development.
+This *developmental mixture model*  makes the same assumptions about developmental change in the individual information sources as the *integration model* but, in addition, assumes that the way that the the mutual exclusivity and the common ground inference are combined with one another changes over time.
+This model is structurally identical to the *mixture model* but the mixture parameter $\phi$ is a function of age.
+
+In this section, we make use of all the available data to arbitrate between these alternative models (a fully Bayesian analysis).
+As before, Experiments 1 and 2 directly constrain the parameters governing semantic knowledge, speaker informativeness, and the prior distribution over referents (via common ground; Expt.
+2).
+Now, in addition, we incorporate the data from Experiment 3 to additionally constrain these parameters as well as inform the mixture parameter for the mixture model.
 
@@
 
-The *integration model* in this section differs from the same model in the prediction section only in the distributions for the parameters representing the different information sources.
-Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the appendix show how the  parameter distributions differ between the prediction and the explanation version of the *integration* model.
-As a quick summary, we can say that semantic knowledge and speaker informativeness have similar distributions when taking into account all the data compared to when estimating these parameters only based on experiment 1 and 2.
-In contrast, the intercept for common ground sensitivity is estimated to be larger and the slope shallower.
+The *integration model* in this section differs from the integration model in the **Prediction Section** only in that the parameter distributions are now additionally informed by the data from Experiment 3.
+Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the Appendix show how the parameter distributions differ between the prediction and the explanation version of the *integration* model.
+Semantic knowledge and speaker informativeness have similar posterior distributions when taking into account all the data compared to when estimating these parameters only based on experiment 1 and 2.
+In contrast, the intercept for common ground sensitivity is estimated to be larger and the slope shallower after taking into account Experiment 3 data.
+That is, our best guess for common ground sensitivity after taking into account the data from Experiment 3 is that children overall are more sensitive to the common ground manipulation and there is less developmental change.
 The code to run the model can be found in the associated online repository (file: xxxxxxx).
@@
 
-In the *mixture model* the two inferences are computed in the same way as in in the *integration model*. Subsequently, they are weighted by the mixture parameter $\phi$:
+In the *mixture model* the two inferences (common ground and mutual exclusivity) are computed in the same way as in in the *integration model*.
+Subsequently, they are weighted by the mixture parameter $\phi$:
 

### 2020-04-10 paper/bda_fig.tex
first draft of bda plate diagram fig

\documentclass{article}
    % General document formatting
    \usepackage[margin=0.7in]{geometry}
    \usepackage[parfill]{parskip}
    \usepackage[utf8]{inputenc}

    % Related to math
    \usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{tikz}
\usepackage{subfigure}
\usetikzlibrary{bayesnet}

\begin{document}

\begin{figure}[ht]
\begin{center}
\begin{tabular}{cc}
\begin{tikzpicture}
	%% RSA nodes and data
	\node[obs](data_comb){$d^{CM}_{i, j, k}$};
	\node[obs, left=3 of data_comb, yshift=3cm](data_me){$d^{ME}_{i, j}$};
	\node[obs, right=2 of data_comb, yshift=1cm](data_cg){$d^{CG}_{i}$};

	\node[det, above=of data_me](L1_me){$L'_1$};
	\node[det, above=of data_comb](L1_comb){$L_1$};

	\edge{L1_me}{data_me};
	\edge{L1_comb}{data_comb};

	% COMMON GROUND
	\node[latent, above=of data_cg](rho){$\rho_i$};
	\node[latent, above=of rho, xshift=-0.5cm](beta_rho_int){$\beta^{\rho}_0$};
	\node[latent, above=of rho, xshift=0.5cm](beta_rho_slope){$\beta^{\rho}_1$};

	\edge{rho}{data_cg};
	\edge{beta_rho_int}{rho};
	\edge{beta_rho_slope}{rho};
	\edge{rho}{L1_comb};

	%% SPEAKER INFORMATIVITY

	\node[latent, above=of L1_me](alpha){$\alpha_i$};
	\node[latent, above=of alpha, xshift=-0.5cm](beta_alpha_int){$\beta^{\alpha}_0$};
	\node[latent, above=of alpha, xshift=0.5cm](beta_alpha_slope){$\beta^{\alpha}_1$};

	\edge{alpha}{L1_me};
	\edge{beta_alpha_int}{alpha};
	\edge{beta_alpha_slope}{alpha};
	\edge{alpha}{L1_comb};

	%% SEMANTIC KNOWLEDGE model

	\node[latent, above=of L1_comb](theta){$\theta_{ij}$};
	\node[latent, above=of theta, xshift=-1.25cm](beta_theta_int){$\beta^{\theta}_{0, j}$};
	\node[latent, above=of theta, xshift=1.25cm](beta_theta_slope){$\beta^{\theta}_{1, j}$};

	\node[latent, above=of beta_theta_int, xshift=-0.5cm](mu_theta_int){$\mu^{\theta}_{0}$};
	\node[latent, above=of beta_theta_int, xshift=0.5cm](sigma_theta_int){$\sigma^{\theta}_{0}$};

	\node[latent, above=of beta_theta_slope, xshift=-0.5cm](mu_theta_slope){$\mu^{\theta}_{1}$};
	\node[latent, above=of beta_theta_slope, xshift=0.5cm](sigma_theta_slope){$\sigma^{\theta}_{1}$};

	\edge{theta}{L1_me};
	\edge{theta}{L1_comb};
	\edge{beta_theta_int}{theta};
	\edge{beta_theta_slope}{theta};
	\edge{mu_theta_int}{beta_theta_int};
	\edge{sigma_theta_int}{beta_theta_int};
	\edge{mu_theta_slope}{beta_theta_slope};
	\edge{sigma_theta_slope}{beta_theta_slope};

	\plate{plate_data_me}{
		(data_me)
	}{$i \in \mathcal{P}_{1}$}

	\plate{plate_data_comb}{
		(data_comb)
	}{$i \in \mathcal{P}_{3}$}

	\plate{plate_data_cg}{
		(data_cg)
	}{$i \in \mathcal{P}_{2}$}

	\plate{plate_condition}{(plate_data_comb)}{$k \in \mathcal{K}$};

	\plate{plate_items}{
		(plate_data_me)
		(plate_data_comb)
		(plate_condition)
		(L1_me)
		(L1_comb)
		(theta)
		(beta_theta_int)
		(beta_theta_slope)
	}{$j \in \mathcal{J}$}

\end{tikzpicture}

    \end{tabular}
  \end{center}
  \caption{ Put a caption here.}
  \label{fig:bayesnet}
\end{figure}

\end{document}

### 2020-04-10 paper/bda_fig.tex
a few more versions of the bda model

@@
 	%% RSA nodes and data
-	\node[obs](data_comb){$d^{CM}_{i, j, k}$};
-	\node[obs, left=3 of data_comb, yshift=3cm](data_me){$d^{ME}_{i, j}$};
-	\node[obs, right=2 of data_comb, yshift=1cm](data_cg){$d^{CG}_{i}$};
+	\node[obs](data_comb){$d^{CM}_{{i}, j, k}$};
+	\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{ME}_{{i}, j}$};
+	\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};
 
@@
 	\node[det, above=of data_comb](L1_comb){$L_1$};
+	\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};
 
@@
 	\edge{L1_comb}{data_comb};
+	\edge{RSA}{L1_me};
+	\edge{RSA}{L1_comb};
 
 	% COMMON GROUND
-	\node[latent, above=of data_cg](rho){$\rho_i$};
-	\node[latent, above=of rho, xshift=-0.5cm](beta_rho_int){$\beta^{\rho}_0$};
-	\node[latent, above=of rho, xshift=0.5cm](beta_rho_slope){$\beta^{\rho}_1$};
+	\node[latent, above=of data_cg, yshift=0.1cm](rho){$\rho_i$};
+	\node[latent, right=of rho, yshift=0.5cm](beta_rho_int){$\beta^{\rho}_0$};
+	\node[latent, right=of rho, yshift=-0.5cm](beta_rho_slope){$\beta^{\rho}_1$};
 
@@
 
-	\node[latent, above=of L1_me](alpha){$\alpha_i$};
-	\node[latent, above=of alpha, xshift=-0.5cm](beta_alpha_int){$\beta^{\alpha}_0$};
-	\node[latent, above=of alpha, xshift=0.5cm](beta_alpha_slope){$\beta^{\alpha}_1$};
+	\node[latent, left=of RSA, xshift=-1cm](alpha){$\alpha_i$};
+	\node[latent, left=of alpha, yshift=0.5cm](beta_alpha_int){$\beta^{\alpha}_0$};
+	\node[latent, left=of alpha, yshift=-0.5cm](beta_alpha_slope){$\beta^{\alpha}_1$};
+
+%	\edge{alpha}{L1_me};
+	\edge{beta_alpha_int}{alpha};
+	\edge{beta_alpha_slope}{alpha};
+	\edge{alpha}{RSA};
+
+	%% SEMANTIC KNOWLEDGE model
+
+	\node[latent, above=of RSA, yshift=-0.25cm](theta){$\theta_{ij}$};
+	\node[latent, above=of theta, xshift=-1.25cm, yshift=-0.5cm](beta_theta_int){$\beta^{\theta}_{0, j}$};
+	\node[latent, above=of theta, xshift=1.25cm, yshift=-0.5cm](beta_theta_slope){$\beta^{\theta}_{1, j}$};
+
+	\node[latent, above=of beta_theta_int, xshift=-0.5cm](mu_theta_int){$\mu^{\theta}_{0}$};
+	\node[latent, above=of beta_theta_int, xshift=0.5cm](sigma_theta_int){$\sigma^{\theta}_{0}$};
+
+	\node[latent, above=of beta_theta_slope, xshift=-0.5cm](mu_theta_slope){$\mu^{\theta}_{1}$};
+	\node[latent, above=of beta_theta_slope, xshift=0.5cm](sigma_theta_slope){$\sigma^{\theta}_{1}$};
+
+	\edge{theta}{RSA};
+%	\edge{theta}{L1_comb};
+	\edge{beta_theta_int}{theta};
+	\edge{beta_theta_slope}{theta};
+	\edge{mu_theta_int}{beta_theta_int};
+	\edge{sigma_theta_int}{beta_theta_int};
+	\edge{mu_theta_slope}{beta_theta_slope};
+	\edge{sigma_theta_slope}{beta_theta_slope};
+
+%	\plate{plate_data_me}{
+%		(data_me)
+%	}{$i \in \mathcal{P}_{1}$}
+
+%	\plate{plate_data_cg}{
+%		(data_cg)
+%	}{$i \in \mathcal{P}_{2}$}
+
+	\plate{plate_condition}{(data_comb)(L1_comb)}{$k \in \text{expt.~conditions}$};
+
+	\plate{plate_items}{
+%		(plate_data_me)
+%		(plate_data_comb)
+%		(plate_condition)
+	(plate_condition)
+		(data_comb)
+		(data_me)
+		(L1_me)
+		(L1_comb)
+		(theta)
+		(beta_theta_int)
+		(beta_theta_slope)
+	}{$j \in \text{items}$}
+
+	\plate{plate_data_comb}{
+		(data_comb)
+		(data_cg)
+		(data_me)
+		(plate_condition)
+		(rho)
+		(theta)
+		(alpha)
+		(L1_me)
+		(L1_comb)
+%		(plate_items)
+	}{$i \in \text{2-to-4 year olds}$}
+
+\end{tikzpicture}
+
+    \end{tabular}
+  \end{center}
+  \caption{ Put a caption here.}
+  \label{fig:bayesnet}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+\begin{tabular}{cc}
+\begin{tikzpicture}
+	%% RSA nodes and data
+	\node[obs](data_comb){$d^{CM}_{i, j, k}$};
+	\node[det, above=of data_comb](L1_comb){$L_1$};
+	\edge{L1_comb}{data_comb};
+
+%	\node[det, right=of data_me](L1_me){$L'_1$};
+
+%	\edge{L1_me}{data_me};
+
+	% COMMON GROUND
+	\node[latent, right=of L1_comb](rho){$\rho_i$};
+	\node[obs, right=of rho](data_cg){$d^{CG}_{i}$};
+	\node[latent, right=of rho, yshift=-2cm](beta_rho_int){$\beta^{\rho}_0$};
+	\node[latent, right=of rho, yshift=-3cm](beta_rho_slope){$\beta^{\rho}_1$};
+
+	\edge{rho}{data_cg};
+	\edge{beta_rho_int}{rho};
+	\edge{beta_rho_slope}{rho};
+	\edge{rho}{L1_comb};
+
+	%% SPEAKER INFORMATIVITY
+
+	\node[latent, left=of L1_comb](alpha){$\alpha_i$};
+	\node[latent, left=of alpha, yshift=-2cm](beta_alpha_int){$\beta^{\alpha}_0$};
+	\node[latent, left=of alpha, yshift=-3cm](beta_alpha_slope){$\beta^{\alpha}_1$};
+	\node[det, left=of alpha](L1_me){$L'_1$};
+	\node[obs, left=of L1_me](data_me){$d^{ME}_{i, j}$};
 
@@
 	\edge{alpha}{L1_comb};
+	\edge{L1_me}{data_me};
 
@@
 
+		\plate{plate_items_me}{
+		(data_me)
+	}{$j \in \text{items}$}
+
 	\plate{plate_data_me}{
 		(data_me)
+		(L1_me)
+		(alpha)
+		(plate_items_me)
 	}{$i \in \mathcal{P}_{1}$}
 
+	\plate{plate_data_cg}{
+		(data_cg)(rho)
+	}{$i \in \mathcal{P}_{2}$}
+
+	\plate{plate_items}{
+		(data_comb)(L1_comb)(theta)
+	}{$j \in \text{items}$}
+
 	\plate{plate_data_comb}{
-		(data_comb)
-	}{$i \in \mathcal{P}_{3}$}
+		(data_comb)(rho)(alpha)(theta)(plate_items)
+	}{$i \in \mathcal{P}_{2}$}
+
+\end{tikzpicture}
+
+    \end{tabular}
+  \end{center}
+  \caption{ Put a caption here.}
+  \label{fig:bayesnet}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+\begin{tabular}{cc}
+\begin{tikzpicture}
+	%% RSA nodes and data
+	\node[obs](data_comb){$d^{CM}_{i, j, k}$};
+	\node[det, above=of data_comb](L1_comb){$L_1$};
+	\edge{L1_comb}{data_comb};
+
+%	\node[det, right=of data_me](L1_me){$L'_1$};
+
+%	\edge{L1_me}{data_me};
+
+	% COMMON GROUND
+	\node[latent, right=of L1_comb](rho){$\rho_i$};
+	\node[obs, right=of rho](data_cg){$d^{CG}_{i}$};
+	\node[latent, right=of rho, yshift=-2cm](beta_rho_int){$\beta^{\rho}_0$};
+	\node[latent, right=of rho, yshift=-3cm](beta_rho_slope){$\beta^{\rho}_1$};
+
+	\edge{rho}{data_cg};
+	\edge{beta_rho_int}{rho};
+	\edge{beta_rho_slope}{rho};
+	\edge{rho}{L1_comb};
+
+	%% SPEAKER INFORMATIVITY
+
+	\node[latent, left=of L1_comb, yshift=0.5cm](alpha){$\alpha_i$};
+	\node[latent, left=of alpha, yshift=-2cm](beta_alpha_int){$\beta^{\alpha}_0$};
+	\node[latent, left=of alpha, yshift=-3cm](beta_alpha_slope){$\beta^{\alpha}_1$};
+	\node[det, left=of alpha, yshift=1.8cm](L1_me){$L'_1$};
+	\node[obs, left=of L1_me](data_me){$d^{ME}_{i, j}$};
+
+	\edge{alpha}{L1_me};
+	\edge{beta_alpha_int}{alpha};
+	\edge{beta_alpha_slope}{alpha};
+	\edge{alpha}{L1_comb};
+	\edge{L1_me}{data_me};
+
+	%% SEMANTIC KNOWLEDGE model
+
+	\node[latent, above=of L1_comb](theta){$\theta_{ij}$};
+	\node[latent, above=of theta, xshift=-1.25cm](beta_theta_int){$\beta^{\theta}_{0, j}$};
+	\node[latent, above=of theta, xshift=1.25cm](beta_theta_slope){$\beta^{\theta}_{1, j}$};
+
+	\node[latent, above=of beta_theta_int, xshift=-0.5cm](mu_theta_int){$\mu^{\theta}_{0}$};
+	\node[latent, above=of beta_theta_int, xshift=0.5cm](sigma_theta_int){$\sigma^{\theta}_{0}$};
+
+	\node[latent, above=of beta_theta_slope, xshift=-0.5cm](mu_theta_slope){$\mu^{\theta}_{1}$};
+	\node[latent, above=of beta_theta_slope, xshift=0.5cm](sigma_theta_slope){$\sigma^{\theta}_{1}$};
+
+	\edge{theta}{L1_me};
+	\edge{theta}{L1_comb};
+	\edge{beta_theta_int}{theta};
+	\edge{beta_theta_slope}{theta};
+	\edge{mu_theta_int}{beta_theta_int};
+	\edge{sigma_theta_int}{beta_theta_int};
+	\edge{mu_theta_slope}{beta_theta_slope};
+	\edge{sigma_theta_slope}{beta_theta_slope};
+
+	{
+	\tikzset{plate caption/.append style={below right=2pt and 0pt of #1.south west}}
+		\plate{plate_items_me}{
+			(data_me)(L1_me)(theta)(beta_theta_int)(beta_theta_slope)
+		}{$j \in \text{items}$}	
+	}
+
+	{
+	\tikzset{plate caption/.append style={below right=0pt and 0pt of #1.south west}}
+	\plate{plate_data_me}{
+		(data_me)
+		(L1_me)
+		(alpha)
+%		(plate_items_me)
+	}{$i \in \mathcal{P}_{1}$}
+	}
 
 	\plate{plate_data_cg}{
-		(data_cg)
+		(data_cg)(rho)
 	}{$i \in \mathcal{P}_{2}$}
 
-	\plate{plate_condition}{(plate_data_comb)}{$k \in \mathcal{K}$};
+	\plate{plate_items}{
+		(data_comb)(L1_comb)(theta)
+	}{$j \in \text{items}$}
 
-	\plate{plate_items}{
-		(plate_data_me)
-		(plate_data_comb)
-		(plate_condition)
-		(L1_me)
-		(L1_comb)
-		(theta)
-		(beta_theta_int)
-		(beta_theta_slope)
-	}{$j \in \mathcal{J}$}
+	\plate{plate_data_comb}{
+		(data_comb)(rho)(alpha)(theta)(plate_items)
+	}{$i \in \mathcal{P}_{3}$}
 

### 2020-04-13 paper/bda_fig.tex
add a caption

@@
 	%% RSA nodes and data
-	\node[obs](data_comb){$d^{CM}_{{i}, j, k}$};
-	\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{ME}_{{i}, j}$};
+	\node[obs](data_comb){$d^{CM}_{ijk}$};
+	\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{ME}_{ij}$};
 	\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};
@@
 
-	\plate{plate_condition}{(data_comb)(L1_comb)}{$k \in \text{expt.~conditions}$};
+	\plate{plate_condition}{(data_comb)(L1_comb)}{$k \in \text{alignments}$};
 
@@
   \end{center}
-  \caption{ Put a caption here.}
+  \caption{Graphical model representing the Bayesian data analysis for \emph{Integration model} used for \emph{Explanation}.
+$L_1$ represents the RSA model defined by Eq.
+X, used to predict the Combination Data from Expt.~3 $d^{CM}$ for each unique age bin $i$, lexical item $j$, and alignment condition $k$.
+This RSA model takes as input a speaker optimality parameter $\alpha_i$ (which varies by age), a semantic knowledge parameter $\theta_{ij}$, and a common ground sensitivity $\rho_i$ (which varies by age).
+Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{ME}$; Expt.~1), via a related RSA model $L'_1$;  common ground sensitivity parameters $\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{CG}$; Expt.~2).
+  Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\beta_0$ and $\beta_1$, respectively).
+Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\mu$ and $\sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories.}
   \label{fig:bayesnet}
 \end{figure}
+%S2 represents the RSA speaker model defined by Eq.
+1, which is used to predict the production responses dprod of each participant i, for each state s (number of hearts), for each utterance w, in each goal condition g.
+The RSA speaker model takes as input the literal meaning variables θ, which additionally are used to predict the literal meaning judgments dlit assuming a Bernoulli linking function.
+Additionally, the RSA model takes the speaker’s goal weights ω and intended presentational goal weight φ, which are inferred separately for each goal condition g.
+Finally, the RSA model uses two global free parameters: the cost of negation c and the speaker’s rationality parameter α.
 

### 2020-04-13 paper/supplementary_material.Rmd
begin fleshing out model math

@@
 
+$$
+P_{L}(r \mid u)\propto P_{S}(u \mid r) \cdot P(r \mid \rho_i) \\ 
+P_{S}(u \mid r)\propto Informativity(u;r)^{\alpha_i} \\
+Informativity(u; r) = P(r|u) \propto P(r \mid \rho_i) \cdot \mathcal{L}(u \mid \theta_{ij})
+$$
+
 Our model describes a listener jointly reasoning about the referent of a speaker's utterance and trying to learn a lexicon (object--word mappings).
@@
 
-The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their literal semantics, would infer upon hearing the utterance.
+The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.
 Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows.
-We assume that a listener's knowledge of a word's semantics is graded (not categorical).
-That is, for each object involved there is a probability $p$ that the literal listener knows the word for it.
-For each of the novel objects, this semantic knowledge is 0, which assumes that the novel word is equaliy likely to refer to the novel object as it is to refer to the familiar object.
-For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the kind of object (its expected acquisition trajectory) as well as on the child's age.
+We parameterize the  listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1.
+$\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene.
+Each of the novel objects are assumed to have semantic knowledge of 0.
+For $\theta \in (0, 1)$, the semantic interpretation function will pick out the familiar referent with probability $\theta + \frac{1 - \theta}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with  probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.
+For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the kind of object $j$ (its expected acquisition trajectory) as well as on the child's age $i$.
 
@@
 
-\begin{equation} 
-to be adjusted .... P_{L_1}(r, \mathcal{L}|u) = \phi P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)
-\end{equation}
+<!-- \begin{equation}  -->
+$$P^{mixture}_{L_1}(r, \mathcal{L}|u) = \phi \cdot P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)$$
+<!-- \end{equation}  -->
 

### 2020-04-13 paper/supplementary_material.Rmd
tweak math

@@
 
-Our model describes a listener jointly reasoning about the referent of a speaker's utterance and trying to learn a lexicon (object--word mappings).
-This reasoning is contextualized by the prior probability of each referent.
-This prior probability is thought to be a function of the common ground shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later.
-We assume that the degree to which interactions around objects are integrated into the common ground and thus change the prior probability of those objects depends on the child's age.
+Our model describes a listener reasoning about the referent referred to by a speaker's utterance.
+This reasoning is contextualized by the prior probability of each referent $P(r \mid \rho_i)$ .
+This prior probability is thought to be a function of the common ground $\rho$ shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later.
+We assume that the degree to which interactions around objects are integrated into the common ground and thus change the prior probability of those objects depends on the child's age $i$.
 
@@
 However, this expectation of speaker informativeness may vary and is captured by the parameter $\alpha$.
-In particular, we take $\alpha$ to be a function of the child's age.
+In particular, we take $\alpha$ to be a function of the child's age $i$.
 

### 2020-04-14 paper/bda_fig.tex
update supplement working in comments from MH

@@
 X, used to predict the Combination Data from Expt.~3 $d^{CM}$ for each unique age bin $i$, lexical item $j$, and alignment condition $k$.
-This RSA model takes as input a speaker optimality parameter $\alpha_i$ (which varies by age), a semantic knowledge parameter $\theta_{ij}$, and a common ground sensitivity $\rho_i$ (which varies by age).
+This RSA model takes as input a speaker optimality parameter $\alpha_i$ (which varies by age), a semantic knowledge parameter $\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\rho_i$ (which varies by age).
 Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{ME}$; Expt.~1), via a related RSA model $L'_1$;  common ground sensitivity parameters $\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{CG}$; Expt.~2).

### 2020-04-14 paper/supplementary_material.Rmd
update supplement working in comments from MH

@@
 
+```{r bda, include = T, fig.align = "center", fig.cap = "tbd."}
+#knitr::include_graphics("../graphs/method_overview.png")
+```
+
 ## Loci of development
@@
 As a consequence, each familiar object has a unique developmental trajectory with respect to semantic knowledge.
-Technically, the object-specific parameters are estimated in the form of a hierarchical regression (mixed-effects) model; that is, each object's trajectory is estimated as a deviation from an overall trajectory of vocabulary development.
-This overall (vocabulary) trajectory represents the development of semantic knowledge that is independent of a particular familiar object--label pairing.
-
-(MH: This paragraph is opaque)
-Semantic knowledge enters the likelihood term of the model specified above.
-The likelihood depends not just on the parameter settings for semantic knowledge but also on the value of the parameter capturing expectations about speaker informativeness ($\alpha$ - see next section).
-As a consequence, these parameters are jointly estimated and co-vary with one another.
+Technically, the object-specific parameters ($\theta_{ij}$) are estimated in the form of a hierarchical regression (mixed-effects) model; that is, each object's trajectory is estimated as a deviation from an overall trajectory of vocabulary development.
+This overall (vocabulary) trajectory represents the development of semantic knowledge that is independent of a particular familiar object--label pairing (see Figure \@ref(fig:bda)).
 
@@
 @bohn_tessler_merrick_frank_2019; @frank2014inferring; @yoon2019role].
-As mentioned above, this parameter is jointly estimated with the parameters for semantic knowledge.
 
@@
 We restricted the slope to be positive because negative values for speaker informativeness are conceptually implausible.
-For semantic knowledge we used $unif(-3,3)$ for the intercept and $unif(0,2)$ for the slope, again because negative values of semantic knowledge have no meaningful interpretation.
+For semantic knowledge we used $unif(-3,3)$ for the intercept and $unif(0,2)$ for the slope, because it is implausible to assume that semantic knowledge decreases with age.
 For the parameter capturing the variability the object specific trajectories around these overall parameters we used $unif(0,2)$ for the intercept and $unif(0,1)$ for the slope.
@@
 We used the data from Experiment 1 to then infer the parameters.
-That is, we inferred the intercepts and slopes for speaker informativeness and semantic knowledge that  generated RSA model predictions to match the responses generated in Experiment 1.
+That is, we inferred the intercepts and slopes for speaker informativeness (linear regression) and semantic knowledge (logistic regression) that generated RSA model predictions to match the responses generated in Experiment 1.
 To estimate the parameters representing sensitivity to common ground, we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in Experiment 2.
@@
 The first lesionsed model takes in speaker informativeness and common ground sensitivity as well as general semantic knowledge, but omits semantic knowledge that is specific to the familiar objects.
-We described above that the parameters for semantic knowledge are fitted via a hiearchical regression (mixed effects) model.
+We described above that the parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model.
 In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects).
@@
 This model takes in object specific semantic knowledge and speaker informativeness but ignores common ground.
-Thus, the prior distribution over objects $P(r)$ in the model described above is uniform (e.g., [0.5, 0.5]).
+Thus, the prior distribution over objects in the model described above is uniform (e.g., [0.5, 0.5]).
 This corresponds to a listener who only focuses on the mutual exclusivity inference and ignores the common ground manipulation.
@@
 This corresponds to a listener who only focuses on common ground and ignores the identity of the objects on the tables as well as any inferences their semantic knowledge of the familiar objects license.
-The model predictions therefore correspond to the prior distribution over objects $P(r)$.
+The model predictions therefore correspond to the prior distribution over objects $P(r \mid \rho_i)$.
 
@@
 The results shows a very high correlation between the predictions of the *integration model* and the data in all age groups suggesting that the model accurately captures the variation in the data.
+Correlations for the *integration model* were also higher compared to the other models considered.
 The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds.
-The mis-match for the oldest age group is probably a consequence of the model making very extreme predictions for this group.
-[MH: Do we know why the model makes extreme predictions for the older age?
-Is it because they are at ceiling on the ME and/or common ground task, and our model posits no integration cost?] Correlations for the *integration model* were also higher compared to the other models considered.
+The mis-match for the oldest age group is probably a consequence of the model making very extreme predictions in the congruent condition.
+This results from the fact that 4-year-olds show very high performance in the mututal exclusivity as well as the common ground task.
+When combined in the model, the two inferences amplify one another because we do not assume that there is any cost of integration.
+We made this choice because the parameter representing integration cost would have to be estimated based on the integration data itslef.
 
 We additionally compared models based on the marginal likelihood of the data under each model -- the likelihood of the data averaging over ("marginalizing over") the prior distribution on parameters; the pair-wise ratio of marginal likelihoods for two models is known as the Bayes Factor (see file `model_comparison.Rmd` in the associated online repository).
-Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by their prior probability); by averaging over the prior distribution on parameters, Bayes Factor implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the possible better predictions that a model with more parameters can achieve (CITE: Lee & Wagenmakers 2014 Bayesian Cognitive Modeling).
+Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by their prior probability); by averaging over the prior distribution on parameters, Bayes Factor implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the possible better predictions that a model with more parameters can achieve [@lee2014bayesian].
 For this analysis, we treated age continuously.
@@
 
-The *integration* and *mixture* models have different implications for developmental change.
+The *integration* and *mixture* models have potentially different implications for developmental change.
 The *integration model* assumes that the process by which information is integrated remains constant across development.
 What changes is children's semantic knowledge, their expectations about speaker informativeness, and their sensitivity to common ground, but the way these information sources are combined remains the same across age.
-The *mixture model* alternatively posits that there is some bias or preference for one information source, and this bias could across development.
+The *mixture model* alternatively posits that there is some bias or preference for one information source, and this bias could change across development.
 This *developmental mixture model*  makes the same assumptions about developmental change in the individual information sources as the *integration model* but, in addition, assumes that the way that the the mutual exclusivity and the common ground inference are combined with one another changes over time.
-This model is structurally identical to the *mixture model* but the mixture parameter $\phi$ is a function of age.
+This model is structurally identical to the *mixture model* but the mixture parameter $\phi$ is a function of age (i.e.
+represented by an intercept and a slope).
 
@@
 In contrast, the intercept for common ground sensitivity is estimated to be larger and the slope shallower after taking into account Experiment 3 data.
-That is, our best guess for common ground sensitivity after taking into account the data from Experiment 3 is that children overall are more sensitive to the common ground manipulation and there is less developmental change.
+That is, our best guess for common ground sensitivity after taking into account the data from Experiment 3 is that younger children are more sensitive to the common ground manipulation and there is less developmental change.
 The code to run the model can be found in the associated online repository (file: xxxxxxx).
@@
 
-Perhaps unsurprisingly, we see that updating the parameters for semantic knowledge, speaker informativeness and common ground sensitivity greatly improves the model fit (comparison: integration (explanation) vs integration (prediction)).
+Perhaps unsurprisingly, we see that further constraining the parameters for semantic knowledge, speaker informativeness and common ground sensitivity by the data from experiment 3 greatly improves the model fit (comparison: integration (explanation) vs integration (prediction)).
 We also see that the explanation *integration model* provides, by far, the best fit to the data compared to the two *mixture models*.
-Interestingly, the prediction *integration model* also had a better fit, even though its parameters were not updated based on the data from experiment 3.
+Interestingly, the prediction *integration model* also had a better fit, even though its parameters were not constrained by the data from experiment 3.
 When comparing the two *mixture models* directly, we see that an age sensitive mixture parameter did not result in a substantially better fit.
 
-This analysis shows that the inference and integration process described by the *ingetration model* accurately captures the data and also explains the integration process better compared to the additive *mixture models*.
+This analysis shows that the inference and integration processes described by the *ingetration model* accurately capture the data and also explain information integration better compared to the additive *mixture models*.
 As a consequence, we may say that instead of being biased towards one type of inference, children are rationally integrating all the information sources available.
@@
 We found a very close alignment of the model predictions and the data across the entire age range.
-Furthermore, the *integration model* provided a better fit to the data compared to a number of lesion models, which selectively omitted one type of information.
+Furthermore, the *integration model* provided a better fit to the data compared to a number of lesioned models, which selectively omitted one type of information.
 This suggests that children flexibly integrate all available information.
@@
 We found that the *integration model* better explained the data compared to these alternative model.
-In sum, we found that children's integration of semantic and pragmatic information during word learning is best described as a form of rational social inference.
+In sum, we found that children's integration of semantic and pragmatic information during word learning is best described as a form of Bayesian social inference.
 

### 2020-04-14 paper/supplementary_material.Rmd
add reference to model files to supplement

@@
 All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
-The corresponding model code can be found in the associated online repository (file xxxxx).
+The corresponding model code can be found in the associated online repository (file `webppl/prediction_model.wppl`).
 To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned.
@@
 That is, our best guess for common ground sensitivity after taking into account the data from Experiment 3 is that younger children are more sensitive to the common ground manipulation and there is less developmental change.
-The code to run the model can be found in the associated online repository (file: xxxxxxx).
+The code to run the model can be found in the associated online repository (file: `webppl/explanation_integration_model.wppl`).
 Figure \@ref(fig:fig9) shows model predictions for the *integration model* in comparison to the data from experiment 3.
@@
 To estimate $\phi$ as well as the other parameters, we make use of all the available data.
-The model code can be found in the associated online repository (file: xxxxxxx).
+The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`).
 The posterior distribution for the mixture parameter $\phi$ is shown in figure \@ref(fig:fig10)A.
@@
 For this model, we make the mixture parameter $\phi$ a function of age and estimate the intercept and slope that yield the best model predictions compared to the data from experiment 3.
+The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`).
 Figure \@ref(fig:fig10)B visualizes the developmental trajectory of the mixture parameter.

### 2020-04-16 paper/supplementary_material.Rmd
edits to model parameters sections, add regression math

@@
 Our model describes a listener reasoning about the referent referred to by a speaker's utterance.
-This reasoning is contextualized by the prior probability of each referent $P(r \mid \rho_i)$ .
-This prior probability is thought to be a function of the common ground $\rho$ shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later.
-We assume that the degree to which interactions around objects are integrated into the common ground and thus change the prior probability of those objects depends on the child's age $i$.
+This reasoning is contextualized by the prior probability of each referent $P(r \mid \rho_i)$.
+This prior probability is a function of the common ground $\rho$ shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later.
+We assume that the degree to which interactions around objects are integrated into the common ground (and thus change the prior probability of those objects) depends on the child's age $i$.
 
@@
 $\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene.
-Each of the novel objects are assumed to have semantic knowledge of 0.
-For $\theta \in (0, 1)$, the semantic interpretation function will pick out the familiar referent with probability $\theta + \frac{1 - \theta}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with  probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.
-For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the kind of object $j$ (its expected acquisition trajectory) as well as on the child's age $i$.
+Each of the novel words are assumed to have semantic knowledge of 0.
+For $\theta \in (0, 1)$, the semantic interpretation function will select the familiar referent with probability $\theta + (1 - \theta)\frac{1}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.^[
+  One could also define $\theta$ to directly denote the probability of selecting the familiar~vs.~unfamiliar referent.
+The model behavior would be the same except for a translation of this parameter.
+We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete uncertainty.
+] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.
 
@@
 Each of theses components is represented by a parameter that plays a particular functional role in the model.
-We capture developmental change by making these parameters a function of age and therefore estimating a developmental trajectory (intercept and slope) for each parameter.
+We capture developmental change by making these parameters a function of age $i$ for which we estimate a developmental trajectory (intercept and slope in a (logistic-) linear model) for each parameter.
 
@@
 Semantic knowledge captures the degree of certainty with which the naive listener is assumed to know the label for the familiar object.
-As a consequence, semantic knowledge differs between familiar objects.
-For objects whose labels are generally acquired earlier (e.g.
-carrot) semantic knowledge should generally be high whereas for others (e.g.
-pawn) semantic knowledge should generally be lower.
+As a consequence, semantic knowledge differs among familiar words.
+For objects whose labels are generally acquired earlier (e.g., "carrot") semantic knowledge should generally be high whereas for others (e.g., "pawn") semantic knowledge should generally be lower.
 However, semantic knowledge also varies with age such that older children are more likely to know the labels for more of the familiar objects compared to younger children.
-As a consequence, each familiar object has a unique developmental trajectory with respect to semantic knowledge.
-Technically, the object-specific parameters ($\theta_{ij}$) are estimated in the form of a hierarchical regression (mixed-effects) model; that is, each object's trajectory is estimated as a deviation from an overall trajectory of vocabulary development.
-This overall (vocabulary) trajectory represents the development of semantic knowledge that is independent of a particular familiar object--label pairing (see Figure \@ref(fig:bda)).
+As a consequence, each familiar word has a unique developmental semantic knowledge trajectory.
+
+Technically, the item-specific parameters ($\theta_{ij}$) are estimated in the form of a hierarchical regression (mixed-effects) model: $\theta_{ij} = \text{logistic}(\beta^{\theta}_{0, j} + i \cdot \beta^{\theta}_{1, j})$; each word's lexical development trajectory (the intercept $\beta^{\theta}_{0, j}$  and slope $\beta^{\theta}_{1, j}$ of the regression line for each object) is estimated as a deviation from an overall trajectory of vocabulary development.
+The intercept and slope for each item are sampled from Gaussian distributions with means $\mu^\theta_0, \mu^\theta_1$ and variances $\sigma^\theta_0, \sigma^\theta_1$: $\beta^{\theta}_{0, j} \sim \mathcal{N}(\mu^\theta_0, \sigma^\theta_0)$ and $\beta^{\theta}_{1, j} \sim \mathcal{N}(\mu^\theta_1, \sigma^\theta_1)$.
+$\mu^\theta_0$ and $\mu^\theta_1$ represent the overall vocabulary development independent of particular familiar object--label pairings, and $\sigma^\theta_0$ and $\sigma^\theta_1$ represent the overall variability of intercepts and of slopes between items (see Figure \@ref(fig:bda)).
+For all regression components, intercepts correspond to the knowledge or sensitivity for our youngest age bin: 2-year-olds.
+For example, $\mu^\theta_0$ represents the average semantic knowledge of our 2-year-olds and $\mu^\theta_1$ represents the growth in semantic knowledge over developmental time.
+$\sigma^\theta_0$ represents the variability in the semantic knowledge of our items (for the 2-year-olds) and $\sigma^\theta_1$ represents the variability in growth of semantic knowledge across our different items.
 
@@
 
-A second locus of developmental change is a listener's expectations about speaker informativeness.
+A second locus of developmental change is a listener's expectations about speaker informativeness $\alpha$.
 In the context of the model, speaker informativeness corresponds to the degree with which the listener expects the speaker to choose the most informative of the available utterances.
 We assume that children at different ages could have different expectations about how rational or informative speakers are [see e.g.
-@bohn_tessler_merrick_frank_2019; @frank2014inferring; @yoon2019role].
+@bohn_tessler_merrick_frank_2019; @frank2014inferring; @yoon2019role], which we model with a linear function: $\alpha_i = \beta^\alpha_0 + i \cdot \beta^\alpha_1$.
 
@@
 
-Sensitivity to common ground refers to the probability that an object is taken to be the referent of the utterance before actually hearing the utterance.
+Sensitivity to common ground $\rho$ refers to the probability that an object is taken to be the referent of the utterance before actually hearing the utterance.
 Thus, it captures the salience of an object due to its role in the social interaction that precedes the utterance.
-We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [akhtar1996role; @diesendruck2004two].
+We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [akhtar1996role; @diesendruck2004two], which we model with a logistic-linear function: $\rho_i = \text{logistic}(\beta^\rho_0 + i \cdot \beta^\rho_1)$.
 
@@
 We used the following prior distributions for model parameters.
-Intercept and slope for sensitivity to common ground: $unif(-2,2)$.
-For the speaker informativeness we used $unif(-3,3)$ for the intercept $unif(-0,4)$ for the slope.
-We restricted the slope to be positive because negative values for speaker informativeness are conceptually implausible.
-For semantic knowledge we used $unif(-3,3)$ for the intercept and $unif(0,2)$ for the slope, because it is implausible to assume that semantic knowledge decreases with age.
-For the parameter capturing the variability the object specific trajectories around these overall parameters we used $unif(0,2)$ for the intercept and $unif(0,1)$ for the slope.
+Intercept and slope for sensitivity to common ground: $\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$.
+Speaker informativeness:  $\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ for the intercept and $\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ for the slope.
+We restricted the slope to be positive because negative values for speaker informativeness are conceptually implausible: We do not expect sensitivity to speaker informativeness to decrease across our age range.
+For the global semantic knowledge (vocabulary) parameters, we used $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ for the intercept and $\mu^\theta_1 \sim \text{Uniform}(0,2)$ for the slope, because it is implausible to assume that semantic knowledge decreases with age.
+For the parameters capturing the variability the object specific trajectories around these overall parameters we used $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ for the intercept and $\sigma^\theta_1 \sim \text{Uniform}(0,1)$ for the slope.
 Some choices regarding these prior distributions were made to ease model convergence.

### 2020-04-16 paper/supplementary_material.Rmd
further details of functional form of rsa components

@@
 P_{S}(u \mid r)\propto Informativity(u;r)^{\alpha_i} \\
-Informativity(u; r) = P(r|u) \propto P(r \mid \rho_i) \cdot \mathcal{L}(u \mid \theta_{ij})
+Informativity(u; r) = P(r|u) \propto \mathcal{L}(u \mid \theta_{ij})
 $$
@@
 
-The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.
-Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows.
+The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
+  Following @Frank2014, we use an implicit uniform prior over referents in the literal listener.
+] Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows.
 We parameterize the  listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1.
@@
 
-Sensitivity to common ground $\rho$ refers to the probability that an object is taken to be the referent of the utterance before actually hearing the utterance.
-Thus, it captures the salience of an object due to its role in the social interaction that precedes the utterance.
+Sensitivity to common ground $\rho$ refers to the probability that an object is taken to be the referent of the utterance, before actually hearing the utterance.
+In our paradigm, common ground takes the form of *discourse novelty*, and $\rho$ captures the salience (or lack thereof) of an object due to its presence or absence in the social interaction that precedes the utterance.
+Specifically, the pragmatic listener uses the common ground parameter $\rho$ as the prior probability of the discourse-novel (i.e., the referent that was absent in the social interaction that preceded the utterance): In the *congruent* condition, the object in the prior social interaction (i.e., the discourse-familiar object) was the familiar object, and hence, both common ground (discourse novelty) and mutual exclusivity are cues to the same referent; in the *incongruent* condition, the object in the prior social interaction was the novel object, and hence, common ground (discourse-novelty) and mutual exclusitivity are cues to different referents.
 We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [akhtar1996role; @diesendruck2004two], which we model with a logistic-linear function: $\rho_i = \text{logistic}(\beta^\rho_0 + i \cdot \beta^\rho_1)$.
@@
 The following model comparison therefore asks which types of information are necessary to make good predictions about how information is integrated.
+All models used age-specific parameters when the parameter was present.
 We do not compare models that make different assumptions about how information is integrated, since they require additional parameters specific to Experiment 3.
@@
 That is, it takes in object-specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above.
-Figure \@ref(fig:fig5) visualizes the corresponding model predictions in comparison to the data from experiment 3.
+Figure \@ref(fig:fig5) visualizes the corresponding model predictions in comparison to the data from Experiment 3.
 
@@
 
-The first lesionsed model takes in speaker informativeness and common ground sensitivity as well as general semantic knowledge, but omits semantic knowledge that is specific to the familiar objects.
+The first lesioned model takes in speaker informativeness and common ground sensitivity as well as general semantic knowledge (vocabulary development), but omits semantic knowledge that is specific to the familiar objects.
 We described above that the parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model.
 In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects).
-The *no word knowledge* model takes in the overall trajectory for semantic knowledge but ignores object-specific variation.
+The *no word knowledge* model takes in the overall trajectory for semantic knowledge---represented by $\mu^\theta_0$ and $\mu^\theta_1$---but ignores object-specific variation.
+Formally, the semantic knowledge for each item is the same: $\theta_{ij} = \mu^\theta_0 +  i \cdot \mu^\theta_1$.
 That is, the model assumes a listener whose mutual exclusivity inference does not vary depending on the particular familiar object but only depends on the average semantic knowledge.
@@
 
-This model takes in object specific semantic knowledge and speaker informativeness but ignores common ground.
+This model takes in object specific semantic knowledge and speaker informativeness but ignores common ground $\rho_i$.
 Thus, the prior distribution over objects in the model described above is uniform (e.g., [0.5, 0.5]).

### 2020-04-16 paper/bda_fig.tex
switch rsa params to be deterministic outputs for regression params

@@
 	% COMMON GROUND
-	\node[latent, above=of data_cg, yshift=0.1cm](rho){$\rho_i$};
+	\node[det, above=of data_cg, yshift=0.1cm](rho){$\rho_i$};
 	\node[latent, right=of rho, yshift=0.5cm](beta_rho_int){$\beta^{\rho}_0$};
@@
 
-	\node[latent, left=of RSA, xshift=-1cm](alpha){$\alpha_i$};
+	\node[det, left=of RSA, xshift=-1cm](alpha){$\alpha_i$};
 	\node[latent, left=of alpha, yshift=0.5cm](beta_alpha_int){$\beta^{\alpha}_0$};
@@
 
-	\node[latent, above=of RSA, yshift=-0.25cm](theta){$\theta_{ij}$};
+	\node[det, above=of RSA, yshift=-0.25cm](theta){$\theta_{ij}$};
 	\node[latent, above=of theta, xshift=-1.25cm, yshift=-0.5cm](beta_theta_int){$\beta^{\theta}_{0, j}$};
@@
 $L_1$ represents the RSA model defined by Eq.
-X, used to predict the Combination Data from Expt.~3 $d^{CM}$ for each unique age bin $i$, lexical item $j$, and alignment condition $k$.
+X, used to predict the Combination Data $d^{CM}$  from Expt.~3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$.
 This RSA model takes as input a speaker optimality parameter $\alpha_i$ (which varies by age), a semantic knowledge parameter $\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\rho_i$ (which varies by age).
-Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{ME}$; Expt.~1), via a related RSA model $L'_1$;  common ground sensitivity parameters $\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{CG}$; Expt.~2).
+Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{ME}$; Expt.~1), via the same RSA model with no common ground $L'_1$;  common ground sensitivity parameters $\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{CG}$; Expt.~2).
   Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\beta_0$ and $\beta_1$, respectively).

### 2020-04-17 paper/supplementary_material.Rmd
reorganize repo and add bda figure to supplement

@@
 As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning.
-In experiment 1, we show that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge.
+In Experiment 1, we show that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge.
 In a second experiment, we show that children make inferences about word meanings based on common ground.
@@
 As a part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground.
-We then use the our modelling framework to ask which of these information sources are necessary to predict children's responses in experiment 3.
+We then use the our modelling framework to ask which of these information sources are necessary to predict children's responses in Experiment 3.
 
@@
 
-The experiment was preregistered at https://osf.io/gy37b. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_me.html`.
+The experiment was preregistered at https://osf.io/gy37b. The experiment itself can be run by downloading the associated repository and opening the file `experiments/ex1_me.html`.
 
@@
 
-In experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study).
+In Experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study).
 The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?".
@@
 plot_aoa_ratings <- aoa_ratings%>%
-  mutate(image = paste("../experiments/kids/images/",item,".png", sep=""))
+  mutate(image = paste("../experiments/images/",item,".png", sep=""))
 
@@
 
-knitr::kable(me_comp, caption = "Model comparison in experiment 1 based on WAIC scores and weights.", digits = 2, align = "l")
+knitr::kable(me_comp, caption = "Model comparison in Experiment 1 based on WAIC scores and weights.", digits = 2, align = "l")
 ```
@@
 
-The experiment was preregistered at https://osf.io/au5hr. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_novel.html`.
+The experiment was preregistered at https://osf.io/au5hr. The experiment itself can be run by downloading the associated repository and opening the file `experiments/ex2_novel.html`.
 
@@
 
-## Experiment 3: Integration
+## Experiment 3: Combination
 
@@
 
-The experiment was preregistered at https://osf.io/4nm8g. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_combination.html`.
+The experiment was preregistered at https://osf.io/4nm8g. The experiment itself can be run by downloading the associated repository and opening the file `experiments/ex3_combination.html`.
 
@@
 We pre-registered to include item as a fixed effect in Experiment 3.
-The corresponding model was too complex to be constrained by the data.
-Furthermore, as explained in Experiment 1, items were chosen based on their rated age of acquisition.
+However, we chose to model it as a random effect instead because, as explained in Experiment 1, items were chosen based on their rated age of acquisition.
 That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge.
@@
 The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`).
-The incongruent condition had a strong negative impact (*$\beta$* = `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q97.5)%>%round(2)`), showing that children differentiated between the two conditions.
+The incongruent condition had a strong negative impact (*$\beta$* = `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q97.5)%>%round(2)`), showing that children showed a weaker mutual exclusivity inference when common ground information pointed to the other object as the referent.
+Thus, children differentiated between the two alignment conditions.
 The interaction term was weakly - though not entirely - negative, suggesting a shallower slope for age in the incongruent condition (*$\beta$* = `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q97.5)%>%round(2)`).
@@
 
-knitr::kable(comb_comp, caption = "Model comparison in experiment 3 based on WAIC scores and weights.", digits = 2, align = "l")
+knitr::kable(comb_comp, caption = "Model comparison in Experiment 3 based on WAIC scores and weights.", digits = 2, align = "l")
 ```
@@
 Experiment 1 showed that children of all age groups make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented.
-Experiment 2 showed that children are sensitive the common ground manipulation we implemented and that this inference increases with age.
-Finally, experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another.
+Experiment 2 showed that children are sensitive to the common ground manipulation we implemented and that this inference increases with age.
+Finally, Experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another.
 In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when inferences are combined with one another.
@@
 To do so, we use Bayesian cognitive models of pragmatic reasoning.
-We first describe an *integration model* which we think best represents the inference and integration processes and then specify how this model captures developmental change.
+We first describe an **integration model** which we think best represents the inference and integration processes and then specify how this model captures developmental change.
 Next, we ask how well this model *predicts* how children integrate information.
-That is, in a situation in which we know the development trajectories for the mutual exclusivity inference (for a particualr familiar object) as well as for the common ground inference, what can we say about what happens when they are combined.
-We then test the predictive power of the model by comparing the model predictions to the data from experiment 3.
-We use formal model comparison methods to test the *integration model* against a range of alternative models.
+That is, in a situation in which we know the development trajectories for the mutual exclusivity inference (for a particular familiar object) as well as the common ground inference, what can we say about what happens when they are combined.
+We then test the predictive power of the model by comparing the model predictions to the data from Experiment 3.
+We use formal model comparison methods to test the **integration model** against a range of alternative models.
 
 Finally, we ask how well our model *explains* the way that children integrate the different information sources.
-For this analysis, we fit the free parameters in the model to all the available data, those from experiment 1 and 2 as well as the integration data from experiment 3.
+For this analysis, we fit the free parameters in the model to all the available data, those from Experiment 1 and 2 as well as the integration data from Experiment 3.
 We then compare the model to a range of alternative models that make different assumptions about how information is integrated and how this process develops.
@@
 
-Our model describes a listener reasoning about the referent referred to by a speaker's utterance.
+Our model describes a listener ($P_L$) reasoning about the referent referred to by a speaker's ($P_S$) utterance.
 This reasoning is contextualized by the prior probability of each referent $P(r \mid \rho_i)$.
@@
 The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
-  Following @Frank2014, we use an implicit uniform prior over referents in the literal listener.
+  Following @frank2014inferring, we use an implicit uniform prior over referents in the literal listener.
 ] Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows.
@@
 
-```{r bda, include = T, fig.align = "center", fig.cap = "tbd."}
-#knitr::include_graphics("../graphs/method_overview.png")
-```
-
 ## Loci of development
@@
 Each of theses components is represented by a parameter that plays a particular functional role in the model.
-We capture developmental change by making these parameters a function of age $i$ for which we estimate a developmental trajectory (intercept and slope in a (logistic-) linear model) for each parameter.
+We capture developmental change by making these parameters a function of age $i$ for which we estimate a developmental trajectory (intercept and slope in a (logistic-) linear model, see Figure \@ref(fig:bda)).
 
@@
 The intercept and slope for each item are sampled from Gaussian distributions with means $\mu^\theta_0, \mu^\theta_1$ and variances $\sigma^\theta_0, \sigma^\theta_1$: $\beta^{\theta}_{0, j} \sim \mathcal{N}(\mu^\theta_0, \sigma^\theta_0)$ and $\beta^{\theta}_{1, j} \sim \mathcal{N}(\mu^\theta_1, \sigma^\theta_1)$.
-$\mu^\theta_0$ and $\mu^\theta_1$ represent the overall vocabulary development independent of particular familiar object--label pairings, and $\sigma^\theta_0$ and $\sigma^\theta_1$ represent the overall variability of intercepts and of slopes between items (see Figure \@ref(fig:bda)).
-For all regression components, intercepts correspond to the knowledge or sensitivity for our youngest age bin: 2-year-olds.
-For example, $\mu^\theta_0$ represents the average semantic knowledge of our 2-year-olds and $\mu^\theta_1$ represents the growth in semantic knowledge over developmental time.
-$\sigma^\theta_0$ represents the variability in the semantic knowledge of our items (for the 2-year-olds) and $\sigma^\theta_1$ represents the variability in growth of semantic knowledge across our different items.
+$\mu^\theta_0$ and $\mu^\theta_1$ represent the overall vocabulary development independent of particular familiar word--object pairings, and $\sigma^\theta_0$ and $\sigma^\theta_1$ represent the overall variability of intercepts and of slopes between items (see Figure \@ref(fig:bda)).
+For all regression components, intercepts correspond to the knowledge or sensitivity for our youngest children: 2-year-olds (2.00 years of age).
+For example, $\mu^\theta_0$ represents the average semantic knowledge of a 2-year-old and $\mu^\theta_1$ represents the growth in semantic knowledge over developmental time.
+$\sigma^\theta_0$ represents the variability in the semantic knowledge of our items (for a 2-year-old) and $\sigma^\theta_1$ represents the variability in growth of semantic knowledge across our different items.
 
@@
 Sensitivity to common ground $\rho$ refers to the probability that an object is taken to be the referent of the utterance, before actually hearing the utterance.
-In our paradigm, common ground takes the form of *discourse novelty*, and $\rho$ captures the salience (or lack thereof) of an object due to its presence or absence in the social interaction that precedes the utterance.
-Specifically, the pragmatic listener uses the common ground parameter $\rho$ as the prior probability of the discourse-novel (i.e., the referent that was absent in the social interaction that preceded the utterance): In the *congruent* condition, the object in the prior social interaction (i.e., the discourse-familiar object) was the familiar object, and hence, both common ground (discourse novelty) and mutual exclusivity are cues to the same referent; in the *incongruent* condition, the object in the prior social interaction was the novel object, and hence, common ground (discourse-novelty) and mutual exclusitivity are cues to different referents.
-We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [akhtar1996role; @diesendruck2004two], which we model with a logistic-linear function: $\rho_i = \text{logistic}(\beta^\rho_0 + i \cdot \beta^\rho_1)$.
+In our paradigm, common ground takes the form of *discourse novelty*, and $\rho$ captures the salience (or lack thereof) of an object due to its presence or absence in the social interaction that precedes the utterance (see \@ref(fig:fig1)B).
+Specifically, the pragmatic listener uses the common ground parameter $\rho$ as the prior probability of the discourse-novel (i.e., the referent that was absent in the social interaction that preceded the utterance): In the *congruent* condition, the object in the prior social interaction (i.e., the discourse-familiar object) was the familiar object, and hence, both common ground (discourse novelty) and mutual exclusivity are cues to the same referent; in the *incongruent* condition, the object in the prior social interaction was the novel object, and hence, common ground (discourse-novelty) and mutual exclusitivity are cues to different referents (see Figure \@ref(fig:fig1)C).
+We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [@akhtar1996role; @diesendruck2004two], which we model with a logistic-linear function: $\rho_i = \text{logistic}(\beta^\rho_0 + i \cdot \beta^\rho_1)$.
+
+```{r bda, engine='tikz', echo = F,fig.align = "center", fig.cap = "Graphical model representing the Bayesian data analysis for **integration model** used for *Explanation*.
+$L_1$ represents the RSA model defined by Eq.
+X, used to predict the Combination Data $d^{CM}$  from Expt.
+3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$.
+This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\\rho_i$ (which varies by age).
+Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{ME}$; Expt.
+1), via the same RSA model with no common ground $L'_1$;  common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{CG}$; Expt.
+2).
+Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\beta_0$ and $\\beta_1$, respectively).
+Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu$ and $sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}
+
+\usetikzlibrary{bayesnet}
+
+\begin{tikzpicture}
+%% RSA nodes and data
+\node[obs](data_comb){$d^{CM}_{ijk}$};
+\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{ME}_{ij}$};
+\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};
+
+\node[det, above=of data_me](L1_me){$L'_1$};
+\node[det, above=of data_comb](L1_comb){$L_1$};
+\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};
+
+\edge{L1_me}{data_me};
+\edge{L1_comb}{data_comb};
+\edge{RSA}{L1_me};
+\edge{RSA}{L1_comb};
+
+% COMMON GROUND
+\node[det, above=of data_cg, yshift=0.1cm](rho){$\rho_i$};
+\node[latent, right=of rho, yshift=0.5cm](beta_rho_int){$\beta^{\rho}_0$};
+\node[latent, right=of rho, yshift=-0.5cm](beta_rho_slope){$\beta^{\rho}_1$};
+
+\edge{rho}{data_cg};
+\edge{beta_rho_int}{rho};
+\edge{beta_rho_slope}{rho};
+\edge{rho}{L1_comb};
+
+%% SPEAKER INFORMATIVITY
+
+\node[det, left=of RSA, xshift=-1cm](alpha){$\alpha_i$};
+\node[latent, left=of alpha, yshift=0.5cm](beta_alpha_int){$\beta^{\alpha}_0$};
+\node[latent, left=of alpha, yshift=-0.5cm](beta_alpha_slope){$\beta^{\alpha}_1$};
+
+%	\edge{alpha}{L1_me};
+\edge{beta_alpha_int}{alpha};
+\edge{beta_alpha_slope}{alpha};
+\edge{alpha}{RSA};
+
+%% SEMANTIC KNOWLEDGE model
+
+	\node[det, above=of RSA, yshift=-0.25cm](theta){$\theta_{ij}$};
+\node[latent, above=of theta, xshift=-1.25cm, yshift=-0.5cm](beta_theta_int){$\beta^{\theta}_{0, j}$};
+\node[latent, above=of theta, xshift=1.25cm, yshift=-0.5cm](beta_theta_slope){$\beta^{\theta}_{1, j}$};
+
+\node[latent, above=of beta_theta_int, xshift=-0.5cm](mu_theta_int){$\mu^{\theta}_{0}$};
+\node[latent, above=of beta_theta_int, xshift=0.5cm](sigma_theta_int){$\sigma^{\theta}_{0}$};
+
+\node[latent, above=of beta_theta_slope, xshift=-0.5cm](mu_theta_slope){$\mu^{\theta}_{1}$};
+\node[latent, above=of beta_theta_slope, xshift=0.5cm](sigma_theta_slope){$\sigma^{\theta}_{1}$};
+
+\edge{theta}{RSA};
+%	\edge{theta}{L1_comb};
+\edge{beta_theta_int}{theta};
+\edge{beta_theta_slope}{theta};
+\edge{mu_theta_int}{beta_theta_int};
+\edge{sigma_theta_int}{beta_theta_int};
+\edge{mu_theta_slope}{beta_theta_slope};
+\edge{sigma_theta_slope}{beta_theta_slope};
+
+%	\plate{plate_data_me}{
+%		(data_me)
+%	}{$i \in \mathcal{P}_{1}$}
+
+%	\plate{plate_data_cg}{
+%		(data_cg)
+%	}{$i \in \mathcal{P}_{2}$}
+
+\plate{plate_condition}{(data_comb)(L1_comb)}{$k \in \text{alignments}$};
+
+	\plate{plate_items}{
+%		(plate_data_me)
+%		(plate_data_comb)
+%		(plate_condition)
+(plate_condition)
+	(data_comb)
+	(data_me)
+	(L1_me)
+	(L1_comb)
+	(theta)
+	(beta_theta_int)
+	(beta_theta_slope)
+}{$j \in \text{items}$}
+
+	\plate{plate_data_comb}{
+	(data_comb)
+	(data_cg)
+	(data_me)
+	(plate_condition)
+	(rho)
+	(theta)
+	(alpha)
+	(L1_me)
+	(L1_comb)
+%		(plate_items)
+	}{$i \in \text{2-to-4 year olds}$}
+
+\end{tikzpicture}
+
+```
 
@@
 The corresponding model code can be found in the associated online repository (file `webppl/prediction_model.wppl`).
-To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned.
-The resulting predictions come in the form of distributions of developmental trajectories for each object in the congruent and the incongruent condition.
+To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned (Figure \@ref(fig:bda)).
+The resulting predictions come in the form of distributions of developmental trajectories for each familiar object in the congruent and the incongruent condition.
 
@@
 In this section we evaluate different models in terms of how well they *predict* information integration.
-That is, in a situation in which we know the development of the mutual exclusivity inference as well as the common ground inference, we look at each model's ability to predict what happens when the two are combined (combination data from Experiment 3).
+That is, in a situation in which we know the development of the (object specific) mutual exclusivity inference as well as the common ground inference, we look at each model's ability to predict what happens when the two are combined (combination data from Experiment 3).
 Investigating "pure" (or, *a priori*) prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g., a heuristic, non-integrating mixture model, described below).
@@
 To estimate the parameters representing sensitivity to common ground, we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in Experiment 2.
+Figure \@ref(fig:bda) visualizes how parameters were estimated.
 
@@
 We excluded samples from one chain because it got stuck on a local maximum which resulted in parameter distributions that were substantially different from the other chains.
-The model outputs can be found in the following online repository: git large file storage.
+The model outputs can be found in the following online repository: XXXXXX.
 
@@
 Note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in terms of which parameters they included.
-The models described below are a full model (*integration model*) and three lesioned models, which selectively omit one type of information.
+The models described below are a full model (**integration model**) and three lesioned models, which selectively omit one type of information.
 The following model comparison therefore asks which types of information are necessary to make good predictions about how information is integrated.
@@
 
-The integration model serves as the full model and takes in all available information.
+The **integration model** serves as the full model and takes in all available information.
 That is, it takes in object-specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above.
@@
 In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects).
-The *no word knowledge* model takes in the overall trajectory for semantic knowledge---represented by $\mu^\theta_0$ and $\mu^\theta_1$---but ignores object-specific variation.
+The **no word knowledge model** takes in the overall trajectory for semantic knowledge---represented by $\mu^\theta_0$ and $\mu^\theta_1$---but ignores object-specific variation.
 Formally, the semantic knowledge for each item is the same: $\theta_{ij} = \mu^\theta_0 +  i \cdot \mu^\theta_1$.
@@
 
-The last lesion model only takes in the common ground sensitivity.
+The last lesioned model only takes in the common ground sensitivity.
 This corresponds to a listener who only focuses on common ground and ignores the identity of the objects on the tables as well as any inferences their semantic knowledge of the familiar objects license.
@@
 Figure \@ref(fig:fig6) visualizes the correlation between model predictions and the data for all models.
-The results shows a very high correlation between the predictions of the *integration model* and the data in all age groups suggesting that the model accurately captures the variation in the data.
-Correlations for the *integration model* were also higher compared to the other models considered.
+The results shows a very high correlation between the predictions of the **integration model** and the data in all age groups indicating that the model accurately captures the variation in the data.
+Correlations for the **integration model** were also higher compared to the other models considered.
 The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds.
@@
 When combined in the model, the two inferences amplify one another because we do not assume that there is any cost of integration.
-We made this choice because the parameter representing integration cost would have to be estimated based on the integration data itslef.
+We made this choice because the parameter representing integration cost would have to be estimated based on the integration data of Experiment 3 itslef.
 
@@
 Table \@ref(tab:table5) lists the Bayes factors for the different model comparisons.
-The results show that the *integration model*, by far, outperformed all the other models.
-When comparing the lesion models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the *no mutual exclusivity model*.
+The results show that the **integration model**, by far, outperformed all the other models.
+When comparing the lesioned models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the *no mutual exclusivity model*.
 
 Taken together, these analyses showed two things.
-First, the *integration model* makes accurate predictions about how mutual exclusivity and common ground inferences are integrated.
+First, the **integration model** makes accurate predictions about how mutual exclusivity and common ground inferences are integrated.
 It does so based on knowing the strength and development of each inference alone, and incorporating them into a structured probabilistic model of pragmatic reasoning.
@@
 This result exemplifies that children across the entire age range flexibly integrate all the available information.
-In the next section we ask whether there are other ways think about the process of information integration than the way formalized in the *integration model*.
+In the next section we ask whether there are other ways think about the process of information integration than the way formalized in the **integration model**.
 
@@
 We explore alternative ways to think about information integration.
-The *integration model* outlined above operates via Bayesian inference in that the prior probability of a referent (a consequence of the common ground manipulation) is updated via the likelihood of hearing the utterance heard from a speaker, which is used to derive the mutual exclusivity inference.
+The **integration model** outlined above operates via Bayesian inference in that the prior probability of a referent (a consequence of the common ground manipulation) is updated via the likelihood of hearing the utterance heard from a speaker, which is used to derive the mutual exclusivity inference.
 In essence, this model is a multiplicative model because the posterior probability of each referent given the utterance is proportional to the product of the likelihood of a speaker saying that utterance and the prior probability of that referent.
@@
 
-The *integration* and *mixture* models have potentially different implications for developmental change.
-The *integration model* assumes that the process by which information is integrated remains constant across development.
+The **integration** and **mixture** models have potentially different implications for developmental change.
+The **integration model** assumes that the process by which information is integrated remains constant across development.
 What changes is children's semantic knowledge, their expectations about speaker informativeness, and their sensitivity to common ground, but the way these information sources are combined remains the same across age.
-The *mixture model* alternatively posits that there is some bias or preference for one information source, and this bias could change across development.
-This *developmental mixture model*  makes the same assumptions about developmental change in the individual information sources as the *integration model* but, in addition, assumes that the way that the the mutual exclusivity and the common ground inference are combined with one another changes over time.
-This model is structurally identical to the *mixture model* but the mixture parameter $\phi$ is a function of age (i.e.
+The **mixture model** alternatively posits that there is some bias or preference for one information source, and this bias could change across development.
+This **developmental mixture model**  makes the same assumptions about developmental change in the individual information sources as the **integration model** but, in addition, assumes that the way that the mutual exclusivity and the common ground inference are combined with one another changes over time.
+This model is structurally identical to the **mixture model** but the mixture parameter $\phi$ is a function of age (i.e.
 represented by an intercept and a slope).
@@
 2).
-Now, in addition, we incorporate the data from Experiment 3 to additionally constrain these parameters as well as inform the mixture parameter for the mixture model.
+Now, in addition, we incorporate the data from Experiment 3 to additionally constrain these parameters as well as inform the mixture parameter for the mixture model (see Figure \@ref(fig:bda)).
 
@@
 
-The *integration model* in this section differs from the integration model in the **Prediction Section** only in that the parameter distributions are now additionally informed by the data from Experiment 3.
-Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the Appendix show how the parameter distributions differ between the prediction and the explanation version of the *integration* model.
-Semantic knowledge and speaker informativeness have similar posterior distributions when taking into account all the data compared to when estimating these parameters only based on experiment 1 and 2.
+The **integration model** in this section differs from the integration model in the [prediction section](#prediction) only in that the parameter distributions are now additionally informed by the data from Experiment 3.
+Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the Appendix show how the parameter distributions differ between the prediction and the explanation version of the **integration model**.
+Semantic knowledge and speaker informativeness have similar posterior distributions when taking into account all the data compared to when estimating these parameters only based on Experiment 1 and 2.
 In contrast, the intercept for common ground sensitivity is estimated to be larger and the slope shallower after taking into account Experiment 3 data.
@@
 The code to run the model can be found in the associated online repository (file: `webppl/explanation_integration_model.wppl`).
-Figure \@ref(fig:fig9) shows model predictions for the *integration model* in comparison to the data from experiment 3.
+Figure \@ref(fig:fig9) shows model predictions for the **integration model** in comparison to the data from Experiment 3.
 
@@
 
-In the *mixture model* the two inferences (common ground and mutual exclusivity) are computed in the same way as in in the *integration model*.
+In the **mixture model** the two inferences (common ground and mutual exclusivity) are computed in the same way as in in the **integration model**.
 Subsequently, they are weighted by the mixture parameter $\phi$:
@@
 
-For this model, we make the mixture parameter $\phi$ a function of age and estimate the intercept and slope that yield the best model predictions compared to the data from experiment 3.
+For this model, we make the mixture parameter $\phi$ a function of age and estimate the intercept and slope that yield the best model predictions compared to the data from Experiment 3.
 The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`).
@@
 Figure \@ref(fig:fig11) shows correlations between model predictions and the data, each binned by year and object.
-Even though model predictions and data are closely aligned for all models, the *integration model* shows the highest correlation in all age groups.
+Even though model predictions and data are closely aligned for all models, the **integration model** shows the highest correlation in all age groups.
 Next we directly compared models based using Bayes factors (see Table \@ref(tab:table6)).
-We also included the prediction *integration model* into this analysis.
-
-Perhaps unsurprisingly, we see that further constraining the parameters for semantic knowledge, speaker informativeness and common ground sensitivity by the data from experiment 3 greatly improves the model fit (comparison: integration (explanation) vs integration (prediction)).
-We also see that the explanation *integration model* provides, by far, the best fit to the data compared to the two *mixture models*.
-Interestingly, the prediction *integration model* also had a better fit, even though its parameters were not constrained by the data from experiment 3.
-When comparing the two *mixture models* directly, we see that an age sensitive mixture parameter did not result in a substantially better fit.
-
-This analysis shows that the inference and integration processes described by the *ingetration model* accurately capture the data and also explain information integration better compared to the additive *mixture models*.
+We also included the prediction **integration model** into this analysis.
+
+Perhaps unsurprisingly, we see that further constraining the parameters for semantic knowledge, speaker informativeness and common ground sensitivity by the data from Experiment 3 greatly improves the model fit (comparison: integration (explanation) vs integration (prediction)).
+We also see that the explanation **integration model** provides, by far, the best fit to the data compared to the two **mixture models**.
+Interestingly, the prediction **integration model** also had a better fit, even though its parameters were not constrained by the data from Experiment 3.
+When comparing the two **mixture models** directly, we see that an age sensitive mixture parameter did not result in a substantially better fit.
+
+This analysis shows that the inference and integration processes described by the **integration model** accurately capture the data and also explain information integration better compared to the additive **mixture models**.
 As a consequence, we may say that instead of being biased towards one type of inference, children are rationally integrating all the information sources available.
@@
 Here we studied how 2 to 5 year old children integrate semantic and pragmatic information during word learning.
-In three experiments, we first showed that children make a mutual exclusivity inference and that this inference varied depending on children's familiarity with the objects involved (experiment 1).
-Next, we showed that children make common ground inferences based on their interactions with a speaker (experiment 2).
-When the two inferences were combined, we found that children were sensitive to the way in which they were aligned (experiment 3).
-
-We then introduced a computational model to investigate the process by which children integrated the inferences in experiment 3.
+In three experiments, we first showed that children make a mutual exclusivity inference and that this inference varied depending on children's familiarity with the objects involved (Experiment 1).
+Next, we showed that children make common ground inferences based on their interactions with a speaker (Experiment 2).
+When the two inferences were combined, we found that children were sensitive to the way in which they were aligned (Experiment 3).
+
+We then introduced a computational model to investigate the process by which children integrated the inferences in Experiment 3.
 As a start, we described mutual exclusivity as a pragmatic inference, which takes in children's emerging semantic knowledge and their expectations about how informative a speaker is.
-The *integration model* assumes that this inference is then flexibly integrated with children's developing sensitivity to common ground.
+The **integration model** assumes that this inference is then flexibly integrated with children's developing sensitivity to common ground.
 
 Next, we tested the predictive power of this model.
-That is, we asked how well the model would predict the data of experiment 3, when only knowing the developmental trajectories for mutual exclusivity (based on experiment 1) and common ground (experiment 2).
+That is, we asked how well the model would predict the data of Experiment 3, when only knowing the developmental trajectories for mutual exclusivity (based on Experiment 1) and common ground (Experiment 2).
 We found a very close alignment of the model predictions and the data across the entire age range.
-Furthermore, the *integration model* provided a better fit to the data compared to a number of lesioned models, which selectively omitted one type of information.
+Furthermore, the **integration model** provided a better fit to the data compared to a number of lesioned models, which selectively omitted one type of information.
 This suggests that children flexibly integrate all available information.
@@
 In the final section, we studied which process best explained children's information integration.
-We compared the *integration model* to a *mixture model* which assumed that children are biased towards one type of inference.
-We found that the *integration model* better explained the data compared to these alternative model.
+We compared the **integration model** to a **mixture model** which assumed that children are biased towards one type of inference.
+We found that the **integration model** better explained the data compared to these alternative model.
 In sum, we found that children's integration of semantic and pragmatic information during word learning is best described as a form of Bayesian social inference.
@@
 In the following, we visualize the model parameters for semantic knowledge, speaker informativeness and common ground sensitivity.
-Please note that the alternative lesion models presented in the prediction section used the same parameter distributions as the prediction *integration model*.
+Please note that the alternative lesion models presented in the prediction section used the same parameter distributions as the prediction **integration model**.
 

### 2020-04-17 paper/supplementary_material.Rmd
add figure

@@
 ```{r fig1,echo = F, fig.align = "center", fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
-knitr::include_graphics("../graphs/method_overview.png")
+knitr::include_graphics("../figures/method_overview.png")
 ```

### 2020-04-17 paper/supplementary_material.Rmd
finish edits through supplement; add a fully parameterized version of rsa math

@@
 library(BayesFactor)
+library(pdftools)
 
@@
 P_{L}(r \mid u)\propto P_{S}(u \mid r) \cdot P(r \mid \rho_i) \\ 
-P_{S}(u \mid r)\propto Informativity(u;r)^{\alpha_i} \\
-Informativity(u; r) = P(r|u) \propto \mathcal{L}(u \mid \theta_{ij})
+P_{S}(u \mid r)\propto P(r\mid u) ^{\alpha_i} \\
+P(r\mid u) \propto \mathcal{L}(u, r \mid \theta_{ij})
 $$
@@
 ] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.
+
+The model with each data-analytic parameter represented explicitly in $\{, \}s$ is:
+
+$$
+P_{L}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) \\ 
+P_{S}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} \\
+P(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})
+$$
 
@@
 Figure \@ref(fig:fig5) visualizes the corresponding model predictions in comparison to the data from Experiment 3.
+
+We compare this model to three alternative, "lesioned" models that lack certain components of the full integration model.
 
@@
 
-The first lesioned model takes in speaker informativeness and common ground sensitivity as well as general semantic knowledge (vocabulary development), but omits semantic knowledge that is specific to the familiar objects.
+A marginally less-complex model than the full integration model uses the same model architecture, taking in speaker informativeness and common ground sensitivity, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge).
 We described above that the parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model.
@@
 
-This model takes in object specific semantic knowledge and speaker informativeness but ignores common ground $\rho_i$.
-Thus, the prior distribution over objects in the model described above is uniform (e.g., [0.5, 0.5]).
-This corresponds to a listener who only focuses on the mutual exclusivity inference and ignores the common ground manipulation.
+We consider a model that ignores common ground information, $\rho_i$.
+This model takes in object specific semantic knowledge and speaker informativeness butuses a prior distribution over objects that is constant across alignment conditions and uniform (e.g., [0.5, 0.5]).
+This model corresponds to a listener who only focuses on the mutual exclusivity inference and ignores the common ground manipulation.
 As a consequence, the listener does not differentiate between the two common ground alignment conditions.
@@
 
-The last lesioned model only takes in the common ground sensitivity.
-This corresponds to a listener who only focuses on common ground and ignores the identity of the objects on the tables as well as any inferences their semantic knowledge of the familiar objects license.
-The model predictions therefore correspond to the prior distribution over objects $P(r \mid \rho_i)$.
+Finally, we consider a model that focuses only on common ground information and ignores the identity of the objects on the tables as well as any inferences their semantic knowledge of the familiar objects license.
+The predictions of this model correspond to the prior distribution over objects $P(r \mid \rho_i)$.
 
@@
 We compared the models mentioned above in two ways.
-On the one hand, we used correlations between model predictions and the data.
-For this analysis, we binned the model predictions and the data by age in years and familiar object.
+First, we used correlations between model predictions and the data.
+For this analysis, we binned the model predictions and the data by age in years and by the type of familiar object.
 Figure \@ref(fig:fig6) visualizes the correlation between model predictions and the data for all models.
@@
 The mis-match for the oldest age group is probably a consequence of the model making very extreme predictions in the congruent condition.
-This results from the fact that 4-year-olds show very high performance in the mututal exclusivity as well as the common ground task.
-When combined in the model, the two inferences amplify one another because we do not assume that there is any cost of integration.
-We made this choice because the parameter representing integration cost would have to be estimated based on the integration data of Experiment 3 itslef.
+This results from the fact that 4-year-olds show very high performance both the mututal exclusivity and common ground tasks.
+When combined in the model, the two inferences amplify one another because we assume no cost of integration.
+We maintain no cost to integration because positing integration cost introduces a free parameter that could only be estimated based on the integration data of Experiment 3 itself (i.e., such a model would not make precise *a priori* predictions).
 
 We additionally compared models based on the marginal likelihood of the data under each model -- the likelihood of the data averaging over ("marginalizing over") the prior distribution on parameters; the pair-wise ratio of marginal likelihoods for two models is known as the Bayes Factor (see file `model_comparison.Rmd` in the associated online repository).
-Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by their prior probability); by averaging over the prior distribution on parameters, Bayes Factor implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the possible better predictions that a model with more parameters can achieve [@lee2014bayesian].
+Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by the prior probabilities of those parameter values); by averaging over the prior distribution on parameters, Bayes Factor implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the potential gains in predictive accuracy that a model with more parameters can achieve [@lee2014bayesian].
 For this analysis, we treated age continuously.
@@
 This result exemplifies that children across the entire age range flexibly integrate all the available information.
-In the next section we ask whether there are other ways think about the process of information integration than the way formalized in the **integration model**.
+In the next section we ask investigate alternative formulations of the process of information integration.
 
@@
 
-In this section we explore how we can best explain information integration across development.
+In this section we explore how to best explain information integration across development.
 We explore alternative ways to think about information integration.
@@
 
-Information sources need not be integrated in a Bayesian manner.
-Rather than be part of the same pragmatic reasoning architecture, the common ground and mutual exclusitivity inferences we consider could be computed separately and then combined.
+Information sources need not be integrated in a Bayesian manner as part of the same pragmatic reasoning architecture.
+Instead, the common ground and mutual exclusitivity inferences we consider could be computed separately and combined in a more heuristic fashion.
 A listener could integrate these two independent inferences in an additive manner, weighting the sources of information by some ratio $\phi$.
 $\phi$ is then a bias to prefer one type of inference relative to the other.
-We formalize this alternative hypothesis as a  *mixture model*.
+We formalize this alternative hypothe sis as a  *mixture model*.
 
@@
 The **integration model** assumes that the process by which information is integrated remains constant across development.
-What changes is children's semantic knowledge, their expectations about speaker informativeness, and their sensitivity to common ground, but the way these information sources are combined remains the same across age.
+What changes is children's sensitivity to different cues: semantic knowledge, their expectations about speaker informativeness, and their sensitivity to common ground.
 The **mixture model** alternatively posits that there is some bias or preference for one information source, and this bias could change across development.
-This **developmental mixture model**  makes the same assumptions about developmental change in the individual information sources as the **integration model** but, in addition, assumes that the way that the mutual exclusivity and the common ground inference are combined with one another changes over time.
-This model is structurally identical to the **mixture model** but the mixture parameter $\phi$ is a function of age (i.e.
-represented by an intercept and a slope).
+This **developmental mixture model**  makes the same assumptions about developmental change in sensitivities to individual information sources as the **integration model** but, in addition, assumes that the way that the mutual exclusivity and the common ground inference are combined changes over time.
+This model is structurally identical to the **mixture model** but the mixture parameter $\phi$ is a function of age, which we model via a logistic-linear model: $\phi_i = \text{logistic}(\beta^\phi_0 + i \cdot \beta^\phi_1)$, whose parameters we infer via Bayesian inference.
 
@@
 2).
-Now, in addition, we incorporate the data from Experiment 3 to additionally constrain these parameters as well as inform the mixture parameter for the mixture model (see Figure \@ref(fig:bda)).
+Now, in addition, we incorporate the data from Experiment 3 to additionally constrain these parameters as well as inform the mixture parameter for the mixture models (see Figure \@ref(fig:bda)).
 
@@
 <!-- \begin{equation}  -->
-$$P^{mixture}_{L_1}(r, \mathcal{L}|u) = \phi \cdot P_{S_1}(u|r_{t}, \mathcal{L}) + (1-\phi) P( \mathcal{L})P(r)$$
+$$
+P^{mixture}_{L}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i) \\
+P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\}) \propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\})
+$$
+where $P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})$ represents a mutual-exclusivity inference from a listener with a uniform prior on referents. $P_{S}(u \mid r_{t}$ is the same as in Eq. S above.
 <!-- \end{equation}  -->
@@
 
-For this model, we make the mixture parameter $\phi$ a function of age and estimate the intercept and slope that yield the best model predictions compared to the data from Experiment 3.
+For this model, we make the mixture parameter $\phi$ as a logistic-linear function of age-- $\phi_i = \text{logistic}(\beta^\phi_0 + i \cdot \beta^\phi_1)$ --- and estimate the intercept and slope that yield the best model predictions compared to the data from Experiment 3.
+The mixture model is then:
+$$
+P^{dev\_mixture}_{L}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i) \cdot P(r \mid \rho_i) \\
+$$
 The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`).
@@
 
-We compared models based on correlations and Bayes factors.
-Figure \@ref(fig:fig11) shows correlations between model predictions and the data, each binned by year and object.
-Even though model predictions and data are closely aligned for all models, the **integration model** shows the highest correlation in all age groups.
+As before, we compared models based on correlations and Bayes factors.
+Figure \@ref(fig:fig11) shows correlations between model predictions and the data, each binned by year and by object.
+Even though both mixture models have more free parameters then the *integration model*, the **integration model** shows the highest correlation in all age groups, though model predictions and data are closely aligned for all models.
 Next we directly compared models based using Bayes factors (see Table \@ref(tab:table6)).
@@
 
-Perhaps unsurprisingly, we see that further constraining the parameters for semantic knowledge, speaker informativeness and common ground sensitivity by the data from Experiment 3 greatly improves the model fit (comparison: integration (explanation) vs integration (prediction)).
-We also see that the explanation **integration model** provides, by far, the best fit to the data compared to the two **mixture models**.
+Perhaps unsurprisingly, we see that informing the parameters for semantic knowledge, speaker informativeness and common ground sensitivity by the data from Experiment 3 greatly improves the model fit (comparison: integration (explanation) vs integration (prediction)).
+We also see that the explanation **integration model** provides, by far, the best fit to the data compared to the two **mixture models**, even though the integration model has fewer free parameters than the mixture model.
 Interestingly, the prediction **integration model** also had a better fit, even though its parameters were not constrained by the data from Experiment 3.
-When comparing the two **mixture models** directly, we see that an age sensitive mixture parameter did not result in a substantially better fit.
+When comparing the two **mixture models** directly, we see that an age sensitive mixture parameter did not result in a substantially better fit, providing additional evidence that the integration process itself is not changing across development.
 
@@
 Furthermore, the **integration model** provided a better fit to the data compared to a number of lesioned models, which selectively omitted one type of information.
-This suggests that children flexibly integrate all available information.
+These results suggest that children flexibly integrate all available information.
 
 In the final section, we studied which process best explained children's information integration.
-We compared the **integration model** to a **mixture model** which assumed that children are biased towards one type of inference.
-We found that the **integration model** better explained the data compared to these alternative model.
+We compared the **integration model** to a **mixture model** which assumed that children are biased towards one type of inference, and a **developmental mixture model** that assumed that the bias could change across development.
+We found that the **integration model** better explained the data compared to both of these mixture models, even though the mixture models had more free parameters.
 In sum, we found that children's integration of semantic and pragmatic information during word learning is best described as a form of Bayesian social inference.

### 2020-04-17 paper/bda_fig.tex
reorganize repo and add bda figure to supplement
add rsa eqns to bda fig; add some priors

@@
 
-	\node[det, above=of data_me](L1_me){$L'_1$};
-	\node[det, above=of data_comb](L1_comb){$L_1$};
+\node[det, above=of data_me](L1_me){$L'$};
+\node[det, above=of data_comb](L1_comb){$L$};
 \node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};
@@
 
-%	\plate{plate_data_me}{
-%		(data_me)
-%	}{$i \in \mathcal{P}_{1}$}
-
-%	\plate{plate_data_cg}{
-%		(data_cg)
-%	}{$i \in \mathcal{P}_{2}$}
+\
 
@@
 	}{$i \in \text{2-to-4 year olds}$}
+
+\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,5) { 
+$\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
+$\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ \\
+$\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
+ $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ \\
+ $\mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
+ $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ \\
+ $\sigma^\theta_1 \sim \text{Uniform}(0,1)$
+};
+
+\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ $P_{L}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\
+$P_{S}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} $\\
+$P(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})$
+};
 

### 2020-04-17 paper/bda_fig.tex
adjust math in bda fig

@@
 
-\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,5) { 
+\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5) { 
 $\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
+ $\rho_i = \text{logistic}(\beta^\rho_0  + i \cdot \beta^\alpha_1)$ \\
 $\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ \\
 $\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
+ $\alpha_i = \beta^\alpha_0  + i \cdot \beta^\alpha_1$ \\
  $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ \\
@@
  $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ \\
- $\sigma^\theta_1 \sim \text{Uniform}(0,1)$
+ $\sigma^\theta_1 \sim \text{Uniform}(0,1)$ \\
+ $\beta^\theta_0 \sim \text{Gaussian}(\mu^\theta_0, \mu^\sigma_0)$ \\
+$\beta^\theta_1 \sim \text{Gaussian}(\mu^\theta_1, \mu^\sigma_1)$  \\
+ $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$
 };
@@
   \caption{Graphical model representing the Bayesian data analysis for \emph{Integration model} used for \emph{Explanation}.
-$L_1$ represents the RSA model defined by Eq.
+$L$ represents the RSA model defined by Eq.
 X, used to predict the Combination Data $d^{CM}$  from Expt.~3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$.
 This RSA model takes as input a speaker optimality parameter $\alpha_i$ (which varies by age), a semantic knowledge parameter $\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\rho_i$ (which varies by age).
-Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{ME}$; Expt.~1), via the same RSA model with no common ground $L'_1$;  common ground sensitivity parameters $\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{CG}$; Expt.~2).
+Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{ME}$; Expt.~1), via the same RSA model with no common ground $L$;  common ground sensitivity parameters $\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{CG}$; Expt.~2).
   Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\beta_0$ and $\beta_1$, respectively).

### 2020-04-20 paper/supplementary_material.Rmd
update supplement

@@
 subtitle: "Supplementary material"
-author: "Manuel Bohn, Michael Henry Tessler and Michael C. Frank"
+author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
 output: 
@@
     fig_caption: yes
-    code_folding: hide
+    #code_folding: hide
     number_sections: false
@@
 
-The goal of this study is to investigate the integration of semantic and pragmatic information during word learning in children between 2 and 5 years of age.
+The goal of this study is to investigate the integration of information during word learning in children between 2 and 5 years of age.
 As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning.
-In Experiment 1, we show that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge.
-In a second experiment, we show that children make inferences about word meanings based on common ground.
-In a third experiment, we find that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.
-
-Next, we introduce a computational framework which we use to formalize the process of how the inferences are integrated.
-As a part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground.
-We then use the our modelling framework to ask which of these information sources are necessary to predict children's responses in Experiment 3.
-
-In the final section, we turn to the process by which information is integrated.
-We contrast the process of rational Bayesian inference we introduced in our model with a biased integration process in which one type of inference is given more weight.
+In [Experiment 1](#experiment-1-mutual-exclusivity), we show that children make a so-called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge.
+In [Experiment 2](#experiment-2-common-ground), we show that children make inferences about word meanings based on common ground.
+In [Experiment 3](#experiment-3-combination), we show that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.
+
+[Next](#cognitive-models), we introduce a computational cognitive model (**integration model**) in which we formalize the process of how information sources are integrated.
+As part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground.
+We then use the our modelling framework to ask which of these information sources are necessary to [predict](#prediction) children's responses in Experiment 3.
+
+In the [final section](#explanation), we turn to the process by which information is integrated.
+We contrast the process of Bayesian inference we introduced in our model with a biased integration process in which some inforamtion sources are weighted as more important.
 As part of this, we also explore alternative ways to think about developmental change in the integration process.
@@
 
-The first experiment tested the so called mutual exclusivity inference in children between 2 and 5 years of age.
-The general phenomena is that when presented with a familiar and an unfamiliar object, children expect a novel word to refer to the unfamiliar object [e.g.
+The first experiment tested the so-called mutual exclusivity inference in children between 2 and 5 years of age.
+The general inference can be described as follows: when presented with a familiar and an unfamiliar object, children expect a novel word to refer to the unfamiliar object [e.g.
 @markman1988children].
 A range of explanations have been put forward for the cognitive basis of this inference [see @lewis2020-me for a discussion].
-Here, we treat the mutual exclusivity inference as pragmatic [e.g.
+Here, we treat mutual exclusivity as a pragmatic phenomenon [e.g.
 @clark1987principle].
@@
 @lewis2020-me].
-The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object.
+The assumption is that the strength of the mutual exclusivity inference varies with knowledge of the word for the familiar object presented alongside the novel object.
 That is, when the familiar object is an object for which children are less likely to know the word, they are less likely to assume that the novel word refers to the unfamiliar object.
@@
 
-The experiment was preregistered at https://osf.io/gy37b. The experiment itself can be run by downloading the associated repository and opening the file `experiments/ex1_me.html`.
+The experiment was preregistered at https://osf.io/gy37b.
+The experiment itself can be run by downloading the associated repository (https://github.com/manuelbohn/spin) and opening the file `experiments/ex1_me.html`.
 
@@
 Children saw an animal standing on a little hill between two tables.
-For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to make requests.
+For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to talk to the child and make requests.
 Each experiment started with two training trials in which the speaker requested known objects (car and ball).
@@
 
-```{r fig1,echo = F, fig.align = "center", fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
+```{r fig1,echo = F,  fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
 knitr::include_graphics("../figures/method_overview.png")
@@
 Familiar objects were selected to vary along the dimension of how likely children were to know the word for each object.
-This including objects that most 2-year-olds could name (e.g.
-a duck) as well as objects that only very few 5-year-olds could name (e.g.
+This including objects that most 2-year-olds can name (e.g.
+a duck) as well as objects that only very few 5-year-olds can name (e.g.
 a pawn).
@@
 While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned.
-Figure \@ref(fig:fig2)A shows the objects used in the experiment.
+Figure \@ref(fig:fig2)A shows the words and objects used in the experiment.
 We induced this variation to estimate the role of semantic knowledge in a mutual exclusivity inference.
@@
 
-```{r table1, echo=T}
+```{r table1, echo=F}
 chance_me <- me_data %>%
@@
 For this analysis, we aggregated participants' responses across familiar objects.
-We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes factor (BF) in favor of the hypothesis that children chose the novel object more often than expected by chance (50% correct).
+We used the function `ttestBF` from the R-package `BayesFactor` [@R-BayesFactor] to compute a Bayes Factor (BF) in favor of the hypothesis that children chose the novel object more often than expected by chance (50%).
 Table \@ref(tab:table1) shows that all age groups made the inference.
 
-```{r, echo=T}
+```{r, echo=F}
 # prior_me <- c(prior(normal(0, 5), class = Intercept),
@@
 
-```{r}
+```{r, cache = T}
 fixef_me <- as_tibble(fixef(bm_me), rownames = "term")
@@
 However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent.
-The priors we used were `normal(0,5)` for fixed effects and `cauchy(0,1)` for standard deviations of random effects.
+The priors we used were $\text{Gaussian}(0,5)$ for fixed (population level) effects and $\text{Cauchy}(0,1)$ for standard deviations of random effects.
 The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`.
@@
 Figure \@ref(fig:fig2)B visualizes the model based developmental trajectory for each familiar object and illustrates the substantial variation between them, both in terms of absolute strength of the inference as well as its developmental trajectory.
-Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept.
+Figure \@ref(fig:fig2)C shows the correlation between rated age of acquisition and object specific model intercept (i.e.
+mutual exclusivity inference at age 2.00).
 The mutual exclusivity effect was stronger for words that were rated to be acquired earlier.
@@
 
-```{r table2, echo=T}
+```{r table2, echo=F, cache = T}
 
@@
   SE = round(c(me_waic$loos$bm_me$estimates["waic","SE"],me_waic$loos$bm_me2$estimates["waic","SE"]),2),
-  weight = round(c(me_weights[1],me_weights[2]))
+  weight = format(round(c(me_weights[1],me_weights[2]),2), nsmall = 2)
 )
@@
 
-```{r fig2, include = T, fig.align = "center", fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition.
+```{r fig2, include = T, fig.cap = "A:Familiar words and corresponding pictures by rated age of acquisition.
 B: Developmental trajectories of mututal exclusivity effect by familiar object based on the mean of the model posterior distribution.
@@
 Then the speaker returned and requested an object in the same way as in Experiment 1 (see also Figure \@ref(fig:fig1)B).
-The positioning of the novel object in the beginning of the experiment as well as the location the speaker turned to first was counterbalanced.
+The positioning of the novel object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced.
 Children received five trials, each with a different pair of novel objects.
@@
 
-```{r table3, echo=T}
+```{r table3, echo=F}
 chance_prior <- prior_data %>%
@@
 
-```{r, echo=T}
+```{r, echo=F}
 # prior_cg <- c(prior(normal(0, 5), class = Intercept),
@@
 As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but also the role that each object (novel and familiar) had played in the preceding interaction.
-Combining the two procedures created two conditions: In the *congruent* condition, the novel object was also the object that was new to the speaker.
+Combining the two procedures created two alignment conditions: In the *congruent condition*, the novel object was also the object that was new to the speaker.
 In this case, the mutual exclusivity inference as well as the common ground inference pointed to the novel object as the referent.
 In the *incongurent condition*, the familiar object was new to the speaker.
-Int his case, the two inferences pointed to different objects.
+In this case, the two inferences pointed to different objects.
 The main focus of the overall study was to model how children integrate and balance these different information sources.
-We investigate this question in depth in the [modelling](#model) section below.
+We investigate this question in depth in the [modelling](#cognitive-models) section below.
 Here, we limit the discussion to whether children differentiated between the two conditions.
@@
 
-Experiment 3 followed the same procedure as Experiment 2 but involved the same objects as Experiment 1.
+Experiment 3 followed the same procedure as Experiment 2 but involved the same objects as Experiment 1 (Figure \@ref(fig:fig1)C).
 In the beginning, one table was empty while there was an object (novel or familiar) on the other one.
@@
 Familiar objects were the same as in Experiment 1.
-The positioning of the objects on the tables and the location the speaker first turned to were counterbalanced.
+The positioning of the objects on the tables, the speaker and the location the speaker first turned to were counterbalanced.
 Participants could stop the experiment after six trials (three per condition).
-If a participant stopped after half of the trials, we tested an additional participant to reach a pre-registered number of data points per cell.
+If a participant stopped after half of the trials, we tested an additional participant to reach a pre-registered number of data points per age group (2-, 3- and 4-year-olds).
 
@@
 All results are reported from the perspective of the mutual exclusivity inference (`correct` in the model formula below).
-In the incongruent condition, high proportions speak to a mutual exclusivity inference and low proportion for a common ground inference.
+In the incongruent condition, high proportions speak to a mutual exclusivity inference and low proportion to a common ground inference.
 In the congruent condition, both inferences pointed in the same direction.
@@
 
-```{r, echo=T}
+```{r, echo=F}
 
@@
 
-```{r}
+```{r, cache = T}
 fixef_comb <- as_tibble(fixef(bm_comb), rownames = "term")
@@
 
-```{r table4, echo=T}
+```{r table4, echo=F, cache = T}
 
@@
   SE = round(c(comb_waic$loos$bm_comb$estimates["waic","SE"],comb_waic$loos$bm_comb2$estimates["waic","SE"]),2),
-  weight = round(c(comb_weights[1],comb_weights[2]))
+  weight = format(round(c(comb_weights[1],comb_weights[2]),2), nsmall = 2)
 )
@@
 
-```{r fig3, include = T, fig.align = "center", fig.cap = "Proportion of choosing the object that was new to the speaker by age.
+```{r fig3, include = T,  fig.cap = "Proportion of choosing the object that was new to the speaker by age.
 Dots show the mean response for each participant.
@@
 The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate.
-Experiment 1 showed that children of all age groups make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented.
-Experiment 2 showed that children are sensitive to the common ground manipulation we implemented and that this inference increases with age.
+Experiment 1 showed that children of all age groups make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on children's semantic knowledge.
+Experiment 2 showed that children are sensitive to the common ground manipulation we implemented and that the sensitivity to common ground increases with age.
 Finally, Experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another.
@@
 
-# Models
+# Cognitive models
 
@@
 
-$$
-P_{L}(r \mid u)\propto P_{S}(u \mid r) \cdot P(r \mid \rho_i) \\ 
-P_{S}(u \mid r)\propto P(r\mid u) ^{\alpha_i} \\
-P(r\mid u) \propto \mathcal{L}(u, r \mid \theta_{ij})
-$$
-
-Our model describes a listener ($P_L$) reasoning about the referent referred to by a speaker's ($P_S$) utterance.
+\begin{equation}
+P_{L_1}(r \mid u)\propto P_{S_1}(u \mid r) \cdot P(r \mid \rho_i) \\ 
+P_{S_1}(u \mid r)\propto P_{L_0}(r\mid u) ^{\alpha_i} \\
+P_{L_0}(r\mid u) \propto \mathcal{L}(u, r \mid \theta_{ij})
+(\#eq:rsabasic)
+\end{equation}
+
+Our model describes a listener ($L_1$) reasoning about the referent referred to by a speaker's ($S_1$) utterance.
 This reasoning is contextualized by the prior probability of each referent $P(r \mid \rho_i)$.
@@
 
-To decide between referents, the listener reasons about what a rational speaker would say given an intended referent.
+To decide between referents, the listener ($L_1$) reasons about what a rational speaker ($S_1$) would say given an intended referent.
 This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one.
@@
 
-The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
+The informativity of each utterance is given by imagining which referent a literal listener ($L_0$), who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
   Following @frank2014inferring, we use an implicit uniform prior over referents in the literal listener.
@@
 
-The model with each data-analytic parameter represented explicitly in $\{, \}s$ is:
-
-$$
-P_{L}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) \\ 
-P_{S}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} \\
-P(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})
-$$
+The model with each data-analytic parameter represented explicitly in $\{ \}$ is:
+
+\begin{equation}
+P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) \\ 
+P_{S_1}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P_{L_0}(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} \\
+P_{L_0}(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})
+(\#eq:rsafull)
+\end{equation}
 
@@
 
-```{r bda, engine='tikz', echo = F,fig.align = "center", fig.cap = "Graphical model representing the Bayesian data analysis for **integration model** used for *Explanation*.
+```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **Integration model** used for *Explanation*.
 $L_1$ represents the RSA model defined by Eq.
-X, used to predict the Combination Data $d^{CM}$  from Expt.
+2, used to predict the Combination Data $d^{Ex3}$ from Expt.
 3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$.
-This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\\rho_i$ (which varies by age).
-Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{ME}$; Expt.
-1), via the same RSA model with no common ground $L'_1$;  common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{CG}$; Expt.
+This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity parameter $\\rho_i$ (which varies by age).
+Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{Ex1}$; Expt.
+1), via the same RSA model with no common ground $L'_1$;  common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt.
 2).
-Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\beta_0$ and $\\beta_1$, respectively).
-Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu$ and $sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}
+Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\\beta_0$ and $\\beta_1$, respectively).
+Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu^{\\theta}$ and $\\sigma^{\\theta}$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}
 
@@
 
+\resizebox{1\textwidth}{!}{
+
 \begin{tikzpicture}
-%% RSA nodes and data
-\node[obs](data_comb){$d^{CM}_{ijk}$};
-\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{ME}_{ij}$};
-\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};
-
-\node[det, above=of data_me](L1_me){$L'_1$};
+
+\node[obs](data_comb){$d^{Ex3}_{ijk}$};
+\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{Ex1}_{ij}$};
+\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{Ex2}_{i}$};
+
+\node[det, above=of data_me](L1_me){$L_1'$};
 \node[det, above=of data_comb](L1_comb){$L_1$};
@@
 
+\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5) { 
+$\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
+ $\rho_i = \text{logistic}(\beta^\rho_0  + i \cdot \beta^\alpha_1)$ \\
+$\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ \\
+$\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
+ $\alpha_i = \beta^\alpha_0  + i \cdot \beta^\alpha_1$ \\
+ $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ \\
+ $\mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
+ $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ \\
+ $\sigma^\theta_1 \sim \text{Uniform}(0,1)$ \\
+ $\beta^\theta_0 \sim \text{Gaussian}(\mu^\theta_0, \mu^\sigma_0)$ \\
+$\beta^\theta_1 \sim \text{Gaussian}(\mu^\theta_1, \mu^\sigma_1)$  \\
+ $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$
+};
+
+\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ $P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\
+$P_{S_1}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P_{L_0}(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} $\\
+$P_{L_0}(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})$
+};
+
 \end{tikzpicture}
+
+}
 
@@
 We excluded samples from one chain because it got stuck on a local maximum which resulted in parameter distributions that were substantially different from the other chains.
-The model outputs can be found in the following online repository: XXXXXX.
+To direclty access the model predictions see the file `model_comparison.Rmd` in the online repository.
 
@@
 
-```{r fig4, include = T, fig.align = "center", fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity.
+```{r fig4, include = T, fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity.
 Solid lines in show the MAP estimate for each parameter.
@@
 
-```{r fig5, include = T, fig.align = "center", fig.cap = "Predicting information integration across development.
+```{r fig5, include = T, cache = T, fig.cap = "Predicting information integration across development.
 Model predictions based on the integration model.
@@
 The **no word knowledge model** takes in the overall trajectory for semantic knowledge---represented by $\mu^\theta_0$ and $\mu^\theta_1$---but ignores object-specific variation.
-Formally, the semantic knowledge for each item is the same: $\theta_{ij} = \mu^\theta_0 +  i \cdot \mu^\theta_1$.
-That is, the model assumes a listener whose mutual exclusivity inference does not vary depending on the particular familiar object but only depends on the average semantic knowledge.
+Formally, the semantic knowledge for each item is the same: $\theta_{i} = \mu^\theta_0 +  i \cdot \mu^\theta_1$.
+That is, the model assumes a listener whose mutual exclusivity inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.
+
+\begin{equation}
+P^{no\_wk}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{i}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{i}\}) \cdot P(r \mid \rho_i) \\ 
+(\#eq:noword)
+\end{equation}
 
@@
 
+\begin{equation}
+P^{no\_cg}_{L_1}(r \mid u; \{\alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \\ 
+(\#eq:nocg)
+\end{equation}
+
 #### No mutual exclusivity model
@@
 Finally, we consider a model that focuses only on common ground information and ignores the identity of the objects on the tables as well as any inferences their semantic knowledge of the familiar objects license.
-The predictions of this model correspond to the prior distribution over objects $P(r \mid \rho_i)$.
+The predictions of this model correspond to the prior distribution over objects.
+
+\begin{equation}
+P^{no\_me}_{L_1}(r \mid u; \{\rho_i\})\propto P(r \mid \rho_i) 
+(\#eq:nome)
+\end{equation}
 
@@
 The results show that the **integration model**, by far, outperformed all the other models.
-When comparing the lesioned models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the *no mutual exclusivity model*.
+When comparing the lesioned models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the **no mutual exclusivity model**.
 
@@
 
-```{r fig6, include = T, fig.align = "center", fig.cap = "Predicting information integration.
+```{r fig6, include = T,  fig.cap = "Predicting information integration.
 Correlations between model predictions and data binned by year, item and condition.
@@
 $\phi$ is then a bias to prefer one type of inference relative to the other.
-We formalize this alternative hypothe sis as a  *mixture model*.
+We formalize this alternative hypothesis as a  **mixture model**.
 
@@
 
-```{r fig9, include = T, fig.align = "center", fig.cap = "Explaining information integration across development.
+```{r fig9, include = T, cache = T,  fig.cap = "Explaining information integration across development.
 Model predictions based on the integration model.
@@
 
-<!-- \begin{equation}  -->
-$$
-P^{mixture}_{L}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i) \\
-P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\}) \propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\})
-$$
-where $P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})$ represents a mutual-exclusivity inference from a listener with a uniform prior on referents. $P_{S}(u \mid r_{t}$ is the same as in Eq. S above.
-<!-- \end{equation}  -->
+\begin{equation}
+P^{mixture}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i) \\
+P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\}) \propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\})
+(\#eq:mix)
+\end{equation}
+
+where $P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})$ represents a mutual-exclusivity inference from a listener with a uniform prior on referents.
+$P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}$ is the same as in Eq.
+\@ref(eq:rsafull) above.
 
@@
 For this model, we make the mixture parameter $\phi$ as a logistic-linear function of age-- $\phi_i = \text{logistic}(\beta^\phi_0 + i \cdot \beta^\phi_1)$ --- and estimate the intercept and slope that yield the best model predictions compared to the data from Experiment 3.
-The mixture model is then:
-$$
-P^{dev\_mixture}_{L}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i) \cdot P(r \mid \rho_i) \\
-$$
+The **developmental mixture model** is then:
+
+\begin{equation}
+P^{dev\_mixture}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i) \cdot P(r \mid \rho_i) \\
+(\#eq:devmix)
+\end{equation}
+
 The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`).
@@
 
-```{r fig10, include = T, fig.align = "center", fig.cap = "Mixture component for the mixture model (A) and the developmental mixture model (B).
-(A) shows the posterior distribution of the mixture component and (B) shows developmental trajectories for the mixture component based on 300 random draws from the posterior distribution for intercept and slope.", fig.width=10, fig.height = 4, fig.align= "center"}
+```{r fig10, include = T, fig.cap = "Mixture component for the mixture model (A) and the developmental mixture model (B).
+(A) shows the posterior distribution of the mixture component and (B) shows developmental trajectories for the mixture component based on 300 random draws from the posterior distribution for intercept and slope.", fig.width=10, fig.height = 4, }
 ggarrange(plot_mixture, plot_dev_mixture,  labels = c("A","B"), nrow = 1)
@@
 Figure \@ref(fig:fig11) shows correlations between model predictions and the data, each binned by year and by object.
-Even though both mixture models have more free parameters then the *integration model*, the **integration model** shows the highest correlation in all age groups, though model predictions and data are closely aligned for all models.
+Even though both mixture models have more free parameters then the **integration model**, the **integration model** shows the highest correlation in all age groups, though model predictions and data are closely aligned for all models.
 Next we directly compared models based using Bayes factors (see Table \@ref(tab:table6)).
@@
 
-```{r fig11, include = T, fig.align = "center", fig.cap = "Explaining information integration.
+```{r fig11, include = T,  fig.cap = "Explaining information integration.
 Correlations between model predictions and data binned by year, item and condition.
@@
 
-```{r figa1, include = T, fig.align = "center", fig.cap = "Posterior distribution of intercept term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
+```{r figa1, include = T, cache=T,  fig.cap = "Posterior distribution of intercept term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
 
@@
 
-```{r figa2, include = T, fig.align = "center", fig.cap = "Posterior distribution of slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
+```{r figa2, include = T, cache=T,  fig.cap = "Posterior distribution of slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
 
@@
 
-```{r figa3, include = T, fig.align = "center", fig.cap = "Posterior distribution of slope and intercept terms for speaker informativeness and sensitivity to common ground by model.", fig.width=8, fig.height = 6, fig.align="center"}
+```{r figa3, include = T, cache=T, fig.cap = "Posterior distribution of slope and intercept terms for speaker informativeness and sensitivity to common ground by model.", fig.width=8, fig.height = 6}
 
@@
   theme_few()+
-  theme(legend.position = "bottom")+
+  theme(legend.position = "right")+
   scale_fill_ptol(name = "Model")+

### 2020-04-20 stats/model_comparison.Rmd
update supplement

@@
 
+# Model predictions
+
+Model predictions can be downloaded via the following link: https://keeper.mpdl.mpg.de/d/7ae3805dba064bada8e5/
+In the code below, model predictions are assumed to be in a subfolder called `saves/`.
+
 # Model comparison prediction
@@
 
-saveRDS(model_by_chain, "../saves/pred_model_likelihood_chain.rds")
+#saveRDS(model_by_chain, "../saves/pred_model_likelihood_chain.rds")
 
@@
 
-saveRDS(model, "../saves/pred_model_likelihood.rds")
+#saveRDS(model, "../saves/pred_model_likelihood.rds")
 
@@
 
-saveRDS(model_comp, "../saves/pred_model_comparison.rds")
+#saveRDS(model_comp, "../saves/pred_model_comparison.rds")
 
@@
 
-saveRDS(model_by_chain, "../saves/expl_model_likelihood_chain.rds")
+#saveRDS(model_by_chain, "../saves/expl_model_likelihood_chain.rds")
 
@@
 
-saveRDS(model, "../saves/expl_model_likelihood.rds")
+#saveRDS(model, "../saves/expl_model_likelihood.rds")
 
@@
 
-saveRDS(model_comp, "../saves/expl_model_comparison.rds")
+#saveRDS(model_comp, "../saves/expl_model_comparison.rds")
 

### 2020-04-20 paper/supplementary_material.Rmd
include knit to PDF

@@
 output: 
+  bookdown::pdf_document2:
+    toc: yes 
+    number_sections: false    
   bookdown::html_document2:
@@
 However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent.
-The priors we used were $\text{Gaussian}(0,5)$ for fixed (population level) effects and $\text{Cauchy}(0,1)$ for standard deviations of random effects.
+The priors we used were $\mathcal{N}(0,5)$ for fixed (population level) effects and $\text{Cauchy}(0,1)$ for standard deviations of random effects.
 The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`.
@@
 \begin{equation}
-P_{L_1}(r \mid u)\propto P_{S_1}(u \mid r) \cdot P(r \mid \rho_i) \\ 
-P_{S_1}(u \mid r)\propto P_{L_0}(r\mid u) ^{\alpha_i} \\
+P_{L_1}(r \mid u)\propto P_{S_1}(u \mid r) \cdot P(r \mid \rho_i)
+(\#eq:rsabasic1)
+\end{equation}
+
+\begin{equation}
+P_{S_1}(u \mid r)\propto P_{L_0}(r\mid u) ^{\alpha_i}
+(\#eq:rsabasic2)
+\end{equation}
+
+\begin{equation}
 P_{L_0}(r\mid u) \propto \mathcal{L}(u, r \mid \theta_{ij})
-(\#eq:rsabasic)
+(\#eq:rsabasic3)
 \end{equation}
@@
 \begin{equation}
-P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) \\ 
-P_{S_1}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P_{L_0}(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} \\
+P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i)
+(\#eq:rsafull1)
+\end{equation}
+
+\begin{equation}
+P_{S_1}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P_{L_0}(r \mid u; \{\theta_{ij}\}) ^{\alpha_i}
+(\#eq:rsafull2)
+\end{equation}
+
+\begin{equation}
 P_{L_0}(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})
-(\#eq:rsafull)
+(\#eq:rsafull3)
 \end{equation}
@@
 ```
+
 ### Models
@@
 \begin{equation}
-P^{mixture}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i) \\
+P^{mixture}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)
+(\#eq:mix1)
+\end{equation}
+
+\begin{equation}
 P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\}) \propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\})
-(\#eq:mix)
+(\#eq:mix2)
 \end{equation}
@@
 $P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}$ is the same as in Eq.
-\@ref(eq:rsafull) above.
+\@ref(eq:rsafull2) above.
 
@@
 \begin{equation}
-P^{dev\_mixture}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i) \cdot P(r \mid \rho_i) \\
+P^{dev\_mixture}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i) \cdot P(r \mid \rho_i)
 (\#eq:devmix)

### 2020-04-20 paper/supplementary_material.Rmd
minor edits

@@
 For $\theta \in (0, 1)$, the semantic interpretation function will select the familiar referent with probability $\theta + (1 - \theta)\frac{1}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.^[
-  One could also define $\theta$ to directly denote the probability of selecting the familiar~vs.~unfamiliar referent.
+  One could also define $\theta$ to directly denote the probability of selecting the familiar vs.
+unfamiliar referent.
 The model behavior would be the same except for a translation of this parameter.
-We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete uncertainty.
+We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete ignorance, corresponding to maximal uncertainty about which object the word applies to.
 ] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.
@@
 We consider a model that ignores common ground information, $\rho_i$.
-This model takes in object specific semantic knowledge and speaker informativeness butuses a prior distribution over objects that is constant across alignment conditions and uniform (e.g., [0.5, 0.5]).
+This model takes in object specific semantic knowledge and speaker informativeness but uses a prior distribution over objects that is constant across alignment conditions and uniform (e.g., [0.5, 0.5]).
 This model corresponds to a listener who only focuses on the mutual exclusivity inference and ignores the common ground manipulation.

### 2020-04-20 paper/bda_fig.tex
add data distributions to list of eqns, subscript RSA models

@@
 
-\node[det, above=of data_me](L1_me){$L'$};
-\node[det, above=of data_comb](L1_comb){$L$};
+\node[det, above=of data_me](L1_me){$L'_{ij}$};
+\node[det, above=of data_comb](L1_comb){$L_{ijk}$};
 \node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};
@@
 
-\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5) { 
+\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5.75) { 
 $\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
  $\rho_i = \text{logistic}(\beta^\rho_0  + i \cdot \beta^\alpha_1)$ \\
-$\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ \\
-$\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
+ $d^{CG}_{i} \sim \text{Bernoulli}(\rho_i)$ \\
+ \\
+$\beta^\alpha_0 \sim \text{Uniform}(-3,3); \beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
  $\alpha_i = \beta^\alpha_0  + i \cdot \beta^\alpha_1$ \\
- $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ \\
- $\mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
- $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ \\
- $\sigma^\theta_1 \sim \text{Uniform}(0,1)$ \\
- $\beta^\theta_0 \sim \text{Gaussian}(\mu^\theta_0, \mu^\sigma_0)$ \\
-$\beta^\theta_1 \sim \text{Gaussian}(\mu^\theta_1, \mu^\sigma_1)$  \\
- $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$
+ \\
+ $\mu^\theta_0 \sim \text{Uniform}(-3,3); \mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
+ $\sigma^\theta_0 \sim \text{Uniform}(0,2); \sigma^\theta_1 \sim \text{Uniform}(0,1)$ \\
+ $\beta^\theta_0 \sim \text{Gaussian}(\mu^\theta_0, \mu^\sigma_0); \beta^\theta_1 \sim \text{Gaussian}(\mu^\theta_1, \mu^\sigma_1)$  \\
+ $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$ \\
+ $d^{ME}_{ij} \sim L',  d^{CM}_{ij} \sim L$
 };

### 2020-04-20 paper/supplementary_material.Rmd
modify bda figure

@@
 output: 
-  bookdown::pdf_document2:
-    toc: yes 
-    number_sections: false    
   bookdown::html_document2:
@@
     #code_folding: hide
+    number_sections: false
+  bookdown::pdf_document2:
+    toc: yes 
     number_sections: false    
@@
 
-```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **Integration model** used for *Explanation*.
+```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **integration model** used for *Explanation*.
+$RSA$ represents the general model architecture and paremeters defined by Eq.
+\\@ref(eq:rsabasic1) - \\@ref(eq:rsabasic3).
 $L_1$ represents the RSA model defined by Eq.
-2, used to predict the Combination Data $d^{Ex3}$ from Expt.
+\\@ref(eq:rsafull1), used to predict the combination data $d^{Ex3}$ from Expt.
 3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$.
-This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity parameter $\\rho_i$ (which varies by age).
+This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\\rho_i$ (which varies by age).
 Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{Ex1}$; Expt.
-1), via the same RSA model with no common ground $L'_1$;  common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt.
+1), via the same RSA model with no common ground $L$; common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt.
 2).
 Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\\beta_0$ and $\\beta_1$, respectively).
-Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu^{\\theta}$ and $\\sigma^{\\theta}$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}
+Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu$ and $\\sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}
 
@@
 
-\node[det, above=of data_me](L1_me){$L_1'$};
-\node[det, above=of data_comb](L1_comb){$L_1$};
+\node[det, above=of data_me](L1_me){$L'_{1_{ij}}$};
+\node[det, above=of data_comb](L1_comb){$L_{1_{ijk}}$};
 \node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};
@@
 
-\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5) { 
+\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5.75) { 
 $\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
  $\rho_i = \text{logistic}(\beta^\rho_0  + i \cdot \beta^\alpha_1)$ \\
-$\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ \\
-$\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
+ $d^{Ex2}_{i} \sim \text{Bernoulli}(\rho_i)$ \\
+ \\
+$\beta^\alpha_0 \sim \text{Uniform}(-3,3); \beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
  $\alpha_i = \beta^\alpha_0  + i \cdot \beta^\alpha_1$ \\
- $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ \\
- $\mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
- $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ \\
- $\sigma^\theta_1 \sim \text{Uniform}(0,1)$ \\
- $\beta^\theta_0 \sim \text{Gaussian}(\mu^\theta_0, \mu^\sigma_0)$ \\
-$\beta^\theta_1 \sim \text{Gaussian}(\mu^\theta_1, \mu^\sigma_1)$  \\
- $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$
+ \\
+ $\mu^\theta_0 \sim \text{Uniform}(-3,3); \mu^\theta_1 \sim \text{Uniform}(0,2)$ \\
+ $\sigma^\theta_0 \sim \text{Uniform}(0,2); \sigma^\theta_1 \sim \text{Uniform}(0,1)$ \\
+ $\beta^\theta_0 \sim \text{Gaussian}(\mu^\theta_0, \mu^\sigma_0); \beta^\theta_1 \sim \text{Gaussian}(\mu^\theta_1, \mu^\sigma_1)$  \\
+ $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$ \\
+ $d^{Ex1}_{ij} \sim L'_1,  d^{Ex3}_{ij} \sim L_1$
 };

### 2020-04-28 paper/supplementary_material.Rmd
fix typo

@@
 As part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground.
-We then use the our modelling framework to ask which of these information sources are necessary to [predict](#prediction) children's responses in Experiment 3.
+We then use the modelling framework to ask which of these information sources are necessary to [predict](#prediction) children's responses in Experiment 3.
 

### 2020-05-17 paper/bda_fig.tex
modify bda figure
update supplement! !

@@
 \begin{tabular}{cc}
+
 \begin{tikzpicture}
@@
 
-\node[det, above=of data_me](L1_me){$L'_{ij}$};
-\node[det, above=of data_comb](L1_comb){$L_{ijk}$};
+\node[det, above=of data_me](L1_me){$L'_{1_{ij}}$};
+\node[det, above=of data_comb](L1_comb){$L_{1_{ij}}$};
 \node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};
@@
 
-\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ $P_{L}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\
+\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ $P_{L_{1}}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\
 $P_{S}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} $\\

### 2020-05-17 paper/supplementary_material.Rmd
update supplement! !

@@
 ---
-title: "Word learning at the semantics pragmatics interface"
+title: "How young children integrate information during word learning"
 subtitle: "Supplementary material"
@@
     #code_folding: hide
-    number_sections: false
-  bookdown::pdf_document2:
-    toc: yes 
     number_sections: false

### 2020-05-18 paper/supplementary_material.Rmd
update color scheme

@@
   theme(legend.position = "bottom")+
-  scale_fill_ptol(name = "Model")+
-  scale_color_ptol(name = "Model")
+  scale_fill_colorblind(name = "Model")+
+  scale_color_colorblind(name = "Model")
 ```
@@
   theme(legend.position = "right")+
-  scale_fill_ptol(name = "Model")+
-  scale_color_ptol(name = "Model")
-```
+  scale_fill_colorblind(name = "Model")+
+  scale_color_colorblind(name = "Model")
+```

### 2020-06-24 paper/supplementary_material.Rmd
presubmission clean up

@@
 ---
-title: "How young children integrate information during word learning"
+title: "Young children rationally integrate semantic and pragmatic information sources to infer the meaning of words"
 subtitle: "Supplementary material"
@@
 
-[Next](#cognitive-models), we introduce a computational cognitive model (**integration model**) in which we formalize the process of how information sources are integrated.
+[Next](#cognitive-models), we introduce a computational cognitive model (**rational integration model**) in which we formalize the process of how information sources are integrated.
 As part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground.
-We then use the modelling framework to ask which of these information sources are necessary to [predict](#prediction) children's responses in Experiment 3.
+We then use the modeling framework to ask which of these information sources are necessary to [predict](#prediction) children's responses in Experiment 3.
 
 In the [final section](#explanation), we turn to the process by which information is integrated.
-We contrast the process of Bayesian inference we introduced in our model with a biased integration process in which some inforamtion sources are weighted as more important.
+We contrast the process of Bayesian inference we introduced in our model with a biased integration process in which some information sources are weighted as more important.
 As part of this, we also explore alternative ways to think about developmental change in the integration process.
@@
 That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects).
-We did not pre-register agent as a random effect, but retrospecitvely included it to be consistent with Experiment 2 and 3.
+We did not pre-register agent as a random effect, but retrospectively included it to be consistent with Experiment 2 and 3.
 
@@
 Older children were more likely to make a mutual exclusivity inference.
-To assess the variability accross objects, we compared the fit of the above model to a model lacking `object` as a random effect.
+To assess the variability across objects, we compared the fit of the above model to a model lacking `object` as a random effect.
 Following McElreath [-@rethinking], we compared models using WAIC (widely applicable information criterion) scores and weights.
@@
 Experiment 3 combined the procedures from Experiment 1 and 2.
-As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licences but also the role that each object (novel and familiar) had played in the preceding interaction.
+As a consequence, children had to consider not just their semantic knowledge of the word for the familiar object and the inference this licenses but also the role that each object (novel and familiar) had played in the preceding interaction.
 Combining the two procedures created two alignment conditions: In the *congruent condition*, the novel object was also the object that was new to the speaker.
@@
 To do so, we use Bayesian cognitive models of pragmatic reasoning.
-We first describe an **integration model** which we think best represents the inference and integration processes and then specify how this model captures developmental change.
+We first describe an **rational integration model** which we think best represents the inference and integration processes and then specify how this model captures developmental change.
 Next, we ask how well this model *predicts* how children integrate information.
@@
 We then test the predictive power of the model by comparing the model predictions to the data from Experiment 3.
-We use formal model comparison methods to test the **integration model** against a range of alternative models.
+We use formal model comparison methods to test the **rational integration model** against a range of alternative models.
 
@@
 We parameterize the listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1.
-$\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene.
+$\theta = 0$ corresponds to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene.
 Each of the novel words are assumed to have semantic knowledge of 0.
@@
 In our paradigm, common ground takes the form of *discourse novelty*, and $\rho$ captures the salience (or lack thereof) of an object due to its presence or absence in the social interaction that precedes the utterance (see \@ref(fig:fig1)B).
-Specifically, the pragmatic listener uses the common ground parameter $\rho$ as the prior probability of the discourse-novel (i.e., the referent that was absent in the social interaction that preceded the utterance): In the *congruent* condition, the object in the prior social interaction (i.e., the discourse-familiar object) was the familiar object, and hence, both common ground (discourse novelty) and mutual exclusivity are cues to the same referent; in the *incongruent* condition, the object in the prior social interaction was the novel object, and hence, common ground (discourse-novelty) and mutual exclusitivity are cues to different referents (see Figure \@ref(fig:fig1)C).
+Specifically, the pragmatic listener uses the common ground parameter $\rho$ as the prior probability of the discourse-novel (i.e., the referent that was absent in the social interaction that preceded the utterance): In the *congruent* condition, the object in the prior social interaction (i.e., the discourse-familiar object) was the familiar object, and hence, both common ground (discourse novelty) and mutual exclusivity are cues to the same referent; in the *incongruent* condition, the object in the prior social interaction was the novel object, and hence, common ground (discourse-novelty) and mutual exclusivity are cues to different referents (see Figure \@ref(fig:fig1)C).
 We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [@akhtar1996role; @diesendruck2004two], which we model with a logistic-linear function: $\rho_i = \text{logistic}(\beta^\rho_0 + i \cdot \beta^\rho_1)$.
 
-```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **integration model** used for *Explanation*.
+```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **rational integration model** used for *Explanation*.
 $RSA$ represents the general model architecture and paremeters defined by Eq.
@@
 
-\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ $P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\
+\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Rational integration model\\ $P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) $\\
 $P_{S_1}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P_{L_0}(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} $\\
@@
 That is, in a situation in which we know the development of the (object specific) mutual exclusivity inference as well as the common ground inference, we look at each model's ability to predict what happens when the two are combined (combination data from Experiment 3).
-Investigating "pure" (or, *a priori*) prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g., a heuristic, non-integrating mixture model, described below).
+Investigating "pure" (or, *a priori*) prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g., a heuristic, non-integrating biased model, described below).
 To generate *a priori* predictions, we independently estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.
@@
 We excluded samples from one chain because it got stuck on a local maximum which resulted in parameter distributions that were substantially different from the other chains.
-To direclty access the model predictions see the file `model_comparison.Rmd` in the online repository.
+To directly access the model predictions see the file `model_comparison.Rmd` in the online repository.
 
@@
 Note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in terms of which parameters they included.
-The models described below are a full model (**integration model**) and three lesioned models, which selectively omit one type of information.
+The models described below are a full model (**rational integration model**) and three lesioned models, which selectively omit one type of information.
 The following model comparison therefore asks which types of information are necessary to make good predictions about how information is integrated.
@@
 
-#### Integration model
-
-The **integration model** serves as the full model and takes in all available information.
+#### Rational integration model
+
+The **rational integration model** serves as the full model and takes in all available information.
 That is, it takes in object-specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above.
@@
 
-We compare this model to three alternative, "lesioned" models that lack certain components of the full integration model.
+We compare this model to three alternative, "lesioned" models that lack certain components of the rational integration model.
 
 ```{r fig5, include = T, cache = T, fig.cap = "Predicting information integration across development.
-Model predictions based on the integration model.
+Model predictions based on the rational integration model.
 Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution.
@@
 
-A marginally less-complex model than the full integration model uses the same model architecture, taking in speaker informativeness and common ground sensitivity, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge).
+A marginally less-complex model than the rational integration model uses the same model architecture, taking in speaker informativeness and common ground sensitivity, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge).
 We described above that the parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model.
@@
 Figure \@ref(fig:fig6) visualizes the correlation between model predictions and the data for all models.
-The results shows a very high correlation between the predictions of the **integration model** and the data in all age groups indicating that the model accurately captures the variation in the data.
-Correlations for the **integration model** were also higher compared to the other models considered.
+The results shows a very high correlation between the predictions of the **rational integration model** and the data in all age groups indicating that the model accurately captures the variation in the data.
+Correlations for the **rational integration model** were also higher compared to the other models considered.
 The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds.
 The mis-match for the oldest age group is probably a consequence of the model making very extreme predictions in the congruent condition.
-This results from the fact that 4-year-olds show very high performance both the mututal exclusivity and common ground tasks.
+This results from the fact that 4-year-olds show very high performance both the mutual exclusivity and common ground tasks.
 When combined in the model, the two inferences amplify one another because we assume no cost of integration.
@@
 Table \@ref(tab:table5) lists the Bayes factors for the different model comparisons.
-The results show that the **integration model**, by far, outperformed all the other models.
+The results show that the **rational integration model**, by far, outperformed all the other models.
 When comparing the lesioned models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the **no mutual exclusivity model**.
@@
 Taken together, these analyses showed two things.
-First, the **integration model** makes accurate predictions about how mutual exclusivity and common ground inferences are integrated.
+First, the **rational integration model** makes accurate predictions about how mutual exclusivity and common ground inferences are integrated.
 It does so based on knowing the strength and development of each inference alone, and incorporating them into a structured probabilistic model of pragmatic reasoning.
@@
 We explore alternative ways to think about information integration.
-The **integration model** outlined above operates via Bayesian inference in that the prior probability of a referent (a consequence of the common ground manipulation) is updated via the likelihood of hearing the utterance heard from a speaker, which is used to derive the mutual exclusivity inference.
+The **rational integration model** outlined above operates via Bayesian inference in that the prior probability of a referent (a consequence of the common ground manipulation) is updated via the likelihood of hearing the utterance heard from a speaker, which is used to derive the mutual exclusivity inference.
 In essence, this model is a multiplicative model because the posterior probability of each referent given the utterance is proportional to the product of the likelihood of a speaker saying that utterance and the prior probability of that referent.
@@
 Information sources need not be integrated in a Bayesian manner as part of the same pragmatic reasoning architecture.
-Instead, the common ground and mutual exclusitivity inferences we consider could be computed separately and combined in a more heuristic fashion.
+Instead, the common ground and mutual exclusivity inferences we consider could be computed separately and combined in a more heuristic fashion.
 A listener could integrate these two independent inferences in an additive manner, weighting the sources of information by some ratio $\phi$.
 $\phi$ is then a bias to prefer one type of inference relative to the other.
-We formalize this alternative hypothesis as a  **mixture model**.
-
-The **integration** and **mixture** models have potentially different implications for developmental change.
-The **integration model** assumes that the process by which information is integrated remains constant across development.
+We formalize this alternative hypothesis as a **biased model**.
+
+The **rational integration** and **biased integration** models have potentially different implications for developmental change.
+The **rational integration model** assumes that the process by which information is integrated remains constant across development.
 What changes is children's sensitivity to different cues: semantic knowledge, their expectations about speaker informativeness, and their sensitivity to common ground.
-The **mixture model** alternatively posits that there is some bias or preference for one information source, and this bias could change across development.
-This **developmental mixture model**  makes the same assumptions about developmental change in sensitivities to individual information sources as the **integration model** but, in addition, assumes that the way that the mutual exclusivity and the common ground inference are combined changes over time.
-This model is structurally identical to the **mixture model** but the mixture parameter $\phi$ is a function of age, which we model via a logistic-linear model: $\phi_i = \text{logistic}(\beta^\phi_0 + i \cdot \beta^\phi_1)$, whose parameters we infer via Bayesian inference.
+The **biased integration model** alternatively posits that there is some bias or preference for one information source, and this bias could change across development.
+This **developmental bias model**  makes the same assumptions about developmental change in sensitivities to individual information sources as the **rational integration model** but, in addition, assumes that the way that the mutual exclusivity and the common ground inference are combined changes over time.
+This model is structurally identical to the **biased model** but the bias parameter $\phi$ is a function of age, which we model via a logistic-linear model: $\phi_i = \text{logistic}(\beta^\phi_0 + i \cdot \beta^\phi_1)$, whose parameters we infer via Bayesian inference.
 
@@
 2).
-Now, in addition, we incorporate the data from Experiment 3 to additionally constrain these parameters as well as inform the mixture parameter for the mixture models (see Figure \@ref(fig:bda)).
-
-### Integration model
+Now, in addition, we incorporate the data from Experiment 3 to additionally constrain these parameters as well as inform the bias parameter for the **biased models** (see Figure \@ref(fig:bda)).
+
+### Rational integration model
 
@@
 
-The **integration model** in this section differs from the integration model in the [prediction section](#prediction) only in that the parameter distributions are now additionally informed by the data from Experiment 3.
-Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the Appendix show how the parameter distributions differ between the prediction and the explanation version of the **integration model**.
+The **rational integration model** in this section differs from the rational integration model in the [prediction section](#prediction) only in that the parameter distributions are now additionally informed by the data from Experiment 3.
+Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the Appendix show how the parameter distributions differ between the prediction and the explanation version of the **rational integration model**.
 Semantic knowledge and speaker informativeness have similar posterior distributions when taking into account all the data compared to when estimating these parameters only based on Experiment 1 and 2.
@@
 The code to run the model can be found in the associated online repository (file: `webppl/explanation_integration_model.wppl`).
-Figure \@ref(fig:fig9) shows model predictions for the **integration model** in comparison to the data from Experiment 3.
+Figure \@ref(fig:fig9) shows model predictions for the **rational integration model** in comparison to the data from Experiment 3.
 
 ```{r fig9, include = T, cache = T,  fig.cap = "Explaining information integration across development.
-Model predictions based on the integration model.
+Model predictions based on the rational integration model.
 Colored lines show developmental trajectories for each familiar object and condition based on 300 random draws from the model posterior distribution.
@@
 
-### Mixture model
-
-In the **mixture model** the two inferences (common ground and mutual exclusivity) are computed in the same way as in in the **integration model**.
-Subsequently, they are weighted by the mixture parameter $\phi$:
+### Biased model
+
+In the **biased model** the two inferences (common ground and mutual exclusivity) are computed in the same way as in in the **rational integration model**.
+Subsequently, they are weighted by the bias parameter $\phi$:
 
 \begin{equation}
-P^{mixture}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)
+P^{biased}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)
 (\#eq:mix1)
@@
 The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`).
-The posterior distribution for the mixture parameter $\phi$ is shown in figure \@ref(fig:fig10)A.
+The posterior distribution for the bias parameter $\phi$ is shown in figure \@ref(fig:fig10)A.
 It suggests that the mutual exclusivity inference is weighted as slightly more important compared to the common ground inference.
@@
 
-### Developmental mixture model
-
-For this model, we make the mixture parameter $\phi$ as a logistic-linear function of age-- $\phi_i = \text{logistic}(\beta^\phi_0 + i \cdot \beta^\phi_1)$ --- and estimate the intercept and slope that yield the best model predictions compared to the data from Experiment 3.
-The **developmental mixture model** is then:
+### Developmental bias model
+
+For this model, we make the bias parameter $\phi$ as a logistic-linear function of age-- $\phi_i = \text{logistic}(\beta^\phi_0 + i \cdot \beta^\phi_1)$ --- and estimate the intercept and slope that yield the best model predictions compared to the data from Experiment 3.
+The **developmental bias model** is then:
 
 \begin{equation}
-P^{dev\_mixture}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i) \cdot P(r \mid \rho_i)
+P^{dev\_bias}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i) \cdot P(r \mid \rho_i)
 (\#eq:devmix)
@@
 The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`).
-Figure \@ref(fig:fig10)B visualizes the developmental trajectory of the mixture parameter.
+Figure \@ref(fig:fig10)B visualizes the developmental trajectory of the bias parameter.
 Based on this model, the common ground inference seems to decrease in importance compared to the mutual exclusivity inference with age.
@@
 
-```{r fig10, include = T, fig.cap = "Mixture component for the mixture model (A) and the developmental mixture model (B).
-(A) shows the posterior distribution of the mixture component and (B) shows developmental trajectories for the mixture component based on 300 random draws from the posterior distribution for intercept and slope.", fig.width=10, fig.height = 4, }
+```{r fig10, include = T, fig.cap = "Bias parameter for the biased model (A) and the developmental bias model (B).
+(A) shows the posterior distribution of the bias parameter and (B) shows developmental trajectories for the bias parameter based on 300 random draws from the posterior distribution for intercept and slope.", fig.width=10, fig.height = 4, }
 ggarrange(plot_mixture, plot_dev_mixture,  labels = c("A","B"), nrow = 1)
@@
 Figure \@ref(fig:fig11) shows correlations between model predictions and the data, each binned by year and by object.
-Even though both mixture models have more free parameters then the **integration model**, the **integration model** shows the highest correlation in all age groups, though model predictions and data are closely aligned for all models.
+Even though both biased models have more free parameters then the **rational integration model**, the **rational integration model** shows the highest correlation in all age groups, though model predictions and data are closely aligned for all models.
 Next we directly compared models based using Bayes factors (see Table \@ref(tab:table6)).
-We also included the prediction **integration model** into this analysis.
+We also included the prediction **rational integration model** into this analysis.
 
 Perhaps unsurprisingly, we see that informing the parameters for semantic knowledge, speaker informativeness and common ground sensitivity by the data from Experiment 3 greatly improves the model fit (comparison: integration (explanation) vs integration (prediction)).
-We also see that the explanation **integration model** provides, by far, the best fit to the data compared to the two **mixture models**, even though the integration model has fewer free parameters than the mixture model.
-Interestingly, the prediction **integration model** also had a better fit, even though its parameters were not constrained by the data from Experiment 3.
-When comparing the two **mixture models** directly, we see that an age sensitive mixture parameter did not result in a substantially better fit, providing additional evidence that the integration process itself is not changing across development.
-
-This analysis shows that the inference and integration processes described by the **integration model** accurately capture the data and also explain information integration better compared to the additive **mixture models**.
+We also see that the explanation **rational integration model** provides, by far, the best fit to the data compared to the two **biased models**, even though the rational integration model has fewer free parameters than the **biased model**.
+Interestingly, the prediction **rational integration model** also had a better fit, even though its parameters were not constrained by the data from Experiment 3.
+When comparing the two **biased models** directly, we see that an age sensitive bias parameter did not result in a substantially better fit, providing additional evidence that the integration process itself is not changing across development.
+
+This analysis shows that the inference and integration processes described by the **rational integration model** accurately capture the data and also explain information integration better compared to the additive **biased models**.
 As a consequence, we may say that instead of being biased towards one type of inference, children are rationally integrating all the information sources available.
@@
 plot_cor_model_exp <- readRDS( "../saves/corr_model_data_exp.rds")%>%
-  mutate(model = factor(model, levels = c("integration", "mixture", "developmental mixture")))
+  mutate(model = fct_recode(model, 
+                            "biased" = "mixture",
+                            "developmental bias" = "developmental mixture"),
+         model = factor(model, levels = c("integration", "biased", "developmental bias")))
 
@@
                             "integration (explanation) vs integration (prediction)" = "fb_vs_free",
-                            "integration (explanation) vs mixture" = "fb_vs_mixture",
-                            "integration (prediction) vs mixture" = "free_vs_mixture",
-                            "integration (explanation) vs developmental mixture" = "fb_vs_dev_mixture",
-                            "integration (prediction) vs developmental mixture" = "free_vs_dev_mixture",
-                            "developmental mixture vs mixture" = "dev_mixture_vs_mixture"),
+                            "integration (explanation) vs biased" = "fb_vs_mixture",
+                            "integration (prediction) vs biased" = "free_vs_mixture",
+                            "integration (explanation) vs developmental bias" = "fb_vs_dev_mixture",
+                            "integration (prediction) vs developmental bias" = "free_vs_dev_mixture",
+                            "developmental bias vs biased" = "dev_mixture_vs_mixture"),
         `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%
@@
 As a start, we described mutual exclusivity as a pragmatic inference, which takes in children's emerging semantic knowledge and their expectations about how informative a speaker is.
-The **integration model** assumes that this inference is then flexibly integrated with children's developing sensitivity to common ground.
+The **rational integration model** assumes that this inference is then flexibly integrated with children's developing sensitivity to common ground.
 
@@
 We found a very close alignment of the model predictions and the data across the entire age range.
-Furthermore, the **integration model** provided a better fit to the data compared to a number of lesioned models, which selectively omitted one type of information.
+Furthermore, the **rational integration model** provided a better fit to the data compared to a number of lesioned models, which selectively omitted one type of information.
 These results suggest that children flexibly integrate all available information.
@@
 In the final section, we studied which process best explained children's information integration.
-We compared the **integration model** to a **mixture model** which assumed that children are biased towards one type of inference, and a **developmental mixture model** that assumed that the bias could change across development.
-We found that the **integration model** better explained the data compared to both of these mixture models, even though the mixture models had more free parameters.
+We compared the **rational integration model** to a **biased model** which assumed that children are biased towards one type of inference, and a **developmental bias model** that assumed that the bias could change across development.
+We found that the **rational integration model** better explained the data compared to both of these biased models, even though the biased models had more free parameters.
 In sum, we found that children's integration of semantic and pragmatic information during word learning is best described as a form of Bayesian social inference.
@@
 In the following, we visualize the model parameters for semantic knowledge, speaker informativeness and common ground sensitivity.
-Please note that the alternative lesion models presented in the prediction section used the same parameter distributions as the prediction **integration model**.
+Please note that the alternative lesion models presented in the prediction section used the same parameter distributions as the prediction **rational integration model**.
 
@@
   item_params %>% mutate(model = "integration (prediction)"),
-  item_params_mixture %>% mutate(model = "mixture"),
-  item_params_dev_mixture %>% mutate(model = "developmental mixture")
+  item_params_mixture %>% mutate(model = "biased"),
+  item_params_dev_mixture %>% mutate(model = "developmental bias")
 )%>%
-  mutate(model = factor(model, levels = c("integration (prediction)","integration (explanation)", "mixture","developmental mixture")))
+  mutate(model = factor(model, levels = c("integration (prediction)","integration (explanation)", "biased","developmental bias")))
 
@@
   global_params %>% mutate(model = "integration (prediction)"),
-  global_params_mixture %>% mutate(model = "mixture"),
-  global_params_dev_mixture %>% mutate(model = "developmental mixture")
+  global_params_mixture %>% mutate(model = "biased"),
+  global_params_dev_mixture %>% mutate(model = "developmental bias")
 )%>%
@@
                                "speaker informativeness" = "speaker_optimality"))%>%
-  mutate(model = factor(model, levels = c("integration (prediction)","integration (explanation)", "mixture","developmental mixture")))
+  mutate(model = factor(model, levels = c("integration (prediction)","integration (explanation)", "biased","developmental bias")))
 

### 2020-08-06 paper/manuscript.Rmd
add rmd paper

---
title             : "How young children integrate information sources to infer the meaning of words"
shorttitle        : "Rational information integration in children"

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2,*"
    corresponding : yes    # Define only one corresponding author
    address       : "Leipzig Research Center for Early Child Development, Jahnallee 59, 04109 Leipzig, Germany"
    email         : "manuel.bohn@uni-leipzig.de"
  - name          : "Michael Henry Tessler"
    affiliation   : "3,*"
  - name          : "Megan Merrick"
    affiliation   : "1"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
  - id            : "2"
    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
  - id            : "3"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
  - id            : "*"
    institution   : "These authors contributed equally to this work"

abstract: |
  Before formal education begins, children typically acquire a vocabulary of thousands of words. This learning process requires the use of many different     information sources in their social environment, including their current knowledge state as well as the context in which they hear words used. How is this information integrated? We specify a model according to which children consider all available information sources and integrate them via Bayesian inference. This model accurately predicted 2-to-5 year-old children’s word learning across a range of experimental conditions. Model comparison suggests that the integration process is stable across development and that the main locus of development is an increased sensitivity to individual information sources. We present a quantitative developmental theory of information integration for language learning, embedded in a larger framework that grounds language use and learning in social cognition.

keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"
wordcount         : "X"

bibliography      : "library.bib"
csl: nature.csl

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Humans rely on language for communication, making language acquisition a key learning objective of early childhood [@tomasello2018natural]. A central problem in language learning is referent identification: To learn the conventional symbolic relation between a word and an object, the child has to determine the intended referent of the word. Referents can only be identified in an inferential manner by reasoning about the speaker’s intentions [@bohn2019pervasive]. That is, the child has to infer what the speaker is communicating about based on information sources in the social context of the utterance.

From early on in development, children use a number of different mechanisms to harness such social-contextual information sources [@bohn2019pervasive; @clark2009first; @bloom2002children].

expand (more stuff on ME - talk about interplay of word knowledge and inference)
For example, children expect speakers to use novel words for unknown objects [@markman1988children], (use pre-existing word knowledge and combine this with inferential process by which the novel word is assumed to go with the novel object footnote(the nature of this inference is debated, we focus on one version)). Extensively studied, early developing

expand (more about informativeness etc?)
to talk about objects that are relevant [@frank2014inferring; @schulze20133],

(mention common ground, cite and talk about more)
new in context [@akhtar1996role], or related to the ongoing conversation [@sullivan2016discourse;@horowitz2015young] cite the other gang. Mention preference and somehow weave in the other gang + computational models.

These mechanisms, however, have largely been investigated in isolation. The picture of the learning process that emerges is that of a “bag of tricks”: mechanisms that operate (and develop) independently from one another [@bloom2002children]. Yet in natural social interaction, many sources of information are present [@bergelson2017nature;@frank2013social]. -- childs needs to integrate the different inforamtion sources. talk about braodly speaking pragmatic theories of language development that solve this problem: grice, sperber tomasello: social inference based on multiple inforamtion sources. the actual process of inforamtion integration is, however, described only in vague terms -- As a consequence, we have no explicit and quantitative theory of how the different word learning mechanisms can be integrated. Quantitative framework allows directly testing and comparing different hypothesis, a feature we use later on.

We present a theory of this integration process. Information sources serve different functional roles, all part of an integrated social inference process [@sperber2001relevance; @grice1991studies; @shafto2012learning]. Children use all available information to make inferences about the intentions behind a speaker’s utterance, which then leads them to correctly identify referents in the world and learn conventional word–object mappings. 
-- mention that this is an old idea, but that the theories were vague with respect to the intergration process --

We formalize this process and how it develops in a computational cognitive model [@frank2012predicting; @goodman2016pragmatic; @oberauer2019addressing], allowing us to quantify how well this theory predicts children’s actual learning in complex situations as well as to compare it directly to alternative theories. We consider theoretical competitors according to which children either ignore some information sources or process them in isolation.

To empirically test the predictive and explanatory power of the model, we focus on three information sources that operate on different timescales: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children]. While (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development. This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word]. We jointly manipulated these information sources and tested how well different theories predicted children’s behavior.

-- say what we did, first look at predictive pwoer of the model and whether children use all the available information. Then look at the intergration proceess itself and use models to decide between different processes by which information could be integrated. --

```{r fig1, include = T, fig.align = "center", fig.cap = "Experimental task and model. (A and B) Screenshots from the experimental task. (i) The speaker encounters one object and then leaves the scene (ii). While the speaker is away, a second object appears (iii), when returning, the speaker uses a novel word to request an object (iv). Sections (i) to (iii) establish common ground between the speaker and the listener, in that one object is new in context (green). The request in (iv) licenses an inference based on expectations about how informative speakers are (red). Listeners' semantic knowledge enters the task because the identity of the  known object on one of the tables is varied from well-known objects like a duck to relatively unfamiliar objects like a chess pawn (total of 12 objects - blue). (A) shows the condition in which common ground information is congruent (i.e. point to the same object) with speaker informativeness and (B) shows the incongruent condition. The congruent and incongruent conditions are each paired with the 12 known objects, resulting in 24 unique conditions. (C to E) show developmental trajectories for each information source, estimated from separate experiments (see supplement). (F) gives the model equation for the rational integration model and links information sources to model parameters.", out.width="100%"}
knitr::include_graphics("./figures/figure1.png")
```
To test the model, we constructed a word learning paradigm (Fig. 1) in which children interacted on a table computer with a series of storybook speakers [@frank2016using]. The speakers used novel words (e.g., wug) in the context of two potential referents. This situation is depicted in Fig. 1A-iv, in which a speaker (here, a frog) appears with a known object (a duck, left) and an unfamiliar object (the diamond-shaped object, right). To identify the referent, the child could rely upon the three information sources described above. First, they may infer that a cooperative speaker would have used the word duck to refer to the known object (the duck); the fact that the speaker did not say duck then suggests that the speaker is most likely referring to a different object (the unfamiliar object). Thus, the listener can infer the referent of the novel word by assuming that the speaker is a rational agent who chooses the most informative words to refer to objects [@frank2014inferring]. Second, the child may rely upon what has already been established in the common ground with the speaker. Listeners expect speakers to communicate about things that are new to the common ground [@akhtar1996role]. Thus, the inference about the novel word referring to the unfamiliar object also depends on which object is new in context (Fig. 1A and B i-iii). Finally, the child may rely upon their previously acquired semantic knowledge, that is, how sure they are that the known object is called duck. If the known object is something less familiar, such as a chess piece (e.g., a pawn), a 3-year-old child may draw a weaker inference, if they draw any inference at all [@lewis2020-me]. Taken together, the child has the opportunity to integrate their assumptions about (1) informative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge. In some versions of the experiment, these information sources were aligned (Fig. 1A) but in some they were in conflict (Fig. 1B).

Our rational integration model arbitrates between information sources via Bayesian inference (Fig. 1F). A listener (L1) reasons about the referent of a speaker's (S1) utterance. This reasoning is contextualized by the prior probability of each referent $\rho$ which we take to be a function of the common ground shared between the listener and the speaker. To decide between referents, the listener (L1) reasons about what a rational speaker (S1) with informativeness $\alpha$ would say given an intended referent. This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one. The informativity of each utterance is given by imagining which referent a listener who interprets words according to their literal semantics (what we call a literal listener, L0), would infer upon hearing the utterance. Naturally, this reasoning depends on what kind of semantic knowledge (for object j) $\theta$~j~ the speaker ascribes to the (literal) listener. Taken together, this model provides a quantitative theory of information integration during language learning. Furthermore, the model presents an explicit and substantive theory of development. It assumes that, while children’s sensitivity to the individual information sources increases with age, the way integration proceeds remains constant [@bohn2019pervasive]. In the model, this is accomplished by making the parameters capturing sensitivity to speaker informativeness ($\alpha$~i~, Fig. 1D), the common ground ($\rho$i, Fig. 1C), and object specific semantic knowledge ($\theta$~i,j~, Fig. 1E) a function of the child’s age.

# Results

## Predicting information integration accross development

We tested the model in its ability to predict children’s actual behavior - at an age (between 2 and 5 years) at which they learn language at an exponential rate [@bloom2002children]. We estimated children’s (N=148) developing sensitivity to individual information sources in separate experiments (see Fig. 1C-E). We then generated - and pre-registered [26] - parameter-free, quantitative, *a priori* model predictions (developmental trajectories) representing the model's expectations about how children should behave in a new situation in which all three information sources had to be integrated. We generated model predictions for 24 experimental conditions: 12 objects of different familiarities (requiring different levels of semantic knowledge), with novelty either conflicting or coinciding; Fig. 1. We compared these predictions to newly collected data from N = 220 children from the same age range. The results showed a very close alignment between model predictions and the data across the entire age range and explained 79% of the variance in the data (Figs. 2 and S6).

Next, we formalized the alternative view that children selectively ignore information sources in the form of three lesioned models (Fig. 2). These models assume that children follow the heuristic “ignore X” (with X being one of the information sources) when multiple information sources are presented together.

The marginally less-complex *no word knowledge model* uses the same model architecture. It takes in expectations about speaker informativeness and common ground, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge). The object specific parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model. In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects). The *no word knowledge model* takes in the overall trajectory for semantic knowledge but ignores object-specific variation. That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.

We found little support taht children make inferences following one of the heuristic models. In fact, the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Bayesian model comparison via marginal likelihood of the data, [@lee2014bayesian], Fig. 2). Thus, children considered all available information sources.

(ref:figlab2) **Predicting information integration**. Correlation between model predictions and child inference data for all 24 conditions and for each age group (binned by year) for the rational integration model and the three lesioned models. Horizontal and vertical error bars show 95% HDI. Inset shows an example of model predictions as developmental trajectories (see Fig. 3). The no word knowledge model includes developmental change for overall vocabulary development but ignores the identity of the known object. The no common ground model assumes that children ignore information from common ground and the no speaker informativeness model assumes that children ignore inferences that are licensed by expectations about informative communication. BF~10~ gives the Bayes Factor in favor of the integration model based on the marginal likelihood of the data under each model.

```{r fig2, include = T, fig.align = "center", fig.cap = "(ref:figlab2)", out.width="100%"}

knitr::include_graphics("./figures/figure2.png")
```

## Explaining the process of information integration

The fact that children took into account all the available information sources may be surprising, but does not rule out the alternative view that the different information sources are processed independently from one another. It is equally plausible that children compute separate inferences based on a subset of the available information and then integrate them by weighting them, for example according to some ratio $\phi$. On this view, children would also consider all information sources, but they would be biased towards some of them. We formalized this alternative view as a biased integration model.

The parameter $\phi$ in the biased integration model is unknown ahead of time and has to be estimated based on the experimental data. That is, in contrast to the rational integration model, the biased integration model does not allow to make *a priori* predictions about new data in the way we describe above. For the model comparison, we therefore constrained the parameters in the rational integration model by the experimental data as well. As a consequence, both models use all the information available to constrain their parameters.

Even though the biased integration model makes reasonable predictions, the rational integration model presents a much better fit to the data, both in terms of correlation and marginal likelihood of the data (Fig. 3). A final amendment of the biased integration view could be that children are in fact biased towards some information sources, but this bias changes with age. (In contrast, to the rational integration model which assumes that the integration process itself does not change with age [@bohn2019pervasive]). To decide between these two perspectives, we formalized a developmental bias model, which is structurally identical to the biased integration model but in which the parameter $\phi$ changes with age. When directly compared, the rational integration model again provided a much better explanation of the data and the underlying developmental process (Fig. 3). Interestingly, the rational integration model also outperformed both bias models when its parameters are not constrained by the experimental data (see supplement).

(ref:figlab3) **Explaining information integration across development**. (A) Model predictions from the rational integration model (colored lines) next to the behavioral data (dotted black lines with 95% CI in gray) for all 24 experimental conditions. Top row (blue) shows conditions in which common ground information is congruent with speaker informativeness, bottom row (red) shows conditions in which they are incongruent. Known objects are ordered based on their rated age of acquisition (left to right). Light dots represent individual data points. (B) Correlations between model predictions binned by age and condition for the integration model and the two mixture models. Vertical and horizontal error bars show 95% HDIs. BF~10~ gives the Bayes Factor in favor of the rational integration model based on the marginal likelihood of the data under each model.

```{r fig3, include = T, fig.align = "center", fig.cap = "(ref:figlab3)", out.width="100%"}
knitr::include_graphics("./figures/figure3.png")
```

# Discussion

These findings show that young children can flexibly integrate multiple information sources during language learning, even from relatively early in development. To answer the question of how they do so, we presented a formal cognitive model that assumes that information sources are rationally integrated via Bayesian inference. This model accurately predicted children’s behavior between 2 and 5 years of age and provided a better explanation of the integration process and its development compared to a range of competitor models that either neglected or prioritized some information sources.

Replicate with other languages and other cultural settings.

more explicit model of common ground (see perspective taking work mcc)
integrate process of word learning itself via cross-situational learning

The model is derived from a more general framework for pragmatic inference, which has been used to explain a wide variety of phenomena in adults’ language use and comprehension [@monroe2017colors; @wang2016learning; @tessler2019language; @yoon_frank_tessler_goodman_2018]. Thus, it can be generalized in a natural way to capture word learning in contexts that offer more, fewer, or different types of information [e.g. @bohn_tessler_merrick_frank_2019]. The flexibility of the framework stems from its conceptualization of human communication as a form of rational social action.

Connections to naive utility caluclus stuff?

As such, this work adds to theories that see the onto- and phylogenetic emergence of language as deeply rooted in social cognition.

# Methods

## Particiapnts

## Materials

## Procedure

## Data analysis

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2020-08-06 paper/supplementary_material.Rmd
add rmd paper

@@
   geom_jitter(data = plot_cg_data,aes(x = age_num, y= correct), width = .00, height = .01, alpha = .5)+
-  geom_line(data = plot_cg_samples, aes(x = age+min(prior_data$age_num), y = y, group = sample), size = .025)+
+  geom_line(data = plot_cg_samples, aes(x = age+min(prior_data$age_num), y = y, group = sample), alpha = .05)+
   geom_line(data = plot_cg_map, aes(x =age+min(prior_data$age_num), y = y), size = 1)+
@@
 
-```{r figa1, include = T, cache=T,  fig.cap = "Posterior distribution of intercept term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
+```{r figa1, include = T, cache=F,  fig.cap = "Posterior distribution of intercept term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
 
@@
 
-```{r figa2, include = T, cache=T,  fig.cap = "Posterior distribution of slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
+```{r figa2, include = T, cache=F,  fig.cap = "Posterior distribution of slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
 

### 2020-08-08 paper/manuscript.Rmd
ideas for expanded paper

@@
 Quantitative framework allows directly testing and comparing different hypothesis, a feature we use later on.
+
+intorduce previous work (including modelling work) looking at inforamtion integration: Mostly lingusitc with pragmatic infotmation - however, no manipulation of lingusitc ususally.
+
+More generally talk about quantitative models of child developmetn (review paper   gopnik and bonawitz, Sophie) and their usefulness in theory building.
 

### 2020-08-21 paper/manuscript.Rmd
reformat paper

--- 2020-08-06 paper/manuscript.Rmd
@@
   - name          : "Manuel Bohn"
-    affiliation   : "1,2,*"
+    affiliation   : "1,*"
     corresponding : yes    # Define only one corresponding author
-    address       : "Leipzig Research Center for Early Child Development, Jahnallee 59, 04109 Leipzig, Germany"
-    email         : "manuel.bohn@uni-leipzig.de"
+    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
+    email         : "manuel_bohn@eva.mpg.de"
   - name          : "Michael Henry Tessler"
-    affiliation   : "3,*"
+    affiliation   : "2,*"
   - name          : "Megan Merrick"
-    affiliation   : "1"
+    affiliation   : "3"
   - name          : "Michael C. Frank"
-    affiliation   : "1"
+    affiliation   : "3"
 
@@
   - id            : "1"
+    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
+  - id            : "2"
+    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
+  - id            : "3"
     institution   : "Department of Psychology, Stanford University"
-  - id            : "2"
-    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
-  - id            : "3"
-    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
   - id            : "*"
@@
 library("papaja")
+library("tidyverse")
+library("coda")
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+
 ```
@@
 A central problem in language learning is referent identification: To learn the conventional symbolic relation between a word and an object, the child has to determine the intended referent of the word.
-Referents can only be identified in an inferential manner by reasoning about the speaker’s intentions [@bohn2019pervasive].
+Referents can only be identified in an inferential manner by reasoning about the speaker’s intentions [@bohn2019pervasive; @bruner1983child; @clark2009first; @tomasello2009constructing].
 That is, the child has to infer what the speaker is communicating about based on information sources in the social context of the utterance.
@@
 From early on in development, children use a number of different mechanisms to harness such social-contextual information sources [@bohn2019pervasive; @clark2009first; @bloom2002children].
+For example, children expect speakers to use novel words for unknown objects [@clark1987principle; @markman1988children; @carey1978acquiring; @halberda2003development], to talk about objects that are relevant [@frank2014inferring; @schulze20133], new in context [@akhtar1996role; @diesendruck2004two], or related to the ongoing conversation [@bohn_le_peloquin_koymen_frank_2020; @sullivan2016discourse; @horowitz2015young].
+These different mechanisms, however, have largely been described and theorized about in isolation.
+The picture of the learning process that emerges is that of a “bag of tricks”: mechanisms that operate (and develop) independently from one another [@bloom2002children].
+As such, this view of the learning process does not capture the complexity of natural social interaction during which many sources of information are present [@bergelson2017nature;@frank2013social].
+Theses information sources need to be integrated in order to accurately infer a speaker's intention.
 
-expand (more stuff on ME - talk about interplay of word knowledge and inference)
-For example, children expect speakers to use novel words for unknown objects [@markman1988children], (use pre-existing word knowledge and combine this with inferential process by which the novel word is assumed to go with the novel object footnote(the nature of this inference is debated, we focus on one version)).
-Extensively studied, early developing
-
-expand (more about informativeness etc?)
-to talk about objects that are relevant [@frank2014inferring; @schulze20133],
-
-(mention common ground, cite and talk about more)
-new in context [@akhtar1996role], or related to the ongoing conversation [@sullivan2016discourse;@horowitz2015young] cite the other gang.
-Mention preference and somehow weave in the other gang + computational models.
-
-These mechanisms, however, have largely been investigated in isolation.
-The picture of the learning process that emerges is that of a “bag of tricks”: mechanisms that operate (and develop) independently from one another [@bloom2002children].
-Yet in natural social interaction, many sources of information are present [@bergelson2017nature;@frank2013social].
--- childs needs to integrate the different inforamtion sources.
-talk about braodly speaking pragmatic theories of language development that solve this problem: grice, sperber tomasello: social inference based on multiple inforamtion sources.
-the actual process of inforamtion integration is, however, described only in vague terms -- As a consequence, we have no explicit and quantitative theory of how the different word learning mechanisms can be integrated.
-Quantitative framework allows directly testing and comparing different hypothesis, a feature we use later on.
+When researchers do look at inforamtion integration in children [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers], they mostly focus on how children interpret an ambiguous referring expression in light of social-contextual information.
+In one of these studies [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it.
+The speaker, sitting on the opposite side of the display, saw only 3 of the compartments: the ball, the pen, and one of the glasses.
+When the speaker asked for "the glass", children had to integrate the semantics of the utterance with the perspective of the speaker to correctly infer which of the glasses - from their perspective - the speaker was referring to.
+This study, along with others, found that preschoolers use both information sources.
+What these studies do not do, however, is specify the process by which children integrate the different information sources.
+When discussing their results, authors refer to social-pragmatic theories of language use and learning [@grice1991studies; @sperber2001relevance; @clark1996using; @clark2009first; @tomasello2009constructing], all of which assume that information is integrated as part of a social inference process, but none of which clearly defines the process.
+As a consequence, we have no explicit and quantitative theory of how different information sources (and word learning mechanisms) are integrated.
 
 We present a theory of this integration process.
-Information sources serve different functional roles, all part of an integrated social inference process [@sperber2001relevance; @grice1991studies; @shafto2012learning].
+Following social-pragmatic theories of language learning [@clark2009first; @tomasello2009constructing], our theory is based on the following premises: information sources serve different functional roles, all part of an integrated social inference process [@clark1996using; @grice1991studies; @shafto2012learning; @sperber2001relevance].
 Children use all available information to make inferences about the intentions behind a speaker’s utterance, which then leads them to correctly identify referents in the world and learn conventional word–object mappings.
--- mention that this is an old idea, but that the theories were vague with respect to the intergration process --
+We formalize the computational steps that underlie this inference process in a cognitive model [@frank2012predicting; @goodman2016pragmatic; @oberauer2019addressing].
+This model makes quantitative predictions about how children should integrate information sources - predictions we can test against new data.
+It also allows us to test alternative theories about *whether* and *how* information is integrated.
+Finally, we can compare alternative views on how the integration process itself *develops*.
 
-We formalize this process and how it develops in a computational cognitive model [@frank2012predicting; @goodman2016pragmatic; @oberauer2019addressing], allowing us to quantify how well this theory predicts children’s actual learning in complex situations as well as to compare it directly to alternative theories.
-We consider theoretical competitors according to which children either ignore some information sources or process them in isolation.
-
-To empirically test the predictive and explanatory power of the model, we focus on three information sources that operate on different timescales: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].
+To test this model, we focus on three information sources that play an integral part in theorizing about language use and learning and operate on different timescales: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].
 While (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development.
 This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word].
-We jointly manipulated these information sources and tested how well different theories predicted children’s behavior.
-
--- say what we did, first look at predictive pwoer of the model and whether children use all the available information.
-Then look at the intergration proceess itself and use models to decide between different processes by which information could be integrated.
---
 
@@
 ```
-To test the model, we constructed a word learning paradigm (Fig.
-1) in which children interacted on a table computer with a series of storybook speakers [@frank2016using].
-The speakers used novel words (e.g., wug) in the context of two potential referents.
+
+To test the predictive and explanatory power of our model, we developed an world-learning paradigm in which we jointly manipulated these three information sources (Fig.
+1).
+Children interacted on a tablet computer with a series of storybook speakers [@frank2016using].
+The speakers used novel words (e.g., "wug") in the context of two potential referents.
 This situation is depicted in Fig.
@@
 Second, the child may rely upon what has already been established in the common ground with the speaker.
-Listeners expect speakers to communicate about things that are new to the common ground [@akhtar1996role].
+Listeners expect speakers to communicate about things that are new to the common ground [@akhtar1996role; @diesendruck2004two].
 Thus, the inference about the novel word referring to the unfamiliar object also depends on which object is new in context (Fig.
 1A and B i-iii).
-Finally, the child may rely upon their previously acquired semantic knowledge, that is, how sure they are that the known object is called duck.
+Finally, the child may rely upon their previously acquired semantic knowledge, that is, how sure they are that the known object is called "duck".
 If the known object is something less familiar, such as a chess piece (e.g., a pawn), a 3-year-old child may draw a weaker inference, if they draw any inference at all [@lewis2020-me].
 Taken together, the child has the opportunity to integrate their assumptions about (1) informative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge.
-In some versions of the experiment, these information sources were aligned (Fig.
+In some versions of the experiment, some of these information sources were aligned (Fig.
 1A) but in some they were in conflict (Fig.
@@
 
-Our rational integration model arbitrates between information sources via Bayesian inference (Fig.
-1F).
-A listener (L1) reasons about the referent of a speaker's (S1) utterance.
+Our *rational integration model* arbitrates between information sources via Bayesian inference (see Fig.
+1F for model formula).
+A listener ($L_{1}$) reasons about the referent of a speaker's ($S_{1}$) utterance.
 This reasoning is contextualized by the prior probability of each referent $\rho$ which we take to be a function of the common ground shared between the listener and the speaker.
-To decide between referents, the listener (L1) reasons about what a rational speaker (S1) with informativeness $\alpha$ would say given an intended referent.
+To decide between referents, the listener ($L_{1}$) reasons about what a rational speaker ($S_{1}$) with informativeness $\alpha$ would say given an intended referent.
 This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one.
-The informativity of each utterance is given by imagining which referent a listener who interprets words according to their literal semantics (what we call a literal listener, L0), would infer upon hearing the utterance.
+The informativity of each utterance is given by imagining which referent a listener who interprets words according to their literal semantics (what we call a literal listener, $L_{0}$), would infer upon hearing the utterance.
 Naturally, this reasoning depends on what kind of semantic knowledge (for object j) $\theta$~j~ the speaker ascribes to the (literal) listener.
@@
 Furthermore, the model presents an explicit and substantive theory of development.
-It assumes that, while children’s sensitivity to the individual information sources increases with age, the way integration proceeds remains constant [@bohn2019pervasive].
+It assumes that, while children’s sensitivity to the individual information sources increases with age, the way integration proceeds remains constant [@bohn2019pervasive; @bohn_tessler_merrick_frank_2019].
 In the model, this is accomplished by making the parameters capturing sensitivity to speaker informativeness ($\alpha$~i~, Fig.
-1D), the common ground ($\rho$i, Fig.
+1D), the common ground ($\rho$~i~, Fig.
 1C), and object specific semantic knowledge ($\theta$~i,j~, Fig.
@@
 1C-E).
-We then generated - and pre-registered [26] - parameter-free, quantitative, *a priori* model predictions (developmental trajectories) representing the model's expectations about how children should behave in a new situation in which all three information sources had to be integrated.
+We then generated parameter-free, quantitative, *a priori* model predictions (developmental trajectories) representing the model's expectations about how children should behave in a new situation in which all three information sources had to be integrated.
 We generated model predictions for 24 experimental conditions: 12 objects of different familiarities (requiring different levels of semantic knowledge), with novelty either conflicting or coinciding; Fig.
@@
 We compared these predictions to newly collected data from N = 220 children from the same age range.
-The results showed a very close alignment between model predictions and the data across the entire age range and explained 79% of the variance in the data (Figs.
-2 and S6).
+The results showed a very close alignment between model predictions and the data across the entire age range.
+That is, the average developmental trajectories predicted by the model resembled the trajectories found in the data (Fig.
+S6).
+For a more quantitative analysis, we binned predictions and data by year and correlated them.
+We found a high correlation showing that the model explained 79% of the variance in the data (Fig.
+2).
+These results seem to support the assumption in the model that children consider all available information source.
+However, it is still possible that simpler models might make equally good or better predictions.
 
-Next, we formalized the alternative view that children selectively ignore information sources in the form of three lesioned models (Fig.
+Thus, we formalized the alternative view that children selectively ignore information sources in the form of three lesioned models (Fig.
 2).
@@
 
-The marginally less-complex *no word knowledge model* uses the same model architecture.
+The marginally less-complex *no word knowledge model* uses the same model architecture as the rational integration model.
 It takes in expectations about speaker informativeness and common ground, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge).
@@
 In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects).
-The *no word knowledge model* takes in the overall trajectory for semantic knowledge but ignores object-specific variation.
-That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.
+The no word knowledge model takes in the overall trajectory for semantic knowledge but ignores object-specific variation.
+That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.The *no common ground model* takes in object specific semantic knowledge and speaker informativeness but ignores common ground information.
+Instead of assuming that one object has a higher prior probability to be the referent because it is new in context, the speaker thinks that both objects are equally likely to be the referent.
+As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources.Finally, according to the *no speaker inforamtiveness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance.
+As a consequence, the inference is solely based on common ground expectations.
 
-We found little support taht children make inferences following one of the heuristic models.
-In fact, the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Bayesian model comparison via marginal likelihood of the data, [@lee2014bayesian], Fig.
+We found little support that children make inferences following one of the heuristic models.
+When using Bayesian model comparison via marginal likelihood of the data, [@lee2014bayesian], we find that the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Fig.
 2).
-Thus, children considered all available information sources.
+Taken together, we may conclude that children considered all available information sources.
 
@@
 
-The fact that children took into account all the available information sources may be surprising, but does not rule out the alternative view that the different information sources are processed independently from one another.
-It is equally plausible that children compute separate inferences based on a subset of the available information and then integrate them by weighting them, for example according to some ratio $\phi$.
-On this view, children would also consider all information sources, but they would be biased towards some of them.
-We formalized this alternative view as a biased integration model.
+The fact that children integrated all the available information sources may be surprising, but does not rule out that the integration process itself might be different from the one described in the rational integration model.
+Remember that this model assumes that all information sources enter into an integrated inference process.
+However, a more modular view seems equally plausible: children might compute separate inferences based on a subset of the available information and then integrate them by weighting them according to some ratio.
+This view would allow for the possibility that some information sources are considered to be more important than others.
+In other words, children might be biased towards some information sources (e.g.
+a 60:40 ratio).
+We formalized this alternative view as a *biased integration model*.
+This model assumes that semantic knowledge and expectations about speaker informativeness enter into one inference (mutual exclusivity inference [@markman1988children; @lewis2020-me; @clark1987principle]) while common ground information enters into a second one.
+The outcome of both processes are then weighted according to the parameter $\phi$.
+Like the rational integration model, this model takes in all available integration sources and assumes that they are integrated, the integration process itself, however, is construed in a different way.
 
@@
 For the model comparison, we therefore constrained the parameters in the rational integration model by the experimental data as well.
-As a consequence, both models use all the information available to constrain their parameters.
+As a consequence, both models use all the information available to constrain their parameters (see Fig.
+S4).
 
-Even though the biased integration model makes reasonable predictions, the rational integration model presents a much better fit to the data, both in terms of correlation and marginal likelihood of the data (Fig.
-3).
-A final amendment of the biased integration view could be that children are in fact biased towards some information sources, but this bias changes with age.
-(In contrast, to the rational integration model which assumes that the integration process itself does not change with age [@bohn2019pervasive]).
-To decide between these two perspectives, we formalized a developmental bias model, which is structurally identical to the biased integration model but in which the parameter $\phi$ changes with age.
-When directly compared, the rational integration model again provided a much better explanation of the data and the underlying developmental process (Fig.
-3).
-Interestingly, the rational integration model also outperformed both bias models when its parameters are not constrained by the experimental data (see supplement).
+```{r}
+mixture_parameter <- readRDS("../saves/mixture_mm.rds")
+
+phi <- mixture_parameter%>%
+  summarise(mode = estimate_mode(p_informative), 
+            lci = hdi_lower(p_informative), 
+            uci = hdi_upper(p_informative))
+```
+
+The biased integration model makes reasonable predictions that explain a large proportion of the variance in the data (Fig.
+3B).
+The parameter $\phi$ - indicating the bias to one of the inferences - was estimated to favor the mutual exclusivity inference (mode = `r phi%>%pull(mode)`; 95% HDI: `r phi%>%pull(lci)` - `r phi%>%pull(uci)`, see Fig.
+3B).
+However, the rational integration model presented a much better fit to the data, both in terms of correlation and marginal likelihood of the data (Fig.
+3B).
+Thus, a fully integrated - as opposed to a segmented, biased - integration process explains the data better.
+
+The rational integration model assumes that the integration process itself does not change with age [@bohn2019pervasive].
+That is, while children's sensitivity to each information source develops, the way they relate to one another remains the same.
+An alternative perspective would be to assume that the integration process itself changes with age.
+The biased integration model provides a way to think about developmental change in the integration process: Children are biased towards some information sources, but this bias itself changes with age.
+We formalize such an alternative view as a *developmental bias model* which is structurally identical to the biased integration model but in which the parameter $\phi$ changes with age.
+The model assumes that the importance of the different information sources changes with age.
+
+```{r}
+developmental_mixture_parameter <- readRDS("../saves/mixture_dmm.rds")
+
+phi_dev <- developmental_mixture_parameter%>%
+  filter(type == "slope")%>%
+  summarise(mode = estimate_mode(value), 
+            lci = hdi_lower(value), 
+            uci = hdi_upper(value))
+```
+
+The developmental bias model explains a substantial portion of the variance in the data (Fig.
+3B).
+The estimated developmental trajectory for the bias parameter $\phi$ (Fig.
+3B) suggests that younger children put a higher emphasis on common ground information, while older children rely more on the mutual exclusivity inference.
+Yet again, when we directly compare the competitor models, we find that the data is several orders of magnitude more likely under the rational integration model (Fig.
+3B).
+Interestingly, when we compare the rational integration model with its parameters not constrained by the experimental data (i.e.
+the "pure" prediction model described above), it also outperformed both bias models (see Fig.
+S10 and Tab.
+S6).
+Taken together, these results suggest that the integration process is best described as a) fully integrated and b) stable over time.
 
@@
 Light dots represent individual data points.
-(B) Correlations between model predictions binned by age and condition for the integration model and the two mixture models.
+(B) Correlations between model predictions binned by age and condition for the integration model and (C) the two mixture models.
 Vertical and horizontal error bars show 95% HDIs.
 BF~10~ gives the Bayes Factor in favor of the rational integration model based on the marginal likelihood of the data under each model.
+(D) Posterior distribution of the bias parameter in the biased integration model and 300 random draws from the posterior distribution of the intercept and slope for the bias parameter in the developmental bias model.
 
@@
 more explicit model of common ground (see perspective taking work mcc)
-integrate process of word learning itself via cross-situational learning
+
+integrate process of word learning itself via cross-situational learning [@frank2009using; @mcmurray2012word] dan yurovski work
 

### 2020-08-22 paper/manuscript.Rmd

@@
 
-When researchers do look at inforamtion integration in children [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers], they mostly focus on how children interpret an ambiguous referring expression in light of social-contextual information.
+When researchers do look at information integration in children [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers], they mostly focus on how children interpret an ambiguous referring expression in light of social-contextual information.
 In one of these studies [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it.

### 2020-08-22 paper/supplementary_material.Rmd

@@
 
-#### No mutual exclusivity model
-
-Finally, we consider a model that focuses only on common ground information and ignores the identity of the objects on the tables as well as any inferences their semantic knowledge of the familiar objects license.
-The predictions of this model correspond to the prior distribution over objects.
+#### No speaker informativeness model
+
+Finally, we consider a model that assumes that the speaker does not communicate in an informative way.
+This corresponds to $\alpha_i$ = 0, which causes the likelihood term to always be 1.
+As a consequence, this model also ignores semantic knowledge (which affects the likelihood term) and the predictions of this model correspond to the prior distribution over objects.
 
@@
 The correlation increased from 2- to 3-year-olds but then again dropped for 4-year-olds.
-The mis-match for the oldest age group is probably a consequence of the model making very extreme predictions in the congruent condition.
+The mismatch for the oldest age group is probably a consequence of the model making very extreme predictions in the congruent condition.
 This results from the fact that 4-year-olds show very high performance both the mutual exclusivity and common ground tasks.
@@
 The results show that the **rational integration model**, by far, outperformed all the other models.
-When comparing the lesioned models among each other, we see that models including the mutual exclusivity inference make better predictions compared to the **no mutual exclusivity model**.
+When comparing the lesioned models among each other, we see that the more information sources a model takes in, the better predictions it makes (roughly: **no word knowledge** > **no common ground** > **no speaker informativeness**.
 
@@
 plot_cor_model_pred <- readRDS( "../saves/corr_model_data_pred.rds")%>%
-  mutate(model = factor(model, levels = c("integration", "no word knowledge", "no common ground", "no mutual exclusivity")))
+  mutate(model = factor(model, levels = c("integration", "no word knowledge", "no common ground", "no speaker informativeness")))
 
@@
                             "integration vs no common ground" = "prag_vs_flat",
-                            "integration vs no mutual exclusivity" = "prag_vs_prior",
-                            "no word knowledge vs no mutual exclusivity" = "global_vs_flat",
-                            "no word knowledge vs no common ground" = "global_vs_prior",
-                            "no mutual exclusivity vs no common ground" = "flat_vs_prior"),
+                            "integration vs no speaker informativeness" = "prag_vs_prior",
+                            "no word knowledge vs no common ground" = "global_vs_flat",
+                            "no word knowledge vs no speaker informativeness" = "global_vs_prior",
+                            "no common ground vs no speaker informativeness" = "flat_vs_prior"),
         `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%

### 2020-08-25 paper/manuscript.Rmd
advance paper reformatting

@@
 The picture of the learning process that emerges is that of a “bag of tricks”: mechanisms that operate (and develop) independently from one another [@bloom2002children].
-As such, this view of the learning process does not capture the complexity of natural social interaction during which many sources of information are present [@bergelson2017nature;@frank2013social].
-Theses information sources need to be integrated in order to accurately infer a speaker's intention.
+As such, this view of the learning process does not capture the complexity of natural social interaction during which many sources of information are present [@bergelson2017nature; @frank2013social].
+Theses sources need to be integrated in order to accurately infer a speaker's intention.
 
@@
 We formalize the computational steps that underlie this inference process in a cognitive model [@frank2012predicting; @goodman2016pragmatic; @oberauer2019addressing].
-This model makes quantitative predictions about how children should integrate information sources - predictions we can test against new data.
-It also allows us to test alternative theories about *whether* and *how* information is integrated.
-Finally, we can compare alternative views on how the integration process itself *develops*.
+In the remainder of this paper, we rigorously test this theory by asking how well it serves the two purposes of any psychological theory: prediction and explanation [@shmueli2010explain; @yarkoni2017choosing].
+First, we use the model to make quantitative predictions about children's behavior in new situations - predictions we test against new data.
+Next, we test how well the model explains the integration process by comparing it to alternative models that make different assumptions about *whether* information is integrated, *how* it is integrated and how the integration process *develops*.
 
-To test this model, we focus on three information sources that play an integral part in theorizing about language use and learning and operate on different timescales: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].
-While (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development.
+We focus on three information sources that play an integral part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].
+These inforamtion sources operate on different timescales: while (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development.
 This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word].
+
+Our *rational integration model* arbitrates between information sources via Bayesian inference (see Fig.
+1F for model formula).
+A listener ($L_{1}$) reasons about the referent of a speaker's ($S_{1}$) utterance.
+This reasoning is contextualized by the prior probability of each referent $\rho$ which we take to be a function of the common ground shared between the listener and the speaker.
+To decide between referents, the listener ($L_{1}$) reasons about what a rational speaker ($S_{1}$) with informativeness $\alpha$ would say given an intended referent.
+This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one.
+The informativity of each utterance is given by imagining which referent a listener, who interprets words according to their literal semantics (what we call a literal listener, $L_{0}$), would infer upon hearing the utterance.
+Naturally, this reasoning depends on what kind of semantic knowledge (for object j) $\theta$~j~ the speaker ascribes to the (literal) listener.
+Taken together, this model provides a quantitative theory of information integration during language learning.
+Furthermore, the model presents an explicit and substantive theory of development.
+It assumes that, while children’s sensitivity to the individual information sources increases with age, the way integration proceeds remains constant [@bohn2019pervasive; @bohn_tessler_merrick_frank_2019].
+In the model, this is accomplished by making the parameters capturing sensitivity to speaker informativeness ($\alpha$~i~, Fig.
+1D), the common ground ($\rho$~i~, Fig.
+1C), and object specific semantic knowledge ($\theta$~i,j~, Fig.
+1E) a function of the child’s age.
 
@@
 
-To test the predictive and explanatory power of our model, we developed an world-learning paradigm in which we jointly manipulated these three information sources (Fig.
+To generate data to test the predictive and explanatory power of our model, we developed a world-learning paradigm in which we jointly manipulated the three information sources (Fig.
 1).
@@
 First, they may infer that a cooperative speaker would have used the word duck to refer to the known object (the duck); the fact that the speaker did not say duck then suggests that the speaker is most likely referring to a different object (the unfamiliar object).
-Thus, the listener can infer the referent of the novel word by assuming that the speaker is a rational agent who chooses the most informative words to refer to objects [@frank2014inferring].
+This basic inference is oftentimes referred to as a mutual exclusivity inference [@markman1988children; @halberda2003development].
+More generally speaking, the listener can infer the referent of the novel word by assuming that the speaker is a rational agent who chooses the most informative words to refer to objects [@clark1987principle; @frank2014inferring].
 Second, the child may rely upon what has already been established in the common ground with the speaker.
@@
 1B).
-
-Our *rational integration model* arbitrates between information sources via Bayesian inference (see Fig.
-1F for model formula).
-A listener ($L_{1}$) reasons about the referent of a speaker's ($S_{1}$) utterance.
-This reasoning is contextualized by the prior probability of each referent $\rho$ which we take to be a function of the common ground shared between the listener and the speaker.
-To decide between referents, the listener ($L_{1}$) reasons about what a rational speaker ($S_{1}$) with informativeness $\alpha$ would say given an intended referent.
-This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one.
-The informativity of each utterance is given by imagining which referent a listener who interprets words according to their literal semantics (what we call a literal listener, $L_{0}$), would infer upon hearing the utterance.
-Naturally, this reasoning depends on what kind of semantic knowledge (for object j) $\theta$~j~ the speaker ascribes to the (literal) listener.
-Taken together, this model provides a quantitative theory of information integration during language learning.
-Furthermore, the model presents an explicit and substantive theory of development.
-It assumes that, while children’s sensitivity to the individual information sources increases with age, the way integration proceeds remains constant [@bohn2019pervasive; @bohn_tessler_merrick_frank_2019].
-In the model, this is accomplished by making the parameters capturing sensitivity to speaker informativeness ($\alpha$~i~, Fig.
-1D), the common ground ($\rho$~i~, Fig.
-1C), and object specific semantic knowledge ($\theta$~i,j~, Fig.
-1E) a function of the child’s age.
 
@@
 2).
-These results seem to support the assumption in the model that children consider all available information source.
+These results seem to support the assumptions in the model that children integrate all available information sources.
 However, it is still possible that simpler models might make equally good or better predictions.
@@
 Instead of assuming that one object has a higher prior probability to be the referent because it is new in context, the speaker thinks that both objects are equally likely to be the referent.
-As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources.Finally, according to the *no speaker inforamtiveness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance.
+As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources.
+Finally, according to the *no speaker inforamtiveness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance.
 As a consequence, the inference is solely based on common ground expectations.
@@
 The outcome of both processes are then weighted according to the parameter $\phi$.
-Like the rational integration model, this model takes in all available integration sources and assumes that they are integrated, the integration process itself, however, is construed in a different way.
+Like the rational integration model, this model takes in all available information sources in an age sensitive way and assumes that they are integrated - the integration process itself, however, is construed in a different way.
 
@@
 3B) suggests that younger children put a higher emphasis on common ground information, while older children rely more on the mutual exclusivity inference.
+The relative importance of the two inferences seems to switch at around 3 years.
 Yet again, when we directly compare the competitor models, we find that the data is several orders of magnitude more likely under the rational integration model (Fig.
 3B).
-Interestingly, when we compare the rational integration model with its parameters not constrained by the experimental data (i.e.
+Interestingly, when we compared the rational integration model with its parameters not constrained by the experimental data (i.e.
 the "pure" prediction model described above), it also outperformed both bias models (see Fig.
@@
 S6).
-Taken together, these results suggest that the integration process is best described as a) fully integrated and b) stable over time.
+Taken together, these results show that the integration process is best described as fully integrated and stable over time.
 
@@
 BF~10~ gives the Bayes Factor in favor of the rational integration model based on the marginal likelihood of the data under each model.
-(D) Posterior distribution of the bias parameter in the biased integration model and 300 random draws from the posterior distribution of the intercept and slope for the bias parameter in the developmental bias model.
+(D) Posterior distribution of the bias parameter in the biased integration model and developmental trajectories for the bias parameter in the developmental bias model based on 300 random draws from the posterior distribution of the intercept and slope.
 
@@
 
-These findings show that young children can flexibly integrate multiple information sources during language learning, even from relatively early in development.
+The environment in which children learn language is complex.
+Children have to integrate different information sources, some of which relate to expectations in the moment, others to the dynamics of the unfolding interactions and yet others to their previously acquired knowledge.
+Our findings show that young children can flexibly integrate multiple information sources during language learning - even from relatively early in development.
 To answer the question of how they do so, we presented a formal cognitive model that assumes that information sources are rationally integrated via Bayesian inference.
-This model accurately predicted children’s behavior between 2 and 5 years of age and provided a better explanation of the integration process and its development compared to a range of competitor models that either neglected or prioritized some information sources.
 
-Replicate with other languages and other cultural settings.
+Our model is based on classic social- pragmatic views on language use and comprehension [@clark1996using; @grice1991studies; @sperber2001relevance; @tomasello2009constructing].
+As a consequence, instead of assuming that different information sources feed into separate word-learning mechanisms, we assume that they all play a functional role in an integrated social inference process.
+Our model goes beyond previous theoretical and empirical work by specifying the computations that may underlie this inference process.
+Furthermore, we present a substantive theory about how this integration process develops: We assume that children become increasingly sensitive to different information sources but that the way these information sources are integrated, remains the same.
+We used this model to predict and explain children's information integration in a new word learning paradigm in which they had to integrate (1) their assumptions about informative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge.
 
-more explicit model of common ground (see perspective taking work mcc)
+We found that this rational integration model made accurate quantitative predictions across a range of experimental conditions - in some of which information sources were aligned, in some of which they were in conflict.
+Predictions from the model better explained the data compared to lesioned models - which assumed that children ignore one of the information sources - suggesting that children used all available information.
 
-integrate process of word learning itself via cross-situational learning [@frank2009using; @mcmurray2012word] dan yurovski work
+To test the explanatory power of the model - how well it explains the process by which information is integrated - we formalized an alternative, modular, view.
+According to the biased integration model, children use all available information sources but compute separate inferences based on a subset of them.
+Integration happens by weighting the outcomes of these separate inferences by some ratio.
+By allowing the ratio to be in favor of one of the inferences, this model captures the idea that children might be biased to some information sources over others.
+Even though such a model made reasonable predictions, we found that the rational integration model explained children's behavior much more accurately.
+Finally, we tested an alternative view on the development of the integration process.
+According tot the developmental bias model, the importance of the different information sources changed with age.
+Again, the rational integration model provided a much better fit to the data, suggesting that the integration process remains stable over time.
 
-The model is derived from a more general framework for pragmatic inference, which has been used to explain a wide variety of phenomena in adults’ language use and comprehension [@monroe2017colors; @wang2016learning; @tessler2019language; @yoon_frank_tessler_goodman_2018].
-Thus, it can be generalized in a natural way to capture word learning in contexts that offer more, fewer, or different types of information [e.g.
-@bohn_tessler_merrick_frank_2019].
-The flexibility of the framework stems from its conceptualization of human communication as a form of rational social action.
+The rational integration model is derived from a more general framework for pragmatic inference, which has been used to explain a wide variety of phenomena in adults’ language use and comprehension [@monroe2017colors; @wang2016learning; @tessler2019language; @yoon_frank_tessler_goodman_2018;@frank2012predicting; @goodman2016pragmatic].
+Thus, it can be generalized in a natural way to capture word learning in contexts that offer more, fewer, or different types of information.
+For example, in a recent study with adults and children, Bohn and colleagues [@bohn_tessler_merrick_frank_2019] manipulated expectations about informativeness and common ground in a different way.
+Using a structurally similar model, they also found a close alignment between model predictions and the data.
+The flexibility of this modeling framework stems from its conceptualization of human communication as a form of rational social action.
+As such, it connects to computational and empirical work that tries to explain social reasoning by assuming that humans expect each other to behave in a way that maximizes the benefits and minimizes the cost associated with actions [@bridgers2020young; @jara2016naive; @jara2020social].
 
-Connections to naive utility caluclus stuff?
+There are multiple ways in which the model and the experiments presented here could be extended.
+First, it would be important to replicate our findings in a more diverse sample, that is, with children from a different cultural background who learn a different language.
+In such a study, we would not expect that our results replicate in a strict sense - that is, we would not expect to see the same developmental trajectories in all cultures and/or languages.
+Substantial variation is much more likely.
+Our computational model provides a way to think about how to reconcile cross-cultural variation with a universal cognitive architecture: We expect differences in how sensitive children are to the individual information sources at different ages, but similarities in how information is integrated [@bohn2019pervasive].
+In computational terms, we assume a universal architecture that specifies the relation between a set of parameters with varying values.
 
-As such, this work adds to theories that see the onto- and phylogenetic emergence of language as deeply rooted in social cognition.
+Second, it would be useful to flesh out the cognitive processes that underlie reasoning about common ground.
+In its current form, our model does not specify how the listener arrives at the expectation that some objects are more likely referents given previous interactions with the speaker.
+We assume that common ground changes speaker's expectations about what are likely referents [@hanna2003effects] and measured these expectations to inform the parameter values in our model.
+Computationally, the model does not differentiate between common ground information and other reasons that might make an object contextually more salient.
+A good starting point to address this issue could be work that formalizes reasoning about common ground as trading-off between (differing) perspectives [@heller2016perspective; @mozuraitis2018modeling].
+
+Finally, our model is a model of referent identification in the moment of the utterance.
+Word learning, however, is a cumulative process which happens across multiple time points and contexts.
+Thus, it would be fruitful to connect our model with frameworks that focus on the temporal and cross-situational aspects of word learning [@frank2009using; @mcmurray2012word; @yurovsky2015integrative].
+
+Taken together, this work helps us understand how children navigate the complexity of their learning environment.
+Methodologically, it illustrates how formal, computational models can be used to test theories - bot in terms of their predictive and explanatory power.
+From a theoretical perspective, it adds to broader frameworks that see the onto- and phylogenetic emergence of language as deeply rooted in social cognition.
 
@@
 
-## Particiapnts
+A more detailed description of the experiments and the models can be found in the supplementary material.
+The experimental procedure, sample size and analysis for each experiment was pre-registered (https://osf.io/7rg9j/registrations).
+Experimental procedures, model and analysis scripts can be found in an online repository (https://github.com/manuelbohn/spin).
+Experiment 1 and 2 were designed to estimate children's developing sensitivity to each information source.
+Their results inform he parameter values in the model (see Fig.
+1).
+Experiment 3 was designed to test how children integrate the different information sources.
+
+## Participants
+
+```{r}
+me_data <- read_csv("../data/me.csv")
+prior_data <- read_csv("../data/novelty.csv")
+comb_data <- read_csv("../data/combination.csv")
+```
+
+Across three experiments, a total of `r length(unique(me_data$subid)) + length(unique(prior_data$subid)) + length(unique(comb_data$subid))` children participated.
+Experiment 1 involved `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls).
+Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1).
+
+In Experiment 2, we tested `r length(unique(prior_data$subid))` children from the same general population as in Experiment 1, including `r length(unique(prior_data$subid[prior_data$subage == 2]))` 2-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 2]),2), nsmall = 2)`, 7 girls), `r length(unique(prior_data$subid[prior_data$subage == 3]))` 3-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 3]),2), nsmall = 2)`, 14 girls) and  `r length(unique(prior_data$subid[prior_data$subage == 4]))` 4-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 4]),2), nsmall = 2)`, 14 girls).
+Data from 5 additional children was not included because they were either exposed to less than 75% of English at home (3) or the technical equipment failed (2).
+
+Finally, Experiment 3 involved `r length(unique(comb_data$subid))` children, including `r length(unique(comb_data$subid[comb_data$subage == 2]))` 2-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 2]),2), nsmall = 2)`, 7 girls), `r length(unique(comb_data$subid[comb_data$subage == 3]))` 3-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 3]),2), nsmall = 2)`, 14 girls) and  `r length(unique(comb_data$subid[comb_data$subage == 4]))` 4-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 4]),2), nsmall = 2)`, 14 girls).
+Data from 20 additional children was not included because they were either exposed to less than 75% of English at home (15), did not finish at least half of the test trials (3) or the technical equipment failed (2).
+
+All participants were recruited from the floor of a Children’s museum in San José, California, USA.
+This population is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status.
+Parents consented to their children’s participation and provided demographic information.
+All experiments were approved by the Stanford Institutional Review Board (protocol no.
+19960).
 
@@
 
+All experiments were presented as an interactive picture book on a tablet computer [@frank2016using].
+Fig.
+1A and B show screenshots from the actual experiments.
+The general setup involved an animal standing on a little hill between two tables.
+For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to talk to the child and make requests.
+Each experiment started with two training trials in which the speaker requested known objects (car and ball).
+
 ## Procedure
 
+Experiment 1 tested the so-called mutual exclusivity inference [@markman1988children; @lewis2020-me].
+On one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study) (Fig.
+1A/B iv and Fig.
+S1A).
+The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?".
+Children responded by touching one of the objects.
+The location of the novel object (left or right table) and the animal character were counterbalanced.
+We coded as correct choice if children chose the novel object as the referent of the novel word.
+Each child completed 12 trials, each with a different familiar and a different novel object.
+Familiar objects were selected to vary along the dimension of how likely children were to know the word for it.
+This including objects that most 2-year-olds can name (e.g.
+a duck) as well as objects that only very few 5-year-olds can name (e.g.
+a pawn).
+The selection was based on age of acquisition ratings from Kuperman and colleagues [-@kuperman2012age].
+While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned.
+Fig.
+S2A in the supplementary material shows the words and objects used in the experiment.
+We induced this variation to estimate the role of semantic knowledge in a mutual exclusivity inference.
+
+Experiment 2 tested children's sensitivity to common ground that is build up over the course of a conversation.
+In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two].
+The general setup was the same as in Experiment 1 (Fig.
+S1B).
+The speaker was positioned between the tables.
+There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty.
+Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object.
+Then the speaker disappeared.
+While the speaker was away, a second novel object appeared on the previously empty table.
+Then the speaker returned and requested an object in the same way as in Experiment 1.
+The positioning of the novel object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced.
+Children received five trials, each with a different pair of novel objects.
+We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.
+
+Experiment 3 combined the procedures from Experiment 1 and 2.
+It followed the same procedure as Experiment 2 but involved the same objects as Experiment 1 (Fig.
+1 i-iv and Fig.
+S1C).
+In the beginning, one table was empty while there was an object (novel or familiar) on the other one.
+After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or novel).
+Next, the speaker re-appeared and made the usual request.
+In the congruent condition, the familiar object was present in the beginning and the novel object appeared while the speaker was away (Fig.
+1A and Fig.
+S1C - left).
+In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent.
+In the incongruent condition, the novel object was present in the beginning and the familiar object appeared later.
+In this case, the two inferences pointed to different objects (Fig.
+1B and Fig.
+S1C - right).
+This resiulted in a total of 2 (congruent vs incongurent) x 12 (familiar objects) = 24 different conditions.
+Participants received up to 12 test trials, six in each condition, each with a different familiar and novel object.
+Familiar objects were the same as in Experiment 1.
+The positioning of the objects on the tables, the speaker and the location the speaker first turned to were counterbalanced.
+Participants could stop the experiment after six trials (three per condition).
+If a participant stopped after half of the trials, we tested an additional participant to reach a pre-registered number of data points per age group (2-, 3- and 4-year-olds).
+
 ## Data analysis
+
+We used generalized linear mixed models to analyze the data in each of the separate experiments.
+These analyses were used to check whether the experimental manipulations affected children's behavior at all.
+Since the focus of the paper is on how information sources were integrated, we describe the details in the supplementary material.
+
+To estimate the parameters for semantic knowledge and speaker informativeness, we adapted the rational integration to a situation in which both objects (novel and familiar) have equal prior probability (i.e., no common ground information).
+We used the data from Experiment 1 to then infer the parameters.
+That is, we inferred the intercepts and slopes for speaker informativeness (linear regression) and semantic knowledge (logistic regression) that generated model predictions to match the responses generated in Experiment 1.
+To estimate the parameters representing sensitivity to common ground, we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in Experiment 2.
+A more detailed description of these parameters were estimated (including a graphical model) can be found in the supplementary material.
+
+To generate model predictions we combined the parameters in the rational integration model - congruent ??
+
+All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
+The corresponding model code can be found in the associated online repository.
+To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned (Figure \@ref(fig:bda)).
+The resulting predictions come in the form of distributions of developmental trajectories for each familiar object in the congruent and the incongruent condition.
 

### 2020-08-26 paper/manuscript.Rmd
rename model files

@@
 S1C - right).
-This resiulted in a total of 2 (congruent vs incongurent) x 12 (familiar objects) = 24 different conditions.
+This resulted in a total of 2 (congruent vs incongurent) x 12 (familiar objects) = 24 different conditions.
 Participants received up to 12 test trials, six in each condition, each with a different familiar and novel object.
@@
 
-We used generalized linear mixed models to analyze the data in each of the separate experiments.
-These analyses were used to check whether the experimental manipulations affected children's behavior at all.
-Since the focus of the paper is on how information sources were integrated, we describe the details in the supplementary material.
+To analyze how the manipulations in each experiment affected children's behavior, we used generalized linear mixed models.
+Since the focus of the paper is on how information sources were integrated, we moved these models to the supplementary material.
+In the following, we focus on the cognitive models.
+A detailed, mathematical description, of the different cognitive models along with details about estimation procedures and priors can be found in the supplementary material.
+All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
+The corresponding model code can be found in the associated online repository.
 
-To estimate the parameters for semantic knowledge and speaker informativeness, we adapted the rational integration to a situation in which both objects (novel and familiar) have equal prior probability (i.e., no common ground information).
+As a first step, we used the data from Experiment 1 and 2 to estimate children's developing sensitivity to each information source.
+To estimate the parameters for semantic knowledge ($\theta$) and speaker informativeness ($\alpha$), we adapted the rational integration model to a situation in which both objects (novel and familiar) have equal prior probability (i.e., no common ground information).
 We used the data from Experiment 1 to then infer the parameters.
 That is, we inferred the intercepts and slopes for speaker informativeness (linear regression) and semantic knowledge (logistic regression) that generated model predictions to match the responses generated in Experiment 1.
-To estimate the parameters representing sensitivity to common ground, we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in Experiment 2.
+To estimate the parameters representing sensitivity to common ground ($\rho$), we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in Experiment 2.
 A more detailed description of these parameters were estimated (including a graphical model) can be found in the supplementary material.
 
-To generate model predictions we combined the parameters in the rational integration model - congruent ??
-
-All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
-The corresponding model code can be found in the associated online repository.
-To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned (Figure \@ref(fig:bda)).
-The resulting predictions come in the form of distributions of developmental trajectories for each familiar object in the congruent and the incongruent condition.
+To generate model predictions for the rational integration model we combined the parameters according to the model formula (Fig.
+1F).
+As mentioned above, common ground information could either be aligned or in conflict with the other information sources.
+In the congruent condition, the novel object was also the discourse novel object and thus had the prior probability $\rho$.
+In the incongruent condition, the novel object was the "old" object and thus had the prior probability of $1 - \rho$.
 

### 2020-08-26 paper/supplementary_material.Rmd
advance paper reformatting
rename model files

@@
 The location of the novel object (left or right table) and the animal character were counterbalanced.
-Each child received 12 trials, one with each familiar object.
-The novel object also changed from trial to trial.
 We coded as correct choice if children chose the novel object as the referent of the novel word.
@@
 All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
-The corresponding model code can be found in the associated online repository (file `webppl/prediction_model.wppl`).
+The corresponding model code can be found in the associated online repository (file `webppl/prediction_all_models.wppl`).
 To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned (Figure \@ref(fig:bda)).
@@
 To estimate $\phi$ as well as the other parameters, we make use of all the available data.
-The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`).
+The model code can be found in the associated online repository (file: `webppl/explanation_bias_model.wppl`).
 The posterior distribution for the bias parameter $\phi$ is shown in figure \@ref(fig:fig10)A.
@@
 
-The model code can be found in the associated online repository (file: `webppl/explanation_mixture_model.wppl`).
+The model code can be found in the associated online repository (file: `webppl/explanation_dev_bias_model.wppl`).
 Figure \@ref(fig:fig10)B visualizes the developmental trajectory of the bias parameter.

### 2020-08-26 paper/manuscript.Rmd
first draft reformatted paper

@@
 
-When researchers do look at information integration in children [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers], they mostly focus on how children interpret an ambiguous referring expression in light of social-contextual information.
+When information integration in children is studied directly [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers], the focus is mostly on how children interpret an ambiguous referring expression in light of social-contextual information.
 In one of these studies [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it.
@@
 Our *rational integration model* arbitrates between information sources via Bayesian inference (see Fig.
-1F for model formula).
+1f for model formula).
 A listener ($L_{1}$) reasons about the referent of a speaker's ($S_{1}$) utterance.
@@
 In the model, this is accomplished by making the parameters capturing sensitivity to speaker informativeness ($\alpha$~i~, Fig.
-1D), the common ground ($\rho$~i~, Fig.
-1C), and object specific semantic knowledge ($\theta$~i,j~, Fig.
-1E) a function of the child’s age.
+1d), the common ground ($\rho$~i~, Fig.
+1c), and object specific semantic knowledge ($\theta$~i,j~, Fig.
+1e) a function of the child’s age.
 
 ```{r fig1, include = T, fig.align = "center", fig.cap = "Experimental task and model.
-(A and B) Screenshots from the experimental task.
+(a and b) Screenshots from the experimental task.
 (i) The speaker encounters one object and then leaves the scene (ii).
@@
 Listeners' semantic knowledge enters the task because the identity of the  known object on one of the tables is varied from well-known objects like a duck to relatively unfamiliar objects like a chess pawn (total of 12 objects - blue).
-(A) shows the condition in which common ground information is congruent (i.e.
-point to the same object) with speaker informativeness and (B) shows the incongruent condition.
+(a) shows the condition in which common ground information is congruent (i.e.
+point to the same object) with speaker informativeness and (b) shows the incongruent condition.
 The congruent and incongruent conditions are each paired with the 12 known objects, resulting in 24 unique conditions.
-(C to E) show developmental trajectories for each information source, estimated from separate experiments (see supplement).
-(F) gives the model equation for the rational integration model and links information sources to model parameters.", out.width="100%"}
+(c to e) show developmental trajectories for each information source, estimated from separate experiments (see supplement).
+(f) gives the model equation for the rational integration model and links information sources to model parameters.", out.width="100%"}
 knitr::include_graphics("./figures/figure1.png")
@@
 This situation is depicted in Fig.
-1A-iv, in which a speaker (here, a frog) appears with a known object (a duck, left) and an unfamiliar object (the diamond-shaped object, right).
+1a iv, in which a speaker (here, a frog) appears with a known object (a duck, left) and an unfamiliar object (the diamond-shaped object, right).
 To identify the referent, the child could rely upon the three information sources described above.
@@
 Thus, the inference about the novel word referring to the unfamiliar object also depends on which object is new in context (Fig.
-1A and B i-iii).
+1a and b i-iii).
 Finally, the child may rely upon their previously acquired semantic knowledge, that is, how sure they are that the known object is called "duck".
@@
 In some versions of the experiment, some of these information sources were aligned (Fig.
-1A) but in some they were in conflict (Fig.
-1B).
+1a) but in some they were in conflict (Fig.
+1b).
 
@@
 We estimated children’s (N=148) developing sensitivity to individual information sources in separate experiments (see Fig.
-1C-E).
+1c-e).
 We then generated parameter-free, quantitative, *a priori* model predictions (developmental trajectories) representing the model's expectations about how children should behave in a new situation in which all three information sources had to be integrated.
@@
 We found a high correlation showing that the model explained 79% of the variance in the data (Fig.
-2).
+2a).
 These results seem to support the assumptions in the model that children integrate all available information sources.
@@
 Thus, we formalized the alternative view that children selectively ignore information sources in the form of three lesioned models (Fig.
-2).
+2b).
 These models assume that children follow the heuristic “ignore X” (with X being one of the information sources) when multiple information sources are presented together.
@@
 It takes in expectations about speaker informativeness and common ground, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge).
-The object specific parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model.
-In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects).
-The no word knowledge model takes in the overall trajectory for semantic knowledge but ignores object-specific variation.
 That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.The *no common ground model* takes in object specific semantic knowledge and speaker informativeness but ignores common ground information.
@@
 (ref:figlab2) **Predicting information integration**.
-Correlation between model predictions and child inference data for all 24 conditions and for each age group (binned by year) for the rational integration model and the three lesioned models.
+Correlation between model predictions and child inference data for all 24 conditions and for each age group (binned by year) for the rational integration model (a) and the three lesioned models (b).
 Horizontal and vertical error bars show 95% HDI.
@@
 The biased integration model makes reasonable predictions that explain a large proportion of the variance in the data (Fig.
-3B).
-The parameter $\phi$ - indicating the bias to one of the inferences - was estimated to favor the mutual exclusivity inference (mode = `r phi%>%pull(mode)`; 95% HDI: `r phi%>%pull(lci)` - `r phi%>%pull(uci)`, see Fig.
-3B).
+3b).
+The parameter $\phi$ - indicating the bias to one of the inferences - was estimated to favor the mutual exclusivity inference (mode = `r phi%>%pull(mode)`; 95% highest density interval (HDI): `r phi%>%pull(lci)` - `r phi%>%pull(uci)`, see Fig.
+3d).
 However, the rational integration model presented a much better fit to the data, both in terms of correlation and marginal likelihood of the data (Fig.
-3B).
-Thus, a fully integrated - as opposed to a segmented, biased - integration process explains the data better.
+3).
+Thus, a fully integrated - as opposed to a segmented and biased - integration process explained the data better.
 
@@
 The developmental bias model explains a substantial portion of the variance in the data (Fig.
-3B).
-The estimated developmental trajectory for the bias parameter $\phi$ (Fig.
-3B) suggests that younger children put a higher emphasis on common ground information, while older children rely more on the mutual exclusivity inference.
+3c).
+The estimated developmental trajectory for the bias parameter $\phi$ suggests that younger children put a higher emphasis on common ground information, while older children rely more on the mutual exclusivity inference (Fig.
+3d).
 The relative importance of the two inferences seems to switch at around 3 years.
 Yet again, when we directly compare the competitor models, we find that the data is several orders of magnitude more likely under the rational integration model (Fig.
-3B).
+3).
 Interestingly, when we compared the rational integration model with its parameters not constrained by the experimental data (i.e.
@@
 (ref:figlab3) **Explaining information integration across development**.
-(A) Model predictions from the rational integration model (colored lines) next to the behavioral data (dotted black lines with 95% CI in gray) for all 24 experimental conditions.
+(a) Model predictions from the rational integration model (colored lines) next to the behavioral data (dotted black lines with 95% CI in gray) for all 24 experimental conditions.
 Top row (blue) shows conditions in which common ground information is congruent with speaker informativeness, bottom row (red) shows conditions in which they are incongruent.
@@
 Light dots represent individual data points.
-(B) Correlations between model predictions binned by age and condition for the integration model and (C) the two mixture models.
+(b) Correlations between model predictions binned by age and condition for the integration model and (c) the two mixture models.
 Vertical and horizontal error bars show 95% HDIs.
 BF~10~ gives the Bayes Factor in favor of the rational integration model based on the marginal likelihood of the data under each model.
-(D) Posterior distribution of the bias parameter in the biased integration model and developmental trajectories for the bias parameter in the developmental bias model based on 300 random draws from the posterior distribution of the intercept and slope.
+(d) Posterior distribution of the bias parameter in the biased integration model and developmental trajectories for the bias parameter in the developmental bias model based on 300 random draws from the posterior distribution of the intercept and slope.
 
@@
 Fig.
-1A and B show screenshots from the actual experiments.
+1a and b show screenshots from the actual experiments.
 The general setup involved an animal standing on a little hill between two tables.
@@
 On one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study) (Fig.
-1A/B iv and Fig.
-S1A).
+1a/b iv and Fig.
+S1a).
 The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?".
@@
 The general setup was the same as in Experiment 1 (Fig.
-S1B).
+S1b).
 The speaker was positioned between the tables.
@@
 1 i-iv and Fig.
-S1C).
+S1c).
 In the beginning, one table was empty while there was an object (novel or familiar) on the other one.
@@
 In the congruent condition, the familiar object was present in the beginning and the novel object appeared while the speaker was away (Fig.
-1A and Fig.
-S1C - left).
+1a and Fig.
+S1c - left).
 In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent.
@@
 1B and Fig.
-S1C - right).
+S1c - right).
 This resulted in a total of 2 (congruent vs incongurent) x 12 (familiar objects) = 24 different conditions.
@@
 To estimate the parameters representing sensitivity to common ground ($\rho$), we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in Experiment 2.
+For the explanation models, these parameters were additionally constrained by the data from Experiment 3.
 A more detailed description of these parameters were estimated (including a graphical model) can be found in the supplementary material.
 
-To generate model predictions for the rational integration model we combined the parameters according to the model formula (Fig.
-1F).
+To generate model predictions, we combined the parameters according to the respective model formula.
 As mentioned above, common ground information could either be aligned or in conflict with the other information sources.
@@
 In the incongruent condition, the novel object was the "old" object and thus had the prior probability of $1 - \rho$.
+
+The rational integration model is defined as $P^{int}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i)$.
+The three lesioned models that were used to compare how well the model predicts new data are reduced versions of this model.
+The no word knowledge model uses the same model architecture: $P^{no\_wk}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{i}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{i}\}) \cdot P(r \mid \rho_i)$ and the only difference lies in the parameter $\theta$.
+The object specific parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model.
+In this model, there is an overall developmental trajectory for semantic knowledge (main effect - $\theta_{i}$) and then there is object-specific variation around this trajectory (random effects -- $\theta_{ij}$).
+Thus, the no word knowledge model takes in the overall trajectory for semantic knowledge ($\theta_{i}$) but ignores object-specific variation.
+The no common ground model ignores common ground information (represented by $\rho$) and is thus defined as $P^{no\_cg}_{L_1}(r \mid u; \{\alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\})$.
+For the no speaker informativeness model, the parameter $\alpha = 0$.
+As a consequence, the likelihood term in the model is 1 and the model therefore reduces to $P^{no\_si}_{L_1}(r \mid u; \{\rho_i\})\propto P(r \mid \rho_i)$.
+
+As noted above, the explanation models used parameters that were additionally constrained by the data from Experiment 3.
+This had no effect on the way these parameters were combined in the rational integration model.
+The biased integration model is defined as $P^{biased}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)$ with $P_{ME}$ representing a mutual exclusivity inference which takes in speaker inforamtiveness and object specific semantic knowledge.
+This inference is then weighted by the parameter $\phi$ and added to the respective prior probability, which is weighted by $1-\phi_i$.
+Thus, $\phi$ represents the bias in favor of the mutual exclusivity inference.
+In the developmental bias model the parameter $\phi$ is made to change with age ($\phi_i$) and the model is thus defined as $P^{dev\_bias}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i)$.
+
+We compared models in two ways.
+First, we used Pearson correlations between model predictions and the data.
+For this analysis, we binned the model predictions and the data by age in years and by the type of familiar object (see Fig.
+2 and 3 as well as S7 and S10).
+Second, we compared models based on the marginal likelihood of the data under each model -- the likelihood of the data averaging over ("marginalizing over") the prior distribution on parameters; the pairwise ratio of marginal likelihoods for two models is known as the Bayes Factor.
+It is interpreted as how many times more likely the data is under one model compared to the other.
+Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by the prior probabilities of those parameter values); by averaging over the prior distribution on parameters, Bayes Factor implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the potential gains in predictive accuracy that a model with more parameters can achieve [@lee2014bayesian].
+For this analysis, we treated age continuously.
 

### 2020-08-31 paper/manuscript.Rmd
work on paper

@@
 
-When information integration in children is studied directly [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers], the focus is mostly on how children interpret an ambiguous referring expression in light of social-contextual information.
+When information integration is studied directly, the focus is mostly on how children interpret an ambiguous referring expression in light of social-contextual information [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers].
 In one of these studies [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it.
@@
 
-We focus on three information sources that play an integral part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].
-These inforamtion sources operate on different timescales: while (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development.
+We focus on three information sources that play an integral part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using; @clark2015common], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].
+These information sources operate on different timescales: while (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development.
 This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word].
@@
 A listener ($L_{1}$) reasons about the referent of a speaker's ($S_{1}$) utterance.
-This reasoning is contextualized by the prior probability of each referent $\rho$ which we take to be a function of the common ground shared between the listener and the speaker.
+This reasoning is contextualized by the prior probability of each referent $\rho$ -- which we take to be a function of the common ground shared between the listener and the speaker.
 To decide between referents, the listener ($L_{1}$) reasons about what a rational speaker ($S_{1}$) with informativeness $\alpha$ would say given an intended referent.
@@
 
-To generate data to test the predictive and explanatory power of our model, we developed a world-learning paradigm in which we jointly manipulated the three information sources (Fig.
+To test the predictive and explanatory power of our model, we developed a world-learning paradigm in which we jointly manipulated the three information sources (Fig.
 1).
@@
 To identify the referent, the child could rely upon the three information sources described above.
-First, they may infer that a cooperative speaker would have used the word duck to refer to the known object (the duck); the fact that the speaker did not say duck then suggests that the speaker is most likely referring to a different object (the unfamiliar object).
+First, they may infer that a cooperative speaker would have used the word "duck" to refer to the known object (the duck); the fact that the speaker did not say duck then suggests that the speaker is most likely referring to a different object (the unfamiliar object).
 This basic inference is oftentimes referred to as a mutual exclusivity inference [@markman1988children; @halberda2003development].
@@
 We tested the model in its ability to predict children’s actual behavior - at an age (between 2 and 5 years) at which they learn language at an exponential rate [@bloom2002children].
-We estimated children’s (N=148) developing sensitivity to individual information sources in separate experiments (see Fig.
+We estimated children’s (N=148) developing sensitivity to individual information sources in separate experiments (Experiment 1 and 2) (see Fig.
 1c-e).
@@
 1.
-We compared these predictions to newly collected data from N = 220 children from the same age range.
+We compared these predictions to newly collected data from N = 220 children from the same age range (Experiment 3).
 The results showed a very close alignment between model predictions and the data across the entire age range.
@@
 For a more quantitative analysis, we binned predictions and data by year and correlated them.
-We found a high correlation showing that the model explained 79% of the variance in the data (Fig.
+We found a high correlation, with the model explaining 79% of the variance in the data (Fig.
 2a).
 These results seem to support the assumptions in the model that children integrate all available information sources.
-However, it is still possible that simpler models might make equally good or better predictions.
+However, it is still possible that simpler models might make equally good -- or even better -- predictions.
 
@@
 
-The marginally less-complex *no word knowledge model* uses the same model architecture as the rational integration model.
+The *no word knowledge model* uses the same model architecture as the rational integration model.
 It takes in expectations about speaker informativeness and common ground, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge).
-That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.The *no common ground model* takes in object specific semantic knowledge and speaker informativeness but ignores common ground information.
+That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.
+The *no common ground model* takes in object specific semantic knowledge and speaker informativeness but ignores common ground information.
 Instead of assuming that one object has a higher prior probability to be the referent because it is new in context, the speaker thinks that both objects are equally likely to be the referent.
@@
 
-We found little support that children make inferences following one of the heuristic models.
+We found little support that children make inferences following one of the heuristic models (Fig.
+2b).
 When using Bayesian model comparison via marginal likelihood of the data, [@lee2014bayesian], we find that the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Fig.
@@
 This view would allow for the possibility that some information sources are considered to be more important than others.
-In other words, children might be biased towards some information sources (e.g.
-a 60:40 ratio).
+In other words, children might be biased towards some information sources.
 We formalized this alternative view as a *biased integration model*.
@@
 An alternative perspective would be to assume that the integration process itself changes with age.
-The biased integration model provides a way to think about developmental change in the integration process: Children are biased towards some information sources, but this bias itself changes with age.
+The biased integration model provides a way to think about developmental change in the integration process: Children are biased towards some information sources, but the bias itself changes with age.
 We formalize such an alternative view as a *developmental bias model* which is structurally identical to the biased integration model but in which the parameter $\phi$ changes with age.
@@
 3d).
-The relative importance of the two inferences seems to switch at around 3 years.
+The relative importance of the two inferences seems to switch at around age 3.
 Yet again, when we directly compare the competitor models, we find that the data is several orders of magnitude more likely under the rational integration model (Fig.
@@
 We found that this rational integration model made accurate quantitative predictions across a range of experimental conditions - in some of which information sources were aligned, in some of which they were in conflict.
-Predictions from the model better explained the data compared to lesioned models - which assumed that children ignore one of the information sources - suggesting that children used all available information.
+Predictions from the model better explained the data compared to lesioned models which assumed that children ignore one of the information sources, suggesting that children used all available information.
 
@@
 Finally, we tested an alternative view on the development of the integration process.
-According tot the developmental bias model, the importance of the different information sources changed with age.
+According to the developmental bias model, the importance of the different information sources changed with age.
 Again, the rational integration model provided a much better fit to the data, suggesting that the integration process remains stable over time.
@@
 First, it would be important to replicate our findings in a more diverse sample, that is, with children from a different cultural background who learn a different language.
-In such a study, we would not expect that our results replicate in a strict sense - that is, we would not expect to see the same developmental trajectories in all cultures and/or languages.
+In such a study, we would not expect that our results replicate in a strict sense; that is, we would not expect to see the same developmental trajectories in all cultures and/or languages.
 Substantial variation is much more likely.
 Our computational model provides a way to think about how to reconcile cross-cultural variation with a universal cognitive architecture: We expect differences in how sensitive children are to the individual information sources at different ages, but similarities in how information is integrated [@bohn2019pervasive].
-In computational terms, we assume a universal architecture that specifies the relation between a set of parameters with varying values.
+In computational terms, we assume a universal architecture that specifies the relation between a set of varying parameters.
 
 Second, it would be useful to flesh out the cognitive processes that underlie reasoning about common ground.
-In its current form, our model does not specify how the listener arrives at the expectation that some objects are more likely referents given previous interactions with the speaker.
+In its current form, our model does not specify how the listener arrives at the expectation that some objects are more likely referents because they are new in common ground.
 We assume that common ground changes speaker's expectations about what are likely referents [@hanna2003effects] and measured these expectations to inform the parameter values in our model.
@@
 A more detailed description of the experiments and the models can be found in the supplementary material.
-The experimental procedure, sample size and analysis for each experiment was pre-registered (https://osf.io/7rg9j/registrations).
+The experimental procedure, sample size and analysis for each experiment were pre-registered (https://osf.io/7rg9j/registrations).
 Experimental procedures, model and analysis scripts can be found in an online repository (https://github.com/manuelbohn/spin).
@@
 Their results inform he parameter values in the model (see Fig.
-1).
+1 c-f).
 Experiment 3 was designed to test how children integrate the different information sources.
@@
 
-Across three experiments, a total of `r length(unique(me_data$subid)) + length(unique(prior_data$subid)) + length(unique(comb_data$subid))` children participated.
+Across the three experiments, a total of `r length(unique(me_data$subid)) + length(unique(prior_data$subid)) + length(unique(comb_data$subid))` children participated.
 Experiment 1 involved `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls).

### 2020-09-01 paper/manuscript.Rmd
first draft paper

@@
 Experiment 1 tested the so-called mutual exclusivity inference [@markman1988children; @lewis2020-me].
-On one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study) (Fig.
+On one table, there was a familiar object, on the other table, there was an unfamiliar object (drawn for the purpose of the study) (Fig.
 1a/b iv and Fig.
@@
 Children responded by touching one of the objects.
-The location of the novel object (left or right table) and the animal character were counterbalanced.
-We coded as correct choice if children chose the novel object as the referent of the novel word.
-Each child completed 12 trials, each with a different familiar and a different novel object.
+The location of the unfamiliar object (left or right table) and the animal character were counterbalanced.
+We coded as correct choice if children chose the unfamiliar object as the referent of the novel word.
+Each child completed 12 trials, each with a different familiar and a different unfamiliar object.
 Familiar objects were selected to vary along the dimension of how likely children were to know the word for it.
-This including objects that most 2-year-olds can name (e.g.
+This included objects that most 2-year-olds can name (e.g.
 a duck) as well as objects that only very few 5-year-olds can name (e.g.
@@
 S2A in the supplementary material shows the words and objects used in the experiment.
-We induced this variation to estimate the role of semantic knowledge in a mutual exclusivity inference.
 
@@
 The speaker was positioned between the tables.
-There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty.
+There was an unfamiliar object (drawn for the purpose of the study) on one of the tables while the other table was empty.
 Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object.
 Then the speaker disappeared.
-While the speaker was away, a second novel object appeared on the previously empty table.
+While the speaker was away, a second unfamiliar object appeared on the previously empty table.
 Then the speaker returned and requested an object in the same way as in Experiment 1.
-The positioning of the novel object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced.
-Children received five trials, each with a different pair of novel objects.
+The positioning of the unfamiliar object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced.
+Children received five trials, each with a different pair of unfamiliar objects.
 We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.
@@
 S1c).
-In the beginning, one table was empty while there was an object (novel or familiar) on the other one.
-After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or novel).
+In the beginning, one table was empty while there was an object (unfamiliar or familiar) on the other one.
+After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or unfamiliar).
 Next, the speaker re-appeared and made the usual request.
-In the congruent condition, the familiar object was present in the beginning and the novel object appeared while the speaker was away (Fig.
+In the congruent condition, the familiar object was present in the beginning and the unfamiliar object appeared while the speaker was away (Fig.
 1a and Fig.
@@
 In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent.
-In the incongruent condition, the novel object was present in the beginning and the familiar object appeared later.
+In the incongruent condition, the unfamiliar object was present in the beginning and the familiar object appeared later.
 In this case, the two inferences pointed to different objects (Fig.
-1B and Fig.
+1b and Fig.
 S1c - right).
 This resulted in a total of 2 (congruent vs incongurent) x 12 (familiar objects) = 24 different conditions.
-Participants received up to 12 test trials, six in each condition, each with a different familiar and novel object.
+Participants received up to 12 test trials, six in each alignment condition, each with a different familiar and unfamiliar object.
 Familiar objects were the same as in Experiment 1.
 The positioning of the objects on the tables, the speaker and the location the speaker first turned to were counterbalanced.
-Participants could stop the experiment after six trials (three per condition).
-If a participant stopped after half of the trials, we tested an additional participant to reach a pre-registered number of data points per age group (2-, 3- and 4-year-olds).
+Participants could stop the experiment after six trials (three per alignment condition).
+If a participant stopped after half of the trials, we tested an additional participant to reach the preregistered number of data points per age group (2-, 3- and 4-year-olds).
 
@@
 To analyze how the manipulations in each experiment affected children's behavior, we used generalized linear mixed models.
-Since the focus of the paper is on how information sources were integrated, we moved these models to the supplementary material.
-In the following, we focus on the cognitive models.
-A detailed, mathematical description, of the different cognitive models along with details about estimation procedures and priors can be found in the supplementary material.
+Since the focus of the paper is on how information sources were integrated, we discuss these models in the supplementary material and focus here on the cognitive models instead.
+A detailed, mathematical description of the different cognitive models along with details about estimation procedures and priors can be found in the supplementary material.
 All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
@@
 For the explanation models, these parameters were additionally constrained by the data from Experiment 3.
-A more detailed description of these parameters were estimated (including a graphical model) can be found in the supplementary material.
+A more detailed description of how these parameters were estimated (including a graphical model) can be found in the supplementary material.
 
@@
 As mentioned above, common ground information could either be aligned or in conflict with the other information sources.
-In the congruent condition, the novel object was also the discourse novel object and thus had the prior probability $\rho$.
+In the congruent condition, the unfamiliar object was also new in context and thus had the prior probability $\rho$.
 In the incongruent condition, the novel object was the "old" object and thus had the prior probability of $1 - \rho$.
@@
 The object specific parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model.
-In this model, there is an overall developmental trajectory for semantic knowledge (main effect - $\theta_{i}$) and then there is object-specific variation around this trajectory (random effects -- $\theta_{ij}$).
+That is, there is an overall developmental trajectory for semantic knowledge (main effect - $\theta_{i}$) and then there is object-specific variation around this trajectory (random effects -- $\theta_{ij}$).
 Thus, the no word knowledge model takes in the overall trajectory for semantic knowledge ($\theta_{i}$) but ignores object-specific variation.

### 2020-09-01 paper/supplementary_material.Rmd
first draft reformatted paper
first draft paper

@@
 \begin{equation}
-P^{no\_me}_{L_1}(r \mid u; \{\rho_i\})\propto P(r \mid \rho_i) 
+P^{no\_si}_{L_1}(r \mid u; \{\rho_i\})\propto P(r \mid \rho_i) 
 (\#eq:nome)
@@
 plot_cor_model_pred <- readRDS( "../saves/corr_model_data_pred.rds")%>%
-  mutate(model = factor(model, levels = c("integration", "no word knowledge", "no common ground", "no speaker informativeness")))
+  mutate(model = ifelse(model == "no mutual exclusivity", "no speaker informativeness", model),
+    model = factor(model, levels = c("integration", "no word knowledge", "no common ground", "no speaker informativeness")))
 

### 2020-09-02 paper/manuscript.Rmd
draft for paper 2

@@
 
-## Predicting information integration accross development
+## Predicting information integration across development
 
@@
 As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources.
-Finally, according to the *no speaker inforamtiveness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance.
+Finally, according to the *no speaker informativeness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance.
 As a consequence, the inference is solely based on common ground expectations.
@@
 Experiment 1 and 2 were designed to estimate children's developing sensitivity to each information source.
-Their results inform he parameter values in the model (see Fig.
+Their results inform the parameter values in the model (see Fig.
 1 c-f).
@@
 All participants were recruited from the floor of a Children’s museum in San José, California, USA.
-This population is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status.
+This population is characterized by a diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status.
 Parents consented to their children’s participation and provided demographic information.
@@
 
-Experiment 2 tested children's sensitivity to common ground that is build up over the course of a conversation.
+Experiment 2 tested children's sensitivity to common ground that is built up over the course of a conversation.
 In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two].
@@
 This had no effect on the way these parameters were combined in the rational integration model.
-The biased integration model is defined as $P^{biased}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)$ with $P_{ME}$ representing a mutual exclusivity inference which takes in speaker inforamtiveness and object specific semantic knowledge.
+The biased integration model is defined as $P^{biased}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)$ with $P_{ME}$ representing a mutual exclusivity inference which takes in speaker informativeness and object specific semantic knowledge.
 This inference is then weighted by the parameter $\phi$ and added to the respective prior probability, which is weighted by $1-\phi_i$.

### 2020-09-27 paper/manuscript.Rmd
first draft paper

@@
 
-Humans rely on language for communication, making language acquisition a key learning objective of early childhood [@tomasello2018natural].
-A central problem in language learning is referent identification: To learn the conventional symbolic relation between a word and an object, the child has to determine the intended referent of the word.
+Human communicative communicative abilities are unrivaled in the animal kingdom [@taylor2016language; @tomasello2008origins; @fitch2010evolution].
+Language - in whatever modality - is the medium that allows humans to collaborate and coordinate in species-unique ways, making it the bedrock of human culture and society [@smith1997major].
+Thus, in order to absorb the culture around them and become functioning members of a society, children need to learn language [@tomasello2018natural].
+A central problem in language learning is referent identification: to learn the conventional symbolic relation between a word and an object, a child has to determine the intended referent of the word.
 Referents can only be identified in an inferential manner by reasoning about the speaker’s intentions [@bohn2019pervasive; @bruner1983child; @clark2009first; @tomasello2009constructing].
@@
 
-We focus on three information sources that play an integral part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using; @clark2015common], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].
+We focus on three information sources that play an integral part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle; @sperber2001relevance], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using; @clark2015common], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].
 These information sources operate on different timescales: while (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development.
@@
 Finally, the child may rely upon their previously acquired semantic knowledge, that is, how sure they are that the known object is called "duck".
-If the known object is something less familiar, such as a chess piece (e.g., a pawn), a 3-year-old child may draw a weaker inference, if they draw any inference at all [@lewis2020-me].
-Taken together, the child has the opportunity to integrate their assumptions about (1) informative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge.
+If the known object is something less familiar, such as a chess piece (e.g., a pawn), a 3-year-old child may draw a weaker inference, if they draw any inference at all [@lewis2020-me; @grassmann2015children].
+Taken together, the child has the opportunity to integrate their assumptions about (1) cooperative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge.
 In some versions of the experiment, some of these information sources were aligned (Fig.
@@
 We compared these predictions to newly collected data from N = 220 children from the same age range (Experiment 3).
+
 The results showed a very close alignment between model predictions and the data across the entire age range.
@@
 
-The fact that children integrated all the available information sources may be surprising, but does not rule out that the integration process itself might be different from the one described in the rational integration model.
-Remember that this model assumes that all information sources enter into an integrated inference process.
+The fact that children integrated all the available information sources may be surprising, but does not rule out that the integration process itself might be different from the one described in the rational integration model, which assumes that all information sources enter into an integrated inference process.
 However, a more modular view seems equally plausible: children might compute separate inferences based on a subset of the available information and then integrate them by weighting them according to some ratio.
@@
 The outcome of both processes are then weighted according to the parameter $\phi$.
-Like the rational integration model, this model takes in all available information sources in an age sensitive way and assumes that they are integrated - the integration process itself, however, is construed in a different way.
+Like the rational integration model, this model takes in all available information sources in an age sensitive way and assumes that they are integrated - the only difference lies in the nature of the integration process.
 
@@
 That is, in contrast to the rational integration model, the biased integration model does not allow to make *a priori* predictions about new data in the way we describe above.
-For the model comparison, we therefore constrained the parameters in the rational integration model by the experimental data as well.
+For the model comparison, we therefore constrained the parameters in the rational integration model by the data from EXperiment 3 as well.
 As a consequence, both models use all the information available to constrain their parameters (see Fig.
@@
 3).
-Thus, a fully integrated - as opposed to a segmented and biased - integration process explained the data better.
+Thus, a fully integrated - as opposed to a sequential and biased - integration process explained the data better.
 
@@
 
-The developmental bias model explains a substantial portion of the variance in the data (Fig.
+The developmental bias model also explains a substantial portion of the variance in the data (Fig.
 3c).
@@
 
-Our model is based on classic social- pragmatic views on language use and comprehension [@clark1996using; @grice1991studies; @sperber2001relevance; @tomasello2009constructing].
+Our work extends the study of information integration during language comprehension [@tanenhaus1995integration; @kamide2003integration; @hagoort2004integration; @ozyurek2007line; @heller2016perspective] to pragmatics.
+Our model is based on classic social-pragmatic theories on language use and comprehension [@clark1996using; @grice1991studies; @sperber2001relevance; @tomasello2009constructing].
 As a consequence, instead of assuming that different information sources feed into separate word-learning mechanisms, we assume that they all play a functional role in an integrated social inference process.
@@
 There are multiple ways in which the model and the experiments presented here could be extended.
-First, it would be important to replicate our findings in a more diverse sample, that is, with children from a different cultural background who learn a different language.
+First, it would be important to replicate our findings in a more diverse sample, that is, with children from a different cultural background who learn a different language [@nielsen2017persistent].
 In such a study, we would not expect that our results replicate in a strict sense; that is, we would not expect to see the same developmental trajectories in all cultures and/or languages.
 Substantial variation is much more likely.
-Our computational model provides a way to think about how to reconcile cross-cultural variation with a universal cognitive architecture: We expect differences in how sensitive children are to the individual information sources at different ages, but similarities in how information is integrated [@bohn2019pervasive].
+Nevertheless, our computational model provides a way to think about how to reconcile cross-cultural variation with a universal cognitive architecture: We expect differences in how sensitive children are to the individual information sources at different ages, but similarities in how information is integrated [@bohn2019pervasive].
 In computational terms, we assume a universal architecture that specifies the relation between a set of varying parameters.
@@
 Computationally, the model does not differentiate between common ground information and other reasons that might make an object contextually more salient.
-A good starting point to address this issue could be work that formalizes reasoning about common ground as trading-off between (differing) perspectives [@heller2016perspective; @mozuraitis2018modeling].
 
@@
 A detailed, mathematical description of the different cognitive models along with details about estimation procedures and priors can be found in the supplementary material.
-All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
+All Bayesian cognitive models and Bayesian data analytic models were implemented in the probabilistic programming language `WebPPL` [@dippl].
 The corresponding model code can be found in the associated online repository.

### 2020-10-23 paper/manuscript.Rmd
prep for submission

@@
   - name          : "Manuel Bohn"
-    affiliation   : "1,*"
+    affiliation   : "1,2,*"
     corresponding : yes    # Define only one corresponding author
@@
   - name          : "Michael Henry Tessler"
-    affiliation   : "2,*"
+    affiliation   : "3,*"
   - name          : "Megan Merrick"
-    affiliation   : "3"
+    affiliation   : "1"
   - name          : "Michael C. Frank"
-    affiliation   : "3"
+    affiliation   : "1"
 
@@
   - id            : "1"
+    institution   : "Department of Psychology, Stanford University"
+  - id            : "2"
     institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
-  - id            : "2"
+  - id            : "3"
     institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
-  - id            : "3"
-    institution   : "Department of Psychology, Stanford University"
   - id            : "*"
@@
   Before formal education begins, children typically acquire a vocabulary of thousands of words.
-This learning process requires the use of many different information sources in their social environment, including their current knowledge state as well as the context in which they hear words used.
+This learning process requires the use of many different information sources in their social environment, including the context in which they hear words used and their current state of knowledge.
 How is this information integrated?
-We specify a model according to which children consider all available information sources and integrate them via Bayesian inference.
+We specify a developmental model according to which children consider information sources in an age-specific way and integrate them via Bayesian inference.
 This model accurately predicted 2-to-5 year-old children’s word learning across a range of experimental conditions.
-Model comparison suggests that the integration process is stable across development and that the main locus of development is an increased sensitivity to individual information sources.
-We present a quantitative developmental theory of information integration for language learning, embedded in a larger framework that grounds language use and learning in social cognition.
+Model comparison suggests that the central locus of development is an increased sensitivity to individual information sources, rather than changes in  integration ability.
+This work presents a quantitative developmental theory of information integration during language learning, and illustrates how formal models can be used to make a quantitative test of the predictive and explanatory power of competing theories.
 
 keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"
-wordcount         : "X"
 
@@
 
-Human communicative communicative abilities are unrivaled in the animal kingdom [@taylor2016language; @tomasello2008origins; @fitch2010evolution].
-Language - in whatever modality - is the medium that allows humans to collaborate and coordinate in species-unique ways, making it the bedrock of human culture and society [@smith1997major].
-Thus, in order to absorb the culture around them and become functioning members of a society, children need to learn language [@tomasello2018natural].
-A central problem in language learning is referent identification: to learn the conventional symbolic relation between a word and an object, a child has to determine the intended referent of the word.
-Referents can only be identified in an inferential manner by reasoning about the speaker’s intentions [@bohn2019pervasive; @bruner1983child; @clark2009first; @tomasello2009constructing].
-That is, the child has to infer what the speaker is communicating about based on information sources in the social context of the utterance.
+Human communicative abilities are unrivaled in the animal kingdom[@taylor2016language; @tomasello2008origins; @fitch2010evolution].
+Language -- in whatever modality -- is the medium that allows humans to collaborate and coordinate in species-unique ways, making it the bedrock of human culture and society [@smith1997major].
+Thus, to absorb the culture around them and become functioning members of society, children need to learn language [@tomasello2018natural].
+A central problem in language learning is referent identification: To acquire the conventional symbolic relation between a word and an object, a child must determine the intended referent of the word.
+However, there is no unique cue to reference that can be used across all situations [@frank2013social].
+Instead, referents can only be identified inferentially by reasoning about the speaker’s intentions [@bohn2019pervasive; @bruner1983child; @clark2009first; @tomasello2009constructing].
+That is, the child has to infer what the speaker is communicating about based on information sources in the utterance’s social context.
 
-From early on in development, children use a number of different mechanisms to harness such social-contextual information sources [@bohn2019pervasive; @clark2009first; @bloom2002children].
-For example, children expect speakers to use novel words for unknown objects [@clark1987principle; @markman1988children; @carey1978acquiring; @halberda2003development], to talk about objects that are relevant [@frank2014inferring; @schulze20133], new in context [@akhtar1996role; @diesendruck2004two], or related to the ongoing conversation [@bohn_le_peloquin_koymen_frank_2020; @sullivan2016discourse; @horowitz2015young].
-These different mechanisms, however, have largely been described and theorized about in isolation.
-The picture of the learning process that emerges is that of a “bag of tricks”: mechanisms that operate (and develop) independently from one another [@bloom2002children].
-As such, this view of the learning process does not capture the complexity of natural social interaction during which many sources of information are present [@bergelson2017nature; @frank2013social].
-Theses sources need to be integrated in order to accurately infer a speaker's intention.
+From early in development, children use several different mechanisms to harness social-contextual information sources [@bohn2019pervasive; @clark2009first; @bloom2002children].
+Children expect speakers to use novel words for unknown objects [@clark1987principle; @markman1988children; @carey1978acquiring; @halberda2003development], to talk about objects that are relevant [@frank2014inferring; @schulze20133], new in context [@akhtar1996role; @diesendruck2004two], or related to the ongoing conversation [@bohn_le_peloquin_koymen_frank_2020; @sullivan2016discourse; @horowitz2015young].
+These different mechanisms, however, have been mainly described and theorized about in isolation.
+The picture of the learning process that emerges is that of a "bag of tricks": mechanisms that operate (and develop) independently from one another [@bloom2002children].
+As such, this view of the learning process does not address the complexity of natural social interaction during which many sources of information are present [@bergelson2017nature; @frank2013social].
+How do children arbitrate between these sources in order to accurately infer a speaker’s intention?
 
-When information integration is studied directly, the focus is mostly on how children interpret an ambiguous referring expression in light of social-contextual information [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers].
-In one of these studies [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it.
-The speaker, sitting on the opposite side of the display, saw only 3 of the compartments: the ball, the pen, and one of the glasses.
-When the speaker asked for "the glass", children had to integrate the semantics of the utterance with the perspective of the speaker to correctly infer which of the glasses - from their perspective - the speaker was referring to.
-This study, along with others, found that preschoolers use both information sources.
-What these studies do not do, however, is specify the process by which children integrate the different information sources.
-When discussing their results, authors refer to social-pragmatic theories of language use and learning [@grice1991studies; @sperber2001relevance; @clark1996using; @clark2009first; @tomasello2009constructing], all of which assume that information is integrated as part of a social inference process, but none of which clearly defines the process.
+When information integration is studied directly, the focus is mostly on how children interpret an ambiguous referring expression in light of social-contextual information [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers; @kachel2021young].
+In one classic study [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it.
+The speaker, sitting on the opposite side of the display, saw only three of the four compartments: the ball, the pen, and one of the glasses.
+When the speaker asked for "the glass", children had to integrate the semantics of the utterance with the speaker’s perspective to correctly infer which of the glasses the speaker was referring to.
+This study advanced our understanding by documenting that preschoolers use both information sources, a finding confirmed by a variety of other work [@graham2017words; @khu2020preschoolers; @nilsen2009preschoolers].
+Yet these studies do not specify -- or test -- the process by which children integrate different information sources.
+When interpreting their findings, work in this tradition refers to social-pragmatic theories of language use and learning [@grice1991studies; @sperber2001relevance; @clark1996using; @clark2009first; @tomasello2009constructing], all of which assume that information is integrated as part of a social inference process, but none of which clearly defines the process.
 As a consequence, we have no explicit and quantitative theory of how different information sources (and word learning mechanisms) are integrated.
@@
 We present a theory of this integration process.
-Following social-pragmatic theories of language learning [@clark2009first; @tomasello2009constructing], our theory is based on the following premises: information sources serve different functional roles, all part of an integrated social inference process [@clark1996using; @grice1991studies; @shafto2012learning; @sperber2001relevance].
+Following social-pragmatic theories of language learning [@clark2009first; @tomasello2009constructing], our theory is based on the following premises: information sources serve different functional roles but are combined as part of an integrated social inference process [@clark1996using; @grice1991studies; @shafto2012learning; @sperber2001relevance].
 Children use all available information to make inferences about the intentions behind a speaker’s utterance, which then leads them to correctly identify referents in the world and learn conventional word–object mappings.
@@
 In the remainder of this paper, we rigorously test this theory by asking how well it serves the two purposes of any psychological theory: prediction and explanation [@shmueli2010explain; @yarkoni2017choosing].
-First, we use the model to make quantitative predictions about children's behavior in new situations - predictions we test against new data.
-Next, we test how well the model explains the integration process by comparing it to alternative models that make different assumptions about *whether* information is integrated, *how* it is integrated and how the integration process *develops*.
+First, we use the model to make quantitative predictions about children’s behavior in new situations -- predictions we test against new data.
+This form of model testing has been successfully used with adults [@frank2012predicting; @lake2015human] and here we extend it to children.
+Next, we quantify how well the model explains the integration process by comparing it to alternative models that make different assumptions about *whether* information is integrated, *how* it is integrated, and how the integration process *develops.*
 
-We focus on three information sources that play an integral part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle; @sperber2001relevance], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using; @clark2015common], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].
-These information sources operate on different timescales: while (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development.
-This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word].
+We focus on three information sources that play a central part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle; @sperber2001relevance], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using; @clark2015common], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].
 
 Our *rational integration model* arbitrates between information sources via Bayesian inference (see Fig.
-1f for model formula).
-A listener ($L_{1}$) reasons about the referent of a speaker's ($S_{1}$) utterance.
+1f for model formulae).
+A listener ($L_{1}$) reasons about the referent of a speaker’s ($S_{1}$) utterance.
 This reasoning is contextualized by the prior probability of each referent $\rho$ -- which we take to be a function of the common ground shared between the listener and the speaker.
@@
 Naturally, this reasoning depends on what kind of semantic knowledge (for object j) $\theta$~j~ the speaker ascribes to the (literal) listener.
+
 Taken together, this model provides a quantitative theory of information integration during language learning.
+The three information sources operate on different timescales: speaker informativeness is a momentary expectation about a particular utterance, common ground grows over the course of a conversation, and semantic knowledge is learned across development.
+This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word], and we link these different time-dependent processes together via their hypothesized impact on model components.
 Furthermore, the model presents an explicit and substantive theory of development.
 It assumes that, while children’s sensitivity to the individual information sources increases with age, the way integration proceeds remains constant [@bohn2019pervasive; @bohn_tessler_merrick_frank_2019].
-In the model, this is accomplished by making the parameters capturing sensitivity to speaker informativeness ($\alpha$~i~, Fig.
+In the model, this is accomplished by creating age-dependent parameters capturing developmental changes in sensitivity to speaker informativeness ($\alpha$~i~, Fig.
 1d), the common ground ($\rho$~i~, Fig.
 1c), and object specific semantic knowledge ($\theta$~i,j~, Fig.
-1e) a function of the child’s age.
+1e).
 
@@
 The request in (iv) licenses an inference based on expectations about how informative speakers are (red).
-Listeners' semantic knowledge enters the task because the identity of the  known object on one of the tables is varied from well-known objects like a duck to relatively unfamiliar objects like a chess pawn (total of 12 objects - blue).
-(a) shows the condition in which common ground information is congruent (i.e.
-point to the same object) with speaker informativeness and (b) shows the incongruent condition.
+Listeners’ semantic knowledge enters the task because the identity of the known object on one of the tables is varied from well-known objects like a duck to relatively unfamiliar objects like a chess pawn (total of 12 objects -- blue).
+(a) shows the version of the experiment in which common ground information is congruent (i.e., point to the same object) with speaker informativeness and (b) shows the incongruent condition.
 The congruent and incongruent conditions are each paired with the 12 known objects, resulting in 24 unique conditions.
@@
 
-To test the predictive and explanatory power of our model, we developed a world-learning paradigm in which we jointly manipulated the three information sources (Fig.
+To test the predictive and explanatory power of our model we designed a world-learning experiment in which we jointly manipulated the three information sources (Fig.
 1).
 Children interacted on a tablet computer with a series of storybook speakers [@frank2016using].
-The speakers used novel words (e.g., "wug") in the context of two potential referents.
 This situation is depicted in Fig.
 1a iv, in which a speaker (here, a frog) appears with a known object (a duck, left) and an unfamiliar object (the diamond-shaped object, right).
-To identify the referent, the child could rely upon the three information sources described above.
-First, they may infer that a cooperative speaker would have used the word "duck" to refer to the known object (the duck); the fact that the speaker did not say duck then suggests that the speaker is most likely referring to a different object (the unfamiliar object).
+The speakers used a novel word (e.g., "wug") in the context of two potential referents, and then the child was asked to identify a new instance of the novel word, testing their inference about the speaker’s intended referent.
+To vary the strength of the child’s inference, we systematically manipulated the familiarity of the known object (from e.g., the highly familiar "duck" to the relatively unfamiliar "pawn") and whether the familiar or novel object was new to the speaker (meaning that it was not part of common ground).
+
+This paradigm allows us to examine the integration of the three information sources described above.
+First, the child may infer that a cooperative and informative speaker [@clark1987principle; @frank2014inferring] would have used the word "duck" to refer to the known object (the duck); the fact that the speaker did not say "duck" then suggests that the speaker is most likely referring to a different object (the unfamiliar object).
 This basic inference is oftentimes referred to as a mutual exclusivity inference [@markman1988children; @halberda2003development].
-More generally speaking, the listener can infer the referent of the novel word by assuming that the speaker is a rational agent who chooses the most informative words to refer to objects [@clark1987principle; @frank2014inferring].
-Second, the child may rely upon what has already been established in the common ground with the speaker.
+Second, the child may draw upon what has already been established in the common ground with the speaker.
 Listeners expect speakers to communicate about things that are new to the common ground [@akhtar1996role; @diesendruck2004two].
@@
 1a and b i-iii).
-Finally, the child may rely upon their previously acquired semantic knowledge, that is, how sure they are that the known object is called "duck".
-If the known object is something less familiar, such as a chess piece (e.g., a pawn), a 3-year-old child may draw a weaker inference, if they draw any inference at all [@lewis2020-me; @grassmann2015children].
+Finally, the child may use their previously acquired semantic knowledge, that is, how sure they are that the known object is called "duck".
+If the known object is something less familiar, such as a chess piece (e.g., a pawn), a 3-year-old child may draw a weaker inference, if they draw any inference at all [@lewis2020-me; @grassmann2015children; @ohmerreinforcement].
 Taken together, the child has the opportunity to integrate their assumptions about (1) cooperative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge.
-In some versions of the experiment, some of these information sources were aligned (Fig.
-1a) but in some they were in conflict (Fig.
+In one condition of the experiment, information sources were aligned (Fig.
+1a) while in the other they were in conflict (Fig.
 1b).
@@
 
-We tested the model in its ability to predict children’s actual behavior - at an age (between 2 and 5 years) at which they learn language at an exponential rate [@bloom2002children].
-We estimated children’s (N=148) developing sensitivity to individual information sources in separate experiments (Experiment 1 and 2) (see Fig.
+We tested the model in its ability to predict 2 - 5 year-old children’s judgments about word meaning.
+We estimated children’s (N=148) developing sensitivity to individual information sources in two separate experiments (Experiments 1 and 2; see Fig.
 1c-e).
-We then generated parameter-free, quantitative, *a priori* model predictions (developmental trajectories) representing the model's expectations about how children should behave in a new situation in which all three information sources had to be integrated.
-We generated model predictions for 24 experimental conditions: 12 objects of different familiarities (requiring different levels of semantic knowledge), with novelty either conflicting or coinciding; Fig.
+We then generated parameter-free *a priori* model predictions (developmental trajectories) representing the model’s expectations about how children should behave in a new situation in which all three information sources had to be integrated.
+We generated predictions for 24 experimental conditions: 12 objects of different familiarities (requiring different levels of semantic knowledge), with novelty either conflicting or coinciding; Fig.
 1.
 We compared these predictions to newly collected data from N = 220 children from the same age range (Experiment 3).
+All procedures, sample sizes and analysis were pre-registered (see methods).
 
@@
 S6).
-For a more quantitative analysis, we binned predictions and data by year and correlated them.
+For a more quantitative analysis, we binned predictions and data by child age (in years) and correlated the two.
 We found a high correlation, with the model explaining 79% of the variance in the data (Fig.
 2a).
-These results seem to support the assumptions in the model that children integrate all available information sources.
-However, it is still possible that simpler models might make equally good -- or even better -- predictions.
+These results support the assumption of the model that children integrate three all available information sources.
+However, it is still possible that simpler models might make equally good – or even better – predictions.
 
@@
 2b).
-These models assume that children follow the heuristic “ignore X” (with X being one of the information sources) when multiple information sources are presented together.
+These models assume that children follow the heuristic "ignore $x$" (with $x$ being one of the information sources) when multiple information sources are presented together.
 
-The *no word knowledge model* uses the same model architecture as the rational integration model.
-It takes in expectations about speaker informativeness and common ground, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge).
-That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge.
-The *no common ground model* takes in object specific semantic knowledge and speaker informativeness but ignores common ground information.
+The no *word knowledge model* uses the same model architecture as the rational integration model.
+It uses expectations about speaker informativeness and common ground but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge).
+That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age-specific average semantic knowledge.
+The *no common ground model* takes in object-specific semantic knowledge and speaker informativeness but ignores common ground information.
 Instead of assuming that one object has a higher prior probability to be the referent because it is new in context, the speaker thinks that both objects are equally likely to be the referent.
 As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources.
-Finally, according to the *no speaker informativeness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance.
+Finally, according to the *no speaker informativeness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the utterance.
 As a consequence, the inference is solely based on common ground expectations.
 
-We found little support that children make inferences following one of the heuristic models (Fig.
+We found little support for these heuristic models (Fig.
 2b).
-When using Bayesian model comparison via marginal likelihood of the data, [@lee2014bayesian], we find that the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Fig.
+When using Bayesian model comparison via marginal likelihood of the data [@lee2014bayesian], we find that the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Fig.
 2).
-Taken together, we may conclude that children considered all available information sources.
+Figure 2c exemplifies the differences between the models: all heuristic models systematically underestimate children’s performance in the congruent condition.
+Thus, even when the information sources are redundant (i.e.
+they all point to the same referent), children’s inferences are notably strengthened by each of them.
+In the incongruent condition, the no word knowledge model underestimates performance, because it does not differentiate between the different familiar objects, and in the case of a highly familiar word such as duck, underestimates the strength of the mutual exclusivity inference and its compensatory effect.
+The no speaker informativeness completely ignores this inferences, which leads to even worse predictions.
+On the contrary, the no common ground model overestimates performance because it ignores the dampening effect of common ground pointing to a different referent.
+Taken together, we conclude that children considered all available information sources.
 
@@
 3).
-The no word knowledge model includes developmental change for overall vocabulary development but ignores the identity of the known object.
-The no common ground model assumes that children ignore information from common ground and the no speaker informativeness model assumes that children ignore inferences that are licensed by expectations about informative communication.
 BF~10~ gives the Bayes Factor in favor of the integration model based on the marginal likelihood of the data under each model.
+(c) Predictions from all models considered alongside the data (with 95% HDI) for two experimental conditions (familiar word: *duck*).
 
@@
 
-The fact that children integrated all the available information sources may be surprising, but does not rule out that the integration process itself might be different from the one described in the rational integration model, which assumes that all information sources enter into an integrated inference process.
-However, a more modular view seems equally plausible: children might compute separate inferences based on a subset of the available information and then integrate them by weighting them according to some ratio.
+In the previous section, we established that children integrated all available information sources.
+This result, however, does not speak to the process by which information is assumed to be integrated.
+Thus, in this section, we ask which integration process best explains children’s behavior.
+
+The rational integration model assumes that all information sources enter into a joint inference process, but alternative integration processes are conceivable and might be consistent with the data.
+For example, the "bag of tricks" [@bloom2002children] hypothesis mentioned in the introduction could be re-phrased as a modular integration process: children might compute independent inferences based on subsets of the available information and then integrate them in a post-hoc manner by weighting them according to some parameter.
 This view would allow for the possibility that some information sources are considered to be more important than others.
@@
 This model assumes that semantic knowledge and expectations about speaker informativeness enter into one inference (mutual exclusivity inference [@markman1988children; @lewis2020-me; @clark1987principle]) while common ground information enters into a second one.
-The outcome of both processes are then weighted according to the parameter $\phi$.
-Like the rational integration model, this model takes in all available information sources in an age sensitive way and assumes that they are integrated - the only difference lies in the nature of the integration process.
+The outcomes of both processes are then weighted according to the parameter $\phi$.
+Like the rational integration model, this model takes in all available information sources in an age-sensitive way and assumes that they are integrated.
+The only difference lies in the nature of the integration process: the biased integration model privileges some information sources of others in an ad-hoc manner.
 
 The parameter $\phi$ in the biased integration model is unknown ahead of time and has to be estimated based on the experimental data.
-That is, in contrast to the rational integration model, the biased integration model does not allow to make *a priori* predictions about new data in the way we describe above.
-For the model comparison, we therefore constrained the parameters in the rational integration model by the data from EXperiment 3 as well.
-As a consequence, both models use all the information available to constrain their parameters (see Fig.
+That is, in contrast to the rational integration model, the biased integration model has an additional degree of freedom which does not allow us to make *a priori* predictions about new data in the way we describe above.
+For a fair comparison, we therefore constrained the parameters in the rational integration model by the data from Experiment 3 as well.
+As a consequence, both models use all the data available to constrain their parameters (see Fig.
 S4).
@@
 
-The biased integration model makes reasonable predictions that explain a large proportion of the variance in the data (Fig.
+The biased integration model makes reasonable predictions and explains 78% of the variance in the data (Fig.
 3b).
-The parameter $\phi$ - indicating the bias to one of the inferences - was estimated to favor the mutual exclusivity inference (mode = `r phi%>%pull(mode)`; 95% highest density interval (HDI): `r phi%>%pull(lci)` - `r phi%>%pull(uci)`, see Fig.
+The parameter $\phi$ -- indicating the bias to one of the inferences -- was estimated to favor the mutual exclusivity inference (Maximum A-Posteriori estimate = `r phi%>%pull(mode)`; 95% highest density interval (HDI): `r phi%>%pull(lci)` - `r phi%>%pull(uci)`, see Fig.
 3d).
-However, the rational integration model presented a much better fit to the data, both in terms of correlation and marginal likelihood of the data (Fig.
+However, the rational integration model presented a much better fit to the data, both in terms of correlation and the marginal likelihood of the data (Fig.
 3).
-Thus, a fully integrated - as opposed to a sequential and biased - integration process explained the data better.
+Figure 3e exemplifies the difference between the models: the biased integration model puts extra weight on the mutual exclusivity inference and thus fails to capture performance when this inference is weak compared to the common ground inference -- such as in the congruent condition for younger children.
+Thus, a fully integrated -- as opposed to a modular and biased -- integration process explained the data better.
 
 The rational integration model assumes that the integration process itself does not change with age [@bohn2019pervasive].
-That is, while children's sensitivity to each information source develops, the way they relate to one another remains the same.
-An alternative perspective would be to assume that the integration process itself changes with age.
-The biased integration model provides a way to think about developmental change in the integration process: Children are biased towards some information sources, but the bias itself changes with age.
+That is, while children’s sensitivity to each information source develops, the way they relate to one another remains the same.
+The biased integration model provides an alternative proposal about developmental change, one in which the integration process itself changes with age.
+That is, children may be biased towards some information sources, and that bias itself may change with age.
 We formalize such an alternative view as a *developmental bias model* which is structurally identical to the biased integration model but in which the parameter $\phi$ changes with age.
@@
 
-The developmental bias model also explains a substantial portion of the variance in the data (Fig.
+The developmental bias model also explains a substantial portion of the variance in the data: 78% (Fig.
 3c).
-The estimated developmental trajectory for the bias parameter $\phi$ suggests that younger children put a higher emphasis on common ground information, while older children rely more on the mutual exclusivity inference (Fig.
+The estimated developmental trajectory for the bias parameter $\phi$ suggests that younger children put a stronger emphasis on common ground information, while older children rely more on the mutual exclusivity inference (Fig.
 3d).
@@
 3).
-Interestingly, when we compared the rational integration model with its parameters not constrained by the experimental data (i.e.
+Looking at Figure 3e, we can see that the developmental bias model tends to underestimate children’s performance because the supportive interplay between the different inferences is constrained.
+
+Finally, when we compared the rational integration model with its parameters not constrained by the experimental data (i.e.
 the "pure" prediction model described above), it also outperformed both bias models (see Fig.
@@
 (a) Model predictions from the rational integration model (colored lines) next to the behavioral data (dotted black lines with 95% CI in gray) for all 24 experimental conditions.
-Top row (blue) shows conditions in which common ground information is congruent with speaker informativeness, bottom row (red) shows conditions in which they are incongruent.
-Known objects are ordered based on their rated age of acquisition (left to right).
+Top row (blue) shows congruent conditions, bottom row (red) shows incongruent conditions.
+Familiar objects are ordered based on their rated age of acquisition (left to right).
 Light dots represent individual data points.
-(b) Correlations between model predictions binned by age and condition for the integration model and (c) the two mixture models.
+(b) Correlations between model predictions binned by age and condition for the integration model and (c) the two biased models.
 Vertical and horizontal error bars show 95% HDIs.
 BF~10~ gives the Bayes Factor in favor of the rational integration model based on the marginal likelihood of the data under each model.
-(d) Posterior distribution of the bias parameter in the biased integration model and developmental trajectories for the bias parameter in the developmental bias model based on 300 random draws from the posterior distribution of the intercept and slope.
+(d) Posterior distribution of the bias parameter in the biased integration model and developmental trajectories for the bias parameter in the developmental bias model (e) Predictions from all models considered alongside the data (with 95% HDI) for two experimental conditions (familiar word: duck).
 
@@
 The environment in which children learn language is complex.
-Children have to integrate different information sources, some of which relate to expectations in the moment, others to the dynamics of the unfolding interactions and yet others to their previously acquired knowledge.
-Our findings show that young children can flexibly integrate multiple information sources during language learning - even from relatively early in development.
+Children have to integrate different information sources, some of which relate to expectations in the moment, others to the dynamics of the unfolding interactions, and yet others to their previously acquired knowledge.
+Our findings show that young children can integrate multiple information sources during language learning -- even from relatively early in development.
 To answer the question of how they do so, we presented a formal cognitive model that assumes that information sources are rationally integrated via Bayesian inference.
@@
 Our model is based on classic social-pragmatic theories on language use and comprehension [@clark1996using; @grice1991studies; @sperber2001relevance; @tomasello2009constructing].
-As a consequence, instead of assuming that different information sources feed into separate word-learning mechanisms, we assume that they all play a functional role in an integrated social inference process.
-Our model goes beyond previous theoretical and empirical work by specifying the computations that may underlie this inference process.
-Furthermore, we present a substantive theory about how this integration process develops: We assume that children become increasingly sensitive to different information sources but that the way these information sources are integrated, remains the same.
-We used this model to predict and explain children's information integration in a new word learning paradigm in which they had to integrate (1) their assumptions about informative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge.
+As a consequence, instead of assuming that different information sources feed into separate word-learning mechanisms, we assume that all of these information sources play a functional role in an integrated social inference process.
+Our model goes beyond previous theoretical and empirical work by specifying the computations that underlie this inference process.
+Furthermore, we present a substantive theory about how this integration process develops: We assume that children become increasingly sensitive to different information sources, but that the way these information sources are integrated remains the same.
+We used this model to predict and explain children’s information integration in a new word learning paradigm in which they had to integrate (1) their assumptions about informative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge.
 
-We found that this rational integration model made accurate quantitative predictions across a range of experimental conditions - in some of which information sources were aligned, in some of which they were in conflict.
+We found that this rational integration model made accurate quantitative predictions across a range of experimental conditions both when information sources were aligned and were in conflict.
 Predictions from the model better explained the data compared to lesioned models which assumed that children ignore one of the information sources, suggesting that children used all available information.
-
-To test the explanatory power of the model - how well it explains the process by which information is integrated - we formalized an alternative, modular, view.
+To test the explanatory power of the model -- how well it explains the process by which information is integrated -- we formalized an alternative, modular, view.
 According to the biased integration model, children use all available information sources but compute separate inferences based on a subset of them.
-Integration happens by weighting the outcomes of these separate inferences by some ratio.
-By allowing the ratio to be in favor of one of the inferences, this model captures the idea that children might be biased to some information sources over others.
-Even though such a model made reasonable predictions, we found that the rational integration model explained children's behavior much more accurately.
+Integration happens by weighing the outcomes of these separate inferences by some parameter.
 Finally, we tested an alternative view on the development of the integration process.
 According to the developmental bias model, the importance of the different information sources changed with age.
-Again, the rational integration model provided a much better fit to the data, suggesting that the integration process remains stable over time.
+In both cases, the rational integration model provided a much better fit to the data, suggesting that the integration process remains stable over time.
 
@@
 Thus, it can be generalized in a natural way to capture word learning in contexts that offer more, fewer, or different types of information.
-For example, in a recent study with adults and children, Bohn and colleagues [@bohn_tessler_merrick_frank_2019] manipulated expectations about informativeness and common ground in a different way.
-Using a structurally similar model, they also found a close alignment between model predictions and the data.
+For example, in a recent study with adults and children, we manipulated expectations about informativeness and common ground in a different way.
+Using a structurally similar model [@bohn_tessler_merrick_frank_2019], we also found a close alignment between model predictions and the data.
 The flexibility of this modeling framework stems from its conceptualization of human communication as a form of rational social action.
@@
 
-There are multiple ways in which the model and the experiments presented here could be extended.
-First, it would be important to replicate our findings in a more diverse sample, that is, with children from a different cultural background who learn a different language [@nielsen2017persistent].
-In such a study, we would not expect that our results replicate in a strict sense; that is, we would not expect to see the same developmental trajectories in all cultures and/or languages.
+Our model and empirical paradigm provide a foundation on which to test deeper questions about language development.
+First, our findings should be replicated in children from different cultural backgrounds, learning different languages [@nielsen2017persistent].
+In such studies, we would not expect our results to replicate in a strict sense; that is, we would not expect to see the same developmental trajectories in all cultures and languages.
 Substantial variation is much more likely.
-Nevertheless, our computational model provides a way to think about how to reconcile cross-cultural variation with a universal cognitive architecture: We expect differences in how sensitive children are to the individual information sources at different ages, but similarities in how information is integrated [@bohn2019pervasive].
+Nevertheless, our model provides a way to think about how to reconcile cross-cultural variation with a shared cognitive architecture: We predict differences in how sensitive children are to the individual information sources at different ages, but similarities in how information is integrated [@bohn2019pervasive].
 In computational terms, we assume a universal architecture that specifies the relation between a set of varying parameters.
+Of course, either confirmation or disconfirmation of this prediction would be informative.
 
@@
 In its current form, our model does not specify how the listener arrives at the expectation that some objects are more likely referents because they are new in common ground.
-We assume that common ground changes speaker's expectations about what are likely referents [@hanna2003effects] and measured these expectations to inform the parameter values in our model.
-Computationally, the model does not differentiate between common ground information and other reasons that might make an object contextually more salient.
+We assumed that common ground changes the speaker’s expectations about what are likely referents [@hanna2003effects] and we measured these expectations to inform the parameter values in our model.
+But computationally, the model does not differentiate between common ground information and other reasons that might make an object contextually more salient.
 
 Finally, our model is a model of referent identification in the moment of the utterance.
-Word learning, however, is a cumulative process which happens across multiple time points and contexts.
-Thus, it would be fruitful to connect our model with frameworks that focus on the temporal and cross-situational aspects of word learning [@frank2009using; @mcmurray2012word; @yurovsky2015integrative].
+At the same time, the constructs made use of by our model are shaped by factors that unfold across multiple time points and contexts:  Common ground is built over the course of a conversation, and the lexical knowledge of a child is shaped across a language developmental time-scale.
+Our model makes use of unidimensional representations of these high-dimensional, structured processes and examines how these representations are integrated.
+Connecting our model with frameworks that focus on the temporal and cross-situational aspects of word learning would elucidate further these complex, time-dependent processes [@frank2009using; @mcmurray2012word; @yurovsky2015integrative].
 
-Taken together, this work helps us understand how children navigate the complexity of their learning environment.
-Methodologically, it illustrates how formal, computational models can be used to test theories - bot in terms of their predictive and explanatory power.
-From a theoretical perspective, it adds to broader frameworks that see the onto- and phylogenetic emergence of language as deeply rooted in social cognition.
+Taken together, we hope this work advances our understanding of how children navigate the complexity of their learning environment.
+Methodologically, it illustrates how computational models can be used to test theories; from a theoretical perspective, it adds to broader frameworks that see the onto- and phylogenetic emergence of language as deeply rooted in social cognition.
 
@@
 A more detailed description of the experiments and the models can be found in the supplementary material.
-The experimental procedure, sample size and analysis for each experiment were pre-registered (https://osf.io/7rg9j/registrations).
+The experimental procedure, sample size, and analysis for each experiment were pre-registered (https://osf.io/7rg9j/registrations).
 Experimental procedures, model and analysis scripts can be found in an online repository (https://github.com/manuelbohn/spin).
-Experiment 1 and 2 were designed to estimate children's developing sensitivity to each information source.
-Their results inform the parameter values in the model (see Fig.
+Experiments 1 and 2 were designed to estimate children’s developing sensitivity to each information source.
+The results of these experiments determine the parameter values in the model (see Fig.
 1 c-f).
-Experiment 3 was designed to test how children integrate the different information sources.
+Experiment 3 was designed to test how children integrate different information sources.
 
@@
 Experiment 1 involved `r length(unique(me_data$subid))` children, including `r length(unique(me_data$subid[me_data$subage == 2]))` 2-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 2]),2), nsmall = 2)`, 15 girls), `r length(unique(me_data$subid[me_data$subage == 3]))` 3-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 3]),2), nsmall = 2)`, 22 girls) and  `r length(unique(me_data$subid[me_data$subage == 4]))` 4-year-olds (range = `r format(round(min(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(me_data$age_num[me_data$subage == 4]),2), nsmall = 2)`, 16 girls).
-Data from 10 additional children was not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1).
+Data from 10 additional children were not included because they were either exposed to less than 75% of English at home (5), did not finish at least half of the test trials (2), the technical equipment failed (2) or their parents reported an autism spectrum disorder (1).
 
 In Experiment 2, we tested `r length(unique(prior_data$subid))` children from the same general population as in Experiment 1, including `r length(unique(prior_data$subid[prior_data$subage == 2]))` 2-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 2]),2), nsmall = 2)`, 7 girls), `r length(unique(prior_data$subid[prior_data$subage == 3]))` 3-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 3]),2), nsmall = 2)`, 14 girls) and  `r length(unique(prior_data$subid[prior_data$subage == 4]))` 4-year-olds (range = `r format(round(min(prior_data$age_num[prior_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(prior_data$age_num[prior_data$subage == 4]),2), nsmall = 2)`, 14 girls).
-Data from 5 additional children was not included because they were either exposed to less than 75% of English at home (3) or the technical equipment failed (2).
+Data from 5 additional children were not included because they were either exposed to less than 75% of English at home (3) or the technical equipment failed (2).
 
 Finally, Experiment 3 involved `r length(unique(comb_data$subid))` children, including `r length(unique(comb_data$subid[comb_data$subage == 2]))` 2-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 2]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 2]),2), nsmall = 2)`, 7 girls), `r length(unique(comb_data$subid[comb_data$subage == 3]))` 3-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 3]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 3]),2), nsmall = 2)`, 14 girls) and  `r length(unique(comb_data$subid[comb_data$subage == 4]))` 4-year-olds (range = `r format(round(min(comb_data$age_num[comb_data$subage == 4]),2), nsmall = 2)` - `r format(round(max(comb_data$age_num[comb_data$subage == 4]),2), nsmall = 2)`, 14 girls).
-Data from 20 additional children was not included because they were either exposed to less than 75% of English at home (15), did not finish at least half of the test trials (3) or the technical equipment failed (2).
+Data from 20 additional children were not included because they were either exposed to less than 75% of English at home (15), did not finish at least half of the test trials (3) or the technical equipment failed (2).
 
-All participants were recruited from the floor of a Children’s museum in San José, California, USA.
-This population is characterized by a diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status.
+All participants were recruited in a children’s museum in San José, California, USA.
+This population is characterized by a diverse ethnic background (predominantly White, Asian, or mixed-ethnicity) and high levels of parental education and socioeconomic status.
 Parents consented to their children’s participation and provided demographic information.
@@
 
-All experiments were presented as an interactive picture book on a tablet computer [@frank2016using].
+All experiments were presented as an interactive picture book on a tablet computer.
+Tablet-based storybooks are commonly used to simulate social interactions in developmental research and interventions [@richter2017comparing].
+A recent, direct comparison found similar performance with tablet-based and printed storybooks in a word learning paradigm [@frank2016using].
+Furthermore, our results in Experiment 1 and 2 replicate earlier studies on mutual exclusivity and discourse novelty that used live interactions instead of storybooks [@akhtar1996role; @diesendruck2004two].
+
 Fig.
@@
 
-Experiment 1 tested the so-called mutual exclusivity inference [@markman1988children; @lewis2020-me].
-On one table, there was a familiar object, on the other table, there was an unfamiliar object (drawn for the purpose of the study) (Fig.
+Experiment 1 tested the mutual exclusivity inference [@markman1988children; @lewis2020-me].
+On one table, there was a familiar object, on the other table, there was an unfamiliar object (a novel design drawn for the purpose of the study) (Fig.
 1a/b iv and Fig.
@@
 Each child completed 12 trials, each with a different familiar and a different unfamiliar object.
-Familiar objects were selected to vary along the dimension of how likely children were to know the word for it.
-This included objects that most 2-year-olds can name (e.g.
+We used familiar objects that we expected to vary along the dimension of how likely children were to know the word for it.
+This set included objects that most 2-year-olds can name (e.g.
 a duck) as well as objects that only very few 5-year-olds can name (e.g.
-a pawn).
-The selection was based on age of acquisition ratings from Kuperman and colleagues [-@kuperman2012age].
+a pawn [chess piece]).
+The selection was based on the age of acquisition ratings from Kuperman and colleagues [-@kuperman2012age].
 While these ratings do not capture the absolute age when children acquire these words, they capture the relative order in which words are learned.
@@
 
-Experiment 2 tested children's sensitivity to common ground that is built up over the course of a conversation.
+Experiment 2 tested children’s sensitivity to common ground that is built up over the course of a conversation.
 In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two].
@@
 Then the speaker returned and requested an object in the same way as in Experiment 1.
-The positioning of the unfamiliar object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced.
-Children received five trials, each with a different pair of unfamiliar objects.
-We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.
+The positioning of the unfamiliar object at the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced.
+Children completed five trials, each with a different pair of unfamiliar objects.
+We coded as correct choice if children chose as the referent of the novel word the object that was new to the speaker.
 
-Experiment 3 combined the procedures from Experiment 1 and 2.
+Experiment 3 combined the procedures from Experiments 1 and 2.
 It followed the same procedure as Experiment 2 but involved the same objects as Experiment 1 (Fig.
@@
 After commenting on the presence or absence of an object on each table, the speaker disappeared and a second object appeared (familiar or unfamiliar).
-Next, the speaker re-appeared and made the usual request.
+Next, the speaker re-appeared and made the usual request ("Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?").
 In the congruent condition, the familiar object was present in the beginning and the unfamiliar object appeared while the speaker was away (Fig.
 1a and Fig.
-S1c - left).
-In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent.
+S1c -- left).
+In this case, both the mutual exclusivity and the common ground inference pointed to the novel object as the referent (i.e., it was both novel to the speaker in the context and it was an object that does not have a label in the lexicon).
 In the incongruent condition, the unfamiliar object was present in the beginning and the familiar object appeared later.
@@
 1b and Fig.
-S1c - right).
-This resulted in a total of 2 (congruent vs incongurent) x 12 (familiar objects) = 24 different conditions.
+S1c -- right).
+This resulted in a total of 2 alignments (congruent vs incongruent) x 12 familiar objects = 24 different conditions.
 Participants received up to 12 test trials, six in each alignment condition, each with a different familiar and unfamiliar object.
 Familiar objects were the same as in Experiment 1.
-The positioning of the objects on the tables, the speaker and the location the speaker first turned to were counterbalanced.
+The positioning of the objects on the tables, the speaker, and the location the speaker first turned to were counterbalanced.
 Participants could stop the experiment after six trials (three per alignment condition).
-If a participant stopped after half of the trials, we tested an additional participant to reach the preregistered number of data points per age group (2-, 3- and 4-year-olds).
+If a participant stopped after half of the trials, we tested an additional participant to reach the pre-registered number of data points per age group (2-, 3- and 4-year-olds).
 
@@
 
-To analyze how the manipulations in each experiment affected children's behavior, we used generalized linear mixed models.
+To analyze how the manipulations in each experiment affected children’s behavior, we used generalized linear mixed models.
 Since the focus of the paper is on how information sources were integrated, we discuss these models in the supplementary material and focus here on the cognitive models instead.
 A detailed, mathematical description of the different cognitive models along with details about estimation procedures and priors can be found in the supplementary material.
-All Bayesian cognitive models and Bayesian data analytic models were implemented in the probabilistic programming language `WebPPL` [@dippl].
+All cognitive models and Bayesian data analytic models were implemented in the probabilistic programming language `WebPPL` [@dippl].
 The corresponding model code can be found in the associated online repository.
 
-As a first step, we used the data from Experiment 1 and 2 to estimate children's developing sensitivity to each information source.
-To estimate the parameters for semantic knowledge ($\theta$) and speaker informativeness ($\alpha$), we adapted the rational integration model to a situation in which both objects (novel and familiar) have equal prior probability (i.e., no common ground information).
-We used the data from Experiment 1 to then infer the parameters.
-That is, we inferred the intercepts and slopes for speaker informativeness (linear regression) and semantic knowledge (logistic regression) that generated model predictions to match the responses generated in Experiment 1.
+As a first step, we used the data from Experiments 1 and 2 to estimate children’s developing sensitivity to each information source.
+To estimate the parameters for semantic knowledge ($\theta$) and speaker informativeness ($\alpha$), we adapted the rational integration model to model a situation in which both objects (novel and familiar) have equal prior probability (i.e., no common ground information).
+We used the data from Experiment 1 to then infer the semantic knowledge and speaker informativeness parameters in an age-sensitive manner.
+Specifically, we inferred the intercepts and slopes for speaker informativeness via a linear regression submodel and semantic knowledge via a logistic regression submodel, the values of which were then combined in the cognitive model to generate model predictions to predict the responses generated in Experiment 1.
 To estimate the parameters representing sensitivity to common ground ($\rho$), we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in Experiment 2.
-For the explanation models, these parameters were additionally constrained by the data from Experiment 3.
+For the "prediction" models, the parameters whose values were inferred by the data from Experiments 1 & 2 were then used to make out-of-sample predictions for Experiment 3.
+For the "explanation" models, these parameters were additionally constrained by the data from Experiment 3.
 A more detailed description of how these parameters were estimated (including a graphical model) can be found in the supplementary material.
@@
 
-The rational integration model is defined as $P^{int}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i)$.
+The rational integration model is a mapping from an utterance u to a referent r, defined as $P^{int}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i)$ where $i$ represents the age of the participant and the $j$ the familiar object.
 The three lesioned models that were used to compare how well the model predicts new data are reduced versions of this model.
-The no word knowledge model uses the same model architecture: $P^{no\_wk}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{i}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{i}\}) \cdot P(r \mid \rho_i)$ and the only difference lies in the parameter $\theta$.
-The object specific parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model.
-That is, there is an overall developmental trajectory for semantic knowledge (main effect - $\theta_{i}$) and then there is object-specific variation around this trajectory (random effects -- $\theta_{ij}$).
+The no word knowledge model uses the same model architecture: $P^{no\_wk}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{i}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{i}\}) \cdot P(r \mid \rho_i)$ and the only difference lies in the parameter $\theta$, which does not vary as a function of $j$, the object (i.e., $\theta$ in this model is analogous to a measure of gross vocabulary development).
+The object-specific parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model.
+That is, there is an overall developmental trajectory for semantic knowledge (main effect -- $\theta_{i}$) and then there is object-specific variation around this trajectory (random effects -- $\theta_{ij}$).
 Thus, the no word knowledge model takes in the overall trajectory for semantic knowledge ($\theta_{i}$) but ignores object-specific variation.
@@
 
-As noted above, the explanation models used parameters that were additionally constrained by the data from Experiment 3.
-This had no effect on the way these parameters were combined in the rational integration model.
+As noted above, the explanation models used parameters that were additionally constrained by the data from Experiment 3, but the way these parameters were combined in the rational integration model was the same as above.
 The biased integration model is defined as $P^{biased}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)$ with $P_{ME}$ representing a mutual exclusivity inference which takes in speaker informativeness and object specific semantic knowledge.
@@
 It is interpreted as how many times more likely the data is under one model compared to the other.
-Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by the prior probabilities of those parameter values); by averaging over the prior distribution on parameters, Bayes Factor implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the potential gains in predictive accuracy that a model with more parameters can achieve [@lee2014bayesian].
+Bayes Factors quantify the quality of predictions of a model, averaging over the possible values of the parameters of the models (weighted by the prior probabilities of those parameter values); by averaging over the prior distribution on parameters, Bayes Factors implicitly take into account model complexity because models with more parameters will tend to have a broader prior distribution over parameters, which in effect, can water down the potential gains in predictive accuracy that a model with more parameters can achieve [@lee2014bayesian].
 For this analysis, we treated age continuously.

### 2020-10-23 paper/supplementary_material.Rmd
prep for submission

@@
 ---
-title: "Young children rationally integrate semantic and pragmatic information sources to infer the meaning of words"
+title: "How young children integrate information sources to infer the meaning of words"
 subtitle: "Supplementary material"
@@
 
+```{r}
+#fig2 <- ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
+#ggsave(plot = fig2, "../figures/figureS2.png", width = 12, height = 4)
+```
+
 As a second step, we investigated how the inference changed as a function of age and the familiar object.
@@
 Dotted line indicates a level of performance expected by chance.
-C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", fig.width=12, fig.height = 4}
-ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
+C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", out.width="100%"}
+knitr::include_graphics("../figures/figureS2.png")
 ```

### 2020-11-26 paper/supplementary_material.Rmd
add AIS analysis files

@@
 ```{r}
-#fig2 <- ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
-#ggsave(plot = fig2, "../figures/figureS2.png", width = 12, height = 4)
+#fig2 <- ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.2,1), common.legend = F)
+#ggsave(plot = fig2, "../figures/figureS2.png", width = 12, height = 3, scale = 1.5)
 ```

### 2021-02-26 paper/manuscript.Rmd
add AIS analysis files
clean repo for revision

@@
 We specify a developmental model according to which children consider information sources in an age-specific way and integrate them via Bayesian inference.
-This model accurately predicted 2-to-5 year-old children’s word learning across a range of experimental conditions.
+This model accurately predicted 2-to-5 year-old children’s word learning across a range of experimental conditions in which they had to integrate three information sources.
 Model comparison suggests that the central locus of development is an increased sensitivity to individual information sources, rather than changes in  integration ability.
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 
@@
 
-Human communicative abilities are unrivaled in the animal kingdom[@taylor2016language; @tomasello2008origins; @fitch2010evolution].
+Human communicative abilities are unrivaled in the animal kingdom [@taylor2016language; @tomasello2008origins; @fitch2010evolution].
 Language -- in whatever modality -- is the medium that allows humans to collaborate and coordinate in species-unique ways, making it the bedrock of human culture and society [@smith1997major].
@@
 
-When information integration is studied directly, the focus is mostly on how children interpret an ambiguous referring expression in light of social-contextual information [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers; @kachel2021young].
+When information integration is studied directly, the focus is mostly on how children interpret or learn words in light of social-contextual information [@hollich2000breaking; @ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers; @kachel2021young].
 In one classic study [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it.
@@
 Children use all available information to make inferences about the intentions behind a speaker’s utterance, which then leads them to correctly identify referents in the world and learn conventional word–object mappings.
-We formalize the computational steps that underlie this inference process in a cognitive model [@frank2012predicting; @goodman2016pragmatic; @oberauer2019addressing].
+We formalize the computational steps that underlie this inference process in a cognitive model[@frank2012predicting; @goodman2016pragmatic; @oberauer2019addressing].
+In contrast to earlier modelling work, we treat word learning as the outcome of a social inference process instead of a cross-situational[@fazly2010probabilistic; @frank2009using] or principle-based learning process [@xu2007word].
 In the remainder of this paper, we rigorously test this theory by asking how well it serves the two purposes of any psychological theory: prediction and explanation [@shmueli2010explain; @yarkoni2017choosing].
@@
 This form of model testing has been successfully used with adults [@frank2012predicting; @lake2015human] and here we extend it to children.
-Next, we quantify how well the model explains the integration process by comparing it to alternative models that make different assumptions about *whether* information is integrated, *how* it is integrated, and how the integration process *develops.*
+Next, we quantify how well the model explains the integration process by comparing it to alternative models that make different assumptions about *whether* information is integrated, *how* it is integrated, and how the integration process *develops*.
+Alternative models either assume that children ignore some information sources or -- in line with a “bag of tricks” approach -- they assume that children compute isolated inferences and then weigh their outcome in a post-hoc manner.
 
@@
 A listener ($L_{1}$) reasons about the referent of a speaker’s ($S_{1}$) utterance.
-This reasoning is contextualized by the prior probability of each referent $\rho$ -- which we take to be a function of the common ground shared between the listener and the speaker.
+This reasoning is contextualized by the prior probability of each referent $\rho$.
+We treat $\rho$ as a conversational prior which originates from the common ground shared between the listener and the speaker.
+This interpretation follows from the social nature of our experiments (see below).
+From a modelling perspective, $\rho$ can be (and also also has been) used to capture non-social aspects of a referent, for example its visual salience[@frank2012predicting].
 To decide between referents, the listener ($L_{1}$) reasons about what a rational speaker ($S_{1}$) with informativeness $\alpha$ would say given an intended referent.
@@
 
-```{r fig1, include = T, fig.align = "center", fig.cap = "Experimental task and model.
+(ref:figlab1) **Experimental task and model**.
 (a and b) Screenshots from the experimental task.
-(i) The speaker encounters one object and then leaves the scene (ii).
-While the speaker is away, a second object appears (iii), when returning, the speaker uses a novel word to request an object (iv).
-Sections (i) to (iii) establish common ground between the speaker and the listener, in that one object is new in context (green).
-The request in (iv) licenses an inference based on expectations about how informative speakers are (red).
+(i) The speaker encounters one object and then leaves the scene.
+(ii) While the speaker is away, (iii) a second object appears, (iv) when returning, the speaker uses a novel word to request an object.
+Sections (i) to (iii) establish common ground between the speaker and the listener, in that one object is new in context (red).
+The request in (iv) licenses an inference based on expectations about how informative speakers are (gold).
 Listeners’ semantic knowledge enters the task because the identity of the known object on one of the tables is varied from well-known objects like a duck to relatively unfamiliar objects like a chess pawn (total of 12 objects -- blue).
-(a) shows the version of the experiment in which common ground information is congruent (i.e., point to the same object) with speaker informativeness and (b) shows the incongruent condition.
+(a) shows the condition of the experiment in which common ground information is congruent (i.e., point to the same object) with speaker informativeness and (b) shows the incongruent condition.
 The congruent and incongruent conditions are each paired with the 12 known objects, resulting in 24 unique conditions.
-(c to e) show developmental trajectories for each information source, estimated from separate experiments (see supplement).
-(f) gives the model equation for the rational integration model and links information sources to model parameters.", out.width="100%"}
+Developmental trajectories are shown for (c) sensitivity to common ground, (d) speaker informativeness and (e) semantic knowledge, estimated based on separate experiments (see main text).
+(f) gives the model equation for the rational integration model and links information sources to model parameters.
+
+```{r fig1, include = T, fig.align = "center", fig.cap = "(ref:figlab1)", out.width="100%"}
 knitr::include_graphics("./figures/figure1.png")
@@
 
-To test the predictive and explanatory power of our model we designed a world-learning experiment in which we jointly manipulated the three information sources (Fig.
+To test the predictive and explanatory power of our model we designed a word-learning experiment in which we jointly manipulated the three information sources (Fig.
 1).
@@
 1c-e).
+In Experiment 1, we jointly estimated children’s sensitivity to informativeness and their semantic knowledge.
+In Experiment 2, we estimated sensitivity to common ground.
 We then generated parameter-free *a priori* model predictions (developmental trajectories) representing the model’s expectations about how children should behave in a new situation in which all three information sources had to be integrated.
@@
 However, it is still possible that simpler models might make equally good – or even better – predictions.
+For example, work on children’s use of statistical information during word learning showed that their behaviour was best explained by a model which selectively ignored parts of the input [@gagliardi2017modeling].
 
@@
 The no speaker informativeness completely ignores this inferences, which leads to even worse predictions.
-On the contrary, the no common ground model overestimates performance because it ignores the dampening effect of common ground pointing to a different referent.
+On the contrary, the no common ground model overestimates performance because it ignores the dampening effect of common ground favoring a different referent.
 Taken together, we conclude that children considered all available information sources.
@@
 Like the rational integration model, this model takes in all available information sources in an age-sensitive way and assumes that they are integrated.
-The only difference lies in the nature of the integration process: the biased integration model privileges some information sources of others in an ad-hoc manner.
+The only difference lies in the nature of the integration process: the biased integration model privileges some information sources over others in an ad-hoc manner.
 
 The parameter $\phi$ in the biased integration model is unknown ahead of time and has to be estimated based on the experimental data.
-That is, in contrast to the rational integration model, the biased integration model has an additional degree of freedom which does not allow us to make *a priori* predictions about new data in the way we describe above.
+That is, through Experiment 1 and 2 alone, we do not learn anything about the relative importance of the information sources.
+As a consequence -- and in contrast to the rational integration model -- the biased integration model does not allow us to make *a priori* predictions about new data in the way we describe above.
 For a fair comparison, we therefore constrained the parameters in the rational integration model by the data from Experiment 3 as well.
-As a consequence, both models use all the data available to constrain their parameters (see Fig.
+As a consequence, both models estimate their parameters using all the data available in a fully Bayesian manner (see Fig.
 S4).
@@
 3).
-Figure 3e exemplifies the difference between the models: the biased integration model puts extra weight on the mutual exclusivity inference and thus fails to capture performance when this inference is weak compared to the common ground inference -- such as in the congruent condition for younger children.
-Thus, a fully integrated -- as opposed to a modular and biased -- integration process explained the data better.
+When constrained by the data from all experiments, the rational integration model explains 87% of the variance in the data.
+Fig.
+3e exemplifies the difference between the models: the biased integration model puts extra weight on the mutual exclusivity inference and thus fails to capture performance when this inference is weak compared to the common ground inference -- such as in the congruent condition for younger children.
+As a result, a fully integrated -- as opposed to a modular and biased -- integration process explained the data better.
 
@@
 Looking at Figure 3e, we can see that the developmental bias model tends to underestimate children’s performance because the supportive interplay between the different inferences is constrained.
-
-Finally, when we compared the rational integration model with its parameters not constrained by the experimental data (i.e.
-the "pure" prediction model described above), it also outperformed both bias models (see Fig.
-S10 and Tab.
-S6).
-Taken together, these results show that the integration process is best described as fully integrated and stable over time.
+In the biased models, the overall inference can only be as strong as the strongest of the components -- in the rational integration model, the components interact with one another, enabling a stronger overall inference.
 
@@
 
-Our work extends the study of information integration during language comprehension [@tanenhaus1995integration; @kamide2003integration; @hagoort2004integration; @ozyurek2007line; @heller2016perspective] to pragmatics.
+Previous work on  the study of information integration during language comprehension focused on how adults combine perceptual, semantic or syntactic information [@tanenhaus1995integration; @kamide2003integration; @hagoort2004integration; @ozyurek2007line; @heller2016perspective].
+Our work extends this work to the development of pragmatics.
 Our model is based on classic social-pragmatic theories on language use and comprehension [@clark1996using; @grice1991studies; @sperber2001relevance; @tomasello2009constructing].
-As a consequence, instead of assuming that different information sources feed into separate word-learning mechanisms, we assume that all of these information sources play a functional role in an integrated social inference process.
+As a consequence, instead of assuming that different information sources feed into separate word-learning mechanisms (the “bag of tricks” view), we assume that all of these information sources play a functional role in an integrated social inference process.
 Our model goes beyond previous theoretical and empirical work by specifying the computations that underlie this inference process.
@@
 In both cases, the rational integration model provided a much better fit to the data, suggesting that the integration process remains stable over time.
+That is, there is developmental continuity and therefore no qualitative difference in how a 2-year-old integrates information compared to a 4-year-old.
 
-The rational integration model is derived from a more general framework for pragmatic inference, which has been used to explain a wide variety of phenomena in adults’ language use and comprehension [@monroe2017colors; @wang2016learning; @tessler2019language; @yoon_frank_tessler_goodman_2018;@frank2012predicting; @goodman2016pragmatic].
+The rational integration model is derived from a more general framework for pragmatic inference, which has been used to explain a wide variety of phenomena in adults’ language use and comprehension [@monroe2017colors; @wang2016learning; @tessler2019language; @yoon2020polite; @frank2012predicting; @goodman2016pragmatic; @savinelli2017modeling].
 Thus, it can be generalized in a natural way to capture word learning in contexts that offer more, fewer, or different types of information.
-For example, in a recent study with adults and children, we manipulated expectations about informativeness and common ground in a different way.
-Using a structurally similar model [@bohn_tessler_merrick_frank_2019], we also found a close alignment between model predictions and the data.
+For example, non-verbal aspects of the utterance (e.g.
+eye-gaze or gestures) can affect children’s mutual exclusivity inference [@paulus2014conflicting; @graham2010role; @gangopadhyay2020role; @jaswal2006learning; @grassmann2010young].
+As a first step in this direction, we recently studied how adults and children integrate non-verbal utterances with common ground[@bohn_tessler_merrick_frank_2019].
+Using a structurally similar model, we also found a close alignment between model predictions and the data.
 The flexibility of this modeling framework stems from its conceptualization of human communication as a form of rational social action.
@@
 Substantial variation is much more likely.
+Studies on children’s pragmatic inferences in different cultures have documented similar[@su2015interpretation; @zhao2019development] and different[@fortier_kellier_flecha_frank_2018] developmental trajectories.
 Nevertheless, our model provides a way to think about how to reconcile cross-cultural variation with a shared cognitive architecture: We predict differences in how sensitive children are to the individual information sources at different ages, but similarities in how information is integrated [@bohn2019pervasive].
@@
 Second, it would be useful to flesh out the cognitive processes that underlie reasoning about common ground.
-In its current form, our model does not specify how the listener arrives at the expectation that some objects are more likely referents because they are new in common ground.
-We assumed that common ground changes the speaker’s expectations about what are likely referents [@hanna2003effects] and we measured these expectations to inform the parameter values in our model.
-But computationally, the model does not differentiate between common ground information and other reasons that might make an object contextually more salient.
+The basic assumption that common ground changes interlocutors’ expectations about what are likely referents[@hanna2003effects] has been used in earlier modelling work on the role of common ground in reference resolution [@heller2016perspective].
+Here we went one step further and measured the strength of these expectations to inform the parameter values in our model.
+However, in its current form, our model treats common ground as a conversational prior and does not specify how the listener arrives at the expectation that some objects are more likely referents because they are new in common ground.
+That is, computationally, our model does not differentiate between common ground information and other reasons that might make an object contextually more salient.
+An interesting starting point to overcome this shortcoming would be modelling work on the role of common ground in conversational turn taking [@anderson2021tell].
 
@@
 At the same time, the constructs made use of by our model are shaped by factors that unfold across multiple time points and contexts: Common ground is built over the course of a conversation, and the lexical knowledge of a child is shaped across a language developmental time-scale.
-Our model makes use of unidimensional representations of these high-dimensional, structured processes and examines how these representations are integrated.
-Connecting our model with frameworks that focus on the temporal and cross-situational aspects of word learning would elucidate further these complex, time-dependent processes [@frank2009using; @mcmurray2012word; @yurovsky2015integrative].
+Even speaker informativeness could be imagined to vary over time following repeated interactions with a particular speaker.
+What is more, assessing speaker informativeness is unlikely to be the outcome of a single, easy-to-define process.
+The expectations about informative communication that we take it to represent are probably the result of the interplay between multiple social and non-social inference processes.
+Thus, our model makes use of unidimensional representations of these high-dimensional, structured processes and examines how these representations are integrated.
+Connecting our model with other frameworks that focus on the cognitive, temporal and cross-situational aspects of word learning would elucidate further these complex processes [@frank2009using; @mcmurray2012word; @yurovsky2015integrative].
 
@@
 A more detailed description of the experiments and the models can be found in the supplementary material.
-The experimental procedure, sample size, and analysis for each experiment were pre-registered (https://osf.io/7rg9j/registrations).
+The experimental procedure, sample sizes, and analysis for each experiment were pre-registered (https://osf.io/7rg9j/registrations).
 Experimental procedures, model and analysis scripts can be found in an online repository (https://github.com/manuelbohn/spin).
@@
 
+Sample sizes for each experiment were chosen to have at least 30 data points per cell (i.e.
+unique combination of condition, item and age-group).
 Across the three experiments, a total of `r length(unique(me_data$subid)) + length(unique(prior_data$subid)) + length(unique(comb_data$subid))` children participated.
@@
 The location of the unfamiliar object (left or right table) and the animal character were counterbalanced.
-We coded as correct choice if children chose the unfamiliar object as the referent of the novel word.
+We coded a response as a correct choice if children chose the unfamiliar object as the referent of the novel word.
 Each child completed 12 trials, each with a different familiar and a different unfamiliar object.
@@
 Children completed five trials, each with a different pair of unfamiliar objects.
-We coded as correct choice if children chose as the referent of the novel word the object that was new to the speaker.
+We coded a response as a correct choice if children chose as the referent of the novel word the object that was new to the speaker.
 
@@
 The corresponding model code can be found in the associated online repository.
+Information about priors for parameter estimation and Markov chain Monte Carlo settings can also be found in the supplementary information and the online repository.
 
@@
 \endgroup
+
+# Acknowledgements
+
+M.
+Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
+749229.
+M.
+H.
+Tessler was funded by the National Science Foundation SBE Postdoctoral Research Fellowship Grant No.
+1911790.
+M.
+C.
+Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.
+
+# Author Contributions
+
+M.
+Bohn, M.H.
+Tessler and M.C.
+Frank conceptualized the study, M.
+Merrick collected the data, M.
+Bohn and M.H.
+Tessler analyzed the data, M.
+Bohn, M.
+H.
+Tessler and M.C.
+Frank wrote the manuscript, all authors approved the final version of the manuscript.

### 2021-02-26 paper/supplementary_material.Rmd
clean repo for revision

--- 2020-10-23 paper/supplementary_material.Rmd
@@
 As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning.
-In [Experiment 1](#experiment-1-mutual-exclusivity), we show that children make a so-called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge.
+In [Experiment 1](#experiment-1-mutual-exclusivity), we show that children make a mutual exclusivity inference and that this inference depends on children's developing semantic knowledge.
 In [Experiment 2](#experiment-2-common-ground), we show that children make inferences about word meanings based on common ground.
@@
 
-The first experiment tested the so-called mutual exclusivity inference in children between 2 and 5 years of age.
+The first experiment tested the mutual exclusivity inference in children between 2 and 5 years of age.
 The general inference can be described as follows: when presented with a familiar and an unfamiliar object, children expect a novel word to refer to the unfamiliar object [e.g.
@@
 ```{r fig1,echo = F,  fig.cap = "Schematic experimental procedure with screenshots from the experiments.", out.width="100%"}
-knitr::include_graphics("../figures/method_overview.png")
+knitr::include_graphics("figures/method_overview.png")
 ```
@@
   guides(col = F)
-```
-
-```{r}
-#fig2 <- ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
-#ggsave(plot = fig2, "../figures/figureS2.png", width = 12, height = 4)
 ```
@@
 C: Correlation between rated age of acquisiton and mutual exclusivity effect (model based intercept for each familiar object).", out.width="100%"}
-knitr::include_graphics("../figures/figureS2.png")
+knitr::include_graphics("figures/figureS2.png")
 ```
@@
 
-To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150,000 samples from each chain and removing the first 50,000 for burn-in.
+To estimate the parameter distributions and generate model predictions, we collected samples from six independent MCMC chains, collecting 150,000 samples from each chain and removing the first 50,000 for burn-in.
 We excluded samples from one chain because it got stuck on a local maximum which resulted in parameter distributions that were substantially different from the other chains.
-To directly access the model predictions see the file `model_comparison.Rmd` in the online repository.
+Model predictions can be downloaded via the following link: https://keeper.mpdl.mpg.de/d/7ae3805dba064bada8e5/.
+For the model comparison, we collected 150,000 samples (removing 50,000 for burn-in) from ten independent chains (file: `webppl/llh_model.wppl`, see also `stats/model_comparison.Rmd` in the online repository).
 
@@
 ```{r table5}
-model_comp_pred <- readRDS("../saves/pred_model_comparison.rds")%>%
+model_comp_pred <- readRDS("../saves/model_comparison.rds")%>%
+  filter(!grepl("ias",model))%>%
   mutate(model = factor(model),
@@
                             "no common ground vs no speaker informativeness" = "flat_vs_prior"),
-        `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%
+        `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = T))%>%
   select(-logBF, -model)
@@
 
-### Rational integration model
+### Models
+
+#### Rational integration model
 
@@
 
-### Biased model
+#### Biased model
 
@@
 
-### Developmental bias model
+#### Developmental bias model
 
@@
 
-Perhaps unsurprisingly, we see that informing the parameters for semantic knowledge, speaker informativeness and common ground sensitivity by the data from Experiment 3 greatly improves the model fit (comparison: integration (explanation) vs integration (prediction)).
-We also see that the explanation **rational integration model** provides, by far, the best fit to the data compared to the two **biased models**, even though the rational integration model has fewer free parameters than the **biased model**.
-Interestingly, the prediction **rational integration model** also had a better fit, even though its parameters were not constrained by the data from Experiment 3.
+When comparing models via their marginal likelihood, we again see that the **rational integration model** provides, by far, the best fit to the data compared to the two **biased models**, even though the rational integration model has fewer free parameters than the **biased models**.
 When comparing the two **biased models** directly, we see that an age sensitive bias parameter did not result in a substantially better fit, providing additional evidence that the integration process itself is not changing across development.
@@
 ```{r table6}
-model_comp_pred <- readRDS("../saves/expl_model_comparison.rds")%>%
+model_comp_exp <- readRDS("../saves/model_comparison.rds")%>%
+  filter(grepl("ias",model))%>%
   mutate(model = factor(model),
          `Model comparison` = fct_recode(model, 
-                            "integration (explanation) vs integration (prediction)" = "fb_vs_free",
-                            "integration (explanation) vs biased" = "fb_vs_mixture",
-                            "integration (prediction) vs biased" = "free_vs_mixture",
-                            "integration (explanation) vs developmental bias" = "fb_vs_dev_mixture",
-                            "integration (prediction) vs developmental bias" = "free_vs_dev_mixture",
-                            "developmental bias vs biased" = "dev_mixture_vs_mixture"),
+                            "integration vs biased" = "prag_vs_bias",
+                            "integration vs developmental bias" = "prag_vs_devBias",
+                            "developmental bias vs biased" = "devBias_vs_bias"),
         `Bayes factor` = format(round(exp(logBF)), trim = T, justify = "right", scientific = F))%>%
@@
 
-knitr::kable(model_comp_pred, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2, align = "l")
+knitr::kable(model_comp_exp, caption = "Model comparison using Bayes factors computed based on the marginal likelihood of each model given the data.", digits = 2, align = "l")
 ```
@@
 
-```{r figa1, include = T, cache=F,  fig.cap = "Posterior distribution of intercept term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
-
-item_comp_int <- item_comp %>%
-  filter(parameter == "intercept")
-
-ggplot(item_comp_int, aes(x = value, fill = model, col = model))+
-  geom_density(alpha = 0.8, adjust = 2)+
+```{r figa1, include = T, cache=F,  fig.cap = "Posterior distribution of intercept and slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 5}
+
+ggplot(item_comp, aes(x = value, fill = model, col = model))+
+  geom_density(alpha = 0.3, adjust = 2)+
   xlab("value")+
-  facet_wrap( ~ item, nrow = 2, scales = 'free')+
-  theme_few()+
-  xlim(-10,5)+
-  theme(legend.position = "bottom")+
-  scale_fill_colorblind(name = "Model")+
-  scale_color_colorblind(name = "Model")
-```
-
-### Slope
-
-```{r figa2, include = T, cache=F,  fig.cap = "Posterior distribution of slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
-
-item_comp_slope <- item_comp %>%
-  filter(parameter == "slope")
-
-ggplot(item_comp_slope, aes(x = value, fill = model, col = model))+
-  geom_density(alpha = 0.8, adjust = 2)+
-  xlab("value")+
-  facet_wrap( ~ item, nrow = 2, scales = 'free_y')+
-  xlim(-1,4)+
+  facet_grid( parameter~ item, scales = 'free')+
   theme_few()+
@@
 ggplot(global_comp, aes(x = value, fill = model, col = model))+
-  geom_density(alpha = 0.8, adjust = 2)+
+  geom_density(alpha = 0.3, adjust = 2)+
   xlab("value")+

### 2021-02-26 stats/model_comparison.Rmd
clean repo for revision

--- 2020-02-20 stats/model_comparison.Rmd
@@
 library(tidyverse)
-library(readxl)
 library(matrixStats)
-library(data.table)
+library(ggthemes)
 
@@
 ```
-# Data
 
-```{r}
-data_comb_pre <- read_csv("../data/combination.csv")
+# Model comparison
 
-aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)
-
-aoa_ratings <- aoa_ratings_all %>%
-  filter(Word %in% data_comb_pre$item )%>%
-  mutate(mean_aoa = as.numeric(Rating.Mean),
-         item = Word)%>%
-  select(item,mean_aoa)
-
-data_comb <- data_comb_pre%>%
-  left_join(aoa_ratings)%>%
-  ungroup()%>%
-  mutate(item = fct_reorder(factor(item), mean_aoa), 
-         source = "Data")
-
-d_model_comp <- data_comb%>%
-  select(-age)%>%
-  mutate(age = round(age_month,2),
-         item = as.character(item))%>%
-  select(alignment, item, age, correct)
-
-```
-
-# Model comparison prediction
+Model predictions can be downloaded via the following link: https://keeper.mpdl.mpg.de/d/7ae3805dba064bada8e5/
+In the code below, model predictions are assumed to be in the sub-folder called `webppl/output/`.
 
@@
 
-d_model_comp.summarized <- d_model_comp %>% 
-  group_by(alignment, item, age) %>% 
-  summarize(n=n(), k = sum(correct))
+# sample <- bind_rows(
+#   read_csv("../webppl/output/llh_model_chain1.csv")%>%mutate(chain = 1),
+#   read_csv("../webppl/output/llh_model_chain2.csv")%>%mutate(chain = 2),
+#   read_csv("../webppl/output/llh_model_chain3.csv")%>%mutate(chain = 3),
+#   read_csv("../webppl/output/llh_model_chain7.csv")%>%mutate(chain = 4),
+#   read_csv("../webppl/output/llh_model_chain8.csv")%>%mutate(chain = 5),
+#   read_csv("../webppl/output/llh_model_chain9.csv")%>%mutate(chain = 6),
+#   read_csv("../webppl/output/llh_model_chain10.csv")%>%mutate(chain = 7),
+#   read_csv("../webppl/output/llh_model_chain11.csv")%>%mutate(chain = 8),
+#   read_csv("../webppl/output/llh_model_chain12.csv")%>%mutate(chain = 9),
+#   read_csv("../webppl/output/llh_model_chain13.csv")%>%mutate(chain = 10)
+# )
+# 
+# sample_like <-  sample%>%
+#   filter(a == "likelihood")%>%
+#   rename(type = a,
+#          model = b, 
+#          alignment = c,
+#          age = d,
+#          item = e, 
+#          log_like = f)%>%
+#   mutate(age = as.numeric(age))%>%
+#   group_by(chain, model, iteration) %>%
+#   summarize(total_likelihood_sample = sum(log_like))
+# 
+# saveRDS(sample_like, "../saves/likelihood_sample.rds")
 
-# join predictions with the data
+sample_like <- readRDS("../saves/likelihood_sample.rds")
 
-model_comp <- bind_rows(
+# model_by_chain <- sample_like %>%
+#   group_by(chain, model) %>%
+#   summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
+#   spread(model, marginal_likelihood)
+# 
+# saveRDS(model_by_chain, "../saves/model_likelihood_chain.rds")
 
-  readRDS("../saves/model_pred_prag.rds") %>%
-    right_join(d_model_comp.summarized) %>%
-    select(model,chain,iteration, age, alignment,item,pred, n, k),
+model_by_chain <-  readRDS("../saves/model_likelihood_chain.rds")
 
-  readRDS("../saves/model_pred_global.rds") %>%
-    right_join(d_model_comp.summarized)%>%
-    select(model,chain,iteration, age, alignment,item,pred, n, k),
+# model_like <- sample_like %>%
+#   group_by(model) %>%
+#   summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample))
+# 
+# saveRDS(model_like, "../saves/model_likelihood.rds")
 
-   readRDS("../saves/model_pred_flat.rds") %>%
-    right_join(d_model_comp.summarized)%>%
-    select(model,chain,iteration, age, alignment,item,pred, n, k),
+model_like <-  readRDS("../saves/model_likelihood.rds")
 
-  readRDS("../saves/model_pred_prior.rds") %>%
-    right_join(d_model_comp.summarized)%>%
-    select(model,chain,iteration, age, alignment,item,pred, n, k)
-) %>%
-  mutate(
-    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
-  ) %>%
-  group_by(chain, model, iteration) %>%
-  summarize(total_likelihood_sample = sum(log_like)) %>%
-  group_by(chain, model) %>%
-  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
-  spread(model, marginal_likelihood)%>%
-  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
-         prag_vs_flat= pragmatic - flat,
-         prag_vs_prior= pragmatic - prior,
-         global_vs_flat = global - flat,
-         global_vs_prior = global - prior,
-         flat_vs_prior = flat - prior) %>%
-  select(-pragmatic, -global, -flat, - prior) %>%
-  gather(model, logBF, -chain)
+# model_comp <- model_like  %>%
+#   group_by(model) %>%
+#   spread(model, marginal_likelihood)%>%
+#   mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
+#          prag_vs_flat= pragmatic - flat,
+#          prag_vs_prior= pragmatic - prior_only,
+#          prag_vs_bias = pragmatic - bias,
+#          prag_vs_devBias = pragmatic - devBias,
+#          devBias_vs_bias = devBias - bias,
+#          global_vs_flat = global - flat,
+#          global_vs_prior = global - prior_only,
+#          flat_vs_prior = flat - prior_only) %>%
+#   select(-pragmatic, -global, -flat, - prior_only, -bias, -devBias) %>%
+#   gather(model, logBF)
+# 
+# saveRDS(model_comp, "../saves/model_comparison.rds")
 
+model_comp <- readRDS( "../saves/model_comparison.rds")
 ```
 
-# Model comparison explanation
+# visualize log-likelihood distributions
 
 ```{r}
+p_sample_like <- sample_like%>%
+  mutate(model = fct_recode(model,
+                            "integration" = "pragmatic",
+                            "no word knowledge" = "global",
+                            "no common ground" = "flat",
+                            "no speaker informativeness" = "prior_only",
+                            "biased" = "bias",
+                            "developmental bias" = "devBias"),
+         model = factor(model, levels = c("integration","no word knowledge","no common ground", "no speaker informativeness","biased", "developmental bias")))
 
-d_model_comp.summarized <- d_model_comp %>% 
-  group_by(alignment, item, age) %>% 
-  summarize(n=n(), k = sum(correct))
+p_model_like <- model_like %>%
+  mutate(model = fct_recode(model,
+                            "integration" = "pragmatic",
+                            "no word knowledge" = "global",
+                            "no common ground" = "flat",
+                            "no speaker informativeness" = "prior_only",
+                            "biased" = "bias",
+                            "developmental bias" = "devBias"),
+         model = factor(model, levels = c("integration","no word knowledge","no common ground", "no speaker informativeness","biased", "developmental bias")))
 
-model_like <- bind_rows(
-
-  readRDS("../saves/model_pred_prag.rds") %>%
-    right_join(d_model_comp.summarized) %>%
-    select(model,chain,iteration, age, alignment,item,pred, n, k),
-
-  readRDS("../saves/model_pred_prag_fb.rds") %>%
-    mutate(model = "fullBayes")%>%
-    right_join(d_model_comp.summarized)%>%
-    select(model,chain,iteration, age, alignment,item,pred, n, k)
-
-    ,readRDS("../saves/model_pred_mm.rds") %>%
-    mutate(model = "mixture")%>%
-    right_join(d_model_comp.summarized)%>%
-    select(model,chain,iteration, age, alignment,item,pred, n, k)
-
-      ,readRDS("../saves/model_pred_dmm.rds") %>%
-    mutate(model = "dev_mixture")%>%
-    right_join(d_model_comp.summarized)%>%
-    select(model,chain,iteration, age, alignment,item,pred, n, k)
-) %>%
-  mutate(
-    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
-  ) %>%
-  group_by(chain, model, iteration) %>%
-  summarize(total_likelihood_sample = sum(log_like))
-
-# variation across chains
-
-model_by_chain <- model_like %>%
-  na.omit(chain)%>%
-  group_by(model, chain) %>%
-  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
-  spread(model, marginal_likelihood)
-
-saveRDS(model_by_chain, "../saves/expl_model_likelihood_chain.rds")
-
-# compare models
-model_comp <- model_like %>%
-  na.omit(chain)%>%
-  group_by(model) %>%
-  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
-  spread(model, marginal_likelihood)%>%
-  mutate(fb_vs_free = fullBayes - pragmatic,
-          fb_vs_mixture= fullBayes - mixture,
-         fb_vs_dev_mixture= fullBayes - dev_mixture,
-          free_vs_mixture = pragmatic - mixture,
-         free_vs_dev_mixture = pragmatic - dev_mixture,
-         dev_mixture_vs_mixture = dev_mixture - mixture
-         ) %>%
-  select(-pragmatic, -fullBayes, -mixture, -dev_mixture) %>%
-  gather(model, logBF)
-
-saveRDS(model_comp, "../saves/expl_model_comparison.rds")
-
+ggplot(p_sample_like, aes(x = total_likelihood_sample, col = model, fill = model))+
+  geom_density(alpha = .5)+
+  geom_vline(data = p_model_like, aes(xintercept = marginal_likelihood, col = model), lty = 2)+
+  theme_minimal()+
+  labs(x ="log likelihood (sample)", y = "")+
+  scale_fill_colorblind(name = "Model")+
+  scale_color_colorblind(name = "Model")
 ```

### 2021-05-18 paper/figures/bda_fig.tex
final submission

--- 2020-05-17 paper/bda_fig.tex
@@
  $\theta_{ij} = \text{logistic}(\beta^\theta_{0,j}  + i \cdot \beta^\theta_{1,j})$ \\
- $d^{ME}_{ij} \sim L',  d^{CM}_{ij} \sim L$
+ $d^{ME}_{ij} \sim L'_{ij},  d^{CM}_{ij} \sim L_{ijk}$
 };
@@
   \end{center}
-  \caption{Graphical model representing the Bayesian data analysis for \emph{Integration model} used for \emph{Explanation}.
-$L$ represents the RSA model defined by Eq.
-X, used to predict the Combination Data $d^{CM}$  from Expt.~3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$.
-This RSA model takes as input a speaker optimality parameter $\alpha_i$ (which varies by age), a semantic knowledge parameter $\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\rho_i$ (which varies by age).
-Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{ME}$; Expt.~1), via the same RSA model with no common ground $L$;  common ground sensitivity parameters $\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{CG}$; Expt.~2).
-  Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\beta_0$ and $\beta_1$, respectively).
-Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\mu$ and $\sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories.}
-  \label{fig:bayesnet}
-\end{figure}
-%S2 represents the RSA speaker model defined by Eq.
-1, which is used to predict the production responses dprod of each participant i, for each state s (number of hearts), for each utterance w, in each goal condition g.
-The RSA speaker model takes as input the literal meaning variables θ, which additionally are used to predict the literal meaning judgments dlit assuming a Bernoulli linking function.
-Additionally, the RSA model takes the speaker’s goal weights ω and intended presentational goal weight φ, which are inferred separately for each goal condition g.
-Finally, the RSA model uses two global free parameters: the cost of negation c and the speaker’s rationality parameter α.
-
-\begin{figure}[ht]
-\begin{center}
-\begin{tabular}{cc}
-\begin{tikzpicture}
-	%% RSA nodes and data
-	\node[obs](data_comb){$d^{CM}_{i, j, k}$};
-	\node[det, above=of data_comb](L1_comb){$L_1$};
-	\edge{L1_comb}{data_comb};
-
-%	\node[det, right=of data_me](L1_me){$L'_1$};
-
-%	\edge{L1_me}{data_me};
-
-	% COMMON GROUND
-	\node[latent, right=of L1_comb](rho){$\rho_i$};
-	\node[obs, right=of rho](data_cg){$d^{CG}_{i}$};
-	\node[latent, right=of rho, yshift=-2cm](beta_rho_int){$\beta^{\rho}_0$};
-	\node[latent, right=of rho, yshift=-3cm](beta_rho_slope){$\beta^{\rho}_1$};
-
-	\edge{rho}{data_cg};
-	\edge{beta_rho_int}{rho};
-	\edge{beta_rho_slope}{rho};
-	\edge{rho}{L1_comb};
-
-	%% SPEAKER INFORMATIVITY
-
-	\node[latent, left=of L1_comb](alpha){$\alpha_i$};
-	\node[latent, left=of alpha, yshift=-2cm](beta_alpha_int){$\beta^{\alpha}_0$};
-	\node[latent, left=of alpha, yshift=-3cm](beta_alpha_slope){$\beta^{\alpha}_1$};
-	\node[det, left=of alpha](L1_me){$L'_1$};
-	\node[obs, left=of L1_me](data_me){$d^{ME}_{i, j}$};
-
-	\edge{alpha}{L1_me};
-	\edge{beta_alpha_int}{alpha};
-	\edge{beta_alpha_slope}{alpha};
-	\edge{alpha}{L1_comb};
-	\edge{L1_me}{data_me};
-
-	%% SEMANTIC KNOWLEDGE model
-
-	\node[latent, above=of L1_comb](theta){$\theta_{ij}$};
-	\node[latent, above=of theta, xshift=-1.25cm](beta_theta_int){$\beta^{\theta}_{0, j}$};
-	\node[latent, above=of theta, xshift=1.25cm](beta_theta_slope){$\beta^{\theta}_{1, j}$};
-
-	\node[latent, above=of beta_theta_int, xshift=-0.5cm](mu_theta_int){$\mu^{\theta}_{0}$};
-	\node[latent, above=of beta_theta_int, xshift=0.5cm](sigma_theta_int){$\sigma^{\theta}_{0}$};
-
-	\node[latent, above=of beta_theta_slope, xshift=-0.5cm](mu_theta_slope){$\mu^{\theta}_{1}$};
-	\node[latent, above=of beta_theta_slope, xshift=0.5cm](sigma_theta_slope){$\sigma^{\theta}_{1}$};
-
-	\edge{theta}{L1_me};
-	\edge{theta}{L1_comb};
-	\edge{beta_theta_int}{theta};
-	\edge{beta_theta_slope}{theta};
-	\edge{mu_theta_int}{beta_theta_int};
-	\edge{sigma_theta_int}{beta_theta_int};
-	\edge{mu_theta_slope}{beta_theta_slope};
-	\edge{sigma_theta_slope}{beta_theta_slope};
-
-		\plate{plate_items_me}{
-		(data_me)
-	}{$j \in \text{items}$}
-
-	\plate{plate_data_me}{
-		(data_me)
-		(L1_me)
-		(alpha)
-		(plate_items_me)
-	}{$i \in \mathcal{P}_{1}$}
-
-	\plate{plate_data_cg}{
-		(data_cg)(rho)
-	}{$i \in \mathcal{P}_{2}$}
-
-	\plate{plate_items}{
-		(data_comb)(L1_comb)(theta)
-	}{$j \in \text{items}$}
-
-	\plate{plate_data_comb}{
-		(data_comb)(rho)(alpha)(theta)(plate_items)
-	}{$i \in \mathcal{P}_{2}$}
-
-\end{tikzpicture}
-
-    \end{tabular}
-  \end{center}
-  \caption{ Put a caption here.}
-  \label{fig:bayesnet}
-\end{figure}
-
-\begin{figure}[ht]
-\begin{center}
-\begin{tabular}{cc}
-\begin{tikzpicture}
-	%% RSA nodes and data
-	\node[obs](data_comb){$d^{CM}_{i, j, k}$};
-	\node[det, above=of data_comb](L1_comb){$L_1$};
-	\edge{L1_comb}{data_comb};
-
-%	\node[det, right=of data_me](L1_me){$L'_1$};
-
-%	\edge{L1_me}{data_me};
-
-	% COMMON GROUND
-	\node[latent, right=of L1_comb](rho){$\rho_i$};
-	\node[obs, right=of rho](data_cg){$d^{CG}_{i}$};
-	\node[latent, right=of rho, yshift=-2cm](beta_rho_int){$\beta^{\rho}_0$};
-	\node[latent, right=of rho, yshift=-3cm](beta_rho_slope){$\beta^{\rho}_1$};
-
-	\edge{rho}{data_cg};
-	\edge{beta_rho_int}{rho};
-	\edge{beta_rho_slope}{rho};
-	\edge{rho}{L1_comb};
-
-	%% SPEAKER INFORMATIVITY
-
-	\node[latent, left=of L1_comb, yshift=0.5cm](alpha){$\alpha_i$};
-	\node[latent, left=of alpha, yshift=-2cm](beta_alpha_int){$\beta^{\alpha}_0$};
-	\node[latent, left=of alpha, yshift=-3cm](beta_alpha_slope){$\beta^{\alpha}_1$};
-	\node[det, left=of alpha, yshift=1.8cm](L1_me){$L'_1$};
-	\node[obs, left=of L1_me](data_me){$d^{ME}_{i, j}$};
-
-	\edge{alpha}{L1_me};
-	\edge{beta_alpha_int}{alpha};
-	\edge{beta_alpha_slope}{alpha};
-	\edge{alpha}{L1_comb};
-	\edge{L1_me}{data_me};
-
-	%% SEMANTIC KNOWLEDGE model
-
-	\node[latent, above=of L1_comb](theta){$\theta_{ij}$};
-	\node[latent, above=of theta, xshift=-1.25cm](beta_theta_int){$\beta^{\theta}_{0, j}$};
-	\node[latent, above=of theta, xshift=1.25cm](beta_theta_slope){$\beta^{\theta}_{1, j}$};
-
-	\node[latent, above=of beta_theta_int, xshift=-0.5cm](mu_theta_int){$\mu^{\theta}_{0}$};
-	\node[latent, above=of beta_theta_int, xshift=0.5cm](sigma_theta_int){$\sigma^{\theta}_{0}$};
-
-	\node[latent, above=of beta_theta_slope, xshift=-0.5cm](mu_theta_slope){$\mu^{\theta}_{1}$};
-	\node[latent, above=of beta_theta_slope, xshift=0.5cm](sigma_theta_slope){$\sigma^{\theta}_{1}$};
-
-	\edge{theta}{L1_me};
-	\edge{theta}{L1_comb};
-	\edge{beta_theta_int}{theta};
-	\edge{beta_theta_slope}{theta};
-	\edge{mu_theta_int}{beta_theta_int};
-	\edge{sigma_theta_int}{beta_theta_int};
-	\edge{mu_theta_slope}{beta_theta_slope};
-	\edge{sigma_theta_slope}{beta_theta_slope};
-
-	{
-	\tikzset{plate caption/.append style={below right=2pt and 0pt of #1.south west}}
-		\plate{plate_items_me}{
-			(data_me)(L1_me)(theta)(beta_theta_int)(beta_theta_slope)
-		}{$j \in \text{items}$}	
-	}
-
-	{
-	\tikzset{plate caption/.append style={below right=0pt and 0pt of #1.south west}}
-	\plate{plate_data_me}{
-		(data_me)
-		(L1_me)
-		(alpha)
-%		(plate_items_me)
-	}{$i \in \mathcal{P}_{1}$}
-	}
-
-	\plate{plate_data_cg}{
-		(data_cg)(rho)
-	}{$i \in \mathcal{P}_{2}$}
-
-	\plate{plate_items}{
-		(data_comb)(L1_comb)(theta)
-	}{$j \in \text{items}$}
-
-	\plate{plate_data_comb}{
-		(data_comb)(rho)(alpha)(theta)(plate_items)
-	}{$i \in \mathcal{P}_{3}$}
-
-\end{tikzpicture}
-
-    \end{tabular}
-  \end{center}
-  \caption{ Put a caption here.}
-  \label{fig:bayesnet}
 \end{figure}

### 2021-05-18 paper/manuscript.Rmd
final submission

@@
   - name          : "Megan Merrick"
-    affiliation   : "1"
+    affiliation   : "2"
   - name          : "Michael C. Frank"
-    affiliation   : "1"
+    affiliation   : "2"
 
@@
   - id            : "1"
+    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
+  - id            : "2"
     institution   : "Department of Psychology, Stanford University"
-  - id            : "2"
-    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
   - id            : "3"
@@
   Before formal education begins, children typically acquire a vocabulary of thousands of words.
-This learning process requires the use of many different information sources in their social environment, including the context in which they hear words used and their current state of knowledge.
+This learning process requires the use of many different information sources in their social environment, including including their current state of knowledge and the context in which they hear words used.
 How is this information integrated?
@@
 Model comparison suggests that the central locus of development is an increased sensitivity to individual information sources, rather than changes in  integration ability.
-This work presents a quantitative developmental theory of information integration during language learning, and illustrates how formal models can be used to make a quantitative test of the predictive and explanatory power of competing theories.
+This work presents a developmental theory of information integration during language learning and illustrates how formal models can be used to make a quantitative test of the predictive and explanatory power of competing theories.
 
@@
 classoption       : "man"
-output            : papaja::apa6_docx
+output            : papaja::apa6_pdf
 
@@
 A central problem in language learning is referent identification: To acquire the conventional symbolic relation between a word and an object, a child must determine the intended referent of the word.
-However, there is no unique cue to reference that can be used across all situations [@frank2013social].
+There is no unique cue to reference, however, that can be used across all situations [@frank2013social].
 Instead, referents can only be identified inferentially by reasoning about the speaker’s intentions [@bohn2019pervasive; @bruner1983child; @clark2009first; @tomasello2009constructing].
@@
 These different mechanisms, however, have been mainly described and theorized about in isolation.
-The picture of the learning process that emerges is that of a "bag of tricks": mechanisms that operate (and develop) independently from one another [@bloom2002children].
+The implied picture of the learning process is that of a "bag of tricks": mechanisms that operate (and develop) independently from one another [@bloom2002children].
 As such, this view of the learning process does not address the complexity of natural social interaction during which many sources of information are present [@bergelson2017nature; @frank2013social].
@@
 The speaker, sitting on the opposite side of the display, saw only three of the four compartments: the ball, the pen, and one of the glasses.
-When the speaker asked for "the glass", children had to integrate the semantics of the utterance with the speaker’s perspective to correctly infer which of the glasses the speaker was referring to.
+When the speaker asked for "the glass", children had to integrate the semantics of the utterance with the speaker’s visual perspective to correctly infer which of the glasses the speaker was referring to.
 This study advanced our understanding by documenting that preschoolers use both information sources, a finding confirmed by a variety of other work [@graham2017words; @khu2020preschoolers; @nilsen2009preschoolers].
-Yet these studies do not specify -- or test -- the process by which children integrate different information sources.
-When interpreting their findings, work in this tradition refers to social-pragmatic theories of language use and learning [@grice1991studies; @sperber2001relevance; @clark1996using; @clark2009first; @tomasello2009constructing], all of which assume that information is integrated as part of a social inference process, but none of which clearly defines the process.
+Yet these studies neither specify nor test the process by which children integrate different information sources.
+When interpreting such findings, work in this tradition refers to social-pragmatic theories of language use and learning [@grice1991studies; @sperber2001relevance; @clark1996using; @clark2009first; @tomasello2009constructing], all of which assume that information is integrated as part of a social inference process, but none of which clearly defines the process.
 As a consequence, we have no explicit and quantitative theory of how different information sources (and word learning mechanisms) are integrated.
@@
 Next, we quantify how well the model explains the integration process by comparing it to alternative models that make different assumptions about *whether* information is integrated, *how* it is integrated, and how the integration process *develops*.
-Alternative models either assume that children ignore some information sources or -- in line with a “bag of tricks” approach -- they assume that children compute isolated inferences and then weigh their outcome in a post-hoc manner.
+Alternative models either assume that children ignore some information sources or -- in line with a “bag of tricks” approach -- assume that children compute isolated inferences and then weigh their outcome in a post-hoc manner.
 
@@
 A listener ($L_{1}$) reasons about the referent of a speaker’s ($S_{1}$) utterance.
-This reasoning is contextualized by the prior probability of each referent $\rho$.
+This reasoning is contextualized by the prior probability $\rho$ of each referent.
 We treat $\rho$ as a conversational prior which originates from the common ground shared between the listener and the speaker.
 This interpretation follows from the social nature of our experiments (see below).
-From a modelling perspective, $\rho$ can be (and also also has been) used to capture non-social aspects of a referent, for example its visual salience[@frank2012predicting].
+From a modelling perspective, $\rho$ can be (and in fact has been) used to capture non-social aspects of a referent, for example its visual salience[@frank2012predicting].
 To decide between referents, the listener ($L_{1}$) reasons about what a rational speaker ($S_{1}$) with informativeness $\alpha$ would say given an intended referent.
@@
 The informativity of each utterance is given by imagining which referent a listener, who interprets words according to their literal semantics (what we call a literal listener, $L_{0}$), would infer upon hearing the utterance.
-Naturally, this reasoning depends on what kind of semantic knowledge (for object j) $\theta$~j~ the speaker ascribes to the (literal) listener.
+Naturally, this reasoning depends on what kind of semantic knowledge $\theta$~j~ (for object j) the speaker ascribes to the (literal) listener.
 
@@
 The three information sources operate on different timescales: speaker informativeness is a momentary expectation about a particular utterance, common ground grows over the course of a conversation, and semantic knowledge is learned across development.
-This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word], and we link these different time-dependent processes together via their hypothesized impact on model components.
+This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word], and we link these different time-dependent processes together via their proposed impact on model components.
 Furthermore, the model presents an explicit and substantive theory of development.
@@
 Sections (i) to (iii) establish common ground between the speaker and the listener, in that one object is new in context (red).
-The request in (iv) licenses an inference based on expectations about how informative speakers are (gold).
-Listeners’ semantic knowledge enters the task because the identity of the known object on one of the tables is varied from well-known objects like a duck to relatively unfamiliar objects like a chess pawn (total of 12 objects -- blue).
+The request in (iv) licenses an inference based on expectations about how informative speakers are (blue).
+Listeners’ semantic knowledge enters the task because the identity of the known object on one of the tables is varied from well-known objects like a duck to relatively unfamiliar objects like a chess pawn (total of 12 objects -- yellow).
 (a) shows the condition of the experiment in which common ground information is congruent (i.e., point to the same object) with speaker informativeness and (b) shows the incongruent condition.
@@
 
-To test the predictive and explanatory power of our model we designed a word-learning experiment in which we jointly manipulated the three information sources (Fig.
+To test the predictive and explanatory power of our model, we designed a word-learning experiment in which we jointly manipulated the three information sources (Fig.
 1).
@@
 The speakers used a novel word (e.g., "wug") in the context of two potential referents, and then the child was asked to identify a new instance of the novel word, testing their inference about the speaker’s intended referent.
-To vary the strength of the child’s inference, we systematically manipulated the familiarity of the known object (from e.g., the highly familiar "duck" to the relatively unfamiliar "pawn") and whether the familiar or novel object was new to the speaker (meaning that it was not part of common ground).
+To vary the strength of the child’s inference, we systematically manipulated the familiarity of the known object (from e.g., the highly familiar "duck" to the relatively unfamiliar "pawn") and whether the familiar or novel object was new to the speaker (i.e., whether it was not part of common ground).
 
@@
 First, the child may infer that a cooperative and informative speaker [@clark1987principle; @frank2014inferring] would have used the word "duck" to refer to the known object (the duck); the fact that the speaker did not say "duck" then suggests that the speaker is most likely referring to a different object (the unfamiliar object).
-This basic inference is oftentimes referred to as a mutual exclusivity inference [@markman1988children; @halberda2003development].
+This inference is often referred to as a "mutual exclusivity" inference [@markman1988children; @halberda2003development].
 Second, the child may draw upon what has already been established in the common ground with the speaker.
@@
 
-We tested the model in its ability to predict 2 - 5 year-old children’s judgments about word meaning.
-We estimated children’s (N=148) developing sensitivity to individual information sources in two separate experiments (Experiments 1 and 2; see Fig.
+We tested the model in its ability to predict 2--to--5 year-old children’s judgments about word meaning.
+We estimated children’s (N=148) developing sensitivities to individual information sources in two separate experiments (Experiments 1 and 2; see Fig.
 1c-e).
-In Experiment 1, we jointly estimated children’s sensitivity to informativeness and their semantic knowledge.
+In Experiment 1, we estimated children’s sensitivity to informativeness jointly with their semantic knowledge.
 In Experiment 2, we estimated sensitivity to common ground.
 We then generated parameter-free *a priori* model predictions (developmental trajectories) representing the model’s expectations about how children should behave in a new situation in which all three information sources had to be integrated.
-We generated predictions for 24 experimental conditions: 12 objects of different familiarities (requiring different levels of semantic knowledge), with novelty either conflicting or coinciding; Fig.
-1.
+We generated predictions for 24 experimental conditions: 12 objects of different familiarities (requiring different levels of semantic knowledge), with novelty either conflicting or coinciding (Fig.
+1).
 We compared these predictions to newly collected data from N = 220 children from the same age range (Experiment 3).
-All procedures, sample sizes and analysis were pre-registered (see methods).
+All procedures, sample sizes, and analyses were pre-registered (see methods).
 
@@
 S6).
-For a more quantitative analysis, we binned predictions and data by child age (in years) and correlated the two.
-We found a high correlation, with the model explaining 79% of the variance in the data (Fig.
+With predictions and data binned by child age (in years), the model explained 79% of the variance in the data (Fig.
 2a).
-These results support the assumption of the model that children integrate three all available information sources.
-However, it is still possible that simpler models might make equally good – or even better – predictions.
-For example, work on children’s use of statistical information during word learning showed that their behaviour was best explained by a model which selectively ignored parts of the input [@gagliardi2017modeling].
+These results support the assumption of the model that children integrate all three available information sources.
+
+It is still possible, however, that simpler models might make equally good – or even better – predictions.
+For example, work on children’s use of statistical information during morphology learning showed that children's behaviour was best explained by a model which selectively ignored parts of the input [@gagliardi2017modeling].
 
@@
 
-The no *word knowledge model* uses the same model architecture as the rational integration model.
+The resulting *no word knowledge model* uses the same model architecture as the rational integration model.
 It uses expectations about speaker informativeness and common ground but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge).
-That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age-specific average semantic knowledge.
+That is, the model assumes a listener whose inferences do not vary depending on the particular familiar object but only on the age-specific average semantic knowledge (i.e., a marker of gross vocabulary size).
 The *no common ground model* takes in object-specific semantic knowledge and speaker informativeness but ignores common ground information.
@@
 2b).
-When using Bayesian model comparison via marginal likelihood of the data [@lee2014bayesian], we find that the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Fig.
+When using Bayesian model comparison via marginal likelihood of the data [@lee2014bayesian], the data were several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Fig.
 2).
-Figure 2c exemplifies the differences between the models: all heuristic models systematically underestimate children’s performance in the congruent condition.
-Thus, even when the information sources are redundant (i.e.
-they all point to the same referent), children’s inferences are notably strengthened by each of them.
-In the incongruent condition, the no word knowledge model underestimates performance, because it does not differentiate between the different familiar objects, and in the case of a highly familiar word such as duck, underestimates the strength of the mutual exclusivity inference and its compensatory effect.
-The no speaker informativeness completely ignores this inferences, which leads to even worse predictions.
-On the contrary, the no common ground model overestimates performance because it ignores the dampening effect of common ground favoring a different referent.
+Figure 2c exemplifies the differences between the models: all heuristic models systematically underestimated children’s performance in the congruent condition.
+Thus, even when the information sources are redundant (i.e., they all point to the same referent), children’s inferences are notably strengthened by each of them.
+In the incongruent condition, the no word knowledge model underestimates performance, because it does not differentiate between the different familiar objects, and in the case of a highly familiar word such as "duck", underestimated the strength of the mutual exclusivity inference and its compensatory effect.
+The no speaker informativeness model completely ignores this inferences, which leads to even worse predictions.
+In contrast to the lesioned models that underestimated performance, the no common ground model overestimated performance  in the incongruent condition because it ignored the dampening effect of common ground favoring a different referent.
 Taken together, we conclude that children considered all available information sources.
@@
 
-In the previous section, we established that children integrated all available information sources.
+In the previous section, we established that children integrated all available information sources to infer the meanings of new words.
 This result, however, does not speak to the process by which information is assumed to be integrated.
@@
 The rational integration model assumes that all information sources enter into a joint inference process, but alternative integration processes are conceivable and might be consistent with the data.
-For example, the "bag of tricks" [@bloom2002children] hypothesis mentioned in the introduction could be re-phrased as a modular integration process: children might compute independent inferences based on subsets of the available information and then integrate them in a post-hoc manner by weighting them according to some parameter.
+For example, the "bag of tricks" [@bloom2002children] hypothesis mentioned in the introduction could be restated as a modular integration process: children might compute independent inferences based on subsets of the available information and then integrate them in a post-hoc manner by weighting them according to some parameter.
 This view would allow for the possibility that some information sources are considered to be more important than others.
@@
 We formalized this alternative view as a *biased integration model*.
-This model assumes that semantic knowledge and expectations about speaker informativeness enter into one inference (mutual exclusivity inference [@markman1988children; @lewis2020-me; @clark1987principle]) while common ground information enters into a second one.
-The outcomes of both processes are then weighted according to the parameter $\phi$.
+This model assumes that semantic knowledge and expectations about speaker informativeness enter into one inference (mutual exclusivity inference [@markman1988children; @lewis2020-me; @clark1987principle]) while common ground information enters into a second inference.
+The outcomes of both processes are then weighted according to a bias parameter $\phi$.
 Like the rational integration model, this model takes in all available information sources in an age-sensitive way and assumes that they are integrated.
@@
 The parameter $\phi$ in the biased integration model is unknown ahead of time and has to be estimated based on the experimental data.
-That is, through Experiment 1 and 2 alone, we do not learn anything about the relative importance of the information sources.
-As a consequence -- and in contrast to the rational integration model -- the biased integration model does not allow us to make *a priori* predictions about new data in the way we describe above.
+That is, through Experiments 1 and 2 alone, we do not learn anything about the relative importance of the information sources.
+As a consequence -- and in contrast to the rational integration model -- the biased integration model does not allow us to make *a priori* predictions about the new data (Experiment 3) in the way we described above.
 For a fair comparison, we therefore constrained the parameters in the rational integration model by the data from Experiment 3 as well.
@@
 
-The biased integration model makes reasonable predictions and explains 78% of the variance in the data (Fig.
+The biased integration model makes reasonable posterior predictions and explains 78% of the variance in the data (Fig.
 3b).
@@
 The rational integration model assumes that the integration process itself does not change with age [@bohn2019pervasive].
-That is, while children’s sensitivity to each information source develops, the way they relate to one another remains the same.
-The biased integration model provides an alternative proposal about developmental change, one in which the integration process itself changes with age.
+That is, while children’s sensitivity to each information source develops, the way the information sources relate to one another remains the same.
+The biased integration model can provide the basis for an alternative proposal about developmental change, one in which the integration process itself changes with age.
 That is, children may be biased towards some information sources, and that bias itself may change with age.
@@
 Looking at Figure 3e, we can see that the developmental bias model tends to underestimate children’s performance because the supportive interplay between the different inferences is constrained.
-In the biased models, the overall inference can only be as strong as the strongest of the components -- in the rational integration model, the components interact with one another, enabling a stronger overall inference.
+In the biased models, the overall inference can only be as strong as the strongest of the components -- in the rational integration model, the components interact with one another, allowing for a stronger inference than the individual parts would suggest.
 
@@
 As a consequence, instead of assuming that different information sources feed into separate word-learning mechanisms (the “bag of tricks” view), we assume that all of these information sources play a functional role in an integrated social inference process.
-Our model goes beyond previous theoretical and empirical work by specifying the computations that underlie this inference process.
-Furthermore, we present a substantive theory about how this integration process develops: We assume that children become increasingly sensitive to different information sources, but that the way these information sources are integrated remains the same.
+Our model goes beyond previous theoretical and empirical work by describing the computations that underlie this inference process.
+Furthermore, we presented a substantive theory about how this integration process develops: We assume that children become increasingly sensitive to different information sources, but that the way these information sources are integrated remains the same.
 We used this model to predict and explain children’s information integration in a new word learning paradigm in which they had to integrate (1) their assumptions about informative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge.
 
-We found that this rational integration model made accurate quantitative predictions across a range of experimental conditions both when information sources were aligned and were in conflict.
+The rational integration model made accurate quantitative predictions across a range of experimental conditions both when information sources were aligned and when they were in conflict.
 Predictions from the model better explained the data compared to lesioned models which assumed that children ignore one of the information sources, suggesting that children used all available information.
-To test the explanatory power of the model -- how well it explains the process by which information is integrated -- we formalized an alternative, modular, view.
+We also formalized an alternative, modular, view.
 According to the biased integration model, children use all available information sources but compute separate inferences based on a subset of them.
@@
 Finally, we tested an alternative view on the development of the integration process.
-According to the developmental bias model, the importance of the different information sources changed with age.
+According to the developmental bias model, the importance of the different information sources changes with age.
 In both cases, the rational integration model provided a much better fit to the data, suggesting that the integration process remains stable over time.
@@
 For example, non-verbal aspects of the utterance (e.g.
-eye-gaze or gestures) can affect children’s mutual exclusivity inference [@paulus2014conflicting; @graham2010role; @gangopadhyay2020role; @jaswal2006learning; @grassmann2010young].
+eye-gaze or gestures) can affect children’s mutual exclusivity inferences [@paulus2014conflicting; @graham2010role; @gangopadhyay2020role; @jaswal2006learning; @grassmann2010young].
 As a first step in this direction, we recently studied how adults and children integrate non-verbal utterances with common ground[@bohn_tessler_merrick_frank_2019].
-Using a structurally similar model, we also found a close alignment between model predictions and the data.
+Using a structurally similar rational integration model, we also found a close alignment between model predictions and the data.
 The flexibility of this modeling framework stems from its conceptualization of human communication as a form of rational social action.
@@
 Our model and empirical paradigm provide a foundation on which to test deeper questions about language development.
-First, our findings should be replicated in children from different cultural backgrounds, learning different languages [@nielsen2017persistent].
+First, our experiments should be performed in children from different cultural backgrounds, learning different languages [@nielsen2017persistent].
 In such studies, we would not expect our results to replicate in a strict sense; that is, we would not expect to see the same developmental trajectories in all cultures and languages.
 Substantial variation is much more likely.
-Studies on children’s pragmatic inferences in different cultures have documented similar[@su2015interpretation; @zhao2019development] and different[@fortier_kellier_flecha_frank_2018] developmental trajectories.
+Studies on children’s pragmatic inferences in different cultures have documented both similar[@su2015interpretation; @zhao2019development] and different[@fortier_kellier_flecha_frank_2018] developmental trajectories.
 Nevertheless, our model provides a way to think about how to reconcile cross-cultural variation with a shared cognitive architecture: We predict differences in how sensitive children are to the individual information sources at different ages, but similarities in how information is integrated [@bohn2019pervasive].
@@
 The expectations about informative communication that we take it to represent are probably the result of the interplay between multiple social and non-social inference processes.
-Thus, our model makes use of unidimensional representations of these high-dimensional, structured processes and examines how these representations are integrated.
+The broader point here is that, our model makes use of unidimensional representations of high-dimensional, structured processes and examines how these representations are integrated.
+As such, it is first and foremost a computational description of the inferences and we therefore make no strong claims about the psychological reality of the parameters in it.
 Connecting our model with other frameworks that focus on the cognitive, temporal and cross-situational aspects of word learning would elucidate further these complex processes [@frank2009using; @mcmurray2012word; @yurovsky2015integrative].
 
-Taken together, we hope this work advances our understanding of how children navigate the complexity of their learning environment.
+This work advances our understanding of how children navigate the complexity of their learning environment.
 Methodologically, it illustrates how computational models can be used to test theories; from a theoretical perspective, it adds to broader frameworks that see the onto- and phylogenetic emergence of language as deeply rooted in social cognition.
@@
 A more detailed description of the experiments and the models can be found in the supplementary material.
-The experimental procedure, sample sizes, and analysis for each experiment were pre-registered (https://osf.io/7rg9j/registrations).
-Experimental procedures, model and analysis scripts can be found in an online repository (https://github.com/manuelbohn/spin).
+The experimental procedure, sample sizes, and analysis for each experiment were pre-registered (https://osf.io/7rg9j/registrations; dates of registration: 05/02/2019, 04/05/2019, 03/02/2019).
+Experimental procedures, data, model and analysis scripts can be found in an online repository (https://github.com/manuelbohn/spin).
 Experiments 1 and 2 were designed to estimate children’s developing sensitivity to each information source.
@@
 The positioning of the unfamiliar object at the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced.
-Children completed five trials, each with a different pair of unfamiliar objects.
+Children completed ten trials, each with a different pair of unfamiliar objects.
 We coded a response as a correct choice if children chose as the referent of the novel word the object that was new to the speaker.
@@
 
-The rational integration model is a mapping from an utterance u to a referent r, defined as $P^{int}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i)$ where $i$ represents the age of the participant and the $j$ the familiar object.
+The rational integration model is a mapping from an utterance u to a referent r, defined as 
+\begin{equation}
+P^{int}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i)
+\end{equation}
+where $i$ represents the age of the participant and the $j$ the familiar object.
 The three lesioned models that were used to compare how well the model predicts new data are reduced versions of this model.
-The no word knowledge model uses the same model architecture: $P^{no\_wk}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{i}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{i}\}) \cdot P(r \mid \rho_i)$ and the only difference lies in the parameter $\theta$, which does not vary as a function of $j$, the object (i.e., $\theta$ in this model is analogous to a measure of gross vocabulary development).
+The no word knowledge model uses the same model architecture:
+\begin{equation}
+P^{no\_wk}_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{i}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{i}\}) \cdot P(r \mid \rho_i)
+\end{equation}
+and the only difference lies in the parameter $\theta$, which does not vary as a function of $j$, the object (i.e., $\theta$ in this model is analogous to a measure of gross vocabulary development).
 The object-specific parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model.
@@
 Thus, the no word knowledge model takes in the overall trajectory for semantic knowledge ($\theta_{i}$) but ignores object-specific variation.
-The no common ground model ignores common ground information (represented by $\rho$) and is thus defined as $P^{no\_cg}_{L_1}(r \mid u; \{\alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\})$.
-For the no speaker informativeness model, the parameter $\alpha = 0$.
-As a consequence, the likelihood term in the model is 1 and the model therefore reduces to $P^{no\_si}_{L_1}(r \mid u; \{\rho_i\})\propto P(r \mid \rho_i)$.
+The no common ground model ignores common ground information (represented by $\rho$) and is thus defined as
+\begin{equation}
+P^{no\_cg}_{L_1}(r \mid u; \{\alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\})
+\end{equation}
+For the no speaker informativeness model, the parameter $\alpha = 0$. As a consequence, the likelihood term in the model is 1 and the model therefore reduces to 
+\begin{equation}
+P^{no\_si}_{L_1}(r \mid u; \{\rho_i\})\propto P(r \mid \rho_i)
+\end{equation}
 
 As noted above, the explanation models used parameters that were additionally constrained by the data from Experiment 3, but the way these parameters were combined in the rational integration model was the same as above.
-The biased integration model is defined as $P^{biased}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)$ with $P_{ME}$ representing a mutual exclusivity inference which takes in speaker informativeness and object specific semantic knowledge.
+The biased integration model is defined as
+\begin{equation}
+P^{biased}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)
+\end{equation}
+ with $P_{ME}$ representing a mutual exclusivity inference which takes in speaker informativeness and object specific semantic knowledge.
 This inference is then weighted by the parameter $\phi$ and added to the respective prior probability, which is weighted by $1-\phi_i$.
 Thus, $\phi$ represents the bias in favor of the mutual exclusivity inference.
-In the developmental bias model the parameter $\phi$ is made to change with age ($\phi_i$) and the model is thus defined as $P^{dev\_bias}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i)$.
+In the developmental bias model the parameter $\phi$ is made to change with age ($\phi_i$) and the model is thus defined as
+\begin{equation}
+P^{dev\_bias}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i)
+\end{equation}
 
@@
 C.
-Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.
+Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
 
@@
 Bohn, M.H.
-Tessler and M.C.
+Tessler, and M.C.
 Frank conceptualized the study, M.
@@
 Bohn and M.H.
-Tessler analyzed the data, M.
+Tessler implemented the models and analyzed the data, M.
 Bohn, M.
 H.
-Tessler and M.C.
+Tessler, and M.C.
 Frank wrote the manuscript, all authors approved the final version of the manuscript.

### 2021-05-18 paper/supplementary_material.Rmd
fix trial number in supplement
final submission

@@
 
-```{r table1, echo=F}
-chance_me <- me_data %>%
-  group_by(subage, subid) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(subage)%>%
-  mutate(Mean= round(mean(unlist(correct)),2),
-         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf), scientific = F),
-         `Age group` = subage)%>%
-  ungroup()%>%
-  select(`Age group`, Mean, BayesFactor)
-
-knitr::kable(chance_me, caption = "Proportion of children choosing the novel object compared to a level expected by chance based on a one sample Bayesian t-test.
-Responses are aggregated for each participant across familiar objects.", digits = 2, align = "l")
-```
-
 As a first step, we evaluated whether children made a mutual exclusivity inference.
@@
   guides(col = F)
+```
+
+```{r table1, echo=F}
+chance_me <- me_data %>%
+  group_by(subage, subid) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(subage)%>%
+  mutate(Mean= round(mean(unlist(correct)),2),
+         BayesFactor = format(round(extractBF(ttestBF(unlist(correct), mu = 0.5))$bf), scientific = F),
+         `Age group` = subage)%>%
+  ungroup()%>%
+  select(`Age group`, Mean, BayesFactor)
+
+knitr::kable(chance_me, caption = "Proportion of children choosing the novel object compared to a level expected by chance based on a one sample Bayesian t-test.
+Responses are aggregated for each participant across familiar objects.", digits = 2, align = "l")
 ```
@@
 The positioning of the novel object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced.
-Children received five trials, each with a different pair of novel objects.
+Children received ten trials, each with a different pair of novel objects.
 We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.
@@
 ### Results
+
+Table \@ref(tab:table3) compares children's correct responses to a level expected by chance (50%).
+We found evidence that, as a group, 3- and 4-year-olds, but not 2-year-olds, inferred that the novel word referred to the object that was new to the speaker.
 
@@
 ```
-
-Table \@ref(tab:table3) compares children's correct responses to a level expected by chance (50%).
-We found evidence that, as a group, 3- and 4-year-olds, but not 2-year-olds, inferred that the novel word referred to the object that was new to the speaker.
 
@@
 Lighter lines show 200 random draws from the posterior distribution to depict uncertainty.
-Dotted line indicates a level of performance expected by chance.", fig.width=12, fig.height = 4}
-ggarrange(plot_cg, plot_comb,  labels = c("A","B"), nrow = 1, widths = c(1,2))
+Dotted line indicates a level of performance expected by chance.", out.width="100%"}
+
+#ggsave(plot = ggarrange(plot_cg, plot_comb,  labels = c("A","B"), nrow = 1, widths = c(1,2)), filename = "figures/figureS3.png", width = 12, height = 4)
+
+knitr::include_graphics("figures/figureS3.png")
 ```
@@
 
-```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **rational integration model** used for *Explanation*.
+## Implementation details
+
+All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
+The corresponding model code can be found in the associated online repository (file `webppl/prediction_all_models.wppl`).
+To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned (Figure \@ref(fig:bda)).
+The resulting predictions come in the form of distributions of developmental trajectories for each familiar object in the congruent and the incongruent condition.
+
+We used the following prior distributions for model parameters.
+Intercept and slope for sensitivity to common ground: $\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$.
+Speaker informativeness:  $\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ for the intercept and $\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ for the slope.
+We restricted the slope to be positive because negative values for speaker informativeness are conceptually implausible: We do not expect sensitivity to speaker informativeness to decrease across our age range.
+For the global semantic knowledge (vocabulary) parameters, we used $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ for the intercept and $\mu^\theta_1 \sim \text{Uniform}(0,2)$ for the slope, because it is implausible to assume that semantic knowledge decreases with age.
+For the parameters capturing the variability the object specific trajectories around these overall parameters we used $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ for the intercept and $\sigma^\theta_1 \sim \text{Uniform}(0,1)$ for the slope.
+Some choices regarding these prior distributions were made to ease model convergence.
+However, please note that all models considered used the same prior distributions.
+
+(ref:bdalab) Graphical model representing the Bayesian data analysis for **rational integration model** used for *Explanation*.
 $RSA$ represents the general model architecture and paremeters defined by Eq.
-\\@ref(eq:rsabasic1) - \\@ref(eq:rsabasic3).
+\@ref(eq:rsabasic1) - \@ref(eq:rsabasic3).
 $L_1$ represents the RSA model defined by Eq.
-\\@ref(eq:rsafull1), used to predict the combination data $d^{Ex3}$ from Expt.
+\@ref(eq:rsafull1), used to predict the combination data $d^{Ex3}$ from Expt.
 3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$.
-This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\\rho_i$ (which varies by age).
+This RSA model takes as input a speaker optimality parameter $\alpha_i$ (which varies by age), a semantic knowledge parameter $\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\rho_i$ (which varies by age).
 Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{Ex1}$; Expt.
-1), via the same RSA model with no common ground $L$; common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt.
+1), via the same RSA model with no common ground $L$; common ground sensitivity parameters $\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt.
 2).
-Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\\beta_0$ and $\\beta_1$, respectively).
-Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu$ and $\\sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}
+Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\beta_0$ and $\beta_1$, respectively).
+Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\mu$ and $\sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories.
+
+```{r bda, engine='tikz', echo = F , fig.cap = "(ref:bdalab)", out.width = "100%"}
 
 \usetikzlibrary{bayesnet}
-
-\resizebox{1\textwidth}{!}{
 
@@
 
-}
-
-```
-
-## Implementation details
-
-All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl].
-The corresponding model code can be found in the associated online repository (file `webppl/prediction_all_models.wppl`).
-To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned (Figure \@ref(fig:bda)).
-The resulting predictions come in the form of distributions of developmental trajectories for each familiar object in the congruent and the incongruent condition.
-
-We used the following prior distributions for model parameters.
-Intercept and slope for sensitivity to common ground: $\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$.
-Speaker informativeness:  $\beta^\alpha_0 \sim \text{Uniform}(-3,3)$ for the intercept and $\beta^\alpha_1 \sim \text{Uniform}(-0,4)$ for the slope.
-We restricted the slope to be positive because negative values for speaker informativeness are conceptually implausible: We do not expect sensitivity to speaker informativeness to decrease across our age range.
-For the global semantic knowledge (vocabulary) parameters, we used $\mu^\theta_0 \sim \text{Uniform}(-3,3)$ for the intercept and $\mu^\theta_1 \sim \text{Uniform}(0,2)$ for the slope, because it is implausible to assume that semantic knowledge decreases with age.
-For the parameters capturing the variability the object specific trajectories around these overall parameters we used $\sigma^\theta_0 \sim \text{Uniform}(0,2)$ for the intercept and $\sigma^\theta_1 \sim \text{Uniform}(0,1)$ for the slope.
-Some choices regarding these prior distributions were made to ease model convergence.
-However, please note that all models considered used the same prior distributions.
+```
 
@@
 Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty.
-(A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
-ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1))
+(A) does not include these random draws for the sake of clarity.", out.width="100%"}
+
+#ggsave(plot = ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1)), filename = "figures/figureS4.png", width = 12, height = 4)
+
+knitr::include_graphics("figures/figureS4.png")
 ```
@@
 ```{r fig10, include = T, fig.cap = "Bias parameter for the biased model (A) and the developmental bias model (B).
-(A) shows the posterior distribution of the bias parameter and (B) shows developmental trajectories for the bias parameter based on 300 random draws from the posterior distribution for intercept and slope.", fig.width=10, fig.height = 4, }
-ggarrange(plot_mixture, plot_dev_mixture,  labels = c("A","B"), nrow = 1)
+(A) shows the posterior distribution of the bias parameter and (B) shows developmental trajectories for the bias parameter based on 300 random draws from the posterior distribution for intercept and slope.", out.width="100%"}
+
+#ggsave(plot = ggarrange(plot_mixture, plot_dev_mixture,  labels = c("A","B"), nrow = 1), filename = "figures/figureS10.png", width = 10, height = 4)
+
+knitr::include_graphics("figures/figureS10.png")
 ```
@@
 
-```{r figa1, include = T, cache=F,  fig.cap = "Posterior distribution of intercept and slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 5}
+```{r figa1, include = T, cache=T,  fig.cap = "Posterior distribution of intercept and slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 5}
 
@@
 
-## Speaker informativeness and common ground sensitivity
+## Speaker informativeness and sensitivity to common ground
 

### 2021-05-20 paper/supplementary_material.Rmd
update supplement

@@
     number_sections: false
+  bookdown::pdf_document2:
+    toc: yes 
+    number_sections: false    
 bibliography: library.bib
@@
   \usepackage{caption}
-  \renewcommand{\thetable}{S\arabic{table}} 
-  \renewcommand{\thefigure}{S\arabic{figure}}
+  \renewcommand{\figurename}{Supplementary Figure}
+  \renewcommand{\tablename}{Supplementary Table}
 ---

### 2021-07-01 paper/manuscript.Rmd
add paper citation

@@
 ---
-title             : "How young children integrate information sources to infer the meaning of words"
+title: |
+    | Published as:
+    | Bohn, M., Tessler, M.
+H., Merrick, M., & Frank, M.
+C.
+(2021).
+How young children integrate information sources to infer the meaning of words.
+Nature Human Behaviour.
+https://doi.org/10.1038/s41562-021-01145-1
+    | 
+    | 
+    | 
+    | How young children integrate information sources to infer the meaning of words
+
 shorttitle        : "Rational information integration in children"
